### 2019-07-03 tex/Crossingless.tex
Skeleton of irreducibility proof; mathings macros

\documentclass{amsart}   
\usepackage{RepStyle}

\usepackage{CJKutf8}

\begin{document}

\title{The Two-Column Specht Module of the Hecke Algebra of $S_n$}
\author{Miles Johnson \& Natalie Stewart}
\maketitle

\section{Introduction}
Let $S_{2n}$ be the symmetric group on $2n$ indices, let $\SH = \SH_{k,q}(S_{2n})$ be the corresponding Hecke algebra with parameter $p$, and let $S = \cbr{T_1,\dots,T_{n-1}}$ be the simple transpositions generating $\SH$.
Let $V := S^{(2,\dots,2)}$ be the Specht module corresponding to the young diagram with rows of length 2.
The purpose of this writing is to characterize this representation via an isomorphism with another representation of $\SH$.
\begin{definition}
  A \emph{crossingless matching} on $2n$ indices is a partition of $\cbr{1,\dots,2n}$ into parts of size $2$ such that no two parts ``cross'', i.e. there are no parts $(a,a')$ and $(b,b')$ such that $a < b < a' < b'$.
  Then, define $W_{2n}$ to be the $\CC$-vector space with basis the set of crossingless matchings on 2n indices.

  In order for this to be a $\SH$-module, endow this with the action given by Figure \ref{Action}; if this creates a loop, simply scale by $(1 + q)$, and otherwise deform into a crossingless matching and scale by $q^{1/2}$.
\end{definition}

\begin{figure}
  \[
    \Action{6}{1/4, 2/3, 5/6}{4}{1/6, 2/3, 4/5}{q^{1/2}}
    \hspace{50pt}
    \Action{6}{1/4, 2/3, 5/6}{2}{1/4, 2/3, 5/6}{(1 + q)}
  \]
  \caption{Illustration of the actions $(1 + T_4)w_3$ and $(1 + T_2)w_3$ in $W_6$.
  In general, we act on basis elements by simple transpositions by deleting loops, deforming into a crossingless matching, and scaling based on whether a loop was deleted.}
  \label{Action}
\end{figure}

Let the length of an arc $(i,j)$ be $l(i,j) := j - i + 1$.
Note that the crossingless matchings can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
using this, we may order the crossingless matchings in increasing lexicographical order in order to obtain an order on the basis.
Let $C_n$ be the $n$th catalan number, and let the resulting basis for $W_{2n}$ be $\cbr{w_1,\dots,w_{C_n}}$ as illustrated in Figure \ref{S6 Basis}.

\begin{figure}
  \def\cbasisspacing{5mm}
  $\cbr{
    \begin{gathered}
      \Matching{6}{1/2, 3/4, 5/6}, \hspace{\cbasisspacing}
      \Matching{6}{1/2, 3/6, 4/5}, \hspace{\cbasisspacing}
      \Matching{6}{1/4, 2/3, 5/6}, \hspace{\cbasisspacing}
      \Matching{6}{1/6, 2/3, 4/5}, \hspace{\cbasisspacing}
      \Matching{6}{1/6, 2/5, 3/4}
    \end{gathered}}$
    \caption{The increasing lexicgraphical basis for $W_{6}$.}
  \label{S6 Basis}
\end{figure}

We will prove that $W := W_{2n}$ is isomorphic to $V$ as representations in the case that $\SH$ is semisimple.
To do so, we will prove that $W$ has an irreducible restriction to $S_{2n-1} \subset S_{2n}$;
using the branching theorem, this implies that $W$ is isomorphic to a Specht module corresponding to a rectangular young diagram.

We will move on to prove that these modules have unique dimension up to transposition of the diagram;
then, we will show that $\dim V = \dim W$ so that $W$ corresponds to an $n \times 2$ or $2 \times n$ diagram.
We will then do a short character computation to prove that $V \cong W$.

\section{Irreducibility} 
We can now begin by proving that $\Res_{\SH_{k,p}(S_{2n - 1})}^{\SH_{k,p}(S_{2n})} W$ is irreducible;
in partuclar, this implies that $W$ itself is irreducible, as an $\SH$-subrepresentation is a $\SH_{k,p}(S_{2n - 1})$-subrepresentation.
\begin{proposition}
  Set $\SH' := \SH_{k,p}(S_{2n - 2}) \subset \SH$.
  Then, $\Res_{\SH'}^{\SH} W$ is irreducible if $q$ is generic or a primitive $e$'th root of unity for $e \geq n + 1$ or $e = 2$.
\end{proposition}
\begin{proof}
  We will prove the equivalent condition that each vector in $w \in W$ is \emph{cyclic}, i.e. $\SH' w = W$.

  We will first prove that $w_1$ is cyclic, for which it is sufficient to prove that every basis vector of $W$ is in $Aw_1$.
  fix wome basis vector $w_k$, and suppose that it contains arc $(1,j)$,
  Then, the vector
  \[
    w' := (1 + T_2)(1 + T_4)\dots(1 + T_{j-2})w_1
  \]
  contains an arc $(1,j)$ and all other arcs are of the form $(a,a+1)$ for some $a$.
  We may separately act on the subset of arcs with $1 < a < j$ and with $a > j$;
  this process gave our base case of $W_4$, and allows us to recurse to $W_{2m}$ with $m < n$, outlining explicit vectors $h \in \SH'$ with $hw_1 = w_i$.
  Hence it is sufficient to prove that $w_1$ is generated by every $w \neq 0 \in W$.

  Since the image of $(1 + T_i)$ has arc $(i,i+1)$, it is isomorphic as a vector space to $W_{2n}$ with $2n - 2$ vertices.\footnote{This ismorphism ``ignores'' the arc $(i,i+1)$.}
  This isomorphism carries $w_1$ to an equivalent vector $w'_1$ in $W_{2n - 2}$ containing all length-2 arcs.
  Further, all actions of $(1 + T'_j) \in \SH_{k,p}(S_{2n - 4})$ act identically (through the isomorphism) with simple transpositions other than $1 + T'_i$, which acts equivalently to $(1 + T_i)(1 + T_{i + 1})(1 + T_{i - 1})$ as illustrated in Figure \ref{bigloop};
  hence, if the image of $(1 + T_i)w$ in $W_{2n - 2}$ generates an ideal containing $w'_1$, then $(1 + T_i)w$ generates an ideal containing $w_1$, and hence $w$ is cyclic.

  \begin{figure}[b]
  \[
    \Action{6}{1/6, 2/5, 3/4}{2}{1/6, 2/3, 4/5 }{q^{1/2}} \hspace{20pt} 
    \IsoAction{8}{1/8, 2/7, 3/4, 5/6}{3}{1/8, 2/5, 3/4, 6/7}{q^{1/2}}
  \]
  \caption{The correspondence between the action of $(1 + T_2)$ on $w'_5 \in W_6$ and the action of $(1 + T_3)(1 + T_4)(1 + T_2)$ on the corresponding vector in $W_8$ having arc $(3,4)$.}
  \label{bigloop}
  \end{figure}

  We are now ready to make the central claim in our proof:
  \begin{claim*}
    Suppose $n > 1$.
    Then, the intersection $K := \bigcap_{i = 1}^{2n - 2} \ker (1 + T_i)$ is trivial if and only if $e \neq n + 1$.
  \end{claim*}
  This claim is necessary for irreducibility, as $K$ is a proper subrepresentation of $W$.

  Suppose this claim is true.
  We will use induction on $n$ to prove irreducibility;
  the base case $n = 1$ is clear, so suppose $W_{2n - 2}$ is irreducible for all $e \geq n$ or $e = 2$, and pick some $w \in W_{2n}$.
  Then, pick some $1 + T_i$ such that $(1 + T_i)w \neq 0$, and pick some action $h' \in W_{2n - 2}$ which takes the image of $(1 + T_i)w$ in $W_{2n - 2}$ to $w'_1$;
  this pulls back to an action $h \in W_{2n}$ such that $h(1 + T_i)w = w_1$, so $W_{2n}$ is irreducible.

 \textit{Proof of claim.}
 \newcommand{\textoverline}{$\overline{\mbox{\phantom{L}}}$}
 \begin{CJK}{UTF8}{min}
 \textoverline\verb|\_(ツ)_/|\textoverline
\end{CJK}
\end{proof}

Suppose $\SH$ is semisimple;
then $W$ is a Specht module corresponding to a rectangular region.
We may now use dimension, for which one should note that there is an easy bijection between standard tableaus on $n = 2 + \dots + 2$ and the Dyck paths on $2n$ points by specifying that the number in the $(i,1)$ box of the tableau is the index of the $i$th ``up'' path.
Hence $V_{(2,\dots,2)}$ has dimension the $n$th catalan number $C_n$.

Similarly, we may biject the Dyck paths on $2n$ points with the crossingless matchings, by making the value at point $i$ the number of ``open crossings'' at that point, i.e. the number of arcs $(a,b)$ with $a \leq i < b$.
Hence $V$ and $W$ have the same dimension.
This pins the shape of the diagram corresponding to $W$ as follows.

\begin{proposition}
  Let $V_1$ and $V_2$ be two specht modules corresponding to $a_1 \times b_1$ and $a_2 \times b_2$ rectangular young diagrams.
  Then, $\dim V_1 = \dim V_2$ if and only if the diagram of $V_1$ is the same as or a transposition of the diagram of $V_2$.
\end{proposition}
\begin{proof}
  Recall that, if they have the same diagram then $V_1 \cong V_2$, and if they're transposed from each other, $V_1 \cong V_2 \otimes U$ where $U$ is the alternating representation;
  hence $\dim V_1 = \dim V_2 \cdot \dim U = \dim V_2$.

  Suppose WLOG that $a_1 < a_2 < b_2 < b_1$.
  By the hook-length formula, it is sufficient to give a bijective correspondence between the boxes in $V_2$ and $V_1$ such that the hook-length in $V_2$ is larger than the hool-length in $V_1$, and at least once strictly larger.
  We can give this correspondence by listing the boxes beginning at the bottom right corner, then increasing up left-to-right diagonals, and note that this satisfies our conditions.
\end{proof}

Let $V' := V_{(n,n)}$.
Then, $W$ is isomorphic to exactly one of $V$ and $V'$.
It is hence sufficient to prove that $W$ is not isomorphic to $V'$, and we may do this via a character computation.

\end{document}

### 2019-07-04 tex/Crossingless.tex
Scaled im(1 + T_i) ~ W_{2n - 2} iso; added loop to corresponding figure.

@@
 
+\newpage
 \section{Irreducibility} 
@@
   This isomorphism carries $w_1$ to an equivalent vector $w'_1$ in $W_{2n - 2}$ containing all length-2 arcs.
-  Further, all actions of $(1 + T'_j) \in \SH_{k,p}(S_{2n - 4})$ act identically (through the isomorphism) with simple transpositions other than $1 + T'_i$, which acts equivalently to $(1 + T_i)(1 + T_{i + 1})(1 + T_{i - 1})$ as illustrated in Figure \ref{bigloop};
+  Further, all actions of $(1 + T'_j) \in \SH_{k,p}(S_{2n - 4})$ act identically (through the isomorphism) with simple transpositions other than $1 + T'_i$, which acts equivalently to $q^{-1}(1 + T_i)(1 + T_{i + 1})(1 + T_{i - 1})$ as illustrated in Figure \ref{bigloop};
   hence, if the image of $(1 + T_i)w$ in $W_{2n - 2}$ generates an ideal containing $w'_1$, then $(1 + T_i)w$ generates an ideal containing $w_1$, and hence $w$ is cyclic.
@@
   \]
-  \caption{The correspondence between the action of $(1 + T_2)$ on $w'_5 \in W_6$ and the action of $(1 + T_3)(1 + T_4)(1 + T_2)$ on the corresponding vector in $W_8$ having arc $(3,4)$.}
+  \[
+    \Action{4}{1/4, 2/3}{2}{1/4,2/3}{(1 + q)} \hspace{20pt}
+    \IsoAction{6}{1/6, 2/5, 3/4}{3}{1/6, 2/5, 3/4}{(1 + q)}
+  \]
+  \caption{The correspondence between the action of $(1 + T_2)$ on $w'_5 \in W_6$ and the action of $q^{-1}(1 + T_3)(1 + T_4)(1 + T_2)$ on the corresponding vector in $W_8$ having arc $(3,4)$ first, then on $w'_2 \in W_4$.
+  This demonstrates that the action works with and without creating a loop.
+  }
   \label{bigloop}

### 2019-07-04 tex/Crossingless.tex
Added determinental step to irreducibility proof

@@
     Suppose $n > 1$.
-    Then, the intersection $K := \bigcap_{i = 1}^{2n - 2} \ker (1 + T_i)$ is trivial if and only if $e \neq n + 1$.
+    Then, the intersection $K := \bigcap_{i = 1}^{2n - 2} \ker (1 + T_i)$ is trivial if $e$ does not divide $n + 1$.
   \end{claim*}
@@
  \textit{Proof of claim.}
- \newcommand{\textoverline}{$\overline{\mbox{\phantom{L}}}$}
- \begin{CJK}{UTF8}{min}
- \textoverline\verb|\_(ツ)_/|\textoverline
-\end{CJK}
+ Note that $\bigcap \ker(1 + T_i)=\ker\prn{\bigoplus (1 + T_i)}$.
+ Further, we may postcompose this with the isomorphism $\ima(1 + T_i) \simeq W_{2n - 2}$ in order to arrive at a $(n - 2)C_{n-1} \times C_n$ matrix $A$ whose kernel is $K$.
+ Further, we may apply elementary row operations to this matrix, postcomposing with a change of basis, and preserve the kernel of this matrix as well.
+
+ We may characterize these rows as follows:
+ the row corresponding to $(1 + T_i)$ and mapping into the element $w_k \in W$ is of the form $[a_1,\dots,a_{C_n}]$ where $a_k = 1 + q$, $a_j = q^{1/2}$ whenever $(1 + T_i)w_j = q^{1/2}w_k$, and 0 otherwise.
+ In particular, we may characterize some particular rows with few nonzero entries.
+
+ First, the row of $A$ corresponding to $(1 + T_n)$ and $w_{C_n}$ will be of the form $[0,\dots,0,q^{1/2},q + 1]$.
+ Similarly, row corresponding to $(1 + T_{n - 1})$ and $w_{C_n - 1}$ will be of the form $[0,\dots,0,q^{1/2},0,q+1,q^{1/2}]$.
+ An inductive process is illustrated in Figure \ref{Submatrix}.
+in order to construct a row corresponding to each $(1 + T_{n - i})$ with nonzero components appearing in the order $q^{1/2}, q + 1, q^{1/2}$ and having the last two of these appear above the first two in the row corresponding to $(1 + T_{n - i - 1})$.
+ This process works for $1 \leq i \leq n - 1$, and two-nonzero-element rows, which are in column-alignment with the appropriate elements in $(1 + T_{2})$ and $(1 + T_{n - 1})$.
+
+ \begin{figure}
+   \[
+     \Action{10}{1/2,3/10,4/9,5/8,6/7}{2}{1/10,2/3,4/9,5/8,6/7}{q^{1/2}}
+   \]
+   \[
+     \Action{10}{1/10,2/3,4/9,5/8,6/7}{2}{1/10,2/3,4/9,5/8,6/7}{q+1}
+   \]
+   \[
+     \Action{10}{1/10,2/9,3/4,5/8,6/7}{2}{1/10,2/3,4/9,5/8,6/7}{q^{1/2}}
+   \]
+   \caption{Illustrated is the row constructed for transposition $(1 + T_2)$; clearly these are the only basis elements mapping to multiples of the desired element, and they relate to each other.
+     In general, the basis elements considered are the preimages of $w_{C_{n-1}}$ in the isomorphism $\ima(1 + T_i) \simeq W_{2n - 2}$.}
+ \label{Submatrix}
+ \end{figure}
+
+ This construction yields a $n \times C_n$ submatrix of $A$ which has nonzero entries on the rightmost column, and has (by removing zero columns) the same column space as the following:
+  % this is incredibly finnicky.
+  \newcommand*\bigzero{\makebox(0,15){\text{\Huge0}}}
+  \newcommand*\bigzerotwo{\makebox(-20,15){\text{\Huge0}}}
+  \[
+    \begin{bmatrix}
+      \begin{matrix}
+      q + 1 & q^{1/2} & \\
+      q^{1/2} & q + 1 & q^{1/2}\\
+      & q^{1/2} & q + 1 & q^{1/2}\\
+      &  & \ddots & \ddots
+      \end{matrix}
+      &   \bigzero\\
+      \bigzerotwo & \begin{matrix}
+        q^{1/2} & q+1 & q^{1/2}\\
+        &  q^{1/2} & q + 1
+       \end{matrix}
+    \end{bmatrix}
+  \]
+  We may recursively compute that this matrix has determinent $1 + q + \dots + q^n$, which vanishes exactly at the primitive $e$th roots of unity where $e$ divides $n + 1$;
+  henceforth assume that $q$ does not cause this to vanish.
+  Then, this matrix is invertible, so we may use elementary row operations to transform it into the identity;
+  these correspond to elementary row operations on $A$ which yield a row $[0,\dots,0,1]$.
+  Hence any vector $w \in K$ has a zero coefficient corresponding to $w_{C_n}$.
+  We will now prove that every nonzero vector $w \in K$ must have a nonzero coefficient corresponding to $w_{C_n}$, giving that $K = 0$. 
 \end{proof}

### 2019-07-05 tex/Crossingless.tex
Added summary, fixed issue with induction, included characteristic e fields

@@
 \section{Introduction}
-Let $S_{2n}$ be the symmetric group on $2n$ indices, let $\SH = \SH_{k,q}(S_{2n})$ be the corresponding Hecke algebra with parameter $p$, and let $S = \cbr{T_1,\dots,T_{n-1}}$ be the simple transpositions generating $\SH$.
+Let $S_{2n}$ be the symmetric group on $2n$ indices, let $\SH = \SH_{k,q}(S_{2n})$ be the corresponding Hecke algebra with parameter $q$, and let $S = \cbr{T_1,\dots,T_{n-1}}$ be the simple transpositions generating $\SH$.
+Let $\brk{k}_q = 1 + q + \dots + q^{k-1}$ be the $q$-number of $K$. 
+Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
+Either $q = 1$ and $e$ is the characteristic of $k$, or $q \neq 1$ and $q$ is a primitive $e$th root of unity.
+
 Let $V := S^{(2,\dots,2)}$ be the Specht module corresponding to the young diagram with rows of length 2.
@@
   Set $\SH' := \SH_{k,p}(S_{2n - 2}) \subset \SH$.
-  Then, $\Res_{\SH'}^{\SH} W$ is irreducible if $q$ is generic or a primitive $e$'th root of unity for $e \geq n + 1$ or $e = 2$.
+  Then, $\Res_{\SH'}^{\SH} W$ is irreducible if $e \geq n + 1$.
 \end{proposition}
@@
   Since the image of $(1 + T_i)$ has arc $(i,i+1)$, it is isomorphic as a vector space to $W_{2n}$ with $2n - 2$ vertices.\footnote{This ismorphism ``ignores'' the arc $(i,i+1)$.}
-  This isomorphism carries $w_1$ to an equivalent vector $w'_1$ in $W_{2n - 2}$ containing all length-2 arcs.
   Further, all actions of $(1 + T'_j) \in \SH_{k,p}(S_{2n - 4})$ act identically (through the isomorphism) with simple transpositions other than $1 + T'_i$, which acts equivalently to $q^{-1}(1 + T_i)(1 + T_{i + 1})(1 + T_{i - 1})$ as illustrated in Figure \ref{bigloop};
-  hence, if the image of $(1 + T_i)w$ in $W_{2n - 2}$ generates an ideal containing $w'_1$, then $(1 + T_i)w$ generates an ideal containing $w_1$, and hence $w$ is cyclic.
+  hence, if the image of $(1 + T_i)w$ in $W_{2n - 2}$ generates an ideal containing $w'_1$.
 
+  Then $(1 + T_i)w$ generates an ideal containing the pre-image of $w'_1$, which may either be $w_1$ if $i$ is odd or the basis vector containing $(i-1,i+2)$, $(i,i+1)$, and all other arcs length 2 if $i$ is even.
   \begin{figure}[b]
@@
   We will use induction on $n$ to prove irreducibility;
-  the base case $n = 1$ is clear, so suppose $W_{2n - 2}$ is irreducible for all $e \geq n$ or $e = 2$, and pick some $w \in W_{2n}$.
+  the base case $n = 1$ is clear, so suppose $W_{2n - 2}$ is irreducible for all $e \geq n$ or, and pick some $w \in W_{2n}$.
   Then, pick some $1 + T_i$ such that $(1 + T_i)w \neq 0$, and pick some action $h' \in W_{2n - 2}$ which takes the image of $(1 + T_i)w$ in $W_{2n - 2}$ to $w'_1$;
-  this pulls back to an action $h \in W_{2n}$ such that $h(1 + T_i)w = w_1$, so $W_{2n}$ is irreducible.
+  this pulls back to an action $h \in W_{2n}$ such that $h(1 + T_i)w$ is the preimage of $w'_1$.
+
+  If $i$ is odd then we have $h(1 + T_i)w = w_1$ and we are done. 
+  Otherwise, $h(1 + T_i)w$ is a basis vector with the arc $(i-1,i+2)$ and all other arcs having length 2;
+  hence $(1 + T_{i-1})h(1 + T_i)w = w_1$ and we are done.
 
@@
 
- \begin{figure}
+ \begin{figure}[b]
    \[
@@
   \]
-  We may recursively compute that this matrix has determinent $1 + q + \dots + q^n$, which vanishes exactly at the primitive $e$th roots of unity where $e$ divides $n + 1$;
-  henceforth assume that $q$ does not cause this to vanish.
+  We may recursively compute that this matrix has determinent $\brk{n+1}_q$, which vanishes exactly when $e \mid n + 1$;
+  henceforth assume that this does not vanish.
   Then, this matrix is invertible, so we may use elementary row operations to transform it into the identity;
@@
 
+\section{Correspondence with the Specht Module}
 Suppose $\SH$ is semisimple;
@@
 
+\newpage
+\section{Summary of Results}
+What follows is a color-coded list of propositions on crossingless matchings.
+Those which are blue are {\color{blue}confirmed}, those which are olive are {\color{olive} in progress/soon to be proven}, and those which are red are {\color{red} conjectural}.
+
+{\color{blue}
+\begin{proposition}
+  Suppose $n > 1$.
+  Then, the intersection $K := \bigcap_{i = 1}^{2n - 2} \ker (1 + T_i)$ is trivial if $e$ does not divide $n + 1$.
+\end{proposition}
+
+\begin{proposition}
+  Define the subalgebra $\SH' := \SH_{k,p}(S_{2n - 2}) \subset \SH$.
+  Then, $\Res_{\SH'}^\SH W$ is irreducible if $e \geq n + 1$.
+\end{proposition}}
+
+{\color{olive}
+  \begin{proposition}
+    Suppose $\SH$ is semisimple, i.e. $e > 2n$.
+    Then, $V \simeq W$.
+  \end{proposition}
+}
+
+{\color{red}
+\begin{proposition}
+  The intersection $K := \bigcap_{i = 1}^{2n - 2} \ker (1 + T_i)$ is nontrivial when $e = n + 1$.
+\end{proposition}
+\begin{proposition}
+  $W$ is reducible when $e \leq n + 1$.
+\end{proposition}
+\begin{proposition}
+  Even if $e \leq 2n$, we have $V \simeq W$.
+\end{proposition}
+}
+
 \end{document}

### 2019-07-06 tex/Crossingless.tex
Added disproof of fibonacci representation

@@
   Otherwise, $h(1 + T_i)w$ is a basis vector with the arc $(i-1,i+2)$ and all other arcs having length 2;
-  hence $(1 + T_{i-1})h(1 + T_i)w = w_1$ and we are done.
+  hence $q^{-1/2}(1 + T_{i-1})h(1 + T_i)w = w_1$ and we are done.
 

### 2019-07-06 tex/Fibonacci-Contradiction.tex
Added disproof of fibonacci representation

\documentclass{amsart}   
\usepackage{RepStyle}
\begin{document}
\title{There is no Fibonacci Representation of $\SH_{k,q}(S_{n})$}
\author{Miles Johnson \& Natalie Stewart}
\maketitle

Let $k$ be a field, and let $q \neq 0 \in k$ be the parameter of the Hecke algebra $\SH := \SH_{k,q}(S_n)$.
We will show that there is no ``Fibonacci'' representation of $\SH$.

First, let $F$ be the vector space with basis given by the strings of length $n + 1$ with alphabet $\cbr{p,*}$ such that no two $*$ symbols appear in a row.
This is given an action by the braid group that we will try to emulate.
We want an action which is ``local'', i.e. the simple transposition $T_i$ acts on the string from the $i$th to the ($i + 2$)nd symbol, modifying only the middle character, defined by the following rule:
\begin{align}
  \begin{split}
  \widehat{(*pp)} &:= a(*pp)\\
  \widehat{(*p*)} &:= b(*p*)\\
  \widehat{(p*p)} &:= c(p*p) + d(ppp)\\
  \widehat{(pp*)} &:= a(pp*)\\
  \widehat{(ppp)} &:= d(p*p) + e(ppp).
  \end{split}
  \label{Definitions}
\end{align}
For suitable constants $a,b,c,d,e \in k$.
\subsection*{Quadratic Relation}
Note that the quadratic relation $T_i^2 = (q -1)T_i + q$ imposes the following restrictions on the constants:
\begin{align}
  \begin{split}
  a^2 &= (q-1)a + q\\
  b^2 &= (q-1)b + q\\
  c^2 + d^2 &= (q -1)c + q\\
  de &= (q-1)d\\
  e^2 + d^2 &= (q -1)e + q\\
  dc &= (q-1)d
\end{split}
  \label{Quadratic}
\end{align}
Note that we immediately have
\begin{align}
  \begin{split}
  a,b &\in \cbr{\frac{q - 1 \pm \sqrt{(q-1)^2 + 4q}}{2}}\\
  &= \cbr{\frac{q - 1 \pm (q + 1)}{2}}\\
  &= \cbr{-1,q}.
\end{split}
\label{ab}
\end{align}
Further, if $d = 0$ then we have $c,e \in \cbr{-1,q}$;
if $d \neq 0$ then we have that $c = e = (q - 1)$, and $d \in \cbr{\pm \sqrt{q}}$.

\subsection*{Braid Relations}
Here's where we'll run into some issues.
%First, the braid relation $T_iT_j = T_jT_i$, $\abs{i - j} > 1$ is satisfied, as the action $T_i$ will be entirely unaffected by $T_j$, and one can see that this allows them to easily commute my commitativity of multiplication in $k$.

We must verify the relation $T_iT_{i+1}T_i = T_{i+1}T_iT_{i+1}$.
We can try to directly confirm this on length-4 strings: 
\begin{itemize}
  %\item $(*pp*)$ requires that $a^3 = a^3$, which is guaranteed.
  \item $(*ppp)$ requires that $adb = bcd + ade$ and $a^2d = ae^2 + bd^2$.
    If $d = 0$, then we require that $ae^2 = 0$ with $a,e \neq 0$, a contradiction.
    Hence we require that $d^2 = q$ and $c = e = (q-1)$.

    With the restrictions given above, the first of the above equivalently requires
    \begin{align}
      ab &= b(q-1) + a(q-1)
    \label{appp}
    \end{align}

   \item $(pppp)$ requires that $acd + de^2 = ade$.
     Equivalently, we require that $e^2 = 0$, i.e. $d = q = 1$.
     Then, by \eqref{appp}, we require that $ab = 0$, but $a,b \neq 0$;
     this is a contradiction, so there are no constants $a,b,c,d,e$ which make this a representation of $\SH$.

     \iffalse
    These together imply that $a = b$, and that $a = 2(q-1)$;
    when $q \neq \frac{1}{2}, 2$ this contradicts \eqref{ab}.
  \item $(*p*p)$ requires that $b^2c = bc^2 + ad^2$ and $abd = bcd + ade$.
    Equivalently, we require that
    \begin{align}
      b^2(d^2-1) &= b(d^2-1)^2 + ad^2 \label{bq}\\
      ab &= b(q-1) + a(q - 1).\nonumber
    \end{align}
    In particular, we have that
    \[
      bd^4 + (a - 2b - b^2)d^2 + b - b^2 = 0 = ad^4 + (b - 2a)d^2 - a^2d + a. 
    \]
    Equivalently, $d$ is a root of the polynomial $(a-b)d^4 + (3b - 3a + b^2)d^2 - a^2d + (2b + b^2)$.
    \fi

     %$(*pp*), $(p*pp)$, $(pp*p)$, $(p*p*)$, $(ppp*)$.
\end{itemize}

% this is actually wrong, we need that de = dc = 0, so if d is nonzero then c,e are 0 and the braid relations may give some more interesting restrictions?
\iffalse
\subsection*{The Degenerate Case}
For completeness, let's actually consider the case $q = 0$;
then, as seen above, we actually require that $d = 0$, so that $a,b,c,e \in \cbr{-1,0}$.

Then, the $(*ppp)$ braid relation we require that $ae^2 = 0$, so that at least one of $a,e$ is 0.
As far as I can tell, there are no other restrictions, so there are 12 possible ``Fibonacci'' representations for the case $q = 0$.
\fi
\end{document}

### 2019-07-06 tex/Fibonacci-Contradiction.tex
Corrections/generalization on fibonacci contradiction

@@
 We must verify the relation $T_iT_{i+1}T_i = T_{i+1}T_iT_{i+1}$.
-We can try to directly confirm this on length-4 strings: 
+Let's begin with the case $d \neq 0$, which we can verify on the following strings:
 \begin{itemize}
   %\item $(*pp*)$ requires that $a^3 = a^3$, which is guaranteed.
-  \item $(*ppp)$ requires that $adb = bcd + ade$ and $a^2d = ae^2 + bd^2$.
-    If $d = 0$, then we require that $ae^2 = 0$ with $a,e \neq 0$, a contradiction.
-    Hence we require that $d^2 = q$ and $c = e = (q-1)$.
+  \item $(*ppp)$ requires that $abd = bcd + ade$ and $a^2e = ae^2 + bd^2$.
+    % If $d = 0$, then we require that $ae^2 = 0$ with $a,e \neq 0$, a contradiction.
+    % Hence we require that $d^2 = q$ and $c = e = (q-1)$.
 
-    With the restrictions given above, the first of the above equivalently requires
+    The first of the above equivalently requires
     \begin{align}
@@
 
+Now suppose that $d = 0$.
+One thing which is immediately clear is the decomposition into one-dimensional subrepresentations (the spans of each basis vector) if this is a representation.
+Note that $(*ppp)$ requires that $a^2e = ae^2$, i.e. $a = e$.
+Similarly, $(*p*p)$ requires that $b = c$.
+Further, we still satisfy the relations for $(pppp)$, we always satisfy the relations for $(*pp*)$, and the rest of the strings are compatible by symmetry.
+All that is left are the relations $T_iT_j = T_jT_i$ for $\abs{i - j} > 1$, which are easy to see.
+Hence, for each $q$, there are 4 ``good'' actions on $F$, each of which decomposes into a direct sum of one-dimensional subrepresentations.
+
+\subsection*{A More General Case}
+Now, consider a modification of \eqref{Definitions}:
+\begin{align}
+  \begin{split}
+  \widehat{(*pp)} &:= a(*pp)\\
+  \widehat{(*p*)} &:= b(*p*)\\
+  \widehat{(p*p)} &:= c(p*p) + d(ppp)\\
+  \widehat{(pp*)} &:= g(pp*)\\
+  \widehat{(ppp)} &:= f(p*p) + e(ppp).
+  \end{split}
+  \label{General Definitions}
+\end{align} 
+This time, the quadratic relation reads
+\begin{align}
+  \begin{split}
+  a^2 &= (q-1)a + q\\
+  b^2 &= (q-1)b + q\\
+  g^2 &= (q-1)g + q\\
+  c^2 + df &= (q -1)c + q\\
+  de &= (q-1)d\\
+  e^2 + df &= (q -1)e + q\\
+  fc &= (q-1)f
+\end{split}
+  \label{General Quadratic}
+\end{align}
+Notably, we have $a,b,g \in \cbr{-1.q}$ still.
+If $d = 0$ or $f = 0$, then $c,e \in \cbr{-1,q}$ still, and if $d = 0$ and $f \neq 0$, then $c = (q-1)$, and hence $c = 1$ and $q = 2$.
+If $d \neq 0$, we still have that $c = e = (q-1)$, and we have that $df = q$.
+
+Now, suppose that $d,f \neq 0$.
+Now, $(*ppp)$ requires that $abf = bcf + aef$ and $a^2e = ae^2 + bf^2$, so as before we have that $ab = (a+b)(q-1)$.
+
+$(pppp)$ now requires that $aef = acf + e^2f$.
+This requires that $e^2 = 0$, so that $q = 1$ and $ab = 0$, a contradiction again.
+
+Now, suppose that $f \neq 0$ and $d = 0$, so that $q = 2$ and $c = 1$.
+Then, we have that $a(e-1) = e^2$.
+Then, knowing that $e^2 \neq 0$, we have $e = -1$ so $-2a = 1$, a contradiction.
+By symmetry, we also arrive at a contradiction if $d \neq 0$ and $f = 0$.
+
+Finally, suppose that $d = f = 0$, and note that we now have $a = e = g$ and $b = c$;
+hence our case is precisely the case with $d = f$ and $a = g$, and there are exactly four actions of $\SH$ on $F$ on which each $T_i$ acts analogously on positions $i,i+1,i+2$ as each other, only modifying position $i+1$.
+Each of these actions decomposes into a direct sum of 1-dimensional subrepresentations.
+
 % this is actually wrong, we need that de = dc = 0, so if d is nonzero then c,e are 0 and the braid relations may give some more interesting restrictions?
 \iffalse
+
 \subsection*{The Degenerate Case}

### 2019-07-12 tex/Crossingless.tex
Cleaned up action macro, changed ifthenelse to ifnum
Split matching macros into NatMacros and MilesMacros for workaround
yeet
Initial proof for fibonacci representation

@@
 \usepackage{RepStyle} 
-
-\usepackage{CJKutf8}
-
+\usepackage{NatMacros} %********REPLACE WITH MilesMacros TO KILL RELIANCE ON \ifnum AND HAVE INCOMPLETE OUTPUT***********bleh
 \begin{document}
@@
 \section{Introduction}
-Let $S_{2n}$ be the symmetric group on $2n$ indices, let $\SH = \SH_{k,q}(S_{2n})$ be the corresponding Hecke algebra with parameter $q$, and let $S = \cbr{T_1,\dots,T_{n-1}}$ be the simple transpositions generating $\SH$.
-Let $\brk{k}_q = 1 + q + \dots + q^{k-1}$ be the $q$-number of $K$. 
+Let $S_{2n}$ be the symmetric group on $2n$ indices, let $\SH = \SH_{k,q}(S_{2n})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k$, and let $\cbr{T_i}$ be the simple transpositions generating $\SH$.
+Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of $m$. 
 Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
@@
 there are no parts $(a,a')$ and $(b,b')$ such that $a < b < a' < b'$.
-  Then, define $W_{2n}$ to be the $\CC$-vector space with basis the set of crossingless matchings on 2n indices.
+  We will call these arcs.
+  Then, define $W_{2n}$ to be the $k$-vector space with basis the set of crossingless matchings on 2n indices.
 
@@
   Set $\SH' := \SH_{k,p}(S_{2n - 2}) \subset \SH$.
-  Then, $\Res_{\SH'}^{\SH} W$ is irreducible if $e \geq n + 1$.
+  Then, $\Res_{\SH'}^{\SH} W$ is irreducible if $e > n + 1$.
 \end{proposition}

### 2019-07-12 tex/Fibonacci.tex
Initial proof for fibonacci representation

\documentclass{amsart}   
\usepackage{RepStyle}
\usepackage{ytableau}

\begin{document}
\title{Whoops, there is a Fibonacci Representation of $\SH_{k,q}(S_{n})$}
\author{Miles Johnson \& Natalie Stewart}
\maketitle

Let $k$ be a field, and let $q \neq 0 \in k$ be the parameter of the Hecke algebra $\SH := \SH_{k,q}(S_n)$.
Let $F^m$ be the vector space with basis given by the strings $\cbr{*,p}^{m+2}$ in which the character $*$ doesn't appear twice in a row.
We will act on this by $\SH$ by defining the action of $T_i$ ``locally'', and changing character $i+1$ only dependent on characters $i,i+1,i+2$.
We will use ``hat'' notation e.g. $(1 + T_1)(pppp) = (\widehat{ppp}p)$.
Then, we may define our action as follows:
\begin{align*}
  \widehat{(*pp)} &:= a(*pp)\\
  \widehat{(*p*)} &:= b(*p*)\\
  \widehat{(p*p)} &:= c(p*p) + d(ppp)\\
  \widehat{(pp*)} &:= a(pp*)\\
  \widehat{(ppp)} &:= d(p*p) + e(ppp).
\end{align*}
for constants
\begin{align*}
  a &= -1\\
  b &= q\\
  c &= \tau(q\tau - 1)\\
  d &= \tau^{3/2}(q + 1)\\
  e &= \tau(q-\tau)\\
  \tau &= \frac{2}{1 + \sqrt 5}.
\end{align*}
It is easy to verify that these are compatible with the quadratic and braid relations, and hence define a representation $F^m$ of $\SH$, henceforth referred to as the Fibonacci representation.
This has 4 subrepresentations dependent on the first and last character.
We will characterize these subrepresentations fully in the following section.

\section{Characterization of $F^m$ via Specht Modules}
Let $F^{m} = F^{m}_{*p} \oplus F^{m}_{p*} \oplus F^m_{**} \oplus F^m_{pp}$ be the decomposition of the Fibonacci representation into the 4 subrepresentations depending on the values of the first and last character.
We'll supress the superscripts when the dimension is clear.

Note that $F^m$ has dimension the $m + 1$st fibonacci number $f_{m+2}$, we have $\dim F^m_{**} = f_{m+1}$, $F^m_{*p} \simeq F^m_{p*}$ has dimension $f_m$, and $\dim F^m_{pp} = f_{n-1}$.
Further, note that $m = 2n$ gives that $\dim F^{2m}_{pp} = \dim D^{(2,\dots,2)}$;
we will prove that these modules are isomorphic via the following propositions:
\begin{enumerate}
  \item $F^m_{*p}$ is irreducible, and $\Res \; F^m_{*p} \simeq F^{m-1}_{pp} \simeq F^{m-1}_{*p} \oplus F^{m-1}_{**}$.
  \item $\Res \; F^m_{**} \simeq F^{m-1}_{*p}$.
  \item $F^m$ decomposes into a direct sum of irreducible representations:
    \[
      F^m \simeq 3 F^m_{*p} \oplus 2F_{**}^m
    \]
  \i tem Let $D_{m,k} := D^{(m,m-k)'}$ be the nearly-two-column Specht module. Then,
    \begin{align*}
      \Res \; D_{m,0} &\simeq D_{m-1,1}\\
      \Res \; D_{m,1} &\simeq D_{m-1,0} \oplus D_{m-1,2}\\
      \Res \; D_{m,2} &\simeq D_{m-1,1} \oplus D_{m-1,3}\\
      \Res \; D_{m,3} &\simeq D_{m-1,2}.
     \end{align*}
  \item The claims are henceforth conjectural: 
    \begin{align*}
      F^{2n}_{**} &\simeq D_{n,0}\\ 
      F^{2n-1}_{**} &\simeq D_{n+1,3}\\
      F^{2n}_{*p} &\simeq D_{n+1,2}\\
      F^{2n-1}_{*p} &\simeq D_{n,1}.
     \end{align*}
     If these are true, then
     \begin{align*}
        F^{2n} &\simeq 3D_{n+1,2} \oplus 2D_{n,0}\\
        F^{2n-1} &\simeq 3D_{n,1} \oplus 2D_{n+1,3}.
     \end{align*}
   \item In the $2n = 8$ case, let $K$ be the intersection of kernels of $(1 + T_i)$ for $W$;
    then, we have $W/K \simeq F_{**}$.
\end{enumerate}

We can start by studying low-dimensional cases.
First, note that $F_{*p}^2$ is the sign representation $D^{(2)}$ and $F_{**}^2$ is the trivial representation $D^{(1)^2}$.

$F_{pp}^2$, which is a 2-dimensional representation of a semisimple commutative algebra, and hence decomposes into a direct sum of two subrepresentations.
In particular, we can use the basis $\cbr{(p*p),(ppp)}$ and explicitly write the matrix
\[
  \rho_{T_1} = \begin{bmatrix}
    c & d\\
    d & e
  \end{bmatrix}
\]
having characteristic polynomial $(c - \lambda)(e - \lambda) - d^2 = \lambda^2 - (c + e)\lambda +(ce - d^2)$.
The reader can verify that this has roots are $-1$ and $q$.
The eigenspaces with eigenvalues $-1$ and $q$ are subrepresentations isomorphic to the sign and trivial representation, hence $F_{pp}$ is isomorphic to a direct sum of the trivial and sign representaitons: $F^2_{pp} \simeq F^2_{*p} \oplus F^2_{**}$.

Now let's prove that $F^3_{**}$ is irreducible;
this has basis $\cbr{*p*p}, \cbr{*ppp}$, and the following matrices:
\[
  \rho_{T_1} = \begin{bmatrix}
    b & 0\\
    0 & a
  \end{bmatrix}; \hspace{20pt}
  \rho_{T_2} = \begin{bmatrix}
    c & d\\
    d & e
  \end{bmatrix}.
\]
A subrepresentation must be one-dimensional, and hence an eigenspace of each of these matrices;
since $b \neq a$, the first has eigenspaces given by the spans of basis elements, and since $d \neq 0$, these are not eigenspaces of the second.
Hence $F^3_{**}$ is irreducible.
Now we may move on to the general case.
\begin{proposition}
  The representation $F_{*p} := F^m_{*p}$ is irreducible.
\end{proposition}
\begin{proof}
  We will prove this inductively in $m$.
  We've already proven it for $F^3_{*p}$ and $F^4_{*p}$, so suppose that $F^{m-2}_{*p}$ is irreducible.

  Let $\cbr{v_i}$ be the basis for $F_{*p}$.
  Then, each $v_i$ is cyclic; indeed, we can transform every basis vector into $(*p\dots p)$ by multiplying by the appropriate $\frac{1}{d-c}(T_i - c)$, and we can transform $(*p\dots p)$ into any basis vector by multiplying be the appropriate $\frac{1}{d-e}(T_i - e)$.
  Hence it is sufficient to show that each $v \in F_{*p}$ generate some basis element.

  Let $v'$ be the basis element $(*p*p\dots p)$, which is many copies of $*p$, followed by an extra $p$ if $m$ is odd.
  We will show that each $v \in F$ generates $v'$.

  Say that a basis element $v_i$ is \emph{represented in $v$} if it has nonzero coefficient in $v$.
  Suppose that no elements beginning $(*p*p)$ are represented in $v_i$;
  then, all such elements are represented in $T_3v$, so we may assume that at least one is represented in $v$.

  Note that $(T_2 - a)v$ is a nonzero element where only elements beginning $(*p*p)$ are represented;
  if $F'$ is the subspace of $F_{*p}$ spanned by $v_i$ beginning $(*p*p)$, then $\Res_{\SH(S_{m-2})}^{\SH(S_m)} F' \simeq F^{m-2}_{*p}$, and $v'$ is mapped to the analogous element in $F^{m-2}_{*p}$.
  Hence irreducibility of $F^{m-2}_{*p}$ implies that $v'$ is generated by $(T_2 - a)$, and $F^m_{*p}$ is irreducible.
\end{proof}

There is a bit of bookkeeping to do;
we've equivocated by saying asserting that the subalgebras $\SH_{k,q}(S_{m-r}) \subset \SH_{k,q}(S_{m})$ are equivalent, inclding restrictions.
This works because they are conjugate, and conjugation gives an isomorphism of the restriction of a representation to separate subalgebras.

Knowing this, the restriction statements are clear;
$\Res F_{*p}^m \simeq F_{pp}^{m-1}$ by considering the last $m-2$ transpositions, and $\Res F_{*p}^{m-1} \simeq F_{*p}^{m-1} \oplus F_{**}^{m-1}$ by considering the first $m-2$.
Similarly, $\Res F_{**}^m \simeq F_{*p}^{m-1}$ by considering the first $m-2$ transpositions.
This gives that $F \simeq 3F_{*p} \oplus 2F_{**}$.

Now we may move on and use Young Tableau to characterize $F$.
Recall that the socle of $D^\lambda$ is given by $\bigoplus\limits_{\mu \xrightarrow{\text{good}} \lambda} D^\mu$,  and that $D^\lambda$ is semisimple iff every $\mu \xrightarrow{\text{normal}} \lambda$ is good.
\begin{proposition}
  The irreducible components of $F$ are given by the following isomorphisms:
    \begin{align*}
      F^{2n}_{**} &\simeq D^{(n,n)'}\\ 
      F^{2n-1}_{**} &\simeq D^{(n+1,n-2)'}\\
      F^{2n}_{*p} &\simeq D^{(n+1,n-1)'}\\
      F^{2n-1}_{*p} &\simeq D^{(n,n-1)'}.
     \end{align*}
\end{proposition}
\begin{proof}
  We will prove this by induction on $n$;
  we have already proven the base case $F^{2}$, so suppose that we have proven these isomorphisms for $F^{2n-2}$.
  We will prove the isomorphisms for $F^{2n-1}$ and $F^{2n}$.

  By semisimplicity, $F^{2n-1}_{**} \simeq D^{\lambda_{**}}$ and $F^{2n-1}_{*p} \simeq D^{\lambda_{*p}}$ for some diagrams $\lambda_{**}$ and $\lambda_{*p}$.
  We will show that $\lambda_{**} = (n+1,n-2)'$ and $\lambda_{*p} = (n+1,n-1)'$.

  First, note that we have \[\Res \; D^{\lambda_{**}} \simeq D^{(n,n-2)'} \simeq \Res \; D^{(n+1,n-2)'}\] and \[\Res \; D^{\lambda_{*p}} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)'}.\]
  By semisimplicity, every normal cell in $\lambda_{**}$ and $\lambda_{*p}$ is good, and every good cell is removed in a summand of the restriction.

  In particular, for $\lambda_{**}$, the only tableaus which can remove a cell to yield $D^{(n,n-2)'}$ are $(n+1,n-2)'$, $(n,n-1)'$, and $(n,n-2,1)'$ as illustrated in Figure \ref{OddRes};
  we have already seen that $D^{(n,n-1)'}$ does not have irreducible restriction, so we are left with $(n+1,n-2)'$ and $(n,n-2,1)'$.
  To have irreducible restriction, $\lambda_{**}$ must have 1 as its only normal number;
  we may directly check that $(n,n-2,1)'$ doesn't satisfy this, as we have the following:
  \begin{align*}
    \beta_\lambda(1,2) &= 3 - 2 + (n-2) = n-1\\
    \beta_\lambda(1,3) &= 3 - 1 + n = n+2\\
    \beta_\lambda(2,3) &= 2 - 1 + 3 = 4.
   \end{align*}
  At least one of $\beta(1,2)$ and $\beta(1,3)$ is nonzero, and hence at least one of $M_2$ and $M_3$ is empty.
  Hence at least one of 2 or 3 is normal, and $\lambda_{**} = (n+1,n-2)$.

  For $\lambda_{*p}$, we immediately see from Figure \ref{OddRes} that the only option is $(n,n-1)$.
  \begin{figure}
    \[
      \cbr{
        \begin{gathered}
        \ydiagram{2,2,2,1,1,1}. \; \;
        \ydiagram{2,2,2,2,1}, \; \;
        \ydiagram{3,2,2,1,1}
      \end{gathered} 
    }\longrightarrow \begin{gathered}
      \ydiagram{2,2,2,1,1}
      \end{gathered}
      \hspace{50pt}
      \cbr{
        \begin{gathered}
          \ydiagram{2,2,2,2,1}
        \end{gathered}
      }\longrightarrow
      \begin{gathered}
        \ydiagram{2,2,2,1,1},\;\;
        \ydiagram{2,2,2,2}.
      \end{gathered}
    \]
    \caption{
      Illustration of the partitions of $9$ which can, via row removal, yield $(n,n-2)'$ alone, or both $(n,n-2)'$ and $(n-1,n-1)'$.
    }\label{OddRes}
  \end{figure}

  We can perform a similar argument for the $F^{2n}$ case, finding now that 
  \[\Res \; D^{\mu_{**}} \simeq D^{(n,n-1)'} \simeq \Res \; D^{(n,n)'}\] and 
  \[\Res \; D^{\mu_{*p}} \simeq D^{(n,n-1)'} \oplus D^{(n+1,n-2)'} \simeq \Res \; D^{(n+1,n-1)'}.\]

  Through a similar process, we see that $\mu_{*p} = (n+1,n-1)'$.
  We narrow down $\mu_{**}$ to one of $(n,n)'$ or $(n,n-1,1)'$, and note that
  \begin{align*}
    \beta_\mu(1,2) &= 3 - 2 + (n-1) = n\\
    \beta_\mu(1,3) &= 3 - 1 + n = n+2\\
    \beta_\mu(2,3) &= 2 - 1 + 2 = 3
  \end{align*}
  and hence at least one of 2 or 3 is normal, $\Res D^{(n,n-1,1)'}$ is not irreducible, and $\mu_{**} = (n,n)'$, finishing our proof.
\end{proof}
Hence $F$ is semisimple, and we have its decomposition into quotients of specht modules.
We've proven almost everything that we've set out to;
all that's left is explicit transition matrices $W \rightarrow F_{**}$.

% this was kept for archival purposes
\iffalse
\newpage
\section{Incorrect Proof of Relations}

First, let $F$ be the vector space with basis given by the strings of length $n + 1$ with alphabet $\cbr{p,*}$ such that no two $*$ symbols appear in a row.
This is given an action by the braid group that we will try to emulate.
We want an action which is ``local'', i.e. the simple transposition $T_i$ acts on the string from the $i$th to the ($i + 2$)nd symbol, modifying only the middle character, defined by the following rule:
\begin{align}
  \begin{split}
  \widehat{(*pp)} &:= a(*pp)\\
  \widehat{(*p*)} &:= b(*p*)\\
  \widehat{(p*p)} &:= c(p*p) + d(ppp)\\
  \widehat{(pp*)} &:= a(pp*)\\
  \widehat{(ppp)} &:= d(p*p) + e(ppp).
  \end{split}
  \label{Definitions}
 \end{align} 
For suitable constants $a,b,c,d,e \in k$.
\subsection{Quadratic Relation}
Note that the quadratic relation $T_i^2 = (q -1)T_i + q$ imposes the following restrictions on the constants:
\begin{align}
  \begin{split}
  a^2 &= (q-1)a + q\\
  b^2 &= (q-1)b + q\\
  c^2 + d^2 &= (q -1)c + q\\
  de &= (q-1)d\\
  e^2 + d^2 &= (q -1)e + q\\
  dc &= (q-1)d
\end{split}
  \label{Quadratic}
\end{align}
Note that we immediately have
\begin{align}
  \begin{split}
  a,b &\in \cbr{\frac{q - 1 \pm \sqrt{(q-1)^2 + 4q}}{2}}\\
  &= \cbr{\frac{q - 1 \pm (q + 1)}{2}}\\
  &= \cbr{-1,q}.
\end{split}
\label{ab}
\end{align}
Further, if $d = 0$ then we have $c,e \in \cbr{-1,q}$;
if $d \neq 0$ then we have that $c = e = (q - 1)$, and $d \in \cbr{\pm \sqrt{q}}$.

\subsection{Braid Relations}
Here's where we'll run into some issues.
%First, the braid relation $T_iT_j = T_jT_i$, $\abs{i - j} > 1$ is satisfied, as the action $T_i$ will be entirely unaffected by $T_j$, and one can see that this allows them to easily commute my commitativity of multiplication in $k$.

We must verify the relation $T_iT_{i+1}T_i = T_{i+1}T_iT_{i+1}$.
Let's begin with the case $d \neq 0$, which we can verify on the following strings:
\begin{itemize}
  %\item $(*pp*)$ requires that $a^3 = a^3$, which is guaranteed.
  \item $(*ppp)$ requires that $abd = bcd + ade$ and $a^2e = ae^2 + bd^2$.
    % If $d = 0$, then we require that $ae^2 = 0$ with $a,e \neq 0$, a contradiction.
    % Hence we require that $d^2 = q$ and $c = e = (q-1)$.

    The first of the above equivalently requires
    \begin{align}
      ab &= b(q-1) + a(q-1)
    \label{appp}
    \end{align}

    \item $(pppp)$ requires that $acd + de^2 = ade$.
     Equivalently, we require that $e^2 = 0$, i.e. $d = q = 1$.
     Then, by \eqref{appp}, we require that $ab = 0$, but $a,b \neq 0$;
     this is a contradiction, so there are no constants $a,b,c,d,e$ which make this a representation of $\SH$.

     \iffalse
    These together imply that $a = b$, and that $a = 2(q-1)$;
     when $q \neq \frac{1}{2}, 2$ this contradicts \eqref{ab}.
  \item $(*p*p)$ requires that $b^2c = bc^2 + ad^2$ and $abd = bcd + ade$.
    Equivalently, we require that
    \begin{align}
      b^2(d^2-1) &= b(d^2-1)^2 + ad^2 \label{bq}\\
      ab &= b(q-1) + a(q - 1).\nonumber
    \end{align}
    In particular, we have that
    \[
      bd^4 + (a - 2b - b^2)d^2 + b - b^2 = 0 = ad^4 + (b - 2a)d^2 - a^2d + a. 
    \]
    Equivalently, $d$ is a root of the polynomial $(a-b)d^4 + (3b - 3a + b^2)d^2 - a^2d + (2b + b^2)$.
    \fi

      %$(*pp*), $(p*pp)$, $(pp*p)$, $(p*p*)$, $(ppp*)$.
\end{itemize}

Now suppose that $d = 0$.
One thing which is immediately clear is the decomposition into one-dimensional subrepresentations (the spans of each basis vector) if this is a representation.
Note that $(*ppp)$ requires that $a^2e = ae^2$, i.e. $a = e$.
Similarly, $(*p*p)$ requires that $b = c$.
Further, we still satisfy the relations for $(pppp)$, we always satisfy the relations for $(*pp*)$, and the rest of the strings are compatible by symmetry.
All that is left are the relations $T_iT_j = T_jT_i$ for $\abs{i - j} > 1$, which are easy to see.
Hence, for each $q$, there are 4 ``good'' actions on $F$, each of which decomposes into a direct sum of one-dimensional subrepresentations.

\subsection{A More General Case}
Now, consider a modification of \eqref{Definitions}:
\begin{align}
  \begin{split}
  \widehat{(*pp)} &:= a(*pp)\\
  \widehat{(*p*)} &:= b(*p*)\\
  \widehat{(p*p)} &:= c(p*p) + d(ppp)\\
  \widehat{(pp*)} &:= g(pp*)\\
  \widehat{(ppp)} &:= f(p*p) + e(ppp).
  \end{split}
  \label{General Definitions}
\end{align} 
This time, the quadratic relation reads
\begin{align}
  \begin{split}
  a^2 &= (q-1)a + q\\
  b^2 &= (q-1)b + q\\
  g^2 &= (q-1)g + q\\
  c^2 + df &= (q -1)c + q\\
  de &= (q-1)d\\
  e^2 + df &= (q -1)e + q\\
  fc &= (q-1)f
\end{split}
  \label{General Quadratic}
\end{align}
Notably, we have $a,b,g \in \cbr{-1.q}$ still.
If $d = 0$ or $f = 0$, then $c,e \in \cbr{-1,q}$ still, and if $d = 0$ and $f \neq 0$, then $c = (q-1)$, and hence $c = 1$ and $q = 2$.
If $d \neq 0$, we still have that $c = e = (q-1)$, and we have that $df = q$.

Now, suppose that $d,f \neq 0$.
Now, $(*ppp)$ requires that $abf = bcf + aef$ and $a^2e = ae^2 + bf^2$, so as before we have that $ab = (a+b)(q-1)$.

$(pppp)$ now requires that $aef = acf + e^2f$.
This requires that $e^2 = 0$, so that $q = 1$ and $ab = 0$, a contradiction again.

Now, suppose that $f \neq 0$ and $d = 0$, so that $q = 2$ and $c = 1$.
Then, we have that $a(e-1) = e^2$.
Then, knowing that $e^2 \neq 0$, we have $e = -1$ so $-2a = 1$, a contradiction.
By symmetry, we also arrive at a contradiction if $d \neq 0$ and $f = 0$.

Finally, suppose that $d = f = 0$, and note that we now have $a = e = g$ and $b = c$;
hence our case is precisely the case with $d = f$ and $a = g$, and there are exactly four actions of $\SH$ on $F$ on which each $T_i$ acts analogously on positions $i,i+1,i+2$ as each other, only modifying position $i+1$. 
Each of these actions decomposes into a direct sum of 1-dimensional subrepresentations.

\newpage

\fi
\end{document}

### 2019-07-12 code/crossingless.py

@@ -5,41 +5,55 @@ from cmath import sqrt
 # for example, {1:4,4:1,2:3,3:2} is the S4 rainbow
 #
 #
+
+
 class basis_element:
-	def __init__(self, n, match):
-		assert n%2==0, 'n must be even'
-		self.n=n
-		assert len(match.keys())==n, 'must have n nodes'
-		for i in match.keys():
-			assert match[i]!=i, 'an element cannot be paired with itself'
-			assert i==match[match[i]], 'matchings are not symmetric'
-			for j in range(min(i,match[i])+1,max(i,match[i])):
-				assert min(i,match[i])<match[j] and max(i,match[i])>match[j], 'matchings cross'
-		self.match=match
-	
-	# returns dictionary of matches nodes
-	def get_matches(self):
-		dictt={}
-		for i in self.match.keys():
-			dictt[i]=self.match[i]
-		return dictt
-	
-	#returns matching node to i
-	def pair(self,i):
-		return self.match[i]
-	
-	def __eq__(self,i):
-		return i.get_matches()==self.get_matches()
-	
-	#so that you can use the basis elements to index in a dictionary
-	def __hash__(self):
-		a=0
-		for i in range(self.n):
-			a=a+self.n**i*self.match[i+1]
-		return a
-	
-	def __str__(self):
-		return str(self.match)
+    def __init__(self, n, match):
+        assert n % 2 == 0, 'n must be even'
+        self.n = n
+        assert len(match.keys()) == n, 'must have n nodes'
+        for i in match.keys():
+            assert match[i] != i, 'an element cannot be paired with itself'
+            assert i == match[match[i]], 'matchings are not symmetric'
+            for j in range(min(i, match[i])+1, max(i, match[i])):
+                assert min(i, match[i]) < match[j] and max(
+                    i, match[i]) > match[j], 'matchings cross'
+        self.match = match
+
+    # returns dictionary of matches nodes
+    def get_matches(self):
+        dictt = {}
+        for i in self.match.keys():
+            dictt[i] = self.match[i]
+        return dictt
+
+    # returns matching node to i
+    def pair(self, i):
+        return self.match[i]
+
+    # creates tex to call the Matchings macro on the given basis elt
+    def output_latex(self):
+        prematching = []
+        for key in self.match.keys():
+            if key < self.match[key]:
[…]

### 2019-07-12 code/kernel_ranks.py

@@ -1,114 +1,192 @@
-import cmath
-import numpy
-import crossingless
-import time
-import csv
-import math
+from cmath import sqrt
 
-def make_matrix(n,q,restriction = 1):
-    """
+# n: number of nodes (note that this must be even)
+# match: dictionary sending node to matching node
+# for example, {1:4,4:1,2:3,3:2} is the S4 rainbow
+#
+#
 
-    Create the matrix for the direct sum (1 + t_1) oplus ... oplus (1 + t_{i - 1 - restriction}) for parameter q
-    This has trivial kernel iff the restriction to S_{n - restriction} is irreducible.
-    
-    KEYWORD ARGUMENTS:
-    n -- parameter from S_n
-    q -- parameter of the hecke algebra (T_i - q)(T_i + 1) = 0
-    restriction -- the number of simple transpositions ignored.
-    """
-    assert n % 2 == 0
 
-    # generate a basis; basisraw has basis_element elements, basis has module_element
-    basisraw = crossingless.generate_basis(n)
-    basis = [crossingless.module_element(n,{b:1},q) for b in basisraw]
+class basis_element:
+    def __init__(self, n, match):
+        assert n % 2 == 0, 'n must be even'
+        self.n = n
+        assert len(match.keys()) == n, 'must have n nodes'
+        for i in match.keys():
+            assert match[i] != i, 'an element cannot be paired with itself'
+            assert i == match[match[i]], 'matchings are not symmetric'
+            for j in range(min(i, match[i])+1, max(i, match[i])):
+                assert min(i, match[i]) < match[j] and max(
+                    i, match[i]) > match[j], 'matchings cross'
+        self.match = match
 
-    C = len(basis)
-    m = numpy.zeros(C)
-    # i iterates over the simple transpositions considered
-    for i in range(n - restriction - 1):
-        # generate the matrix by applying the transposition to each basis vector and taking the resulting coefficients
-        outs = [b.mult_generator(i+1) for b in basis]
-        outsmat = numpy.matrix([[out.coeff(b) for out in outs] for b in basisraw])
-        m = numpy.vstack([m,outsmat])
-    
-    # prune zero rows from matrix
-    m = m[[i for i, x in enumerate(m) if x.any()]]
-    return m
+    # returns dictionary of matches nodes
+    def get_matches(self):
+        dictt = {}
+        for i in self.match.keys():
+            dictt[i] = self.match[i]
+        return dictt
 
-def kernel_dimension(n,q,restriction=1):
-    """
[…]

### 2019-07-12 tex/Generalized-Crossingless.tex
Initial proof for uneven-height two-column spect modules

\documentclass{amsart}   
\usepackage{RepStyle} 
\usepackage{NatMacros} %********REPLACE WITH MilesMacros TO KILL RELIANCE ON \ifnum AND HAVE INCOMPLETE OUTPUT***********bleh
\begin{document}

\title{The Uneven-Height Two-Column Specht Modules of the Hecke Algebra of $S_n$}
\author{Miles Johnson \& Natalie Stewart}
\maketitle

\section{Introduction}
Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices, let $\SH = \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k$, and let $\cbr{T_i}$ be the simple transpositions generating $\SH$.
Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of $m$. 
Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
Either $q = 1$ and $e$ is the characteristic of $k$, or $q \neq 1$ and $q$ is a primitive $e$th root of unity.

Let $V_{2n}^r := S^{(n,n-r)'}$ be the Specht module corresponding to the young diagram with two columns with height difference $r$.
The purpose of this writing is to characterize this representation via an isomorphism with another representation of $\SH$.
\begin{definition}
  A \emph{generalized crossingless matching} on $2n+r$ indices with $r$ anchors is a partition of $\cbr{1,\dots,2n+r}$ into parts of size $2$ or 1 such that no two parts of size two``cross'', i.e. there are no parts $(a,a')$ and $(b,b')$ such that $a < b < a' < b'$, and no parts of size one are ``inside'' of a part of size two, i.e. there are no $c, (a,a')$ such that $a < c < a'$.
  We will call these arcs and anchors, respectively.
  Then, define $W^r_{2n+r}$ to be the $k$-vector space with basis the set of generalized crossingless matchings on $2n+r$ indices with $r$ anchors.

  In order for this to be a $\SH$-module, endow this with the action given by Figure \ref{Action}; if this involves no anchors, act as in $W$; if it involves one loop, deform to another generalized crossingless matching and scale by $q^{1/2}$, and otherwise scale by 0.
\end{definition}

\begin{figure}
  \[
    \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{4}{2/3, 4/5}{1/1,6/2}{q^{1/2}}
    \hspace{50pt}
    \GeneralizedZeroAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{5}
  \]
  \caption{Illustration of the actions $(1 + T_4)w_{\abs{W^2_6}}$ and $(1 + T_2)w_{\abs{W^2_6}}$ in $W^2_6$.
    In general, we act on basis elements away from anchors as we did for $W$, at one anchor we act by deforming and scaling by $q^{1/2}$, and at two anchors we send the element to zero.}
  \label{Action}
\end{figure}

Let the length of an arc $(i,j)$ be $l(i,j) := j - i + 1$.
Note that the crossingless matchings can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
using this, we may order the crossingless matchings with 0 hooks in increasing lexicographical order in order to obtain an order on the subbasis containing a particular set of anchors;
let the basis be ordered first by the position of the anchors in increasing lexicographical order, then increasing for the matchings between each anchor.
Let this basis be $\cbr{w_i}$.
This basis is illustrated for $W_{5}^1$ in Figure \ref{S5 Basis}.

\begin{figure}
  \def\cbasisspacing{5mm}
  $\cbr{
    \begin{gathered}
      \GeneralizedMatching{5}{2/3, 4/5}{1}{1/1}{3/4}, \hspace{\cbasisspacing}
      \GeneralizedMatching{5}{2/5, 3/4}{1}{1/1}{3/4}, \hspace{\cbasisspacing}
      \GeneralizedMatching{5}{1/2, 4/5}{1}{3/1}{3/4}, \hspace{\cbasisspacing}
      \GeneralizedMatching{5}{1/2, 3/4}{1}{5/1}{3/4}, \hspace{\cbasisspacing}
      \GeneralizedMatching{5}{1/4, 2/3}{1}{5/1}{3/4}, \hspace{\cbasisspacing}
     \end{gathered}}$ 
    \caption{The basis for $W_5^1$.}
  \label{S5 Basis}
\end{figure}

We will prove that $W := W_{2n+r}^r$ and $V^{(n+r,n)'}$ are isomorphic as representations in the case that $\SH$ is semisimple.

\newpage
\section{Correspondence} 
We can now begin by proving that $W$ is irreducible;
then $W \simeq S^\lambda$ for some partition $\lambda$ of $2n + r$, and we may use branching rules to determne $W$.
\begin{proposition}
  Suppose $n > 2$.
  Then, $W_{2n + r}^r$ is irreducible if $e > n + 1$.
\end{proposition}
\begin{proof}
  We will prove the equivalent condition that each vector in $w \in W\backslash \cbr 0$ is \emph{cyclic}, i.e. $\SH w = W$.
  Note that, similar to the $r = 0$ case, each basis vector is cyclic;
  we may act between each anchor to have only anchors and length-2 arcs, move the anchors to the desired position, and use irreducibility of $W_{m}^0$ to act btween arcs in order to generate any other basis element.

  Let $U_{x_1\dots x_r}$ be the subspace of $W$ with anchors $x_1,\dots,x_r$.
  Order these in increasing lexicographical order;
  let $U_{a_1\dots a_r}$ be the first of these on which $w$ projects to a nonzero vector.
  Then, we may use irreducibility of $W_{m}^0$ to act between the anchors to generate a vector $w'$ which projects in $U_{a_1\dots a_r}$ to the basis element of arcs of length 2 between arcs $a_1,\dots,a_r$.

  Note that $n + r - a_r$ is even;
  hence we can apply
  \[
    h = (1 + T_{n + r - 3})(1 + T_{n+r-5})(1 + T_{n+r-4})(1 + T_{n+r-7})(1 + T_{n+r-6})\dots(1 + T_{a_r +2})(1 + T_{a_r+1})
  \]
  and we find that all basis vectors represented in $hw'$ are one in $U_{a_1\dots a_r}$ containing arc $(2n + r - 1, 2n + r)$ or others containing anchor $2n + r$.
  Hence $(T_{2n + r - 1} - q)hw'$ is a nonzero vector (since $q^{1/2} \neq q$ as $e > 3$) represeting a unique basis element, giving that $w$ is cyclic and $W_{2n + r}^r$ is irreducible.
\end{proof}

The next piece in our puzzle is to characterize the restrictions of $W$ to $\SH' := \SH_{k,q}(S_{2n + r - 1}) \subset \SH$.
Recall that, when $r,n>0$, $\Res S^{(n+r,n)'} \simeq S^{(n+r-1,n)'} \oplus S^{(n+r,n-1)'}$.
Further, note that $S^{(n+r,n)'}$ is the unique irreducible having this restriction.

Next, note that we have already proven the correspondence for $W_{2n}^0$;
for $W_{0 + r}^{r}$, this is the sign representation, which is given correctly by $S^{(r)}$.
Hence, pending information on restrictions, we may prove this via induction on $2n + r$.

\begin{proposition}
  Suppose that $n,r > 0$ and $\SH$ is semisimple.
  Then, $\Res \; W_{2n + r}^r \simeq W_{2n + r - 1}^{r-1} \oplus W_{2n + r - 1}^{r + 1}$.
\end{proposition}
\begin{proof}
  Note that we may identify the subrepresentation of $\Res \; W_{2n + r}^r$ having anchor $n$ with $W_{2n + r - 1}^{r-1}$.
  By semisimplicity, it is sufficient to prove that $U := \Res \; W_{2n + r}^r / W_{2n + r - 1}^{r-1}$ is isomorphic to $W_{2n + r - 1}^{r +1}$.

  Let $\phi:U \rightarrow W_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $W_{2n + r - 1}^{r + 1}$.
  It is not hard to verify that this is a well-defined isomorphism of vector spaces, so we must show that it is $\SH$-linear.

  Given a basis vector $w_j$ with arc $(i,2n + r)$, $\phi$ is clearly compatible with $T_{i'}$ with $i' \neq i,i-1$.
  Further, it's easy to verify that $\phi$ is compatible with $T_{i}$ and $T_{i-1}$, as actions on one anchor were designed for this deformation.
  When there are anchors $(i,i+1)$, then $\phi(T_iw_j) = T_i\phi(w_j) = 0$, and similar for $T_{i -1}$.
  Hence $\phi$ is an isomorphism of representations, and the statement is proven.
\end{proof}

\begin{corollary}
  $W_{2n + r}^r \simeq S^{(n + r,r)'}$.
\end{corollary}
\begin{proof}
  We may argue by induction on $2n + r$, knowing that we have proven the base case $2n + r = 2$.
  Assume that we have proven the isomorphism for all $W_{2n + s}^{s}$ with $2n + s = 2n + r - 2$.
  We have proven the $n = 0$ and $r = 0$ cases already, so assume $n,r > 0$.

  Then, $W_{2n + r}^{r}$ is the unique irreducible representation of $\SH$ having restriction $S^{(n+r-1,n)'} \oplus S^{(n + r,n-1)'}$, implying the desired isomorphism.
\end{proof}

\end{document}

### 2019-07-13 tex/Generalized-Crossingless.tex
Version 2 of gen. cross. proof

@@
 \section{Introduction}
-Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices, let $\SH = \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k$, and let $\cbr{T_i}$ be the simple transpositions generating $\SH$.
+Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices, let $\SH = \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k^\times$, and let $\cbr{T_i}$ be the reflections generating $\SH$.
 Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of $m$. 
@@
 
-Let $V_{2n}^r := S^{(n,n-r)'}$ be the Specht module corresponding to the young diagram with two columns with height difference $r$.
+Let $S^{(n+r,n)'}$ be the Specht module corresponding to the young diagram with two columns with height difference $r$.
 The purpose of this writing is to characterize this representation via an isomorphism with another representation of $\SH$.
 \begin{definition}
-  A \emph{generalized crossingless matching} on $2n+r$ indices with $r$ anchors is a partition of $\cbr{1,\dots,2n+r}$ into parts of size $2$ or 1 such that no two parts of size two``cross'', i.e.
+  A \emph{generalized crossingless matching} on $2n+r$ indices with $r$ anchors is a partition of $\cbr{1,\dots,2n+r}$ into $n$ parts of size $2$ and $r$ of size 1 such that no two parts of size two``cross'', i.e.
 there are no parts $(a,a')$ and $(b,b')$ such that $a < b < a' < b'$, and no parts of size one are ``inside'' of a part of size two, i.e.
@@
 
-  In order for this to be a $\SH$-module, endow this with the action given by Figure \ref{Action}; if this involves no anchors, act as in $W$; if it involves one loop, deform to another generalized crossingless matching and scale by $q^{1/2}$, and otherwise scale by 0.
+  In order for this to be a $\SH$-module, endow this with the action given by Figure \ref{Action}; if this involves no anchors, act as in $W_{2n}^0$; if it involves one anchor, deform to another generalized crossingless matching and scale by $q^{1/2}$, and otherwise scale by 0.
 \end{definition}
@@
 
-We will prove that $W := W_{2n+r}^r$ and $V^{(n+r,n)'}$ are isomorphic as representations in the case that $\SH$ is semisimple.
+We will prove that $W := W_{2n+r}^r$ and $S := S^{(n+r,n)'}$ are isomorphic as representations in the case that $\SH$ is semisimple.
 
@@
 then $W \simeq S^\lambda$ for some partition $\lambda$ of $2n + r$, and we may use branching rules to determne $W$.
+\begin{lemma}
+  Every basis vector in $W_{2n + r}^r$ is cyclic.
+\end{lemma}
+\begin{proof}
+  We have already proven this in the $r = 0$ case, so suppose that $r > 0$.
+
+    Note that, between anchors $a<a'$ having no arc $b$ with $a < b < a'$, the $W_{a'-a}^0$ case allows us to generate the vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.\footnote{At the ends, we apply the $W_a^0$ case or the $W_{2n + r - a}^{0}$ case in the same way for the first $a$ or last $2n + r - a$ indices.}
+
+  Applying this between each arc gives us a vector with length-2 arcs and anchors, and we may use the appropriate $(1+T_i)$ to move anchors to any positions, and the reverse process from above to generate the correct matchings between arcs and generate any other basis vector.
+\end{proof}
+
 \begin{proposition}
-  Suppose $n > 2$.
-  Then, $W_{2n + r}^r$ is irreducible if $e > n + 1$.
+  \;
+
+  \begin{enumerate}[label={(\roman*)}]
+    \item The representation $W_{2+r}^r$ is reducible iff $e \mid r+2$.
+    \item When $n \neq 1$ and $e > n+1$, the representation $W_{2n + r}^r$ is irreducible.
+  \end{enumerate}
 \end{proposition}
 \begin{proof}
+  \def\sectionsep{7pt}
+  \textbf{(i)}
+  Note that $\ima (1 + T_i)$ is 1-dimensional for each $i$, so it is equivalent that 
+  \[K := \bigcap_{i=1}^{r+1} \ker(1 + T_i) = \ker \bigoplus_{i=1}^{r+1} (1 + T_i)\] 
+  is trivial via the lemma.
+  The transformation $\bigoplus (1 + T_i)$ is a linear operator on $W_{2 + r}^r$ given by the following matrix:
+  \newcommand*\bigzero{\makebox(0,15){\text{\Huge0}}}
+  \newcommand*\bigzerotwo{\makebox(-20,15){\text{\Huge0}}}
+  \[
+    A_{r + 1} = 
+    \begin{bmatrix}
+      \begin{matrix}
+      q + 1 & q^{1/2} & \\
+      q^{1/2} & q + 1 & q^{1/2}\\
+      & q^{1/2} & q + 1 & q^{1/2}\\
+      &  & \ddots & \ddots
+      \end{matrix}
+      &   \bigzero\\
+      \bigzerotwo & \begin{matrix}
+        q^{1/2} & q+1 & q^{1/2}\\
+        &  q^{1/2} & q + 1
+       \end{matrix}
+    \end{bmatrix}
+  \].
+  Hence $K$ is trivial iff the determinant $\det A_{r + 1} = \brk{r + 2}_q$ is 0, or equivalently iff $e \mid r + 2$.
+
+  \iffalse % Previous proof, kept for archival purposes
+  \vspace{\sectionsep}
+  \textbf{(ii)}
+  We have already proven this for $r = 0$ and $n = 0$, so suppose $r > 0$ and $n > 1$.
+  We will break into case work on $r$;
+  suppose first that $r = 1$.
+  Then, it is easy to verify that $W_{2n + 1}^1 \simeq \Res W_{2n + 1}^0$, which we have already proven irreducible.
+  We may henceforth assume that $r > 1$.
+
   We will prove the equivalent condition that each vector in $w \in W\backslash \cbr 0$ is \emph{cyclic}, i.e. $\SH w = W$.
-  Note that, similar to the $r = 0$ case, each basis vector is cyclic;
-  we may act between each anchor to have only anchors and length-2 arcs, move the anchors to the desired position, and use irreducibility of $W_{m}^0$ to act btween arcs in order to generate any other basis element.
+  This will proceed in two steps: we will make sure a particular basis vector is represented with the earliest possible position of the second to last anchor $a_{r-1}$, then we will annihilate all other vectors in order to generate a basis vector.
+  Then, by the lemma, we will have proven that $w$ is cyclic.
 
-  Let $U_{x_1\dots x_r}$ be the subspace of $W$ with anchors $x_1,\dots,x_r$.
-  Order these in increasing lexicographical order;
-  let $U_{a_1\dots a_r}$ be the first of these on which $w$ projects to a nonzero vector.
-  Then, we may use irreducibility of $W_{m}^0$ to act between the anchors to generate a vector $w'$ which projects in $U_{a_1\dots a_r}$ to the basis element of arcs of length 2 between arcs $a_1,\dots,a_r$.
+  Overall, we will use induction on $2n + r$;
+  this is easily shown via identification with the sign or trivial representation when $2n + r = 2$, so assume that it is true for all $W_{2m + s}^s$ with $2m + s < 2n + r$.
 
-  Note that $n + r - a_r$ is even;
-  hence we can apply
+  Let $U_{x_{r-1}}$ be the subspace of $W$ containing at most one anchor at positions $i > x_{r-1}$.
+  Order these in increasing order;
+  let $U := U_{a_{r-1}}$ be the first of these into which $w$ projects to a nonzero vector.
+  Then, by our inductive hypothesis, we may use only actions $T_i$ with $i < a_{r-1}$ to generate a vector $w'$ which projects to a nonzero element in $U$ for which all basis elements represented have anchors $1,\dots,r-1$ and all length-2 arcs at indices $i \leq a_{r-1}$.
+
+  Define the element
   \[
-    h = (1 + T_{n + r - 3})(1 + T_{n+r-5})(1 + T_{n+r-4})(1 + T_{n+r-7})(1 + T_{n+r-6})\dots(1 + T_{a_r +2})(1 + T_{a_r+1})
+    h = (1 + T_{n + r - 1})(1 + T_{n+r-3})(1 + T_{n+r-2})(1 + T_{n + r - 4})\dots(1 + T_{a_{r-1} +1})(1 + T_{a_{r-1}+2}).
   \]
-  and we find that all basis vectors represented in $hw'$ are one in $U_{a_1\dots a_r}$ containing arc $(2n + r - 1, 2n + r)$ or others containing anchor $2n + r$.
-  Hence $(T_{2n + r - 1} - q)hw'$ is a nonzero vector (since $q^{1/2} \neq q$ as $e > 3$) represeting a unique basis element, giving that $w$ is cyclic and $W_{2n + r}^r$ is irreducible.
+  Note that $h$ carries a basis element to a multiples of another basis element, and a basis element is in $\ker \, h$ iff it is not in $U$.
+  Hence $hw'$ is a nonzero multiple of a basis element, giving $w$ cyclic.
+  \fi
+
+  \vspace{\sectionsep}
+  \textbf{(ii)}
+  We will prove the equivalent condition that each vector in $w \in W\backslash \cbr 0$ is \emph{cyclic}, i.e. $\SH w = W$.
+  We will break into case work on $r$;
+  suppose first that $r = 1$.
+  Then, it is easy to verify that $W_{2n + 1}^1 \simeq \Res W_{2n + 1}^0$, which we have already proven irreducible.
+  We may henceforth assume that $r > 1$.
+
+  Overall, we will use induction on $2n + r$;
+  this is easily shown via identification with the sign or trivial representation when $2n + r = 2$, so assume that it is true for all $W_{2m + s}^s$ with $2m + s = 2n + r - 2$.
+
+  The proof will proceed in two steps: first we will make sure a particular basis vector is represented with the earliest possible position of the last anchor $a_r$, then we will use this to generate a nonzero vector representing only vectors with a certain collection of anchors, using the inductive hypothesis to prove that $w$ is cyclic.
+
+  \vspace{\sectionsep}
+  \textit{Step 1.}
+  Let $U_{x_r}$ be the subspace of $W$ containing only anchors at positions $i \leq x_r$.
+  Order these in increasing order;
+  let $U := U_{a_r}$ be the first of these into which $w$ projects to a nonzero vector.
+  If $a_r = n + r$, then $w$ only represents vectors containing anchor $r$;
+  then, we may use the inductive hypothesis on the first $n + r - 1$ indices to yield a basis vector, and we are done.
+
+  Henceforth assume $a_r < n + r$.
+  Then, by our inductive hypothesis, we may use only actions $T_i$ with $i < a_r$ to generate a vector $w'$ which projects to a vector in $U$ representing basis elements with anchors $1,2,\dots,r$ and all length-2 arcs at indices $r < i \leq a_r$.
+
+  Now, recall that $\Res_{\SH(S_{2n + r - a_r-1})}^{\SH(S_{2n + r - a_r})} \; W_{2n + r - a_r}^0$ is irreducible;
+  hence we may only use actions $T_i$ with $i > a_r+1$ to generate a vector $w''$ which projects to the basis vector $U$ containing anchors $1,\dots,r$ and is otherwise all length-2 arcs.\footnote{Any action by $T_i$ with $i > a_r + 1$ sends basis vectors outside of $U$ to 0 or nonzero vectors outside of $U$, as they cannot generate a vector which doesn't have an anchor in some position $j > a_r$.}
+
+  \vspace{\sectionsep}
+  \textit{Step 2.}
+  Define an element $h \in \SH$ by
+  \[
+    h := (1 + T_{n + r - 2})(1 + T_{n+r-1})(1 + T_{n+r-3})(1 + T_{n+r-2})\dots(1 + T_{r+1})(1 + T_{r+2})
+  \]
+  Then, every basis vector represented in $hw'' \neq 0$ contains anchors $1,\dots,r-1$.
+  This is illustrated in Figure \ref{h}.
+
+  Let $U'$ be the subspace of $W$ having anchors $1,\dots,r-1$.
+  Note that $hw'' \in U'$.
+  Further, $U' \simeq W_{2n + 1}^1$ as vector spaces, and every action in $W_{2n + 1}^1$ is reflected by an action of $\SH$ on $W_{2n + r}^r$.
+  Since $r > 1$, we may use the inductive hypothesis to act on indices $i \geq r$ and generate a basis vector, giving $w$ cyclic.
+
+  \begin{figure}
+    \[
+      \GeneralizedNAction{6}{1/2,4/5}{2}{3/1, 6/2}{3/4}{3/1, 2/2}{1/4, 2/3}{5/1, 6/2}{q}
+      \hspace{50pt}
+      \GeneralizedNAction{6}{1/2,4/5}{2}{3/1, 6/2}{3/4}{4/1, 3/2}{1/2, 3/4}{5/1, 6/2}{x}
+    \]
+  \caption{
+    Demonstration of how the transformation $(1 + T_{i+1})(1 + T_i)$ ``moves'' anchors from positions $i,i+1$ to position $i+3$, with constant $x = q^{1/2}(q+1)$.
+    Iterating this across all elements between $r+1$ and $2n + r$ via $h$ concentrates all anchors at the beginning or end; 
+    if there are at least two anchors in $w_j$ after $r+1$, then we must act on two anchors eventually, giving $w_j \in \ker \, h$.
+  }\label{h}
+\end{figure}
 \end{proof}
 
+\begin{corollary}
+  Other than $W_{3}^1$, the representation $W_{2n + r}^r$ is irreducible when $e > n + 1$.
+\end{corollary}
+
 The next piece in our puzzle is to characterize the restrictions of $W$ to $\SH' := \SH_{k,q}(S_{2n + r - 1}) \subset \SH$.
-Recall that, when $r,n>0$, $\Res S^{(n+r,n)'} \simeq S^{(n+r-1,n)'} \oplus S^{(n+r,n-1)'}$.
+Recall that, when $r,n>0$ and $\SH$ is semisimple,  $\Res S^{(n+r,n)'} \simeq S^{(n+r-1,n)'} \oplus S^{(n+r,n-1)'}$.
 Further, note that $S^{(n+r,n)'}$ is the unique irreducible having this restriction.
@@
 \begin{corollary}
-  $W_{2n + r}^r \simeq S^{(n + r,r)'}$.
+  When $\SH$ is semisimple, $W_{2n + r}^r \simeq S^{(n + r,r)'}$.
 \end{corollary}

### 2019-07-13 tex/Generalized-Crossingless.tex
Rewrote proof of composition series for gen. cross.

@@
 \section{Introduction}
-Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices, let $\SH = \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k^\times$, and let $\cbr{T_i}$ be the reflections generating $\SH$.
+Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices with $2n + r \geq 2$, let $\SH = \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k^\times$, and let $\cbr{T_i}$ be the reflections generating $\SH$.
 Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of $m$. 
@@
   Overall, we will use induction on $2n + r$;
-  this is easily shown via identification with the sign or trivial representation when $2n + r = 2$, so assume that it is true for all $W_{2m + s}^s$ with $2m + s = 2n + r - 2$.
+  this is easily shown via identification with the sign or trivial representation when $2n + r = 2$, so assume that it is true for all $W_{2m + s}^s$ with $2m + s < 2n + r$.
 
@@
 \begin{proposition}
-  Suppose that $n,r > 0$ and $\SH$ is semisimple.
-  Then, $\Res \; W_{2n + r}^r \simeq W_{2n + r - 1}^{r-1} \oplus W_{2n + r - 1}^{r + 1}$.
+  Suppose that $n,r > 0$.
+  Then, a filtration of $\Res W_{2n + r}^r$ is given by
+  \begin{equation}
+    0 \subset W_{2n + r - 1}^{r-1} \subset \Res \, W_{2n + r}^r \label{Filtration}
+  \end{equation}
+  with $\Res \, W_{2n + r}^r / W_{2n + r - 1}^{r-1} \simeq W_{2n + r - 1}^{r + 1}$. 
 \end{proposition}
@@
   Note that we may identify the subrepresentation of $\Res \; W_{2n + r}^r$ having anchor $n$ with $W_{2n + r - 1}^{r-1}$.
-  By semisimplicity, it is sufficient to prove that $U := \Res \; W_{2n + r}^r / W_{2n + r - 1}^{r-1}$ is isomorphic to $W_{2n + r - 1}^{r +1}$.
 
+  Let $U := \Res \; W_{2n + r}^r / W_{2n + r - 1}^{r - 1}$. 
   Let $\phi:U \rightarrow W_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $W_{2n + r - 1}^{r + 1}$.
@@
 \end{proof}
+
+\begin{corollary}
+  Suppose $n,r > 0$ and $e > n + 1$.
+  Then, the sequence \eqref{Filtration} is a composition series of $\Res \, W_{2n + r}^r$.\qed
+\end{corollary}
+\begin{corollary}
+  Suppose $n,r > 0$ and $\SH$ is semisimple.
+  Then, $\Res \; W_{2n + r}^r \simeq W_{2n + r - 1}^{r - 1} \oplus W_{2n + r - 1}^{r +1}$.\qed
+\end{corollary}
 

### 2019-07-18 tex/Generalized-Crossingless.tex
Hecke Algebra Relations Verifications

@@
 
-We will prove that $W := W_{2n+r}^r$ and $S := S^{(n+r,n)'}$ are isomorphic as representations in the case that $\SH$ is semisimple.
+We will prove that $W := W_{2n+r}^r$ and $S := S^{(n+r,n)'}$ are isomorphic as representations in the case that $e > n + r + 1$ is semisimple.
 
@@
 \section{Correspondence} 
-We can now begin by proving that $W$ is irreducible;
-then $W \simeq S^\lambda$ for some partition $\lambda$ of $2n + r$, and we may use branching rules to determne $W$.
+\begin{proposition}
+  Suppose that $n,r > 0$.
+  Then, a filtration of $\Res W_{2n + r}^r$ is given by
+  \begin{equation}
+    0 \subset W_{2n + r - 1}^{r-1} \subset \Res \, W_{2n + r}^r \label{Filtration}
+  \end{equation}
+  with $\Res \, W_{2n + r}^r / W_{2n + r - 1}^{r-1} \simeq W_{2n + r - 1}^{r + 1}$. 
+\end{proposition}
+\begin{proof}
+  Note that we may identify the subrepresentation of $\Res \; W_{2n + r}^r$ having anchor $n$ with $W_{2n + r - 1}^{r-1}$.
+
+  Let $U := \Res \; W_{2n + r}^r / W_{2n + r - 1}^{r - 1}$. 
+  Let $\phi:U \rightarrow W_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $W_{2n + r - 1}^{r + 1}$.
+  It is not hard to verify that this is a well-defined isomorphism of vector spaces, so we must show that it is $\SH$-linear.
+
+  Given a basis vector $w_j$ with arc $(i,2n + r)$, $\phi$ is clearly compatible with $T_{i'}$ with $i' \neq i,i-1$.
+  Further, it's easy to verify that $\phi$ is compatible with $T_{i}$ and $T_{i-1}$, as actions on one anchor were designed for this deformation.
+  When there are anchors $(i,i+1)$, then $\phi(T_iw_j) = T_i\phi(w_j) = 0$, and similar for $T_{i -1}$.
+  Hence $\phi$ is an isomorphism of representations, and the statement is proven.
+\end{proof}
+
 \begin{lemma}
@@
 \begin{proposition}
-  \;
-
-  \begin{enumerate}[label={(\roman*)}]
-    \item The representation $W_{2+r}^r$ is reducible iff $e \mid r+2$.
-    \item When $n \neq 1$ and $e > n+1$, the representation $W_{2n + r}^r$ is irreducible.
-  \end{enumerate}
+  The representation $W_{2n + r}^r$ is irreducible when $e > n + r + 1$. 
 \end{proposition}
@@
   \def\sectionsep{7pt}
+  \iffalse % now unnecessary, kept for archival purposes.
+  The representation $W_{2+r}^r$ is reducible iff $e \mid r+2$.
   \textbf{(i)}
@@
 
-  \iffalse % Previous proof, kept for archival purposes
   \vspace{\sectionsep}
@@
   Hence $hw'$ is a nonzero multiple of a basis element, giving $w$ cyclic.
-  \fi
 
@@
 \end{figure}
+  \fi
+  We proceed by induction on $2n + r$.
+  Note that, by identification with the trivial and sign representations, the base case $2n + r = 2$ is already prove, so suppose we have proven this for each $2m + s < 2n + r$.
+
+  We will prove this in essentially the same way as before;
+  the inductive argument continues to apply assuming that $K := \ker \, \bigoplus(1 + T_i)$ is trivial, and we will prove that this is trivial when $e \not| n + r + 1$ using a similar argument.
+  This argument is very long, and I will recreate it later.
 \end{proof}
@@
 
-\begin{proposition}
-  Suppose that $n,r > 0$.
-  Then, a filtration of $\Res W_{2n + r}^r$ is given by
-  \begin{equation}
-    0 \subset W_{2n + r - 1}^{r-1} \subset \Res \, W_{2n + r}^r \label{Filtration}
-  \end{equation}
-  with $\Res \, W_{2n + r}^r / W_{2n + r - 1}^{r-1} \simeq W_{2n + r - 1}^{r + 1}$. 
-\end{proposition}
-\begin{proof}
-  Note that we may identify the subrepresentation of $\Res \; W_{2n + r}^r$ having anchor $n$ with $W_{2n + r - 1}^{r-1}$.
-
-  Let $U := \Res \; W_{2n + r}^r / W_{2n + r - 1}^{r - 1}$. 
-  Let $\phi:U \rightarrow W_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $W_{2n + r - 1}^{r + 1}$.
-  It is not hard to verify that this is a well-defined isomorphism of vector spaces, so we must show that it is $\SH$-linear.
-
-  Given a basis vector $w_j$ with arc $(i,2n + r)$, $\phi$ is clearly compatible with $T_{i'}$ with $i' \neq i,i-1$.
-  Further, it's easy to verify that $\phi$ is compatible with $T_{i}$ and $T_{i-1}$, as actions on one anchor were designed for this deformation.
-  When there are anchors $(i,i+1)$, then $\phi(T_iw_j) = T_i\phi(w_j) = 0$, and similar for $T_{i -1}$.
-  Hence $\phi$ is an isomorphism of representations, and the statement is proven.
-\end{proof}
-
 \begin{corollary}
@@
 
-\begin{corollary}
-  When $\SH$ is semisimple, $W_{2n + r}^r \simeq S^{(n + r,r)'}$.
-\end{corollary}
+\begin{proposition}
+  Suppose $e > n + r + 1$, and let $\lambda$ be a partition of $2n + r$.
+  \begin{enumerate}[label={(\roman*)}]
+    \item Suppose $n,r > 0$.
+      If $\Res \, S^\lambda$ admits a filtration $0 \subset S^{(n+r-1,n)'} \subset \Res \, S^\lambda$ with $\Res \, S^\lambda / S^{(n + r - 1,n)'} \simeq S^{(n + r,n-1)'}$ then $\lambda = (n+r,n)'$.
+    \item Suppose $r = 0$.
+      If $\Res \, S^\lambda \simeq S^{(n,n-1)'}$, then $\lambda = (n,n)'$.
+  \end{enumerate}
+\end{proposition}
 \begin{proof}
-  We may argue by induction on $2n + r$, knowing that we have proven the base case $2n + r = 2$.
-  Assume that we have proven the isomorphism for all $W_{2n + s}^{s}$ with $2n + s = 2n + r - 2$.
-  We have proven the $n = 0$ and $r = 0$ cases already, so assume $n,r > 0$.
+  \textbf{(i)}
+  Recall that the characteristic-free classical branching theorem gives that every specht module $S^{\lambda}$ admits a filtration 
+  \begin{equation}
+    0 = M_0 \subset \dots \subset M_l = S^{\lambda} \label{filtration}
+  \end{equation}  
+    with $M_i/M_{i-1} \simeq S^{\lambda(i)}$.
+  Hence $\lambda = (n + r, n)'$ satisfies the above formula.
 
-  Then, $W_{2n + r}^{r}$ is the unique irreducible representation of $\SH$ having restriction $S^{(n+r-1,n)'} \oplus S^{(n + r,n-1)'}$, implying the desired isomorphism.
+  Note that, when $e > n + r + 1$, this filtration gives a composition series.
+  Hence the sequence \eqref{filtration} is at most length-2.
+
+  Suppose it is length-1.
+  Then $\lambda$ is rectangle-shaped;
+  to have rows removed to the above we then need that that it be $\lambda = \prn{\frac{2n + r}{2}, \frac{2n + r}{2}}'$, so that $\Res S^{\lambda} \simeq S^{\prn{\frac{2n + r}{2}, \frac{2n + r}{2} - 1}'}$.
+  However, since $e > n + r + 1 \geq n + \frac{r}{2} + 1$, $\Res \, S^{\lambda}$ is irreducible, contradicting the existence of a length-2 composition series in the hypothesis.
+
+  Now suppose that \eqref{filtration} is length 2, so that it is also a composition series.
+  Then, by the Jordan-H\"older theorem, there is a rearranement of the composition factors of \ref{filtration} to give $S^{(n + r - 1,n)'}$ and $S^{(n + r, n - 1)'}$.
+  This implies that both $(n + r - 1,n)'$ and $(n + r,n-1)'$ can be acquired by removing rows of $\lambda$, giving that $\lambda = (n+r,n)'$.
+
+  \vspace{7pt}
+  \textbf{(ii)}
+  Note that, since $e > n + 1$, $\Res S^\lambda$ is irreducible.
+  Hence the sequence \eqref{filtration} is a composition series of length 1, and $\lambda(1) = (n,n-1)'$.
+  The first implies that $\lambda$ is rectangular, and the second implies that $\lambda = (n,n)'$.
 \end{proof}
 
+\begin{corollary}
+  If $e > n + r + 1$, then $W_{2n + r}^r \simeq S^{(n + r,n)'}$.\qed
+\end{corollary}
+
 \end{document}

### 2019-07-18 tex/Rough-Overview.tex
Hecke Algebra Relations Verifications

\documentclass{amsart}   
\usepackage{RepStyle} 
\usepackage{NatMacros} %********REPLACE WITH MilesMacros TO KILL RELIANCE ON \ifnum AND HAVE INCOMPLETE OUTPUT***********bleh
\begin{document}

\title{Rough Cut of Proven Work on $\SH$.}
\author{Miles Johnson \& Natalie Stewart}
\maketitle

\section{Introduction}
Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices with $2n + r \geq 2$, let $\SH = \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k^\times$ having square root $q^{1/2}$, and let $\cbr{T_i}$ be the reflections generating $\SH$.
Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of $m$. 
Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
Either $q = 1$ and $e$ is the characteristic of $k$, or $q \neq 1$ and $q$ is a primitive $e$th root of unity.

Let $S^{(n+r,n)'}$ be the Specht module corresponding to the young diagram with two columns with height difference $r$, and let $D^{(n+r,n)'}$ be the corresponding irreducible quotient.
The purpose of this writing is to characterize these representation via an isomorphism with two graphical representations of $\SH$.

\subsection{Crossingless Matchings}
\begin{definition}
  A \emph{crossingless matching on $2n+r$ indices with $r$ anchors} is a partition of $\cbr{1,\dots,2n+r}$ into $n$ parts of size $2$ and $r$ of size 1 such that no two parts of size two``cross'', i.e. there are no parts $(a,a')$ and $(b,b')$ such that $a < b < a' < b'$, and no parts of size one are ``inside'' of a part of size two, i.e. there are no $c, (a,a')$ such that $a < c < a'$.
  We will call these arcs and anchors, respectively.
  Then, define $W^r_{2n+r}$ to be the $k$-vector space with basis the set of generalized crossingless matchings on $2n+r$ indices with $r$ anchors.

  In order for this to be a $\SH$-module, endow this with the action given by Figure \ref{Action}; 
  if a ``loop'' is created, scale by $q+1$, if a loop is not created and the action involves fewer than 2 anchors, deform into a new crossingless maching and scale by $q^{1/2}$, and if it involves two anchors, scale by 0.
  We verify that this is well-defined in appendix \ref{Cross Relations}.
\end{definition}

\begin{figure}
  \[
    \begin{tabular}{l l}
      \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{2}{1/4, 2/3}{5/1,6/2}{(1+q)}
      \hspace{20pt}
      &
      \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{3}{1/2, 3/4}{5/1,6/2}{q^{1/2}}\\
      \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{4}{2/3, 4/5}{1/1,6/2}{q^{1/2}}
      &
      \GeneralizedZeroAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{5}
    \end{tabular}
  \]

  \caption{Illustration of the actions $(1 + T_i)w_{\abs{W^2_6}}$.
    In general, we act by deleting loops, deforming into a new crossingless matching, and scaling by either $q^{1/2}$, $(q + 1)$, or 0.
  }
  \label{Action}
\end{figure}

Let the length of an arc $(i,j)$ be $l(i,j) := j - i + 1$.
Note that the crossingless matchings on $2n$ indices with no anchros can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
using this, we may order the crossingless matchings with no anchors in increasing lexicographical order in order to obtain an order on the subbasis containing a particular set of anchors;
let the basis be ordered first by the position of the anchors in increasing lexicographical order, then increasing for the matchings between each anchor.
Let this basis be $\cbr{w_i}$.
This basis is illustrated for $W_{5}^1$ in Figure \ref{S5 Basis}.

\begin{figure}
  \def\cbasisspacing{5mm}
  $\cbr{
    \begin{gathered}
      \GeneralizedMatching{5}{2/3, 4/5}{1}{1/1}{3/4}, \hspace{\cbasisspacing}
      \GeneralizedMatching{5}{2/5, 3/4}{1}{1/1}{3/4}, \hspace{\cbasisspacing}
      \GeneralizedMatching{5}{1/2, 4/5}{1}{3/1}{3/4}, \hspace{\cbasisspacing}
      \GeneralizedMatching{5}{1/2, 3/4}{1}{5/1}{3/4}, \hspace{\cbasisspacing}
      \GeneralizedMatching{5}{1/4, 2/3}{1}{5/1}{3/4}, \hspace{\cbasisspacing}
     \end{gathered}}$ 
    \caption{The basis for $W_5^1$.}
  \label{S5 Basis}
\end{figure}

We will prove that $W := W_{2n+r}^r$ and $S := S^{(n+r,n)'}$ are isomorphic as representations in the case that $e > n + r + 1$.
Note that, when $r = 0$, these have the same dimension given by the $n$th catalan number $C_n$.

\subsection{Fibonacci Representation}
Now suppose that $k = \CC$ and $q = \exp\prn{2 \pi i \ell/5}$ is a primitive 5th root of unity.
Let $V^m$ be a $k$-vector space with basis given by the strings $\cbr{*,p}^{n+1}$ such that the character $*$ never appears twice in a row. 
We will surpress the superscript whenever it is clear from context.

We wish to endow this with a $\SH$-action which acts on a basis vector only dependent on characters $i,i+1,i+2$, sending each basis vector to a combination of the other basis vectors having the same characters $1,\dots,i,i+2,\dots,n+1$ as follows:
\def\vara{\alpha}
\def\varb{\beta}
\def\varc{\gamma}
\def\vard{\delta}
\def\vare{\varepsilon}

\begin{equation}
  \begin{split}
  T_1 \, (*pp) &:= \vara(*pp)\\
  T_1 \, (pp*) &:= \vara(pp*)\\
  T_1 \, (*p*) &:= \varb(*p*)\\
  T_1 \, (p*p) &:= \varc(p*p) + \vard(ppp)\\
  T_1 \, (ppp) &:= \vard(p*p) + \vare(ppp)
\end{split} \label{Fib Action} 
\end{equation}
for constants
\begin{equation}
  \begin{split}
  \vara &= -1\\
  \varb &= q\\
  \varc &= \tau(q\tau - 1)\\
  \vard &= \tau^{3/2}(q + 1)\\
  \vare &= \tau(q-\tau)\\
  \tau &= \begin{cases}
    \frac{1}{2}\prn{\sqrt 5 - 1} & \ell \equiv 1,4 \pmod 5\\
    \frac{1}{2}\prn{\sqrt 5 + 1} & \ell \equiv 2,3 \pmod 5
  \end{cases}
\end{split} \label{Fib Constants} 
\end{equation}
with $T_i$ acting similarly on the substring $i,i+1,i+2$.
We will verify that this is a representation of $\SH$ in Appendix \ref{Fib Relations}

This contains 4 subrepresentations based on the first and last character of the string, which are not modified by $\SH$.
Label the subrepresentation of strings $(*\dots*)$ by $V_{**}$, and similar for the other 3.
It is easy to see that $V_{*p} \simeq V_{p*}$, so that
\[
  V \simeq 2V_{*p} \oplus V_{**} \oplus V_{pp}.
\]
We will show that $V_{pp} \simeq V_{*p} \oplus V_{**}$, and give the following isomorphisms with irreducible quotients of specht modules depending on the parity of the number of indices in $\SH$:
\begin{equation}
  \begin{split}    
    F^{2n}_{**} &\simeq D^{(n,n)'}\\ 
    F^{2n-1}_{**} &\simeq D^{(n+1,n-2)'}\\
    F^{2n}_{*p} &\simeq D^{(n+1,n-1)'}\\
    F^{2n-1}_{*p} &\simeq D^{(n,n-1)'}.
  \end{split} \label{Fib Isos}
\end{equation}

\section{Crossingless Matchings and Specht Modules}
\section{The Fibonacci Representation and Specht Modules}
\section{Explicit Relationships}

\newpage
\appendix
 \section{Compatibility of Representations with the Relations}
In general, we define representations above for the free algebra on generators $\cbr{T_i}$.
Recall that we may give a presentation of $\SH$ having generators $T_i$ and relations
\begin{align}
  (T_i - q)(T_i + 1) &= 0 \label{quadratic}\\
  T_iT_{i+1}T_i &= T_{i+1}T_iT_{i+1} \label{braid1}\\ 
  T_iT_j &= T_jT_i \hspace{40pt} \abs{i - j} > 1. \label{braid2}
\end{align}
We call \eqref{quadratic} the \emph{quadratic relation} and \eqref{braid1}, \eqref{braid2} the \emph{braid relations}.
It is easily seen that a representation of $\SH$ is equivalent to a representation of the free algebra $k\langle T_i \rangle$ which acts as 0 on the relations (henceforth referred to as \emph{compatibility} with the relations).
We will prove in the following sections that $V$ and $W$ are compatible with the Hecke algebra relations.

\subsection{The Crossingless Matchings Representaiton}
\label{Cross Relations}
Take some basis vector $w_i$.
We will first check \eqref{quadratic} by case work:
\begin{itemize}
  \item Suppose there is an arc $(i,i+1)$.
    Then, $(T_i-q)(T_i + 1)w = (1 + q)\brk{(1 + T_i)w - (1 + q)w} = 0$, giving \eqref{quadratic}.

  \item Suppose there is no arc $(i,i+1)$ and $i,i+1$ do not both have anchors;
    then $(T_i +  1)w = q^{1/2}w''$ for some basis vector $w'$ having arc $(i,i+1)$, and the computation follows as above for \eqref{quadratic}.
  \item Suppose $i,i+1$ are anchrors;
    then $(T_i + 1)w = 0$, giving \eqref{quadratic}.
\end{itemize}

\vspace{5pt}
Now we verify \eqref{braid1}.
Let $h := (1 + T_i)(1 + T_{i+1})(1+T_i)$, and let $g := (1 + T_{i+1})(1 + T_i)(1 + T_{i+1})$.
Note the following expansion:  
  \begin{align*}
      hw
      &= 1 + 2T_i + T_i^2 + T_{i+1} + T_iT_{i+1} + T_{i+1}T_i + T_iT_{i+1}T_i\\
      &= 1 + (1+q)T_i + T_{i+1} + T_iT_{i+1} + T_{i+1}T_i + T_iT_{i+1}T_i.
    \end{align*}
    An analogous formula gives an analogous equality in $g$.
    Hence we have
    \[
      (h-g)w = q(T_i - T_{i+1}) + T_iT_{i+1}T_i - T_{i+1}T_iT_{i+1}.
    \]
    Hence we may equivalently check that $(h-g)w = q(T_i - T_{i+1})$.
    This is illustrated in Figure \ref{braid1arc}.
    \begin{figure}[b]
  \[
    \GeneralizedNAction{5}{1/2,3/4}{1}{5/1}{3/4}{2/1, 1/2,2/3}{1/4,2/3}{5/1}{q^{3/2}}
    \hspace{20pt}
    \GeneralizedNAction{5}{1/2,3/4}{1}{5/1}{3/4}{1/1, 2/2,1/3}{1/2,3/4}{5/1}{q(q+1)}
  \]
  \[
    \NAction{6}{1/6,2/5,3/4}{1/1,2/2,1/3}{1/2,3/4,5/6}{q^{3/2}}
    \hspace{20pt}
    \NAction{6}{1/6,2/5,3/4}{2/1,1/2,2/3}{1/6,2/3,4/5}{q^{3/2}}
  \]
  \[
    \GeneralizedZeroAction{4}{3/4}{2}{1/1,2/2}{.5}{1}
    \hspace{20pt}
    \GeneralizedNAction{4}{3/4}{2}{1/1,2/2}{.5}{2/1, 1/2,2/3}{2/3}{1/1,4/2}{q(q+1)}
  \]
  \caption{
    Here we verify in small cases that $hw = qT_i$ and $gw = qT_{i+1}$.
    These 6 cases cover the situations that there is an arc among the indices $i,i+1,i+2$, that there isn't and there are not two arcs, and that there are two arcs.
  }
  \label{braid1arc}
\end{figure}

Lastly, we have the equation
\[
  (1 + T_i)(1 + T_j) - (1 + T_j)(1 + T_i) = T_iT_j - T_jT_i
\]
and hence we simply need to verify that $(1 + T_i)$ and $(1 + T_j)$ commute, which the reader may easily check.

\subsection{The Fibonacci Representation} 
\label{Fib Relations}
Similar to before, the reader may verify that \eqref{braid2} follows easily, and the others may be verified on strings of length 3 and 4.
By considering the coefficients in order of \eqref{Fib Action}, the quadratic relation \eqref{quadratic} gives the following quadratics:
\begin{equation}
  \begin{split}
    (\vara - q)(\vara + 1) &= 0\\
    (\varb - q)(\varb + 1) &= 0\\
    \varc\vard + \vard\vare &= (q-1)\vard\\
    \varc^2 + \vard^2 &= (q -1)\varc + q\\
    \vare^2 + \vard^2 &= (q -1)\vare + q
  \end{split}
\end{equation}
The first two of these are easily verified for any $q$.
Since $\vard \neq 0$, the third is equivalently given by
\[
  (q - 1) = \varc + \vare = t(q\tau - 1 + q - \tau) = (\tau^2 + \tau)(q - 1)
\]
or that $\prn{\tau^2 + \tau - 1}(q-1) = 0$.
The reader may verify that $\tau^2 + \tau - 1 = 0$, so this is true for every $q$.

The fourth is given by the quadratic
\[
  \tau^2\brk{(q\tau-1)^2 - \tau(q+1)} = \tau(q-1)(q\tau - 1) + q
\]
or equivalently,
\[
  (\tau^2 + \tau - 1)\brk{q\prn{qt^2 + 1} + t} = 0
\]
which is true for every $q$.

The fifth is similarly given by
\[
  (\tau^2 + \tau - 1)\brk{q\prn{qt + 1} + t^2} = 0 
\]
which is true for every $q$.

\vspace{7pt}
We now verify \eqref{braid1}.
We may order the basis for $V^4$ as follows:
\[
  \cbr{(pppp),(*pp*),(ppp*),(*ppp),(*p*p),(p*p*),(pp*p),(p*pp)}.
\]
Then, in verifying the braid relation \eqref{braid1} in this order, we encounter the following quadratics (with tautologies and repetitions omitted):
\begin{align*}
    \vara\vare^2 + \varb\vard^2 &= \vara^2 \vare\\
    \vara\vard\vare + \varb\varc\vard &= \vara\varb\vard\\
    \varb\varc^2 + \vara\vard^2 &= \varb^2\varc\\
    \vara\varc^2 + \vard^2\vare &= \vara^2\varc\\
    \vard\vare^2 + \vara\varc\vard &= \vara\vard\vare
\end{align*}
The reader may verify that each of these are satisfied for $q$ a primitive 5th root of unity and $\tau$ as defined.

This highlights the difficulty with deforming our module to $q = 1$ at any field;
the quadratic relations require that $(\tau^2 + \tau - 1)(\tau^2 + \tau + 1) = 0$, but neither of these appear in the first braid relation, which reads $\tau (\tau^3 - 6 \tau^2 + 1) = 0$.
If we have $\tau^2 + \tau \pm 1 = 0$, then $\tau \neq 0$ and $-7\tau^2 \pm \tau + 1 = 0$.
Hence $(7 \pm 1)\tau + (1 \pm 1) = 0$, implying that $\tau = \frac{1}{4},0$, neither of which satisfy $\tau^2 + \tau \pm 1 = 0$, a contradiction.

To attempt to deform this to $q = 1$ would require that we rewrite $\varc,\vard,\vare$ entirely, rather than simply modifying $\tau$.

\end{document}

### 2019-07-19 tex/Rough-Overview.tex
Rough overview minus some technical details

@@
 Either $q = 1$ and $e$ is the characteristic of $k$, or $q \neq 1$ and $q$ is a primitive $e$th root of unity.
+
+\textbf{*** Insert Jargon about Good Numbers Here ***}
 
@@
 using this, we may order the crossingless matchings with no anchors in increasing lexicographical order in order to obtain an order on the subbasis containing a particular set of anchors;
-let the basis be ordered first by the position of the anchors in increasing lexicographical order, then increasing for the matchings between each anchor.
+let the basis be ordered first by the position of the anchors in decreasing lexicographical order, then increasing for the matchings between each anchor.
 Let this basis be $\cbr{w_i}$.
@@
     \begin{gathered}
+      \GeneralizedMatching{5}{1/2, 3/4}{1}{5/1}{3/4}, \hspace{\cbasisspacing}
+      \GeneralizedMatching{5}{1/4, 2/3}{1}{5/1}{3/4}, \hspace{\cbasisspacing}
+      \GeneralizedMatching{5}{1/2, 4/5}{1}{3/1}{3/4}, \hspace{\cbasisspacing}
       \GeneralizedMatching{5}{2/3, 4/5}{1}{1/1}{3/4}, \hspace{\cbasisspacing}
       \GeneralizedMatching{5}{2/5, 3/4}{1}{1/1}{3/4}, \hspace{\cbasisspacing}
-      \GeneralizedMatching{5}{1/2, 4/5}{1}{3/1}{3/4}, \hspace{\cbasisspacing}
-      \GeneralizedMatching{5}{1/2, 3/4}{1}{5/1}{3/4}, \hspace{\cbasisspacing}
-      \GeneralizedMatching{5}{1/4, 2/3}{1}{5/1}{3/4}, \hspace{\cbasisspacing}
      \end{gathered}}$ 
@@
 
+\newpage
 \section{Crossingless Matchings and Specht Modules}
+Our goal is to prove that $W_{2n + r}^r \simeq S^{(n+r,n)'}$ when $e > n + r + 1$.
+\begin{proposition}
+  \begin{enumerate}[label={(\roman*)}]
+    \item
+    Suppose that $n,r > 0$.
+    Then, a filtration of $\Res W_{2n + r}^r$ is given by
+    \begin{equation}
+      0 \subset W_{2n + r - 1}^{r-1} \subset \Res \, W_{2n + r}^r \label{Filtration}
+    \end{equation}
+    with $\Res \, W_{2n + r}^r / W_{2n + r - 1}^{r-1} \simeq W_{2n + r - 1}^{r + 1}$. 
+    \item
+      We have the following isomorphism of representations:
+      \begin{equation}
+        W_{2n - 1}^1 \simeq \Res \; W_{2n}^0 \label{0 Restriction}
+      \end{equation}
+  \end{enumerate}
+\end{proposition}
+\begin{proof}
+  \textbf{(i)}
+  Note that we may identify the subrepresentation of $\Res \; W_{2n + r}^r$ having anchor $n$ with $W_{2n + r - 1}^{r-1}$.
+
+  Let $U := \Res \; W_{2n + r}^r / W_{2n + r - 1}^{r - 1}$. 
+  Let $\phi:U \rightarrow W_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $W_{2n + r - 1}^{r + 1}$.
+  It is not hard to verify that this is a well-defined isomorphism of vector spaces, so we must show that it is $\SH$-linear.
+
+  Given a basis vector $w_j$ with arc $(i,2n + r)$, $\phi$ is clearly compatible with $T_{i'}$ with $i' \neq i,i-1$.
+  Further, it's easy to verify that $\phi$ is compatible with $T_{i}$ and $T_{i-1}$, as actions on one anchor were designed for this deformation.
+  When there are anchors $(i,i+1)$, then $\phi(T_iw_j) = T_i\phi(w_j) = 0$, and similar for $T_{i -1}$.
+  Hence $\phi$ is an isomorphism of representations, and the statement is proven.
+
+  \textbf{(ii)}
+  This follows with the above proof, defining $W_{2n - 1}^{-1} := 0$
+\end{proof}
+
+\begin{lemma}
+  Every basis vector in $W_{2n + r}^r$ is cyclic.
+\end{lemma}
+\begin{proof}
+  We have already proven this in the $r = 0$ case, so suppose that $r > 0$.
+
+    Note that, between anchors $a<a'$ having no arc $b$ with $a < b < a'$, the $W_{a'-a}^0$ case allows us to generate the vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.\footnote{At the ends, we apply the $W_a^0$ case or the $W_{2n + r - a}^{0}$ case in the same way for the first $a$ or last $2n + r - a$ indices.}
+
+  Applying this between each arc gives us a vector with length-2 arcs and anchors, and we may use the appropriate $(1+T_i)$ to move anchors to any positions, and the reverse process from above to generate the correct matchings between arcs and generate any other basis vector.
+\end{proof}
+
+Let $K := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$.
+This will be a large technical tool in our proof of irreducibility.
+\begin{lemma}\label{Represented}
+  Let $w_j$ be the basis vector with anchors $1,\dots,r$ and all arcs of maximal length.
+  Suppose $w \in K \backslash \cbr 0$.
+  Then, $w_j$ is represented in $w$.
+\end{lemma}
+\begin{proof}
+  We will show this in steps; first, we show that, given that a vector is represented with anchors $1,\dots,s$, there must be a vector represented in $w$ with $(s+1)$st anchor, including when $s = 0$;
+  this implies that a vector is represented with anchors $1,\dots,r$.
+  Then, we will show that, given a vector is represented with anchors $1,\dots,r$ and first $s$ arc-lengths $n,n-2,\dots,n-2s$, there is a vector represented with these and the $(s+1)$st arc-length $n-2s-2$.
+  This implies that $w_j$ is represented.
+
+  \def\lemsep{7pt}
+  \vspace{\lemsep}
+  \textit{Step 1.}
+  Suppose that $s < r$ is the maximal number such that a vector with anchors $1,\dots,s$ is represented.
+  Take the vector $w_i$ which, among vectors represented in $w$ with anchors $1,\dots,s$, has $(s+1)$st anchor at minimal index $t > s + 1$,
+  Then, $q^{-1/2}(1 + T_{t-1})w_i$ has anchors $1,\dots,s$ and a earlier index than $t$, so it was not represented before;
+  further, for any other basis vector $w_l \neq w_i$ to map onto $q^{-1/2}(1 + T_{t-1})w_i$, we would require that $w_l$ has anchors $1,\dots,s$ and some other anchor at index $t' < t$, so it is not represented.
+  Hence $w_i$ is unique among the vectors represented mapping onto $q^{-1/2}(1 + T_{t-1})w_i$, and $(1 + T_{t-1})w$ represents this vector, giving $w \notin \ker (1 + T_{t-1})$.
+
+  When $s = 0$, this is similar, and we simply perform this logic on the 1st anchor.
+  Each lead to contradiction, so we must have $s = r$.
+
+  \vspace{\lemsep}
+  \textit{Step 2.}
+  This step is similar;
+  suppose that $s < n$ is the maximal number such that a vector with anchors $1,\dots,r$ and first $s$ arc-lengths $n,\dots,n-2s$ is represented.
+  Take the vector $w_i$ which, among vectors represented in $w$ with anchors $1,\dots,r$ and first $s$ arc-lenths $n,\dots,n-2s$, has maximal length $t$ of the arc beginning at index $r + s + 1$.
+  Then, $q^{1/2}(1 + T_{r + s + t})w_i$ is mapped to only by $w_i$ and vectors having anchors $1,\dots,r$ and first $s+1$ arc-lengths $n,\dots,n-2s,t'$ with $t' > t$, which are not represented in $w$;
+  hence $q^{-1/2}(1 + T_{r + s + t})w_i$ is represented in $(1 + T_{r+s+t})w$, giving $w \notin \ker (1 + T_{r + s + t})$.
+  The $s = 0$ case is similar, and implies that $s = n$.
+\end{proof}
+
+\begin{lemma}\label{Trivial}
+  Suppose $e \nmid n + r + 1$.
+  Then, $K = 0$.
+\end{lemma}
+\begin{proof}
+  Consider the matrix $A = \bigoplus (1 + T_i)$ having kernel $K$.
+  It is sufficient by lemma \ref{Represented} to show that $A$ includes a row $[0,\dots,0,1,0,\dots,0]$ with a nonzero entry only on the column $j$.
+
+  Now, we may characterize the rows of $A$ as follows;
+  if the row corresponding to $(1 + T_i)$ and mapping onto the element $w_l \in W$ is nonzero, then it is of the form $\brk{a_1,\dots,a_{\abs W}}$ where $a_l = 1 + q$, $a_m = q^{1/2}$ whenever $(1 + T_i)w_m = q^{1/2}w_l$, and $a_m = 0$ otherwise.
+
+  Seeing this, the row corresponding to $(1 + T_{n + r})$ and $w_j$ has nonzero entries $q^{1/2}$ at $w_j$ and $(1 + q)$ at the vector $w$ agreeing with $w_j$ at all indices except having arcs at $(n+r-1,n+r)$ and $(n+r+1,n+r+2)$.
+  Similar justification leads the row corresponding to $(1 + T_{n+r-1})$ at $w$ to have nonzero entries $q^{1/2}$ at $w$ and $(1 + q)$ at $w_j$ and the vector with anchors $1,\dots,r$ , arc $(n+r-3,n+r-2)$, and all other arcs maximum length.
+
+  \begin{figure}
+   \[
+     \Action{10}{1/2,3/10,4/9,5/8,6/7}{2}{1/10,2/3,4/9,5/8,6/7}{q^{1/2}}
+   \]
+   \[
+     \Action{10}{1/10,2/3,4/9,5/8,6/7}{2}{1/10,2/3,4/9,5/8,6/7}{q+1}
+   \]
+   \[
+     \Action{10}{1/10,2/9,3/4,5/8,6/7}{2}{1/10,2/3,4/9,5/8,6/7}{q^{1/2}}
+   \]
+   \caption{Illustrated is the row constructed for transposition $(1 + T_2)$; clearly these are the only basis elements mapping to multiples of the desired element, and they relate to each other.
+     replacing the outermost and/or innermost arc with an anchor typifies the rows constructed with three nonzero coefficients.}
+ \label{Submatrix}
+ \end{figure}
+
+  We may iterate this process as illustrated in Figure \ref{Submatrix}, eventually ending at a row with two nonzero entries, either an arc $(1,2)$ or an arc $(2,3)$, and all anchors otherwise left-aligned and arcs of maximum length.
+  These rows together form an $(n + r) \times \abs{W_{2n + r}^r}$ sumbatrix of $A$ which has a nonzero column in the row corresponding to $j$, and has (by removing zero columns) the same column space as the following square matrix:
+  \newcommand*\bigzero{\makebox(0,15){\text{\Huge0}}}
+  \newcommand*\bigzerotwo{\makebox(-20,15){\text{\Huge0}}}
+  \[
+    B_{n + r} := \begin{bmatrix}
+      \begin{matrix}
+      q + 1 & q^{1/2} & \\
+      q^{1/2} & q + 1 & q^{1/2}\\
+      & q^{1/2} & q + 1 & q^{1/2}\\
+      &  & \ddots & \ddots
+      \end{matrix}
+      &   \bigzero\\
+      \bigzerotwo & \begin{matrix}
+        q^{1/2} & q+1 & q^{1/2}\\
+        &  q^{1/2} & q + 1
+       \end{matrix}
+    \end{bmatrix}.
+  \]
+  We will show that this matrix is invertible;
+  then, a sequence of elementary row operations will yield the identity, and in particular, when applied to $A$, will yield a row with a nonzero entry only on column $j$, giving $K = 0$.
+
+  We may prove invertibility of this matrix by proving that $\det B_{n + r} = \brk{n + r + 1}_q$ inductively on $n+r$.
+  This is satisfied for our base case $n + r = 1$, so supose that it is true for each $m < n + r$.
+  Then,
+  \begin{align*}
+    \det B_{n+r} &= (q + 1) \det B_{n + r - 1} - q \det B_{n + r - 2}\\
+    &= (q + 1)(1 + \dots + q^{n + r - 1}) - (q + \dots + q^{n + r - 1})\\
+    &= 1 + \dots + q^{n + r}\\
+    &= \brk{n + r + 1}_q.
+  \end{align*}
+  Hence $\det B_{n + r} \neq 0$, and $K = 0$.
+\end{proof}
+
+\begin{proposition}
+  The representation $W_{2n + r}^r$ is irreducible when $e > n + r + 1$. 
+\end{proposition}
+\begin{proof}
+  We proceed by induction on $2n + r$.
+  Note that, by identification with the trivial and sign representations, the base case $2n + r = 2$ is already prove, so suppose we have proven this for each $2m + s < 2n + r$.
+
+  Take some $w \in W$ and some $(1 + T_i)$ not annhialating $w$.
+  Note that \[\ima (1 + T_i) = \Span\cbr{w_j \mid w_j \text{ contains arc }(i,i+1)}.\]
+  Hence, as vector spaces, there is an isomorphism $\varphi:\ima(1 + T_i) \rightarrow W_{2(n-1) + r}^r$ ``deleting'' the arc $(i,i+1)$.
+  This sends every basis vector to another basis vector.
+
+  We will show that, for every action $(1 + T_j') \in \SH(S_{2(n-1) + r})$, there is some action $h_j \in W_{2n + r}^r$ such that the following commutes:
+  \[
+    \begin{tikzcd}
+      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] \arrow[d,"h_j"] & W_{2(n-1) + r}^r \arrow[d,"1 + T_j"]\\
+      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] & W_{2(n-1) + r}^r
+    \end{tikzcd}
+  \]
+  Indeed, when $i \neq j$ this is given by $h_j = 1 + T_j$, and we have $h_i = q^{-1}(1 + T_i)(1 + T_{i+1})(1 + T_{i-1})$, as given by Figure \ref{bigloop}.
+
+  Due to the inductive hypothesis, there is some action $h' \in \SH(S_{2(n-1) + r})$ sending $\varphi((1 + T_i)w)$ to a basis vector;
+  then, the action $\SH$ generates the endomorphism $\varphi^{-1}h'\varphi$ sending $(1 + T_i)w$ to a basis vector, giving $w$ cyclic and hence $W_{2n + r}^r$ irreducible.
+  \begin{figure}
+  \[
+    \Action{6}{1/6, 2/5, 3/4}{2}{1/6, 2/3, 4/5 }{q^{1/2}} \hspace{20pt} 
+    \IsoAction{8}{1/8, 2/7, 3/4, 5/6}{3}{1/8, 2/5, 3/4, 6/7}{q^{1/2}}
+  \]
+  \[
+    \Action{4}{1/4, 2/3}{2}{1/4,2/3}{(1 + q)} \hspace{20pt}
+    \IsoAction{6}{1/6, 2/5, 3/4}{3}{1/6, 2/5, 3/4}{(1 + q)}
+  \]
+  \caption{The correspondence between the action of $(1 + T_2)$ on $w'_5 \in W^0_6$ and the action of $q^{-1}(1 + T_3)(1 + T_4)(1 + T_2)$ on the corresponding vector in $W^0_8$ having arc $(3,4)$ first, then on $w'_2 \in W^0_4$.
+  This demonstrates that the action works with and without creating a loop.
+  }
+  \label{bigloop}
+  \end{figure}
+\end{proof}
+
+\iffalse
+The next piece in our puzzle is to characterize the restrictions of $W$ to $\SH' := \SH_{k,q}(S_{2n + r - 1}) \subset \SH$.
+Recall that, when $r,n>0$ and $\SH$ is semisimple,  $\Res S^{(n+r,n)'} \simeq S^{(n+r-1,n)'} \oplus S^{(n+r,n-1)'}$.
+Further, note that $S^{(n+r,n)'}$ is the unique irreducible having this restriction.
+
+Next, note that we have already proven the correspondence for $W_{2n}^0$;
+for $W_{0 + r}^{r}$, this is the sign representation, which is given correctly by $S^{(r)}$.
+Hence, pending information on restrictions, we may prove this via induction on $2n + r$.
+\fi
+
+\begin{corollary}
+  Suppose $n,r > 0$ and $e > n + 1$.
+  Then, the sequence \eqref{Filtration} is a composition series of $\Res \, W_{2n + r}^r$.\qed
+\end{corollary}
+
+\begin{theorem}
+  Suppose $e > n + r + 1$, $n > 0$.
+  Then, $W_{2n + r}^r \simeq S^{(n+r,n)'}$.
+\end{theorem}
+\begin{proof}
+  By irreducibility, we know that $W_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
+  We will proceed in two steps;
+  first we prove that $\lambda = (n+r,n)'$, then we prove that $S^{(n+r,n)'}$ is irreducible.
+
+  This will be done inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $W_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e.
+$e > m + s + 1$).
+
+  \def\thmsep{7pt}
+  \vspace{\thmsep}
+  \textit{Step 1.}
+  By the inductive hypothesis and irreducibility, we have a composition series given by 
+  \begin{equation}
+    \label{Composition Series} 0 \longrightarrow D^{(n + r - 1,n)'} \longrightarrow \Res \, D^\lambda \longrightarrow D^{(n+r,n-1)'} \longrightarrow 0
+  \end{equation}
+  In particular, by the Jordan-H\"older theorem, if we have some module $D^\mu \subset \Res \, D^\lambda$, then $\mu = (n+r-1,n)'$ or $\mu = (n+r,n-1)'$.
+
+  By Kleschev, we know that $\soc(D^\lambda) = \bigoplus_{\mu} D^\mu$, where $\mu$ ranges over $\lambda(i)$ for every good number $i$ of $\lambda$.
+  Immediately this narrows down $\lambda$ to three options;
+  the only $\lambda$ with some $\lambda(i)$ giving $(n + r - 1,n)'$ are $\lambda_1 ;= (n+r-1,n,1)'$, $\lambda_2 = (n+r-1,n+1)'$, and $\lambda_3 = (n+r,n)'$.
+
+  Note numbers $\beta_l(i,j)$ correspond to hook-lengths, and each $\lambda_;$ has maximum hook length $n + r + 1$;
+  hence $\beta_l(i,j) \not\equiv 0 \pmod e$ for all $i,j,l$, and 3 is a good number in $\lambda_1$ and 2 in $\lambda_2$.
+  This implies $D^{(n+r-2,n,1)'} \subset D^{\lambda_1}$ and $D^{(n+r-2,n+1)'} \subset D^{\lambda_2}$, giving that $\lambda = \lambda_3$ as desired.
+
+  \vspace{\thmsep}
+  \textit{Step 2.}
+  Let the hook length of node $(a,b)$ in $\brk \lambda$ be written $h_{ab}^\lambda$.
+  Let $\nu_p(h_{ab}^\lambda)$ be the $p$-adic valuation of $h_{ab}^\lambda$, and let $\nu_{e,p}(h_{ab}^\lambda)$ be $\nu_p(h^{J})$.
+  Mathas Theorem 5.42 says, for $\lambda$ $e$-restricted, $S^\lambda$ is irreducible if $\nu_{e,p}(h_{ab}^\lambda) = \nu_{e,p}(h_{ac}^\lambda)$ for a suitable prime $p$.
+  In particular, since $h_{ab}^\lambda < e$ for all $a,b$, we have $\nu_{e,p}(h_{ab}^\lambda) = -1$ for all $a,b$, and $S^\lambda$ is irreducible.
+\end{proof}
+
+\iffalse
+\begin{proposition}
+  Suppose $e > n + r + 1$, and let $\lambda$ be a partition of $2n + r$.
+  \begin{enumerate}[label={(\roman*)}]
+    \item Suppose $n,r > 0$.
+      If $\Res \, D^\lambda$ admits a filtration $0 \subset S^{(n+r-1,n)'} \subset \Res \, S^\lambda$ with $\Res \, S^\lambda / S^{(n + r - 1,n)'} \simeq S^{(n + r,n-1)'}$ then $\lambda = (n+r,n)'$.
+    \item Suppose $r = 0$.
+      If $\Res \, S^\lambda \simeq S^{(n,n-1)'}$, then $\lambda = (n,n)'$.
+  \end{enumerate}
+\end{proposition}
+\begin{proof}
+  \textbf{(i)}
+  Recall that the characteristic-free classical branching theorem gives that every specht module $S^{\lambda}$ admits a filtration 
+  \begin{equation}
+    0 = M_0 \subset \dots \subset M_l = S^{\lambda} \label{filtration}
+  \end{equation}  
+    with $M_i/M_{i-1} \simeq S^{\lambda(i)}$.
+  Hence $\lambda = (n + r, n)'$ satisfies the above formula.
+
+  Note that, when $e > n + r + 1$, this filtration gives a composition series.
+  Hence the sequence \eqref{filtration} is at most length-2.
+
+  Suppose it is length-1.
+  Then $\lambda$ is rectangle-shaped;
+  to have rows removed to the above we then need that that it be $\lambda = \prn{\frac{2n + r}{2}, \frac{2n + r}{2}}'$, so that $\Res S^{\lambda} \simeq S^{\prn{\frac{2n + r}{2}, \frac{2n + r}{2} - 1}'}$.
+  However, since $e > n + r + 1 \geq n + \frac{r}{2} + 1$, $\Res \, S^{\lambda}$ is irreducible, contradicting the existence of a length-2 composition series in the hypothesis.
+
+  Now suppose that \eqref{filtration} is length 2, so that it is also a composition series.
+  Then, by the Jordan-H\"older theorem, there is a rearranement of the composition factors of \ref{filtration} to give $S^{(n + r - 1,n)'}$ and $S^{(n + r, n - 1)'}$.
+  This implies that both $(n + r - 1,n)'$ and $(n + r,n-1)'$ can be acquired by removing rows of $\lambda$, giving that $\lambda = (n+r,n)'$.
+
+  \vspace{7pt}
+  \textbf{(ii)}
+  Note that, since $e > n + 1$, $\Res S^\lambda$ is irreducible.
+  Hence the sequence \eqref{filtration} is a composition series of length 1, and $\lambda(1) = (n,n-1)'$.
+  The first implies that $\lambda$ is rectangular, and the second implies that $\lambda = (n,n)'$.
+\end{proof}
+\fi
+
 \section{The Fibonacci Representation and Specht Modules}
+We can start our study of $V$ by studying low-dimensional cases.
+First, note that $V_{*p}^2$ is the sign representation $D^{(2)}$ and $V_{**}^2$ is the trivial representation $D^{(1)^2}$.
+
+$V_{pp}^2$ is a 2-dimensional representation of a semisimple commutative algebra, and hence decomposes into a direct sum of two subrepresentations.
+In particular, we can use the basis $\cbr{(p*p),(ppp)}$ and explicitly write the matrix
+\[
+  \rho_{T_1} = \begin{bmatrix}
+    \varc & \vard\\
+    \vard & \vare
+  \end{bmatrix}
+\]
+having characteristic polynomial $(c - \lambda)(e - \lambda) - d^2 = \lambda^2 - (c + e)\lambda +(ce - d^2)$.
+The reader can verify that this has roots $-1$ and $q$.
+The eigenspaces with eigenvalues $-1$ and $q$ are subrepresentations isomorphic to the sign and trivial representation, hence $F_{pp}$ is isomorphic to a direct sum of the trivial and sign representations: $V^2_{pp} \simeq V^2_{*p} \oplus V^2_{**}$.
+
+Now let's prove that $V^3_{**}$ is irreducible;
+this has basis $\cbr{*p*p}, \cbr{*ppp}$, and the following matrices:
+\[
+  \rho_{T_1} = \begin{bmatrix}
+    \varb & 0\\
+    0 & \vara
+  \end{bmatrix}; \hspace{20pt}
+  \rho_{T_2} = \begin{bmatrix}
+    \varc & \vard\\
+    \vard & \vare
+  \end{bmatrix}.
+\]
+A subrepresentation must be one-dimensional, and hence an eigenspace of each of these matrices;
+since $\varb \neq \vara$, the first has eigenspaces given by the spans of basis elements, and since $\vard \neq 0$, these are not eigenspaces of the second.
+Hence $V^3_{**}$ is irreducible.
+Now we may move on to the general case.
+\begin{proposition}
+  The representation $V_{*p} := V^m_{*p}$ is irreducible.
+\end{proposition}
+\begin{proof}
+  We will prove this inductively in $m$.
+  We've already proven it for $V^2_{*p}$ and $V^3_{*p}$, so suppose that $V^{m-2}_{*p}$ is irreducible.
+
+  Let $\cbr{v_i}$ be the basis for $V_{*p}$.
+  Then, each $v_i$ is cyclic; indeed, we can transform every basis vector into $(*p\dots p)$ by multiplying by the appropriate $\frac{1}{\vard-\varc}(T_i - \varc)$, and we can transform $(*p\dots p)$ into any basis vector by multiplying be the appropriate $\frac{1}{\vard-\vare}(T_i - \vare)$.
+  Hence it is sufficient to show that each $v \in V_{*p}$ generate some basis element.
+
+  Let $v'$ be the basis element $(*p*p\dots p)$, which is many copies of $*p$, followed by an extra $p$ if $m$ is odd.
+  We will show that each $v \in F$ generates $v'$.
+
+  Suppose that no elements beginning $(*p*p)$ are represented in $v_i$;
+  then, all such elements are represented in $T_3v$, so we may assume that at least one is represented in $v$.
+
+  Note that $\ima (T_2 - \vara) = \Span\cbr{\text{Basis vectors beginning }(*p*p)}$ and $(T_2 - \vara)v \neq 0$.
+  Further, note that $\Res_{\SH(S_{m-2})}^{\SH(S_m)} \ima (T_2 - \vara) \simeq V^{m-2}_{*p}$ as representations.
+  Hence irreducibility of $V^{m-2}_{*p}$ implies that $v'$ is generated by $(T_2 - \vara)v$, and $V^m_{*p}$ is irreducible.
+\end{proof}
+
+Knowing this, the restriction statements are clear;
+$\Res V_{*p}^m \simeq V_{pp}^{m-1}$ by considering the last $m-2$ transpositions, and $\Res V_{*p}^{m-1} \simeq V_{*p}^{m-1} \oplus V_{**}^{m-1}$ by considering the first $m-2$.
+Similarly, $\Res V_{**}^m \simeq V_{*p}^{m-1}$ by considering the first $m-2$ transpositions.
+This gives that $V \simeq 3V_{*p} \oplus 2V_{**}$.
+
+Now we may move on and use Young Tableau to characterize $V$.
+Recall that the socle of $D^\lambda$ is given by $\bigoplus\limits_{\mu \xrightarrow{\text{good}} \lambda} D^\mu$,  and that $D^\lambda$ is semisimple iff every $\mu \xrightarrow{\text{normal}} \lambda$ is good.
+\begin{theorem}
+  The irreducible components of $V$ are given by the following isomorphisms:
+    \begin{align*} 
+      V^{2n}_{**} &\simeq D^{(n,n)'}\\ 
+      V^{2n-1}_{**} &\simeq D^{(n+1,n-2)'}\\
+      V^{2n}_{*p} &\simeq D^{(n+1,n-1)'}\\
+      V^{2n-1}_{*p} &\simeq D^{(n,n-1)'}.
+     \end{align*}
+\end{theorem}
+\begin{proof}
+  We will prove this by induction on $n$;
+  we have already proven the base case $V^{2}$, so suppose that we have proven these isomorphisms for $V^{2n-2}$.
+  We will prove the isomorphisms for $V^{2n-1}$ and $V^{2n}$.
+
+  By irreducibility, $V^{2n-1}_{**} \simeq D^{\lambda_{**}}$ and $V^{2n-1}_{*p} \simeq D^{\lambda_{*p}}$ for some diagrams $\lambda_{**}$ and $\lambda_{*p}$.
+  We will show that $\lambda_{**} = (n+1,n-2)'$ and $\lambda_{*p} = (n+1,n-1)'$.
+
+  First, note that we have \[\Res \; D^{\lambda_{**}} \simeq D^{(n,n-2)'} \simeq \Res \; D^{(n+1,n-2)'}\] and \[\Res \; D^{\lambda_{*p}} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)'}.\]
+  By semisimplicity of $\Res D^{\lambda_{**}}$ and $\Res D^{\lambda_{*p}}$, every normal cell in $\lambda_{**}$ and $\lambda_{*p}$ is good, and every good cell is removed in a summand of the restriction.
+
+  In particular, for $\lambda_{**}$, the only tableaux which can remove a cell to yield $D^{(n,n-2)'}$ are $(n+1,n-2)'$, $(n,n-1)'$, and $(n,n-2,1)'$ as illustrated in Figure \ref{OddRes};
+  we have already seen that $D^{(n,n-1)'}$ does not have irreducible restriction, so we are left with $(n+1,n-2)'$ and $(n,n-2,1)'$.
+  To have irreducible restriction, $\lambda_{**}$ must have 1 as its only normal number;
+  we may directly check that $(n,n-2,1)'$ doesn't satisfy this, as we have the following:
+  \begin{align*}
+    \beta_\lambda(1,2) &= 3 - 2 + (n-2) = n-1\\
+    \beta_\lambda(1,3) &= 3 - 1 + n = n+2\\
+    \beta_\lambda(2,3) &= 2 - 1 + 3 = 4.
+   \end{align*}
+  At least one of $\beta(1,2)$ and $\beta(1,3)$ is nonzero, and hence at least one of $M_2$ and $M_3$ is empty.
+  Hence at least one of 2 or 3 is normal, and $\lambda_{**} = (n+1,n-2)$.
+
+  For $\lambda_{*p}$, we immediately see from Figure \ref{OddRes} that the only option is $(n,n-1)$.
+  \begin{figure}
+    \[
+      \cbr{
+        \begin{gathered}
+        \ydiagram{2,2,2,1,1,1}. \; \;
+        \ydiagram{2,2,2,2,1}, \; \;
+        \ydiagram{3,2,2,1,1}
+      \end{gathered} 
+    }\longrightarrow \begin{gathered}
+      \ydiagram{2,2,2,1,1}
+      \end{gathered}
+      \hspace{50pt}
+      \cbr{
+        \begin{gathered}
+          \ydiagram{2,2,2,2,1}
+        \end{gathered}
+      }\longrightarrow
+      \begin{gathered}
+        \ydiagram{2,2,2,1,1},\;\;
+        \ydiagram{2,2,2,2}.
+      \end{gathered}
+    \]
+    \caption{
+      Illustration of the partitions of $9$ which can, via row removal, yield $(n,n-2)'$ alone, or both $(n,n-2)'$ and $(n-1,n-1)'$.
+    }\label{OddRes}
+  \end{figure}
+
+  We can perform a similar argument for the $V^{2n}$ case, finding now that 
+  \[\Res \; D^{\mu_{**}} \simeq D^{(n,n-1)'} \simeq \Res \; D^{(n,n)'}\] and 
+  \[\Res \; D^{\mu_{*p}} \simeq D^{(n,n-1)'} \oplus D^{(n+1,n-2)'} \simeq \Res \; D^{(n+1,n-1)'}.\]
+
+  Through a similar process, we see that $\mu_{*p} = (n+1,n-1)'$.
+  We narrow down $\mu_{**}$ to one of $(n,n)'$ or $(n,n-1,1)'$, and note that
+  \begin{align*}
+    \beta_\mu(1,2) &= 3 - 2 + (n-1) = n\\
+    \beta_\mu(1,3) &= 3 - 1 + n = n+2\\
+    \beta_\mu(2,3) &= 2 - 1 + 2 = 3
+  \end{align*}
+  and hence at least one of 2 or 3 is normal, $\Res D^{(n,n-1,1)'}$ is not irreducible, and $\mu_{**} = (n,n)'$, finishing our proof.
+\end{proof}
+\begin{corollary}
+  We have the following isomorphisms of representations:
+  \begin{align*}
+    V^{2n} \simeq 3D^{(n+1,n-1)'} \oplus 2D^{(n,n)'}
+    V^{2n - 1} \simeq 3D^{(n,n-1)'} \oplus 2D^{(n+1,n-2)'}
+  \end{align*}
+\end{corollary}
+
 \section{Explicit Relationships}
@@
 
+\section{Miscellaneous Algebra Facts}
+\begin{proposition}
+  Suppose $B,B'$ are subalgebras of the $k$-algebra $A$ with $B = uB'u^{-1}$, and let $V$ be a representation of $A$.
+  Then, $\Res_{B}^A V \simeq \Res_{B'}^a V$.
+\end{proposition}
+
 \end{document}

### 2019-07-19 tex/Rough-Overview.tex
Good/Normal jargon, statement of conjugacy of subalgebras

@@
 
-\textbf{*** Insert Jargon about Good Numbers Here ***}
+Throughout the text, we will refer to partitions of $2n + r$;
+identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
+Identify each of these with a subset $\brk \lambda \subset \NN^2$ as defined in Kleshev, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.
+
+Fixing some partition $\lambda$, for $1 \leq i \leq j \leq l$, let $\beta(i,j)$ be the hook length
+\[
+  \beta(i,j) = \lambda_i - \lambda_j + \sum_{t = i}^j a_t.
+\]
+Then, adopting Kleshev's terminology, $j$ is normal in $\lambda$ if $\beta(i,j) \not\equiv 0 \pmod e$ for all $i < j$, and $j$ is good if it is the largest normal number (these are stronger conditions than generally necessary).
 
@@
   By semisimplicity of $\Res D^{\lambda_{**}}$ and $\Res D^{\lambda_{*p}}$, every normal cell in $\lambda_{**}$ and $\lambda_{*p}$ is good, and every good cell is removed in a summand of the restriction.
+  In particular, the only normal number in $\lambda_{**}$ is 1.
 
-  In particular, for $\lambda_{**}$, the only tableaux which can remove a cell to yield $D^{(n,n-2)'}$ are $(n+1,n-2)'$, $(n,n-1)'$, and $(n,n-2,1)'$ as illustrated in Figure \ref{OddRes};
+  For $\lambda_{**}$, the only tableaux which can remove a cell to yield $D^{(n,n-2)'}$ are $(n+1,n-2)'$, $(n,n-1)'$, and $(n,n-2,1)'$ as illustrated in Figure \ref{OddRes};
   we have already seen that $D^{(n,n-1)'}$ does not have irreducible restriction, so we are left with $(n+1,n-2)'$ and $(n,n-2,1)'$.
-  To have irreducible restriction, $\lambda_{**}$ must have 1 as its only normal number;
-  we may directly check that $(n,n-2,1)'$ doesn't satisfy this, as we have the following:
+  We may directly check that $(n,n-2,1)'$ doesn't satisfy this, as we have the following:
   \begin{align*}
@@
    \end{align*}
-  At least one of $\beta(1,2)$ and $\beta(1,3)$ is nonzero, and hence at least one of $M_2$ and $M_3$ is empty.
-  Hence at least one of 2 or 3 is normal, and $\lambda_{**} = (n+1,n-2)$.
+  At least one of $\beta(1,2)$ and $\beta(1,3)$ is nonzero, since $\beta_\lambda(1,3) - \beta_\lambda(1,2) = 3 \not\equiv 0 \pmod e$, and hence at least one of $M_2$ and $M_3$ is empty.
+  Hence at least one of 2 or 3 is normal in $(n,n-2,1)'$, and $\lambda_{**} = (n+1,n-2)$.
 
@@
 \section{Miscellaneous Algebra Facts}
+Throughout the text, for some representation $V$, we refer to $\Res_{\SH(S_{l})}^{\SH(S_m)} V$ without specifying exactly which subalgebra $\SH(S_{l})$.
 \begin{proposition}
   Suppose $B,B'$ are subalgebras of the $k$-algebra $A$ with $B = uB'u^{-1}$, and let $V$ be a representation of $A$.
-  Then, $\Res_{B}^A V \simeq \Res_{B'}^a V$.
+  Then, the linear isomorphism $V \xrightarrow{\phi} V$ given by $v \mapsto uv$ causes the following to commute for any $b \in B$:
+  \[
+    \begin{tikzcd}
+      V \arrow[r,"\phi"] \arrow[d,"b"] & V \arrow[d,"ubu^{-1}"]\\
+      V \arrow[r,"\phi"] & V
+    \end{tikzcd}
+  \]
+  Hence, through the identification of $B$ and $B'$ via conjugation, we have $\Res_{B}^A V \simeq \Res_{B'}^A V$
 \end{proposition}
+\begin{proof}
+  This is simply given by $(ubu^{-1})uv = ubv$.
+\end{proof}
+
+\begin{corollary}
+  Suppose $\SH',\SH''$ are two subalgebras of $\SH(S_m)$ generated by $l$ reflections and $V$ is a representation of $\SH$.
+  Then, $\Res_{\SH'}^{\SH} V \simeq \Res_{\SH''}^\SH V$.
+\end{corollary}
+\begin{proof}
+  Let $\SH'$ and $\SH''$ be the subalgebras of $\SH(S_m)$ generated by the reflections $\cbr{T_{i_1},\dots,T_{i_l}}$ and $\cbr{T_{i_1},\dots,T_{i_{j-1}},T_{i_j + 1},T_{i_{j+1}},\dots,T_{i_l}}$ for $1 \leq i_1 < \dots < i_{j-1} < i_j + 1 < i_{j+1} < \dots < i_l \leq n$.
+  It is sufficient to prove that $\SH'$ and $\SH''$ are conjugate;
+  then transitivity gives conjugacy of any $S_l \subset S_m$, and the previous proposition gives isomorphisms of the representations.
+
+  In fact, the reader can verify that $\SH'' = T_{i_j}\SH'T_{i_j}^{-1}$.
+\end{proof}
 

### 2019-07-21 code/kernel_ranks.py
Added code to kernel_ranks to generate matrices for representation

@@ -1,192 +1,147 @@
-from cmath import sqrt
+import cmath
+import numpy
+import crossingless
+import time
+import csv
+import math
 
-# n: number of nodes (note that this must be even)
-# match: dictionary sending node to matching node
-# for example, {1:4,4:1,2:3,3:2} is the S4 rainbow
-#
-#
+def make_matrix(n,q,restriction = 1):
+    """
 
+    Create the matrix for the direct sum (1 + t_1) oplus ... oplus (1 + t_{i - 1 - restriction}) for parameter q
+    This has trivial kernel iff the restriction to S_{n - restriction} is irreducible.
+    
+    KEYWORD ARGUMENTS:
+    n -- parameter from S_n
+    q -- parameter of the hecke algebra (T_i - q)(T_i + 1) = 0
+    restriction -- the number of simple transpositions ignored.
+    """
+    assert n % 2 == 0
 
-class basis_element:
-    def __init__(self, n, match):
-        assert n % 2 == 0, 'n must be even'
-        self.n = n
-        assert len(match.keys()) == n, 'must have n nodes'
-        for i in match.keys():
-            assert match[i] != i, 'an element cannot be paired with itself'
-            assert i == match[match[i]], 'matchings are not symmetric'
-            for j in range(min(i, match[i])+1, max(i, match[i])):
-                assert min(i, match[i]) < match[j] and max(
-                    i, match[i]) > match[j], 'matchings cross'
-        self.match = match
+    # generate a basis; basisraw has basis_element elements, basis has module_element
+    basisraw = crossingless.generate_basis(n)
+    basis = [crossingless.module_element(n,{b:1},q) for b in basisraw]
 
-    # returns dictionary of matches nodes
-    def get_matches(self):
-        dictt = {}
-        for i in self.match.keys():
-            dictt[i] = self.match[i]
-        return dictt
+    C = len(basis)
+    m = numpy.zeros(C)
+    # i iterates over the simple transpositions considered
+    for i in range(n - restriction - 1):
+        # generate the matrix by applying the transposition to each basis vector and taking the resulting coefficients
+        outs = [b.mult_generator(i+1) for b in basis]
+        outsmat = numpy.matrix([[out.coeff(b) for out in outs] for b in basisraw])
+        m = numpy.vstack([m,outsmat])
+    
+    # prune zero rows from matrix
+    m = m[[i for i, x in enumerate(m) if x.any()]]
+    return m
 
-    # returns matching node to i
-    def pair(self, i):
[…]

### 2019-07-21 code/kernel_ranks.py
Oh my god why does runge.mit.edu not have numpy

@@ -134,14 +134,12 @@ for n in range(nmin,nmax+1,2):
     oldtime = newtime
 """
 
-
-n = 4
 q = 1
-write = csv.writer(open("Representation n={}.csv".format(n),"w"))
-rep = representation(n,q)
-rep = [arr.astype(int) for arr in rep]
-for arr in rep:
-    write.writerows(arr)
-    write.writerow(["/"])
-
-print(rep)
+for n in range(4,17,2):
+    write = csv.writer(open("Representation n={}.csv".format(n),"w"))
+    rep = representation(n,q)
+    rep = [arr.astype(int) for arr in rep]
+    for arr in rep:
+        write.writerows(arr)
+        write.writerow(["/"])
+    print("n={} completed.".format(n))

### 2019-07-21 code/kernel_ranks.py
Changed data to be more easily readible

@@ -136,10 +136,11 @@ for n in range(nmin,nmax+1,2):
 
 q = 1
 for n in range(4,17,2):
-    write = csv.writer(open("Representation n={}.csv".format(n),"w"))
+    f = open("Representation n={}.csv".format(n),"w")
+    
     rep = representation(n,q)
-    rep = [arr.astype(int) for arr in rep]
-    for arr in rep:
-        write.writerows(arr)
-        write.writerow(["/"])
+    rep = [arr.astype(int).tolist() for arr in rep]
+    rep = [[[str(i) for i in j] for j in k] for k in rep]
+    f.write("\n/\n".join(["\n".join([",".join(row) for row in arr]) for arr in rep]))
+    f.close()
     print("n={} completed.".format(n))

### 2019-07-22 code/crossingless.py
Fixed issue

@@ -88,7 +88,7 @@ class module_element:
             if basis.pair(i) == i+1:
                 new = new + \
                     module_element(
-                        self.n, {basis: self.vecpairs[basis]*sqrt(self.q)}, self.q)
+                        self.n, {basis: self.vecpairs[basis]*(self.q + 1)}, self.q)
             else:
                 match = basis.get_matches()
 
@@ -102,7 +102,7 @@ class module_element:
                 newbasis = basis_element(self.n, match)
                 new = new + \
                     module_element(
-                        self.n, {newbasis: self.vecpairs[basis]*(1 + self.q)}, self.q)
+                        self.n, {newbasis: self.vecpairs[basis]*sqrt(self.q)}, self.q)
         return new
 
     # Action by constant c, returns new element

### 2019-07-22 code/kernel_ranks.py
Fixed data

@@ -136,7 +136,7 @@ for n in range(nmin,nmax+1,2):
 
 q = 1
 for n in range(4,17,2):
-    f = open("Representation n={}.csv".format(n),"w")
+    f = open("Representation n={}".format(n),"w")
     
     rep = representation(n,q)
     rep = [arr.astype(int).tolist() for arr in rep]

### 2019-07-23 tex/Rough-Overview.tex
Added code to kernel_ranks to generate matrices for representation
Fixed data
Comments for the kernel proof

@@
 Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
-Either $q = 1$ and $e$ is the characteristic of $k$, or $q \neq 1$ and $q$ is a primitive $e$th root of unity.
+Either $q = 1$ and $e$ is the characteristic of $k$ (with $0$ replaced by $\infty$), or $q \neq 1$ and $q$ is a primitive $e$th root of unity.
 
@@
   \vare &= \tau(q-\tau)\\
-  \tau &= \begin{cases}
-    \frac{1}{2}\prn{\sqrt 5 - 1} & \ell \equiv 1,4 \pmod 5\\
-    \frac{1}{2}\prn{\sqrt 5 + 1} & \ell \equiv 2,3 \pmod 5
-  \end{cases}
+  \tau &= -1-q^2-q^3
 \end{split} \label{Fib Constants} 
@@
   \begin{split}    
-    F^{2n}_{**} &\simeq D^{(n,n)'}\\ 
-    F^{2n-1}_{**} &\simeq D^{(n+1,n-2)'}\\
-    F^{2n}_{*p} &\simeq D^{(n+1,n-1)'}\\
-    F^{2n-1}_{*p} &\simeq D^{(n,n-1)'}.
+    V^{2n}_{**} &\simeq D^{(n,n)'}\\ 
+    V^{2n-1}_{**} &\simeq D^{(n+1,n-2)'}\\
+    V^{2n}_{*p} &\simeq D^{(n+1,n-1)'}\\
+    V^{2n-1}_{*p} &\simeq D^{(n,n-1)'}.
   \end{split} \label{Fib Isos}
@@
 or that $\prn{\tau^2 + \tau - 1}(q-1) = 0$.
-The reader may verify that $\tau^2 + \tau - 1 = 0$, so this is true for every $q$.
+One may verify that \[\tau^2 + \tau - 1 = q^6 + 2q^5 + q^4 + q^3 + q^2 - 1 = (-1+q+q^2)\brk{5}_q = 0.\]
 
@@
 \end{align*}
-The reader may verify that each of these are satisfied for $q$ a primitive 5th root of unity and $\tau$ as defined.
-
-This highlights the difficulty with deforming our module to $q = 1$ at any field;
-the quadratic relations require that $(\tau^2 + \tau - 1)(\tau^2 + \tau + 1) = 0$, but neither of these appear in the first braid relation, which reads $\tau (\tau^3 - 6 \tau^2 + 1) = 0$.
-If we have $\tau^2 + \tau \pm 1 = 0$, then $\tau \neq 0$ and $-7\tau^2 \pm \tau + 1 = 0$.
-Hence $(7 \pm 1)\tau + (1 \pm 1) = 0$, implying that $\tau = \frac{1}{4},0$, neither of which satisfy $\tau^2 + \tau \pm 1 = 0$, a contradiction.
-
-To attempt to deform this to $q = 1$ would require that we rewrite $\varc,\vard,\vare$ entirely, rather than simply modifying $\tau$.
+Substituting in $\tau$ and dividing by $\delta$ whenever possible, these are equivalent to the vanishing of the following polynomials in $q$:
+\begin{align*}
+  -q (1 + q) (1 + q^2 + q^3) (2 + q + 3 q^2 + 2 q^3) \brk{5}_q &= 0\\
+  (1 + 2 q + q^3 + q^4) \brk{5}_q &= 0\\
+  (1+q)^2 (1+q^2+q^3) (1+3q^3 - q^4 + q^6)\brk{5}_q &= 0\\
+  (1+q)^2 (1+q^2+q^3) (1+5q+5q^2+3q^3+3q^4+3q^5+q^6)\brk{5}_q &= 0\\
+  (1+q) (1+q^2+q^3) (-1+2q+q^2+q^3+q^4)\brk{5}_q &= 0.
+\end{align*}
+Notably, each of these vanish when $e = 5$.
 

### 2019-07-23 tex/kernel.tex
Comments for the kernel proof

\documentclass{amsart}

\usepackage{NatMacros}
\usepackage{RepStyle}

\begin{document}

\title{A discussion of the intersection of the kernels of each $(1+T_i)$ acting on $W_{2n+r}^r$}
\author{Miles Johnson \& Natalie Stewart}

\maketitle

{\color{magenta} Natalie comments are magenta.}

\section{Introduction}

Let $\{T_i\}$ be the transpositions generating the Hecke algebra $\SH_{2n+r}(q)$. We assume $q\in \CC$.
{\color{magenta} It seems to me so far that the results of this anchor work in an arbitrary field, and that we may only at the end have to restrict to a field of characteristic at least $n + r + 1$ whenever $e \mid n + r + 1$.
Usually replacing $\CC^\times$ with $k^\times$ is free generality.
}
Let $W_{2n+r}^r$ be the generalized crossingless matchings representation with $2n+r$ nodes, $r$ of which are anchors. Fix the standard basis; we will refer to no other basis in this document. Here we characterize the intersection of the kernels of each $(1+T_i)$, a subrepresentation of $W_{2n+r}^r$. I claim this intersection is at most one dimensional, and is nontrivial if and only if $q$ is a $n+r+1$st root of unity.
{\color{magenta} I'll stop making this point after this, but this is not equivalent to $e = n + r + 1$.}

For compactness, in this document I use $\sim $ to denote "proportional to".

 \section{restricting the kernel}

\begin{definition}

  Fix some basis element $M\in W_{2n+r}^r$. Define $M(a):=b$ iff $a$ and $b$ are matched in $M$, $M(a):=a$ if $a$ is an anchor in $M$.
  {\color{magenta} Should specify that $a,b$ are integers $1 \leq a,b \leq 2n + r$.} 
  Given that $M$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $M(a,b)$ of $M$ to be the basis element $K\in W_{b-a+1}^{r'}$ specified by $K(i)=M(i+a-1)-a+1$. This sub-matching is defined for $a<b$ when $M(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$. See Figure 1.
\end{definition}

\begin{figure} 
	\def\cbasisspacing{5mm}
	$\cbr{
		\begin{gathered}
		\Matching{6}{1/2, 3/6, 4/5}, \hspace{\cbasisspacing}
		\Matching{4}{1/4, 2/3}
		\end{gathered}}$
	\caption{$M\in W_6^0$ is pictured on the left, $K\in W_4^0$ is pictured on the right. $M(3,6)=K$. $M(2,5)$ is not defined.}
	\label{S6 Basis}
\end{figure}

Define the rainbow element $R\in W_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$. In other words, the basis element with all anchors to the left then a rainbow.

\begin{proposition}
	Let $w$ be an arbitrary vector in $W_{2n+r}^r$. I claim that if $w\in \cap\text{ker}(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero.

\end{proposition}

\begin{proof}
  Let $Y$ be the set of basis elements with nonzero coordinate in $w$. Let $k$ be the greatest integer such that there exists $y\in Y$ where $y(1)=...=y(k)=0$ {\color{magenta} should this be $y(1)-1 = \dots = y(k) - k = 0$? Also, we should avoid using $k$ as an integer, as it's used elsewhere as a field.}, and let $U\subset Y$ be the set of such $y$. In other words, $U$ is the set of basis elements in $Y$ which have the most anchors to the far left.

	Suppose $k<r$. Then for each $y\in U$ there exists a minimal $i_y>k+2$ such that $y(i_y)=0$. In other words, $i_y$ is the position of the next leftmost anchor in $y$.  Fix $\tilde{y}$ such that $i_{\tilde{y}}\leq i_y$ for all $y$. Then I claim the basis element $y':=q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}$ has nonzero coordinate in $(1+T_{i_{\tilde{y}}-1})w$, implying $w\not\in \cap\text{ker}(1+T_i)$. To see this, we can show that $\tilde{y}$ is the only element in $Y$ such that $q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$. $y'$ still has $k$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$. If $x\in Y,\not\in U$, the basis element proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$. If $x\in U$ the basis element proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$. Since this is the only match altered by action $(1+T_{i_{\tilde{y}}-1})$ on $x$, if $(1+T_{i_{\tilde{y}}-1})x\sim y'$ this implies $x=\tilde{y}$. So if $k<r$ $w$ is not in the desired kernel.

	Suppose $k=r$ but $R\not\in U$ (so $R\not\in Y$). Let us define a sequence of subsets of $U$ in the following way: $U_0:=U$, $U_{i+1}:=\{u\in U_i| u(r+i+1)=2n+2r-i+1 \}$. Since $R\not\in U$, $\exists t<n-1$ such that $U_{t+1}=\emptyset$. Choose $\tilde{u}\in U_t$ such that $\tilde{u}(r+t+1)\geq u(r+t+1)$ for all $u\in U_t$. Consider the basis element $u':=q^{-1/2}(1+T_{\tilde{u}(r+t+1)})\tilde{u}$. I claim that $\tilde{u}$ is the only element in $Y$ such that $(1+T_{\tilde{u}(r+t+1)})\tilde{u}\sim u'$, again implying that $w$ is not in the desired kernel. $u'$ still has $k$ anchors on the left, $u'(r+i)=2n+2r-i+2$, $1\leq i\leq t$, and $u'(r+t+1)>\tilde{u}(r+t+1)$, so $u'\not\in Y$. If $x\in Y,\not\in U$,  the basis element $x'$ proportional to $(1+T_{\tilde{u}(r+t+1)})x$ will have $r$ leftmost anchors only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$. Similarly, if $x\in U,\not\in U_t$, the basis element $x'$ will have the property $x'(r+t)=2n+2r-t+2$ only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$. If $x\in U_t$, $x'(r+t+1)=u'(r+t+1)$ if and only if $x(r+t+1)=\tilde{u}(r+t+1)$ and $x(x(r+t+1)+1)=\tilde{u}(\tilde{u}(r+t+1)+1)$ (since $u'\not \in Y$). These are the only matches altered by the action $(1+T_{\tilde{u}(r+t+1)})$, so this implies $x=\tilde{u}$. Thus we have proved that if $R\not\in Y$, $w$ is not in the desired kernel.

\end{proof}
{\color{magenta} Nice. I felt the formalism around matchings ($M(a)$, $M(a,b)$ and all that) made this proof much more clear.}

Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ humps to the right or left, respectively. Examples are pictured in figure 2. Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.

\begin{figure}
		\def\cbasisspacing{5mm}
	$\cbr{
		\begin{gathered}
		\Matching{8}{1/8, 2/7, 3/6, 4/5}, \hspace{\cbasisspacing}
		\Matching{8}{1/8, 2/7, 3/4, 5/6}, \hspace{\cbasisspacing}
		\Matching{8}{1/8, 2/3, 4/7, 5/6}, \hspace{\cbasisspacing}
		\Matching{8}{1/2,3/8,4/7,5/6}
		\end{gathered}}$
	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right}
\end{figure}

 Define $Q_n:=(q^n+...+1)/q^{n/2}(-1)^n$ for $n\in \{0,1,...\}$. The following proposition says that, for any element in the kernel, if some basis element $y$ has coordinate $c$ in that element, and if $y$ has a rainbow sub-matching, the basis elements where you replace that sub-matching by the shifted rainbow matchings $R_{L,i}$ or $R_{R,i}$ both have coordinate $Q_ic$ in the kernel element.

\begin{proposition}
	Let $w$ be an element in the kernel intersection $\cap (1+T_k)$ in some generalized crossingless matchings representation. Let $y$ be a basis element with coordinate $c$ in $w$. Suppose $\exists a,b$ such that $y(a,b)=R$, the rainbow element. Define the basis elements $\theta_i,\phi_i$ by $\theta_i(1,a-1)=\phi(1,a-1)=y(1,a-1)$, $\theta_i(b+1,2n)=\phi(b+1,2n)=y(b+1,2n)$, $\theta_i(a,b)=R_{R,i}$, $\phi_i(a,b)=R_{L,i}$ (leave $\theta_i$ or $\phi_i$ undefined for any $i$ where $R_{R,i},R_{L,i}$ are undefined, respectively). The coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.
\end{proposition}

Proof of this proposition requires a simple algebraic fact that will be used throughout this document, so I state it as a lemma.

\begin{lemma}
	$Q_1Q_n-Q_{n-1}=Q_{n+1}$
\end{lemma}

\textit{Proof of lemma.}

$Q_1Q_n-Q_{n-1}=\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}=\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}=\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}$.
{\color{magenta} Imo the align* environment would help this.}

Now let us prove the proposition.

\begin{proof}
	Consider acting on $w$ by an element $(1+T_k)$. The coordinate of $\phi_i$ in $(1+T_k)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_k)$. Specifically, it will be $(1+q)c\alpha+(q^1/2)\sum c_\beta$ where $\alpha=1$ if $y(k)=k+1$, $\alpha=0$ otherwise, and $c_\beta$ are the coordinates of all basis elements $\beta$ where $(1+T_k)\beta\sim y$.

	Let $n:=a+b-1$ and $r$ be the number of anchors in $y(a,b)$. Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$. This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in figure 2.3. I claim that the only basis elements $\beta$ where $(1+T_{a-1+r+n/2-i})\beta\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist (we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$).

	Note that the action of any $(1+T_k)$ on a basis element $\beta$ creates exactly two lines: an arc of length two connecting $k$ and $k+1$, and either an anchor or an arc of length $\geq 2$ connecting $\beta(k)$ and $\beta(k+1)$. The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.

	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in figure 2.3. Suppose there was another basis element $\beta$ sent to $\phi_i$ by the given transposition. We note that if $\beta$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching. Thus, if $\beta$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\beta\sim \phi_i=>\beta\sim \phi$. If $\beta$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\beta\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\beta(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\beta(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor. All other matchings remain unchanged, so this implies $\beta=\phi_{i+1}$. Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\beta=\phi_{i-1}$. For boundary cases, note that for $\phi_0=\theta_0$, the only other basis element sent to this by the middle transposition is $\phi_1=\theta_1$. Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case is unhelpful to us. Lastly, note that our argument was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors. Thus the claim is proved.

	Given this claim and lemma 2.4, the proposition follows quickly through induction.

	Acting by $(1+T_{a-1+r+n/2})$ on $w$, the new coordinate of $\phi_0=y$ is $(q+1)c+q^{1/2}c_{\phi_1}$ where $c_{\phi_1}$ is the coordinate of $\phi_1$ in $w$. Since $w$ is in the kernel, we have $(q+1)c+q^{1/2}c_{\phi_1}=0=>c_{\phi_1}=Q_1c$. $\phi_1=\theta_1$ so this gives us all our base cases.

	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$. By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_i=0$ so $c_{\phi_{i+1}}=Q_1Q_i-Q_{i-1}=Q_{i+1}$ by lemma 2.4. $\theta_i$ is an identical proof, so the proposition follows.

	\begin{figure}
		\[
		\GeneralizedAction{8}{3/4,5/8,6/7}{2}{1/1,2/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{(1+q)}
		\]
		\[
		\GeneralizedAction{8}{2/3,5/8,6/7}{2}{1/1,4/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
		\]
		\[
		\GeneralizedAction{8}{3/8,4/5,6/7}{2}{1/1,2/2}{1.25}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
		\]
    \caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $W_{8}^2$ and $i=2$.{\color{magenta} I made the last of these a bit taller so that the anchors weren't close to touching the arc.}}
		\label{Action}
	\end{figure}
\end{proof}	
{\color{magenta} This proof is pretty technical, and I don't quite have the time to go through it tonight. I'll go through it more closely later.}

We are now ready to prove our first interesting result. Define $e$ as before.

\begin{proposition}
	Let $W_{2n+r}^r$ be a generalized crossingless matchings representation. Suppose $e$ does not divide $n+r+1$. Then $\cap\text{ker}(1+T_i)=\emptyset$.
\end{proposition}

\begin{proof}
	Suppose $\cap\text{ker}(1+T_i)=K\not=\emptyset$. Take $w\in K$. By Proposition 2.2, the coordinate of the rainbow vector $R$ is nonzero; suppose the coordinate is $c$. By proposition 2.3, the coordinates of the basis elements $R_{L,n+r-1}$ and $R_{L,n+r-2}$ are $Q_{n+r-1}c$ and $Q_{n+r-2}c$ respectively.

	Consider the coordinate of $R_{L,n+r-1}$ in $(1+T_1)w$. Using the same logic as in the proof of proposition 2.3, we note that if a basis element $\beta$ has no anchor at position $3$ and is not equal to $R_{L,n+r-2}$, $(1+T_1)\beta\not\sim R_{L,n+r-1}$. Thus the desired coordinate is equal to $(1+q)Q_{n+r-1}c+q^{1/2}Q_{n+r-2}c=-q^{1/2}Q_{n+r}c$ by lemma 2.4. Since $w\in K$, we must have $-q^{1/2}Q_{n+r}c=0$. We have that $c$ is nonzero, and we assume $q$ nonzero, and $Q_{n+r}$ is zero iff $q$ is a root of $q^{n+r}+...+1$, implying $e|n+r+1$. Thus we have arrived at contradiction, and $K=\emptyset$.
\end{proof}
{\color{magenta} Nice. Is the goal that basically this style of proof with yield the same result when $e \neq n + r + 1$? At any rate, I think a final text should place more emphasis on the fact that proposition 2.3 specifies a one-dimensional subspace containing the kernel;
in effect, this specifies that the sign representation appears at most once as a submodule, and gives a formula for when it does.}

\end{document}

### 2019-07-23 tex/Rough-Overview.tex
Polished the fix for e=5 fib

@@
 \]
-having characteristic polynomial $(c - \lambda)(e - \lambda) - d^2 = \lambda^2 - (c + e)\lambda +(ce - d^2)$.
-The reader can verify that this has roots $-1$ and $q$.
-The eigenspaces with eigenvalues $-1$ and $q$ are subrepresentations isomorphic to the sign and trivial representation, hence $F_{pp}$ is isomorphic to a direct sum of the trivial and sign representations: $V^2_{pp} \simeq V^2_{*p} \oplus V^2_{**}$.
+having characteristic polynomial $(\varc - \lambda)(\vare - \lambda) - \vard^2 = \lambda^2 - (\varc + \vare)\lambda +(\varc\vare - \vard^2)$.
+We may verify that, for $\lambda = -1$, this evaluates to
+\[
+  -((-1 + q + q^2) (1 + q^3 + q^4 + q^5 + 2 q^6 + q^7))\brk{5}_q = 0
+\]
+and for $\lambda = q$ this evaluates to 
+\[
+-(q^2 (-1 + q + q^2) (1 + q + q^2 + q^3 + 2 q^4 + q^5)) \brk{5}_q = 0
+\]
+hence $\rho_{T_1}$ has eigenvalues $-1$ and $q$.
+
+The eigenspaces with eigenvalues $-1$ and $q$ are subrepresentations isomorphic to the sign and trivial representation, hence $V_{pp}$ is isomorphic to a direct sum of the trivial and sign representations: $V^2_{pp} \simeq V^2_{*p} \oplus V^2_{**}$.
 

### 2019-07-23 tex/Rough-Overview.tex
Fib data, conjectures

@@
 \subsection{Fibonacci Representation}
-Now suppose that $k = \CC$ and $q = \exp\prn{2 \pi i \ell/5}$ is a primitive 5th root of unity.
+Now suppose that $e = 5$ and $k$ contains the algebraic number $(-1 - q^2 - q^3)^{3/2}$.
 Let $V^m$ be a $k$-vector space with basis given by the strings $\cbr{*,p}^{n+1}$ such that the character $*$ never appears twice in a row. 
@@
 
-\section{Explicit Relationships}
+\section{Conjecture}
+Recall that $K_{2n + r}^r := K$ is the direct sum of all copies of the sign representation in $W$.
+Hence the following characterises sign subrepresentations of $W$ completely:
+\begin{proposition}
+  $K \subset W_{2n + r}^r$ is trivial when $e \neq n + r + 1$, and $\dim \, K = 1$ when $e = n + r + 1$.\qed
+\end{proposition} 
+\begin{proposition}
+  Suppose $e < n + r + 1$, and suppose $n'$ is such that $e = n' + r + 1$.
+  Note that $h := (1 + T_1)(1 + T_3)\dots(1 + T_{n - n'})$ maps $W_{2n + r}^r$ onto $W_{2n' + r}^r$.
+  Then, the preimage $h^{-1}(K_{2n + r}^r)$ is a subrepresentation of $W_{2n + r}^r$, and the series
+  \[
+    0 \subset h^{-1}(K_{2n + r}^r) \subset W_{2n + r}^r
+  \]
+  is a composition series of $W_{2n + r}^r$.\qed
+\end{proposition}
+\begin{proposition}
+  Denote the composition factor $W_{2n + r}^r / h^{-1}(K_{2n + r}^r)$ by $U_{2n + r}^r$.
+  Then, there exist some naturals $m,s$ satisfying $2m + s = 2n + r$ and $m + s > n + r$ such that the following is an isomorphism of $\SH$-modules \[h^{-1}\prn{K_{2n + r}^r} \simeq U_{2m + s}^s\].
+  \qed
+\end{proposition}
+\begin{proposition}
+  For the same $m,s$ as above, we have the following composition series of specht modules:
+  \[
+    0 \longrightarrow D^{(m+s,m)'} \longrightarrow S^{(n+r,n)'} \longrightarrow D^{(n+r,n)'} \longrightarrow 0.
+  \]
+\end{proposition}
+\begin{proposition}
+  $W_{2n + r}^r \simeq S^{(n+r,n)'}$ and $U_{2m +s}^s \simeq D^{(m+s,m)'}$.
+\end{proposition}
 
 \newpage
+
 \appendix

### 2019-07-23 code/fibonacci.py

@@ -1,0 +1,50 @@
+def generate_basis_star(n,memo={}):
+    if n == 2:
+        return ["*p*"]
+    elif n == 3:
+        return ["*pp*"]
+    
+    basis = ["*"+"p"*(n-1)+"*"]
+    for i in range(1,n-2):
+        if n-i-1 not in memo.keys():
+            memo[n-i-1] = generate_basis_star(n-i-1,memo)
+        for elt in memo[n-i-1]:
+            basis += ["*"+"p"*i+elt]
+    return basis
+
+def action(s,i,t):
+    if s[:i+1] != t[:i+1] or s[i+2:] != t[i+2:]:
+        return "0"
+
+    if s[i:i+3] in ["*pp","pp*"]:
+        return "a"
+
+    if s[i:i+3] == "*p*":
+        return "b"
+
+    if s[i+1] != t[i+1]:
+        return "d"
+
+    if s[i+1] == "*":
+        return "c"
+
+    return "e"
+
+def generate_matrices_star(n):
+    """
+    Generate the matrices for the fibonacci representation on n indices.
+    """
+    basis = generate_basis_star(n)
+    out = [[[0 for i in range(len(basis))] for j in range(len(basis))] for k in range(n-1)]
+    for i in range(n-1):
+        for x,b in enumerate(basis):
+            for y,c in enumerate(basis):
+                out[i][x][y] = action(b,i,c)
+    return out
+
+
+for n in range(2,16):
+    f = open("Fib m={}".format(n),"w")
+    f.write("\n/\n".join(["\n".join([",".join(row) for row in arr]) for arr in generate_matrices_star(n)]))
+    f.close()
+    print("m={} completed.".format(n))

### 2019-07-25 tex/kernel.tex
added stuff to kernel

@@
 
+\newpage
+\section{Defining the kernel for $e=n+r+1$}
+
+In this section we will fully characterize $\cap\text{ker}(1+T_i)$ when $e=n+r+1$.
+Note that we still have not proved the kernel is trivial when $e$ divides but is not equal to $n+r+1$.
+That proof requires results from this section, and will come next section.
+
+The following proposition states the forward direction of our characterization: if the kernel is nontrivial, it must have the following properties.
+
+\vspace{5mm}
+\begin{proposition}
+
+	Let $W_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$.
+Let $w\in\cap\text{ker}(1+T_i)$.
+WLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition 2.2).
+	\\
+
+	\begin{center}	
+		a) For any basis element $\beta\in W_{2n+r}^r$, the coordinate of $\beta$ in $w$ must be some rational function of $q$, say $x_\beta(q)$.
+
+	\end{center}
+	\vspace{5mm}
+
+	Generally, for any matching $\alpha$, define $x_\alpha$ to be the rational function corresponding to the coordinate of that basis element in its respective kernel element.
+We will need to prove this is well defined.
+
+	Suppose $\beta(1)=a$. Assume 1 is not an anchor. Then $\beta$ has two sub-matchings $\alpha_1=\beta(2,a-1)$ and $\alpha_2=\beta(a+1,2n+r)$. Then we have the following:
+	\\
+
+	\begin{center}
+
+		b) $x_\beta(q)=x_1(q)x_2(q)\frac{Q_{n+r-1}...Q_{n+r-(a/2)}}{Q_1...Q_{a/2-1}}$
+
+	\end{center}
+
+	\vspace{5mm}
+
+	If 1 is an anchor, we have a sub-matching $\beta(2,2n+r)$ with coordinate $x_3(q)$ in its respective kernel element, and I claim $x_\beta(q)=x_3(q)$.
+
+\end{proposition}
+
+\vspace{5mm}
+Before proving this proposition, it will be useful to clarify exactly what it states.
+
+The first statement of this proposition says that, given an element of the kernel $w$, we can write the coordinate of any basis element $\beta$ in $w$ as a rational function of $q$ as long as $Q_1...Q_{n+r-1}\not=0$.
+
+The second statement is meant to inductively define the coordinate of an arbitrary basis element.
+The first statement lets this induction make sense.
+Essentially, the second statement says the following: we can find the coordinate of any basis element by dividing it into two sub-matchings and scaling by a specific constant which depends on the lengths of the sub-matchings.
+
+An illustration of this proposition is shown in figure 4.
+
+\begin{proof}
+
+	As with many proofs in this section, this will be a proof by induction.
+
+	First, let us specify our base case: $W_{2}^0$ only has the rainbow element, which has coordinate 1. We also define the coordinate of an empty matching (i.e. no nodes) to be 1.
+
+	\begin{figure}
+		\def\cbasisspacing{5mm}
+
+		$\cbr{
+			\begin{gathered}
+			\GeneralizedMatching{11}{1/6, 2/3,4/5,7/10,8/9}{1}{11/1}{11/8}, \hspace{\cbasisspacing}
+			\Matching{4}{1/2, 3/4}, 
+			\hspace{\cbasisspacing}
+			\GeneralizedMatching{5}{1/4, 2/3}{1}{5/1}{3/4}, \hspace{\cbasisspacing}
+			\end{gathered}}$ 
+		\caption{Suppose the second and third elements have coefficients $x_2(q)$ and $x_3(q)$}
+	\end{figure}
+
+\end{proof}
+
 \end{document}

### 2019-07-26 tex/Rough-Overview.tex
Generalized code, got arguments in outline (minus Miles) to current

@@
 
-\title{Rough Cut of Proven Work on $\SH$.}
-\author{Miles Johnson \& Natalie Stewart}
+\title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules  of Hecke Algebras}
+\author[Miles Johnson \& Natalie Stewart]{Miles Johnson \& Natalie Stewart\\
+  Mentor Oron Propp\\
+Project Suggested by Roman Bezrukavnikov\\ \; \\
+July 31, 2019
+}
+
+\begin{titlepage}
   \maketitle
+  \begin{abstract}
+  Abstract goes here
+  \end{abstract}
+\end{titlepage}
 
@@
 identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
-Identify each of these with a subset $\brk \lambda \subset \NN^2$ as defined in Kleshev, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.
+Identify each of these with a subset $\brk \lambda \subset \NN^2$ as defined in Kleshchev, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.
 
@@
 \]
-Then, adopting Kleshev's terminology, $j$ is normal in $\lambda$ if $\beta(i,j) \not\equiv 0 \pmod e$ for all $i < j$, and $j$ is good if it is the largest normal number (these are stronger conditions than generally necessary).
+Then, adopting Kleshchev's terminology, $j$ is normal in $\lambda$ if $\beta(i,j) \not\equiv 0 \pmod e$ for all $i < j$, and $j$ is good if it is the largest normal number (these are stronger conditions than generally necessary).
 
@@
 
-\begin{figure}
+\begin{figure}[b]
   \[
@@
 \subsection{Fibonacci Representation}
-Now suppose that $e = 5$ and $k$ contains the algebraic number $(-1 - q^2 - q^3)^{3/2}$.
-Let $V^m$ be a $k$-vector space with basis given by the strings $\cbr{*,p}^{n+1}$ such that the character $*$ never appears twice in a row. 
-We will surpress the superscript whenever it is clear from context.
-
-We wish to endow this with a $\SH$-action which acts on a basis vector only dependent on characters $i,i+1,i+2$, sending each basis vector to a combination of the other basis vectors having the same characters $1,\dots,i,i+2,\dots,n+1$ as follows:
 \def\vara{\alpha}
@@
 \def\vare{\varepsilon}
+\def\vs{\texttt{*}}
+\def\vp{\texttt{0}}
+Now suppose that $e = 5$ and $k$ contains the algebraic number $(-1 - q^2 - q^3)^{3/2}$.
+Let $V^m$ be a $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{n+1}$ such that the character $\vs$ never appears twice in a row. 
+We will suppress the superscript whenever it is clear from context.
+
+We wish to endow this with a $\SH$-action which acts on a basis vector only dependent on characters $i,i+1,i+2$, sending each basis vector to a combination of the other basis vectors having the same characters $1,\dots,i,i+2,\dots,n+1$ as follows:
 
@@
   \begin{split}
-  T_1 \, (*pp) &:= \vara(*pp)\\
-  T_1 \, (pp*) &:= \vara(pp*)\\
-  T_1 \, (*p*) &:= \varb(*p*)\\
-  T_1 \, (p*p) &:= \varc(p*p) + \vard(ppp)\\
-  T_1 \, (ppp) &:= \vard(p*p) + \vare(ppp)
+    T_1 \, \prn{\vs\vp\vp} &:= \vara\prn{\vs\vp\vp}\\
+    T_1 \, \prn{\vp\vp\vs} &:= \vara\prn{\vp\vp\vs}\\
+    T_1 \, \prn{\vs\vp\vs} &:= \varb\prn{\vs\vp\vs}\\
+    T_1 \, \prn{\vp\vs\vp} &:= \varc\prn{\vp\vs\vp} + \vard\prn{\vp\vp\vp}\\
+    T_1 \, \prn{\vp\vp\vp} &:= \vard\prn{\vp\vs\vp} + \vare\prn{\vp\vp\vp}
 \end{split} \label{Fib Action} 
@@
 This contains 4 subrepresentations based on the first and last character of the string, which are not modified by $\SH$.
-Label the subrepresentation of strings $(*\dots*)$ by $V_{**}$, and similar for the other 3.
-It is easy to see that $V_{*p} \simeq V_{p*}$, so that
+Label the subrepresentation spanned by strings $(\vs\dots\vs)$ by $V_{\vs\vs}$, and similar for the other 3.
+It is easy to see that $V_{\vs\vp} \simeq V_{\vp\vs}$, so that
 \[
-  V \simeq 2V_{*p} \oplus V_{**} \oplus V_{pp}.
+  V \simeq 2V_{\vs\vp} \oplus V_{\vs\vs} \oplus V_{\vp\vp}.
 \]
-We will show that $V_{pp} \simeq V_{*p} \oplus V_{**}$, and give the following isomorphisms with irreducible quotients of specht modules depending on the parity of the number of indices in $\SH$:
+We will show that $V_{\vp\vp} \simeq V_{\vs\vp} \oplus V_{\vs\vs}$, and give the following isomorphisms with irreducible quotients of specht modules depending on the parity of the number of indices in $\SH$:
 \begin{equation}
   \begin{split}    
-    V^{2n}_{**} &\simeq D^{(n,n)'}\\ 
-    V^{2n-1}_{**} &\simeq D^{(n+1,n-2)'}\\
-    V^{2n}_{*p} &\simeq D^{(n+1,n-1)'}\\
-    V^{2n-1}_{*p} &\simeq D^{(n,n-1)'}.
+    V^{2n}_{\vs\vs} &\simeq D^{(n,n)'}\\ 
+    V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)'}\\
+    V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)'}\\
+    V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)'}.
   \end{split} \label{Fib Isos}
@@
 \newpage
-\section{Crossingless Matchings and Specht Modules}
-Our goal is to prove that $W_{2n + r}^r \simeq S^{(n+r,n)'}$ when $e > n + r + 1$.
+\section{Preliminaries on Specht Modules}
 \begin{proposition}
@@
 \begin{lemma}
+  Suppose $n,r > 0$.
+  Then, we may characterize the socle of $\Res \, D^\lambda$ as follows:
+  \[
+    \soc\prn{\Res \, D^{(n+r,n)'}} \simeq \begin{cases}
+      D^{(n + r - 1,n)'} & e \mid r+2\\
+      D^{(n + r,n-1)'} & e \nmid r+2, \; e \mid r\\
+      D^{(n+r-1,n)'} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
+    \end{cases}
+  \]
+\end{lemma}
+\begin{proof}
+  This amounts to computations of the hook lengths $\beta(1,2)$ and $\gamma(1,2)$:
+  \begin{align*}
+    \beta_\lambda(1,2) &= r + 2\\
+    \gamma_\lambda(1,2) &= r
+  \end{align*}
+  Since $2$ is the largest removable number, $D^{(n+r,n-1)'} \subset D^{(n+r,n)'}$ iff $e \nmid r + 2$.
+  Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)'} \subset D^{(n+r,n)'}$ iff 1 is good iff $e \nmid r$
+\end{proof}
+
+\begin{lemma}\label{S irreducibility}
+  \begin{enumerate}[label={(\roman*)}]
+    Assume $e > 2$ and $n > 0$.
+    \item Suppose $e > n$.
+      Then, $S^{(n+r,n)'}$ is irreducible iff $e \nmid l$ for all $r + 2 \leq l \leq n + r + 1$.
+    \item Suppose $e \leq n$.
+      Then, $S^{(n+r,n)'}$ is irreducible iff $e | r + 1$ and $\nu_{e,p}(h_{ab}^\lambda)$ acquires exactly two values over rows $a \leq n$.
+  \end{enumerate}  
+\end{lemma}
+\begin{proof}
+  \textbf{(i)}
+  Note that $\nu_p(l) \neq -1$ for all $l$ and only hook lengths in the first column may vanish mod $e$;
+  hence we may equivalently prove that $e$ divides no hook lengths in the first $n$ rows of the first column.
+  These hook lengths are precisely $r + 2,\dots,n+r+1$.
+
+  \textbf{(ii)}
+  Note that we have $\nu_{e,p}\prn{h^\lambda_{n-e+1,2}} \neq -1$.
+  Suppose that $e \nmid r + 1$.
+  Then, \[\nu_{e,p}\prn{h^\lambda_{n-e+1,1}} = \nu_{e,p}\prn{h^\lambda_{n-e,2} + r + 1} = -1,\]
+  giving $S^{(n+r,n)'}$ reducible.
+
+  Note that $\nu$ acquires at least two values since $e$ is a hook length.
+  Now, suppose that \[0 \leq \nu_{e,p}(h^{\lambda}_{ab}) < \nu_{e,p}\prn{h^{\lambda}_{a'b'}}\] and $S^{(n+r,n)'}$ is irreducible.
+  If $a=a'$ then we have reducibility, so assume $a \neq a'$.
+  Further, if $b = b'$, then we may replace $b$ with the other column;
+  hence we may assume WLOG that $b \neq b'$ as well.
+
+  Note that $p$-adic valuation is monotonic, so $h^\lambda_{ab} < h^\lambda_{a'b'}$.
+  If $b < b'$, then $\nu_p(h_{ab}) = \nu_p(h_{ab'}) < \nu(h_{a'b'})$ while $h_{ab'} > h_{a'b'}$, a contradiction.
+  If $b > b'$, then $\nu_p(h_{ab}) = \nu_p(h_{ab'})$ and $h_{ab} < h_{ab'}$, so there is some $c < b$ with $\nu_{e,b}(h_{ab}) = \nu_{e,p}(h_{ac})$; we may replace $b$ with $c$, and repeat until $b = b'$ to reach contradiction.
+
+  Finally, assume $e | r + 1$ and $\nu_{e,p}$ acquires two values over the top $n$ rows.
+  Since $e | r + 1$, $e \mid h_{a1}^\lambda$ iff $e \mid h_{a2}$;
+  since $\nu_{e,p}$ acquires only two values, this proves that $\nu_{e,p}(h_{a1}) = \nu_{e,p}(h_{a2})$ across these rows, giving the lemma.
+\end{proof}
+
+This is complicated and annoying, and the second amounts to a condition on $p$.
+We will illustrate that irreducibility interpolates between $p = 2$ and $p$ large:
+\begin{corollary}
+  Assume $2 < e \leq n$.
+  \begin{enumerate}[label={(\roman*)}]
+    \item Suppose $p > n + r + 1$. Then, $S^{(n + r,n)'}$ is irreducible iff $e | r + 1$.
+    \item Suppose $p = 2$. Then, $S^{(n+r,n)'}$ is not irreducible.
+  \end{enumerate}
+\end{corollary}
+\begin{proof}
+  (i) is clear.
+  (ii) is given by noting that $e + r + 1 \geq 2e$;
+  then, $h_{n-e+1,1} - h_{n-e+1,2} \geq 1$, giving reducibility.
+\end{proof}
+
+\begin{proposition}\label{Combinatorics}
+  Suppose that $e,n,r$ satisfy criterion (i) of Proposition \ref{S irreducibility}.
+  Let $\lambda$ be a partition of $2n + r$.
+  \begin{enumerate}[label={(\roman*)}]
+    \item Suppose $r > 0$.
+      If $D^\lambda$ has the composition series 
+      \begin{equation}\label{D Composition Series}
+        0 \subset D^{(n+r-1,n)'} \subset \Res \, D^{\lambda}
+      \end{equation}
+      with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)'} \simeq D^{(n+r,n)'}$, then $\lambda = (n+r,n)'$.
+    \item Suppose $r = 0$ and $D^{(n,n-1)'} \simeq \Res \, D^\lambda$.
+      Then $\lambda = (n,n)'$.
+  \end{enumerate}
+\end{proposition}
+\begin{proof}
+  \textbf{(i)}
+  Let $\varpi := (n+r-1,n,1)$, let $\varsigma := (n+r-1,n+1)'$, and let $\mu := (n + r,n)'$.
+  Since $D^{(n+r-1,n)'} \subset \Res \, D^\lambda$, we have $(n + r - 1,n)' \longrightarrow \lambda$, implying $\lambda = \varpi,\varsigma,\mu$.
+
+  We will show that $\varpi, \varsigma$ do not have socle compatible with \eqref{D Composition Series};
+  then, we will have $\lambda = \mu$.
+
+  First, we focus on $\varpi$;
+  Suppose $r > 1$ and $e \mid n + 1$;
+  then, $\beta_{\varpi}(2,3) = n + 1 \equiv 0 \pmod e$, so $3$ is not normal and $D^{(n+r-1,n)'}$ is not in the socle of $D^\varpi$, giving $\lambda \neq \varpi$.
+
+  Now suppose $r > 1$ and $e \nmid n + 1$.
+  Then $S^{(n+r-2,n,1)'} \simeq D^{(n+r-2,n,1)'}$.
+  Then, we have $D^{(n + r - 2,n,1)'} \simeq S^{(n + r - 2,n,1} \subset \Res \, D^{\varpi}$ since 1 is normal;
+  this is not a composition factor in \eqref{D Composition Series}, so $\lambda \neq \varpi$.
+
+  Similarly, assume $r = 1$;
+  then, by the same logic, $D^{(n+r-1,n)'} \not\subset \Res \, D^\varpi$ or $D^{(n,n-1,1)} \subset \Res \, D^\varpi$, also implying $\lambda \neq \varpi$.
+  \iffalse % keeping just in case
+  \begin{align*}
+    \beta_{\varpi}(1,2)     &= r + 1 \\
+    \beta_{\varpi}(1,3)     &= n + r + 1 \\
+    \beta_{\varpi}(2,3)     &= n + 1\\
+    \gamma_{\varpi}(1,2)    &= r\\
+    \gamma_{\varpi}(1,3)    &= n + r\\
+    \gamma_{\varpi}(2,3)    &= n\\
+  \end{align*}
+  \fi
+
+  \vspace{5pt}
+  Now, focus on $\varsigma$;
+  if $r < 2$, then $\varsigma$ is not a partition.
+  If $r = 2$, then $\Res \, D^\varsigma \simeq D^{(n+1,n)'}$ is irreducible, contradicting \eqref{D Composition Series}. 
+  If $r > 2$, then $D^{(n + r - 2,n+1)'}$ is irreducible, so $D^{(n+r-2,n+1)'} \simeq S^{(n+r-2,n+1)'} \subset D^\varsigma$, contradicting \eqref{D Composition Series}.
+
+  \textbf{(ii)}
+  This result is fundamentally similar to the previous result;
+  since the socle of $D^\lambda$ is irreducible, we require that 1 is the only normal number, which pins $\lambda$.
+\end{proof}
+
+\iffalse
+\begin{proposition}
+  Suppose that $n > 0$ and $e \nmid n + r$.
+  \begin{enumerate}[label={(\roman*)}]
+    \item Suppose $r > 0$, $n > 1$, and either $e \nmid n + 1$ or $e \nmid n + r + 1, n + r - 1$.
+      If $D^\lambda$ has the composition series 
+      \begin{equation}\label{D Composition Series}
+        0 \subset D^{(n+r-1,n)'} \subset \Res \, D^{\lambda}
+      \end{equation}
+      with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)'} \simeq D^{(n+r,n)'}$, then $\lambda = (n+r,n)'$.
+    \item Suppose $n = 1$ and $e \nmid r+2$, and suppose that we have composition series \eqref{D Composition Series}.
+      Then $\lambda=(r+1,r+2)'$.
+    \item Suppose $r = 0$, either $e \nmid n+2$ or $e > 3$, and $D^{(n,n-1)'} \simeq \Res \, D^\lambda$.
+      Then $\lambda = (n,n)'$.
+  \end{enumerate}
+  The above conditions are unilaterally met whenever $e > n + r + 1$ and $(n,r) \neq (1,0)$.
+\end{proposition}
+\begin{proof}
+  \textbf{(i)}
+  Let $\lambda_1 := (n+r-1,n,1)$, let $\lambda_2 := (n+r-1,n+1)'$, and let $\lambda_3 := (n + r,n)'$.
+  Since $D^{(n+r-1,n)'} \subset \Res \, D^\lambda$, we have $(n + r - 1,n)' \longrightarrow \lambda$, implying $\lambda = \lambda_i$ for some $i = 1,2,3$.
+  We will show that $\lambda_1,\lambda_2$ each have good numbers other than 1, leading to elements of their socle that are not factors in \eqref{D Composition Series};
+  then, we will have $\lambda = \lambda_3$.
+
+  We may straightforwardly compute this.
+  First assume $n \geq 2$, so that
+  \begin{align*}
+    \beta_{\lambda_1}(1,2) &= n + 1\\
+    \beta_{\lambda_1}(1,3) &= n + r + 1\\
+    \beta_{\lambda_1}(2,3) &= n + r - 1\\
+    \beta_{\lambda_2}(1,2) &= n + r
+  \end{align*}
+
+  \textbf{(ii)}
+  The choices are the same as above, but now $\lambda_1$ only has two removable nodes, so that
+  \begin{align*}
+    \beta_{\lambda_1}(1,3) &= r + 2\\
+    \beta_{\lambda_2}(1,2) &= r + 1
+  \end{align*}
+
+  \textbf{(iii)}
+  Let $\lambda_1 := (n,n-1,1)'$, let $\lambda_2 := (n+1,n-1)'$, and let $\lambda_3 := (n,n)'$;
+  as before we know that $\lambda = \lambda_i$ for $i = 1,2,3$, so we will eliminate $\lambda_1,\lambda_2$.
+  First, we will show that $\lambda_1$ has a good number other than 1:
+  \begin{align*}
+    \beta_{\lambda_1}(1,2) &= n\\
+    \beta_{\lambda_1}(1,3) &= n + 2\\
+    \beta_{\lambda_1}(2,3) &= n\\
+  \end{align*}
+  Hence we may rule out $\lambda_1$ when $e | n$.
+
+  Suppose $D^{\lambda_2}$ satisfies the isomorphism;
+  then the number 2 is normal.
+  We may make the following computations:
+  \begin{align*}
+    \beta_{\lambda_2}(1,2) &= n + 2\\
+    \gamma_{\lambda_2}(1,2) &= 3.
+  \end{align*}
+  When $e | n + 2$, this brings contradiction;
+  when $e \nmid n + 2$ and $e > 3$, 2 is a good number (recalling that $e > 2$), giving non-semisimple restriction, a contradiction.
+  Hence $\lambda = \lambda_3$ and the proposition is proven.
+\end{proof}
+\fi
+
+\section{Crossingless Matchings and Specht Modules}
+\subsection{Preliminaries on Crossingless Matchings}
+\begin{lemma}
+  \label{Cyclic}
   Every basis vector in $W_{2n + r}^r$ is cyclic.
@@
   We may iterate this process as illustrated in Figure \ref{Submatrix}, eventually ending at a row with two nonzero entries, either an arc $(1,2)$ or an arc $(2,3)$, and all anchors otherwise left-aligned and arcs of maximum length.
-  These rows together form an $(n + r) \times \abs{W_{2n + r}^r}$ sumbatrix of $A$ which has a nonzero column in the row corresponding to $j$, and has (by removing zero columns) the same column space as the following square matrix:
+  These rows together form an $(n + r) \times \abs{W_{2n + r}^r}$ submatrix of $A$ which has a nonzero column in the row corresponding to $j$, and has (by removing zero columns) the same column space as the following square matrix:
   \newcommand*\bigzero{\makebox(0,15){\text{\Huge0}}}
   \newcommand*\bigzerotwo{\makebox(-20,15){\text{\Huge0}}}
-  \[
+  \begin{equation}\label{Bnr}
     B_{n + r} := \begin{bmatrix}
@@
     \end{bmatrix}.
-  \]
+  \end{equation}
   We will show that this matrix is invertible;
@@
   We may prove invertibility of this matrix by proving that $\det B_{n + r} = \brk{n + r + 1}_q$ inductively on $n+r$.
-  This is satisfied for our base case $n + r = 1$, so supose that it is true for each $m < n + r$.
+  This is satisfied for our base case $n + r = 1$, so suppose that it is true for each $m < n + r$.
   Then,
@@
 
+\subsection{Correspondence}
 \begin{proposition}
@@
 
-\iffalse
-The next piece in our puzzle is to characterize the restrictions of $W$ to $\SH' := \SH_{k,q}(S_{2n + r - 1}) \subset \SH$.
-Recall that, when $r,n>0$ and $\SH$ is semisimple,  $\Res S^{(n+r,n)'} \simeq S^{(n+r-1,n)'} \oplus S^{(n+r,n-1)'}$.
-Further, note that $S^{(n+r,n)'}$ is the unique irreducible having this restriction.
-
-Next, note that we have already proven the correspondence for $W_{2n}^0$;
-for $W_{0 + r}^{r}$, this is the sign representation, which is given correctly by $S^{(r)}$.
-Hence, pending information on restrictions, we may prove this via induction on $2n + r$.
-\fi
-
 \begin{corollary}
@@
 \begin{theorem}
-  Suppose $e > n + r + 1$, $n > 0$.
+  Suppose $e > n + r + 1$.
   Then, $W_{2n + r}^r \simeq S^{(n+r,n)'}$.
@@
 \begin{proof}
+  The case $n = 0$ is already proven, so suppose $n > 0$.
+
   By irreducibility, we know that $W_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
-  We will proceed in two steps;
-  first we prove that $\lambda = (n+r,n)'$, then we prove that $S^{(n+r,n)'}$ is irreducible.
-
-  This will be done inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $W_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e.
+  We will prove this inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $W_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e.
 $e > m + s + 1$).
 
-  \def\thmsep{7pt}
-  \vspace{\thmsep}
-  \textit{Step 1.}
   By the inductive hypothesis and irreducibility, we have a composition series given by 
@@
    \end{equation}
-  In particular, by the Jordan-H\"older theorem, if we have some module $D^\mu \subset \Res \, D^\lambda$, then $\mu = (n+r-1,n)'$ or $\mu = (n+r,n-1)'$.
-
-  By Kleschev, we know that $\soc(D^\lambda) = \bigoplus_{\mu} D^\mu$, where $\mu$ ranges over $\lambda(i)$ for every good number $i$ of $\lambda$.
-  Immediately this narrows down $\lambda$ to three options;
-  the only $\lambda$ with some $\lambda(i)$ giving $(n + r - 1,n)'$ are $\lambda_1 ;= (n+r-1,n,1)'$, $\lambda_2 = (n+r-1,n+1)'$, and $\lambda_3 = (n+r,n)'$.
-
-  Note numbers $\beta_l(i,j)$ correspond to hook-lengths, and each $\lambda_;$ has maximum hook length $n + r + 1$;
-  hence $\beta_l(i,j) \not\equiv 0 \pmod e$ for all $i,j,l$, and 3 is a good number in $\lambda_1$ and 2 in $\lambda_2$.
-  This implies $D^{(n+r-2,n,1)'} \subset D^{\lambda_1}$ and $D^{(n+r-2,n+1)'} \subset D^{\lambda_2}$, giving that $\lambda = \lambda_3$ as desired.
-
-  \vspace{\thmsep}
-  \textit{Step 2.}
-  Let the hook length of node $(a,b)$ in $\brk \lambda$ be written $h_{ab}^\lambda$.
-  Let $\nu_p(h_{ab}^\lambda)$ be the $p$-adic valuation of $h_{ab}^\lambda$, and let $\nu_{e,p}(h_{ab}^\lambda)$ be $\nu_p(h^{J})$.
-  Mathas Theorem 5.42 says, for $\lambda$ $e$-restricted, $S^\lambda$ is irreducible if $\nu_{e,p}(h_{ab}^\lambda) = \nu_{e,p}(h_{ac}^\lambda)$ for a suitable prime $p$.
-  In particular, since $h_{ab}^\lambda < e$ for all $a,b$, we have $\nu_{e,p}(h_{ab}^\lambda) = -1$ for all $a,b$, and $S^\lambda$ is irreducible.
+  Hence the theorem is given by Proposition \ref{Combinatorics}.
 \end{proof}
@@
 \iffalse
-\begin{proposition}
-  Suppose $e > n + r + 1$, and let $\lambda$ be a partition of $2n + r$.
-  \begin{enumerate}[label={(\roman*)}]
-    \item Suppose $n,r > 0$.
-      If $\Res \, D^\lambda$ admits a filtration $0 \subset S^{(n+r-1,n)'} \subset \Res \, S^\lambda$ with $\Res \, S^\lambda / S^{(n + r - 1,n)'} \simeq S^{(n + r,n-1)'}$ then $\lambda = (n+r,n)'$.
-    \item Suppose $r = 0$.
-      If $\Res \, S^\lambda \simeq S^{(n,n-1)'}$, then $\lambda = (n,n)'$.
-  \end{enumerate}
-\end{proposition}
+We may reuse the above structure of proof as above;
+suppose $W_{2n + r}^r$ and $S^{(n+r,n)'}$ are irreducible, and $\lambda = (n+r,n)'$ is the unique diagram having composition series \eqref{Composition Series}.
+Then, $W_{2n + r}^r \simeq S^{(n+r,n)'}$.
+
+We have covered all irreducible cases for $r = 0$ and $n = 0$ above.
+For example, another case where we may show all irreducible cases is $n = 1$, which we will do now.
+\begin{lemma}\label{n=1 irreducibility}
+    Set $n = 1$. 
+    Then $W_{2 + r}^r$ is irreducible iff $e \nmid r + 2$.
+\end{lemma}
 \begin{proof}
-  \textbf{(i)}
-  Recall that the characteristic-free classical branching theorem gives that every specht module $S^{\lambda}$ admits a filtration 
-  \begin{equation}
-    0 = M_0 \subset \dots \subset M_l = S^{\lambda} \label{filtration}
-  \end{equation}  
-    with $M_i/M_{i-1} \simeq S^{\lambda(i)}$.
-  Hence $\lambda = (n + r, n)'$ satisfies the above formula.
+  A basis element $w_i \in W$ is determined entirely by the position of the arc, of which there are $r + 1$ options.
+  Hence $\dim W = r + 1$.
 
-  Note that, when $e > n + r + 1$, this filtration gives a composition series.
-  Hence the sequence \eqref{filtration} is at most length-2.
+  Further, $\dim\prn{\ima (1 + T_i)} = 1$ for all $i$;
+  by lemma \ref{Cyclic} $W$ is irreducible iff $K := \bigcap_{i = 1}^{r+1} \ker (1 + T_i) = \ker \bigoplus (1 + T_i)$ is trivial.
+  By \ref{Trivial}, this is true iff $e \nmid r + 2$.
+\end{proof}
 
-  Suppose it is length-1.
-  Then $\lambda$ is rectangle-shaped;
-  to have rows removed to the above we then need that that it be $\lambda = \prn{\frac{2n + r}{2}, \frac{2n + r}{2}}'$, so that $\Res S^{\lambda} \simeq S^{\prn{\frac{2n + r}{2}, \frac{2n + r}{2} - 1}'}$.
-  However, since $e > n + r + 1 \geq n + \frac{r}{2} + 1$, $\Res \, S^{\lambda}$ is irreducible, contradicting the existence of a length-2 composition series in the hypothesis.
-
-  Now suppose that \eqref{filtration} is length 2, so that it is also a composition series.
-  Then, by the Jordan-H\"older theorem, there is a rearranement of the composition factors of \ref{filtration} to give $S^{(n + r - 1,n)'}$ and $S^{(n + r, n - 1)'}$.
-  This implies that both $(n + r - 1,n)'$ and $(n + r,n-1)'$ can be acquired by removing rows of $\lambda$, giving that $\lambda = (n+r,n)'$.
-
-  \vspace{7pt}
-  \textbf{(ii)}
-  Note that, since $e > n + 1$, $\Res S^\lambda$ is irreducible.
-  Hence the sequence \eqref{filtration} is a composition series of length 1, and $\lambda(1) = (n,n-1)'$.
-  The first implies that $\lambda$ is rectangular, and the second implies that $\lambda = (n,n)'$.
+\begin{theorem}
+  Set $n = 1$ and suppose $e \nmid r + 2$.
+  Then $W_{2 + r}^r \simeq S^{(1+r,1)'}$.
+\end{theorem}
+\begin{proof}
+  Using lemma \ref{n=1 irreducibility} and \ref{S irreducibility} it is sufficient to prove that, for $D^\lambda$ having composition series \eqref{Composition Series}, we have $\lambda = (1+r,1)'$.
+  Similar to before, we consider the options $\lambda_1 := (r,1,1)'$, $\lambda_2 := (r,2)'$, and $\lambda_3 = (1+r,1);$.
+  We may straightforwardly check that $\lambda_1$ and $\lambda_2$ have socle containing partitions other than the composition factors in \eqref{Composition Series} by showing that each have a good number 2 as follows:
+  \begin{align*}
+    \beta_{\lambda_1}(1,2) &= 3 - 1 + r = r+2\\
+    \beta_{\lambda_2}(1,2) &= 2 - 1 + r + 1 = r+2.
+  \end{align*}
+  These are each nonvanishing mod $e$, so they are good and $\lambda = \lambda_3$, giving the theorem.
 \end{proof}
@@
 
-\section{The Fibonacci Representation and Specht Modules}
+\section{The Fibonacci Representation and Quotients of Specht Modules}
 We can start our study of $V$ by studying low-dimensional cases.
-First, note that $V_{*p}^2$ is the sign representation $D^{(2)}$ and $V_{**}^2$ is the trivial representation $D^{(1)^2}$.
+First, note that $V_{\vs\vp}^2$ is the sign representation $D^{(2)}$ and $V_{\vs\vp}^2$ is the trivial representation $D^{(1)^2}$.
 
-$V_{pp}^2$ is a 2-dimensional representation of a semisimple commutative algebra, and hence decomposes into a direct sum of two subrepresentations.
-In particular, we can use the basis $\cbr{(p*p),(ppp)}$ and explicitly write the matrix
+$V_{\vp\vp}^2$ is a 2-dimensional representation of a semisimple commutative algebra, and hence decomposes into a direct sum of two subrepresentations.
+In particular, we can use the basis $\cbr{(\vp\vs\vp),(\vp\vp\vp)}$ and explicitly write the matrix
 \[
@@
 
-The eigenspaces with eigenvalues $-1$ and $q$ are subrepresentations isomorphic to the sign and trivial representation, hence $V_{pp}$ is isomorphic to a direct sum of the trivial and sign representations: $V^2_{pp} \simeq V^2_{*p} \oplus V^2_{**}$.
+The eigenspaces with eigenvalues $-1$ and $q$ are subrepresentations isomorphic to the sign and trivial representation, hence $V_{\vp\vp}$ is isomorphic to a direct sum of the trivial and sign representations: $V^2_{\vp\vp} \simeq V^2_{\vs\vp} \oplus V^2_{\vs\vs}$.
 
-Now let's prove that $V^3_{**}$ is irreducible;
-this has basis $\cbr{*p*p}, \cbr{*ppp}$, and the following matrices:
+Now let's prove that $V^3_{\vs\vs}$ is irreducible;
+this has basis $\cbr{\vs\vp\vs\vp}, \cbr{\vs\vp\vp\vp}$, and the following matrices:
 \[
@@
 since $\varb \neq \vara$, the first has eigenspaces given by the spans of basis elements, and since $\vard \neq 0$, these are not eigenspaces of the second.
-Hence $V^3_{**}$ is irreducible.
+Hence $V^3_{\vs\vs}$ is irreducible.
 Now we may move on to the general case.
 \begin{proposition}
-  The representation $V_{*p} := V^m_{*p}$ is irreducible.
+  The representation $V_{\vs\vp} := V^m_{\vs\vp}$ is irreducible.
 \end{proposition}
@@
   We will prove this inductively in $m$.
-  We've already proven it for $V^2_{*p}$ and $V^3_{*p}$, so suppose that $V^{m-2}_{*p}$ is irreducible.
+  We've already proven it for $V^2_{\vs\vp}$ and $V^3_{\vs\vp}$, so suppose that $V^{m-2}_{\vs\vp}$ is irreducible.
 
-  Let $\cbr{v_i}$ be the basis for $V_{*p}$.
-  Then, each $v_i$ is cyclic; indeed, we can transform every basis vector into $(*p\dots p)$ by multiplying by the appropriate $\frac{1}{\vard-\varc}(T_i - \varc)$, and we can transform $(*p\dots p)$ into any basis vector by multiplying be the appropriate $\frac{1}{\vard-\vare}(T_i - \vare)$.
-  Hence it is sufficient to show that each $v \in V_{*p}$ generate some basis element.
+  Let $\cbr{v_i}$ be the basis for $V_{\vs\vp}$.
+  Then, each $v_i$ is cyclic; indeed, we can transform every basis vector into $(\vs\vp \dots \vp)$ by multiplying by the appropriate $\frac{1}{\vard-\varc}(T_i - \varc)$, and we can transform $(\vs\vp \dots \vp)$ into any basis vector by multiplying be the appropriate $\frac{1}{\vard-\vare}(T_i - \vare)$.
+  Hence it is sufficient to show that each $v \in V_{\vs\vp}$ generate some basis element.
 
-  Let $v'$ be the basis element $(*p*p\dots p)$, which is many copies of $*p$, followed by an extra $p$ if $m$ is odd.
+  Let $v'$ be the basis element $(\vs\vp\vs\vp\dots \vp)$, which is many copies of $\vs\vp$, followed by an extra $\vp$ if $m$ is odd.
   We will show that each $v \in F$ generates $v'$.
 
-  Suppose that no elements beginning $(*p*p)$ are represented in $v_i$;
+  Suppose that no elements beginning $(\vs\vp\vs\vp)$ are represented in $v_i$;
   then, all such elements are represented in $T_3v$, so we may assume that at least one is represented in $v$.
 
-  Note that $\ima (T_2 - \vara) = \Span\cbr{\text{Basis vectors beginning }(*p*p)}$ and $(T_2 - \vara)v \neq 0$.
-  Further, note that $\Res_{\SH(S_{m-2})}^{\SH(S_m)} \ima (T_2 - \vara) \simeq V^{m-2}_{*p}$ as representations.
-  Hence irreducibility of $V^{m-2}_{*p}$ implies that $v'$ is generated by $(T_2 - \vara)v$, and $V^m_{*p}$ is irreducible.
+  Note that $\ima (T_2 - \vara) = \Span\cbr{\text{Basis vectors beginning }(\vs\vp\vs\vp)}$ and $(T_2 - \vara)v \neq 0$.
+  Further, note that $\Res_{\SH(S_{m-2})}^{\SH(S_m)} \ima (T_2 - \vara) \simeq V^{m-2}_{\vs\vp}$ as representations.
+  Hence irreducibility of $V^{m-2}_{\vs\vp}$ implies that $v'$ is generated by $(T_2 - \vara)v$, and $V^m_{\vs\vp}$ is irreducible.
 \end{proof}
@@
 Knowing this, the restriction statements are clear;
-$\Res V_{*p}^m \simeq V_{pp}^{m-1}$ by considering the last $m-2$ transpositions, and $\Res V_{*p}^{m-1} \simeq V_{*p}^{m-1} \oplus V_{**}^{m-1}$ by considering the first $m-2$.
-Similarly, $\Res V_{**}^m \simeq V_{*p}^{m-1}$ by considering the first $m-2$ transpositions.
-This gives that $V \simeq 3V_{*p} \oplus 2V_{**}$.
+$\Res V_{\vs\vp}^m \simeq V_{\vp\vp}^{m-1}$ by considering the last $m-2$ transpositions, and $\Res V_{\vs\vp}^{m-1} \simeq V_{\vs\vp}^{m-1} \oplus V_{\vs\vs}^{m-1}$ by considering the first $m-2$.
+Similarly, $\Res V_{\vs\vs}^m \simeq V_{\vs\vp}^{m-1}$ by considering the first $m-2$ transpositions.
+This gives that $V \simeq 3V_{\vs\vp} \oplus 2V_{\vs\vs}$.
 
@@
      \begin{align*}  
-      V^{2n}_{**} &\simeq D^{(n,n)'}\\ 
-      V^{2n-1}_{**} &\simeq D^{(n+1,n-2)'}\\
-      V^{2n}_{*p} &\simeq D^{(n+1,n-1)'}\\
-      V^{2n-1}_{*p} &\simeq D^{(n,n-1)'}.
+      V^{2n}_{\vs\vs} &\simeq D^{(n,n)'}\\ 
+      V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)'}\\
+      V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)'}\\
+      V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)'}.
      \end{align*}
@@
 
-  By irreducibility, $V^{2n-1}_{**} \simeq D^{\lambda_{**}}$ and $V^{2n-1}_{*p} \simeq D^{\lambda_{*p}}$ for some diagrams $\lambda_{**}$ and $\lambda_{*p}$.
-  We will show that $\lambda_{**} = (n+1,n-2)'$ and $\lambda_{*p} = (n+1,n-1)'$.
+  By irreducibility, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda_{\vs\vs}}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\lambda_{\vs\vp}}$ for some diagrams $\lambda_{\vs\vs}$ and $\lambda_{\vs\vp}$.
+  We will show that $\lambda_{\vs\vs} = (n+1,n-2)'$ and $\lambda_{\vs\vp} = (n+1,n-1)'$.
 
-  First, note that we have \[\Res \; D^{\lambda_{**}} \simeq D^{(n,n-2)'} \simeq \Res \; D^{(n+1,n-2)'}\] and \[\Res \; D^{\lambda_{*p}} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)'}.\]
-  By semisimplicity of $\Res D^{\lambda_{**}}$ and $\Res D^{\lambda_{*p}}$, every normal cell in $\lambda_{**}$ and $\lambda_{*p}$ is good, and every good cell is removed in a summand of the restriction.
-  In particular, the only normal number in $\lambda_{**}$ is 1.
+  First, note that we have \[\Res \; D^{\lambda_{\vs\vs}} \simeq D^{(n,n-2)'} \simeq \Res \; D^{(n+1,n-2)'}\] and \[\Res \; D^{\lambda_{\vs\vp}} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)'}.\]
+  By semisimplicity of $\Res D^{\lambda_{\vs\vs}}$ and $\Res D^{\lambda_{\vs\vp}}$, every normal cell in $\lambda_{\vs\vs}$ and $\lambda_{\vs\vp}$ is good.
+  In particular, the only normal number in $\lambda_{\vs\vs}$ is 1.
 
-  For $\lambda_{**}$, the only tableaux which can remove a cell to yield $D^{(n,n-2)'}$ are $(n+1,n-2)'$, $(n,n-1)'$, and $(n,n-2,1)'$ as illustrated in Figure \ref{OddRes};
-  we have already seen that $D^{(n,n-1)'}$ does not have irreducible restriction, so we are left with $(n+1,n-2)'$ and $(n,n-2,1)'$.
-  We may directly check that $(n,n-2,1)'$ doesn't satisfy this, as we have the following:
+  For $\lambda_{\vs\vs}$, the only tableaux which can remove a cell to yield $D^{(n,n-2)'}$ are $(n+1,n-2)'$, $(n,n-1)'$, and $(n,n-2,1)'$ as illustrated in Figure \ref{OddRes};
+  we have already seen that $D^{(n,n-1)'}$ does not have irreducible restriction, so we are left with $(n+1,n-2)'$ and $\lambda = (n,n-2,1)'$.
+  We may directly check that $\lambda$ doesn't satisfy this, as we have the following:
   \begin{align*} 
@@
    \end{align*} 
-  At least one of $\beta(1,2)$ and $\beta(1,3)$ is nonzero, since $\beta_\lambda(1,3) - \beta_\lambda(1,2) = 3 \not\equiv 0 \pmod e$, and hence at least one of $M_2$ and $M_3$ is empty.
-  Hence at least one of 2 or 3 is normal in $(n,n-2,1)'$, and $\lambda_{**} = (n+1,n-2)$.
+  At least one of $\beta_\lambda(1,2)$ and $\beta_\lambda(1,3)$ is nonzero, since $\beta_\lambda(1,3) - \beta_\lambda(1,2) = 3 \not\equiv 0 \pmod e$, and hence at least one of $M_2$ and $M_3$ is empty.
+  Hence at least one of 2 or 3 is normal in $(n,n-2,1)'$, and $\lambda_{\vs\vs} = (n+1,n-2)$.
 
-  For $\lambda_{*p}$, we immediately see from Figure \ref{OddRes} that the only option is $(n,n-1)$.
+  For $\lambda_{\vs\vp}$, we immediately see from Figure \ref{OddRes} that the only option is $(n,n-1)$.
   \begin{figure}
-    \[
+    \begin{align*}
       \cbr{
         \begin{gathered}
-        \ydiagram{2,2,2,1,1,1}. \; \;
-        \ydiagram{2,2,2,2,1}, \; \;
-        \ydiagram{3,2,2,1,1}
+        \ydiagram{6,3}. \; \;
+        \ydiagram{5,4}, \; \;
+        \ydiagram{5,3,1}
       \end{gathered} 
-    }\longrightarrow \begin{gathered}
-      \ydiagram{2,2,2,1,1}
-      \end{gathered}
-      \hspace{50pt}
+    }&\longrightarrow \begin{gathered}
+      \ydiagram{5,3}
+      \end{gathered}\\
       \cbr{
         \begin{gathered}
-          \ydiagram{2,2,2,2,1}
+          \ydiagram{5,4}
         \end{gathered}
-      }\longrightarrow
+      }&\longrightarrow
       \begin{gathered}
-        \ydiagram{2,2,2,1,1},\;\;
-        \ydiagram{2,2,2,2}.
+        \ydiagram{5,3},\;\;
+        \ydiagram{4,4}.
       \end{gathered}
-    \]
+    \end{align*}
     \caption{
@@
   We can perform a similar argument for the $V^{2n}$ case, finding now that 
-  \[\Res \; D^{\mu_{**}} \simeq D^{(n,n-1)'} \simeq \Res \; D^{(n,n)'}\] and 
-  \[\Res \; D^{\mu_{*p}} \simeq D^{(n,n-1)'} \oplus D^{(n+1,n-2)'} \simeq \Res \; D^{(n+1,n-1)'}.\]
+  \[\Res \; D^{\mu_{\vs\vs}} \simeq D^{(n,n-1)'} \simeq \Res \; D^{(n,n)'}\] and 
+  \[\Res \; D^{\mu_{\vs\vp}} \simeq D^{(n,n-1)'} \oplus D^{(n+1,n-2)'} \simeq \Res \; D^{(n+1,n-1)'}.\]
 
-  Through a similar process, we see that $\mu_{*p} = (n+1,n-1)'$.
-  We narrow down $\mu_{**}$ to one of $(n,n)'$ or $(n,n-1,1)'$, and note that
+  Through a similar process, we see that $\mu_{\vs\vp} = (n+1,n-1)'$.
+  We narrow down $\mu_{\vs\vs}$ to one of $(n,n)'$ or $\mu := (n,n-1,1)'$, and note that
   \begin{align*} 
@@
   \end{align*}
-  and hence at least one of 2 or 3 is normal, $\Res D^{(n,n-1,1)'}$ is not irreducible, and $\mu_{**} = (n,n)'$, finishing our proof.
+  and hence at least one of 2 or 3 is normal, $\Res D^{(n,n-1,1)'}$ is not irreducible, and $\mu_{\vs\vs} = (n,n)'$, finishing our proof.
 \end{proof}
@@
   \begin{align*} 
-    V^{2n} \simeq 3D^{(n+1,n-1)'} \oplus 2D^{(n,n)'}
-    V^{2n - 1} \simeq 3D^{(n,n-1)'} \oplus 2D^{(n+1,n-2)'}
+    V^{2n} &\simeq 3D^{(n+1,n-1)'} \oplus 2D^{(n,n)'}\\
+    V^{2n - 1} &\simeq 3D^{(n,n-1)'} \oplus 2D^{(n+1,n-2)'}
   \end{align*}
@@
 
+\section{Empirical Results}
+
+\section{Acknowledgements}
+
+\begin{thebibliography}{9}
+
+\bibitem{Brundan}
+  Brundan citation here
+
+\bibitem{Etingof}
+  Etingof citation here
+
+\bibitem{Kleschev}
+  Kleschev citation here
+
+\bibitem{Mathas Book}
+  Mathas book citation here
+
+\bibitem{Mathas}
+  Mathas article citation here
+
+\bibitem{Shor}
+  Shor citation here
+
+\end{thebibliography}
+
 \newpage
-
 \appendix
@@
     This is illustrated in Figure \ref{braid1arc}.
-    \begin{figure}[b]
+    \begin{figure}
   \[
@@
 \[
-  \cbr{(pppp),(*pp*),(ppp*),(*ppp),(*p*p),(p*p*),(pp*p),(p*pp)}.
+  \cbr{(\vp\vp\vp\vp),(\vs\vp\vp\vs),(\vp\vp\vp\vs),(\vs\vp\vp\vp),(\vs\vp\vs\vp),(\vp\vs\vp\vs),(\vp\vp\vs\vp),(\vp\vs\vp\vp)}.
 \]

### 2019-07-26 code/generalized_crossingless.py

@@ -1,0 +1,229 @@
+from cmath import sqrt
+
+# n: number of nodes (note that this must be even)
+# match: dictionary sending node to matching node
+# for example, {1:4,4:1,2:3,3:2} is the S4 rainbow
+#
+#
+
+
+class basis_element:
+    def __init__(self, n, match, r=0):
+        assert n % 2 == 0, 'n must be even'
+        
+        self.n = n
+        self.r = r
+        assert len(match.keys()) == n, 'must have n nodes, do not specify r'
+        for i in match.keys():
+            assert match[i] != i, 'an element cannot be paired with itself'
+            assert i == match[match[i]], 'matchings are not symmetric'
+            for j in range(min(i, match[i])+1, max(i, match[i])):
+                assert min(i, match[i]) < match[j] and max(
+                    i, match[i]) > match[j], 'matchings cross'
+        
+        # anchors match to -1
+        # note: this does not check validity.        
+        for i in range(1,n + r + 1): 
+            if i not in match.keys():
+                match[i] = i
+        self.match = match
+
+    # returns dictionary of matches nodes
+    def get_matches(self):
+        dictt = {}
+        for i in self.match.keys():
+            dictt[i] = self.match[i]
+        return dictt
+
+    # returns matching node to i
+    def pair(self, i):
+        return self.match[i]
+
+    # creates tex to call the Matchings macro on the given basis elt
+    def output_latex(self):
+        prematching = []
+        for key in self.match.keys():
+            if key < self.match[key]:
+                prematching += ["{}/{}".format(key, self.match[key])]
+
+        matching = "\\Matching{{{}}}{{{}}}".format(
+            self.n, ",".join(prematching))
+        return matching
+
+    def __eq__(self, i):
+        return i.get_matches() == self.get_matches()
+
+    # so that you can use the basis elements to index in a dictionary
+    def __hash__(self):
+        a = 0
+        for i in range(self.n):
+            a = a+self.n**i*self.match[i+1]
+        return a
+
+    def __str__(self):
+        return str(self.match)
+
+
+# vecpairs: dictionary sending basis element to coefficient
+# for example, the element (rainbow+two humps) in S4 would be implemented
+# using a dictionary sending the rainbow basis element to 1, and the two humps
+# element to 1
+class module_element:
+    def __init__(self, n, vecpairs, q=1, r=0):
[…]

### 2019-07-26 code/kernel_ranks_generalized.py

@@ -1,0 +1,148 @@
+import cmath
+import numpy
+import generalized_crossingless as crossingless
+import time
+import csv
+import math
+
+def make_matrix_generalized(n,q,restriction = 0,r=0):
+    """
+
+    Create the matrix for the direct sum (1 + t_1) oplus ... oplus (1 + t_{i - 1 - restriction}) for parameter q
+    This has trivial kernel iff the restriction to S_{n - restriction} is irreducible.
+    
+    KEYWORD ARGUMENTS:
+    n -- parameter from S_n
+    q -- parameter of the hecke algebra (T_i - q)(T_i + 1) = 0
+    restriction -- the number of simple transpositions ignored.
+    """
+    assert n % 2 == 0
+
+    # generate a basis; basisraw has basis_element elements, basis has module_element
+    basisraw = crossingless.generate_basis_generalized(n,q,r)
+    basis = [crossingless.module_element(n,{b:1},q,r) for b in basisraw]
+
+    C = len(basis)
+    m = numpy.zeros(C)
+    # i iterates over the simple transpositions considered
+    for i in range(n - restriction - 1):
+        # generate the matrix by applying the transposition to each basis vector and taking the resulting coefficients
+        outs = [b.mult_generator(i+1) for b in basis]
+        outsmat = numpy.matrix([[out.coeff(b) for out in outs] for b in basisraw])
+        m = numpy.vstack([m,outsmat])
+    
+    # prune zero rows from matrix
+    m = m[[i for i, x in enumerate(m) if x.any()]]
+    return m
+
+def representation(n,q=1,r=0):
+    """
+    Create the matrices spelling out the representation
+    """
+    # generate a basis; basisraw has basis_element elements, basis has module_element
+    basisraw = crossingless.generate_basis_generalized(n,q,r)
+    basis = [crossingless.module_element(n,{b:1},q,r) for b in basisraw]
+
+    C = len(basis)
+    m = []
+    # i iterates over the simple transpositions considered
+    for i in range(n + r - 1):
+        # generate the matrix by applying the transposition to each basis vector and taking the resulting coefficients
+        outs = [b.mult_generator(i+1) for b in basis]
+        outsmat = numpy.matrix([[out.coeff(b) for out in outs] for b in basisraw])
+        m = m + [outsmat]
+    
+    return m
+    
+
+def kernel_dimension(n,q,restriction=1,r=0):
+    """
[…]

### 2019-07-26 tex/kernel.tex

@@
 
+\vspace{5mm}
+We will characterize our kernel in a recursive fashion.
+To motivate this characterization, consider the following lemma.
+In simpler terms, this lemma states that if a basis element $\beta$ has some sub-matching $\beta(a,b)$, we may act on $\beta$ as if we are acting on $\beta(a,b)$.
+
+\vspace{5mm}
+\begin{lemma}
+	Take a basis element $\beta\in W_{2n+r}^r$. Suppose $\beta$ has some sub-matching $\beta(a,b)$ with $r'$ anchors.
+
+	We may consider the restriction $\text{Res}_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}W_{2n+r}^r$ of this representation to the algebra generated by transpositions $T_a,...,T_{b-1}$.
+
+	Define $Y_\beta\subset \text{Res}_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}W_{2n+r}^r$ to be the subrepresentation generated by the set of basis elements $\{\alpha| \alpha(1,a-1)=\beta(1,a-1),\ \alpha(b+1,2n+r)=\beta(b+1,2n+r)\}$.
+Then the map $\rho:Y_\beta\rightarrow W_{b-a+1}^{r'}$ defined by $$\rho(\alpha)=\alpha(a,b)$$ is an isomorphism of representations.
+\end{lemma}
+
+\vspace{5mm}
+\begin{proof}
+
+	The map is clearly bijective. Thus it is sufficient to prove the following: $$\rho(T_{i+a-1}\alpha)=T_i\rho(\alpha)$$.
+
+	As mentioned in the previous section, the action of a transposition $T_i$ can change at most 4 nodes, so we need to show that the transpositions end up changing the same nodes in the same way in  $\rho(T_{i+a-1}\alpha)$ and $T_i\rho(\alpha)$.
+
+	Suppose $\alpha(i+a-1)=s,\alpha(i+a)=t$.
+Then $(T_{i+a-1}\alpha)(i+a-1)=i+a$, $(T_{i+a-1}\alpha)(s)=t$, so $\rho(T_{i+a-1}\alpha)(i)=i+1$, $\rho(T_{i+a-1}\alpha)(s-a+1)=t-a+1$.
+Separately, $\rho(\alpha)(i)=s-a+1$ and $\rho(\alpha)(i+1)=t-a+1$, so $T_i\rho(\alpha)(i)=i+1$ and $T_i\rho(\alpha)(s-a+1)=t-a+1$ as desired.
+So the map is an isomorphism and the lemma is proved.
+\end{proof}
+
+\vspace{5mm}
 The following proposition states the forward direction of our characterization: if the kernel is nontrivial, it must have the following properties.
@@
 	\begin{center}	
-		a) For any basis element $\beta\in W_{2n+r}^r$, the coordinate of $\beta$ in $w$ must be some rational function of $q$, say $x_\beta(q)$.
+		(i) For any basis element $\beta\in W_{2n+r}^r$, the coordinate of $\beta$ in $w$ must be some rational function of $q$, say $x_\beta(q)$.
 
@@
 
-	Suppose $\beta(1)=a$. Assume 1 is not an anchor. Then $\beta$ has two sub-matchings $\alpha_1=\beta(2,a-1)$ and $\alpha_2=\beta(a+1,2n+r)$. Then we have the following:
+	\vspace{5mm}
+	Suppose $\beta(1)=a$. Assume 1 is not an anchor. Then $\beta$ has two sub-matchings $\alpha_1=\beta(2,a-1)$ and $\alpha_2=\beta(a+1,2n+r)$, and we have the following:
 	\\
@@
 
-		b) $x_\beta(q)=x_1(q)x_2(q)\frac{Q_{n+r-1}...Q_{n+r-(a/2)}}{Q_1...Q_{a/2-1}}$
+		(ii) $x_\beta(q)=x_{\alpha_1}(q)x_{\alpha_2}(q)\frac{Q_{n+r-1}...Q_{n+r-(a/2)}}{Q_1...Q_{a/2-1}}$
 
@@
 
-	If 1 is an anchor, we have a sub-matching $\beta(2,2n+r)$ with coordinate $x_3(q)$ in its respective kernel element, and I claim $x_\beta(q)=x_3(q)$.
+	If 1 is an anchor, we have a sub-matching $\alpha_3=\beta(2,2n+r)$ and I claim $x_\beta(q)=x_{\alpha_3}(q)$.
 
@@
 
+\vspace{5mm}
 The first statement of this proposition says that, given an element of the kernel $w$, we can write the coordinate of any basis element $\beta$ in $w$ as a rational function of $q$ as long as $Q_1...Q_{n+r-1}\not=0$.
 
+\vspace{5mm}
 The second statement is meant to inductively define the coordinate of an arbitrary basis element.
@@
 
+\vspace{5mm}
 An illustration of this proposition is shown in figure 4.
-
-\begin{proof}
-
-	As with many proofs in this section, this will be a proof by induction.
-
-	First, let us specify our base case: $W_{2}^0$ only has the rainbow element, which has coordinate 1. We also define the coordinate of an empty matching (i.e. no nodes) to be 1.
 
@@
 			\end{gathered}}$ 
-		\caption{Suppose the second and third elements have coefficients $x_2(q)$ and $x_3(q)$}
+		\caption{Suppose the second and third elements have coordinates $x_2(q_1)$ and $x_3(q_2)$ in their respective kernel elements, where for $q_1$, $e=3$ and for $q_2$ $e=4$.
+The coordinate of the first element is $x(q)=x_2(q)x_3(q)\frac{Q_5Q_4Q_3}{Q_1Q_2}$, where for $q$, $e=7$}
 	\end{figure}
+
+\vspace{5mm}
+The structure of the proof is as follows:
+
+\begin{enumerate}
+	\item Use proposition 2.3 to find the coefficient of the basis element with $a/2$ humps then a rainbow element.
+
+	\item Use proposition 2.3 in a somewhat reversed manner to find the coefficient of the basis element consisting of the rainbow for the first $a$ nodes then the rainbow for the final $2n+r-a$ nodes.
+
+	\item Use lemma 3.1 to finish the proof through induction.
+\end{enumerate}
+
+\vspace{10mm}
+\begin{proof}
+
+	Need more specific notation for the rainbow elements of specific representations.
 

### 2019-07-26 tex/kernel.tex
slightly more progress on kernel proof

@@
 \end{proposition}
+{\color{red} Need to note that some of these may not be sub-matchings}
 
@@
 \begin{proof}
+	Note that statement (i) was necessary to state (ii), but it is natural to prove both statements together, so this is how we will proceed.
+	\\
 
-	Need more specific notation for the rainbow elements of specific representations.
+	By proposition 2.2 the rainbow element has coordinate 1 in $w\in W_{2n+r}^r$.
+By proposition 2.3 the element $R_1:=R_{L,n+r-1}$ has coordinate $Q_{n+r-1}$ in $w$.
+Then $R_1(3,2n+r)$ is the rainbow element in  $W_{2(n-1)+r}^r$, so the element $R_2$ defined by $R_2(1,2)=R_1(1,2)$, $R_2(3,2n+r)=R_{L,n+r-2}\in W_{2(n-1)+r}^r$ has coordinate $Q_{n-1}Q_{n-2}$.
+Generally, define $R_i$ by $R_i(1,2(i-1))=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r)=R_{L,2n+r-i}$.
+Then the coefficient of $R_i$ is $Q_{n+r-1}...Q_{n+r-i}$.
+These elements are shown in figure 5.
+
+	\begin{figure}
+		\def\cbasisspacing{5mm}
+
+		$\cbr{
+			\begin{gathered}
+			\GeneralizedMatching{8}{3/8, 4/7,5/6}{2}{1/1,2/2}{5/4}, \hspace{\cbasisspacing}
+			\GeneralizedMatching{8}{1/2, 5/8,6/7}{2}{3/1,4/2}{5/4}, 
+			\hspace{\cbasisspacing}
+			\GeneralizedMatching{8}{1/2, 3/4,7/8}{2}{5/1,6/2}{5/4}, \hspace{\cbasisspacing}
+			\end{gathered}}$ 
+		\caption{In order, the rainbow element, $R_1$, and $R_2$.
+The coordinate of the rainbow element is 1.
+The coordinate of $R_1$ is $Q_{4}$.
+The coordinate of $R_2$ is $Q_4Q_3$.
+Generally, $R_i$ is the element with $i$ humps then a rainbow element, and has coordinate $Q_{n+r-1}...Q_{n+r-i}$.}
+	\end{figure}
+
+	Now define basis elements $E_i$ by $E_i(2i+1,2n+r)=R_i(2i+1,2n+r)$, $E_i(1,2i)=R$, $R$ the appropriate rainbow element.
+By the same argument as above, if $E_i$ has coordinate $c$ in $w$, $R_i$ has coordinate $Q_{i-1}...Q_{1}c$.
+One way to make this more clear is to consider intermediate basis elements $\alpha_j^{E_i}$ defined by $\alpha_j^{E_i}(2i+1,2n+r)=E_i(2i+1,2n+r)$ and $\alpha_j^{E_i}(1,2i)=R_{L,j}$.
+Then the coordinates of $\alpha_j^{E_i}(2i+1,2n+r)$ in terms of the coordinate $c$ of $E_i$ are $Q_{i-1}...Q_{i-j}$, and $R_i=\alpha_{i-1}^{E_i}$.
+
+	Since we assume $Q_i\not=0$ for $i< n+r$, this implies the coefficient of $E_i$ is $\frac{Q_{n+r-1}...Q_i}{Q_1...Q_{i-1}}$.
+In particular, returning to our desired basis element $\beta$, the coordinate of $E_{a/2}$ is $\frac{Q_{n+r-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$.
+	\\
+
+	Now, I claim that this method can be applied to any rainbow sub-matching in exactly the same way. In other words, extraneous nodes add no complexity to this argument.
+
+	Formally, given some basis element $\alpha$, suppose $\alpha(s,t)=R$ with $2n'+r'$ nodes and $r'$ anchors, and that $\alpha$ has coordinate $c$.
+Then the basis elements $\theta_i$ defined by $\theta_i(1,s-1)=\alpha(1,s-1)$, $\theta_i(t+1,2n+r)=\alpha(t+1,2n+r)$, and $\theta_i(s,t)=E_i$ have coordinates $\frac{Q_{n'+r'-1}...Q_{n'+r'-i}}{Q_1...Q_{i-1}}c$.
+
+	\begin{figure}
+		\def\cbasisspacing{5mm}
+
+		$\cbr{
+			\begin{gathered}
+			\GeneralizedMatching{14}{1/2,3/4,5/6,9/12,10/11,13/14}{2}{7/1,8/2}{5/4}, \hspace{\cbasisspacing}
+			\GeneralizedMatching{14}{1/6,2/5,3/4,9/12,10/11,13/14}{2}{7/1,8/2}{5/4}, \hspace{\cbasisspacing}
+			\end{gathered}}$ 
+		\caption{The figure on the left has submatching $R_3$ ignoring the last two nodes.
+The figure on the right has sub-matching $E_3$ also ignoring the last two nodes.
+Since the last two nodes have the same structure for both elements, if the coordinate of the second element is $c$, the coordinate of the first is $Q_2Q_1c$.}
+	\end{figure}
+
+	An example is given in figure 6.
+	\\
+
+	To turn this into an inductive proof, suppose statements (i) and (ii) are true for all representations with $2n'+r'<2n+r$ nodes.
+
+	Consider the set of basis elements $B=\{\alpha|\alpha(a+1,2n+r)=R\}$.
+We have shown that the element $\alpha_R\in B$ defined by $\alpha_R(1,a)=R$ has nonzero coefficient $\frac{Q_{n+r-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$.
+So, by our inductive hypothesis, the element $\tilde{\alpha_1}\in B$ defined by $\tilde{\alpha_1}(1,a)=\beta(1,a)=\alpha_1$ has coefficient $x_{\alpha_1}\frac{Q_{n+r-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$.
+
+	Similarly, consider the set of basis elements $B'=\{\upsilon|\upsilon(1,a)=\alpha_1\}$.
+We have shown that the element $\upsilon_R=\tilde{\alpha_1}$ has nonzero coefficient $x_{\alpha_1}\frac{Q_{n+r-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$.
+So, by our inductive hypothesis, $\beta$ has coefficient $x_{\alpha_2}x_{\alpha_1}\frac{Q_{n+r-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$ and the inductive step is proven.
+
+	Note that if the first node is an anchor, we need only consider the sub-matching of the rainbow element $R(2,2n+r)$ and use the inductive hypothesis. Thus the inductive step is proven in all cases.
+
+	For base cases, we consider those representations with 2 or less nodes.
+If there is only one node, it must be an anchor.
+In this case, the single anchor element is the only element and it is the rainbow element, so it has coefficient 1.
+For two nodes, if there are two anchors we may use the inductive step.
+Otherwise, there is one match, which is again the only element and is the rainbow element.
+Since the number 1 is a rational function of $q$, the base cases are proved.
+
+	So, by induction, the proposition holds.
 

### 2019-07-26 tex/Rough-Overview.tex

@@
   \begin{abstract}
-  Abstract goes here
+    We are concerned with Specht Modules corresponding to Young diagrams of two rows.
+    When the Iwahori-Hecke algebra of the symmetric group has vanishing parameter $e$, for diagram $(n + r,n)$ we first define a \emph{Crossingless Matchings Representation} on $2n + r$ nodes with $r$ anchors $M_{2n + r}^r$, and we use modular branching rules to prove the isomorphism to the corresponding specht module $M_{2n + r}^r \simeq S^{(n+r,n)'}$ in the case that $e > n$ and the specht module is irreducible.
+    We additionally give conjecture in the direction of a proof in the general case.
+    Next, we adopt the Fibonacci representation $V$ to the Iwahori-Hecke algebra in the case $e = 5$ and characterise the quotients $D^{(n+r,n)}$ with $r \leq 3$ via isomorphism with two subrepresentations based on first and last character;
+    additionally, we decompose the other two of these into direct sums of the first two, and thus achieve a graphical realization of $D^{(n+r,n)}$ at $e = 5$, $r\leq 3$ and decompose the fibonacci representation into a direct sum of these quotients of Specht modules.
+    Last, some heuristics are presented to support our conjecture and give explicit transitions from $M \rightarrow V$ in cases with small $n$.
   \end{abstract}
+
+\tableofcontents
+
 \end{titlepage}

### 2019-07-27 tex/Drafts/Draft-1.tex
First draft section 2, overview, bibliography, some more data

--- 2019-07-26 tex/Rough-Overview.tex
@@
   \documentclass{amsart}   
-\usepackage{RepStyle} 
-\usepackage{NatMacros} %********REPLACE WITH MilesMacros TO KILL RELIANCE ON \ifnum AND HAVE INCOMPLETE OUTPUT***********bleh
+  \usepackage{../RepStyle} 
+  \usepackage{../NatMacros}
+
+  % Emulates \subsection* but doesn't add to ToC (I don't know why amsart is weird 
+  \newcommand{\fakesubsection}[1]{
+    \vspace{7pt}
+    \noindent \textbf{#1.}
+  }
+
+  \makeatletter
+  %Table of Contents
+  \setcounter{tocdepth}{3}
+
+  % Add bold to \section titles in ToC and remove . after numbers
+  \renewcommand{\tocsection}[3]{%
+    \indentlabel{\@ifnotempty{#2}{\bfseries\ignorespaces#1 #2\quad}}\bfseries#3}
+  % Remove . after numbers in \subsection
+  \renewcommand{\tocsubsection}[3]{%
+    \indentlabel{\@ifnotempty{#2}{\ignorespaces#1 #2\quad}}#3}
+  \let\tocsubsubsection\tocsubsection% Update for \subsubsection
+  %...
+
+  \newcommand\@dotsep{4.5}
+  \def\@tocline#1#2#3#4#5#6#7{\relax
+    \ifnum #1>\c@tocdepth % then omit
+    \else
+      \par \addpenalty\@secpenalty\addvspace{#2}%
+      \begingroup \hyphenpenalty\@M
+      \@ifempty{#4}{%
+        \@tempdima\csname r@tocindent\number#1\endcsname\relax
+      }{%
+        \@tempdima#4\relax
+      }%
+      \parindent\z@ \leftskip#3\relax \advance\leftskip\@tempdima\relax
+      \rightskip\@pnumwidth plus1em \parfillskip-\@pnumwidth
+      #5\leavevmode\hskip-\@tempdima{#6}\nobreak
+      \leaders\hbox{$\m@th\mkern \@dotsep mu\hbox{.}\mkern \@dotsep mu$}\hfill
+      \nobreak
+      \hbox to\@pnumwidth{\@tocpagenum{\ifnum#1=1\bfseries\fi#7}}\par% <-- \bfseries for \section page
+      \nobreak
+      \endgroup
+    \fi}
+
+  \def\l@subsection{\@tocline{2}{0pt}{2.5pc}{5pc}{}}
+  \makeatother
+
   \begin{document}
 
-\title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules  of Hecke Algebras}
+  \title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules of Iwahori-Hecke Algebras of the Symmetric Group}
   \author[Miles Johnson \& Natalie Stewart]{Miles Johnson \& Natalie Stewart\\
@@
     \begin{abstract}
-  Abstract goes here
+      We consider the Iwahori-Hecke algebra of the symmetric group on $2n + r$ indices with parameter $q \in k^\times$.
+      Let $e$ be the smallest integer such that $\brk{e}_q = 0$, or set $e = \infty$ if none exist.
+      We modify Khovanov's crossingless matchings to include $2n$ nodes and $r$ anchors, and prove that the corresponding module is isomorphic to the Specht module $S^{(n+r,n)}$ when $e > n + r + 1$.
+      Additionally, we prove heuristics in support of the general case.
+      Lastly, when $e = 5$, we prove an isomorphism between $D^{(n+r,n)}$ with $r \leq 3$ and some subrepresentations of Jordan-Shor's Fibonacci representation.
     \end{abstract}
+
+  \tableofcontents
+
   \end{titlepage}
@@
 
+  {\color{orange} Literature review and motivation goes here.}\cite{Kleshchev}
+
+  \normalsize
   Throughout the text, we will refer to partitions of $2n + r$;
@@
 
-Let $S^{(n+r,n)'}$ be the Specht module corresponding to the young diagram with two columns with height difference $r$, and let $D^{(n+r,n)'}$ be the corresponding irreducible quotient.
+  Let $S^{(n+r,n)}$ be the Specht module corresponding to the young diagram with two rows with height difference $r$, and let $D^{(n+r,n)}$ be the corresponding irreducible quotient.
   The purpose of this writing is to characterize these representation via an isomorphism with two graphical representations of $\SH$.
 
-\subsection{Crossingless Matchings}
+  \fakesubsection{Crossingless Matchings}
+
   \begin{definition}
@@
     We will call these arcs and anchors, respectively.
-  Then, define $W^r_{2n+r}$ to be the $k$-vector space with basis the set of generalized crossingless matchings on $2n+r$ indices with $r$ anchors.
+    Then, define $M^r_{2n+r}$ to be the $k$-vector space with basis the set of generalized crossingless matchings on $2n+r$ indices with $r$ anchors.
 
     In order for this to be a $\SH$-module, endow this with the action given by Figure \ref{Action}; 
-  if a ``loop'' is created, scale by $q+1$, if a loop is not created and the action involves fewer than 2 anchors, deform into a new crossingless maching and scale by $q^{1/2}$, and if it involves two anchors, scale by 0.
+    if a ``loop'' is created, scale by $q+1$, if a loop is not created and the action involves fewer than 2 anchors, deform into a new crossingless matching and scale by $q^{1/2}$, and if it involves two anchors, scale by 0.
     We verify that this is well-defined in appendix \ref{Cross Relations}.
   \end{definition}
+  {\color{orange} Fix Definition with isotopy.}
 
@@
 
-  \caption{Illustration of the actions $(1 + T_i)w_{\abs{W^2_6}}$.
+    \caption{Illustration of the actions $(1 + T_i)w_{\abs{M^2_6}}$.
       In general, we act by deleting loops, deforming into a new crossingless matching, and scaling by either $q^{1/2}$, $(q + 1)$, or 0.
@@
   Let the length of an arc $(i,j)$ be $l(i,j) := j - i + 1$.
-Note that the crossingless matchings on $2n$ indices with no anchros can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
-using this, we may order the crossingless matchings with no anchors in increasing lexicographical order in order to obtain an order on the subbasis containing a particular set of anchors;
+  Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
+  using this, we may order the crossingless matchings with no anchors in increasing lexicographical order in order to obtain an order on the sub-basis containing a particular set of anchors;
   let the basis be ordered first by the position of the anchors in decreasing lexicographical order, then increasing for the matchings between each anchor.
   Let this basis be $\cbr{w_i}$.
-This basis is illustrated for $W_{5}^1$ in Figure \ref{S5 Basis}.
+  This basis is illustrated for $M_{5}^1$ in Figure \ref{S5 Basis}.
 
@@
        \end{gathered}}$ 
-    \caption{The basis for $W_5^1$.}
+      \caption{The basis for $M_5^1$.}
     \label{S5 Basis}
@@
 
-We will prove that $W := W_{2n+r}^r$ and $S := S^{(n+r,n)'}$ are isomorphic as representations in the case that $e > n + r + 1$.
-Note that, when $r = 0$, these have the same dimension given by the $n$th catalan number $C_n$.
-
-\subsection{Fibonacci Representation}
-\def\vara{\alpha}
-\def\varb{\beta}
-\def\varc{\gamma}
+  Note that the representations $M_{0 + r}^r$ and $S^{(r)}$ are isomorphic to the sign representation; 
+  we will prove that $M_{2n+r}^r$ and $S^{(n+r,n)}$ are isomorphic as representations in the case that $e > n$ and $S^{(n+r,n)}$ is irreducible.
+  Note that, when $r = 0$, these have the same dimension given by the $n$th Catalan number $C_n$.
+
+  \def\vara{\alpha_1}
+  \def\varb{\alpha_2}
+  \def\varc{\varepsilon_1}
   \def\vard{\delta}
-\def\vare{\varepsilon}
+  \def\vare{\varepsilon_2}
   \def\vs{\texttt{*}}
   \def\vp{\texttt{0}}
+  \fakesubsection{Fibonacci Representation}
   Now suppose that $e = 5$ and $k$ contains the algebraic number $(-1 - q^2 - q^3)^{3/2}$.
@@
     \begin{split}    
-    V^{2n}_{\vs\vs} &\simeq D^{(n,n)'}\\ 
-    V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)'}\\
-    V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)'}\\
-    V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)'}.
+      V^{2n}_{\vs\vs} &\simeq D^{(n,n)}\\ 
+      V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)}\\
+      V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)}\\
+      V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)}.
     \end{split} \label{Fib Isos}
@@
 
+  \fakesubsection{Overview of Paper}
+  In Section \ref{Specht Modules Section} we give corollaries to standard theorems concerning Specht modules.
+  First, James-Mathas provides a sharp characterization of the irreducibility of $e$-regular, called the \emph{Carter criterion}.\cite{Mathas-book}
+  We specialize this to the case that $\lambda = (n+r,n)$ to give a tractable combinatorial expression for irreducibility of $S^{(n+r,n)}$.
+  We note that this irreducibility depends only on $e$ when $e > n$;
+  otherwise it depends on the characteristic of the field.
+  Next, we specialize theorems introduced by Kleshchev and generalized by Brundan describing $\Hom{W, \Res \, D^\lambda}$ where $W$ is either $S^\mu$ or $D^\mu$ for $\mu$ a partition of $2n + r - 1$ and our restriction is taken to the subalgebra generated $2n + r - 2$ simple transpositions.\cite{Kleshchev}\cite{Brundan}
+  We verify that this is unambiguous in Appendix \ref{Algebra}.
+  These allow us to prove our first significant statement: if $S^\lambda \simeq D^\lambda$ and $e > n$, then a particular length-2 composition series uniquely determines $\lambda$;
+  further, an irreducible restriction to $D^{(n,n-1)}$ determines $\lambda$ as well.
+
+  In Section \ref{Crossingless Matchings Section}, we begin by attempting to prove that $M := M_{2n + r}^r$ is irreducible whenever $e > n+r+1$.
+  We do this by first proving that every vector in our basis for $M$ is cyclic, then that $M$ contains no sign subrepresentation.
+  We then use these facts to inductively prove irreducibility.
+  Following this, we prove a particular filtration with factors given by other crossingless matchings representations;
+  this becomes a composition series, and an inductive argument combined with the branching of Section \ref{Specht Modules Section} allows us to prove $M \simeq S^{(n+r,n)}$.
+  Last, we finish the section by proving more general statements concerning sign subrepresentations, which contribute to conjectures later in the paper.
+
+  In Section \ref{Fibonacci Section}, we begin by establishing isomorphisms of the subrepresentations of $V^m$ in the case that $m = 2$, as well as irreducibility of $V^3_{\vs\vp}$.
+  We then use these cases to prove that $V_{\vs\vp}$ is irreducibility, having as a corollary that $V_{\vs\vs}$ is irreducible.
+  From this, we inductively prove isomorphisms between the representations $V_{\vs\vs}$, $V_{\vs\vp}$ and $D^{(n+r,n)}$ with $r$ depending on the subscript of $V$ and the parity of $m$.
+
+  {\color{orange} Overview of Conjecture and Empirics goes here.}
+
+  % Acknowledgements should be given section-level heading in toc, subsection-level in text.
+  \addcontentsline{toc}{section}{\textbf{Acknowledgements}}
+  \fakesubsection{Acknowledgements}
+  {\color{orange} Acknowledgements go here.}
+
   \newpage
-\section{Preliminaries on Specht Modules}
-\begin{proposition}
+
+\section{Preliminaries on Specht Modules}\label{Specht Modules Section}
+  For this section and the rest of the paper, assume $n > 0$.
+
+  In the following section, we cite a theorem of James-Mathas which precisely characterizes the irreducibility of $S^\lambda$ in the case that $\lambda$ is $e$-regular, and we specialize this result to the case of two-row specht modules.
+  This falls into two cases: either $e > n$, where $S^{(n+r,n)}$ is irreducible iff $e \nmid r+2,\dots,n+r+1$, or $e \leq n$, where the irreducibility of $S^{(n+r,n)}$ is complicated and depends on the characteristic of $k$.
+  We will focus primarily on the former case.
+
+  Following this, we cite the branching theorems of Kleshchev-Brundan, which allow us to fully characterize the Socle of $\Res S^{\lambda}$.
+  This and some combinatorial arguments allow us to come to the main result of this section, which may loosely be stated as follows:
+  the composition series of $D^{(n+r,n)}$ is restrictive enough in many cases with $S^{(n+r,n)}$ irreducible and $e > n$ case that such a composition series uniquely characterizes irreducibles.
+  This will be immensely useful later for characterizing $M$ via Specht modules, as it will include all cases with $e > n + r + 1$.
+
+  \subsection{Irreducibility of $S^\lambda$}
+  Let $k$ have characteristic $\ell$;
+  then, set
+  \[
+    p := \begin{cases}
+      \ell & \ell > 0\\
+      \infty & \ell = 0
+    \end{cases}.
+  \]
+  Note that $p = e$ when $q = 1$.
+  For $h$ a natural number, let $\nu_p(h)$ be the $p$-adic evaluation of $h$.
+  As a convention, set $\nu_\infty(h) = 0$ for all $h$.
+  Define the function $\nu_{e,p} : \NN \rightarrow \cbr{-1} \cup \NN$ by
+  \[
+    \nu_{e,p}(h) := \begin{cases}
+      \nu_p(h) & e \mid h\\
+      -1 & e \nmid h
+    \end{cases}.
+  \]
+  Lastly, let $h_{ab}^\lambda$ be the hook length of node $(a,b)$ in $\brk \lambda$.
+  With this language, we may express the following theorem, part (ii) of which is named the \emph{carter criterion}, due to James-Mathas.\cite{Mathas-book}
+  \begin{theorem}[James-Mathas]
+    The following are equivalent:
     \begin{enumerate}[label={(\roman*)}]
-    \item
-    Suppose that $n,r > 0$.
-    Then, a filtration of $\Res W_{2n + r}^r$ is given by
-    \begin{equation}
-      0 \subset W_{2n + r - 1}^{r-1} \subset \Res \, W_{2n + r}^r \label{Filtration}
-     \end{equation}
-     with $\Res \, W_{2n + r}^r / W_{2n + r - 1}^{r-1} \simeq W_{2n + r - 1}^{r + 1}$. 
-    \item
-      We have the following isomorphism of representations:
-      \begin{equation}
-        W_{2n - 1}^1 \simeq \Res \; W_{2n}^0 \label{0 Restriction}
-       \end{equation}
+      \item $S^{\lambda} \simeq D^{\lambda}$.
+      \item $\lambda$ is $e$-regular and $S^\lambda$ is irreducible.
+      \item $\nu_{e,p}\prn{h_{ab}^\lambda} = \nu_{e,p}\prn{h_{ac}^\lambda}$ for all nodes $(a,b)$ and $(a,c)$ in $\brk \lambda$.
+    \qed\end{enumerate}
+  \end{theorem}
+  This result gives information solely on $e$-regular partitions, and the general irreducibility of $S^\lambda$ away from $p=2$ is not well understood.
+  We will henceforth specialize slightly to the case that $(n+r,n)$ is $e$-restricted.
+
+  \begin{corollary}\label{S irreducibility}
+    If $r = 0$, assume $e > 2$.
+    \begin{enumerate}[label={(\roman*)}]
+      \item Suppose $e > n$.
+        Then, $S^{(n+r,n)}$ is irreducible iff $e \nmid l$ for all $r + 2 \leq l \leq n + r + 1$.
+      \item Suppose $e \leq n$.
+        Then, $S^{(n+r,n)}$ is irreducible iff $e | r + 1$ and $\nu_{e,p}(h_{ab}^\lambda)$ acquires exactly two values.
     \end{enumerate}  
-\end{proposition}
-\begin{proof}
+  \end{corollary}
+  In the case that $\lambda = (n+r,n)$ and $e$ satisfy hypothesis \eqref{S irreducibility}.(i), say that $\lambda$ is \emph{$e$-top-indivisible}.
+  \begin{proof}
+    The beginning condition implies that $\lambda$ is $e$-regular, which we will use below.
+
     \textbf{(i)}
-  Note that we may identify the subrepresentation of $\Res \; W_{2n + r}^r$ having anchor $n$ with $W_{2n + r - 1}^{r-1}$.
-
-  Let $U := \Res \; W_{2n + r}^r / W_{2n + r - 1}^{r - 1}$. 
-  Let $\phi:U \rightarrow W_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $W_{2n + r - 1}^{r + 1}$.
-  It is not hard to verify that this is a well-defined isomorphism of vector spaces, so we must show that it is $\SH$-linear.
-
-  Given a basis vector $w_j$ with arc $(i,2n + r)$, $\phi$ is clearly compatible with $T_{i'}$ with $i' \neq i,i-1$.
-  Further, it's easy to verify that $\phi$ is compatible with $T_{i}$ and $T_{i-1}$, as actions on one anchor were designed for this deformation.
-  When there are anchors $(i,i+1)$, then $\phi(T_iw_j) = T_i\phi(w_j) = 0$, and similar for $T_{i -1}$.
-  Hence $\phi$ is an isomorphism of representations, and the statement is proven.
-
-  \textbf{(ii)}
-  This follows with the above proof, defining $W_{2n - 1}^{-1} := 0$
-\end{proof}
-
-\begin{lemma}
-  Suppose $n,r > 0$.
-  Then, we may characterize the socle of $\Res \, D^\lambda$ as follows:
-  \[
-    \soc\prn{\Res \, D^{(n+r,n)'}} \simeq \begin{cases}
-      D^{(n + r - 1,n)'} & e \mid r+2\\
-      D^{(n + r,n-1)'} & e \nmid r+2, \; e \mid r\\
-      D^{(n+r-1,n)'} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
-    \end{cases}
-  \]
-\end{lemma}
-\begin{proof}
-  This amounts to computations of the hook lengths $\beta(1,2)$ and $\gamma(1,2)$:
-  \begin{align*}
-    \beta_\lambda(1,2) &= r + 2\\
-    \gamma_\lambda(1,2) &= r
-  \end{align*}
-  Since $2$ is the largest removable number, $D^{(n+r,n-1)'} \subset D^{(n+r,n)'}$ iff $e \nmid r + 2$.
-  Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)'} \subset D^{(n+r,n)'}$ iff 1 is good iff $e \nmid r$
-\end{proof}
-
-\begin{lemma}\label{S irreducibility}
-  \begin{enumerate}[label={(\roman*)}]
-    Assume $e > 2$ and $n > 0$.
-    \item Suppose $e > n$.
-      Then, $S^{(n+r,n)'}$ is irreducible iff $e \nmid l$ for all $r + 2 \leq l \leq n + r + 1$.
-    \item Suppose $e \leq n$.
-      Then, $S^{(n+r,n)'}$ is irreducible iff $e | r + 1$ and $\nu_{e,p}(h_{ab}^\lambda)$ acquires exactly two values over rows $a \leq n$.
-  \end{enumerate}  
-\end{lemma}
-\begin{proof}
-  \textbf{(i)}
-  Note that $\nu_p(l) \neq -1$ for all $l$ and only hook lengths in the first column may vanish mod $e$;
-  hence we may equivalently prove that $e$ divides no hook lengths in the first $n$ rows of the first column.
+    Note that $\nu_p(l) \neq -1$ for all $l$ and only hook lengths in the top row may vanish mod $e$;
+    hence we may equivalently prove that $e$ divides no hook lengths in the leftmost $n$ columns of the second column.
     These hook lengths are precisely $r + 2,\dots,n+r+1$.
@@
     Then, \[\nu_{e,p}\prn{h^\lambda_{n-e+1,1}} = \nu_{e,p}\prn{h^\lambda_{n-e,2} + r + 1} = -1,\]
-  giving $S^{(n+r,n)'}$ reducible.
-
-  Note that $\nu$ acquires at least two values since $e$ is a hook length.
-  Now, suppose that \[0 \leq \nu_{e,p}(h^{\lambda}_{ab}) < \nu_{e,p}\prn{h^{\lambda}_{a'b'}}\] and $S^{(n+r,n)'}$ is irreducible.
-  If $a=a'$ then we have reducibility, so assume $a \neq a'$.
-  Further, if $b = b'$, then we may replace $b$ with the other column;
-  hence we may assume WLOG that $b \neq b'$ as well.
+    giving $S^{(n+r,n)}$ reducible.
+
+    \def\corsecsep{5pt}
+    \vspace{\corsecsep}
+    Now, suppose that $\nu$ acquires at least three values, and \[0 \leq \nu_{e,p}(h^{\lambda}_{ab}) < \nu_{e,p}\prn{h^{\lambda}_{a'b'}}\] and $S^{(n+r,n)}$ is irreducible.
+    If $b=b'$ then we have reducibility, so assume $b \neq b'$.
+    Further, if $a = a'$, then we may replace $a$ with the other column;
+    hence we may assume WLOG that $a \neq a'$ as well.
 
     Note that $p$-adic valuation is monotonic, so $h^\lambda_{ab} < h^\lambda_{a'b'}$.
+    If $(a,b)$ is in the rightmost $r$ columns, then we may $0 \leq \nu_{e,p}\prn{h^\lambda_{a''b''}} \leq \nu_{e,p}\prn{h^\lambda_{ab}}$ for some $(a'',b'')$ in the rightmost $n$ columns;
+    this has the same hook length as a cell in the leftmost $n$ columns and bottom row, so we may assume $(a,b)$ is not in the rightmost $r$ columns.
+    Similar logic allows us to assume $(a',b')$ is in the leftmost $n$ columns as well.
+
     If $b < b'$, then $\nu_p(h_{ab}) = \nu_p(h_{ab'}) < \nu(h_{a'b'})$ while $h_{ab'} > h_{a'b'}$, a contradiction.
@@
 
-  Finally, assume $e | r + 1$ and $\nu_{e,p}$ acquires two values over the top $n$ rows.
+    \vspace{\corsecsep}
+    Finally, assume $e | r + 1$ and $\nu_{e,p}$ acquires two values.
     Since $e | r + 1$, $e \mid h_{a1}^\lambda$ iff $e \mid h_{a2}$;
@@
 
-This is complicated and annoying, and the second amounts to a condition on $p$.
-We will illustrate that irreducibility interpolates between $p = 2$ and $p$ large:
+  From condition (ii) we see that irreducibiliy at $e > n$ is not dependent on $p$, and we may cover many modular cases without reference to the characteristic of $k$.
+  We will finish our discussion of irreducibilty of $S^\lambda$ via the following special cases of (ii) above.
   \begin{corollary}
-  Assume $2 < e \leq n$.
+    If $r = 0$, assume $e > 2$.
+    Suppose $e \leq n$.
     \begin{enumerate}[label={(\roman*)}]
-    \item Suppose $p > n + r + 1$. Then, $S^{(n + r,n)'}$ is irreducible iff $e | r + 1$.
-    \item Suppose $p = 2$. Then, $S^{(n+r,n)'}$ is not irreducible.
+      \item Suppose $p > n + r + 1$. Then, $S^{(n + r,n)}$ is irreducible iff $e | r + 1$.
+      \item Suppose $p = 2$. Then, $S^{(n+r,n)}$ is not irreducible.
     \end{enumerate}
@@
   \end{proof}
-
+  \subsection{Branching}
+  In this section as well as later sections, we will consider the restruction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}(S_{2n + r - 1}$.
+  We verify in Appendix \ref{Algebra} that any two subalgebras of $\SH$ generated by $2n + r - 2$ simple transpositions give isomorphic restrictions of representations (through a particular isomorphism of the subalgebras).
+  We will hence abuse notation, pick one such subalgebra $\SH'$, and notate $\Res_{\SH'}^\SH W$ by $\Res W$ for any $\SH$-module $W$.
+
+  The following statements, collectively called \emph{modular branching rules} of $D^\lambda$, were originally written by Kleshchev for Specht modules of the group algebra $k\brk{S_n}$, then generalized to the Hecke algebra case by Brundan.\cite{Kleshchev}\cite{Brundan}
+  They entirely characterize the Socle of $\Res D^\lambda$, as well as the condition that $\soc\prn{\Res D^\lambda} \simeq \Res D^\lambda$.
+  \begin{theorem}[Kleshchev-Brundan]
+    We have the following isomorphisms of vector spaces
+    \begin{align*}
+      \Homarg{\SH'}{S^\mu,\Res D^\lambda} 
+      &\simeq \begin{cases}
+        k & \mu \xrightarrow{\text{normal}} \lambda\\
+        0 & \text{otherwise}
+      \end{cases}\\
+      \Homarg{\SH'}{D^\mu,\Res D^\lambda} 
+      &\simeq \begin{cases}
+        k & \mu \xrightarrow{\text{good}} \lambda\\
+        0 & \text{otherwise}
+      \end{cases}
+    \end{align*}
+    and $\Res D^\lambda$ is semisimple if and only if every normal number in $\lambda$ is good.\qed
+  \end{theorem}
+
+  Using this, we immediately see that, for any rectangular partition $(m^\ell)$, we have
+  \[
+    \Res D^{(m^\ell)} \simeq D^{(m^{\ell-1},m-1)}.
+  \]
+  The non-rectangular two-row case is more complicated, but we may still describe it fully as follows.
+  \begin{corollary}\label{D Restrictions}
+    Suppose $r > 0$.
+    Then, we may characterize the socle of $\Res \, D^\lambda$ as follows:
+    \[
+      \soc\prn{\Res \, D^{(n+r,n)}} \simeq \begin{cases}
+        D^{(n + r - 1,n)} & e \mid r+2\\
+        D^{(n + r,n-1)} & e \nmid r+2, \; e \mid r\\
+        D^{(n+r-1,n)} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
+      \end{cases}
+    \]
+  \end{corollary}
+  \begin{proof}
+    This amounts to computations of the hook lengths $\beta(1,2)$ and $\gamma(1,2)$:
+    \begin{align*}
+      \beta_\lambda(1,2) &= r + 2\\
+      \gamma_\lambda(1,2) &= r
+    \end{align*}
+    Since $2$ is the largest removable number, $D^{(n+r,n-1)} \subset D^{(n+r,n)}$ iff $e \nmid r + 2$.
+    Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)} \subset D^{(n+r,n)}$ iff 1 is good iff $e \nmid r$
+  \end{proof}
+
+  Now that we've characterized how these restrict, we can describe how strongly these restrictions characterize irreducibles.
+  Namely, we will prove that a composition series consistent with $(n+r,n)$ and $e$ top-indivisibility of $(n+r-1,n+1)$ is sufficient to determine that an irreducible is $D^{(n+r,n)}$ when either $r \neq 0$ or $e \neq 4$.
   \begin{proposition}\label{Combinatorics}
-  Suppose that $e,n,r$ satisfy criterion (i) of Proposition \ref{S irreducibility}.
-  Let $\lambda$ be a partition of $2n + r$.
+    Let $\lambda$ be an $e$-regular partition of $2n + r$.
     \begin{enumerate}[label={(\roman*)}]
-    \item Suppose $r > 0$.
+      \item Suppose $r > 0$, suppose $e \nmid r+1, r + 2,\dots,n + r + 1$, and suppose either $e \mid r$ or $e \nmid r$.
         If $D^\lambda$ has the composition series 
         \begin{equation}\label{D Composition Series}
-        0 \subset D^{(n+r-1,n)'} \subset \Res \, D^{\lambda}
+          0 \subset D^{(n+r-1,n)} \subset \Res \, D^{\lambda}
         \end{equation}
-      with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)'} \simeq D^{(n+r,n)'}$, then $\lambda = (n+r,n)'$.
-    \item Suppose $r = 0$ and $D^{(n,n-1)'} \simeq \Res \, D^\lambda$.
-      Then $\lambda = (n,n)'$.
+        with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)} \simeq D^{(n+r,n)}$, then $\lambda = (n+r,n)$.
+      \item Suppose $r = 0$, suppose $e \nmid 4$, and suppose $D^{(n,n-1)} \simeq \Res \, D^\lambda$.
+        Then $\lambda = (n,n)$. 
     \end{enumerate}
@@
   \begin{proof}
+    Note that $e > n$.
+
     \textbf{(i)}
-  Let $\varpi := (n+r-1,n,1)$, let $\varsigma := (n+r-1,n+1)'$, and let $\mu := (n + r,n)'$.
-  Since $D^{(n+r-1,n)'} \subset \Res \, D^\lambda$, we have $(n + r - 1,n)' \longrightarrow \lambda$, implying $\lambda = \varpi,\varsigma,\mu$.
-
+    Let $\varpi := (n+r-1,n,1)$, let $\varsigma := (n+r-1,n+1)$, and let $\mu := (n + r,n)$.
+    Since $D^{(n+r-1,n)} \subset \Res \, D^\lambda$, we have $(n + r - 1,n) \longrightarrow \lambda$, implying $\lambda = \varpi,\varsigma,\mu$.
     We will show that $\varpi, \varsigma$ do not have socle compatible with \eqref{D Composition Series};
@@
 
-  First, we focus on $\varpi$;
-  Suppose $r > 1$ and $e \mid n + 1$;
-  then, $\beta_{\varpi}(2,3) = n + 1 \equiv 0 \pmod e$, so $3$ is not normal and $D^{(n+r-1,n)'}$ is not in the socle of $D^\varpi$, giving $\lambda \neq \varpi$.
-
-  Now suppose $r > 1$ and $e \nmid n + 1$.
-  Then $S^{(n+r-2,n,1)'} \simeq D^{(n+r-2,n,1)'}$.
-  Then, we have $D^{(n + r - 2,n,1)'} \simeq S^{(n + r - 2,n,1} \subset \Res \, D^{\varpi}$ since 1 is normal;
-  this is not a composition factor in \eqref{D Composition Series}, so $\lambda \neq \varpi$.
-
-  Similarly, assume $r = 1$;
-  then, by the same logic, $D^{(n+r-1,n)'} \not\subset \Res \, D^\varpi$ or $D^{(n,n-1,1)} \subset \Res \, D^\varpi$, also implying $\lambda \neq \varpi$.
+    Suppose that $\lambda = \varpi$.
+    We will break into cases with $r$.
+    \begin{itemize}
+      \item Suppose that $r > 1$.
+        Note that $e \nmid r + 1 = \beta_\varpi(1,2)$, so $2$ is normal.
+        Further, $\gamma_\varpi(2,3) = n \not\equiv 0 \pmod e$, so 2 is good and $D^{(n+r-1,n-1,1)} \subset D^\varpi$, which is not a composition factor in \eqref{D Composition Series}.
+        Hence, by Jordan-H\"older, $\lambda \neq \varpi$.\cite{Etingof}
+
+      \item Suppose that $r = 1$.
+        Then, $\varpi = (n,n,1)$ has $\gamma_{\varpi}(1,2) = n \not\equiv 0 \pmod e$, giving $D^{(n,n-1,1)} \subset D^\varpi$ and hence $\lambda \neq \varpi$.
+    \end{itemize} 
   \iffalse % keeping just in case
@@
   \vspace{5pt}
-  Now, focus on $\varsigma$;
-  if $r < 2$, then $\varsigma$ is not a partition.
-  If $r = 2$, then $\Res \, D^\varsigma \simeq D^{(n+1,n)'}$ is irreducible, contradicting \eqref{D Composition Series}. 
-  If $r > 2$, then $D^{(n + r - 2,n+1)'}$ is irreducible, so $D^{(n+r-2,n+1)'} \simeq S^{(n+r-2,n+1)'} \subset D^\varsigma$, contradicting \eqref{D Composition Series}.
+  Now suppose that $\lambda = \varsigma$ and break into cases with $r$:
+  \begin{itemize}
+    \item Suppose $r > 2$.
+      Then, by Corollary \ref{D Restrictions}, we require that $e \nmid r$ and $e \mid r - 2$;
+      these are not satisfied, so $\lambda \neq \varsigma$.
+    \item Suppose $r = 2$.
+      Then $\Res \, D^\varsigma \simeq D^{(n+1,n)}$ is irreducible, contradicting \eqref{D Composition Series}. 
+    \item Suppose $r < 2$. 
+      Then $\varsigma$ is not a partition.
+  \end{itemize}
 
   \textbf{(ii)}
-  This result is fundamentally similar to the previous result;
-  since the socle of $D^\lambda$ is irreducible, we require that 1 is the only normal number, which pins $\lambda$.
+  This result is easier than the previous result;
+  since the socle of $D^\lambda$ is irreducible, we require that 1 is the only normal number and $\lambda(1) = (n,n-1)$.
+  This reduces to the cases of $\varsigma := (n + 1, n - 1)$ and $\mu := (n,n)$;
+  if $\lambda = \varsigma$, then we have that $e \mid \beta_\varsigma(1,2) = 4$, a contradiction.
+  Hence $\lambda = \mu$.
 \end{proof}
@@
       \begin{equation}\label{D Composition Series}
-        0 \subset D^{(n+r-1,n)'} \subset \Res \, D^{\lambda}
+        0 \subset D^{(n+r-1,n)} \subset \Res \, D^{\lambda}
       \end{equation}
-      with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)'} \simeq D^{(n+r,n)'}$, then $\lambda = (n+r,n)'$.
+      with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)} \simeq D^{(n+r,n)}$, then $\lambda = (n+r,n)$.
     \item Suppose $n = 1$ and $e \nmid r+2$, and suppose that we have composition series \eqref{D Composition Series}.
-      Then $\lambda=(r+1,r+2)'$.
-    \item Suppose $r = 0$, either $e \nmid n+2$ or $e > 3$, and $D^{(n,n-1)'} \simeq \Res \, D^\lambda$.
-      Then $\lambda = (n,n)'$.
+      Then $\lambda=(r+1,r+2)$.
+    \item Suppose $r = 0$, either $e \nmid n+2$ or $e > 3$, and $D^{(n,n-1)} \simeq \Res \, D^\lambda$.
+      Then $\lambda = (n,n)$.
   \end{enumerate}
@@
   \textbf{(i)}
-  Let $\lambda_1 := (n+r-1,n,1)$, let $\lambda_2 := (n+r-1,n+1)'$, and let $\lambda_3 := (n + r,n)'$.
-  Since $D^{(n+r-1,n)'} \subset \Res \, D^\lambda$, we have $(n + r - 1,n)' \longrightarrow \lambda$, implying $\lambda = \lambda_i$ for some $i = 1,2,3$.
+  Let $\lambda_1 := (n+r-1,n,1)$, let $\lambda_2 := (n+r-1,n+1)$, and let $\lambda_3 := (n + r,n)$.
+  Since $D^{(n+r-1,n)} \subset \Res \, D^\lambda$, we have $(n + r - 1,n) \longrightarrow \lambda$, implying $\lambda = \lambda_i$ for some $i = 1,2,3$.
   We will show that $\lambda_1,\lambda_2$ each have good numbers other than 1, leading to elements of their socle that are not factors in \eqref{D Composition Series};
@@
   \textbf{(iii)}
-  Let $\lambda_1 := (n,n-1,1)'$, let $\lambda_2 := (n+1,n-1)'$, and let $\lambda_3 := (n,n)'$;
+  Let $\lambda_1 := (n,n-1,1)$, let $\lambda_2 := (n+1,n-1)$, and let $\lambda_3 := (n,n)$;
   as before we know that $\lambda = \lambda_i$ for $i = 1,2,3$, so we will eliminate $\lambda_1,\lambda_2$.
@@
 
-\section{Crossingless Matchings and Specht Modules}
-\subsection{Preliminaries on Crossingless Matchings}
+\section{Crossingless Matchings and Specht Modules}\label{Crossingless Matchings Section}
+\subsection{Irreducibility of $M$}
 \begin{lemma}
   \label{Cyclic}
-  Every basis vector in $W_{2n + r}^r$ is cyclic.
+  Every basis vector in $M_{2n + r}^r$ is cyclic.
 \end{lemma}
@@
 
-    Note that, between anchors $a<a'$ having no arc $b$ with $a < b < a'$, the $W_{a'-a}^0$ case allows us to generate the vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.\footnote{At the ends, we apply the $W_a^0$ case or the $W_{2n + r - a}^{0}$ case in the same way for the first $a$ or last $2n + r - a$ indices.}
+    Note that, between anchors $a<a'$ having no arc $b$ with $a < b < a'$, the $M_{a'-a}^0$ case allows us to generate the vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.\footnote{At the ends, we apply the $M_a^0$ case or the $M_{2n + r - a}^{0}$ case in the same way for the first $a$ or last $2n + r - a$ indices.}
 
@@
 This will be a large technical tool in our proof of irreducibility.
+
+\iffalse
 \begin{lemma}\label{Represented}
@@
 \end{proof}
+\fi
 
@@
 \end{lemma}
-\begin{proof}
+\begin{proof}[Proof 1.]
   Consider the matrix $A = \bigoplus (1 + T_i)$ having kernel $K$.
-  It is sufficient by lemma \ref{Represented} to show that $A$ includes a row $[0,\dots,0,1,0,\dots,0]$ with a nonzero entry only on the column $j$.
+  It is sufficient by lemma \ref{Represented} to show that $A$ includes a row $[0,\dots,0,1,0,\dots,0]$ with a nonzero entry only on the row $j$.
 
@@
   We may iterate this process as illustrated in Figure \ref{Submatrix}, eventually ending at a row with two nonzero entries, either an arc $(1,2)$ or an arc $(2,3)$, and all anchors otherwise left-aligned and arcs of maximum length.
-  These rows together form an $(n + r) \times \abs{W_{2n + r}^r}$ submatrix of $A$ which has a nonzero column in the row corresponding to $j$, and has (by removing zero columns) the same column space as the following square matrix:
+  These rows together form an $(n + r) \times \abs{M_{2n + r}^r}$ submatrix of $A$ which has a nonzero row in the row corresponding to $j$, and has (by removing zero rows) the same row space as the following square matrix:
   \newcommand*\bigzero{\makebox(0,15){\text{\Huge0}}}
@@
   We will show that this matrix is invertible;
-  then, a sequence of elementary row operations will yield the identity, and in particular, when applied to $A$, will yield a row with a nonzero entry only on column $j$, giving $K = 0$.
+  then, a sequence of elementary row operations will yield the identity, and in particular, when applied to $A$, will yield a row with a nonzero entry only on row $j$, giving $K = 0$.
 
@@
 \end{proof}
-
-\subsection{Correspondence}
 \begin{proposition}
-  The representation $W_{2n + r}^r$ is irreducible when $e > n + r + 1$. 
-\end{proposition}
-\begin{proof}
-  We proceed by induction on $2n + r$.
-  Note that, by identification with the trivial and sign representations, the base case $2n + r = 2$ is already prove, so suppose we have proven this for each $2m + s < 2n + r$.
-
-  Take some $w \in W$ and some $(1 + T_i)$ not annhialating $w$.
+  Suppose that $(n+r,n)$ is $e$ top-indivisible.
+  Then, the representation $M_{2n + r}^r$ is irreducible. 
+\end{proposition}
+\begin{proof}
+  We proceed by induction on $n$.
+  Note that, by identification with the trivial and sign representation, the base case $n = 0$ is already proven.
+
+  Take an arbitrary vector $w \in W$.
+  By Lemma \ref{Trivial} there exists some $(1 + T_i) \in \SH$ such that $(1 + T_i)w$.
   Note that \[\ima (1 + T_i) = \Span\cbr{w_j \mid w_j \text{ contains arc }(i,i+1)}.\]
-  Hence, as vector spaces, there is an isomorphism $\varphi:\ima(1 + T_i) \rightarrow W_{2(n-1) + r}^r$ ``deleting'' the arc $(i,i+1)$.
-  This sends every basis vector to another basis vector.
-
-  We will show that, for every action $(1 + T_j') \in \SH(S_{2(n-1) + r})$, there is some action $h_j \in W_{2n + r}^r$ such that the following commutes:
+  Hence, as vector spaces, there is an isomorphism $\varphi:\ima(1 + T_i) \rightarrow M_{2(n-1) + r}^r$ ``deleting'' the arc $(i,i+1)$.
+
+  We will show that, for every action $(1 + T_j') \in \SH(S_{2(n-1) + r})$, there is some action $h_j \in M_{2n + r}^r$ such that the following commutes:
   \[
     \begin{tikzcd}
-      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] \arrow[d,"h_j"] & W_{2(n-1) + r}^r \arrow[d,"1 + T_j"]\\
-      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] & W_{2(n-1) + r}^r
+      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] \arrow[d,"h_j"] & M_{2(n-1) + r}^r \arrow[d,"1 + T_j"]\\
+      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] & M_{2(n-1) + r}^r
     \end{tikzcd}
@@
 
-  Due to the inductive hypothesis, there is some action $h' \in \SH(S_{2(n-1) + r})$ sending $\varphi((1 + T_i)w)$ to a basis vector;
-  then, the action $\SH$ generates the endomorphism $\varphi^{-1}h'\varphi$ sending $(1 + T_i)w$ to a basis vector, giving $w$ cyclic and hence $W_{2n + r}^r$ irreducible.
+  Note that, by $e$ top-indivisibility of $(n+r,n)$, we have $e \nmid r+2,\dots,n+r$, and hence $(n+r-1,n-1)$ is $e$ top-indivisible as well.
+  Then, due to the inductive hypothesis, there is some action $h' \in \SH(S_{2(n-1) + r})$ sending $\varphi((1 + T_i)w)$ to the image of a basis vector;
+  then, the action $\SH$ generates the endomorphism $\varphi^{-1}h'\varphi$ sending $(1 + T_i)w$ to a basis vector, giving $w$ cyclic and hence $M_{2n + r}^r$ irreducible.
   \begin{figure}
@@
   \]
-  \caption{The correspondence between the action of $(1 + T_2)$ on $w'_5 \in W^0_6$ and the action of $q^{-1}(1 + T_3)(1 + T_4)(1 + T_2)$ on the corresponding vector in $W^0_8$ having arc $(3,4)$ first, then on $w'_2 \in W^0_4$.
+  \caption{The correspondence between the action of $(1 + T_2)$ on $w'_5 \in M^0_6$ and the action of $q^{-1}(1 + T_3)(1 + T_4)(1 + T_2)$ on the corresponding vector in $M^0_8$ having arc $(3,4)$ first, then on $w'_2 \in M^0_4$.
   This demonstrates that the action works with and without creating a loop.
@@
 
-\begin{corollary}
-  Suppose $n,r > 0$ and $e > n + 1$.
-  Then, the sequence \eqref{Filtration} is a composition series of $\Res \, W_{2n + r}^r$.\qed
-\end{corollary}
+\subsection{Correspondence}
+\begin{proposition}\;
+
+  \begin{enumerate}[label={(\roman*)}]
+    \item
+    Suppose that $n,r > 0$.
+    Then, a filtration of $\Res M_{2n + r}^r$ is given by
+    \begin{equation}
+      0 \subset M_{2n + r - 1}^{r-1} \subset \Res \, M_{2n + r}^r \label{Filtration}
+     \end{equation}
+     with $\Res \, M_{2n + r}^r / M_{2n + r - 1}^{r-1} \simeq M_{2n + r - 1}^{r + 1}$. 
+    \item
+      We have the following isomorphism of representations:
+      \begin{equation}
+        M_{2n - 1}^1 \simeq \Res \; M_{2n}^0 \label{0 Restriction}
+       \end{equation}
+  \end{enumerate}
+    When the case is type (i) from the irreduibility lemma, this is a composition series.
+\end{proposition}
+\begin{proof}
+  \textbf{(i)}
+  Note that we may identify the subrepresentation of $\Res \; M_{2n + r}^r$ having anchor $n$ with $M_{2n + r - 1}^{r-1}$.
+
+  Let $U := \Res \; M_{2n + r}^r / M_{2n + r - 1}^{r - 1}$. 
+  Let $\phi:U \rightarrow M_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $M_{2n + r - 1}^{r + 1}$.
+  It is not hard to verify that this is a well-defined isomorphism of vector spaces, so we must show that it is $\SH$-linear.
+
+  Given a basis vector $w_j$ with arc $(i,2n + r)$, $\phi$ is clearly compatible with $T_{i'}$ with $i' \neq i,i-1$.
+  Further, it's easy to verify that $\phi$ is compatible with $T_{i}$ and $T_{i-1}$, as actions on one anchor were designed for this deformation.
+  When there are anchors $(i,i+1)$, then $\phi(T_iw_j) = T_i\phi(w_j) = 0$, and similar for $T_{i -1}$.
+  Hence $\phi$ is an isomorphism of representations, and the statement is proven.
+
+  \textbf{(ii)}
+  This follows with the above proof, defining $M_{2n - 1}^{-1} := 0$
+\end{proof}
 
@@
   Suppose $e > n + r + 1$.
-  Then, $W_{2n + r}^r \simeq S^{(n+r,n)'}$.
+  Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
 \end{theorem}
@@
   The case $n = 0$ is already proven, so suppose $n > 0$.
-
-  By irreducibility, we know that $W_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
-  We will prove this inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $W_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e.
+  In order to use Proposition \ref{Combinatorics}, suppose either $e \nmid 4$ or $r \neq 0$.
+
+  By irreducibility, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
+  We will prove this inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $M_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e.
 $e > m + s + 1$).
@@
   \begin{equation}
-    \label{Composition Series} 0 \longrightarrow D^{(n + r - 1,n)'} \longrightarrow \Res \, D^\lambda \longrightarrow D^{(n+r,n-1)'} \longrightarrow 0
+    \label{Composition Series} 0 \longrightarrow D^{(n + r - 1,n)} \longrightarrow \Res \, D^\lambda \longrightarrow D^{(n+r,n-1)} \longrightarrow 0
    \end{equation}
   Hence the theorem is given by Proposition \ref{Combinatorics}.
+
+  Now, suppose $e = 4$ and $r = 0$;
+  then $4 > n + 1$, so $n \leq 2$.
+  We've already proven the $n = 1$ case via the trivial representation, so suppose $n = 2$.
+  Then, from the proof of Proposition \ref{Combinatorics}, we know that $M_{4}^0 \simeq D^\lambda$, where $\lambda \in \cbr{(n,n), (n+1,n-1)}$.
+  We have already proven that $M_4^2 \simeq D^{(n+1,n-1)}$, and we may verify that $\dim M_4^0 = 2 \neq 3 = \dim M_4^2$, so we have that $\lambda = (n,n)$ and the theorem is proven for $e = 4$.
 \end{proof}
@@
 We may reuse the above structure of proof as above;
-suppose $W_{2n + r}^r$ and $S^{(n+r,n)'}$ are irreducible, and $\lambda = (n+r,n)'$ is the unique diagram having composition series \eqref{Composition Series}.
-Then, $W_{2n + r}^r \simeq S^{(n+r,n)'}$.
+suppose $M_{2n + r}^r$ and $S^{(n+r,n)}$ are irreducible, and $\lambda = (n+r,n)$ is the unique diagram having composition series \eqref{Composition Series}.
+Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
 
@@
     Set $n = 1$. 
-    Then $W_{2 + r}^r$ is irreducible iff $e \nmid r + 2$.
+    Then $M_{2 + r}^r$ is irreducible iff $e \nmid r + 2$.
 \end{lemma}
@@
   Set $n = 1$ and suppose $e \nmid r + 2$.
-  Then $W_{2 + r}^r \simeq S^{(1+r,1)'}$.
+  Then $M_{2 + r}^r \simeq S^{(1+r,1)}$.
 \end{theorem}
 \begin{proof}
-  Using lemma \ref{n=1 irreducibility} and \ref{S irreducibility} it is sufficient to prove that, for $D^\lambda$ having composition series \eqref{Composition Series}, we have $\lambda = (1+r,1)'$.
-  Similar to before, we consider the options $\lambda_1 := (r,1,1)'$, $\lambda_2 := (r,2)'$, and $\lambda_3 = (1+r,1);$.
+  Using lemma \ref{n=1 irreducibility} and \ref{S irreducibility} it is sufficient to prove that, for $D^\lambda$ having composition series \eqref{Composition Series}, we have $\lambda = (1+r,1)$.
+  Similar to before, we consider the options $\lambda_1 := (r,1,1)$, $\lambda_2 := (r,2)$, and $\lambda_3 = (1+r,1);$.
   We may straightforwardly check that $\lambda_1$ and $\lambda_2$ have socle containing partitions other than the composition factors in \eqref{Composition Series} by showing that each have a good number 2 as follows:
@@
 
-\section{The Fibonacci Representation and Quotients of Specht Modules}
+\subsection{Kernels and Further Work}
+\begin{proposition}\label{Represented}
+	Let $w$ be an arbitrary vector in $W_{2n+r}^r$. I claim that if $w\in \cap\text{ker}(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero.
+\end{proposition}	
+\begin{proof}
+  Let $Y$ be the set of basis elements with nonzero coordinate in $w$.
+Let $k$ be the greatest integer such that there exists $y\in Y$ where $y(1)=...=y(k)=0$ {\color{magenta} should this be $y(1)-1 = \dots = y(k) - k = 0$?
+Also, we should avoid using $k$ as an integer, as it's used elsewhere as a field.}, and let $U\subset Y$ be the set of such $y$.
+In other words, $U$ is the set of basis elements in $Y$ which have the most anchors to the far left.
+
+	Suppose $k<r$.
+Then for each $y\in U$ there exists a minimal $i_y>k+2$ such that $y(i_y)=0$.
+In other words, $i_y$ is the position of the next leftmost anchor in $y$.
+Fix $\tilde{y}$ such that $i_{\tilde{y}}\leq i_y$ for all $y$.
+Then I claim the basis element $y':=q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}$ has nonzero coordinate in $(1+T_{i_{\tilde{y}}-1})w$, implying $w\not\in \cap\text{ker}(1+T_i)$.
+To see this, we can show that $\tilde{y}$ is the only element in $Y$ such that $q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$.
+$y'$ still has $k$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$.
+If $x\in Y,\not\in U$, the basis element proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$.
+If $x\in U$ the basis element proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$.
+Since this is the only match altered by action $(1+T_{i_{\tilde{y}}-1})$ on $x$, if $(1+T_{i_{\tilde{y}}-1})x\sim y'$ this implies $x=\tilde{y}$.
+So if $k<r$ $w$ is not in the desired kernel.
+
+	Suppose $k=r$ but $R\not\in U$ (so $R\not\in Y$).
+Let us define a sequence of subsets of $U$ in the following way: $U_0:=U$, $U_{i+1}:=\{u\in U_i| u(r+i+1)=2n+2r-i+1 \}$.
+Since $R\not\in U$, $\exists t<n-1$ such that $U_{t+1}=\emptyset$.
+Choose $\tilde{u}\in U_t$ such that $\tilde{u}(r+t+1)\geq u(r+t+1)$ for all $u\in U_t$.
+Consider the basis element $u':=q^{-1/2}(1+T_{\tilde{u}(r+t+1)})\tilde{u}$.
+I claim that $\tilde{u}$ is the only element in $Y$ such that $(1+T_{\tilde{u}(r+t+1)})\tilde{u}\sim u'$, again implying that $w$ is not in the desired kernel.
+$u'$ still has $k$ anchors on the left, $u'(r+i)=2n+2r-i+2$, $1\leq i\leq t$, and $u'(r+t+1)>\tilde{u}(r+t+1)$, so $u'\not\in Y$.
+If $x\in Y,\not\in U$,  the basis element $x'$ proportional to $(1+T_{\tilde{u}(r+t+1)})x$ will have $r$ leftmost anchors only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
+Similarly, if $x\in U,\not\in U_t$, the basis element $x'$ will have the property $x'(r+t)=2n+2r-t+2$ only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
+If $x\in U_t$, $x'(r+t+1)=u'(r+t+1)$ if and only if $x(r+t+1)=\tilde{u}(r+t+1)$ and $x(x(r+t+1)+1)=\tilde{u}(\tilde{u}(r+t+1)+1)$ (since $u'\not \in Y$).
+These are the only matches altered by the action $(1+T_{\tilde{u}(r+t+1)})$, so this implies $x=\tilde{u}$.
+Thus we have proved that if $R\not\in Y$, $w$ is not in the desired kernel.
+\end{proof}
+
+{\color{orange} Necessary characterization of the Kernel goes here.}
+
+\begin{proposition}
+  Suppose $e = n + r + 1$.
+  Then $K$ is nontrivial.
+\end{proposition}
+
+\section{Fibonacci Representations and Quotients of Specht Modules}\label{Fibonacci Section}
 We can start our study of $V$ by studying low-dimensional cases.
@@
 
-Now let's prove that $V^3_{\vs\vs}$ is irreducible;
+Now let's prove that $V^3_{\vs\vp}$ is irreducible;
 this has basis $\cbr{\vs\vp\vs\vp}, \cbr{\vs\vp\vp\vp}$, and the following matrices:
@@
 since $\varb \neq \vara$, the first has eigenspaces given by the spans of basis elements, and since $\vard \neq 0$, these are not eigenspaces of the second.
-Hence $V^3_{\vs\vs}$ is irreducible.
+Hence $V^3_{\vs\vp}$ is irreducible.
 Now we may move on to the general case.
@@
 
+\begin{corollary}
+  The representation $V_{\vs\vs}$ is irreducible.\qed
+\end{corollary}
+
 Now we may move on and use Young Tableau to characterize $V$.
@@
      \begin{align*}  
-      V^{2n}_{\vs\vs} &\simeq D^{(n,n)'}\\ 
-      V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)'}\\
-      V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)'}\\
-      V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)'}.
+      V^{2n}_{\vs\vs} &\simeq D^{(n,n)}\\ 
+      V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)}\\
+      V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)}\\
+      V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)}.
      \end{align*}
@@
   By irreducibility, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda_{\vs\vs}}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\lambda_{\vs\vp}}$ for some diagrams $\lambda_{\vs\vs}$ and $\lambda_{\vs\vp}$.
-  We will show that $\lambda_{\vs\vs} = (n+1,n-2)'$ and $\lambda_{\vs\vp} = (n+1,n-1)'$.
-
-  First, note that we have \[\Res \; D^{\lambda_{\vs\vs}} \simeq D^{(n,n-2)'} \simeq \Res \; D^{(n+1,n-2)'}\] and \[\Res \; D^{\lambda_{\vs\vp}} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)'}.\]
+  We will show that $\lambda_{\vs\vs} = (n+1,n-2)$ and $\lambda_{\vs\vp} = (n+1,n-1)$.
+
+  First, note that we have \[\Res \; D^{\lambda_{\vs\vs}} \simeq D^{(n,n-2)} \simeq \Res \; D^{(n+1,n-2)}\] and \[\Res \; D^{\lambda_{\vs\vp}} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)}.\]
   By semisimplicity of $\Res D^{\lambda_{\vs\vs}}$ and $\Res D^{\lambda_{\vs\vp}}$, every normal cell in $\lambda_{\vs\vs}$ and $\lambda_{\vs\vp}$ is good.
@@
 
-  For $\lambda_{\vs\vs}$, the only tableaux which can remove a cell to yield $D^{(n,n-2)'}$ are $(n+1,n-2)'$, $(n,n-1)'$, and $(n,n-2,1)'$ as illustrated in Figure \ref{OddRes};
-  we have already seen that $D^{(n,n-1)'}$ does not have irreducible restriction, so we are left with $(n+1,n-2)'$ and $\lambda = (n,n-2,1)'$.
+  For $\lambda_{\vs\vs}$, the only tableaux which can remove a cell to yield $D^{(n,n-2)}$ are $(n+1,n-2)$, $(n,n-1)$, and $(n,n-2,1)$ as illustrated in Figure \ref{OddRes};
+  we have already seen that $D^{(n,n-1)}$ does not have irreducible restriction, so we are left with $(n+1,n-2)$ and $\lambda = (n,n-2,1)$.
   We may directly check that $\lambda$ doesn't satisfy this, as we have the following:
@@
   At least one of $\beta_\lambda(1,2)$ and $\beta_\lambda(1,3)$ is nonzero, since $\beta_\lambda(1,3) - \beta_\lambda(1,2) = 3 \not\equiv 0 \pmod e$, and hence at least one of $M_2$ and $M_3$ is empty.
-  Hence at least one of 2 or 3 is normal in $(n,n-2,1)'$, and $\lambda_{\vs\vs} = (n+1,n-2)$.
+  Hence at least one of 2 or 3 is normal in $(n,n-2,1)$, and $\lambda_{\vs\vs} = (n+1,n-2)$.
 
@@
     \caption{
-      Illustration of the partitions of $9$ which can, via row removal, yield $(n,n-2)'$ alone, or both $(n,n-2)'$ and $(n-1,n-1)'$.
+      Illustration of the partitions of $9$ which can, via row removal, yield $(n,n-2)$ alone, or both $(n,n-2)$ and $(n-1,n-1)$.
     }\label{OddRes}
@@
   We can perform a similar argument for the $V^{2n}$ case, finding now that 
-  \[\Res \; D^{\mu_{\vs\vs}} \simeq D^{(n,n-1)'} \simeq \Res \; D^{(n,n)'}\] and 
-  \[\Res \; D^{\mu_{\vs\vp}} \simeq D^{(n,n-1)'} \oplus D^{(n+1,n-2)'} \simeq \Res \; D^{(n+1,n-1)'}.\]
-
-  Through a similar process, we see that $\mu_{\vs\vp} = (n+1,n-1)'$.
-  We narrow down $\mu_{\vs\vs}$ to one of $(n,n)'$ or $\mu := (n,n-1,1)'$, and note that
+  \[\Res \; D^{\mu_{\vs\vs}} \simeq D^{(n,n-1)} \simeq \Res \; D^{(n,n)}\] and 
+  \[\Res \; D^{\mu_{\vs\vp}} \simeq D^{(n,n-1)} \oplus D^{(n+1,n-2)} \simeq \Res \; D^{(n+1,n-1)}.\]
+
+  Through a similar process, we see that $\mu_{\vs\vp} = (n+1,n-1)$.
+  We narrow down $\mu_{\vs\vs}$ to one of $(n,n)$ or $\mu := (n,n-1,1)$, and note that
   \begin{align*} 
@@
   \end{align*}
-  and hence at least one of 2 or 3 is normal, $\Res D^{(n,n-1,1)'}$ is not irreducible, and $\mu_{\vs\vs} = (n,n)'$, finishing our proof.
+  and hence at least one of 2 or 3 is normal, $\Res D^{(n,n-1,1)}$ is not irreducible, and $\mu_{\vs\vs} = (n,n)$, finishing our proof.
 \end{proof}
@@
   \begin{align*} 
-    V^{2n} &\simeq 3D^{(n+1,n-1)'} \oplus 2D^{(n,n)'}\\
-    V^{2n - 1} &\simeq 3D^{(n,n-1)'} \oplus 2D^{(n+1,n-2)'}
+    V^{2n} &\simeq 3D^{(n+1,n-1)} \oplus 2D^{(n,n)}\\
+    V^{2n - 1} &\simeq 3D^{(n,n-1)} \oplus 2D^{(n+1,n-2)}
   \end{align*}
@@
 
-\section{Conjecture}
+\section{Conjecture}\label{Conjecture Section}
 Recall that $K_{2n + r}^r := K$ is the direct sum of all copies of the sign representation in $W$.
@@
 \begin{proposition}
-  $K \subset W_{2n + r}^r$ is trivial when $e \neq n + r + 1$, and $\dim \, K = 1$ when $e = n + r + 1$.\qed
+  $K \subset M_{2n + r}^r$ is trivial when $e \neq n + r + 1$, and $\dim \, K = 1$ when $e = n + r + 1$.\qed
 \end{proposition} 
@@
   Suppose $e < n + r + 1$, and suppose $n'$ is such that $e = n' + r + 1$.
-  Note that $h := (1 + T_1)(1 + T_3)\dots(1 + T_{n - n'})$ maps $W_{2n + r}^r$ onto $W_{2n' + r}^r$.
-  Then, the preimage $h^{-1}(K_{2n + r}^r)$ is a subrepresentation of $W_{2n + r}^r$, and the series
-  \[
-    0 \subset h^{-1}(K_{2n + r}^r) \subset W_{2n + r}^r
-  \]
-  is a composition series of $W_{2n + r}^r$.\qed
+  Note that $h := (1 + T_1)(1 + T_3)\dots(1 + T_{n - n'})$ maps $M_{2n + r}^r$ onto $M_{2n' + r}^r$.
+  Then, the preimage $h^{-1}(K_{2n + r}^r)$ is a subrepresentation of $M_{2n + r}^r$, and the series
+  \[
+    0 \subset h^{-1}(K_{2n + r}^r) \subset M_{2n + r}^r
+  \]
+  is a composition series of $M_{2n + r}^r$.\qed
 \end{proposition}
 \begin{proposition}
-  Denote the composition factor $W_{2n + r}^r / h^{-1}(K_{2n + r}^r)$ by $U_{2n + r}^r$.
+  Denote the composition factor $M_{2n + r}^r / h^{-1}(K_{2n + r}^r)$ by $U_{2n + r}^r$.
   Then, there exist some naturals $m,s$ satisfying $2m + s = 2n + r$ and $m + s > n + r$ such that the following is an isomorphism of $\SH$-modules \[h^{-1}\prn{K_{2n + r}^r} \simeq U_{2m + s}^s\].
@@
   \[
-    0 \longrightarrow D^{(m+s,m)'} \longrightarrow S^{(n+r,n)'} \longrightarrow D^{(n+r,n)'} \longrightarrow 0.
+    0 \longrightarrow D^{(m+s,m)} \longrightarrow S^{(n+r,n)} \longrightarrow D^{(n+r,n)} \longrightarrow 0.
   \]
@@
 \begin{proposition}
-  $W_{2n + r}^r \simeq S^{(n+r,n)'}$ and $U_{2m +s}^s \simeq D^{(m+s,m)'}$.
-\end{proposition}
-
-\section{Empirical Results}
-
-\section{Acknowledgements}
-
-\begin{thebibliography}{9}
-
-\bibitem{Brundan}
-  Brundan citation here
-
-\bibitem{Etingof}
-  Etingof citation here
-
-\bibitem{Kleschev}
-  Kleschev citation here
-
-\bibitem{Mathas Book}
-  Mathas book citation here
-
-\bibitem{Mathas}
-  Mathas article citation here
-
-\bibitem{Shor}
-  Shor citation here
-
-\end{thebibliography}
+  $M_{2n + r}^r \simeq S^{(n+r,n)}$ and $U_{2m +s}^s \simeq D^{(m+s,m)}$.
+\end{proposition}
+
+\section{Empirical Results}\label{Empirics Section}
 
@@
 
-\subsection{The Crossingless Matchings Representaiton}
+\subsection{Verifying the Crossingless Matchings Representaitons}
 \label{Cross Relations}
@@
     This is illustrated in Figure \ref{braid1arc}.
-    \begin{figure}
+    \begin{figure}[b]
   \[
@@
 
-\subsection{The Fibonacci Representation} 
+\subsection{Verifying the Fibonacci Representations} 
 \label{Fib Relations}
@@
 
-\section{Miscellaneous Algebra Facts}
+\section{Miscellaneous Algebra Facts}\label{Algebra}
 Throughout the text, for some representation $V$, we refer to $\Res_{\SH(S_{l})}^{\SH(S_m)} V$ without specifying exactly which subalgebra $\SH(S_{l})$.
@@
 
+\bibliographystyle{plain} 
+ \bibliography{../RepBib}
 \end{document}

### 2019-07-27 code/kernel_ranks.py

@@ -135,7 +135,7 @@ for n in range(nmin,nmax+1,2):
 """
 
 q = 1
-for n in range(4,17,2):
+for n in range(2,17,2):
     f = open("Representation n={}".format(n),"w")
     
     rep = representation(n,q)

### 2019-07-28 tex/kernel.tex
First draft section 2, overview, bibliography, some more data
almost finished

@@
 In this section we will fully characterize $\cap\text{ker}(1+T_i)$ when $e=n+r+1$.
+We will prove that it is one dimensional and give a basis.
 Note that we still have not proved the kernel is trivial when $e$ divides but is not equal to $n+r+1$.
 That proof requires results from this section, and will come next section.
-
-\vspace{5mm}
-We will characterize our kernel in a recursive fashion.
-To motivate this characterization, consider the following lemma.
-In simpler terms, this lemma states that if a basis element $\beta$ has some sub-matching $\beta(a,b)$, we may act on $\beta$ as if we are acting on $\beta(a,b)$.
-
-\vspace{5mm}
-\begin{lemma}
-	Take a basis element $\beta\in W_{2n+r}^r$. Suppose $\beta$ has some sub-matching $\beta(a,b)$ with $r'$ anchors.
-
-	We may consider the restriction $\text{Res}_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}W_{2n+r}^r$ of this representation to the algebra generated by transpositions $T_a,...,T_{b-1}$.
-
-	Define $Y_\beta\subset \text{Res}_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}W_{2n+r}^r$ to be the subrepresentation generated by the set of basis elements $\{\alpha| \alpha(1,a-1)=\beta(1,a-1),\ \alpha(b+1,2n+r)=\beta(b+1,2n+r)\}$.
-Then the map $\rho:Y_\beta\rightarrow W_{b-a+1}^{r'}$ defined by $$\rho(\alpha)=\alpha(a,b)$$ is an isomorphism of representations.
-\end{lemma}
-
-\vspace{5mm}
-\begin{proof}
-
-	The map is clearly bijective. Thus it is sufficient to prove the following: $$\rho(T_{i+a-1}\alpha)=T_i\rho(\alpha)$$.
-
-	As mentioned in the previous section, the action of a transposition $T_i$ can change at most 4 nodes, so we need to show that the transpositions end up changing the same nodes in the same way in  $\rho(T_{i+a-1}\alpha)$ and $T_i\rho(\alpha)$.
-
-	Suppose $\alpha(i+a-1)=s,\alpha(i+a)=t$.
-Then $(T_{i+a-1}\alpha)(i+a-1)=i+a$, $(T_{i+a-1}\alpha)(s)=t$, so $\rho(T_{i+a-1}\alpha)(i)=i+1$, $\rho(T_{i+a-1}\alpha)(s-a+1)=t-a+1$.
-Separately, $\rho(\alpha)(i)=s-a+1$ and $\rho(\alpha)(i+1)=t-a+1$, so $T_i\rho(\alpha)(i)=i+1$ and $T_i\rho(\alpha)(s-a+1)=t-a+1$ as desired.
-So the map is an isomorphism and the lemma is proved.
-\end{proof}
 
@@
 
-	Generally, for any matching $\alpha$, define $x_\alpha$ to be the rational function corresponding to the coordinate of that basis element in its respective kernel element.
-We will need to prove this is well defined.
+	Generally, for any matching $\alpha$, define $x_\alpha$ to be the rational function corresponding to the necessary coordinate of that basis element in its respective kernel element.
+These functions are defined recursively in the next statement.
 
@@
 
-	\item Use lemma 3.1 to finish the proof through induction.
+	\item Finish the proof through induction.
 \end{enumerate}
@@
 
+\vspace{5mm}
+The following few corollaries will help to simplify some later proofs.
+
+\begin{corollary}
+	Let $w\in\cap\text{ker}(1+T_i)$, $w\not=0$. Suppose $\beta(1,a)$ is a sub-matching with no anchors. Then:
+
+	$$x_\beta=x_{\beta(1,a)}(q)x_{\beta(a+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a/2}}{Q_1...Q_{a/2-1}}$$
+\end{corollary}
+
+\begin{proof}
+	Define $a_1=\beta(1)$, $a_i=\beta(a_{i-1}+1)$.
+Then for some $j$ we have $a_j=a$.
+If $j=1$, the statement is the same as the proposition.
+Suppose that the statement is true for any matching with $a_v=a$, $v<j$.
+Then the statement holds for the sub-matching $\beta(a_1+1,2n+r)$, and we have:
+
+	$$x_\beta(q)=x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}}=$$
+
+	$$x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,a)}(q)x_{\beta(a+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}}\frac{Q_{n+r-a_1/2-1}...Q_{n+r-a/2}}{Q_1...Q_{a/2-a_1/2-1}}=$$
+
+	$$x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,a)}(q)x_{\beta(a+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}}\frac{Q_{n+r-a_1/2-1}...Q_{n+r-a/2}}{Q_1...Q_{a/2-a_1/2-1}}(\frac{Q_{a/2-1}...Q_{a/2-a_1/2}}{Q_{a/2-1}...Q_{a/2-a_1/2}})=$$
+
+	$$x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,a)}(q)x_{\beta(a+1,2n+r)}(q)\frac{Q_{a/2-1}...Q_{a/2-a_1/2}}{Q_1...Q_{a_1/2-1}}\frac{Q_{n+r-1}...Q_{n+r-a/2}}{Q_1...Q_{a/2-1}}=$$
+
+	$$=x_{\beta(1,a)}(q)x_{\beta(a+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a/2}}{Q_1...Q_{a/2-1}}$$
+
+	This proves the inductive step, so with base case $j=1$ the corollary holds.
+
+\end{proof}
+
+\vspace{5mm}
+\begin{corollary}
+	$\beta\in W_{2n+r}^r$, then $x_\beta(q)\not=0$ if $e>n+r$.
+\end{corollary}
+
+\begin{proof}
+	For our base cases, if $2n+r=2$ all coefficients are 1, which is nonzero for any $q$.
+
+	Assume the statement is true for all $2n'+r'<2n+r$. We have $$x_\beta(q)=x_{\alpha_1}(q)x_{\alpha_2}(q)\frac{Q_{n+r-1}...Q_{n+r-(a/2)}}{Q_1...Q_{a/2-1}}$$
+	or $$x_\beta(q)=x_{\beta(2,2n+r)}(q)$$
+
+	If $e>n+r$, non of the $Q_i$ terms are zero, and $n'+r'<n+r<e$ for any of the sub-matchings that appear, so those coordinates are nonzero and the corollary holds.
+
+\end{proof}
+
+\vspace{5mm}
+The previous proposition fully characterizes any possible kernel element when $Q_1...Q_{n+r-1}\not=0$. In particular, the following corollary holds:
+
+\begin{corollary}
+	When $Q_1..Q_{n+r-1}\not=0$ and the kernel is nontrivial, the kernel is one dimensional.
+\end{corollary}
+
+This corollary follows from the fact that we may write the coordinate of any basis element as proportional to the coordinate of the rainbow basis element.
+
+\vspace{5mm}
+\noindent\rule{16.5cm}{0.4pt}
+
+\vspace{5mm}
+The remainder of this section will be used to prove that when $e=n+r+1$, the element specified by proposition 3.2 is indeed an element of the kernel.
+
+In service of this goal, a few lemmas will be helpful. The first lemma states that sub-matchings behave identically to the corresponding representations.
+
+\vspace{5mm}
+\begin{lemma}
+	Take a basis element $\beta\in W_{2n+r}^r$. Suppose $\beta$ has some sub-matching $\beta(a,b)$ with $r'$ anchors.
+
+	We may consider the restriction $\text{Res}_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}W_{2n+r}^r$ of this representation to the algebra generated by transpositions $T_a,...,T_{b-1}$.
+
+	Define $Y_\beta\subset \text{Res}_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}W_{2n+r}^r$ to be the subrepresentation generated by the set of basis elements $\{\alpha| \alpha(1,a-1)=\beta(1,a-1),\ \alpha(b+1,2n+r)=\beta(b+1,2n+r)\}$.
+Then the map $\rho:Y_\beta\rightarrow W_{b-a+1}^{r'}$ defined by $$\rho(\alpha)=\alpha(a,b)$$ is an isomorphism of representations.
+\end{lemma}
+
+\vspace{5mm}
+\begin{proof}
+
+	The map is clearly bijective. Thus it is sufficient to prove the following: $$\rho(T_{i+a-1}\alpha)=T_i\rho(\alpha)$$.
+
+	As mentioned in the previous section, the action of a transposition $T_i$ can change at most 4 nodes, so we need to show that the transpositions end up changing the same nodes in the same way in  $\rho(T_{i+a-1}\alpha)$ and $T_i\rho(\alpha)$.
+
+	Suppose $\alpha(i+a-1)=s,\alpha(i+a)=t$.
+Then $(T_{i+a-1}\alpha)(i+a-1)=i+a$, $(T_{i+a-1}\alpha)(s)=t$, so $\rho(T_{i+a-1}\alpha)(i)=i+1$, $\rho(T_{i+a-1}\alpha)(s-a+1)=t-a+1$.
+Separately, $\rho(\alpha)(i)=s-a+1$ and $\rho(\alpha)(i+1)=t-a+1$, so $T_i\rho(\alpha)(i)=i+1$ and $T_i\rho(\alpha)(s-a+1)=t-a+1$ as desired.
+So the map is an isomorphism and the lemma is proved.
+\end{proof}
+
+\vspace{5mm}
+To verify the kernel element, we will need to know exactly which basis elements are mapped to a specific basis element by a given $(1+T_i)$. The next two lemmas help address this question.
+
+\begin{lemma}
+	Take some basis element $\beta\in W_{2n+r}^r$.
+Suppose $\beta(a)=b$ for some $b>a+1$, and that $(1+T_i)\beta=(1+q)\beta$ for some $a<i<b-1$.
+We then have a subrepresentation $\beta(a,b)$ and can define $Y_\beta$ as in the previous lemma.
+Then for all basis elements $\alpha$ such that $(1+T_i)\alpha=q^{1/2}\beta$, we have that $$\alpha\in Y_\beta$$.
+
+	Similarly, if $\beta$ has some anchor at position $u$, and $(1+T_i)\beta=(1+q)\beta$ for some $i>u$, we again have a subrepresentation $\beta(u,2n+r)$ and may define $Y_\beta$ as before.
+Then for all basis elements $\alpha$ such that $(1+T_i)\alpha=q^{1/2}\beta$, we have that $\alpha\in Y_\beta$ again.
+\end{lemma}
+
+\begin{proof}
+	This lemma follows from an observation I made in section 2: a transposition can only create two arcs or an arc and an anchor.
+
+	For the first case of this lemma, if $\alpha\not\in Y_\beta$ either $\alpha(1,a-1)\not=\beta(1,a-1)$ or $\alpha(b+1,2n+r)\not=\beta(b+1,2n+r)$.
+Suppose it is the first case.
+Then for some $s,t\in [1,a-1]$, $s<t$, we have $\beta(s)=t$ and $\alpha(s)\not=t$.
+To have $(1+T_i)\alpha=q^{1/2}\beta$ we must have $\alpha(t)=i+1$, $\alpha(s)=i$.
+But then $\alpha(a)\not=b$ and $\alpha(a)\not=i$ or $i+1$, so $((1+T_i)\alpha)(a)\not=b$ and $(1+T_i)\alpha\not=q^{1/2}\beta$.
+The same argument proves the $\alpha(b+1,2n+r)\not=\beta(b+1,2n+r)$ case.
+
+	An analogous argument proves the anchor case. Specifically, the anchor cannot exist at position $u$ and is not created by action of $(1+T_i)$ if $\alpha(s)=i$ and $\alpha(t)=i+1$.
+
+\end{proof}
+
+\vspace{5mm}
+It is important to note that lemma 3.6 only references cases where a transposition acts under an arc or to the right of an anchor. An example is given in figure 7.
+
+The next lemma characterizes cases where the transposition is not under any arcs and all anchors are to the right.
+
+\begin{figure}[b]
+	\[
+	\begin{tabular}{l l l l}
+	\GeneralizedAction{13}{1/4,2/3,6/7,8/13,9/10,11/12}{1}{5/1}{5/4}{9}{1/4,2/3,6/7,8/13,9/10,11/12}{5/1}{(1+q)}\\
+
+	\GeneralizedAction{13}{1/4,2/3,6/7,8/9,10/13,11/12}{1}{5/1}{5/4}{9}{1/4,2/3,6/7,8/13,9/10,11/12}{5/1}{(q^{1/2})}\\
+
+	\GeneralizedAction{13}{1/4,2/3,6/7,8/13,9/10,11/12}{1}{5/1}{5/4}{6}{1/4,2/3,6/7,8/13,9/10,11/12}{5/1}{(1+q)}\\
+
+	\GeneralizedAction{13}{1/4,2/3,5/6,8/13,9/10,11/12}{1}{7/1}{5/4}{6}{1/4,2/3,6/7,8/13,9/10,11/12}{5/1}{(q^{1/2})}\\
+
+	\end{tabular}
+	\]
+
+	\caption{In the first line we act under an arc, so if another element without that arc is sent to that element, it must fix the arc as shown in the second line.
+In the third line we act to the right of an anchor, so if another element without that anchor is sent to that element, it must fix the anchor as shown in the fourth line.
+	}
+	\label{Action}
+\end{figure}
+
+Essentially, this lemma states that the only elements sent to the same element are those which break at most one of the top level arcs to the left of the leftmost anchor, or that break the leftmost anchor.
+An illustration is given in figure 8.
+
+\vspace{5mm}
+\begin{lemma}
+	Take a basis element $\beta\in W_{2n+r}^r$. Suppose the leftmost anchor in $\beta$ is at index $b$. Define $a_j$ such that $\beta(a_j)=a_{j-1}+1$ and $\beta(a_1)=1$ for all $j$ such that $a_j<b$.
+
+	Suppose $(1+T_i)\beta=(1+q)\beta$ for some $i<b-1$ where $\not\exists s,t$ such that $\beta(s)=t$ and $s<i,t>i+1$.
+Suppose there is some basis element $\alpha$ such that $(1+T_i)\alpha=q^{1/2}\beta$.
+Then I claim the following:
+
+	\vspace{5mm}
+	\begin{center}
+		(i) $\beta(a_{j-1}+2,a_j-1)=\alpha(a_{j-1}+2,a_j-1)$ for all $j$.
+
+		\vspace{5mm}
+		(ii) $\beta(b+1,2n+r)=\alpha(b+1,2n+r)$
+
+		\vspace{5mm}
+		(iii)
+		If $b$ is not an anchor in $\alpha$, $\beta(a_j)=\alpha(a_j)$ for all $j$ such that $a_j\not=i+1$.
+
+		\vspace{5mm}
+		(iiii) If $b$ is an anchor in $\alpha$, there exists exactly one value of $j$ such that $\alpha(a_j)\not=\beta(a_j)$ and $a_j\not=i+1$
+	\end{center}
+\end{lemma}
+
+\begin{proof}
+
+	(i)
+
+	Suppose that, for some $j$ there exists $s,t\in [a_{j-1}+2,a_j-1]$ such that $\beta(s)=t$ but $\alpha(s)\not=t$.
+Then if $(1+T_i)\alpha=q^{1/2}\beta$ we must have $\alpha(i)=s$ or $t$ and $\alpha(i+1)=s$ or $t$.
+But, by definition, $i,i+1\not\in[a_{j-1}+1,a_j]$, so this implies $\alpha(a_j)\not=a_{j-1}+1,i,i+1$, so $((1+T_i)\alpha)(a_j)\not=a_{j-1}+1$ and $(1+T_i)\alpha\not=q^{1/2}\beta$.
+So (i) is proved.
+
+	\vspace{5mm}
+	(ii)
+
+	The proof of (ii) is analogous to the proof of (i). We cannot have $\beta(b+1,2n+r)\not=\alpha(b+1,2n+r)$ and $\beta(b+1,2n+r)=((1+T_i)\alpha)(b+1,2n+r)$ if $((1+T_i)\alpha)(b)=b$.
+
+	\vspace{5mm}
+	(iii)
+
+	If $b$ is not an anchor in $\alpha$ and $(1+T_i)\alpha=q^{1/2}\beta$, we must have $i$ an anchor in $\alpha$, and $\alpha(i+1)=b$. No other nodes in $\alpha$ are changed, so this proves (iii).
+
+	\vspace{5mm}
+	(iiii)
+	From (i)-(iii) we have that the only remaining matchings that can differ are the $(a_{j-1}+1,a_j)$ matchings.
+If one of them differs, by the same argument as before it must be fixed by the action of $(1+T_i)$, and no other nodes are changed, so (iiii) is proved.
+
+\end{proof}
+
+\begin{figure}[b]
+	\[
+	\begin{tabular}{l l l l}
+	\GeneralizedAction{15}{1/6,2/3,4/5,7/8,9/10,12/15,13/14}{1}{11/1}{5/4}{7}{1/6,2/3,4/5,7/8,9/10,12/15,13/14}{11/1}{(1+q)}\\
+
+	\GeneralizedAction{15}{1/8,2/3,4/5,6/7,9/10,12/15,13/14}{1}{11/1}{5/4}{7}{1/6,2/3,4/5,7/8,9/10,12/15,13/14}{11/1}{(q^{1/2})}\\
+
+	\GeneralizedAction{15}{1/6,2/3,4/5,7/10,8/9,12/15,13/14}{1}{11/1}{5/4}{7}{1/6,2/3,4/5,7/8,9/10,12/15,13/14}{11/1}{(q^{1/2})}\\
+
+	\GeneralizedAction{15}{1/6,2/3,4/5,8/11,9/10,12/15,13/14}{1}{7/1}{5/4}{7}{1/6,2/3,4/5,7/8,9/10,12/15,13/14}{11/1}{(q^{1/2})}\\
+
+	\end{tabular}
+	\]
+
+	\caption{The action of $(1+T_7)$ fixes the first basis element.
+Shown are all the basis vectors sent to the same element by the same transposition.
+Note that in all of them nodes 2-5 and 12-15 are the same.
+This illustrates (i) and (ii) in lemma 3.5.
+Note that in the last case where the anchor is in a different place, 1,6 and 9,10 are still matched.
+This illustrates (iii).
+In the middle two cases where the anchor is in the same place, only one of 1,6 or 9,10 are not paired.
+This illustrates (iiii).
+	}
+	\label{Action}
+\end{figure}
+
+\vspace{5mm}
+We are now ready to prove existence of a kernel element.
+To prove this, we will show that if $w\in W_{2n+r}^r$ is as characterized above, the coordinate of any basis element in $(1+T_i)w$ is zero.
+This will split into various cases related to the previous lemmas.
+
+\vspace{5mm}
+\begin{proposition}
+	Suppose $e=n+r+1$. Then $\cap\text{ker}(1+T_i)\not=\emptyset$.
+\end{proposition}
+
+\begin{proof}
+
+	Assume inductively that the statement holds for all $W_{2n'+r'}^{r'}$ where $2n'+r'<2n+r$.
+
+	As a base case, when $2n'+r'\leq 2$, the representation is at most one dimensional.
+If the one basis element has only anchors, it is sent to zero by any $(1+T_i)$, and is in the kernel.
+If the single basis element is a single arc, it is sent to $(1+q)$ times itself, and we take $e=n+r+1=2$ so $1+q=0$ and the base case holds.
+
+	\vspace{5mm}
+	Now we will prove the inductive step.
+Take $w$ as recursively defined by proposition 3.1.
+Formally, suppose $x_\alpha$ is the rational function corresponding to the coordinate of $\alpha$ in its respective kernel element for $\alpha\in W_{2n'+r'}^{r'}$, $2n'+r'<2n+r$.
+Then we define $w$ by its coordinate vector: $\beta\in W_{2n+r}^r$, if $\beta(1)=a\not=1$ then the coordinate of $\beta$ is $x_{\beta(2,a-1)}(q)x_{a+1,2n+r}(q)\frac{Q_{n-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$; if $\beta(1)=1$ then the coordinate of $\beta$ is $x_{\beta(2,2n+r)}(q)$.
+	\\
+
+	Let $E_\beta\subset W_{2n+r}^r$ be the pre-image of $\beta\in (1+T_i)W_{2n+r}^r$ under the action of $(1+T_i)$. To prove $w$ is in the kernel, we must show the following: 
+	\begin{center}
+	(i) $(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=0\text{ for all basis elements }\beta$
+	\end{center}
+	Inductively, we assume this equation holds for basis elements in smaller representations $W_{2n'+r'}^{r'}$, but only for $q$ such that $e=n'+r'+1$.
+For the following proof we will need a slightly stronger inductive assumption.
+Take $\beta'\in W_{2n'+r'}^{r'}$, and suppose either that $\beta'(1)=2n'+r'$, and that $T_i\beta'=(1+q)\beta'$, $1<i<2n'+r'-1$, or that 1 is an anchor in $\beta$.
+Defining $E_{\beta'}$ as before, we assume
+
+	\begin{center}
+		(ii) $(1+q)x_{\beta'}+\sum_{\alpha\in E_{\beta'},\alpha\not=\beta'}q^{1/2}x_\alpha=0\text{ for any } q \text{ with }e>n'+r'$
+	\end{center}
+
+	\vspace{5mm}
+	To prove the inductive step for both (i) and (ii), we must split into cases:
+
+	\begin{enumerate}
+	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, and that $\exists s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\beta(s)=t$.
+Also suppose the leftmost anchor is at some index $u>t$.
+Then we have a sub-matching $\beta(s,t)$, and by lemma 3.6 $E_\beta\subset Y_\beta$.
+Then, using corollary 3.2, the following equality holds:
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=$$
+
+	$$(x_{\beta(1,s-1)}(q)\frac{Q_{n+r-1}...Q_{n+r-(s-1)/2}}{Q_1...Q_{(s-1)/2-1}})((1+q)x_{\beta(s,2n+r)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_{\alpha(s,2n+r)}(q))=$$
+
+	$$(x_{\beta(t+1,2n+r)}(q)\frac{Q_{n+r-(s-1)/2-1}...Q_{n+r-t/2}}{Q_1...Q_{(t-s+1)/2-1}})(x_{\beta(1,s-1)}(q)\frac{Q_{n+r-1}...Q_{n+r-(s-1)/2}}{Q_1...Q_{(s-1)/2-1}})((1+q)x_{\beta(s,t)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_{\alpha(s,t)}(q))$$
+
+	We have that $e>j$ for any $Q_j$ term appearing in the equation above, and $e>n'+r'$ for any sub-matching coordinate appearing above, so by corollary 3.3:
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=0$$
+
+	if and only if
+
+	$$(1+q)x_{\beta(s,t)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_{\alpha(s,t)}(q)=0$$
+
+	Note that $(\beta(s,t))(1)=t-s+1$. So by our inductive hypothesis (ii), we have
+
+	$$(1+q)x_{\beta(s,t)}(q)+\sum_{\alpha\in E_{\beta(s,t)},\alpha\not=\beta(s,t)}q^{1/2}x_{\alpha}(q)=0$$
+
+	By lemma 3.5, if $\alpha\in Y_\beta$, $(1+T_i)\alpha=q^{1/2}\beta$ if and only if $(1+T_{i-s+1})\alpha(s,t)=q^{1/2}\beta(s,t)$, so the previous equation implies $$(1+q)x_{\beta(s,t)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_{\alpha(s,t)}(q)=0$$
+
+	as desired, and this case is proved.
+
+	\vspace{5mm}
+	\item Again take $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, but suppose the leftmost anchor is at some position $u$ where $1<u<i$.
+Then, as before, we have a sub-matching $\beta(u,2n+r)$ and by lemma 3.6 $E_\beta\subset Y_\beta$.
+
+	Note that in both corollary 3.2 and our inductive hypothesis (ii) we specified cases involving anchors. This allows the exact same logic from the proof of the first case to prove this case.
+
+	\vspace{5mm}
+	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, the leftmost anchor is at a position $u>i+1$, and $\not\exists s,t$ such that $\beta(s)=t$ and $s<i<t-1$.
+Lemma $3.7$ characterizes all $\alpha\in E_\beta$.
+We would like to prove the following for arbitrary $q$ where $e>n+r$:
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}$$
+
+	See figure 9 for an example of this equality.
+	\\
+
+	We will prove this equality through yet another inductive proof, this time inducting on the number of top level humps to the left of the rightmost anchor.
+
+	Formally, as we have in earlier lemmas, we will define $a_j$ by $a_1:=\beta(1)$, $a_j:=\beta(a_{j-1}+1)$. Then $a_b=u$ for some $b>1$.
+
+	\end{enumerate}
+\end{proof}
+
 \end{document}

### 2019-07-28 tex/Drafts/Draft-1.tex

@@
 
-  {\color{orange} Literature review and motivation goes here.}\cite{Kleshchev}
+  {\color{orange} Literature review and motivation goes here.}
 
@@
   \end{corollary}
-  In the case that $\lambda = (n+r,n)$ and $e$ satisfy hypothesis \eqref{S irreducibility}.(i), say that $\lambda$ is \emph{$e$-top-indivisible}.
+  In the case that $\lambda = (n+r,n)$ and $e \nmid r+2,r+3,\dots,n+r+1$, say that $\lambda$ is \emph{$e$-top-indivisible}.
+  Since no multiples of $e$ are in an interval of length $n$ in $\NN$, we have $e > n$, so this is precisely case (i) above.
   \begin{proof}
@@
         D^{(n+r-1,n)} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
-      \end{cases}
-    \]
+      \end{cases}.
+    \]
+    Further, when $e \nmid r$ or $e \mid r + 2$, $\Res D^{(n+r,n)}$ is semisimple.
   \end{corollary}
@@
 \section{Crossingless Matchings and Specht Modules}\label{Crossingless Matchings Section}
+In the following section, we will analyze the crossingless matchings representation $M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \simeq S^{(n+r,n)}$ whenever possible.
+We begin by proving irreducibility of $M_{2n + r}^r$ in all cases that $(n+r,n)$ is $e$ top-indivisible;
+when $p = 2$, this is all cases where $S^{(n+r,n)}$ is irreducible.
+This is proven via an inductive process; if $e \nmid n + r + 1$, then $M$ contains no sign subrepresentation, and this allows us to ``project'' down to the case $M_{2(n-1) + r}^r$, and prove irreducibility of $M$ from irreducibility of this space.
+
+Next, we
+
 \subsection{Irreducibility of $M$}
@@
 \subsection{Correspondence}
-\begin{proposition}\;
+The following theorem of Mathas generalizes the characteristic-free version of the classical branching theorem.\cite{Mathas-article}
+It will not be necessary for our present proof of the correspondence, but analogy with $M$ is suggestive.
+\begin{theorem}[Characteristic-Free Classical Branching Theorem]
+  Let $\lambda$ be a partition of $m$ with $\ell$ removable nodes.
+  Then, $\Res \, S^\lambda$ has an $\SH_{k,q}(S_{m-1})$-module filtration
+  \[
+    0 = S^{0,\lambda} \subset S^{1,\lambda} \subset \cdots \subset S^{\ell,\lambda} = \Res S^\lambda
+  \]
+  such that $S^{t,\lambda} / S^{t-1,\lambda} \simeq S^{\lambda(t)}$ for all $1 \leq t \leq \ell$.\qed
+\end{theorem}
+
+If we replace $S^\lambda$ with the appropriate $M_{2n + r}^r$ above, we find the statement of the following proposition.
+\begin{proposition}Suppose that $n > 0$.
 
@@
     \item
-    Suppose that $n,r > 0$.
+    Suppose that $r > 0$.
     Then, a filtration of $\Res M_{2n + r}^r$ is given by
@@
 
+We've now assembled the basic pieces necessary to prove our correspondence in the case $e > n + r  1$.
+Due to some problematic phenomena in the $r = 0$ case, we will initially make an assumption that $e \neq 4$ or $r \neq 0$ so that we may use the combinatorics of Proposition \ref{Combinatorics}.
+We will then assume the remaining case $e = 4, r = 0$, and prove our correspondence using process of elimination via the other surrounding cases for $e = 4$.
+
 \begin{theorem}
@@
   The case $n = 0$ is already proven, so suppose $n > 0$.
-  In order to use Proposition \ref{Combinatorics}, suppose either $e \nmid 4$ or $r \neq 0$.
-
-  By irreducibility, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
+  In order to use Proposition \ref{Combinatorics}, suppose for now that either $e \nmid 4$ or $r \neq 0$.
+
   We will prove this inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $M_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e.
@@
 
-  By the inductive hypothesis and irreducibility, we have a composition series given by 
+  By irreducibility, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
+  By the inductive hypothesis and irreducibility, we have a composition series given by the exact sequence
   \begin{equation}
@@
 \section{Fibonacci Representations and Quotients of Specht Modules}\label{Fibonacci Section}
+We have difficulty characterizing the Specht module above when it is irreducible.
+We may instead attempt to characterize the irreducible quotient $D^\lambda$ of the Specht module.
+In particular, note that, whenever $e \leq r + 2$, the restriction $\Res D^{(n+r,n)}$ decomposes into a direct sum of partitions $(m+s,m)$ such that $e \leq s + 2$ and $2m + s = 2n + r - 1$.
+This forms a recurrence among these representations, allowing a combinatorial description of their dimension.
+In this section we henceforth assume $e = 5$ and note that this recurrence resembles the Fibonacci recurrence;
+we follow this to characterize the restriction $D^{(n+r,n)}$ with $r \leq 3$.
+
+\begin{remark}
+  Let $d_{m}^{0,3}$ be the dimension $\dim D^{(n,n)}$ with $2n = m$ when $m$ is even, and $\dim D^{(n+3,n)}$ with $2n + 3 = m$ when $m$ is odd.
+  Similarly define $d_m^{1,2}$.
+  Then, Corollary \ref{D Restrictions} gives
+  \begin{align*}
+    d_m^{0,3} &= d_{m-1}^{1,2}\\
+    d_m^{1,2} &= d_{m-1}^{1,2} + d_{m-1}^{0,3}\\
+    &= d_{m-1}^{0,3} + d_{m-2}^{0,3}.
+  \end{align*}
+  Carefully following this and noting the base cases $d_2^{0,3} = d_2^{1,2} = 1$, one may note that this recurrences proves that $d_m^{1,2} = d_{m+1}^{0,3} = f_n$, where $f_n$ is the $n$th \emph{Fibonacci number}.
+  This matches the dimension our Fibonacci subrepresentations, motivating their definition.\qed
+\end{remark}
+
 We can start our study of $V$ by studying low-dimensional cases.
@@
 
-Now let's prove that $V^3_{\vs\vp}$ is irreducible;
-this has basis $\cbr{\vs\vp\vs\vp}, \cbr{\vs\vp\vp\vp}$, and the following matrices:
+Now we may prove that $V^3_{\vs\vp}$ is irreducible;
+this has basis $\cbr{\prn{\vs\vp\vs\vp}, \prn{\vs\vp\vp\vp}}$, and the following matrices:
 \[
@@
 Hence $V^3_{\vs\vp}$ is irreducible.
-Now we may move on to the general case.
+
+These establish the low-dimensional behavior that we will use as base cases below.
+The rest of this section will proceed first by proving that $V_{\vs\vp}$ and $V_{\vs\vs}$ are irreducible;
+then, we will use combinatorial arguments to prove that these are isomorphic to the correct two-row Specht module quotients.
+
 \begin{proposition}
@@
 
-Knowing this, the restriction statements are clear;
-$\Res V_{\vs\vp}^m \simeq V_{\vp\vp}^{m-1}$ by considering the last $m-2$ transpositions, and $\Res V_{\vs\vp}^{m-1} \simeq V_{\vs\vp}^{m-1} \oplus V_{\vs\vs}^{m-1}$ by considering the first $m-2$.
-Similarly, $\Res V_{\vs\vs}^m \simeq V_{\vs\vp}^{m-1}$ by considering the first $m-2$ transpositions.
-This gives that $V \simeq 3V_{\vs\vp} \oplus 2V_{\vs\vs}$.
-
+Now, we may begin considering restrictions:
+\begin{lemma}
+  The following branching rules hold:
+  \begin{align*}
+    V^{m-1}_{\vp\vp} \simeq \Res V_{\vs\vp}^m &\simeq V^{m-1}_{\vs\vs} \oplus V^{m-1}_{\vs\vp}\\
+    \Res V_{\vs\vs}^m &\simeq V_{\vs\vp}^{m-1}.
+  \end{align*}
+\end{lemma}
+\begin{proof}
+  The first line follows by considering the last two $m-2$ transpositions for the left isomorphism, then the first two for the right isomorphism.
+  This is well-behaved by Appendix \ref{Algebra}.
+
+  Similarly, the second line follows by considering the last $m-2$ transpositions.
+\end{proof}
+This immediately gives a rather strong characterization of $V$.
 \begin{corollary}
@@
 \end{corollary}
-
-Now we may move on and use Young Tableau to characterize $V$.
-Recall that the socle of $D^\lambda$ is given by $\bigoplus\limits_{\mu \xrightarrow{\text{good}} \lambda} D^\mu$,  and that $D^\lambda$ is semisimple iff every $\mu \xrightarrow{\text{normal}} \lambda$ is good.
+\begin{corollary}
+  The representation $V$ decomposes into a direct sum of irreducible representations as follows:
+  \[
+    V \simeq 3V_{\vs\vp} \oplus 2V_{\vs\vs}.
+  \]\qed
+\end{corollary}
+
+Now we may use these in order to apply Young Tableau to characterize $V$.
 \begin{theorem}
@@
 
-  By irreducibility, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda_{\vs\vs}}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\lambda_{\vs\vp}}$ for some diagrams $\lambda_{\vs\vs}$ and $\lambda_{\vs\vp}$.
-  We will show that $\lambda_{\vs\vs} = (n+1,n-2)$ and $\lambda_{\vs\vp} = (n+1,n-1)$.
-
-  First, note that we have \[\Res \; D^{\lambda_{\vs\vs}} \simeq D^{(n,n-2)} \simeq \Res \; D^{(n+1,n-2)}\] and \[\Res \; D^{\lambda_{\vs\vp}} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)}.\]
-  By semisimplicity of $\Res D^{\lambda_{\vs\vs}}$ and $\Res D^{\lambda_{\vs\vp}}$, every normal cell in $\lambda_{\vs\vs}$ and $\lambda_{\vs\vp}$ is good.
-  In particular, the only normal number in $\lambda_{\vs\vs}$ is 1.
-
-  For $\lambda_{\vs\vs}$, the only tableaux which can remove a cell to yield $D^{(n,n-2)}$ are $(n+1,n-2)$, $(n,n-1)$, and $(n,n-2,1)$ as illustrated in Figure \ref{OddRes};
-  we have already seen that $D^{(n,n-1)}$ does not have irreducible restriction, so we are left with $(n+1,n-2)$ and $\lambda = (n,n-2,1)$.
-  We may directly check that $\lambda$ doesn't satisfy this, as we have the following:
-  \begin{align*} 
-    \beta_\lambda(1,2) &= 3 - 2 + (n-2) = n-1\\
-    \beta_\lambda(1,3) &= 3 - 1 + n = n+2\\
-    \beta_\lambda(2,3) &= 2 - 1 + 3 = 4.
-   \end{align*} 
-  At least one of $\beta_\lambda(1,2)$ and $\beta_\lambda(1,3)$ is nonzero, since $\beta_\lambda(1,3) - \beta_\lambda(1,2) = 3 \not\equiv 0 \pmod e$, and hence at least one of $M_2$ and $M_3$ is empty.
-  Hence at least one of 2 or 3 is normal in $(n,n-2,1)$, and $\lambda_{\vs\vs} = (n+1,n-2)$.
-
-  For $\lambda_{\vs\vp}$, we immediately see from Figure \ref{OddRes} that the only option is $(n,n-1)$.
+  By irreducibility, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\mu}$ for some diagrams $\lambda$ and $\mu$.
+  We will show that $\lambda = (n+1,n-2)$ and $\mu = (n+1,n-1)$.
+
+  First, note that we have \[\Res \; D^{\lambda} \simeq D^{(n,n-2)} \simeq \Res \; D^{(n+1,n-2)}\] and \[\Res \; D^{\mu} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)}.\]
+
+  By irreducibility of $\Res D^{\lambda}$, the only normal number in $\lambda$ is 1.
+  Further, the only tableaux which can remove a cell to yield $D^{(n,n-2)}$ are $(n+1,n-2)$, $(n,n-1)$, and $(n,n-2,1)$ as illustrated in Figure \ref{OddRes};
+  we have already seen that $D^{(n,n-1)}$ does not have irreducible restriction, so we are left with $(n+1,n-2)$ and $\varsigma = (n,n-2,1)$.
+  We may directly check that $\varsigma$ doesn't satisfy this, as we have the following:
+  \begin{align*} 
+    \beta_\varsigma(1,2) &= 3 - 2 + (n-2) = n-1\\
+    \beta_\varsigma(1,3) &= 3 - 1 + n = n+2\\
+    \beta_\varsigma(2,3) &= 2 - 1 + 3 = 4.
+   \end{align*} 
+  At least one of $\beta_\varsigma(1,2)$ and $\beta_\varsigma(1,3)$ is nonzero, since $\beta_\varsigma(1,3) - \beta_\varsigma(1,2) = 3 \not\equiv 0 \pmod e$, and hence at least one of $M_2$ and $M_3$ is empty.
+  Hence at least one of 2 or 3 is normal in $\varsigma$, and $\lambda = (n+1,n-2)$.
+
+  For $\mu$, we immediately see from Figure \ref{OddRes} that the only option is $(n,n-1)$.
   \begin{figure}
@@
   We can perform a similar argument for the $V^{2n}$ case, finding now that 
-  \[\Res \; D^{\mu_{\vs\vs}} \simeq D^{(n,n-1)} \simeq \Res \; D^{(n,n)}\] and 
-  \[\Res \; D^{\mu_{\vs\vp}} \simeq D^{(n,n-1)} \oplus D^{(n+1,n-2)} \simeq \Res \; D^{(n+1,n-1)}.\]
-
-  Through a similar process, we see that $\mu_{\vs\vp} = (n+1,n-1)$.
-  We narrow down $\mu_{\vs\vs}$ to one of $(n,n)$ or $\mu := (n,n-1,1)$, and note that
-  \begin{align*} 
-    \beta_\mu(1,2) &= 3 - 2 + (n-1) = n\\
-    \beta_\mu(1,3) &= 3 - 1 + n = n+2\\
-    \beta_\mu(2,3) &= 2 - 1 + 2 = 3
-  \end{align*}
-  and hence at least one of 2 or 3 is normal, $\Res D^{(n,n-1,1)}$ is not irreducible, and $\mu_{\vs\vs} = (n,n)$, finishing our proof.
+  \[\Res \; D^{\lambda'} \simeq D^{(n,n-1)} \simeq \Res \; D^{(n,n)}\] and 
+  \[\Res \; D^{\mu'} \simeq D^{(n,n-1)} \oplus D^{(n+1,n-2)} \simeq \Res \; D^{(n+1,n-1)}.\]
+
+  Through a similar process, we see that $\mu' = (n+1,n-1)$.
+  We narrow down $\lambda'$ to one of $(n,n)$ or $\varpi := (n,n-1,1)$, and note that
+  \begin{align*} 
+    \beta_\varpi(1,2) &= 3 - 2 + (n-1) = n\\
+    \beta_\varpi(1,3) &= 3 - 1 + n = n+2\\
+    \beta_\varpi(2,3) &= 2 - 1 + 2 = 3
+  \end{align*}
+  and hence at least one of 2 or 3 is normal, $\Res D^{\varpi}$ is not irreducible, and $\lambda' = (n,n)$, finishing our proof.
 \end{proof}
@@
 \section{Empirical Results}\label{Empirics Section}
+In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representaitons.
+All data will be generated via tools available on \underline{\href{https://github.com/nataliesstewart/Hecke-Heuristics}{github}}.\footnote{The full URL to the repository is \underline{\href{https://github.com/nataliesstewart/Hecke-Heuristics}{https://github.com/nataliesstewart/Hecke-Heuristics}}.}
 

### 2019-07-28 tex/Rough-Overview.tex

--- 2019-07-26 tex/Rough-Overview.tex
@@
 \usepackage{RepStyle} 
-\usepackage{NatMacros} %********REPLACE WITH MilesMacros TO KILL RELIANCE ON \ifnum AND HAVE INCOMPLETE OUTPUT***********bleh
+\usepackage{NatMacros}
+
+% Emulates \subsection* but doesn't add to ToC (I don't know why amsart is weird 
+\newcommand{\fakesubsection}[1]{
+  \vspace{7pt}
+  \noindent \textbf{#1.}
+}
+
+\makeatletter
+%Table of Contents
+\setcounter{tocdepth}{3}
+
+% Add bold to \section titles in ToC and remove . after numbers
+\renewcommand{\tocsection}[3]{%
+  \indentlabel{\@ifnotempty{#2}{\bfseries\ignorespaces#1 #2\quad}}\bfseries#3}
+% Remove . after numbers in \subsection
+\renewcommand{\tocsubsection}[3]{%
+  \indentlabel{\@ifnotempty{#2}{\ignorespaces#1 #2\quad}}#3}
+\let\tocsubsubsection\tocsubsection% Update for \subsubsection
+%...
+
+\newcommand\@dotsep{4.5}
+\def\@tocline#1#2#3#4#5#6#7{\relax
+  \ifnum #1>\c@tocdepth % then omit
+  \else
+    \par \addpenalty\@secpenalty\addvspace{#2}%
+    \begingroup \hyphenpenalty\@M
+    \@ifempty{#4}{%
+      \@tempdima\csname r@tocindent\number#1\endcsname\relax
+    }{%
+      \@tempdima#4\relax
+    }%
+    \parindent\z@ \leftskip#3\relax \advance\leftskip\@tempdima\relax
+    \rightskip\@pnumwidth plus1em \parfillskip-\@pnumwidth
+    #5\leavevmode\hskip-\@tempdima{#6}\nobreak
+    \leaders\hbox{$\m@th\mkern \@dotsep mu\hbox{.}\mkern \@dotsep mu$}\hfill
+    \nobreak
+    \hbox to\@pnumwidth{\@tocpagenum{\ifnum#1=1\bfseries\fi#7}}\par% <-- \bfseries for \section page
+    \nobreak
+    \endgroup
+  \fi}
+
+\def\l@subsection{\@tocline{2}{0pt}{2.5pc}{5pc}{}}
+\makeatother
+
 \begin{document}
 
-\title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules  of Hecke Algebras}
+\title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules of Iwahori-Hecke Algebras of the Symmetric Group}
 \author[Miles Johnson \& Natalie Stewart]{Miles Johnson \& Natalie Stewart\\
@@
   \begin{abstract}
-  Abstract goes here
+    We consider the Iwahori-Hecke algebra of the symmetric group on $2n + r$ letters with parameter $q \in k^\times$.
+    Let $e$ be the smallest integer such that $\brk{e}_q = 0$, or set $e = \infty$ if none exist.
+    We modify Khovanov's Crossingless Matchings to include $2n$ nodes and $r$ anchors, and prove that the corresponding module is isomorphic to the Specht module $S^{(n+r,n)}$ when the specht module is irreducible and $e > n$.
+    Additionally, we prove heuristics in support of the general case.
+    Lastly, when $e = 5$, we prove an isomorphism between $D^{(n+r,n)}$ with $r \leq 3$ and a subrepresentations of Jordan-Shor's fibonacci representation.
   \end{abstract}
+
+\tableofcontents
+
 \end{titlepage}
@@
 
-\subsection{Crossingless Matchings}
+\fakesubsection{Crossingless Matchings}
+
 \begin{definition}
@@
 
-We will prove that $W := W_{2n+r}^r$ and $S := S^{(n+r,n)'}$ are isomorphic as representations in the case that $e > n + r + 1$.
+Note that the representations $W_{0 + r}^r$ and $S^{(r)}$ are isomorphic to the sign representation; 
+we will prove that $W := W_{2n+r}^r$ and $S := S^{(n+r,n)'}$ are isomorphic as representations in the case that $e > n$ and $S^{(n+r,n)'}$ is irreducible.
 Note that, when $r = 0$, these have the same dimension given by the $n$th catalan number $C_n$.
 
-\subsection{Fibonacci Representation}
-\def\vara{\alpha}
-\def\varb{\beta}
-\def\varc{\gamma}
+\def\vara{\alpha_1}
+\def\varb{\alpha_2}
+\def\varc{\varepsilon_1}
 \def\vard{\delta}
-\def\vare{\varepsilon}
+\def\vare{\varepsilon_2}
 \def\vs{\texttt{*}}
 \def\vp{\texttt{0}}
+\fakesubsection{Fibonacci Representation}
 Now suppose that $e = 5$ and $k$ contains the algebraic number $(-1 - q^2 - q^3)^{3/2}$.
@@
 
+% Acknowledgements should be given section-level heading in toc, subsection-level in text.
+\addcontentsline{toc}{section}{\textbf{Acknowledgements}}
+\fakesubsection{Acknowledgements}
+
 \newpage
+
 \section{Preliminaries on Specht Modules}
-\begin{proposition}
+\subsection{Irreducibility of $S^\lambda$}
+Let $k$ have characteristic $\ell$;
+then, set
+\[
+  p := \begin{cases}
+    \ell & \ell > 0\\
+    \infty & \ell = 0
+  \end{cases}.
+\]  
+For $h$ a natural number, let $\nu_p(h)$ be the $p$-adic evaluation of $h$.
+As a convention, set $\nu_\infty(h) = 0$ for all $h$.
+Define the function $\nu_{e,p} : \NN \rightarrow \cbr{-1} \cup \NN$ by
+\[
+  \nu_{e,p}(h) := \begin{cases}
+    \nu_p(h) & e \mid h\\
+    -1 & e \nmid h
+  \end{cases}.
+\]
+Lastly, let $h_{ab}^\lambda$ be the hook length of node $(a,b)$ in $\brk \lambda$.
+
+\begin{theorem}[James-Mathas]
+  The following are equivalent:
+  \begin{enumerate}
+    \item $S^{\lambda} \simeq D^{\lambda}$.
+    \item $\lambda$ is $e$-restricted and $S^\lambda$ is irreducible.
+    \item $\nu_{e,p}\prn{h_{ab}^\lambda} = \nu_{e,p}\prn{h_{ac}^\lambda}$ for all nodes $(a,b)$ and $(a,c)$ in $\brk \lambda$.
+  \end{enumerate}\qed
+\end{theorem}
+
+\begin{corollary}\label{S irreducibility}
+  Assume $e > 2$ and $n > 0$.
+
   \begin{enumerate}[label={(\roman*)}]
-    \item
-    Suppose that $n,r > 0$.
-    Then, a filtration of $\Res W_{2n + r}^r$ is given by
-    \begin{equation}
-      0 \subset W_{2n + r - 1}^{r-1} \subset \Res \, W_{2n + r}^r \label{Filtration}
-     \end{equation}
-     with $\Res \, W_{2n + r}^r / W_{2n + r - 1}^{r-1} \simeq W_{2n + r - 1}^{r + 1}$. 
-    \item
-      We have the following isomorphism of representations:
-      \begin{equation}
-        W_{2n - 1}^1 \simeq \Res \; W_{2n}^0 \label{0 Restriction}
-       \end{equation}
-  \end{enumerate}
-\end{proposition}
-\begin{proof}
-  \textbf{(i)}
-  Note that we may identify the subrepresentation of $\Res \; W_{2n + r}^r$ having anchor $n$ with $W_{2n + r - 1}^{r-1}$.
-
-  Let $U := \Res \; W_{2n + r}^r / W_{2n + r - 1}^{r - 1}$. 
-  Let $\phi:U \rightarrow W_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $W_{2n + r - 1}^{r + 1}$.
-  It is not hard to verify that this is a well-defined isomorphism of vector spaces, so we must show that it is $\SH$-linear.
-
-  Given a basis vector $w_j$ with arc $(i,2n + r)$, $\phi$ is clearly compatible with $T_{i'}$ with $i' \neq i,i-1$.
-  Further, it's easy to verify that $\phi$ is compatible with $T_{i}$ and $T_{i-1}$, as actions on one anchor were designed for this deformation.
-  When there are anchors $(i,i+1)$, then $\phi(T_iw_j) = T_i\phi(w_j) = 0$, and similar for $T_{i -1}$.
-  Hence $\phi$ is an isomorphism of representations, and the statement is proven.
-
-  \textbf{(ii)}
-  This follows with the above proof, defining $W_{2n - 1}^{-1} := 0$
-\end{proof}
-
-\begin{lemma}
-  Suppose $n,r > 0$.
-  Then, we may characterize the socle of $\Res \, D^\lambda$ as follows:
-  \[
-    \soc\prn{\Res \, D^{(n+r,n)'}} \simeq \begin{cases}
-      D^{(n + r - 1,n)'} & e \mid r+2\\
-      D^{(n + r,n-1)'} & e \nmid r+2, \; e \mid r\\
-      D^{(n+r-1,n)'} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
-    \end{cases}
-  \]
-\end{lemma}
-\begin{proof}
-  This amounts to computations of the hook lengths $\beta(1,2)$ and $\gamma(1,2)$:
-  \begin{align*}
-    \beta_\lambda(1,2) &= r + 2\\
-    \gamma_\lambda(1,2) &= r
-  \end{align*}
-  Since $2$ is the largest removable number, $D^{(n+r,n-1)'} \subset D^{(n+r,n)'}$ iff $e \nmid r + 2$.
-  Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)'} \subset D^{(n+r,n)'}$ iff 1 is good iff $e \nmid r$
-\end{proof}
-
-\begin{lemma}\label{S irreducibility}
-  \begin{enumerate}[label={(\roman*)}]
-    Assume $e > 2$ and $n > 0$.
     \item Suppose $e > n$.
@@
   \end{enumerate}  
-\end{lemma}
+\end{corollary}
 \begin{proof}
@@
 \end{proof}
+
+In the case that $\lambda = (n+r,n)$ and $e$ satisfy hypothesis \eqref{S irreducibility}.(i), say that $\lambda$ is \emph{$e$-top-indivisible}.
 
@@
   then, $h_{n-e+1,1} - h_{n-e+1,2} \geq 1$, giving reducibility.
+\end{proof}
+
+\subsection{Branching}
+\begin{theorem}[Kleshchev-Brundan]
+  We have the following isomorphisms of vector spaces
+  \begin{align*}
+    \Homarg{\SH'}{S^\mu,\Res D^\lambda} 
+    &\simeq \begin{cases}
+      k & \mu \xrightarrow{\text{normal}} \lambda\\
+      0 & \text{otherwise}
+    \end{cases}\\
+    \Homarg{\SH'}{D^\mu,\Res D^\lambda} 
+    &\simeq \begin{cases}
+      k & \mu \xrightarrow{\text{good}} \lambda\\
+      0 & \text{otherwise}
+    \end{cases}
+  \end{align*}
+  and $\Res D^\lambda$ is semisimple if and only if every normal number in $\lambda$ is good.\qed
+\end{theorem}
+
+\begin{corollary}
+  Suppose $n,r > 0$.
+  Then, we may characterize the socle of $\Res \, D^\lambda$ as follows:
+  \[
+    \soc\prn{\Res \, D^{(n+r,n)'}} \simeq \begin{cases}
+      D^{(n + r - 1,n)'} & e \mid r+2\\
+      D^{(n + r,n-1)'} & e \nmid r+2, \; e \mid r\\
+      D^{(n+r-1,n)'} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
+    \end{cases}
+  \]
+\end{corollary}
+\begin{proof}
+  This amounts to computations of the hook lengths $\beta(1,2)$ and $\gamma(1,2)$:
+  \begin{align*}
+    \beta_\lambda(1,2) &= r + 2\\
+    \gamma_\lambda(1,2) &= r
+  \end{align*}
+  Since $2$ is the largest removable number, $D^{(n+r,n-1)'} \subset D^{(n+r,n)'}$ iff $e \nmid r + 2$.
+  Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)'} \subset D^{(n+r,n)'}$ iff 1 is good iff $e \nmid r$
 \end{proof}
@@
 \section{Crossingless Matchings and Specht Modules}
-\subsection{Preliminaries on Crossingless Matchings}
+\subsection{Irreducibility of $M$}
 \begin{lemma}
@@
 \end{lemma}
-\begin{proof}
+\begin{proof}[Proof 1.]
   Consider the matrix $A = \bigoplus (1 + T_i)$ having kernel $K$.
@@
 \end{proof}
-
-\subsection{Correspondence}
 \begin{proposition}
@@
 
-\begin{corollary}
-  Suppose $n,r > 0$ and $e > n + 1$.
-  Then, the sequence \eqref{Filtration} is a composition series of $\Res \, W_{2n + r}^r$.\qed
-\end{corollary}
+\subsection{Correspondence}
+\begin{proposition}\;
+
+  \begin{enumerate}[label={(\roman*)}]
+    \item
+    Suppose that $n,r > 0$.
+    Then, a filtration of $\Res W_{2n + r}^r$ is given by
+    \begin{equation}
+      0 \subset W_{2n + r - 1}^{r-1} \subset \Res \, W_{2n + r}^r \label{Filtration}
+     \end{equation}
+     with $\Res \, W_{2n + r}^r / W_{2n + r - 1}^{r-1} \simeq W_{2n + r - 1}^{r + 1}$. 
+    \item
+      We have the following isomorphism of representations:
+      \begin{equation}
+        W_{2n - 1}^1 \simeq \Res \; W_{2n}^0 \label{0 Restriction}
+       \end{equation}
+  \end{enumerate}
+    When the case is type (i) from the irreduibility lemma, this is a composition series.
+\end{proposition}
+\begin{proof}
+  \textbf{(i)}
+  Note that we may identify the subrepresentation of $\Res \; W_{2n + r}^r$ having anchor $n$ with $W_{2n + r - 1}^{r-1}$.
+
+  Let $U := \Res \; W_{2n + r}^r / W_{2n + r - 1}^{r - 1}$. 
+  Let $\phi:U \rightarrow W_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $W_{2n + r - 1}^{r + 1}$.
+  It is not hard to verify that this is a well-defined isomorphism of vector spaces, so we must show that it is $\SH$-linear.
+
+  Given a basis vector $w_j$ with arc $(i,2n + r)$, $\phi$ is clearly compatible with $T_{i'}$ with $i' \neq i,i-1$.
+  Further, it's easy to verify that $\phi$ is compatible with $T_{i}$ and $T_{i-1}$, as actions on one anchor were designed for this deformation.
+  When there are anchors $(i,i+1)$, then $\phi(T_iw_j) = T_i\phi(w_j) = 0$, and similar for $T_{i -1}$.
+  Hence $\phi$ is an isomorphism of representations, and the statement is proven.
+
+  \textbf{(ii)}
+  This follows with the above proof, defining $W_{2n - 1}^{-1} := 0$
+\end{proof}
 
@@
 \fi
+
+\subsection{Kernels and Further Work}
+\begin{lemma}\label{Represented}
+  Let $w_j$ be the basis vector with anchors $1,\dots,r$ and all arcs of maximal length.
+  Suppose $w \in K \backslash \cbr 0$.
+  Then, $w_j$ is represented in $w$.
+\end{lemma}
+\begin{proposition}
+  Suppose $e = n + r + 1$.
+  Then $K$ is nontrivial.
+\end{proposition}
 
@@
 
-\section{Acknowledgements}
-
+\bibliography{RepBib}
+\iffalse
 \begin{thebibliography}{9}
@@
 \end{thebibliography}
+\fi
 

### 2019-07-28 tex/Drafts/Draft-1.tex
Empirics on kernels, some more revisions, some comments on kernels

@@
   \begin{figure}[b]
-    \[
+    \begin{adjustbox}{width=\textwidth}
       \begin{tabular}{l l}
@@
       \end{tabular}
-    \]
+  \end{adjustbox}
 
@@
     \def\cbasisspacing{5mm}
+    \begin{adjustbox}{width=\textwidth}
     $\cbr{
@@
        \end{gathered}}$ 
+     \end{adjustbox}
        \caption{The basis for $M_5^1$.}
@@
   \begin{figure}
-  \[
+  \begin{adjustbox}{width=\textwidth}
     \Action{6}{1/6, 2/5, 3/4}{2}{1/6, 2/3, 4/5 }{q^{1/2}} \hspace{20pt} 
     \IsoAction{8}{1/8, 2/7, 3/4, 5/6}{3}{1/8, 2/5, 3/4, 6/7}{q^{1/2}}
-  \]
-  \[
+  \end{adjustbox}
+  \begin{adjustbox}{width=\textwidth}
     \Action{4}{1/4, 2/3}{2}{1/4,2/3}{(1 + q)} \hspace{20pt}
     \IsoAction{6}{1/6, 2/5, 3/4}{3}{1/6, 2/5, 3/4}{(1 + q)}
-  \]
+\end{adjustbox}
   \caption{The correspondence between the action of $(1 + T_2)$ on $w'_5 \in M^0_6$ and the action of $q^{-1}(1 + T_3)(1 + T_4)(1 + T_2)$ on the corresponding vector in $M^0_8$ having arc $(3,4)$ first, then on $w'_2 \in M^0_4$.
@@
   \begin{figure}
-    \begin{align*}
+  \[
       \cbr{
@@
       \end{gathered} 
-    }&\longrightarrow \begin{gathered}
+    }\longrightarrow \begin{gathered}
       \ydiagram{5,3}
-      \end{gathered}\\
-      \cbr{
+  \end{gathered}\]
+      \[\cbr{
         \begin{gathered}
@@
         \end{gathered}
-      }&\longrightarrow
+      }\longrightarrow
       \begin{gathered}
@@
       \end{gathered}
-    \end{align*}
+    \]
       \caption{
@@
 
-\newpage
+The following computations are done in characteristic 0.
+If $p < \infty$ is mentioned, then the computation is done over the algebraic extension of $\FF_p$ by roots of the polynomials $x^{2e} - 1$ and $x^2 - \tau$.
+
+\begin{remark}
+  These results are restricted by two things; first and less fixably, this was computed in Magma, a closed source language with bugs that could not be resolved in certain cases.
+  Second, the memory necessary to store the Hecke algebra via basis elements and structure constants grows with $(n!)^3$;
+  this is probitively large when $m > 7$.
+  An implimentation as a quotient by a free algebra or only specifying multiplication by generators may fix this, however, this is not possible with the Magma language, and the closed source renders modification of the language impossible.\qed
+\end{remark}
+
+We give in Figure \ref{Fib Data} some isomorphisms between $M/K$ and $V$ for $e \geq n + r + 1$ with $p = \infty$;
+all but one of these are cases with $e > n + r + 1$, so $K=0$ and this is an isomorphism with our crossingless matchings representation.
+The case $n = 1$, $r = 3$ gives an example of an isomorphism not proven in general, but proven via our computation.
+All of these computations are done for $q$ a primitive 5th root of unity in the algebraic extension of the Cyclotomic field $\QQ(\zeta_{10})$ by a root of the polynomial $x^2 - \tau$.
+
+We give in Figure \ref{Empirical Kernel} some data supporting a conjecture concerning sign subrepresentations of $M_{2n + r}^r$.
+The computations to support this were done over $\CC$ with $qq$ a 5th root of unity.
+
+\begin{figure}
+\iffalse
+\def\tho{\Phi_3(q^{1/2})}
+\def\tht{\brk{3}_{q^{1/2}}}
+\def\to{q^{1/2}\brk{2}_{q^{1/2}}}
+Define the following coefficients:
+\begin{align*}
+  \tho &:= q^{3/2} + 1\\
+  \tht &:= q^{3/2} + q + q^{1/2} + 1\\
+  \to &:= q + q^{1/2}
+\end{align*}
+\fi
+
+\def\tho{q^{3/2} + 1}
+\def\tht{\brk{4}_{q^{1/2}}}
+\def\to{q^{1/2}\prn{q^{1/2} + 1}}
+\begin{align*}
+  \varphi_6^0, \varphi_5^1 &= \begin{bmatrix}
+    0 & 0 & -\tho & 0 & 0\\
+    0 & -\tho & \tht & 0 & 0\\
+    0 & 0 & \tht & 0 & -\tho\\
+    -\tht & \tht & \to & 0 & \tht\\
+    \tht & 0 & \tht & -\tht & 0
+  \end{bmatrix}\\
+  \varphi_5^3 &= \begin{bmatrix}
+    -\to & \tht & q^{1/2}\\
+    q^{1/2} & q^{3/2} & 0\\
+    0 & -q - 1
+  \end{bmatrix}  \hspace{30pt} 
+  \varphi_4^0 = \begin{bmatrix}
+    0 & -\tht\\
+    -1 & 1
+  \end{bmatrix}\\
+  \varphi_3^1 &= \begin{bmatrix}
+    0 & -\tht\\
+    \to & -\to
+  \end{bmatrix} \hspace{27pt}
+  \varphi_4^2 = \begin{bmatrix}
+    0 & \tht & 0\\
+    1 & -1 & 0\\
+    -1 & 0 & 1
+  \end{bmatrix}
+\end{align*}
+\caption{We define representations $\varphi_{2n + r}^r:M_{2n + r}^r/K_{2n + r}^r \rightarrow V^{2n + r}_{s}$, where $s = \vs\vs$ if $r = 0,3$ and $s = \vs\vp$ otherwise.
+These are given with respect to the basis on $M_{2n + r}^r$ induced by the increasing lexicographic order basis on $M_{2n + 2r}^0$ and the quotient $M_{2n + 2r}^0 \twoheadrightarrow M_{2n + r}^r$.
+These are also given with respect to the basis on $V$ given by increasing lexicographic order $\vs < \vp$.
+  }\label{Fib Data}
+\end{figure}
+
+\begin{figure}
+  \[
+    \ENRGrid{13/7}{3/1,7/1,11/1,2/2,6/2,10/2,1/3,5/3,9/3}
+  \]
+  \caption{
+    Illustration of the modules $M_{2n + r}^r$ having sign submodules for $p = \infty$ and $e = 4$.
+    The value $n + r + 1$ is filled in the squares, and modules having sign submodules are colored magenta.
+    For $p = \infty$ and $2n + r \leq 14$, it has been verified, through a combination of theorems here and empirical computations, that $K_{2n + r}^r$ is nontrivial if and only if $e | n+r+1$ and $e < n$.
+  }\label{Empirical Kernel}
+\end{figure}
+
 \appendix

### 2019-07-28 tex/kernel.tex
Empirics on kernels, some more revisions, some comments on kernels

@@
 	Let $w$ be an arbitrary vector in $W_{2n+r}^r$. I claim that if $w\in \cap\text{ker}(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero.
-
 \end{proposition}
@@
 		\]
-    \caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $W_{8}^2$ and $i=2$.{\color{magenta} I made the last of these a bit taller so that the anchors weren't close to touching the arc.}}
-		\label{Action}
+    \caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $W_{8}^2$ and $i=2$.{\color{magenta} I made the last of these a bit taller so that the anchors weren't close to touching the arc.
+    \LARGE NOTE: I've commented out the Action label because it is multiply defined.
+    I'm not sure why each figure is labeled with the same label, or how this compiles on your machine.
+  }
+  }
+		%\label{Action}
 	\end{figure}
@@
 \section{Defining the kernel for $e=n+r+1$}
-
 In this section we will fully characterize $\cap\text{ker}(1+T_i)$ when $e=n+r+1$.
@@
 	}
-	\label{Action}
+	%\label{Action}
 \end{figure}

### 2019-07-28 tex/Drafts/Draft-1.tex
Literature review

@@
   \usepackage{../RepStyle}
+
+  % Colors links
+  \hypersetup{
+  colorlinks,
+  citecolor=blue,
+  linkcolor=black!30!magenta,
+  urlcolor=blue}
+
   \usepackage{../NatMacros}
@@
 
+  \begingroup
+  \hypersetup{linkcolor=black} % no colored hyperlinks in toc
   \tableofcontents
+  \endgroup
 
@@
 \section{Introduction} 
-  Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices with $2n + r \geq 2$, let $\SH = \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k^\times$ having square root $q^{1/2}$, and let $\cbr{T_i}$ be the reflections generating $\SH$.
+  Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices with $2n + r \geq 2$, let $\SH := \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k^\times$ having square root $q^{1/2}$, and let $\cbr{T_i}$ be the reflections generating $\SH$.
+
   Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of $m$. 
@@
 
-  {\color{orange} Literature review and motivation goes here.}
-
-  \normalsize
+  \vspace{5pt}
+  When $q = 1$, the Hecke algebra $\SH$ is isomorphic to the group algebra $k\brk{S_{2n+r}}$.
+  For $q$ a prime power, let $G := \GL_{2n+r}(q)$ be the general linear group over a field with $q$ elements, let $B := B(q)$ be the Borel subgroup of $G$, and let $1_B$ be the trivial representation of $k\brk{B}$.
+  Then, it is a well known result that the endomorphism algebra $\End_{k\brk{G}} \prn{\Ind_B^G(1_B)}$ is isomorphic to the Hecke algebra $\SH$.\cite{Mathas-book}
+  Hence the representation theory of the Hecke algebra generalizes the representation theory of the symmetric group, and informs the representation theory of the general linear group.
+
+  It is a classical result that $\SH$ is semisimple precisely when $e > 2n + r$, in which case the irreducible representations of $\SH$ are given by \emph{Specht modules} $S^\lambda$, which are indexed by the partitions $\lambda$ of $2n + r$.
+  Further, $\SH$ admits a cellular basis with cell modules given by $S^\lambda$.
+  In particular, these admit quotients $D^\lambda$ such that the set $\cbr{D^\lambda \mid D^\lambda \neq 0, \lambda \vdash n}$ is a complete set of pairwise-nonisomorphic irreducible $\SH$-modules.
+  This set is indexed by the partitions $\lambda \vdash n$ which are $e$-restricted.\cite{Murphy1,Murphy2}
+
+  These representations $D^\lambda$ are well-defined, but many properties of them are unknown.
+  For instance, the dimension of these modules is unknown outside of some special cases.\cite{Mathas-book}
+  However, there does exists an algorithm due to Lascoux, Leclerc, and Thibon (verified by Ariki) which produces the decomposition matrices of the Iwahori-Hecke Algebra $\SH_{\CC,q}(S_{2n + r})$ for $q$ an $e$th root of unity.\cite{Ariki,LLT}
+
+  Further, there are theorems, called \emph{modular branching theorems}, characterizing the socle and semisimplicity of the restriction $\Res D^\lambda$ to a subalgebra generated by $2n + r - 2$ simple transpositions.
+  These are originally due to Kleshchev in the group algebra case, and were generalized to the Hecke algebra by Brundan.\cite{Brundan,Kleshchev}
+
+  These constructions tend to be well-defined but complicated and often intractable.
+  We aim to give simple realizations of some particular $S^\lambda$ and $D^\lambda$ which expose this structure while being intuitive and simple to manipulate.
+
+  \vspace{5pt}
   Throughout the text, we will refer to partitions of $2n + r$;
   identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
-  Identify each of these with a subset $\brk \lambda \subset \NN^2$ as defined in Kleshchev, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.
-
-  Fixing some partition $\lambda$, for $1 \leq i \leq j \leq l$, let $\beta(i,j)$ be the hook length
-  \[
-    \beta(i,j) = \lambda_i - \lambda_j + \sum_{t = i}^j a_t.
-  \]
-  Then, adopting Kleshchev's terminology, $j$ is normal in $\lambda$ if $\beta(i,j) \not\equiv 0 \pmod e$ for all $i < j$, and $j$ is good if it is the largest normal number (these are stronger conditions than generally necessary).
-
-  Let $S^{(n+r,n)}$ be the Specht module corresponding to the young diagram with two rows with height difference $r$, and let $D^{(n+r,n)}$ be the corresponding irreducible quotient.
-  The purpose of this writing is to characterize these representation via an isomorphism with two graphical representations of $\SH$.
+  Identify each of these with a subset $\brk \lambda \subset \NN^2$ as is standard, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.\cite{Kleshchev}
+
+  Note that we follow the convention of Murphy and Kleshchev, which is dual to the conventions of Dipper, James, and Mathas;
+  one may translate our results to the latter convention by transposing all partitions.\cite{Kleshchev,Mathas-book,Murphy1}
+
+  Fixing some partition $\lambda$, for $1 \leq i \leq j \leq l$, let $\beta_\lambda(i,j)$ and $\gamma_\lambda$ be the quantities
+  \begin{align*}
+    \beta_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i}^j a_t\\
+    \gamma_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i+1}^j a_t.
+  \end{align*}
+  Results due to Kleshchev and Brundan refer to \emph{normal} and \emph{good} numbers;
+  note that 1 is always normal, and that $j$ is normal when $\beta_\lambda(i,j) \not\equiv 0 \pmod e$ for all $i \leq j$.
+  Recall that $j$ is good iff $j$ is normal and $\gamma_\lambda(j,j') \not\equiv 0 \pmod e$ for all $j' \geq j$ normal.\cite{Brundan,Kleshchev}
+  These are the combinatorial properties necessary to state and use branching theorems.
+
+  Throughout this paper, we analyze the \emph{two-row partitions} $(n+r,n) \vdash 2n + r$ and their corresponding modules $S^{(n+r,n)}$ and $D^{(n+r,n)}$.
 
@@
   Note that the representations $M_{0 + r}^r$ and $S^{(r)}$ are isomorphic to the sign representation; 
-  we will prove that $M_{2n+r}^r$ and $S^{(n+r,n)}$ are isomorphic as representations in the case that $e > n$ and $S^{(n+r,n)}$ is irreducible.
-  Note that, when $r = 0$, these have the same dimension given by the $n$th Catalan number $C_n$.
+  we will prove that $M_{2n+r}^r$ and $S^{(n+r,n)}$ are isomorphic as representations in the case that $e > n + r + 1$.
+  Additionally, we will prove that $M_{2n + r}^r$ is irreducible everywhere that $e > n$ and $S^{(n+r,n)}$ is irreducible.
+  We will conjecture that $M_{2n + r}^r \simeq S^{(n+r,n)}$ with $e$ unrestricted as well.
 

### 2019-07-28 tex/Drafts/Draft-1.tex
Bibliography hrefs

@@
   \usepackage{../RepStyle} 
-
   % Colors links
@@
 In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representaitons.
-All data will be generated via tools available on \underline{\href{https://github.com/nataliesstewart/Hecke-Heuristics}{github}}.\footnote{The full URL to the repository is \underline{\href{https://github.com/nataliesstewart/Hecke-Heuristics}{https://github.com/nataliesstewart/Hecke-Heuristics}}.}
+All data will be generated via tools available on \href{https://github.com/nataliesstewart/Hecke-Heuristics}{github}.\footnote{The full URL to the repository is \href{https://github.com/nataliesstewart/Hecke-Heuristics}{https://github.com/nataliesstewart/Hecke-Heuristics}.}
 
@@
 
+\newpage
 \appendix

### 2019-07-28 tex/Drafts/Draft-1.tex
Abstract edit

@@
   \newcommand\@dotsep{4.5}
-  \def\@tocline#1#2#3#4#5#6#7{\relax
+  \def\@ocline#1#2#3#4#5#6#7{\relax
     \ifnum #1>\c@tocdepth % then omit
@@
   \author[Miles Johnson \& Natalie Stewart]{Miles Johnson \& Natalie Stewart\\
-    Mentor Oron Propp\\
-  Project Suggested by Roman Bezrukavnikov\\ \; \\
+    Mentor : Oron Propp\\
+  Project Suggested by : Roman Bezrukavnikov\\ \; \\
   July 31, 2019
@@
     \begin{abstract}
-      We consider the Iwahori-Hecke algebra of the symmetric group on $2n + r$ indices with parameter $q \in k^\times$.
-      Let $e$ be the smallest integer such that $\brk{e}_q = 0$, or set $e = \infty$ if none exist.
-      We modify Khovanov's crossingless matchings to include $2n$ nodes and $r$ anchors, and prove that the corresponding module is isomorphic to the Specht module $S^{(n+r,n)}$ when $e > n + r + 1$.
-      Additionally, we prove heuristics in support of the general case.
-      Lastly, when $e = 5$, we prove an isomorphism between $D^{(n+r,n)}$ with $r \leq 3$ and some subrepresentations of Jordan-Shor's Fibonacci representation.
+      We consider the Iwahori--Hecke algebra of the symmetric group on $2n + r$ letters with parameter $q$.
+      Let $e$ be the smallest positive integer such that the $q$-number $\brk{e}_q = 0$, or set $e = \infty$ if none exist.
+      We modify Khovanov's crossingless matchings to include $2n$ ``nodes'' and $r$ ``anchors,'' and prove in the case $e > n + r + 1$ that the associated module is isomorphic to the Specht module $S^{(n+r,n)}$ which corresponds to the partition $(n + r,n) \vdash 2n + r$.
+      We then give heuristics in support of the general case, including explicit composition series for $e = n + r + 1$ and for $2n + r \leq 6$. 
+      Lastly, when $e = 5$, we prove an isomorphism between the irreducible quotient $D^{(n+r,n)}$ with $r \leq 3$ and some subrepresentations of Jordan--Shor's Fibonacci representation.
+      We provide explicit transition matrices between this representation and the crossingless matchings representation for almost all cases where $2n + r \leq 6$.
     \end{abstract}

### 2019-07-29 tex/kernel.tex
First Actual Draft

--- 2019-07-28 tex/kernel.tex
@@
 See Figure 1.
+
+  If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, $M(a,b)$ will still refer to those nodes, but will not be a sub-matching.
+For any other $a,b$, we define $M(a,b)$ to be an element of the representation with no nodes.
 \end{definition}
@@
 \end{proposition}
-{\color{red} Need to note that some of these may not be sub-matchings}
 
@@
 \begin{lemma}
-	Take a basis element $\beta\in W_{2n+r}^r$. Suppose the leftmost anchor in $\beta$ is at index $b$. Define $a_j$ such that $\beta(a_j)=a_{j-1}+1$ and $\beta(a_1)=1$ for all $j$ such that $a_j<b$.
+	Take a basis element $\beta\in W_{2n+r}^r$.
+Suppose the leftmost anchor in $\beta$ is at index $b$, or let $b=2n+r+1$ if there is no anchor.
+Define $a_j$ such that $\beta(a_j)=a_{j-1}+1$ and $\beta(a_1)=1$ for all $j$ such that $a_j<b$.
 
@@
 \vspace{5mm}
+Lastly, we will need a small combinatorial result.
+
+\begin{lemma}
+	Suppose $n>b\geq a>0$ and $e>n$. Then $$Q_{n-a}Q_b-Q_{n-b-1}Q_{a-1}=Q_{n}Q_{b-a}$$
+\end{lemma}
+
+\begin{proof}
+	If $b=1$, the only possibility for $a$ is 1, in which reduces to lemma 2.4.
+
+	Suppose the lemma is true for all $\tilde{b}<b+1$. Then for $a< b$ we have
+
+	$$Q_{n-a}Q_b -Q_{n-b-1}Q_{a-1}=Q_{n}Q_{b-a}$$
+
+	$$Q_1Q_{n-a}Q_b-Q_1Q_{n-b-1}Q_{a-1}=Q_1Q_{n}Q_{b-a}$$
+
+	from lemma 2.4, we have
+
+	$$Q_{n-a}(Q_{b+1}+Q_{b-1})-(Q_{n-b}+Q_{n-b-2})Q_{a-1}=Q_{n}(Q_{b-a-1}+Q_{b-a+1})$$
+
+	and from the inductive hypothesis we have
+
+	$$Q_{n-a}Q_{b+1}-Q_{n-b}Q_{a-1}=Q_{n}Q_{b-a+1}$$
+
+	as desired.
+
+	For $a=b$ we have
+
+	$$Q_{n-b}Q_b -Q_{n-b-1}Q_{b-1}=Q_{n}$$
+
+	$$Q_1Q_{n-b}Q_b-Q_1Q_{n-b-1}Q_{b-1}=Q_1Q_{n}$$
+
+	from lemma 2.4, we have
+
+	$$Q_{n-b}(Q_{b+1}+Q_{b-1})-(Q_{n-b}+Q_{n-b-2})Q_{b-1}=Q_1Q_{n}$$
+
+	$$Q_{n-b}Q_{b+1}-Q_{n-b-2}Q_{b-1}=Q_1Q_{n}$$
+
+	as desired.
+
+	For $a=b+1$, we continue:
+
+	$$Q_1Q_{n-b}Q_{b+1}-Q_1Q_{n-b-2}Q_{b-1}=Q_1Q_1Q_{n}$$
+
+	$$(Q_{n-b-1}+Q_{n-b+1})Q_{b+1}-Q_{n-b-2}(Q_{b}+Q_{b-2})=(1+Q_2)Q_{n}$$
+
+	So by the inductive hypothesis
+
+	$$Q_{n-b-1}Q_{b+1}-Q_{n-b-2}Q_{b}=Q_{n}$$
+
+	as desired, and the proof is finished by induction.
+
+\end{proof}
+
+\vspace{5mm}
 We are now ready to prove existence of a kernel element.
@@
 	\vspace{5mm}
-	To prove the inductive step for both (i) and (ii), we must split into cases:
+	To prove the inductive step for both (i) and (ii), we must split into cases.
+Note that if $E_\beta$ is defined to be the pre-image of $\beta$ under the action of $(1+T_i)$, $E_{\beta(a,b)}$ is defined to be the pre-image of $\beta(a,b)$ under action of $(1+T_{i-a+1})$:
 
@@
 	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, and that $\exists s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\beta(s)=t$.
-Also suppose the leftmost anchor is at some index $u>t$.
+Also suppose the leftmost anchor is at some index $u>t$, or that there are no anchors.
 Then we have a sub-matching $\beta(s,t)$, and by lemma 3.6 $E_\beta\subset Y_\beta$.
@@
 	\vspace{5mm}
-	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, the leftmost anchor is at a position $u>i+1$, and $\not\exists s,t$ such that $\beta(s)=t$ and $s<i<t-1$.
+	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, the leftmost anchor is at a position $u>i+1$ or there are no anchors, and $\not\exists s,t$ such that $\beta(s)=t$ and $s<i<t-1$.
 Lemma $3.7$ characterizes all $\alpha\in E_\beta$.
@@
 	See figure 9 for an example of this equality.
+Note that if $e=n+r+1$, $Q_{n+r}$ is the only zero component in the right side of this equation, so proving this equation is sufficient to prove case three.
 	\\
 
-	We will prove this equality through yet another inductive proof, this time inducting on the number of top level humps to the left of the rightmost anchor.
+	We will prove this equality through yet another inductive proof, this time inducting on the number of top level humps, including the leftmost anchor.
 
-	Formally, as we have in earlier lemmas, we will define $a_j$ by $a_1:=\beta(1)$, $a_j:=\beta(a_{j-1}+1)$. Then $a_b=u$ for some $b>1$.
+	Formally, as we have in earlier lemmas, we will define $a_j$ by $a_1:=\beta(1)$, $a_j:=\beta(a_{j-1}+1)$.
+Then define $b_\beta$ such that $a_{b_\beta}=u$ if there is an anchor or $a_{b_\beta}=2n+r$ otherwise.
+We induct on $b_\beta$.
+	\\
 
+	If $b_\beta=1$, we must be in $W_2^0$ to be in case 3 (otherwise $s<i<t-1$ for some $s,t$ where $\beta(s)=t$), which is trivially satisfied. 
+	\\
+
+%	For our base case we will prove $b=2$. This means either $a_1+1$ is an anchor, or $\beta(a_1+1)=2n+r$. 
+%	\\
+%	
+%	First base case:
+%	
+%	If $a_1+1$ is an anchor, to still be in case 3 we must have $i=1$ and $a_1=2$.
+In this case, lemma 3.7 gives that there is only one element in $E_\beta$, and that element is $\alpha$ defined by $\alpha(4,2n+r)=\beta(4,2n+r)$, $\alpha(1)=1$, and $\alpha(2)=3$.
+Then $x_\beta=Q_{n+r-1}x_\beta(3,2n+r)=Q_{n+r-1}\beta(4,2n+r)$ and $x_\alpha=x_{\alpha(2,2n+r)}=Q_{n+r-2}x_{\beta(4,2n+r)}$.
+So, using lemma 2.4, we have $(q+1)x_\beta(q)+q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(4,2n+4)}(q)Q_{n+r}$ as desired.
+%	\\
+%	
+%	Second base case: 
+%	
+%	If $\beta(a_1+1)=2n+r$, to be in case 3 we need either $a_1=2$ or $a_1=2n+r-2$.
+In both cases lemma 3.7 gives only one element $\alpha$ in $E_\beta$.
+In the first case $x_\beta=Q_{n+r-1}x_{\beta(3,2n+r)}=Q_{n+r-1}x_{\beta(4,2n+r-1)}$, and $x_\alpha=x_{\alpha(2,2n+r-1)}=Q_{n+r-2}x_{\beta(4,2n+r-1)}$ so again using lemma 2.4 $(q+1)x_\beta(q)+q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(4,2n+r)}(q)Q_{n+r}$ as desired.
+In the second case $x_\beta=\frac{Q_{n+r-1}...Q_{1}}{Q_1...Q_{n+r-2}}x_{\beta(2,2n+r-3)}=Q_{n+r-1}x_{\beta(2,2n+r-3)}$, and, using corollary 3.3, $x_\alpha=\frac{Q_{n+r-2}...Q_{1}}{Q_1...Q_{n+r-3}}x_{\alpha(2,2n+r-3)}=Q_{n+r-2}x_{\beta(2,2n+r-3)}$, so again using lemma 2.4, we have $(q+1)x_\beta(q)+q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(1,2n+r-2)}(q)Q_{n+r}$ as desired, and all base cases are proved.
+%	\\
+
+	Suppose for all basis elements $\alpha$ such that $b_\alpha<b_\beta$, the equality holds.
+Suppose $i\not=1$.
+Then $a_1<i$ and lemma 3.7 gives that there is a unique $\upsilon\in E_\beta$ such that $\upsilon(1)\not=a_1$.
+Thus we have the following equality:
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$
+
+	$$(x_{\beta(1,a_1)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}})((1+q)x_{\beta(a_1+1,2n+r)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_{\alpha(a_1+1,2n+r)}(q))$$
+
+	Define $Y_\beta$ as before with respect to the sub-matching $\beta(a_1+1,2n+r)$.
+Then $\alpha\in E_\beta$, $\alpha\not=\upsilon$ implies $\alpha\in Y_\beta$.
+By our inductive hypothesis, we have that
+	$$(1+q)x_{\beta(a_1+1,2n+r)}(q)+\sum_{\alpha\in E_{\beta(a_1+1,2n+r)},\alpha\not=\beta(a_1+1,2n+r)}q^{1/2}x_{\alpha}(q)=$$
+	$$
+	-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}}$$
+
+	By lemma 3.5, $\alpha\subset Y_\beta$, $\alpha\in E_\beta$ if and only if $\alpha(a_1+1,2n+r)\in E_{\beta(a_1+1,2n+r)}$. This implies:
+
+	$$(1+q)x_{\beta(a_1+1,2n+r)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_{\alpha(a_1+1,2n+r)}(q)=$$
+
+	$$-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}}$$
+
+	So, combining with the aforementioned equality, we have
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$
+
+	$$(x_{\beta(1,a_1)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}})(-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}})=$$
+
+	$$(x_{\beta(1,a_1)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}})(-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}})(\frac{Q_{(i-1)/2-1}...Q_{(i-1-a_1)/2}}{Q_{(i-1)/2-1}...Q_{(i-1-a_1)/2}})=$$
+
+	$$-q^{1/2}x_{\beta(1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}(\frac{Q_{n+r-a_1/2}Q_{(i-1)/2}}{Q_{(i-1-a_1)/2}})$$
+	\\
+
+	Separately, note that $\upsilon$ is defined by $\upsilon(2,a_1-1)=\beta(2,a_1-1)$, $\upsilon(a_1+1,i-1)=\beta(a_1+1,i-1)$, $\upsilon(i+2,2n+r)=\beta(i+2,2n+r)$, and $\upsilon(1)=i+1$, $\upsilon(a_1)=i$.
+Thus we may determine $x_\upsilon$, again utilizing corollary 3.2:
+
+	$$x_\upsilon=x_{\beta(i+2,2n+r)}x_{\upsilon(2,i)}\frac{Q_{n+r-1}...Q_{n+r-(i+1)/2}}{Q_1...Q_{(i-1)/2}}=$$
+
+	$$x_{\beta(i+2,2n+r)}(x_{\beta(2,a_1-1)}x_{\upsilon(a_1,i)}\frac{Q_{(i-1)/2-1}...Q_{(i-1)/2-(a_1-2)/2}}{Q_1...Q_{(a_1-2)/2-1}})\frac{Q_{n+r-1}...Q_{n+r-(i+1)/2}}{Q_1...Q_{(i-1)/2}}=$$
+
+	$$x_{\beta(i+2,2n+r)}(x_{\beta(1,a_1)}x_{\beta(a_1+1,i-1)}\frac{Q_{(i-1)/2-1}...Q_{(i-1)/2-(a_1-2)/2}}{Q_1...Q_{(a_1-2)/2-1}})\frac{Q_{n+r-1}...Q_{n+r-(i+1)/2}}{Q_1...Q_{(i-1)/2}}=$$
+
+	$$x_{\beta(i+2,2n+r)}x_{\beta(1,i-1)}\frac{Q_{n+r-1}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}(\frac{Q_{n+r-(i+1)/2}Q_{a_1/2-1}}{Q_{(i-1-a_1)/2}})$$
+	\\
+
+	Adding this into our previous equation, we have:
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=$$
+
+	$$-q^{1/2}x_{\beta(1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}(\frac{Q_{n+r-a_1/2}Q_{(i-1)/2}-Q_{n+r-(i+1)/2}Q_{a_1/2-1}}{Q_{(i-1-a_1)/2}})$$
+
+	Applying lemma 3.8 to the portion of the equation above in parenthesis, the above is equivalent to
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}$$
+
+	as desired. Note that if $e\geq n+r+1$ the only term above that can be zero is $Q_{n+r}$ (by corollary 3.3). Thus we have proved the inductive step for the case where $i\not=1$.
+
+	\vspace{5mm}
+	If $i=1$, we instead look at the sub-matchings $\beta(1,a_{(b_\beta-1)})$, $\beta(a_{(b_\beta-1)}+1,2n+r)$.
+Again lemma 3.7 gives that there is a unique $\upsilon\in E_\beta$ such that $\upsilon(a_{(b_\beta-1)}+1)\not=\beta(a_{(b_\beta-1)}+1)$.
+Taking $Y_\beta$ with respect to the sub-matching $\beta(a_{(b_\beta-1)}+1,a_{b_\beta})$ again we have that $\alpha\in E_\beta$, $\alpha\not=\upsilon$ implies $\alpha\in Y_\beta$.
+Thus, following the same logic as before, we arrive at the following equality:
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$
+
+	$$(x_{\beta(a_{(b_\beta-1)}+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}})(-q^{1/2}x_{\beta(3,a_{(b_\beta-1)})}(q)Q_{a_{(b_\beta-1)}/2})=$$
+
+	$$-q^{1/2}x_{\beta(3,2n+r)}\frac{Q_{n+r-1}Q_{a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$
+	\\
+
+	Again, we know the structure of $\upsilon$ from lemma 3.7.
+Suppose for now that $a_{b_\beta}$ is not an anchor, so it is $2n+r$.
+Then $\upsilon$ is defined by $\upsilon(3,a_{(b_\beta-1)})=\beta(3,a_{(b_\beta-1)})$, $\upsilon(a_{(b_\beta-1)}+2,2n+r-1)=\beta(a_{(b_\beta-1)}+2,2n+r-1)$, and $\upsilon(1)=2n+r$, $\upsilon(2)=a_{(b_\beta-1)}+1$.
+So we may again find $x_\upsilon$:
+
+	$$x_\upsilon=x_{\upsilon(2,2n+r-1)}=x_{\beta(3,a_{(b_\beta-1)})}x_{\beta(a_{(b_\beta-1)}+2,2n+r-1)}\frac{Q_{n+r-2}...Q_{n+r-1-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}}=$$
+
+	$$x_{\beta(3,a_{(b_\beta-1)})}x_{\beta(a_{(b_\beta-1)}+1,2n+r)}\frac{Q_{n+r-2}...Q_{n+r-1-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}}=x_{\beta(3,2n+r)}\frac{Q_{n-r-1-a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$
+
+	Alternatively, if $a_{b_\beta}$ is an anchor, the definition of $\upsilon$ is now $\upsilon(3,a_{b_\beta}-1)=\beta(3,a_{b_\beta}-1)$, $\upsilon(a_{b_\beta}+1,2n+r)=\beta(a_{b_\beta}+1,2n+r)$, and $\upsilon(1)=1$, $\upsilon(2)=a_{b_\beta}$, so we have:
+
+	$$x_\upsilon=x_{\upsilon(2,2n+r)}=x_{\beta(3,a_{(b_\beta-1)})}x_{\beta(a_{b_\beta}+1,2n+r)}\frac{Q_{n+r-2}...Q_{n+r-1-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}}=x_{\beta(3,2n+r)}\frac{Q_{n-r-1-a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$
+
+	so for our purposes $x_\upsilon$ is the same in either case.
+
+	Incorporating into the above equation, we have:
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=$$
+
+	$$-q^{1/2}x_{\beta(3,2n+r)}\frac{Q_{n+r-1}Q_{a_{(b_\beta-1)}/2}-Q_{n-r-1-a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$
+
+	By lemma 3.8, this is simply $-q^{1/2}x_{\beta(3,2n+r)}Q_{n+r}$ as desired, and we have finished proving case 3.
+	\\
+
+	\item The only cases we have not yet dealt with are those where either $1$ is an anchor or $\beta(1)=2n+r$. These are those cases related to our inductive hypothesis (ii).
+
+	To not be in case 1 or 2, we must have that there are no anchors between index 1 and $i$, and that there is no integer $s$ such that $1<s<i<\beta(s)-1$.
+It follows from the same argument that proved lemma 3.6 that there exists exactly one $\upsilon\in E_\beta$ such that $\upsilon(1)\not=\beta(1)$.
+Define $N$ to be $2n+r$ if 1 is an anchor, or $2n+r-1$ if 1 is not an anchor.
+Then, defining $Y_\beta$ with respect to the sub-matching $\beta(2,N)$, we have that $\alpha\in E_\beta, \alpha\not=\upsilon$ if and only if $\alpha(2,N)\in E_{\beta(2,N)}$.
+Note that for $E_{\beta(2,N)}$ we may apply the inductive hypothesis from case 3, so we have:
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$
+
+	$$(1+q)x_{\beta(2,N)}(q)+\sum_{\alpha\in E_{\beta(2,N)},\alpha\not=\beta(2,N)}q^{1/2}x_{\alpha}(q)=$$
+
+	$$-q^{1/2}x_{\beta(2,i-1)}x_{\beta(i+2,N)}\frac{Q_{n+r-1}...Q_{n+r-i/2}}{Q_1...Q_{(i/2-1}}$$
+
+	As in case 3, we can also determine $x_\upsilon$.
+$\upsilon$ is defined by $\upsilon(2,i-1)=\beta(2,i-1)$, $\upsilon(i+2,N)=\beta(i+2,N)$, $\upsilon(1)=i$, and $\upsilon(i+1)=2n+r$ if 1 is not an anchor or $i+1$ if 1 is an anchor, and we have:
+
+	$$x_\upsilon=x_{\beta(2,i-1)}x_{\upsilon(i+2,N)}\frac{Q_{n+r-1}...Q_{n+r-i/2}}{Q_1...Q_{i/2-1}}$$
+
+	Thus we have
+
+	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=$$
+
+	$$-q^{1/2}x_{\beta(2,i-1)}x_{\beta(i+2,N)}\frac{Q_{n+r-1}...Q_{n+r-i/2}}{Q_1...Q_{(i/2-1}}(1-1)=0$$
+
+	as desired, and the last case is proved.
 	\end{enumerate}
+
+It should be noted that the induction for all of the above cases are codependent, but they only depend on the inductive hypotheses for $2n'+r'<2n+r$.
+So, since our base case holds for all the cases that apply to it, induction holds and the proposition is proved.
+
 \end{proof}
 
+\begin{corollary}
+	If $e=n+r+1$, $W_{2n+r}^r$ is reducible, and has a unique sign subrepresentation.
+\end{corollary}
+
 \end{document}

### 2019-07-29 tex/Drafts/Draft-1.tex

@@
   \title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules of Iwahori-Hecke Algebras of the Symmetric Group}
-  \author[Miles Johnson \& Natalie Stewart]{Miles Johnson \& Natalie Stewart\\
+  \author[Miles Johnson and Natalie Stewart]{Miles Johnson and Natalie Stewart\\
     Mentor : Oron Propp\\
@@
       We modify Khovanov's crossingless matchings to include $2n$ ``nodes'' and $r$ ``anchors,'' and prove in the case $e > n + r + 1$ that the associated module is isomorphic to the Specht module $S^{(n+r,n)}$ which corresponds to the partition $(n + r,n) \vdash 2n + r$.
-      We then give heuristics in support of the general case, including explicit composition series for $e = n + r + 1$ and for $2n + r \leq 6$. 
+      We then give heuristics in support of the general case, including explicit composition series for $e = n + r + 1$ and almost all cases where $2n + r \leq 6$. 
       Lastly, when $e = 5$, we prove an isomorphism between the irreducible quotient $D^{(n+r,n)}$ with $r \leq 3$ and some subrepresentations of Jordan--Shor's Fibonacci representation.
@@
   \fakesubsection{Crossingless Matchings}
-
+  The following definition modifies the crossingless matchings defined by Khovanov.\cite{Khovanov}
   \begin{definition}
@@
 
-    In order for this to be a $\SH$-module, endow this with the action given by Figure \ref{Action}; 
-    if a ``loop'' is created, scale by $q+1$, if a loop is not created and the action involves fewer than 2 anchors, deform into a new crossingless matching and scale by $q^{1/2}$, and if it involves two anchors, scale by 0.
+    For convenience, given a basis element $w_j \in M_{2n + r}^r$ and integers $1 \leq a,b \leq 2n + r$, define the $w_j(a) := b$ if $(a,b)$ is an arc in $M$, and $w_j(a) := a$ if $a$ is an anchor in $M$.
+
+    In order to endow this with an $\SH$-action, consider some basis element $w_j$ and some element $(1 + T_i)$ of $\SH$.
+    The elements $\cbr{1} \cup \cbr{1 + T_i | 1 \leq i < 2n + r}$ generate $\SH$, so it is sufficient to define the action of $1 + T_i$ on $w_j$.
+
+    If $w_j$ has arc $(i,i+1)$, define $(1 + T_i)w_j := (1 + q)w_j$.
+    If $w_j$ has anchors $W(i) = i$ and $W(i+1) = i+1$, define $(1 + T_i)w_j := 0$.
+    If $w_j$ has anchor $W(i) = i$ and arc $W(i+1) = b$, define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$, $w_l(b) = b$, and all other arcs agree with $w_j$.
+    If $w_j$ has arcs $W(i) = a$ and $W(i+1) = b$, then define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$,$w(a) = b$, and all other acts agree with $w_j$. 
     We verify that this is well-defined in appendix \ref{Cross Relations}.
   \end{definition}
-  {\color{orange} Fix Definition with isotopy.}
 
@@
     \caption{Illustration of the actions $(1 + T_i)w_{\abs{M^2_6}}$.
-      In general, we act by deleting loops, deforming into a new crossingless matching, and scaling by either $q^{1/2}$, $(q + 1)$, or 0.
+      In general, we act by deleting loops, isotoping onto a new crossingless matching, and scaling by either $q^{1/2}$, $(q + 1)$, or 0.
     }
@@
   \end{figure}
+
+  We may alternately define $M_{2n + r}^r$ topologically;
+  fix $2n + r$ distinct points $a_1,\dots,a_{2n + r}$ points along $\RR \times \cbr{0} \subset \RR^2$ and $r$ distinct points $b_1,\dots,b_r$ along $\RR \times \cbr{1}$, and define $M_{2n + r}^r$ to have basis given by the isotopy classes of $n + r$ paths connecting the points $a_1,\dots,a_{2n+r},b_1,\dots,b_r$ such that no distinct $b_i,b_j$ are connected by a path.
+
+  We will take some basis element $w_j \in M_{2n +r}^r$ and define the action $(1 + T_i)w_j$.
+  To do so, map $w_j$ through the natural embedding $\RR \times \brk{0,1} \hookrightarrow \RR \times \brk{\frac{1}{2},1}$, and form the figure $w_j^i$ by adjoining the lines connecting $a_l$ and $a_l + \prn{0,\frac{1}{2}}$ for all $l \neq i,i+1$ as well as paths from $a_i$ to $a_{i+1}$ and $a_i + \prn{0,\frac{1}{2}}$ to $a_{i+1} + \prn{0,\frac{1}{2}}$.
+  This has either 0 or 1 path components which do not intersect $\RR \times \cbr{0,1}$;
+  these form ``loops.''
+
+  Take the figure $\tilde w_j^i$ without this component.
+  If $\tilde w_j^i$ is not isotopic to some $w_l$, then define $(1 + T_i)w_j := 0$.
+  If $\tilde w_j^i$ is isotopic to some $w_l$, define $(1 + T_i)w_j := (1 + q)w_l$ if $w_j^i$ has a loop and $(1 + T_i)w_j := q^{1/2}w_l$ otherwise.
+  This process is illustrated in Figure \ref{Action}.
+
+  \begin{remark}
+    This definition gives a graphical calculus for working with our module.
+    It should be clear that, if $w_j^i$ has a loop then $w_l(i) = i+1$ and $w_l = w_j$.
+    Further, this easily defines an arbitrary composition:
+    \[
+      (1 + T_{i_1})\cdots(1 + T_{i_\ell})w_j = q^{(\ell - t)\frac{1}{2}}(1 + q)^tw_l
+    \]
+    if the figure we make  via $(1+T_{i_1})\cdots(1+T_{i_\ell})$ is isotopic to $w_l$ after removing $t$ loops.
+  \end{remark}
 
@@
   \fakesubsection{Acknowledgements}
-  {\color{orange} Acknowledgements go here.}
+  The authors thank Professor Roman Bezrukavnikov for suggesting this project, as well as Dr. Slava Gerovitch for his support via organization of the SPUR+ program.
+  We would also like to thank Professor David David Jerison, Professor Ankur Moitra for their role in SPUR+ as well as general and mathematical advice.
+  We would also thank Professor Alexander Kleshchev for his mathematical guidance concerning branching theorems.
+  Lastly, we would like to express our gratitude to our mentor Oron Propp for his help and advice in both acquiring background knowledge and in executing the mathematics in this paper;
+  this project would not be possible without him.
 
@@
 \section{Empirical Results}\label{Empirics Section}
-In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representaitons.
-All data will be generated via tools available on \href{https://github.com/nataliesstewart/Hecke-Heuristics}{github}.\footnote{The full URL to the repository is \href{https://github.com/nataliesstewart/Hecke-Heuristics}{https://github.com/nataliesstewart/Hecke-Heuristics}.}
-
-The following computations are done in characteristic 0.
-If $p < \infty$ is mentioned, then the computation is done over the algebraic extension of $\FF_p$ by roots of the polynomials $x^{2e} - 1$ and $x^2 - \tau$.
+In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representations.\cite{Github}
 
 \begin{remark}
-  These results are restricted by two things; first and less fixably, this was computed in Magma, a closed source language with bugs that could not be resolved in certain cases.
+  These results are restricted by two things; first and with less recourse, this was computed in Magma, a closed source language with bugs that could not be resolved in certain cases.
   Second, the memory necessary to store the Hecke algebra via basis elements and structure constants grows with $(n!)^3$;
-  this is probitively large when $m > 7$.
-  An implimentation as a quotient by a free algebra or only specifying multiplication by generators may fix this, however, this is not possible with the Magma language, and the closed source renders modification of the language impossible.\qed
+  this is prohibitively large when $m \geq 7$.
+  An implementation as a quotient by a free algebra or only specifying multiplication by generators may fix this, however, this is not possible with the Magma language, and the closed source renders modification of the language impossible.
 \end{remark}
@@
 We give in Figure \ref{Empirical Kernel} some data supporting a conjecture concerning sign subrepresentations of $M_{2n + r}^r$.
-The computations to support this were done over $\CC$ with $qq$ a 5th root of unity.
+The computations to support this were done over $\CC$ with $q$ a primitive 5th root of unity.
 
@@
 
-\subsection{Verifying the Crossingless Matchings Representaitons}
+\subsection{Verifying the Crossingless Matchings Representations}
 \label{Cross Relations}
@@
     Hence we may equivalently check that $(h-g)w = q(T_i - T_{i+1})$.
-    This is illustrated in Figure \ref{braid1arc}.
-    \begin{figure}[b]
-  \[
-    \GeneralizedNAction{5}{1/2,3/4}{1}{5/1}{3/4}{2/1, 1/2,2/3}{1/4,2/3}{5/1}{q^{3/2}}
-    \hspace{20pt}
-    \GeneralizedNAction{5}{1/2,3/4}{1}{5/1}{3/4}{1/1, 2/2,1/3}{1/2,3/4}{5/1}{q(q+1)}
-  \]
-  \[
-    \NAction{6}{1/6,2/5,3/4}{1/1,2/2,1/3}{1/2,3/4,5/6}{q^{3/2}}
-    \hspace{20pt}
-    \NAction{6}{1/6,2/5,3/4}{2/1,1/2,2/3}{1/6,2/3,4/5}{q^{3/2}}
-  \]
-  \[
-    \GeneralizedZeroAction{4}{3/4}{2}{1/1,2/2}{.5}{1}
-    \hspace{20pt}
-    \GeneralizedNAction{4}{3/4}{2}{1/1,2/2}{.5}{2/1, 1/2,2/3}{2/3}{1/1,4/2}{q(q+1)}
+    In fact, $hw = q(1 + T_i)$ and $gw = q(1 + T_j)$ by Figure \ref{braid1arc}, giving compatibiliy.
+    \begin{figure}
+\[
+  \begin{gathered}\EmptyNAction{3}{1/1,2/2,1/3}\end{gathered}
+  \longsquigrightarrow
+  \begin{gathered}\EmptyNAction{3}{1/2}\end{gathered}
+  \hspace{50pt}
+  \begin{gathered}\EmptyNAction{3}{2/1,1/2,2/3}\end{gathered}
+  \longsquigrightarrow
+  \begin{gathered}\EmptyNAction{3}{2/1}\end{gathered}
+  \hspace{50pt}
+  \begin{gathered}\EmptyNAction{4}{1/1,3/2}\end{gathered}
+  \longsquigrightarrow
+  \begin{gathered}\EmptyNAction{4}{3/1,1/2}\end{gathered}
 \]
   \caption{
-    Here we verify in small cases that $hw = qT_i$ and $gw = qT_{i+1}$.
-    These 6 cases cover the situations that there is an arc among the indices $i,i+1,i+2$, that there isn't and there are not two arcs, and that there are two arcs.
+    The following give visual intuition for isotopy between $(1 + T_i)(1 + T_{i-1})(1 + T_i)w_j$ and $q(1 + T_i)$,between $(1 + T_{i+1})(1 + T_i)(1 + T_{i+1})w_j$ and $q(1 + T_i)$, and between $(1 + T_i)(1+T_j)w_l$ and $(1 + T_j)(1 + T_i)w_l$.
+    In all cases, these isotopies imply equality between the elements listed.
   }
@@
 \]
-and hence we simply need to verify that $(1 + T_i)$ and $(1 + T_j)$ commute, which the reader may easily check.
+and hence we simply need to verify that $(1 + T_i)$ and $(1 + T_j)$ commute, as shown in Figure \ref{braid1arc}
 
@@
 
-\section{Miscellaneous Algebra Facts}\label{Algebra}
+\section{Conjugate Subalgebras}\label{Algebra}
 Throughout the text, for some representation $V$, we refer to $\Res_{\SH(S_{l})}^{\SH(S_m)} V$ without specifying exactly which subalgebra $\SH(S_{l})$.

### 2019-07-29 tex/Drafts/Draft-1.tex
Low 2n+r transitions, readded kernel_comments, added action isotopy macro to milesMacros

@@
       We modify Khovanov's crossingless matchings to include $2n$ ``nodes'' and $r$ ``anchors,'' and prove in the case $e > n + r + 1$ that the associated module is isomorphic to the Specht module $S^{(n+r,n)}$ which corresponds to the partition $(n + r,n) \vdash 2n + r$.
-      We then give heuristics in support of the general case, including explicit composition series for $e = n + r + 1$ and almost all cases where $2n + r \leq 6$. 
+      We then give heuristics in support of the general case, including explicit composition series for $e = n + r + 1$ and for $2n + r \leq 6$. 
       Lastly, when $e = 5$, we prove an isomorphism between the irreducible quotient $D^{(n+r,n)}$ with $r \leq 3$ and some subrepresentations of Jordan--Shor's Fibonacci representation.
-      We provide explicit transition matrices between this representation and the crossingless matchings representation for almost all cases where $2n + r \leq 6$.
+      We provide explicit transition matrices between this representation and the crossingless matchings representation for $2n + r \leq 6$.
     \end{abstract}
@@
   Second, the memory necessary to store the Hecke algebra via basis elements and structure constants grows with $(n!)^3$;
-  this is prohibitively large when $m \geq 7$.
+  this is prohibitively large when $m > 7$.
   An implementation as a quotient by a free algebra or only specifying multiplication by generators may fix this, however, this is not possible with the Magma language, and the closed source renders modification of the language impossible.
@@
 The computations to support this were done over $\CC$ with $q$ a primitive 5th root of unity.
+
+It is known that, for small $2n + r$, each specht module $S^{(n+r,n)}$ has a composition series of length 2.
+We give in Figures \ref{Composition series e=3} through \ref{Composition series e=6} the map $M_{2n + r}^r \twoheadrightarrow U_{2n + r}^r$, which conjecturally illustrates the quotient $S^{(n+r,n)} \twoheadrightarrow U_{2n + r}^r$ for all $2n + r \leq 7$.
 
@@
     \tht & 0 & \tht & -\tht & 0
+  \end{bmatrix}\\
+  \varphi_6^2 &= \begin{bmatrix}
+    0 & 0 & - q - 1 & 0 & 0 & 0 & 0 & 0\\
+    0 & -q - 1 & -q^{1/2} & 0 & 0 & 0 & 0 & 0\\
+    0 & q + 1 & 0 & q^{1/2} & 0 & 0 & 0 & 0\\
+    0 & 0 & -q^{1/2} & 0 & 0 & 0 & -q^2 - 1 & 0\\
+    q^{1/2} & -q^{1/2} & -\brk{3}_{q^{1/2}} & 0 & 0 & 0 & -q^{1/2} & 0\\
+   -q^{1/2} & q^{1/2} & 0 & \brk{3}_{q^{1/2}} &0 & 0 & 0 & q^{1/2}\\
+   -q^{1/2} & 0 & -q^{1/2} & 0 & q^{1/2} & 0 & 0 & 0\\
+    q^{1/2} & 0 & 0 & 0 & -q^{1/2} & -\brk{3}_{q^{1/2}} & 0 & -q^{1/2}
   \end{bmatrix}\\
@@
 \end{align*}
+
 \caption{We define representations $\varphi_{2n + r}^r:M_{2n + r}^r/K_{2n + r}^r \rightarrow V^{2n + r}_{s}$, where $s = \vs\vs$ if $r = 0,3$ and $s = \vs\vp$ otherwise.
@@
   \[
+    \ENRGrid{13/7}{2/1,5/1,8/1,11/1,1/2,4/2,7/2,10/2}
+  \]\[
     \ENRGrid{13/7}{3/1,7/1,11/1,2/2,6/2,10/2,1/3,5/3,9/3}
@@
   \caption{
-    Illustration of the modules $M_{2n + r}^r$ having sign submodules for $p = \infty$ and $e = 4$.
+    Illustration of the modules $M_{2n + r}^r$ having sign submodules for $p = \infty$ and $e = 3,4$ respectively.
     The value $n + r + 1$ is filled in the squares, and modules having sign submodules are colored magenta.
@@
   }\label{Empirical Kernel}
+\end{figure}
+
+\def\qqo{\alpha}
+\def\tto{\beta}
+\def\vtv{\gamma}
+\def\fft{\delta}
+\def\fto{\varepsilon}
+\setcounter{MaxMatrixCols}{20}
+
+\begin{figure}
+\begin{align*} 
+  \pi_{3,3}^1 = \pi_{3,4}^0 &=  
+\begin{bmatrix}
+  1 & 1
+\end{bmatrix}\\
+\pi_{3,5}^1 = \pi_{3,6}^0&=  
+\begin{bmatrix}
+  1 & 0 & 0 & 0 & 0\\
+  0 & 0 & 1 & 1 & 0\\
+  0 & 1 & 0 & 1 & 0\\
+  0 & 0 & 0 & 1 & 1
+\end{bmatrix}\\
+\pi_{3,6}^4&=  
+\begin{bmatrix}
+  -1 & -1 & 0 & 1 & 1
+\end{bmatrix}\\
+\pi_{3,7}^3&=  
+\begin{bmatrix}
+ 1 & 0 &-1 &-1 & 1 & 0 & -1 & -1 & 0 & 0 & 0 & 0 & 1 & 1
+\end{bmatrix}\\
+\pi_{3,7}^1&=  
+\begin{bmatrix}
+ 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 &-1\\
+ 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
+ 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
+ 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 &-1\\
+ 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
+ 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
+ 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 &-1\\
+ 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 &-1\\
+ 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 1\\
+ 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 1\\
+ 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 &-1\\
+ 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 &-1\\
+ 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1
+\end{bmatrix}
+\end{align*}
+\caption{The maps of representations $\pi_{e,2n+r}^r:M_{2n + r}^r \twoheadrightarrow U_{2n+r}^r$ for $e = 3$.}
+\label{Composition series e=3}
+\end{figure}
+
+\begin{figure}
+\begin{align*}
+  \pi_{4,4}^2&=  
+\begin{bmatrix}
+  1 & \qqo & 1
+\end{bmatrix}\\
+\pi_{4,4}^1&=  
+\begin{bmatrix}
+  1 & \frac{1}{2}\qqo & \frac{1}{2}\qqo & 1 & \frac{1}{2}\qqo
+\end{bmatrix}\\
+\pi_{4,6}^2 &=
+\begin{bmatrix}
+  1& 0& 0& 0& 0& 0& \qqo & 1& 0\\
+  0& 1& 0& 0& 0& -1& -1& -\qqo &0\\
+  0& 0& 1& 0& 0& \qqo& 0 &1 &0\\
+  0& 0& 0& 1& 0& 0& -1& -\qqo &-1\\
+  0& 0& 0& 0& 1& \frac{1}{2}\qqo& \frac{1}{2}\qqo &1 &\frac{1}{2}\qqo
+\end{bmatrix}\\
+\pi_{4,6}^0 &=
+\begin{bmatrix}
+  \qqo & 1 & 1 & \qqo & 1
+\end{bmatrix}\\
+\pi_{4,7}^1 &=
+\begin{bmatrix}
+1& 0& 0& 0& \frac{1}{2}\qqo& 0& -\frac{1}{2}& -\frac{1}{2}& 0& 0& 1& 1/2& \qqo& \frac{1}{2}\\
+0& 1& 0& 0& -1& 0& \frac{1}{2}\qqo& \frac{1}{2}\qqo& 1& 0& \qqo& \frac{1}{2}\qqo& -1 & \frac{1}{2}\qqo\\
+0& 0& 1& 0& -1& 0& 0& \qqo& 1& 0& -\qqo& 0& -1& 0\\
+0& 0& 0& 1& \qqo& 0& 0& -1& -\qqo& 0& 1& -1& 0& 0\\
+0& 0& 0& 0& 0& 1& \frac{1}{2}\qqo& \frac{1}{2}\qqo& 0& 0& 0& \frac{1}{2}\qqo& -1& \frac{1}{2}\qqo\\
+0& 0& 0& 0& 0& 0& 0& 0& 0& 1& -\frac{1}{2}\qqo& \frac{1}{2}\qqo& 1& \frac{1}{2}\qqo
+\end{bmatrix}\\
+\end{align*}
+\caption{The maps of representations $\pi_{e,2n+r}^r:M_{2n + r}^r \twoheadrightarrow U_{2n+r}^r$ for $e = 4$.}
+\label{Composition series e=4}
+\end{figure}
+
+\begin{figure}
+\begin{align*}
+  \pi_{5,5}^3 &=
+\begin{bmatrix}
+  1 & \tto & \tto & 1
+\end{bmatrix}\\
+\pi_{5,6}^2 &=
+\begin{bmatrix}
+  \tto& \tto& 1& 1& \tto+1& \tto & \tto & \tto & 1
+\end{bmatrix}\\
+\pi_{5,7}^3 &=
+\begin{bmatrix}
+1& \tto& \tto& 1& 0& 0& 0& 0& 0& 0& 0& 0& 0& 0\\
+0& 0& 0& 0& 1& \tto& \tto& 1& 0& 0& 0& 0& 0& 0\\
+1& 0& 0& 0& 0& 0& 0& 0& \tto& \tto& 1& 0& 0& 0\\
+\tto& \tto& 1& 0& 1& \tto+1& \tto& 0& \tto& \tto& 0& 1& 0& 0\\
+-\tto-1& -\tto& -\tto& 0& -\tto& -\tto-1& -\tto-1& 0& -\tto-1& -\tto-1& 0& 0& 1& 0\\
+0& 0& 1& 0& 0& 0& \tto& 0& 0& \tto& 0& 0& 0& 1
+\end{bmatrix}\\
+\pi_{5,7}^1 &=
+\begin{bmatrix}
+1& \qqo& \qqo& \qqo& -\tto& \qqo& -\tto& \qqo& -\tto& 1& \qqo& \qqo& \qqo& -\tto
+\end{bmatrix}\\
+\pi_{6,6}^4 &=
+\begin{bmatrix}
+  1 & \vtv & 2 & \vtv & 1 
+\end{bmatrix}\\
+\pi_{6,7}^3 &=
+\begin{bmatrix}
+  \vtv & 2 & \vtv & 1 & 1 & 2\vtv & 3 & \vtv & 2 & 2\vtv & 2 & 2 & \vtv & 1
+\end{bmatrix}\\
+\pi_{6,7}^5 &=
+\begin{bmatrix}
+  1 & \fft & \fto & \fto & \fft & 1
+\end{bmatrix}
+\end{align*}
+\caption{The maps of representations $\pi_{e,2n+r}^r:M_{2n + r}^r \twoheadrightarrow U_{2n+r}^r$ for $e = 5,6$.}
+\label{Composition series e=6}
 \end{figure}

### 2019-07-29 tex/kernel_comments.tex
Low 2n+r transitions, readded kernel_comments, added action isotopy macro to milesMacros

--- 2019-07-28 tex/kernel.tex
@@
 \section{Defining the kernel for $e=n+r+1$}
+{\color{magenta} This is more of a thing to discuss when integrating into the draft, but this needs to be restructured in order to fit in.}
 In this section we will fully characterize $\cap\text{ker}(1+T_i)$ when $e=n+r+1$.
@@
 
+{\color{magenta} May just be a me thing, but I find the amount of vspace and the centering on the proposition statements to be visually confusing.}
+
 \vspace{5mm}
@@
 Let $w\in\cap\text{ker}(1+T_i)$.
-WLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition 2.2).
+WLOG {\color{magenta} assume} the rainbow element $R$ has coordinate 1 in $w$ (by proposition 2.2).
 	\\
@@
 \end{proposition}
-
+{\color{magenta} This may be a stylistic thing, but the phrase ``I claim'' in a written proof feels weird to me.}
 \vspace{5mm}
@@
 
+{\color{magenta} I'm not going to mention it again, but this vspacing is visually confusing to me.
+I've been meaning to bring this up because I'm not exactly sure how to use this;
+I generally use it sparingly (not often and $\leq$ line height) to separate large chunks in proofs.
+It's fair if you like it this way, but I'd be a bit confused reading this.}
+
 \vspace{5mm}
 The first statement of this proposition says that, given an element of the kernel $w$, we can write the coordinate of any basis element $\beta$ in $w$ as a rational function of $q$ as long as $Q_1...Q_{n+r-1}\not=0$.
+{\color{magenta} Is this a bit redundant? This just seems like the whole statement.}
 
@@
 \end{enumerate}
-
+{\color{magenta} I feel this would be better in a paragraph than an enumerated list;
+it isn't complicated enough that a list really does anything but give an informal tone IMO.}
 \vspace{10mm}
@@
 	By proposition 2.2 the rainbow element has coordinate 1 in $w\in W_{2n+r}^r$. 
+  {\color{magenta} Wasn't this already stated in the proposition?}
   By proposition 2.3 the element $R_1:=R_{L,n+r-1}$ has coordinate $Q_{n+r-1}$ in $w$.
 Then $R_1(3,2n+r)$ is the rainbow element in  $W_{2(n-1)+r}^r$, so the element $R_2$ defined by $R_2(1,2)=R_1(1,2)$, $R_2(3,2n+r)=R_{L,n+r-2}\in W_{2(n-1)+r}^r$ has coordinate $Q_{n-1}Q_{n-2}$.
-Generally, define $R_i$ by $R_i(1,2(i-1))=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r)=R_{L,2n+r-i}$.
-Then the coefficient of $R_i$ is $Q_{n+r-1}...Q_{n+r-i}$.
-These elements are shown in figure 5.
+  {\color{magenta} the element $R_2$ defined by submatchings $R_2(1,2) := R_1(1,2)$ and $R_2(3,2n + r) := $\dots}
+  Generally, define $R_i$ by $R_i(1,2(i-1))=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r)=R_{L,2n+r-i}$. Then the coefficient of $R_i$ is $Q_{n+r-1}...Q_{n+r-i}$. These elements are shown in figure 5.
 
@@
 	Now, I claim that this method can be applied to any rainbow sub-matching in exactly the same way. In other words, extraneous nodes add no complexity to this argument.
+  {\color{magenta} If it is significant enough to be stated as ``I claim'', it may be better put in the claim* environment, or as a lemma.}
 
@@
 
+  {\color{magenta} Suppose inductively that\dots}
   To turn this into an inductive proof, suppose statements (i) and (ii) are true for all representations with $2n'+r'<2n+r$ nodes.
@@
 	So, by induction, the proposition holds.
+  {\color{magenta} Two comments on the inductive arument:
+    \begin{enumerate}
+      \item IMO inductive arguments flow better when they begin with the base case.
+      \item I don't think that the verbose treatment of the induction argument is necessary or helpful;
+        one actually needs to use the word induction once.
+        I think a good structure is ``We will prove indutively that \dots For the base case $2n + r = 2$ \dots suppose \textit{indutive hypothesis}\dots qed'', which doesn't require one to remind the reader that they're reading an inductive argument.
+    \end{enumerate}
+}
+\end{proof}
 
-\end{proof}
+{\color{magenta} I do like this proof above, and I like the clear sectioning.
+I think it might even be nice to see a \textit{Step n} at the beginning of each step as well as a small vspace for separation.}
 
@@
 The following few corollaries will help to simplify some later proofs.
+{\color{magenta} ``some later arguments'' (``proofs'' feels like it breaks the tone).}
 
@@
 
+  {\color{magenta} the align* environment would help this a lot.}
 	$$x_\beta(q)=x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}}=$$
@@
 	This proves the inductive step, so with base case $j=1$ the corollary holds.
-
+  {\color{magenta} I don't think this needs to be said.}
 \end{proof}
@@
 \begin{corollary}
-	$\beta\in W_{2n+r}^r$, then $x_\beta(q)\not=0$ if $e>n+r$.
+  {\color{magenta} if $\beta \in W_{2n + r}^r$ is a basis element\dots} $\beta\in W_{2n+r}^r$, then $x_\beta(q)\not=0$ if $e>n+r$.
 \end{corollary}
@@
 
+{\color{magenta} I like this section a lot, and especially how the argument unfolds with the corollaries.
+One comment I have is that the separation between this and the next section would be handled much better with subsections than a horizontal line.}
+
 \vspace{5mm}
 \noindent\rule{16.5cm}{0.4pt}
+{\color{magenta} The rest of this seems technical. I'll pick it back up tomorrow morning.}
 
@@
 In the third line we act to the right of an anchor, so if another element without that anchor is sent to that element, it must fix the anchor as shown in the fourth line.
+    {\color{magenta} This will be handled when we fully assemble the draft, but the figures should be made to fit the margins via adjustbox if possible}
   }

### 2019-07-29 tex/Drafts/Draft-1.tex
Added comments directory

@@
 We can start our study of $V$ by studying low-dimensional cases.
-First, note that $V_{\vs\vp}^2$ is the sign representation $D^{(2)}$ and $V_{\vs\vp}^2$ is the trivial representation $D^{(1)^2}$.
+First, note that $V_{\vs\vp}^2$ is the sign representation $D^{(1^2)}$ and $V_{\vs\vp}^2$ is the trivial representation $D^{(2)}$.
 
@@
 \]
-A subrepresentation must be one-dimensional, and hence an eigenspace of each of these matrices;
+A proper nontrivial subrepresentation of $V_{\vs\vp}^3$ must be one-dimensional, and hence an eigenspace of each of these matrices;
 since $\varb \neq \vara$, the first has eigenspaces given by the spans of basis elements, and since $\vard \neq 0$, these are not eigenspaces of the second.

### 2019-07-29 tex/Drafts/Draft-1.tex
Kernel final comments.

@@
       We modify Khovanov's crossingless matchings to include $2n$ ``nodes'' and $r$ ``anchors,'' and prove in the case $e > n + r + 1$ that the associated module is isomorphic to the Specht module $S^{(n+r,n)}$ which corresponds to the partition $(n + r,n) \vdash 2n + r$.
-      We then give heuristics in support of the general case, including explicit composition series for $e = n + r + 1$ and for $2n + r \leq 6$. 
+      We then give heuristics in support of the general case, including explicit composition series for $e = n + r + 1$ and for $2n + r \leq 7$. 
       Lastly, when $e = 5$, we prove an isomorphism between the irreducible quotient $D^{(n+r,n)}$ with $r \leq 3$ and some subrepresentations of Jordan--Shor's Fibonacci representation.
@@
   Now suppose that $e = 5$ and $k$ contains the algebraic number $(-1 - q^2 - q^3)^{3/2}$.
-  Let $V^m$ be a $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{n+1}$ such that the character $\vs$ never appears twice in a row. 
-  We will suppress the superscript whenever it is clear from context.
+  The following is a modification of Shor--Jordan's Fibonacci representation of the braid group.
+
+  \begin{definition}
+  Let $V^m$ be a $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{n+1}$ such that the bit $\vs$ never appears twice in a row. 
+  We will refer to this as the \emph{Fibonacci representation} and suppress the superscript whenever it is clear from context.
 
@@
   We will verify that this is a representation of $\SH$ in Appendix \ref{Fib Relations}
+  \end{definition}
 
@@
   this project would not be possible without him.
-
-  \newpage
 
@@
   1 & 1
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{3,5}^1 = \pi_{3,6}^0&=  
@@
   0 & 0 & 0 & 1 & 1
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{3,6}^4&=  
@@
   -1 & -1 & 0 & 1 & 1
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{3,7}^3&=  
@@
  1 & 0 &-1 &-1 & 1 & 0 & -1 & -1 & 0 & 0 & 0 & 0 & 1 & 1
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{3,7}^1&=  
@@
  0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1
-\end{bmatrix}
+\end{bmatrix}^\intercal
 \end{align*}
@@
   1 & \qqo & 1
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{4,4}^1&=  
@@
   1 & \frac{1}{2}\qqo & \frac{1}{2}\qqo & 1 & \frac{1}{2}\qqo
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{4,6}^2 &=
@@
   0& 0& 0& 0& 1& \frac{1}{2}\qqo& \frac{1}{2}\qqo &1 &\frac{1}{2}\qqo
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{4,6}^0 &=
@@
   \qqo & 1 & 1 & \qqo & 1
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{4,7}^1 &=
@@
 0& 0& 0& 0& 0& 0& 0& 0& 0& 1& -\frac{1}{2}\qqo& \frac{1}{2}\qqo& 1& \frac{1}{2}\qqo
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \end{align*}
@@
   1 & \tto & \tto & 1
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{5,6}^2 &=
@@
   \tto& \tto& 1& 1& \tto+1& \tto & \tto & \tto & 1
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{5,7}^3 &=
@@
 0& 0& 1& 0& 0& 0& \tto& 0& 0& \tto& 0& 0& 0& 1
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{5,7}^1 &=
@@
 1& \qqo& \qqo& \qqo& -\tto& \qqo& -\tto& \qqo& -\tto& 1& \qqo& \qqo& \qqo& -\tto
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{6,6}^4 &=
@@
   1 & \vtv & 2 & \vtv & 1 
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{6,7}^3 &=
@@
   \vtv & 2 & \vtv & 1 & 1 & 2\vtv & 3 & \vtv & 2 & 2\vtv & 2 & 2 & \vtv & 1
-\end{bmatrix}\\
+\end{bmatrix}^\intercal\\
 \pi_{6,7}^5 &=
@@
   1 & \fft & \fto & \fto & \fft & 1
-\end{bmatrix}
+\end{bmatrix}^\intercal
 \end{align*}

### 2019-07-29 tex/comments/kernel_final_comments.tex
Kernel final comments.

--- 2019-07-29 tex/kernel.tex
@@
 
-\usepackage{NatMacros}
-\usepackage{RepStyle}
+\usepackage{../NatMacros}
+\usepackage{../RepStyle}
 
@@
 
-{\color{magenta} Natalie comments are magenta.}
+{\color{magenta} Natalie comments are magenta. This document contains comments on sections not covered in kernel\_comments}
 
@@
 \vspace{5mm}
+{\color{magenta} I think the definition of $Y_\beta$ could be moved into a definition environment, as its referenced in multiple lemmas.
+Further, it may save a lot of wordy statements to define it as $Y_\beta^{a,b}$ or something else dependent on the restriction.
+}
+
 \begin{lemma}
@@
 \end{lemma}
+{\color{magenta} This may be nice in an enumerate environment;
+for consistency, use [label=\{($\backslash$roman*)\}]}
 
@@
 	This lemma follows from an observation I made in section 2: a transposition can only create two arcs or an arc and an anchor. 
+  {\color{magenta} Put a $\backslash$label at the beginning of section 2, and a $\backslash$ref to that label rather than a 2 here.}
 
@@
 Then I claim the following:
-
+  {\color{magenta} I don't think it's necessary to say that you claim these. Also, $\backslash$nexists looks like $\nexists$.}	
 	\vspace{5mm}
@@
 \end{lemma}
+  {\color{magenta} Why are these centered?}
 
@@
 \end{proof}
+{\color{magenta} Minor suggestion (not by any means a real issue): have you considered \textbf{(i)} in each paragraph just before the text?}
 
@@
 
+  {\color{magenta} Please use the align or align* environment here. The current solution is way more spacy than necessary, and the non-aligned equalities hare hard to follow.}
 \end{proof}
+
+{\color{magenta} After reading this, I think that all of the last 4 lemmas may be best stated in the main text and proven in an appendix.}
 
@@
 \begin{proposition}
+  {\color{magenta} Need $\cap \ker (1 + T_i) \neq 0$; it is never empty.}
 	Suppose $e=n+r+1$. Then $\cap\text{ker}(1+T_i)\not=\emptyset$.
@@
 \begin{proof}
-
+  {\color{magenta} I think this should go after the base case.}	
 	Assume inductively that the statement holds for all $W_{2n'+r'}^{r'}$ where $2n'+r'<2n+r$.
@@
 
+  {\color{magenta} Is $i$ arbitrary? It seems like we should require that $\beta(i) = i+1$ so that $\beta$ is actually in $\ima (1 + T_i)$.}
   Let $E_\beta\subset W_{2n+r}^r$ be the pre-image of $\beta\in (1+T_i)W_{2n+r}^r$ under the action of $(1+T_i)$. To prove $w$ is in the kernel, we must show the following:
+
+  {\color{magenta} I think that there are a lot of ways to present these, but IMO just centring doesn't really work well.
+Putting these in an equation environment would assign them numbers that are continuous with the other such envioronments, which I think is more usual.
+otherwise, they could be put in an enumerate environment with roman numberal labels for a more uniform presentation. I mentioned how to do this in a comment above.} 
   \begin{center}
@@
 
+  {\color{magenta} I think that an itemize environment (bullet points) would be better here; the numbers feel like they suggest that these are in some way ordered or reliant on each other.
+That being said, I don't really know what is common for case-work like this.}
   \begin{enumerate}
@@
 	$$(x_{\beta(t+1,2n+r)}(q)\frac{Q_{n+r-(s-1)/2-1}...Q_{n+r-t/2}}{Q_1...Q_{(t-s+1)/2-1}})(x_{\beta(1,s-1)}(q)\frac{Q_{n+r-1}...Q_{n+r-(s-1)/2}}{Q_1...Q_{(s-1)/2-1}})((1+q)x_{\beta(s,t)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_{\alpha(s,t)}(q))$$
+
+  {\color{magenta} Please use an align environment, either prn or left( right), and simplify these equations if possible.}
 
@@
 \end{proof}
+{\color{magenta} This is technical and I didn't go through all of it;
+in general, I think that it occasionally has a somewhat conversational tone (e.g. ``the only cases we have not yet dealt with''), but otherwise I like this.}
 

### 2019-07-29 tex/kernel_final.tex

--- 2019-07-29 tex/kernel.tex
@@
 
-Let $\{T_i\}$ be the transpositions generating the Hecke algebra $\SH_{2n+r}(q)$. We assume $q\in \CC$.
-{\color{magenta} It seems to me so far that the results of this anchor work in an arbitrary field, and that we may only at the end have to restrict to a field of characteristic at least $n + r + 1$ whenever $e \mid n + r + 1$.
-Usually replacing $\CC^\times$ with $k^\times$ is free generality.
-}
+Let $\{T_i\}$ be the transpositions generating the Hecke algebra $\SH_{2n+r}(q)$.
 Let $W_{2n+r}^r$ be the generalized crossingless matchings representation with $2n+r$ nodes, $r$ of which are anchors.
@@
 Here we characterize the intersection of the kernels of each $(1+T_i)$, a subrepresentation of $W_{2n+r}^r$.
-I claim this intersection is at most one dimensional, and is nontrivial if and only if $q$ is a $n+r+1$st root of unity.
-{\color{magenta} I'll stop making this point after this, but this is not equivalent to $e = n + r + 1$.}
+I claim this intersection is trivial for $e>n+r+1$ and one dimensional for $e=n+r+1$.
 
@@
 
-  Fix some basis element $M\in W_{2n+r}^r$. Define $M(a):=b$ iff $a$ and $b$ are matched in $M$, $M(a):=a$ if $a$ is an anchor in $M$.
-  {\color{magenta} Should specify that $a,b$ are integers $1 \leq a,b \leq 2n + r$.} 
-  Given that $M$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $M(a,b)$ of $M$ to be the basis element $K\in W_{b-a+1}^{r'}$ specified by $K(i)=M(i+a-1)-a+1$.
-This sub-matching is defined for $a<b$ when $M(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$.
+  Fix some basis element $\psi\in W_{2n+r}^r$.
+For $1 \leq a,b \leq 2n + r$ define $\psi(a):=b$ iff $a$ and $b$ are matched in $\psi$, $\psi(a):=a$ if $a$ is an anchor in $\psi$.
+Given that $\psi$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $\psi(a,b)$ of $\psi$ to be the basis element $\sigma\in W_{b-a+1}^{r'}$ specified by $\sigma(i)=\psi(i+a-1)-a+1$.
+This sub-matching is defined for $a<b$ when $\psi(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$.
 See Figure 1.
 
-  If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, $M(a,b)$ will still refer to those nodes, but will not be a sub-matching.
-For any other $a,b$, we define $M(a,b)$ to be an element of the representation with no nodes.
+  If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, $\psi(a,b)$ will always refer to those nodes and they're matchings, though it may not be a sub-matching unless specified.
+For any other $a,b$, we define $\psi(a,b)$ to be an element of the representation with no nodes.
 \end{definition}
@@
 		\end{gathered}}$
-	\caption{$M\in W_6^0$ is pictured on the left, $K\in W_4^0$ is pictured on the right. $M(3,6)=K$. $M(2,5)$ is not defined.}
+	\caption{$\psi\in W_6^0$ is pictured on the left, $\sigma\in W_4^0$ is pictured on the right. $\psi(3,6)=\sigma$. $\psi(2,5)$ is not a sub-matching.}
 	\label{S6 Basis}
@@
   Let $Y$ be the set of basis elements with nonzero coordinate in $w$.
-Let $k$ be the greatest integer such that there exists $y\in Y$ where $y(1)=...=y(k)=0$ {\color{magenta} should this be $y(1)-1 = \dots = y(k) - k = 0$?
-Also, we should avoid using $k$ as an integer, as it's used elsewhere as a field.}, and let $U\subset Y$ be the set of such $y$.
+Let $z$ be the greatest integer such that there exists $y\in Y$ where $y(1)-1=...=y(z)-z=0$, and let $U\subset Y$ be the set of such $y$.
 In other words, $U$ is the set of basis elements in $Y$ which have the most anchors to the far left.
 
-	Suppose $k<r$.
-Then for each $y\in U$ there exists a minimal $i_y>k+2$ such that $y(i_y)=0$.
+  Suppose $z<r$.
+Then for each $y\in U$ there exists a minimal $i_y>z+2$ such that $y(i_y)=0$.
 In other words, $i_y$ is the position of the next leftmost anchor in $y$.
@@
 Then I claim the basis element $y':=q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}$ has nonzero coordinate in $(1+T_{i_{\tilde{y}}-1})w$, implying $w\not\in \cap\text{ker}(1+T_i)$.
-To see this, we can show that $\tilde{y}$ is the only element in $Y$ such that $q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$.
-$y'$ still has $k$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$.
-If $x\in Y,\not\in U$, the basis element proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$.
-If $x\in U$ the basis element proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$.
-Since this is the only match altered by action $(1+T_{i_{\tilde{y}}-1})$ on $x$, if $(1+T_{i_{\tilde{y}}-1})x\sim y'$ this implies $x=\tilde{y}$.
-So if $k<r$ $w$ is not in the desired kernel.
+To see this, we can show that $\tilde{y}$ is the only basis element in $Y$ such that $(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$.
+$y'$ still has $z$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$.
+If $x\in Y,\not\in U$, the basis element $x'$ proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$.
+If $x\in U$, $x'$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$.
+Since this is the only match altered by action of $(1+T_{i_{\tilde{y}}-1})$ on $x$, if $(1+T_{i_{\tilde{y}}-1})x\sim y'$ this implies $x=\tilde{y}$.
+So if $z<r$ $w$ is not in the desired kernel.
 
-	Suppose $k=r$ but $R\not\in U$ (so $R\not\in Y$).
+  Suppose $z=r$ but $R\not\in U$ (so $R\not\in Y$).
 Let us define a sequence of subsets of $U$ in the following way: $U_0:=U$, $U_{i+1}:=\{u\in U_i| u(r+i+1)=2n+2r-i+1 \}$.
@@
 I claim that $\tilde{u}$ is the only element in $Y$ such that $(1+T_{\tilde{u}(r+t+1)})\tilde{u}\sim u'$, again implying that $w$ is not in the desired kernel.
-$u'$ still has $k$ anchors on the left, $u'(r+i)=2n+2r-i+2$, $1\leq i\leq t$, and $u'(r+t+1)>\tilde{u}(r+t+1)$, so $u'\not\in Y$.
+$u'$ still has $r$ anchors on the left, $u'(r+i)=2n+2r-i+2$, $1\leq i\leq t$, and $u'(r+t+1)>\tilde{u}(r+t+1)$, so $u'\not\in Y$.
 If $x\in Y,\not\in U$,  the basis element $x'$ proportional to $(1+T_{\tilde{u}(r+t+1)})x$ will have $r$ leftmost anchors only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
-Similarly, if $x\in U,\not\in U_t$, the basis element $x'$ will have the property $x'(r+t)=2n+2r-t+2$ only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
+Similarly, if $x\in U,\not\in U_t$, the basis element $x'$ will have the property $x'(r+i)=2n+2r-i+2$ for all $i\leq t$ only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
 If $x\in U_t$, $x'(r+t+1)=u'(r+t+1)$ if and only if $x(r+t+1)=\tilde{u}(r+t+1)$ and $x(x(r+t+1)+1)=\tilde{u}(\tilde{u}(r+t+1)+1)$ (since $u'\not \in Y$).
 These are the only matches altered by the action $(1+T_{\tilde{u}(r+t+1)})$, so this implies $x=\tilde{u}$.
-Thus we have proved that if $R\not\in Y$, $w$ is not in the desired kernel.
+Thus we have proved that if $R\not\in Y$, $w$ is not in the kernel.
 
 \end{proof}
-{\color{magenta} Nice. I felt the formalism around matchings ($M(a)$, $M(a,b)$ and all that) made this proof much more clear.}
 
-Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ humps to the right or left, respectively.
+Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively.
 Examples are pictured in figure 2.
@@
 \begin{proposition}
-	Let $w$ be an element in the kernel intersection $\cap (1+T_k)$ in some generalized crossingless matchings representation.
+	Let $w$ be an element in the kernel intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation.
 Let $y$ be a basis element with coordinate $c$ in $w$.
@@
 
-$Q_1Q_n-Q_{n-1}=\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}=\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}=\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}$.
-{\color{magenta} Imo the align* environment would help this.}
+$$Q_1Q_n-Q_{n-1}=\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}=$$
+
+$$\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}=\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}$$.
 
@@
 \begin{proof}
-	Consider acting on $w$ by an element $(1+T_k)$.
-The coordinate of $\phi_i$ in $(1+T_k)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_k)$.
-Specifically, it will be $(1+q)c\alpha+(q^1/2)\sum c_\beta$ where $\alpha=1$ if $y(k)=k+1$, $\alpha=0$ otherwise, and $c_\beta$ are the coordinates of all basis elements $\beta$ where $(1+T_k)\beta\sim y$.
+	Consider acting on $w$ by an element $(1+T_z)$.
+The coordinate of $\phi_i$ in $(1+T_z)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_z)$.
+Specifically, it will be $(1+q)c\iota+(q^1/2)\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.
 
@@
 Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$.
-This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in figure 2.3.
-I claim that the only basis elements $\beta$ where $(1+T_{a-1+r+n/2-i})\beta\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist (we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$).
+This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in figure 3.
+I claim the following:
 
-	Note that the action of any $(1+T_k)$ on a basis element $\beta$ creates exactly two lines: an arc of length two connecting $k$ and $k+1$, and either an anchor or an arc of length $\geq 2$ connecting $\beta(k)$ and $\beta(k+1)$.
-The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.
+	\begin{center}
+		\textit{claim}:
+		The only basis elements $\psi$ where $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist\footnote{we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$}.
+	\end{center}
 
-	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in figure 2.3.
-Suppose there was another basis element $\beta$ sent to $\phi_i$ by the given transposition.
-We note that if $\beta$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
-Thus, if $\beta$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\beta\sim \phi_i=>\beta\sim \phi$.
-If $\beta$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\beta\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\beta(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\beta(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor.
-All other matchings remain unchanged, so this implies $\beta=\phi_{i+1}$.
-Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\beta=\phi_{i-1}$.
+	Note that the action of any $(1+T_z)$ on a basis element $\psi$ creates exactly two lines: an arc of length two connecting $z$ and $z+1$, and either an anchor or an arc of length $\geq 2$ connecting $\psi(z)$ and $\psi(z+1)$.\footnote{Although this fact follows directly from our definition of the representation, it will be used throughout the document, so it is important that the reader understands it.} The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.
+
+	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in figure 3.
+Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition.
+We note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
+Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$.
+If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\psi(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor.
+All other matchings remain unchanged, so this implies $\psi=\phi_{i+1}$.
+Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\psi=\phi_{i-1}$.
 For boundary cases, note that for $\phi_0=\theta_0$, the only other basis element sent to this by the middle transposition is $\phi_1=\theta_1$.
-Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case is unhelpful to us.
+Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case gives no new information.
 Lastly, note that our argument was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors.
@@
 
-	Given this claim and lemma 2.4, the proposition follows quickly through induction.
+	Given this claim and lemma 2.4, the proposition follows quickly through induction:
 
@@
 		\]
-    \caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $W_{8}^2$ and $i=2$.{\color{magenta} I made the last of these a bit taller so that the anchors weren't close to touching the arc.}}
+    \caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $W_{8}^2$ and $i=2$.}
 		\label{Action}
@@
 \end{proof}
-{\color{magenta} This proof is pretty technical, and I don't quite have the time to go through it tonight. I'll go through it more closely later.}
 
@@
 	Consider the coordinate of $R_{L,n+r-1}$ in $(1+T_1)w$.
-Using the same logic as in the proof of proposition 2.3, we note that if a basis element $\beta$ has no anchor at position $3$ and is not equal to $R_{L,n+r-2}$, $(1+T_1)\beta\not\sim R_{L,n+r-1}$.
+Using the same logic as in the proof of proposition 2.3, we note that if a basis element $\psi$ has no anchor at position $3$ and is not equal to $R_{L,n+r-2}$, $(1+T_1)\psi\not\sim R_{L,n+r-1}$.
 Thus the desired coordinate is equal to $(1+q)Q_{n+r-1}c+q^{1/2}Q_{n+r-2}c=-q^{1/2}Q_{n+r}c$ by lemma 2.4.
@@
 \end{proof}
-{\color{magenta} Nice.
-Is the goal that basically this style of proof with yield the same result when $e \neq n + r + 1$?
-At any rate, I think a final text should place more emphasis on the fact that proposition 2.3 specifies a one-dimensional subspace containing the kernel;
-in effect, this specifies that the sign representation appears at most once as a submodule, and gives a formula for when it does.}
 

### 2019-07-29 tex/Drafts/Draft-2.tex
Introduction revisions

--- 2019-07-29 tex/Drafts/Draft-1.tex
@@
   citecolor=blue,
-  linkcolor=black!30!magenta,
+  linkcolor=orange!50!red,
   urlcolor=blue}
@@
 
-  \title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules of Iwahori-Hecke Algebras of the Symmetric Group}
+  \title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules of Iwahori--Hecke Algebras of the Symmetric Group}
   \author[Miles Johnson and Natalie Stewart]{Miles Johnson and Natalie Stewart\\
@@
 \section{Introduction} 
-  Let $S_{2n+r}$ be the symmetric group on $2n+r$ indices with $2n + r \geq 2$, let $\SH := \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over field $k$ with parameter $q \in k^\times$ having square root $q^{1/2}$, and let $\cbr{T_i}$ be the reflections generating $\SH$.
+  Let $S_{2n+r}$ be the symmetric group on $2n+r$ letters with $2n + r \geq 2$, let $\SH := \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over a field $k$ with parameter $q \in k^\times$ having a fixed square root $q^{1/2}$, and let $\cbr{T_i}$ be the simple reflections generating $\SH$.
 
@@
   Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
-  Either $q = 1$ and $e$ is the characteristic of $k$ (with $0$ replaced by $\infty$), or $q \neq 1$ and $q$ is a primitive $e$th root of unity.
+  Note that either $q = 1$ and $e$ is the characteristic of $k$ (with $0$ replaced by $\infty$), or $q \neq 1$ and $q$ is a primitive $e$th root of unity.
 
   \vspace{5pt}
-  When $q = 1$, the Hecke algebra $\SH$ is isomorphic to the group algebra $k\brk{S_{2n+r}}$.
-  For $q$ a prime power, let $G := \GL_{2n+r}(q)$ be the general linear group over a field with $q$ elements, let $B := B(q)$ be the Borel subgroup of $G$, and let $1_B$ be the trivial representation of $k\brk{B}$.
-  Then, it is a well known result that the endomorphism algebra $\End_{k\brk{G}} \prn{\Ind_B^G(1_B)}$ is isomorphic to the Hecke algebra $\SH$.\cite{Mathas-book}
-  Hence the representation theory of the Hecke algebra generalizes the representation theory of the symmetric group, and informs the representation theory of the general linear group.
+  When $q = 1$, the Hecke algebra $\SH$ is isomorphic to the group algebra $k\brk{S_{2n+r}}$;
+  hence the representation theory of $\SH$ generalizes the representation theory of the symmetric group.
+  The Hecke algebra is also well known to be connected to the representation theory of the general linear group over a finite field.\cite{Mathas-book}
 
@@
 
-  These representations $D^\lambda$ are well-defined, but many properties of them are unknown.
+  These representations $D^\lambda$ have explicit constructions, but many of their properties are unknown.
   For instance, the dimension of these modules is unknown outside of some special cases.\cite{Mathas-book}
-  However, there does exists an algorithm due to Lascoux, Leclerc, and Thibon (verified by Ariki) which produces the decomposition matrices of the Iwahori-Hecke Algebra $\SH_{\CC,q}(S_{2n + r})$ for $q$ an $e$th root of unity.\cite{Ariki,LLT}
-
-  Further, there are theorems, called \emph{modular branching theorems}, characterizing the socle and semisimplicity of the restriction $\Res D^\lambda$ to a subalgebra generated by $2n + r - 2$ simple transpositions.
-  These are originally due to Kleshchev in the group algebra case, and were generalized to the Hecke algebra by Brundan.\cite{Brundan,Kleshchev}
-
-  These constructions tend to be well-defined but complicated and often intractable.
-  We aim to give simple realizations of some particular $S^\lambda$ and $D^\lambda$ which expose this structure while being intuitive and simple to manipulate.
+  However, there does exist an algorithm due to Lascoux--Leclerc--Thibon--Ariki which computes the decomposition matrices of the Iwahori--Hecke Algebra $\SH_{\CC,q}(S_{2n + r})$ for $q$ an $e$th root of unity.\cite{LLT,Ariki}
+
+  The cellular basis for $S^\lambda$ and associated construction for $D^\lambda$ tend to be complicated and often computationally intractable.
+  We aim to give simple graphical realizations of $S^\lambda$ and $D^\lambda$ in some cases that $\lambda = (n+r,n)$.
+  These realizations expose the structure of irreducibility and branching in an intuitive and computationally simple way.
 
   \vspace{5pt}
-  Throughout the text, we will refer to partitions of $2n + r$;
-  identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
-  Identify each of these with a subset $\brk \lambda \subset \NN^2$ as is standard, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.\cite{Kleshchev}
-
   Note that we follow the convention of Murphy and Kleshchev, which is dual to the conventions of Dipper, James, and Mathas;
@@
 
-  Fixing some partition $\lambda$, for $1 \leq i \leq j \leq l$, let $\beta_\lambda(i,j)$ and $\gamma_\lambda$ be the quantities
-  \begin{align*}
-    \beta_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i}^j a_t\\
-    \gamma_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i+1}^j a_t.
-  \end{align*}
-  Results due to Kleshchev and Brundan refer to \emph{normal} and \emph{good} numbers;
-  note that 1 is always normal, and that $j$ is normal when $\beta_\lambda(i,j) \not\equiv 0 \pmod e$ for all $i \leq j$.
-  Recall that $j$ is good iff $j$ is normal and $\gamma_\lambda(j,j') \not\equiv 0 \pmod e$ for all $j' \geq j$ normal.\cite{Brundan,Kleshchev}
-  These are the combinatorial properties necessary to state and use branching theorems.
-
   Throughout this paper, we analyze the \emph{two-row partitions} $(n+r,n) \vdash 2n + r$ and their corresponding modules $S^{(n+r,n)}$ and $D^{(n+r,n)}$.
@@
   The following definition modifies the crossingless matchings defined by Khovanov.\cite{Khovanov}
+
   \begin{definition}
-    A \emph{crossingless matching on $2n+r$ indices with $r$ anchors} is a partition of $\cbr{1,\dots,2n+r}$ into $n$ parts of size $2$ and $r$ of size 1 such that no two parts of size two``cross'', i.e.
-there are no parts $(a,a')$ and $(b,b')$ such that $a < b < a' < b'$, and no parts of size one are ``inside'' of a part of size two, i.e.
-there are no $c, (a,a')$ such that $a < c < a'$.
-    We will call these arcs and anchors, respectively.
-    Then, define $M^r_{2n+r}$ to be the $k$-vector space with basis the set of generalized crossingless matchings on $2n+r$ indices with $r$ anchors.
-
-    For convenience, given a basis element $w_j \in M_{2n + r}^r$ and integers $1 \leq a,b \leq 2n + r$, define the $w_j(a) := b$ if $(a,b)$ is an arc in $M$, and $w_j(a) := a$ if $a$ is an anchor in $M$.
-
-    In order to endow this with an $\SH$-action, consider some basis element $w_j$ and some element $(1 + T_i)$ of $\SH$.
-    The elements $\cbr{1} \cup \cbr{1 + T_i | 1 \leq i < 2n + r}$ generate $\SH$, so it is sufficient to define the action of $1 + T_i$ on $w_j$.
-
-    If $w_j$ has arc $(i,i+1)$, define $(1 + T_i)w_j := (1 + q)w_j$.
-    If $w_j$ has anchors $W(i) = i$ and $W(i+1) = i+1$, define $(1 + T_i)w_j := 0$.
-    If $w_j$ has anchor $W(i) = i$ and arc $W(i+1) = b$, define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$, $w_l(b) = b$, and all other arcs agree with $w_j$.
-    If $w_j$ has arcs $W(i) = a$ and $W(i+1) = b$, then define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$,$w(a) = b$, and all other acts agree with $w_j$. 
-    We verify that this is well-defined in appendix \ref{Cross Relations}.
+  Define a \emph{crossingless matching on $2n + r$ nodes and $r$ anchors} to be an isotopy class of $n + r$ nonintersecting paths in the slice $\RR \times \brk{0,1}$ connecting $2n + r$ disctinct points of $\RR \times \cbr{0}$ and $r$ points of $\RR \times \cbr{1}$ such that none of the latter points are conected.
+  Let $M_{2n + r}^r$ have basis given by these matchings.
+  This is illustrated in Figure \ref{S5 Basis}.
+
+  Let the length of an arc $(i,j)$ be $j - i + 1$.
+
+  We endow $M_{2n + r}^r$ with an action by specifying $(1 + T_i)w_j$ for some basis element $w_j$ of $M_{2n + r}$.
+  We do so by concatenating in ``vertical lines'' below each point other than the $i$th and $i+1$st, concatenating paths between the $i$th and $i+1$st points as well as points below them, removing any ``loops'' this forms, and taking isotopy to some matching $w_l$ if possible;
+  if this is not possible, then there are anchors at $i,i+1$ and we set $(1 + T_i)w_j := 0$;
+  if this is possible and there is a ``loop,'' set $(1 + T_i)w_j := (1 + q)w_j$ and otherwise set $(1 + T_i)w_j := q^{1/2}w_l$.
+  This action is illustrated in Figure \ref{Action}, and we verify that this is well-defined in Appendix \ref{Cross Relations}.
   \end{definition}
-
-  \begin{figure}[b]
-    \begin{adjustbox}{width=\textwidth}
-      \begin{tabular}{l l}
-        \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{2}{1/4, 2/3}{5/1,6/2}{(1+q)}
-        \hspace{20pt}
-        &
-        \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{3}{1/2, 3/4}{5/1,6/2}{q^{1/2}}\\
-        \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{4}{2/3, 4/5}{1/1,6/2}{q^{1/2}}
-        &
-        \GeneralizedZeroAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{5}
-      \end{tabular}
-  \end{adjustbox}
-
-    \caption{Illustration of the actions $(1 + T_i)w_{\abs{M^2_6}}$.
-      In general, we act by deleting loops, isotoping onto a new crossingless matching, and scaling by either $q^{1/2}$, $(q + 1)$, or 0.
-    }
-    \label{Action}
-  \end{figure}
-
-  We may alternately define $M_{2n + r}^r$ topologically;
-  fix $2n + r$ distinct points $a_1,\dots,a_{2n + r}$ points along $\RR \times \cbr{0} \subset \RR^2$ and $r$ distinct points $b_1,\dots,b_r$ along $\RR \times \cbr{1}$, and define $M_{2n + r}^r$ to have basis given by the isotopy classes of $n + r$ paths connecting the points $a_1,\dots,a_{2n+r},b_1,\dots,b_r$ such that no distinct $b_i,b_j$ are connected by a path.
-
-  We will take some basis element $w_j \in M_{2n +r}^r$ and define the action $(1 + T_i)w_j$.
-  To do so, map $w_j$ through the natural embedding $\RR \times \brk{0,1} \hookrightarrow \RR \times \brk{\frac{1}{2},1}$, and form the figure $w_j^i$ by adjoining the lines connecting $a_l$ and $a_l + \prn{0,\frac{1}{2}}$ for all $l \neq i,i+1$ as well as paths from $a_i$ to $a_{i+1}$ and $a_i + \prn{0,\frac{1}{2}}$ to $a_{i+1} + \prn{0,\frac{1}{2}}$.
-  This has either 0 or 1 path components which do not intersect $\RR \times \cbr{0,1}$;
-  these form ``loops.''
-
-  Take the figure $\tilde w_j^i$ without this component.
-  If $\tilde w_j^i$ is not isotopic to some $w_l$, then define $(1 + T_i)w_j := 0$.
-  If $\tilde w_j^i$ is isotopic to some $w_l$, define $(1 + T_i)w_j := (1 + q)w_l$ if $w_j^i$ has a loop and $(1 + T_i)w_j := q^{1/2}w_l$ otherwise.
-  This process is illustrated in Figure \ref{Action}.
-
-  \begin{remark}
-    This definition gives a graphical calculus for working with our module.
-    It should be clear that, if $w_j^i$ has a loop then $w_l(i) = i+1$ and $w_l = w_j$.
-    Further, this easily defines an arbitrary composition:
-    \[
-      (1 + T_{i_1})\cdots(1 + T_{i_\ell})w_j = q^{(\ell - t)\frac{1}{2}}(1 + q)^tw_l
-    \]
-    if the figure we make  via $(1+T_{i_1})\cdots(1+T_{i_\ell})$ is isotopic to $w_l$ after removing $t$ loops.
-  \end{remark}
-
-  Let the length of an arc $(i,j)$ be $l(i,j) := j - i + 1$.
-  Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
-  using this, we may order the crossingless matchings with no anchors in increasing lexicographical order in order to obtain an order on the sub-basis containing a particular set of anchors;
-  let the basis be ordered first by the position of the anchors in decreasing lexicographical order, then increasing for the matchings between each anchor.
-  Let this basis be $\cbr{w_i}$.
-  This basis is illustrated for $M_{5}^1$ in Figure \ref{S5 Basis}.
-
   \begin{figure} 
@@
 
-  Note that the representations $M_{0 + r}^r$ and $S^{(r)}$ are isomorphic to the sign representation; 
-  we will prove that $M_{2n+r}^r$ and $S^{(n+r,n)}$ are isomorphic as representations in the case that $e > n + r + 1$.
+  \begin{figure}
+    \begin{adjustbox}{width=\textwidth}
+      \begin{tabular}{l l}
+        \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{2}{1/4, 2/3}{5/1,6/2}{(1+q)}
+        \hspace{20pt}
+        &
+        \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{3}{1/2, 3/4}{5/1,6/2}{q^{1/2}}\\
+        \GeneralizedAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{4}{2/3, 4/5}{1/1,6/2}{q^{1/2}}
+        &
+        \GeneralizedZeroAction{6}{1/4,2/3}{2}{5/1,6/2}{1}{5}
+      \end{tabular}
+  \end{adjustbox}
+
+    \caption{Illustration of the actions $(1 + T_i)w_{\abs{M^2_6}}$.
+      In general, we act by deleting loops, isotoping onto a new crossingless matching, and scaling by either $q^{1/2}$, $(q + 1)$, or 0.
+    }
+    \label{Action}
+  \end{figure}
+
+  Note that the representations $M_{0 + r}^r$ and $S^{(r)}$ are isomorphic to the sign representation.
+  In fact, we will prove that $M_{2n + r}^r \simeq S^{(n+r,n)}$ whenever $e > n + r + 1$.
   Additionally, we will prove that $M_{2n + r}^r$ is irreducible everywhere that $e > n$ and $S^{(n+r,n)}$ is irreducible.
   We will conjecture that $M_{2n + r}^r \simeq S^{(n+r,n)}$ with $e$ unrestricted as well.
+
+  This proves a graphical characterization of $S^\lambda$ in many cases, and hence $D^\lambda$ in the cases where $S^\lambda \simeq D^\lambda$.
+  However, the representation theory of $\SH$ is tied to the modules $D^\lambda$ even in cases where $S^\lambda$ is not irreducible;
+  we will present a characterization of the module $D^{(n+r,n)}$ when $e = 5$ and $r \leq 3$.
 
@@
   \fakesubsection{Fibonacci Representation}
-  Now suppose that $e = 5$ and $k$ contains the algebraic number $(-1 - q^2 - q^3)^{3/2}$.
-  The following is a modification of Shor--Jordan's Fibonacci representation of the braid group.
+  Now suppose that $e = 5$ and $k$ contains the algebraic number $\sqrt{q + q^4}$ for reasons which will be apparent soon.
+  For convenience set $m := 2n + 4$.
+  The following is a modification of Shor--Jordan's Fibonacci representation of the braid group.\cite{Shor}
 
   \begin{definition}
-  Let $V^m$ be a $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{n+1}$ such that the bit $\vs$ never appears twice in a row. 
-  We will refer to this as the \emph{Fibonacci representation} and suppress the superscript whenever it is clear from context.
-
-  We wish to endow this with a $\SH$-action which acts on a basis vector only dependent on characters $i,i+1,i+2$, sending each basis vector to a combination of the other basis vectors having the same characters $1,\dots,i,i+2,\dots,n+1$ as follows:
+  Let $V^m$ be the $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{n+1}$ such that the bit $\vs$ never appears twice consecutively. 
+  We will refer to $V^m$ as the \emph{Fibonacci representation} and suppress the superscript whenever it is clear from context.
+
+  We wish to endow this with a $\SH$-action which acts on a basis vector only dependent on bits $i,i+1,i+2$, sending each basis vector to a combination of the other basis vectors having the same bits $1,\dots,i,i+2,\dots,n+1$ as follows:
 
@@
     \begin{split}
-    \vara &= -1\\
-    \varb &= q\\
-    \varc &= \tau(q\tau - 1)\\
-    \vard &= \tau^{3/2}(q + 1)\\
-    \vare &= \tau(q-\tau)\\
-    \tau &= -1-q^2-q^3
+    \tau  &:= q + q^4\\
+    \vara &:= -1\\
+    \varb &:= q\\
+    \varc &:= \tau(q\tau - 1)\\
+    \vard &:= \tau^{3/2}(q + 1)\\
+    \vare &:= \tau(q-\tau)
   \end{split} \label{Fib Constants} 
@@
 
-  This contains 4 subrepresentations based on the first and last character of the string, which are not modified by $\SH$.
-  Label the subrepresentation spanned by strings $(\vs\dots\vs)$ by $V_{\vs\vs}$, and similar for the other 3.
-  It is easy to see that $V_{\vs\vp} \simeq V_{\vp\vs}$, so that
-  \[
-    V \simeq 2V_{\vs\vp} \oplus V_{\vs\vs} \oplus V_{\vp\vp}.
-  \]
-  We will show that $V_{\vp\vp} \simeq V_{\vs\vp} \oplus V_{\vs\vs}$, and give the following isomorphisms with irreducible quotients of specht modules depending on the parity of the number of indices in $\SH$:
-  \begin{equation}
-    \begin{split}    
+  This contains four subrepresentations spanned by strings with beginning and ending with specified bits.
+  Label the subrepresentation spanned by strings $(\vs\dots\vs)$ by $V_{\vs\vs}$, $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$;
+  these bits are preserved by the action \eqref{Fib Action}.
+  We will show that these are isomorphic to particular $D^\lambda$.
+
+  \fakesubsection{Overview of Paper}
+
+  In Section \ref{Specht Modules Section} we give corollaries to standard theorems concerning Specht modules.
+  First, James-Mathas provides a sharp characterization of the irreducibility $S^\lambda$ for $\lambda \vdash 2n + r$ which is $e$-regular, called the \emph{Carter criterion}.\cite{Mathas-book}
+  We specialize this to the case that $\lambda = (n+r,n)$ to give a combinatorial condition for irreducibility of $S^{(n+r,n)}$.
+  We note that this irreducibility depends only on $e$ when $e > n$;
+  otherwise it depends on both $e$ and the characteristic of the field.
+  Further, we use Kleshchev--Brundan's modular branching rules to prove our first significant statement: if $S^\lambda \simeq D^\lambda$ and $e > n$, then a particular length-2 composition series uniquely determines $\lambda$;
+  further, an irreducible restriction to $D^{(n,n-1)}$ determines $\lambda$ as well.\cite{Kleshchev, Brundan}
+
+  \def\thmcolor{black!60!orange}
+  \vspace{5pt}
+  In Section \ref{Crossingless Matchings Section}, we first prove that every basis vector in $M$ is cyclic, then that $M$ contains no sign subrepresentation.
+  Then, we prove the following theorem.
+  \begingroup
+  \hypersetup{linkcolor=\thmcolor} % no orange theorem label
+  \begin{customthm}{\ref{Irreducibility Theorem}}
+    Suppose $e > n$ and $S^{(n+r,n)}$ is irreducible.
+    Then $M_{2n + r}^r$ is irreducible.
+  \end{customthm}
+  \endgroup
+  Following this, we prove the existence of a particular filtration with factors given by other crossingless matchings representations;
+  using irreducibility, this becomes a composition series, and an inductive argument combined with the branching of Section \ref{Specht Modules Section} allow us to prove the following:
+  \begingroup
+  \hypersetup{linkcolor=\thmcolor}
+  \begin{customthm}{\ref{Correspondence Theorem}}
+    Suppose $e > n + r + 1$.
+    Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
+  \end{customthm}
+  \endgroup
+  Last, we finish the section by proving more general statements concerning sign subrepresentations of $M$, which contribute to conjectures later in the paper.{\color{orange} Fill in with specific information later.}
+
+  \vspace{5pt}
+  In Section \ref{Fibonacci Section}, we begin by establishing isomorphisms as in \ref{Fibonacci Theorem} for the subrepresentations of $V^2$, as well as irreducibility of $V^3_{\vs\vp}$.
+  We then use these cases to prove that $V^m_{\vs\vp}$ is irreducibile for all $m$, which implies that that $V^m_{\vs\vs}$ is irreducible.
+  From this, we inductively prove the following theorem:
+  \begingroup
+  \hypersetup{linkcolor=\thmcolor}
+  \begin{customthm}{\ref{Fibonacci Theorem}}
+    The following isomorphisms characterize the subrepresentations of the Fibonacci representation:
+    \begin{align*}  
        V^{2n}_{\vs\vs} &\simeq D^{(n,n)}\\ 
@@
        V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)}.
-    \end{split} \label{Fib Isos}
-  \end{equation}
-
-  \fakesubsection{Overview of Paper}
-  In Section \ref{Specht Modules Section} we give corollaries to standard theorems concerning Specht modules.
-  First, James-Mathas provides a sharp characterization of the irreducibility of $e$-regular, called the \emph{Carter criterion}.\cite{Mathas-book}
-  We specialize this to the case that $\lambda = (n+r,n)$ to give a tractable combinatorial expression for irreducibility of $S^{(n+r,n)}$.
-  We note that this irreducibility depends only on $e$ when $e > n$;
-  otherwise it depends on the characteristic of the field.
-  Next, we specialize theorems introduced by Kleshchev and generalized by Brundan describing $\Hom{W, \Res \, D^\lambda}$ where $W$ is either $S^\mu$ or $D^\mu$ for $\mu$ a partition of $2n + r - 1$ and our restriction is taken to the subalgebra generated $2n + r - 2$ simple transpositions.\cite{Kleshchev}\cite{Brundan}
-  We verify that this is unambiguous in Appendix \ref{Algebra}.
-  These allow us to prove our first significant statement: if $S^\lambda \simeq D^\lambda$ and $e > n$, then a particular length-2 composition series uniquely determines $\lambda$;
-  further, an irreducible restriction to $D^{(n,n-1)}$ determines $\lambda$ as well.
-
-  In Section \ref{Crossingless Matchings Section}, we begin by attempting to prove that $M := M_{2n + r}^r$ is irreducible whenever $e > n+r+1$.
-  We do this by first proving that every vector in our basis for $M$ is cyclic, then that $M$ contains no sign subrepresentation.
-  We then use these facts to inductively prove irreducibility.
-  Following this, we prove a particular filtration with factors given by other crossingless matchings representations;
-  this becomes a composition series, and an inductive argument combined with the branching of Section \ref{Specht Modules Section} allows us to prove $M \simeq S^{(n+r,n)}$.
-  Last, we finish the section by proving more general statements concerning sign subrepresentations, which contribute to conjectures later in the paper.
-
-  In Section \ref{Fibonacci Section}, we begin by establishing isomorphisms of the subrepresentations of $V^m$ in the case that $m = 2$, as well as irreducibility of $V^3_{\vs\vp}$.
-  We then use these cases to prove that $V_{\vs\vp}$ is irreducibility, having as a corollary that $V_{\vs\vs}$ is irreducible.
-  From this, we inductively prove isomorphisms between the representations $V_{\vs\vs}$, $V_{\vs\vp}$ and $D^{(n+r,n)}$ with $r$ depending on the subscript of $V$ and the parity of $m$.
-
+    \end{align*}
+  \end{customthm}
+  \endgroup
   {\color{orange} Overview of Conjecture and Empirics goes here.}
@@
   \fakesubsection{Acknowledgements}
-  The authors thank Professor Roman Bezrukavnikov for suggesting this project, as well as Dr. Slava Gerovitch for his support via organization of the SPUR+ program.
-  We would also like to thank Professor David David Jerison, Professor Ankur Moitra for their role in SPUR+ as well as general and mathematical advice.
-  We would also thank Professor Alexander Kleshchev for his mathematical guidance concerning branching theorems.
+  The authors thank Prof. Roman Bezrukavnikov for suggesting this project, as well as Dr. Slava Gerovitch for organizing the SPUR+ program.
+  We would also like to thank Profs. David Jerison and Ankur Moitra for their role in SPUR+ as well as general advice.
+  We would also thank Professor Alexander Kleshchev for our helpful conversations concerning branching theorems.
   Lastly, we would like to express our gratitude to our mentor Oron Propp for his help and advice in both acquiring background knowledge and in executing the mathematics in this paper;
@@
 
-  In the following section, we cite a theorem of James-Mathas which precisely characterizes the irreducibility of $S^\lambda$ in the case that $\lambda$ is $e$-regular, and we specialize this result to the case of two-row specht modules.
+  In the following section, we cite a theorem of James-Mathas which precisely characterizes the irreducibility of $S^\lambda$ in the case that $\lambda$ is $e$-regular, and we specialize this result to the case of two-row Specht modules.
   This falls into two cases: either $e > n$, where $S^{(n+r,n)}$ is irreducible iff $e \nmid r+2,\dots,n+r+1$, or $e \leq n$, where the irreducibility of $S^{(n+r,n)}$ is complicated and depends on the characteristic of $k$.
@@
   \subsection{Branching}
-  In this section as well as later sections, we will consider the restruction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}(S_{2n + r - 1}$.
+  In this section as well as later sections, we will consider the restruction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}\prn{S_{2n + r - 1}}$.
   We verify in Appendix \ref{Algebra} that any two subalgebras of $\SH$ generated by $2n + r - 2$ simple transpositions give isomorphic restrictions of representations (through a particular isomorphism of the subalgebras).
   We will hence abuse notation, pick one such subalgebra $\SH'$, and notate $\Res_{\SH'}^\SH W$ by $\Res W$ for any $\SH$-module $W$.
+
+  Throughout the rest of the paper, it will be useful to have precise notation;
+  identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
+  Identify each of these with a subset $\brk \lambda \subset \NN^2$ as is standard, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.\cite{Kleshchev}
+
+  Fixing some partition $\lambda \vdash 2n + r$, for $1 \leq i \leq j \leq l$, let $\beta_\lambda(i,j)$ and $\gamma_\lambda$ be the quantities
+  \begin{align*}
+    \beta_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i}^j a_t\\
+    \gamma_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i+1}^j a_t.
+  \end{align*}
+  Results due to Kleshchev and Brundan refer to \emph{normal} and \emph{good} numbers;
+  for these, we will use the facts that 1 is always normal and that $j$ is normal when $\beta_\lambda(i,j) \not\equiv 0 \pmod e$ for all $i \leq j$.
+  Further, we will use that $j$ is good if and only if $j$ is normal and $\gamma_\lambda(j,j') \not\equiv 0 \pmod e$ for all $j' \geq j$ normal.\cite{Brundan,Kleshchev}
 
@@
 This is proven via an inductive process; if $e \nmid n + r + 1$, then $M$ contains no sign subrepresentation, and this allows us to ``project'' down to the case $M_{2(n-1) + r}^r$, and prove irreducibility of $M$ from irreducibility of this space.
-
-Next, we
 
@@
 \end{proof}
-\begin{proposition}
+\begin{theorem}\label{Irreducibility Theorem}
   Suppose that $(n+r,n)$ is $e$ top-indivisible.
   Then, the representation $M_{2n + r}^r$ is irreducible. 
-\end{proposition}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{theorem}
+\begin{theorem}\label{Correspondence Theorem}
   Suppose $e > n + r + 1$.
@@
 Now we may use these in order to apply Young Tableau to characterize $V$.
-\begin{theorem}
+\begin{theorem}\label{Fibonacci Theorem}
   The irreducible components of $V$ are given by the following isomorphisms:
@@
 \begin{proposition}
-  For the same $m,s$ as above, we have the following composition series of specht modules:
+  For the same $m,s$ as above, we have the following composition series of Specht modules:
   \[
@@
 
-It is known that, for small $2n + r$, each specht module $S^{(n+r,n)}$ has a composition series of length 2.
+It is known that, for small $2n + r$, each Specht module $S^{(n+r,n)}$ has a composition series of length 2.
 We give in Figures \ref{Composition series e=3} through \ref{Composition series e=6} the map $M_{2n + r}^r \twoheadrightarrow U_{2n + r}^r$, which conjecturally illustrates the quotient $S^{(n+r,n)} \twoheadrightarrow U_{2n + r}^r$ for all $2n + r \leq 7$.
 
-\begin{figure}
+\begin{figure}[h]
 \iffalse
@@
 
-\begin{figure}
+\begin{figure}[h]
   \[
@@
 
-\begin{figure}
+\begin{figure}[h]
 \begin{align*} 
@@
 
-\begin{figure}
+\begin{figure}[h]
 \begin{align*}
@@
 We will prove in the following sections that $V$ and $W$ are compatible with the Hecke algebra relations.
+
+\subsection{Explicit Definition of $M$}
+We will give a more careful definition of the crossingless matchings representation here.
+\begin{definition}
+  A \emph{crossingless matching on $2n+r$ indices with $r$ anchors} is a partition of $\cbr{1,\dots,2n+r}$ into $n$ parts of size $2$ and $r$ of size 1 such that no two parts $(a,a')$ and $(b,b')$ satisfy $a < b < a' < b'$, and no parts $(c), (a,a')$ satisfy $a < c < a'$.
+  We will call these arcs and anchors, respectively.
+  Then, define $M^r_{2n+r}$ to be the $k$-vector space with basis the set of crossingless matchings on $2n+r$ indices with $r$ anchors.
+
+  In order to endow $M^r_{2n + r}$ with an $\SH$-action, consider some basis element $w_j$ and some element $(1 + T_i)$ of $\SH$.
+  The elements $\cbr{1} \cup \cbr{1 + T_i | 1 \leq i < 2n + r}$ generate $\SH$, so it is sufficient to define the action of $1 + T_i$ on $w_j$.
+
+  If $w_j$ has arc $(i,i+1)$, define $(1 + T_i)w_j := (1 + q)w_j$.
+  If $w_j$ has anchors $W(i) = i$ and $W(i+1) = i+1$, define $(1 + T_i)w_j := 0$.
+  If $w_j$ has anchor $W(i) = i$ and arc $W(i+1) = b$, define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$, $w_l(b) = b$, and all other arcs agree with $w_j$.
+  If $w_j$ has arcs $W(i) = a$ and $W(i+1) = b$, then define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$,$w(a) = b$, and all other acts agree with $w_j$. 
+  We verify that this is well-defined in Section \ref{Cross Relations}.
+\end{definition}
+
+We may alternately sharpen our topological definition;
+\begin{definition}
+Fix $2n + r$ distinct points $a_1,\dots,a_{2n + r}$ points along $\RR \times \cbr{0} \subset \RR^2$ and $r$ distinct points $b_1,\dots,b_r$ along $\RR \times \cbr{1}$.
+Then, define $M_{2n + r}^r$ to have basis given by the isotopy classes of $n + r$ paths connecting the points $a_1,\dots,a_{2n+r},b_1,\dots,b_r$ such that no distinct $b_i,b_j$ are connected by a path.
+
+We will take some basis element $w_j \in M_{2n +r}^r$ and define the action $(1 + T_i)w_j$.
+To do so, map $w_j$ through the natural embedding $\RR \times \brk{0,1} \hookrightarrow \RR \times \brk{\frac{1}{2},1}$, and form the figure $w_j^i$ by adjoining the lines connecting $a_l$ and $a_l + \prn{0,\frac{1}{2}}$ for all $l \neq i,i+1$ as well as paths from $a_i$ to $a_{i+1}$ and $a_i + \prn{0,\frac{1}{2}}$ to $a_{i+1} + \prn{0,\frac{1}{2}}$.
+This has either 0 or 1 path components which do not intersect $\RR \times \cbr{0,1}$;
+these form ``loops.''
+
+Take the figure $\tilde w_j^i$ without this component.
+If $\tilde w_j^i$ is not isotopic to some $w_l$, then define $(1 + T_i)w_j := 0$.
+If $\tilde w_j^i$ is isotopic to some $w_l$, define $(1 + T_i)w_j := (1 + q)w_l$ if $w_j^i$ has a loop and $(1 + T_i)w_j := q^{1/2}w_l$ otherwise.
+This process is illustrated in Figure \ref{Action}.
+\end{definition}
+
+Let the length of an arc $(i,j)$ be $l(i,j) := j - i + 1$.
+Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
+  This basis is illustrated for $M_{5}^1$ in Figure \ref{S5 Basis}.
+
+\begin{remark}
+  This definition gives a graphical calculus for working with our module.
+  It should be clear that, if $w_j^i$ has a loop then $w_l(i) = i+1$ and $w_l = w_j$.
+  Further, this easily defines an arbitrary composition:
+  \[
+    (1 + T_{i_1})\cdots(1 + T_{i_\ell})w_j = q^{(\ell - t)\frac{1}{2}}(1 + q)^tw_l
+  \]
+  if the figure we make via $(1+T_{i_1})\cdots(1+T_{i_\ell})$ is isotopic to $w_l$ after removing $t$ loops.
+\end{remark}
+
+  Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
+  call this the \emph{increasing lexicographical order basis}.
+  Further, we have a surjection $M_{2n + 2r}^0 \twoheadrightarrow M_{2n + r}^r$ which takes basis elements to basis elements;
+  this induces an order on the basis for $M_{2n +r}^r$, which we will henceforth refer to as the \emph{induced lexicographical order basis.}
+  This basis is illustrated for $M_{5}^1$ in Figure \ref{S5 Basis}.
 

### 2019-07-30 tex/Drafts/Draft-2.tex
Section 2 revisions.

@@
 
-  In the following section, we cite a theorem of James-Mathas which precisely characterizes the irreducibility of $S^\lambda$ in the case that $\lambda$ is $e$-regular, and we specialize this result to the case of two-row Specht modules.
-  This falls into two cases: either $e > n$, where $S^{(n+r,n)}$ is irreducible iff $e \nmid r+2,\dots,n+r+1$, or $e \leq n$, where the irreducibility of $S^{(n+r,n)}$ is complicated and depends on the characteristic of $k$.
+  Throughout the rest of the paper, it will be useful to have precise notation;
+  identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
+  Identify each of these with a subset $\brk \lambda \subset \NN^2$ as in \cite{Kleshchev}, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.
+  Say that $\lambda$ is \emph{$e$-regular} if $\lambda_i - \lambda_{i+1} < e$ for all $i$ and $\lambda_l < e$.
+
+  In the following subsection, we cite a theorem of James--Mathas which precisely characterizes the irreducibility of $S^\lambda$ in the case that $\lambda$ is $e$-regular, and we specialize this result to the case of two-row Specht modules.
+  This falls into two cases: either $e > n$, where $S^{(n+r,n)}$ is irreducible iff $e \nmid r+2,\dots,n+r+1$, or $e \leq n$, where the irreducibility of $S^{(n+r,n)}$ is more complicated and depends also on the characteristic of $k$.
   We will focus primarily on the former case.
 
-  Following this, we cite the branching theorems of Kleshchev-Brundan, which allow us to fully characterize the Socle of $\Res S^{\lambda}$.
-  This and some combinatorial arguments allow us to come to the main result of this section, which may loosely be stated as follows:
-  the composition series of $D^{(n+r,n)}$ is restrictive enough in many cases with $S^{(n+r,n)}$ irreducible and $e > n$ case that such a composition series uniquely characterizes irreducibles.
-  This will be immensely useful later for characterizing $M$ via Specht modules, as it will include all cases with $e > n + r + 1$.
+  Following this, we reproduce the branching theorems of Kleshchev--Brundan, which allow us to fully characterize the socle of $\Res D^{\lambda}$.
+  This and some combinatorial arguments yield the main result of this section, which allows us to determine certain $D^{(n+r,n)}$ via their composition series.
+  This will be instrumental later for characterizing the crossingless matchings representation $M_{2n + r}^r$ as a Specht module, and it will extend to all cases with $e > n + r + 1$.
 
   \subsection{Irreducibility of $S^\lambda$}
-  Let $k$ have characteristic $\ell$;
+  Let $\ell$ be the characteristic of $k$;
   then, set
@@
     p := \begin{cases}
-      \ell & \ell > 0\\
-      \infty & \ell = 0
+      \ell & \text{if }\ell > 0,\\
+      \infty & \text{if }\ell = 0.
+    \end{cases}
+  \]
+  Note that $p = e$ when $q = 1$.
+  For $h$ a natural number, let $\nu_p(h)$ be the $p$-adic valuation of $h$.
+  By convention, set $\nu_\infty(h) = 0$ for all $h$.
+  Define the function $\nu_{e,p} : \NN \rightarrow \cbr{-1} \cup \NN$ by
+  \[
+    \nu_{e,p}(h) := \begin{cases}
+      \nu_p(h) & e \text{if }\mid h\\
+      -1 & e \text{if }\nmid h
     \end{cases}.
   \]
-  Note that $p = e$ when $q = 1$.
-  For $h$ a natural number, let $\nu_p(h)$ be the $p$-adic evaluation of $h$.
-  As a convention, set $\nu_\infty(h) = 0$ for all $h$.
-  Define the function $\nu_{e,p} : \NN \rightarrow \cbr{-1} \cup \NN$ by
-  \[
-    \nu_{e,p}(h) := \begin{cases}
-      \nu_p(h) & e \mid h\\
-      -1 & e \nmid h
-    \end{cases}.
-  \]
-  Lastly, let $h_{ab}^\lambda$ be the hook length of node $(a,b)$ in $\brk \lambda$.
-  With this language, we may express the following theorem, part (ii) of which is named the \emph{carter criterion}, due to James-Mathas.\cite{Mathas-book}
-  \begin{theorem}[James-Mathas]
+  Lastly, let $h_{ab}^\lambda$ be the hook length of node $(a,b)$ in $\brk \lambda$ as defined in \cite{Kleshchev}.
+  With this language, we may express the following theorem, parts (ii)-(iii) of which are known as the \emph{Carter criterion} in the symmetric group case, due to James--Mathas.\cite{Mathas-book}
+  \begin{theorem}[James--Mathas]\label{Mathas Irreducibility}
     The following are equivalent:
@@
   \end{theorem}
+  \begin{proof}
+    See \cite{Mathas-book} theorem 5.42.
+  \end{proof}
   This result gives information solely on $e$-regular partitions, and the general irreducibility of $S^\lambda$ away from $p=2$ is not well understood.
-  We will henceforth specialize slightly to the case that $(n+r,n)$ is $e$-restricted.
+  We will henceforth specialize slightly to the case that $(n+r,n)$ is $e$-regular.
 
@@
       \item Suppose $e > n$.
-        Then, $S^{(n+r,n)}$ is irreducible iff $e \nmid l$ for all $r + 2 \leq l \leq n + r + 1$.
+        Then, $S^{(n+r,n)}$ is irreducible iff $e \nmid r + 2,r+3,\dots,n + r + 1$.
       \item Suppose $e \leq n$.
-        Then, $S^{(n+r,n)}$ is irreducible iff $e | r + 1$ and $\nu_{e,p}(h_{ab}^\lambda)$ acquires exactly two values.
+        If $S^{(n+r,n)}$ is irreducible, then $e \mid r + 1$.
     \end{enumerate}  
   \end{corollary}
-  In the case that $\lambda = (n+r,n)$ and $e \nmid r+2,r+3,\dots,n+r+1$, say that $\lambda$ is \emph{$e$-top-indivisible}.
-  Since no multiples of $e$ are in an interval of length $n$ in $\NN$, we have $e > n$, so this is precisely case (i) above.
-  \begin{proof}
-    The beginning condition implies that $\lambda$ is $e$-regular, which we will use below.
+  Note that the condition $e \nmid r+2,r+3,\dots,n+r+1$ implies that $e > n$.
+  \begin{proof}
+    Our initial assumption on $e$ implies that $\lambda$ is $e$-regular, which we will use below.
 
     \textbf{(i)}
-    Note that $\nu_p(l) \neq -1$ for all $l$ and only hook lengths in the top row may vanish mod $e$;
-    hence we may equivalently prove that $e$ divides no hook lengths in the leftmost $n$ columns of the second column.
+    Note that $\nu_p(h) \neq -1$ for all naturals $h$ and only hook lengths in the top row may vanish mod $e$ by Figure \ref{Hooks};
+    hence we may equivalently prove that $e$ divides no hook lengths in the leftmost $n$ columns of the second row by Theorem \ref{Mathas Irreducibility}.
     These hook lengths are precisely $r + 2,\dots,n+r+1$.
@@
     \textbf{(ii)}
-    Note that we have $\nu_{e,p}\prn{h^\lambda_{n-e+1,2}} \neq -1$.
+    Note that we have $\nu_{e,p}\prn{h^\lambda_{2,n-e+1}} \neq -1$, and $\nu_{e,p}\prn{h^\lambda_{2,n+r}} = -1$ so $\nu_{e,p}$ acquires at least two values.
     Suppose that $e \nmid r + 1$.
-    Then, \[\nu_{e,p}\prn{h^\lambda_{n-e+1,1}} = \nu_{e,p}\prn{h^\lambda_{n-e,2} + r + 1} = -1,\]
-    giving $S^{(n+r,n)}$ reducible.
-
-    \def\corsecsep{5pt}
-    \vspace{\corsecsep}
-    Now, suppose that $\nu$ acquires at least three values, and \[0 \leq \nu_{e,p}(h^{\lambda}_{ab}) < \nu_{e,p}\prn{h^{\lambda}_{a'b'}}\] and $S^{(n+r,n)}$ is irreducible.
-    If $b=b'$ then we have reducibility, so assume $b \neq b'$.
-    Further, if $a = a'$, then we may replace $a$ with the other column;
-    hence we may assume WLOG that $a \neq a'$ as well.
-
-    Note that $p$-adic valuation is monotonic, so $h^\lambda_{ab} < h^\lambda_{a'b'}$.
-    If $(a,b)$ is in the rightmost $r$ columns, then we may $0 \leq \nu_{e,p}\prn{h^\lambda_{a''b''}} \leq \nu_{e,p}\prn{h^\lambda_{ab}}$ for some $(a'',b'')$ in the rightmost $n$ columns;
-    this has the same hook length as a cell in the leftmost $n$ columns and bottom row, so we may assume $(a,b)$ is not in the rightmost $r$ columns.
-    Similar logic allows us to assume $(a',b')$ is in the leftmost $n$ columns as well.
-
-    If $b < b'$, then $\nu_p(h_{ab}) = \nu_p(h_{ab'}) < \nu(h_{a'b'})$ while $h_{ab'} > h_{a'b'}$, a contradiction.
-    If $b > b'$, then $\nu_p(h_{ab}) = \nu_p(h_{ab'})$ and $h_{ab} < h_{ab'}$, so there is some $c < b$ with $\nu_{e,b}(h_{ab}) = \nu_{e,p}(h_{ac})$; we may replace $b$ with $c$, and repeat until $b = b'$ to reach contradiction.
-
-    \vspace{\corsecsep}
-    Finally, assume $e | r + 1$ and $\nu_{e,p}$ acquires two values.
-    Since $e | r + 1$, $e \mid h_{a1}^\lambda$ iff $e \mid h_{a2}$;
-    since $\nu_{e,p}$ acquires only two values, this proves that $\nu_{e,p}(h_{a1}) = \nu_{e,p}(h_{a2})$ across these rows, giving the lemma.
-  \end{proof}
-
-  From condition (ii) we see that irreducibiliy at $e > n$ is not dependent on $p$, and we may cover many modular cases without reference to the characteristic of $k$.
-  We will finish our discussion of irreducibilty of $S^\lambda$ via the following special cases of (ii) above.
+    Then, \[\nu_{e,p}\prn{h^\lambda_{1,n-e+1}} = \nu_{e,p}\prn{h^\lambda_{2,n-e+1} + r + 1} = -1,\]
+    giving $S^{(n+r,n)}$ reducible by Theorem \ref{Mathas Irreducibility}.
+  \end{proof}
+
+  \begin{figure}
+  \ytableausetup{mathmode,boxsize=4.5em}
+  \begin{ytableau}
+    n+r+1 & n + r & \dots & r + 2 & r & r-1 & \dots & 1\\ 
+    n & n-1 & \dots & 1
+  \end{ytableau}
+  \ytableausetup{mathmode,boxsize=normal}
+  \caption{The young diagram corresponding to the partition $(n+r,n)$ with filled-in ook lengths.}\label{Hooks}
+\end{figure}
+
+  From part (i) we see that irreducibility at $e > n$ is not dependent on $p$, and we may cover many modular cases without reference to the characteristic of $k$.
+  We will finish our discussion of irreducibility of $S^\lambda$ via sharp characterization of the $e \leq n$ case.
   \begin{corollary}
     If $r = 0$, assume $e > 2$.
-    Suppose $e \leq n$.
-    \begin{enumerate}[label={(\roman*)}]
-      \item Suppose $p > n + r + 1$. Then, $S^{(n + r,n)}$ is irreducible iff $e | r + 1$.
-      \item Suppose $p = 2$. Then, $S^{(n+r,n)}$ is not irreducible.
-    \end{enumerate}
+    Suppose $e \leq n$, and suppose $p > n + r + 1$.
+    Then, $S^{(n+r,n)}$ is irreducible if and only if $e \mid r+1$.
   \end{corollary}
   \begin{proof}
-    (i) is clear.
-    (ii) is given by noting that $e + r + 1 \geq 2e$;
-    then, $h_{n-e+1,1} - h_{n-e+1,2} \geq 1$, giving reducibility.
+    This follows from the proof of Corollary \ref{S irreducibility} part (ii) and the fact that $\nu_p(h) = \nu_p(h')$ for all naturalls $h,h'$. 
   \end{proof}
   \subsection{Branching}
-  In this section as well as later sections, we will consider the restruction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}\prn{S_{2n + r - 1}}$.
-  We verify in Appendix \ref{Algebra} that any two subalgebras of $\SH$ generated by $2n + r - 2$ simple transpositions give isomorphic restrictions of representations (through a particular isomorphism of the subalgebras).
+  In this section as well as later sections, we will consider the restriction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}\prn{S_{2n + r - 1}}$.
+  We verify in Appendix \ref{Algebra} that any two subalgebras of $\SH$ generated by $2n + r - 2$ simple transpositions are canonically isomorphic, and the corresponding restrictions are canonically isomorphic via this isomorphism of algebras.
   We will hence abuse notation, pick one such subalgebra $\SH'$, and notate $\Res_{\SH'}^\SH W$ by $\Res W$ for any $\SH$-module $W$.
-
-  Throughout the rest of the paper, it will be useful to have precise notation;
-  identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
-  Identify each of these with a subset $\brk \lambda \subset \NN^2$ as is standard, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.\cite{Kleshchev}
 
@@
   \end{align*}
+  Note that $\beta_\lambda(i,j)$ is the hook length of cell $(a_1 + \dots + a_{i-1}+1,\lambda_j)$.
+
   Results due to Kleshchev and Brundan refer to \emph{normal} and \emph{good} numbers;
@@
   Further, we will use that $j$ is good if and only if $j$ is normal and $\gamma_\lambda(j,j') \not\equiv 0 \pmod e$ for all $j' \geq j$ normal.\cite{Brundan,Kleshchev}
-
-  The following statements, collectively called \emph{modular branching rules} of $D^\lambda$, were originally written by Kleshchev for Specht modules of the group algebra $k\brk{S_n}$, then generalized to the Hecke algebra case by Brundan.\cite{Kleshchev}\cite{Brundan}
-  They entirely characterize the Socle of $\Res D^\lambda$, as well as the condition that $\soc\prn{\Res D^\lambda} \simeq \Res D^\lambda$.
+  When $\lambda(i) = \mu$ for $i$ normal, write $\mu \xrightarrow{\text{normal}} \lambda$, and similar in the good case.
+
+  The following statements, collectively known as \emph{modular branching rules} of $D^\lambda$, were originally written by Kleshchev for Specht modules of the group algebra $k\brk{S_n}$, then generalized to the Hecke algebra case by Brundan.\cite{Kleshchev,Brundan}
+  They entirely characterize the socle of $\Res D^\lambda$, as well as semisimplicity od $\Res D^\lambda$.
   \begin{theorem}[Kleshchev-Brundan]
@@
       &\simeq \begin{cases}
-        k & \mu \xrightarrow{\text{normal}} \lambda\\
-        0 & \text{otherwise}
+        k & \text{if }\mu \xrightarrow{\text{normal}} \lambda,\\
+        0 & \text{otherwise}.
       \end{cases}\\
@@
       &\simeq \begin{cases}
-        k & \mu \xrightarrow{\text{good}} \lambda\\
+        k & \text{if } \mu \xrightarrow{\text{good}} \lambda\\
         0 & \text{otherwise}
@@
       \soc\prn{\Res \, D^{(n+r,n)}} \simeq \begin{cases}
-        D^{(n + r - 1,n)} & e \mid r+2\\
-        D^{(n + r,n-1)} & e \nmid r+2, \; e \mid r\\
-        D^{(n+r-1,n)} \oplus D^{(n+r,n-1)} & e \nmid r+2,r
-      \end{cases}.
+        D^{(n + r - 1,n)} & \text{if }e \mid r+2\\
+        D^{(n + r,n-1)} &e \text{if }e\nmid r+2, \; e \mid r\\
+        D^{(n+r-1,n)} \oplus D^{(n+r,n-1)} & \text{if } e \nmid r+2,r
+      \end{cases}
     \]
@@
     \end{align*}
-    Since $2$ is the largest removable number, $D^{(n+r,n-1)} \subset D^{(n+r,n)}$ iff $e \nmid r + 2$.
-    Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)} \subset D^{(n+r,n)}$ iff 1 is good iff $e \nmid r$
-  \end{proof}
-
-  Now that we've characterized how these restrict, we can describe how strongly these restrictions characterize irreducibles.
-  Namely, we will prove that a composition series consistent with $(n+r,n)$ and $e$ top-indivisibility of $(n+r-1,n+1)$ is sufficient to determine that an irreducible is $D^{(n+r,n)}$ when either $r \neq 0$ or $e \neq 4$.
+    Since $2$ is the largest removable number, $D^{(n+r,n-1)} \subset D^{(n+r,n)}$ if and only if $e \nmid r + 2$.
+    Further, if $e \nmid r + 2$, then $D^{(n+r-1,n)} \subset D^{(n+r,n)}$ if and only if 1 is good;
+    this is equivalent to $e \nmid r$.
+  \end{proof}
+
+  Now that we've characterized how $D^\lambda$ restrict, we can describe how strongly these restrictions characterize irreducibles.
+  Namely, we will prove that some $D^\lambda$ having the same composition series as  $D^{(n+r,n)}$ is sufficient to determine that $\lambda = (n+r,n)$ in the case that condition (i) of Corollary \ref{S irreducibility} holds and either $r \neq 0$ or $e \neq 4$.
   \begin{proposition}\label{Combinatorics}
@@
     \begin{enumerate}[label={(\roman*)}]
-      \item Suppose $r > 0$, suppose $e \nmid r+1, r + 2,\dots,n + r + 1$, and suppose either $e \mid r$ or $e \nmid r$.
+      \item Suppose $r > 0$, suppose $e \nmid r+1, r + 2,\dots,n + r + 1$, and suppose either $e \mid r$ or $e \nmid r-2$.
         If $D^\lambda$ has the composition series 
@@
     Note that $e > n$.
+    Further, note that the above characterizations are necessary regardless of $e$-regularity;
+    in the case that $\mu$ below fails too be $e$-regular, this proposition will prove that $\lambda$ does not satisfy \label{D Composition Series}, a contradiction.
 
@@
     Let $\varpi := (n+r-1,n,1)$, let $\varsigma := (n+r-1,n+1)$, and let $\mu := (n + r,n)$.
-    Since $D^{(n+r-1,n)} \subset \Res \, D^\lambda$, we have $(n + r - 1,n) \longrightarrow \lambda$, implying $\lambda = \varpi,\varsigma,\mu$.
-    We will show that $\varpi, \varsigma$ do not have socle compatible with \eqref{D Composition Series};
-    then, we will have $\lambda = \mu$.
-
-    Suppose that $\lambda = \varpi$.
+    Since $D^{(n+r-1,n)} \subset \Res \, D^\lambda$, we have $(n + r - 1,n) \longrightarrow \lambda$, implying $\lambda \in \cbr{\varpi,\varsigma,\mu}$.
+    We will show that $\varpi, \varsigma$ do not have socle compatible with \eqref{D Composition Series}, allowing us to conclude $\lambda = \mu$.
+
+    If $\varpi$ or $\varsigma$ are not $e$-regular, then $D^\varpi = 0$ or $D^\varsigma = 0$, and we may immediately rule these out;
+    henceforth assume that these are each $e$-regular.
+
+    First suppose that that $\lambda = \varpi$.
     We will break into cases with $r$.
@@
         Further, $\gamma_\varpi(2,3) = n \not\equiv 0 \pmod e$, so 2 is good and $D^{(n+r-1,n-1,1)} \subset D^\varpi$, which is not a composition factor in \eqref{D Composition Series}.
-        Hence, by Jordan-H\"older, $\lambda \neq \varpi$.\cite{Etingof}
+        Hence, by the Jordan-H\"older theorem \cite{Etingof}, we have $\lambda \neq \varpi$.
 
       \item Suppose that $r = 1$.
-        Then, $\varpi = (n,n,1)$ has $\gamma_{\varpi}(1,2) = n \not\equiv 0 \pmod e$, giving $D^{(n,n-1,1)} \subset D^\varpi$ and hence $\lambda \neq \varpi$.
+        Then, $\varpi = (n,n,1)$ has $\gamma_{\varpi}(1,2) = n \not\equiv 0 \pmod e$, giving $D^{(n,n-1,1)} \subset D^\varpi$ and hence $\lambda \neq \varpi$ as in the previous case.
     \end{itemize} 
@@
     \item Suppose $r = 2$.
-      Then $\Res \, D^\varsigma \simeq D^{(n+1,n)}$ is irreducible, contradicting \eqref{D Composition Series}. 
+      Then $\Res \, D^\varsigma \simeq D^{(n+1,n)}$ is irreducible, as $\varsigma = (n+1,n+1)$ has rows of the same length;
+      this contradicts \eqref{D Composition Series}. 
     \item Suppose $r < 2$. 
@@
   \end{itemize}
+  This completes the proof.
 
   \textbf{(ii)}
-  This result is easier than the previous result;
-  since the socle of $D^\lambda$ is irreducible, we require that 1 is the only normal number and $\lambda(1) = (n,n-1)$.
+  Since the socle of $D^\lambda$ is irreducible, we require that 1 is the only normal number and $\lambda(1) = (n,n-1)$.
   This reduces to the cases of $\varsigma := (n + 1, n - 1)$ and $\mu := (n,n)$;
@@
 \begin{theorem}\label{Irreducibility Theorem}
-  Suppose that $(n+r,n)$ is $e$ top-indivisible.
+  Suppose that $e \nmid r+2,r+3,\dots,n+r+1$.
   Then, the representation $M_{2n + r}^r$ is irreducible. 
@@
 
-  Note that, by $e$ top-indivisibility of $(n+r,n)$, we have $e \nmid r+2,\dots,n+r$, and hence $(n+r-1,n-1)$ is $e$ top-indivisible as well.
+  Note that, by definition, $e \nmid r+2,\dots,n+r$ as well, and hence $(n+r-1,n-1)$ satisfies the hypotheses of the proposition as well..
   Then, due to the inductive hypothesis, there is some action $h' \in \SH(S_{2(n-1) + r})$ sending $\varphi((1 + T_i)w)$ to the image of a basis vector;
@@
 
-\bibliographystyle{plain} 
+\bibliographystyle{numeric} 
  \bibliography{../RepBib}

### 2019-07-30 tex/kernel_final.tex
Edits finished, ready for further comment

@@
 
-\title{A discussion of the intersection of the kernels of each $(1+T_i)$ acting on $W_{2n+r}^r$}
+\title{A discussion of the intersection of the kernels of each $(1+T_i)$ acting on $M_{2n+r}^r$}
 \author{Miles Johnson \& Natalie Stewart}
@@
 
-{\color{magenta} Natalie comments are magenta.}
-
 \section{Introduction}
@@
 Let $\{T_i\}$ be the transpositions generating the Hecke algebra $\SH_{2n+r}(q)$.
-Let $W_{2n+r}^r$ be the generalized crossingless matchings representation with $2n+r$ nodes, $r$ of which are anchors.
+Let $M_{2n+r}^r$ be the generalized crossingless matchings representation with $2n+r$ nodes, $r$ of which are anchors.
 Fix the standard basis; we will refer to no other basis in this document.
-Here we characterize the intersection of the kernels of each $(1+T_i)$, a subrepresentation of $W_{2n+r}^r$.
+Here we characterize the intersection of the kernels of each $(1+T_i)$, a subrepresentation of $M_{2n+r}^r$.
 I claim this intersection is trivial for $e>n+r+1$ and one dimensional for $e=n+r+1$.
 
-For compactness, in this document I use $\sim $ to denote "proportional to".
+For compactness, in this document I use $\sim $ to denote "proportional to". For convenience, define $M_0^0$ to be the zero representation.
 
@@
 
-  Fix some basis element $\psi\in W_{2n+r}^r$.
+  Fix some basis element $\psi\in M_{2n+r}^r$.
 For $1 \leq a,b \leq 2n + r$ define $\psi(a):=b$ iff $a$ and $b$ are matched in $\psi$, $\psi(a):=a$ if $a$ is an anchor in $\psi$.
-Given that $\psi$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $\psi(a,b)$ of $\psi$ to be the basis element $\sigma\in W_{b-a+1}^{r'}$ specified by $\sigma(i)=\psi(i+a-1)-a+1$.
+Given that $\psi$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $\psi(a,b)$ of $\psi$ to be the basis element $\sigma\in M_{b-a+1}^{r'}$ specified by $\sigma(i)=\psi(i+a-1)-a+1$.
 This sub-matching is defined for $a<b$ when $\psi(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$.
-See Figure 1.
+See \ref{sub-matching example}.
 
@@
 For any other $a,b$, we define $\psi(a,b)$ to be an element of the representation with no nodes.
+
+  \label{sub-matchings}
 \end{definition}
@@
 		\end{gathered}}$
-	\caption{$\psi\in W_6^0$ is pictured on the left, $\sigma\in W_4^0$ is pictured on the right. $\psi(3,6)=\sigma$. $\psi(2,5)$ is not a sub-matching.}
-	\label{S6 Basis}
+	\caption{$\psi\in M_6^0$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right. $\psi(3,6)=\sigma$. $\psi(2,5)$ is not a sub-matching.}
+	\label{sub-matching example}
 \end{figure}
 
-Define the rainbow element $R\in W_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$.
+Define the rainbow element $R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$.
 In other words, the basis element with all anchors to the left then a rainbow.
@@
 \begin{proposition}
-	Let $w$ be an arbitrary vector in $W_{2n+r}^r$. I claim that if $w\in \cap\text{ker}(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero.
+	Let $w$ be an arbitrary vector in $M_{2n+r}^r$. I claim that if $w\in \cap\text{ker}(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero.
+
+	\label{rainbow nonzero}
 \end{proposition}
@@
 Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively.
-Examples are pictured in figure 2.
+Examples are pictured in \ref{shifted rainbow}.
 Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.
@@
 	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right}
+	\label{shifted rainbow}
 \end{figure}
@@
 The coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.
+
+	\label{shifted rainbow coeffs}
 \end{proposition}
@@
 	$Q_1Q_n-Q_{n-1}=Q_{n+1}$
+
+	\label{Q alg}
 \end{lemma}
@@
 
-$$Q_1Q_n-Q_{n-1}=\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}=$$
-
-$$\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}=\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}$$.
+\begin{align*}
+Q_1Q_n-Q_{n-1}=&\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}\\
+=&\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}\\
+=&\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}
+\end{align*}
 
@@
 Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$.
-This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in figure 3.
+This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in \ref{shifted relations}.
 I claim the following:
@@
 		The only basis elements $\psi$ where $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist\footnote{we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$}.
+
 	\end{center}
 
-	Note that the action of any $(1+T_z)$ on a basis element $\psi$ creates exactly two lines: an arc of length two connecting $z$ and $z+1$, and either an anchor or an arc of length $\geq 2$ connecting $\psi(z)$ and $\psi(z+1)$.\footnote{Although this fact follows directly from our definition of the representation, it will be used throughout the document, so it is important that the reader understands it.} The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.
+	Note that the action of any $(1+T_z)$ on a basis element $\psi$ creates exactly two lines: an arc of length two connecting $z$ and $z+1$, and either an anchor or an arc of length $\geq 2$ connecting $\psi(z)$ and $\psi(z+1)$.\footnote{Although this fact follows directly from our definition of the representation, it will be used throughout the document, so it is important that the reader understands it.\label{two humps created}} The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.
 
-	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in figure 3.
+	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in \ref{shifted relations}.
 Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition.
-We note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
+Me note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
 Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$.
@@
 
-	Given this claim and lemma 2.4, the proposition follows quickly through induction:
+	Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction:
 
@@
 	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$.
-By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_i=0$ so $c_{\phi_{i+1}}=Q_1Q_i-Q_{i-1}=Q_{i+1}$ by lemma 2.4.
+By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_i=0$ so $c_{\phi_{i+1}}=Q_1Q_i-Q_{i-1}=Q_{i+1}$ by lemma \ref{Q alg}.
 $\theta_i$ is an identical proof, so the proposition follows.
@@
 		\]
-    \caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $W_{8}^2$ and $i=2$.}
-		\label{Action}
+    \caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $M_{8}^2$ and $i=2$.}
+		\label{shifted relations}
 	\end{figure}
@@
 
-We are now ready to prove our first interesting result. Define $e$ as before.
+Me are now ready to prove our first interesting result. Define $e$ as before.
 
 \begin{proposition}
-	Let $W_{2n+r}^r$ be a generalized crossingless matchings representation. Suppose $e$ does not divide $n+r+1$. Then $\cap\text{ker}(1+T_i)=\emptyset$.
+	Let $M_{2n+r}^r$ be a generalized crossingless matchings representation. Suppose $e$ does not divide $n+r+1$. Then $\cap\text{ker}(1+T_i)=0$.
+
+	\label{trivial kernel}
 \end{proposition}
@@
 \begin{proof}
-	Suppose $\cap\text{ker}(1+T_i)=K\not=\emptyset$.
-Take $w\in K$.
-By Proposition 2.2, the coordinate of the rainbow vector $R$ is nonzero; suppose the coordinate is $c$.
-By proposition 2.3, the coordinates of the basis elements $R_{L,n+r-1}$ and $R_{L,n+r-2}$ are $Q_{n+r-1}c$ and $Q_{n+r-2}c$ respectively.
+	Suppose $\cap\text{ker}(1+T_i)=K\not=0$.
+Take nonzero $w\in K$.
+By Proposition \ref{rainbow nonzero}, the coordinate of the rainbow vector $R$ is nonzero; suppose the coordinate is $c$.
+By proposition \ref{shifted rainbow coeffs}, the coordinates of the basis elements $R_{L,n+r-1}$ and $R_{L,n+r-2}$ are $Q_{n+r-1}c$ and $Q_{n+r-2}c$ respectively.
 
 	Consider the coordinate of $R_{L,n+r-1}$ in $(1+T_1)w$.
-Using the same logic as in the proof of proposition 2.3, we note that if a basis element $\psi$ has no anchor at position $3$ and is not equal to $R_{L,n+r-2}$, $(1+T_1)\psi\not\sim R_{L,n+r-1}$.
-Thus the desired coordinate is equal to $(1+q)Q_{n+r-1}c+q^{1/2}Q_{n+r-2}c=-q^{1/2}Q_{n+r}c$ by lemma 2.4.
+Using the same logic as in the proof of proposition \ref{shifted rainbow coeffs}, we note that if a basis element $\psi$ has no anchor at position $3$ and is not equal to $R_{L,n+r-2}$, $(1+T_1)\psi\not\sim R_{L,n+r-1}$.
+Thus the desired coordinate is equal to $(1+q)Q_{n+r-1}c+q^{1/2}Q_{n+r-2}c=-q^{1/2}Q_{n+r}c$ by lemma \ref{Q alg}.
 Since $w\in K$, we must have $-q^{1/2}Q_{n+r}c=0$.
-We have that $c$ is nonzero, and we assume $q$ nonzero, and $Q_{n+r}$ is zero iff $q$ is a root of $q^{n+r}+...+1$, implying $e|n+r+1$.
-Thus we have arrived at contradiction, and $K=\emptyset$.
+Me have that $c$ is nonzero, and we assume $q$ nonzero, and $Q_{n+r}$ is zero iff $q$ is a root of $q^{n+r}+...+1$, implying $e|n+r+1$.
+Thus we have arrived at contradiction, and $K=0$.
 \end{proof}
@@
 In this section we will fully characterize $\cap\text{ker}(1+T_i)$ when $e=n+r+1$.
-We will prove that it is one dimensional and give a basis.
+Me will prove that it is one dimensional and give a basis.
 Note that we still have not proved the kernel is trivial when $e$ divides but is not equal to $n+r+1$.
@@
 \vspace{5mm}
-The following proposition states the forward direction of our characterization: if the kernel is nontrivial, it must have the following properties.
+First let us formalize a useful property of sub-matchings.
+
+\begin{definition}
+	Given a basis element $\psi\in M_{2n+r}^r$, specify some sub-matching $\psi(a,b)$.
+Let $\Res_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}M_{2n+r}^r$ be the restriction to the sub-algebra generated by transpositions $T_a,...,T_{b-1}$.
+Define $Y_\psi\subset\Res_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}M_{2n+r}^r$ to be the subrepresentation generated by the set of basis elements $\{\sigma| \sigma(1,a-1)=\psi(1,a-1),\ \sigma(b+1,2n+r)=\psi(b+1,2n+r)\}$.
+\end{definition}
+
+\begin{lemma}
+	Take a basis element $\psi\in M_{2n+r}^r$. Suppose $\psi$ has some sub-matching $\psi(a,b)$ with $r'$ anchors. Define $Y_\psi$ with respect to this sub-matching.
+
+	The map $\rho:Y_\psi\rightarrow M_{b-a+1}^{r'}$ defined by $$\rho(\sigma)=\sigma(a,b)$$ is an isomorphism of representations.
+
+	\label{sub-matching isomorphism}
+\end{lemma}
+
+\begin{proof}
+
+	The map is clearly bijective. Thus it is sufficient to prove the following: $$\rho(T_{i+a-1}\sigma)=T_i\rho(\sigma)$$
+
+	As mentioned in the previous section, the action of a transposition $T_i$ can change at most 4 nodes, so we need to show that the transpositions end up changing the same nodes in the same way in  $\rho(T_{i+a-1}\sigma)$ and $T_i\rho(\sigma)$.
+
+	Suppose $\sigma(i+a-1)=s,\sigma(i+a)=t$.
+Then $(T_{i+a-1}\sigma)(i+a-1)=i+a$, $(T_{i+a-1}\sigma)(s)=t$, so $\rho(T_{i+a-1}\sigma)(i)=i+1$, $\rho(T_{i+a-1}\sigma)(s-a+1)=t-a+1$.
+Separately, $\rho(\sigma)(i)=s-a+1$ and $\rho(\sigma)(i+1)=t-a+1$, so $T_i\rho(\sigma)(i)=i+1$ and $T_i\rho(\sigma)(s-a+1)=t-a+1$ as desired.
+So the map is an isomorphism and the lemma is proved.
+\end{proof}
 
 \vspace{5mm}
+The lemma above motivates a recursive characterization of the kernel. To do this, it will be convenient to define some notation.
+
+\begin{definition}
+	Recall $Q_i:=(q^i+...+q+1)/q^{i/2}(-1)^i$ (lemma \ref{Q alg}). For $a>0$ define $Q(0,b):=1$. For $b>a>0$ define $$\Q_b^a:=\frac{Q_{b-1}...Q_{b-a}}{Q_1...Q_{a-1}}$$
+
+\end{definition}
+
+\begin{definition}
+	For $\psi \in M_0^0$, define the function $x_\psi(q):=1$.
+
+	For all other basis elements $\psi\in M_{2n+r}^r$, we define $x_\psi$ recursively:
+
+	$$x_\psi(q):=x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}$$
+
+	I will refer to $x_\psi$ as the \textbf{coordinate function} of $\psi$.
+
+	\label{coeff def}
+\end{definition}
+
+\vspace{2mm}
+The following proposition states the forward direction of our characterization.
 \begin{proposition}
 
-	Let $W_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$.
+	Let $M_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$.
 Let $w\in\cap\text{ker}(1+T_i)$.
-WLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition 2.2).
-	\\
+MLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition \ref{rainbow nonzero}).
+Then the coordinate of any basis element $\psi\in M_{2n+r}^r$ in $w$ is $x_{\psi}(q)$.
 
-	\begin{center}	
-		(i) For any basis element $\beta\in W_{2n+r}^r$, the coordinate of $\beta$ in $w$ must be some rational function of $q$, say $x_\beta(q)$.
-
-	\end{center}
-	\vspace{5mm}
-
-	Generally, for any matching $\alpha$, define $x_\alpha$ to be the rational function corresponding to the necessary coordinate of that basis element in its respective kernel element.
-These functions are defined recursively in the next statement.
-
-	\vspace{5mm}
-	Suppose $\beta(1)=a$. Assume 1 is not an anchor. Then $\beta$ has two sub-matchings $\alpha_1=\beta(2,a-1)$ and $\alpha_2=\beta(a+1,2n+r)$, and we have the following:
-	\\
-
-	\begin{center}
-
-		(ii) $x_\beta(q)=x_{\alpha_1}(q)x_{\alpha_2}(q)\frac{Q_{n+r-1}...Q_{n+r-(a/2)}}{Q_1...Q_{a/2-1}}$
-
-	\end{center}
-
-	\vspace{5mm}
-
-	If 1 is an anchor, we have a sub-matching $\alpha_3=\beta(2,2n+r)$ and I claim $x_\beta(q)=x_{\alpha_3}(q)$.
+	\label{kernel characterization}
 
@@
 
-\vspace{5mm}
-Before proving this proposition, it will be useful to clarify exactly what it states.
-
-\vspace{5mm}
-The first statement of this proposition says that, given an element of the kernel $w$, we can write the coordinate of any basis element $\beta$ in $w$ as a rational function of $q$ as long as $Q_1...Q_{n+r-1}\not=0$.
-
-\vspace{5mm}
-The second statement is meant to inductively define the coordinate of an arbitrary basis element.
-The first statement lets this induction make sense.
-Essentially, the second statement says the following: we can find the coordinate of any basis element by dividing it into two sub-matchings and scaling by a specific constant which depends on the lengths of the sub-matchings.
-
-\vspace{5mm}
-An illustration of this proposition is shown in figure 4.
+An illustration of this proposition is shown in figure \ref{coeff example}.
 
@@
 The coordinate of the first element is $x(q)=x_2(q)x_3(q)\frac{Q_5Q_4Q_3}{Q_1Q_2}$, where for $q$, $e=7$}
+		\label{coeff example}
 	\end{figure}
 
-\vspace{5mm}
-The structure of the proof is as follows:
+\begin{proof}
+	Suppose $\psi(1)=a$.
+The proof is structured as follows: use proposition \ref{shifted rainbow coeffs} to find the coefficient of the basis element with $\lfloor a/2\rfloor$ humps then a rainbow element; use the same proposition in a reversed manner to find the coefficient of the basis element consisting of the rainbow for the first $a$ nodes, then the rainbow for the final $2n+r-a$ nodes; finally, we finish the proof through induction using lemma \ref{sub-matching isomorphism}.
 
-\begin{enumerate}
-	\item Use proposition 2.3 to find the coefficient of the basis element with $a/2$ humps then a rainbow element.
-
-	\item Use proposition 2.3 in a somewhat reversed manner to find the coefficient of the basis element consisting of the rainbow for the first $a$ nodes then the rainbow for the final $2n+r-a$ nodes.
-
-	\item Finish the proof through induction.
-\end{enumerate}
-
-\vspace{10mm}
-\begin{proof}
-	Note that statement (i) was necessary to state (ii), but it is natural to prove both statements together, so this is how we will proceed.
-	\\
-
-	By proposition 2.2 the rainbow element has coordinate 1 in $w\in W_{2n+r}^r$.
-By proposition 2.3 the element $R_1:=R_{L,n+r-1}$ has coordinate $Q_{n+r-1}$ in $w$.
-Then $R_1(3,2n+r)$ is the rainbow element in  $W_{2(n-1)+r}^r$, so the element $R_2$ defined by $R_2(1,2)=R_1(1,2)$, $R_2(3,2n+r)=R_{L,n+r-2}\in W_{2(n-1)+r}^r$ has coordinate $Q_{n-1}Q_{n-2}$.
-Generally, define $R_i$ by $R_i(1,2(i-1))=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r)=R_{L,2n+r-i}$.
+	\vspace{2mm}
+	By proposition \ref{shifted rainbow coeffs} the element $R_1:=R_{L,n+r-1}$ has coordinate $Q_{n+r-1}$ in $w$.
+Then $R_1(3,2n+r)$ is the rainbow element in  $M_{2(n-1)+r}^r$, so the element $R_2$ defined by $R_2(1,2):=R_1(1,2)$, $R_2(3,2n+r):=R_{L,n+r-2}\in M_{2(n-1)+r}^r$ has coordinate $Q_{n-1}Q_{n-2}$.
+Generally, define $R_i$ by $R_i(1,2(i-1)):=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r):=R_{L,n+r-i}\in M_{2(n-i+1)+r}^r$.
 Then the coefficient of $R_i$ is $Q_{n+r-1}...Q_{n+r-i}$.
@@
 
-	Now define basis elements $E_i$ by $E_i(2i+1,2n+r)=R_i(2i+1,2n+r)$, $E_i(1,2i)=R$, $R$ the appropriate rainbow element.
+	Now define basis elements $E_i$ by $E_i(2i+1,2n+r):=R_i(2i+1,2n+r)$, $E_i(1,2i):=R$, the appropriate rainbow element.
 By the same argument as above, if $E_i$ has coordinate $c$ in $w$, $R_i$ has coordinate $Q_{i-1}...Q_{1}c$.
-One way to make this more clear is to consider intermediate basis elements $\alpha_j^{E_i}$ defined by $\alpha_j^{E_i}(2i+1,2n+r)=E_i(2i+1,2n+r)$ and $\alpha_j^{E_i}(1,2i)=R_{L,j}$.
-Then the coordinates of $\alpha_j^{E_i}(2i+1,2n+r)$ in terms of the coordinate $c$ of $E_i$ are $Q_{i-1}...Q_{i-j}$, and $R_i=\alpha_{i-1}^{E_i}$.
+One way to make this more clear is to consider intermediate basis elements $\sigma_j^{E_i}$ defined by $\sigma_j^{E_i}(2i+1,2n+r):=E_i(2i+1,2n+r)$ and $\sigma_j^{E_i}(1,2i):=R_{L,j}$.
+Then the coordinates of $\sigma_j^{E_i}(2i+1,2n+r)$ in terms of the coordinate $c$ of $E_i$ are $Q_{i-1}...Q_{i-j}$, and $R_i=\sigma_{i-1}^{E_i}$.
 
-	Since we assume $Q_i\not=0$ for $i< n+r$, this implies the coefficient of $E_i$ is $\frac{Q_{n+r-1}...Q_i}{Q_1...Q_{i-1}}$.
-In particular, returning to our desired basis element $\beta$, the coordinate of $E_{a/2}$ is $\frac{Q_{n+r-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$.
-	\\
+	Since we assume $Q_i\not=0$ for $i< n+r$, this implies the coefficient of $E_i$ is $\frac{Q_{n+r-1}...Q_{n+r-i}}{Q_1...Q_{i-1}}=\Q^i_{n+r}=x_{E_i}$.
+In particular, returning to our desired basis element $\psi$, the coordinate of $E_{\lfloor a/2\rfloor}$ is $\Q^{\lfloor a/2\rfloor}_{n+r}=x_{E_{\lfloor a/2\rfloor}}$.
 
-	Now, I claim that this method can be applied to any rainbow sub-matching in exactly the same way. In other words, extraneous nodes add no complexity to this argument.
+	Note that the above logic only uses proposition \ref{shifted rainbow coeffs}, which requires only that a sub-matching be a rainbow element.
+So, suppose some basis element $\sigma$ has sub-matching $\sigma(s,t)=R$ with $n'$ nodes and $r'$ anchors, and that the coordinate of $\sigma$ in $w$ is $c$.
+Then it follows that the basis element $\theta_i$ defined by $\theta_i(1,s-1):=\sigma(1,s-1)$, $\theta_i(t+1,2n+r):=\sigma(t+1,2n+r)$, and $\theta_i(s,t):=E_i$ has coefficient $\Q^i_{n'+r'}c$.
+In other words, defining $Y_\psi$ with respect to the sub-matching $\sigma(s,t)$, the operation of finding the coordinate of $E_i$ given the coordinate of $R=\sigma(s,t)$ commutes with the isomorphism to $Y_\psi$.
+An example is given in figure \ref{kernel induct characterization example}.
 
-	Formally, given some basis element $\alpha$, suppose $\alpha(s,t)=R$ with $2n'+r'$ nodes and $r'$ anchors, and that $\alpha$ has coordinate $c$.
-Then the basis elements $\theta_i$ defined by $\theta_i(1,s-1)=\alpha(1,s-1)$, $\theta_i(t+1,2n+r)=\alpha(t+1,2n+r)$, and $\theta_i(s,t)=E_i$ have coordinates $\frac{Q_{n'+r'-1}...Q_{n'+r'-i}}{Q_1...Q_{i-1}}c$.
+	\vspace{2mm}
+	The above technique specifies an algorithm for determining the coordinate of $\psi$.
+
+	As a base case, for the zero element have the algorithm return 1.
+
+	Suppose inductively that the algorithm returns the coordinate for any $\sigma\in M_{2n'+r'}^{r'}$, $2n'+r'<2n+r$, and that that coordinate is equal to the coordinate function $x_\sigma$.
+Also suppose that the algorithm commutes with any isomorphism defined by lemma \ref{sub-matching isomorphism}.
+These statements are clearly true for the base case.
+
+	Given $\psi\in M_{2n+r}^r$, if $\psi(1)=a$, we may find the coordinate of $E_{\lfloor a/2\rfloor}$ as before.
+Note that this operation commutes with any isomorphism defined by lemma \ref{sub-matching isomorphism}.
+Me may define $Y_{E_{\lfloor a/2\rfloor}}$ with respect to the sub-matching $E_{\lfloor a/2\rfloor}(2,a-1)$.
+By the inductive hypothesis, we may apply the algorithm to this sub-matching and commute with the isomorphism with $Y_{E_{\lfloor a/2\rfloor}}$.
+In this way, we find that the coordinate of $\tilde{\psi}$ defined by $\tilde{\psi}(1,a):=\psi(1,a)$ and $\tilde{\psi}(a+1,2n+r)=R$ is $x_{\psi(2,a-1)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_{\tilde{\psi}}(q)$.
+Similarly, define $Y_{\tilde{\psi}}$ with respect to the sub-matching $\tilde{\psi}(a+1,2n+r)$, and commute the algorithm with the isomorphism.
+In the same way, we obtain that the coordinate of $\psi\in Y_{\tilde{\psi}}$ is $x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_\psi(q)$ as desired.
+
+	Note that we only added a single operation to the algorithm in the inductive step, which also commutes with any isomorphism defined by lemma \ref{sub-matching isomorphism}.
+Thus the inductive step holds and the proposition is proved.
 
 	\begin{figure}
-		\def\cbasisspacing{5mm}
+		\def\cbasisspacing{1mm}
+		\begin{adjustbox}{width=\textwidth}
+			\GeneralizedMatching{14}{3/12,4/11,5/10,6/9,7/8,13/14}{2}{1/1,2/2}{12/4}, \hspace{\cbasisspacing}
+			\GeneralizedMatching{14}{1/2,3/4,5/6,9/12,10/11,13/14}{2}{7/1,8/2}{12/4}, \hspace{\cbasisspacing}
+			\GeneralizedMatching{14}{1/6,2/5,3/4,9/12,10/11,13/14}{2}{7/1,8/2}{12/4}
+		\end{adjustbox}
 
-		$\cbr{
-			\begin{gathered}
-			\GeneralizedMatching{14}{1/2,3/4,5/6,9/12,10/11,13/14}{2}{7/1,8/2}{5/4}, \hspace{\cbasisspacing}
-			\GeneralizedMatching{14}{1/6,2/5,3/4,9/12,10/11,13/14}{2}{7/1,8/2}{5/4}, \hspace{\cbasisspacing}
-			\end{gathered}}$ 
-		\caption{The figure on the left has submatching $R_3$ ignoring the last two nodes.
+		\caption{The figure on the left has sub-matching $R$ ignoring the last two nodes.
+The middle figure has submatching $R_3$ ignoring the last two nodes.
 The figure on the right has sub-matching $E_3$ also ignoring the last two nodes.
-Since the last two nodes have the same structure for both elements, if the coordinate of the second element is $c$, the coordinate of the first is $Q_2Q_1c$.}
+Since the last two nodes have the same structure for all elements, if the coordinate of the first element is $c$, the coordinate of the second is $Q_6Q_5Q_4c$, and the coordinate of the third is $\frac{Q_6Q_5Q_4}{Q_1Q_2}c$.}
+
+		\label{kernel induct characterization example}
 	\end{figure}
-
-	An example is given in figure 6.
-	\\
-
-	To turn this into an inductive proof, suppose statements (i) and (ii) are true for all representations with $2n'+r'<2n+r$ nodes.
-
-	Consider the set of basis elements $B=\{\alpha|\alpha(a+1,2n+r)=R\}$.
-We have shown that the element $\alpha_R\in B$ defined by $\alpha_R(1,a)=R$ has nonzero coefficient $\frac{Q_{n+r-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$.
-So, by our inductive hypothesis, the element $\tilde{\alpha_1}\in B$ defined by $\tilde{\alpha_1}(1,a)=\beta(1,a)=\alpha_1$ has coefficient $x_{\alpha_1}\frac{Q_{n+r-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$.
-
-	Similarly, consider the set of basis elements $B'=\{\upsilon|\upsilon(1,a)=\alpha_1\}$.
-We have shown that the element $\upsilon_R=\tilde{\alpha_1}$ has nonzero coefficient $x_{\alpha_1}\frac{Q_{n+r-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$.
-So, by our inductive hypothesis, $\beta$ has coefficient $x_{\alpha_2}x_{\alpha_1}\frac{Q_{n+r-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$ and the inductive step is proven.
-
-	Note that if the first node is an anchor, we need only consider the sub-matching of the rainbow element $R(2,2n+r)$ and use the inductive hypothesis. Thus the inductive step is proven in all cases.
-
-	For base cases, we consider those representations with 2 or less nodes.
-If there is only one node, it must be an anchor.
-In this case, the single anchor element is the only element and it is the rainbow element, so it has coefficient 1.
-For two nodes, if there are two anchors we may use the inductive step.
-Otherwise, there is one match, which is again the only element and is the rainbow element.
-Since the number 1 is a rational function of $q$, the base cases are proved.
-
-	So, by induction, the proposition holds.
 
@@
 \vspace{5mm}
-The following few corollaries will help to simplify some later proofs.
+The following few corollaries will help to simplify some later arguments.
 
 \begin{corollary}
-	Let $w\in\cap\text{ker}(1+T_i)$, $w\not=0$. Suppose $\beta(1,a)$ is a sub-matching with no anchors. Then:
+	Let $w\in\cap\text{ker}(1+T_i)$, $w\not=0$. Suppose $\psi(1,a)$ is a sub-matching with no anchors. Then:
 
-	$$x_\beta=x_{\beta(1,a)}(q)x_{\beta(a+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a/2}}{Q_1...Q_{a/2-1}}$$
+	$$x_\psi=x_{\psi(1,a)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{a/2}_{n+r}$$
+
+	\label{characterization generalization}
 \end{corollary}
@@
 \begin{proof}
-	Define $a_1=\beta(1)$, $a_i=\beta(a_{i-1}+1)$.
+	Define $a_1=\psi(1)$, $a_i=\psi(a_{i-1}+1)$.
 Then for some $j$ we have $a_j=a$.
@@
 Suppose that the statement is true for any matching with $a_v=a$, $v<j$.
-Then the statement holds for the sub-matching $\beta(a_1+1,2n+r)$, and we have:
-
-	$$x_\beta(q)=x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}}=$$
-
-	$$x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,a)}(q)x_{\beta(a+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}}\frac{Q_{n+r-a_1/2-1}...Q_{n+r-a/2}}{Q_1...Q_{a/2-a_1/2-1}}=$$
-
-	$$x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,a)}(q)x_{\beta(a+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}}\frac{Q_{n+r-a_1/2-1}...Q_{n+r-a/2}}{Q_1...Q_{a/2-a_1/2-1}}(\frac{Q_{a/2-1}...Q_{a/2-a_1/2}}{Q_{a/2-1}...Q_{a/2-a_1/2}})=$$
-
-	$$x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,a)}(q)x_{\beta(a+1,2n+r)}(q)\frac{Q_{a/2-1}...Q_{a/2-a_1/2}}{Q_1...Q_{a_1/2-1}}\frac{Q_{n+r-1}...Q_{n+r-a/2}}{Q_1...Q_{a/2-1}}=$$
-
-	$$=x_{\beta(1,a)}(q)x_{\beta(a+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a/2}}{Q_1...Q_{a/2-1}}$$
-
-	This proves the inductive step, so with base case $j=1$ the corollary holds.
+Then the statement holds for the sub-matching $\psi(a_1+1,2n+r)$, and we have:
+	\begin{align*}
+	x_\psi(q)=&x_{\psi(1,a_1)}(q)x_{\psi(a_1+1,2n+r)}(q)\Q^{a_1/2}_{n+r}\\
+	=&x_{\psi(1,a_1)}(q)x_{\psi(a_1+1,a)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{a_1/2}_{n+r}\Q_{n+r-a_1/2}^{a/2-a_1/2}\\
+	=&x_{\psi(1,a_1)}(q)x_{\psi(a_1+1,a)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{a_1/2}_{n+r}\Q_{n+r-a_1/2}^{a/2-a_1/2}\prn{\frac{Q_{a/2-1}...Q_{a/2-a_1/2}}{Q_{a/2-1}...Q_{a/2-a_1/2}}}\\
+	=&x_{\psi(1,a_1)}(q)x_{\psi(a_1+1,a)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{a_1/2}_{a/2}\Q^{a/2}_{n+r}\\
+	=&x_{\psi(1,a)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{a/2}_{n+r}
+	\end{align*}
 
@@
 \begin{corollary}
-	$\beta\in W_{2n+r}^r$, then $x_\beta(q)\not=0$ if $e>n+r$.
+	If $\psi\in M_{2n+r}^r$, then $x_\psi(q)\not=0$ if $e>n+r$.
+
+	\label{coeff nonzero}
 \end{corollary}
@@
 
-	Assume the statement is true for all $2n'+r'<2n+r$. We have $$x_\beta(q)=x_{\alpha_1}(q)x_{\alpha_2}(q)\frac{Q_{n+r-1}...Q_{n+r-(a/2)}}{Q_1...Q_{a/2-1}}$$
-	or $$x_\beta(q)=x_{\beta(2,2n+r)}(q)$$
+	Assume the statement is true for all $2n'+r'<2n+r$. Given $\psi(1)=a$ we have $$x_\psi(q)=x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}$$
 
-	If $e>n+r$, non of the $Q_i$ terms are zero, and $n'+r'<n+r<e$ for any of the sub-matchings that appear, so those coordinates are nonzero and the corollary holds.
+	If $e>n+r$, non of the $Q_i$ term appearing in $\Q^{\lfloor a/2\rfloor}_{n+r}$ are zero, and $n'+r'<n+r<e$ for any of the sub-matchings that appear, so those coordinates are nonzero and the corollary holds.
 
@@
 \vspace{5mm}
-The previous proposition fully characterizes any possible kernel element when $Q_1...Q_{n+r-1}\not=0$. In particular, the following corollary holds:
+The proposition fully characterizes any possible kernel element when $Q_1...Q_{n+r-1}\not=0$. In particular, the following corollary holds:
 
 \begin{corollary}
-	When $Q_1..Q_{n+r-1}\not=0$ and the kernel is nontrivial, the kernel is one dimensional.
+	Mhen $Q_1..Q_{n+r-1}\not=0$ and the kernel is nontrivial, the kernel is one dimensional.
+
+	\ref{1-D}
 \end{corollary}
@@
 \vspace{5mm}
-The remainder of this section will be used to prove that when $e=n+r+1$, the element specified by proposition 3.2 is indeed an element of the kernel.
+The remainder of this section will be used to prove that when $e=n+r+1$, the element specified by proposition \ref{kernel characterization} is indeed an element of the kernel.
 
-In service of this goal, a few lemmas will be helpful. The first lemma states that sub-matchings behave identically to the corresponding representations.
-
-\vspace{5mm}
-\begin{lemma}
-	Take a basis element $\beta\in W_{2n+r}^r$. Suppose $\beta$ has some sub-matching $\beta(a,b)$ with $r'$ anchors.
-
-	We may consider the restriction $\text{Res}_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}W_{2n+r}^r$ of this representation to the algebra generated by transpositions $T_a,...,T_{b-1}$.
-
-	Define $Y_\beta\subset \text{Res}_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}W_{2n+r}^r$ to be the subrepresentation generated by the set of basis elements $\{\alpha| \alpha(1,a-1)=\beta(1,a-1),\ \alpha(b+1,2n+r)=\beta(b+1,2n+r)\}$.
-Then the map $\rho:Y_\beta\rightarrow W_{b-a+1}^{r'}$ defined by $$\rho(\alpha)=\alpha(a,b)$$ is an isomorphism of representations.
-\end{lemma}
-
-\vspace{5mm}
-\begin{proof}
-
-	The map is clearly bijective. Thus it is sufficient to prove the following: $$\rho(T_{i+a-1}\alpha)=T_i\rho(\alpha)$$.
-
-	As mentioned in the previous section, the action of a transposition $T_i$ can change at most 4 nodes, so we need to show that the transpositions end up changing the same nodes in the same way in  $\rho(T_{i+a-1}\alpha)$ and $T_i\rho(\alpha)$.
-
-	Suppose $\alpha(i+a-1)=s,\alpha(i+a)=t$.
-Then $(T_{i+a-1}\alpha)(i+a-1)=i+a$, $(T_{i+a-1}\alpha)(s)=t$, so $\rho(T_{i+a-1}\alpha)(i)=i+1$, $\rho(T_{i+a-1}\alpha)(s-a+1)=t-a+1$.
-Separately, $\rho(\alpha)(i)=s-a+1$ and $\rho(\alpha)(i+1)=t-a+1$, so $T_i\rho(\alpha)(i)=i+1$ and $T_i\rho(\alpha)(s-a+1)=t-a+1$ as desired.
-So the map is an isomorphism and the lemma is proved.
-\end{proof}
-
-\vspace{5mm}
 To verify the kernel element, we will need to know exactly which basis elements are mapped to a specific basis element by a given $(1+T_i)$. The next two lemmas help address this question.
@@
 \begin{lemma}
-	Take some basis element $\beta\in W_{2n+r}^r$.
-Suppose $\beta(a)=b$ for some $b>a+1$, and that $(1+T_i)\beta=(1+q)\beta$ for some $a<i<b-1$.
-We then have a subrepresentation $\beta(a,b)$ and can define $Y_\beta$ as in the previous lemma.
-Then for all basis elements $\alpha$ such that $(1+T_i)\alpha=q^{1/2}\beta$, we have that $$\alpha\in Y_\beta$$.
+	Take some basis element $\psi\in M_{2n+r}^r$.
 
-	Similarly, if $\beta$ has some anchor at position $u$, and $(1+T_i)\beta=(1+q)\beta$ for some $i>u$, we again have a subrepresentation $\beta(u,2n+r)$ and may define $Y_\beta$ as before.
-Then for all basis elements $\alpha$ such that $(1+T_i)\alpha=q^{1/2}\beta$, we have that $\alpha\in Y_\beta$ again.
+	\begin{enumerate}[label={(\roman*)}]
+
+	\item Suppose $\psi(a)=b$ for some $b>a+1$, and that $(1+T_i)\psi=(1+q)\psi$ for some $a<i<b-1$.
+Me then have a subrepresentation $\psi(a,b)$ and define $Y_\psi$ with respect to this subrepresentation.
+Then for all basis elements $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$, we have that $$\sigma\in Y_\psi$$.
+
+	\item Suppose $\psi$ has some anchor at position $u$, and $(1+T_i)\psi=(1+q)\psi$ for some $i>u$, we again have a subrepresentation $\psi(u,2n+r)$ and define $Y_\psi$ with respect to this subrepresentation.
+Then for all basis elements $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$, we have that $\sigma\in Y_\psi$ again.
+
+	\end{enumerate}
+	\label{preimage under hump}
 \end{lemma}
@@
 \begin{proof}
-	This lemma follows from an observation I made in section 2: a transposition can only create two arcs or an arc and an anchor.
+	This lemma follows from an observation I made in section \ref{two humps created}: a transposition can only create two arcs or an arc and an anchor.
 
-	For the first case of this lemma, if $\alpha\not\in Y_\beta$ either $\alpha(1,a-1)\not=\beta(1,a-1)$ or $\alpha(b+1,2n+r)\not=\beta(b+1,2n+r)$.
+	(i) If $\sigma\not\in Y_\psi$ either $\sigma(1,a-1)\not=\psi(1,a-1)$ or $\sigma(b+1,2n+r)\not=\psi(b+1,2n+r)$.
 Suppose it is the first case.
-Then for some $s,t\in [1,a-1]$, $s<t$, we have $\beta(s)=t$ and $\alpha(s)\not=t$.
-To have $(1+T_i)\alpha=q^{1/2}\beta$ we must have $\alpha(t)=i+1$, $\alpha(s)=i$.
-But then $\alpha(a)\not=b$ and $\alpha(a)\not=i$ or $i+1$, so $((1+T_i)\alpha)(a)\not=b$ and $(1+T_i)\alpha\not=q^{1/2}\beta$.
-The same argument proves the $\alpha(b+1,2n+r)\not=\beta(b+1,2n+r)$ case.
+Then for some $s,t\in [1,a-1]$, $s<t$, we have $\psi(s)=t$ and $\sigma(s)\not=t$.
+To have $(1+T_i)\sigma=q^{1/2}\psi$ we must have $\sigma(t)=i+1$, $\sigma(s)=i$.
+But then $\sigma(a)\not=b$ and $\sigma(a)\not=i$ or $i+1$, so $((1+T_i)\sigma)(a)\not=b$ and $(1+T_i)\sigma\not=q^{1/2}\psi$.
+The same argument proves the $\sigma(b+1,2n+r)\not=\psi(b+1,2n+r)$ case.
 
-	An analogous argument proves the anchor case. Specifically, the anchor cannot exist at position $u$ and is not created by action of $(1+T_i)$ if $\alpha(s)=i$ and $\alpha(t)=i+1$.
+	(ii) An analogous argument proves the anchor case. Specifically, the anchor cannot exist at position $u$ and is not created by action of $(1+T_i)$ if $\sigma(s)=i$ and $\sigma(t)=i+1$.
 
@@
 \vspace{5mm}
-It is important to note that lemma 3.6 only references cases where a transposition acts under an arc or to the right of an anchor. An example is given in figure 7.
+It is important to note that lemma \ref{preimage under hump} only references cases where a transposition acts under an arc or to the right of an anchor.
+An example is given in figure \ref{preimage under hump example}.
 
@@
 	}
-	\label{Action}
+	\label{preimage under hump example}
 \end{figure}
@@
 Essentially, this lemma states that the only elements sent to the same element are those which break at most one of the top level arcs to the left of the leftmost anchor, or that break the leftmost anchor.
-An illustration is given in figure 8.
+An illustration is given in figure \ref{preimage under nothing example}.
 
@@
 \begin{lemma}
-	Take a basis element $\beta\in W_{2n+r}^r$.
-Suppose the leftmost anchor in $\beta$ is at index $b$, or let $b=2n+r+1$ if there is no anchor.
-Define $a_j$ such that $\beta(a_j)=a_{j-1}+1$ and $\beta(a_1)=1$ for all $j$ such that $a_j<b$.
+	Take a basis element $\psi\in M_{2n+r}^r$.
+Suppose the leftmost anchor in $\psi$ is at index $b$, or let $b=2n+r+1$ if there is no anchor.
+Define $a_j$ such that $\psi(a_j)=a_{j-1}+1$ and $\psi(a_1)=1$ for all $j$ such that $a_j<b$.
 
-	Suppose $(1+T_i)\beta=(1+q)\beta$ for some $i<b-1$ where $\not\exists s,t$ such that $\beta(s)=t$ and $s<i,t>i+1$.
-Suppose there is some basis element $\alpha$ such that $(1+T_i)\alpha=q^{1/2}\beta$.
-Then I claim the following:
+	Suppose $(1+T_i)\psi=(1+q)\psi$ for some $i<b-1$ where $\nexists s,t$ such that $\psi(s)=t$ and $s<i,t>i+1$. Suppose there is some basis element $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$. Then:
+	\\
 
-	\vspace{5mm}
-	\begin{center}
-		(i) $\beta(a_{j-1}+2,a_j-1)=\alpha(a_{j-1}+2,a_j-1)$ for all $j$.
+	\begin{enumerate}[label={(\roman*)}]
+		\item  $\psi(a_{j-1}+2,a_j-1)=\sigma(a_{j-1}+2,a_j-1)$ for all $j$.
 
-		\vspace{5mm}
-		(ii) $\beta(b+1,2n+r)=\alpha(b+1,2n+r)$
+		\item $\psi(b+1,2n+r)=\sigma(b+1,2n+r)$
 
-		\vspace{5mm}
-		(iii)
-		If $b$ is not an anchor in $\alpha$, $\beta(a_j)=\alpha(a_j)$ for all $j$ such that $a_j\not=i+1$.
+		\item If $b$ is not an anchor in $\sigma$, $\psi(a_j)=\sigma(a_j)$ for all $j$ such that $a_j\not=i+1$.
 
-		\vspace{5mm}
-		(iiii) If $b$ is an anchor in $\alpha$, there exists exactly one value of $j$ such that $\alpha(a_j)\not=\beta(a_j)$ and $a_j\not=i+1$
-	\end{center}
+		\item If $b$ is an anchor in $\sigma$, there exists exactly one value of $j$ such that $\sigma(a_j)\not=\psi(a_j)$ and $a_j\not=i+1$
+	\end{enumerate}
+	\label{preimage under nothing}
 \end{lemma}
@@
 
-	(i)
-
-	Suppose that, for some $j$ there exists $s,t\in [a_{j-1}+2,a_j-1]$ such that $\beta(s)=t$ but $\alpha(s)\not=t$.
-Then if $(1+T_i)\alpha=q^{1/2}\beta$ we must have $\alpha(i)=s$ or $t$ and $\alpha(i+1)=s$ or $t$.
-But, by definition, $i,i+1\not\in[a_{j-1}+1,a_j]$, so this implies $\alpha(a_j)\not=a_{j-1}+1,i,i+1$, so $((1+T_i)\alpha)(a_j)\not=a_{j-1}+1$ and $(1+T_i)\alpha\not=q^{1/2}\beta$.
+	(i) Suppose that, for some $j$ there exists $s,t\in [a_{j-1}+2,a_j-1]$ such that $\psi(s)=t$ but $\sigma(s)\not=t$.
+Then if $(1+T_i)\sigma=q^{1/2}\psi$ we must have $\sigma(i)=s$ or $t$ and $\sigma(i+1)=s$ or $t$.
+But, by definition, $i,i+1\not\in[a_{j-1}+1,a_j]$, so this implies $\sigma(a_j)\not=a_{j-1}+1,i,i+1$, so $((1+T_i)\sigma)(a_j)\not=a_{j-1}+1$ and $(1+T_i)\sigma\not=q^{1/2}\psi$.
 So (i) is proved.
@@
 	\vspace{5mm}
-	(ii)
-
-	The proof of (ii) is analogous to the proof of (i). We cannot have $\beta(b+1,2n+r)\not=\alpha(b+1,2n+r)$ and $\beta(b+1,2n+r)=((1+T_i)\alpha)(b+1,2n+r)$ if $((1+T_i)\alpha)(b)=b$.
+	(ii) The proof of (ii) is analogous to the proof of (i). Me cannot have $\psi(b+1,2n+r)\not=\sigma(b+1,2n+r)$ and $\psi(b+1,2n+r)=((1+T_i)\sigma)(b+1,2n+r)$ if $((1+T_i)\sigma)(b)=b$.
 
 	\vspace{5mm}
-	(iii)
-
-	If $b$ is not an anchor in $\alpha$ and $(1+T_i)\alpha=q^{1/2}\beta$, we must have $i$ an anchor in $\alpha$, and $\alpha(i+1)=b$. No other nodes in $\alpha$ are changed, so this proves (iii).
+	(iii) If $b$ is not an anchor in $\sigma$ and $(1+T_i)\sigma=q^{1/2}\psi$, we must have $i$ an anchor in $\sigma$, and $\sigma(i+1)=b$. No other nodes in $\sigma$ are changed, so this proves (iii).
 
 	\vspace{5mm}
-	(iiii)
-	From (i)-(iii) we have that the only remaining matchings that can differ are the $(a_{j-1}+1,a_j)$ matchings.
+	(iiii) From (i)-(iii) we have that the only remaining matchings that can differ are the $(a_{j-1}+1,a_j)$ matchings.
 If one of them differs, by the same argument as before it must be fixed by the action of $(1+T_i)$, and no other nodes are changed, so (iiii) is proved.
@@
 Note that in all of them nodes 2-5 and 12-15 are the same.
-This illustrates (i) and (ii) in lemma 3.5.
+This illustrates (i) and (ii) in lemma \ref{preimage under nothing}.
 Note that in the last case where the anchor is in a different place, 1,6 and 9,10 are still matched.
@@
 	}
-	\label{Action}
+	\label{preimage under nothing example}
 \end{figure}
@@
 	Suppose $n>b\geq a>0$ and $e>n$. Then $$Q_{n-a}Q_b-Q_{n-b-1}Q_{a-1}=Q_{n}Q_{b-a}$$
+
+	\label{Q lemma}
 \end{lemma}
@@
 \begin{proof}
-	If $b=1$, the only possibility for $a$ is 1, in which reduces to lemma 2.4.
+	If $b=1$, the only possibility for $a$ is 1, in which reduces to lemma \ref{Q alg}.
 
 	Suppose the lemma is true for all $\tilde{b}<b+1$. Then for $a< b$ we have 
+	\begin{align*}	
+	Q_{n-a}Q_b -Q_{n-b-1}Q_{a-1}=&Q_{n}Q_{b-a}\\
+	Q_1Q_{n-a}Q_b-Q_1Q_{n-b-1}Q_{a-1}=&Q_1Q_{n}Q_{b-a}
+	\end{align*}
 
-	$$Q_{n-a}Q_b -Q_{n-b-1}Q_{a-1}=Q_{n}Q_{b-a}$$
-
-	$$Q_1Q_{n-a}Q_b-Q_1Q_{n-b-1}Q_{a-1}=Q_1Q_{n}Q_{b-a}$$
-
-	from lemma 2.4, we have
-
+	from lemma \ref{Q alg}, we have	
 	$$Q_{n-a}(Q_{b+1}+Q_{b-1})-(Q_{n-b}+Q_{n-b-2})Q_{a-1}=Q_{n}(Q_{b-a-1}+Q_{b-a+1})$$
@@
 	For $a=b$ we have 
+	\begin{align*}
+	Q_{n-b}Q_b -Q_{n-b-1}Q_{b-1}=&Q_{n}\\
+	Q_1Q_{n-b}Q_b-Q_1Q_{n-b-1}Q_{b-1}=&Q_1Q_{n}
+	\end{align*}
 
-	$$Q_{n-b}Q_b -Q_{n-b-1}Q_{b-1}=Q_{n}$$
-
-	$$Q_1Q_{n-b}Q_b-Q_1Q_{n-b-1}Q_{b-1}=Q_1Q_{n}$$
-
-	from lemma 2.4, we have
-
-	$$Q_{n-b}(Q_{b+1}+Q_{b-1})-(Q_{n-b}+Q_{n-b-2})Q_{b-1}=Q_1Q_{n}$$
-
-	$$Q_{n-b}Q_{b+1}-Q_{n-b-2}Q_{b-1}=Q_1Q_{n}$$
+	from lemma \ref{Q alg}, we have
+	\begin{align*}
+	Q_{n-b}(Q_{b+1}+Q_{b-1})-(Q_{n-b}+Q_{n-b-2})Q_{b-1}=&Q_1Q_{n}\\
+	Q_{n-b}Q_{b+1}-Q_{n-b-2}Q_{b-1}=&Q_1Q_{n}\\
+	\end{align*}
 
@@
 	For $a=b+1$, we continue:
-
-	$$Q_1Q_{n-b}Q_{b+1}-Q_1Q_{n-b-2}Q_{b-1}=Q_1Q_1Q_{n}$$
-
-	$$(Q_{n-b-1}+Q_{n-b+1})Q_{b+1}-Q_{n-b-2}(Q_{b}+Q_{b-2})=(1+Q_2)Q_{n}$$
+	\begin{align*}
+	Q_1Q_{n-b}Q_{b+1}-Q_1Q_{n-b-2}Q_{b-1}=&Q_1Q_1Q_{n}\\
+	(Q_{n-b-1}+Q_{n-b+1})Q_{b+1}-Q_{n-b-2}(Q_{b}+Q_{b-2})=&(1+Q_2)Q_{n}\\
+	\end{align*}
 
 	So by the inductive hypothesis
-
 	$$Q_{n-b-1}Q_{b+1}-Q_{n-b-2}Q_{b}=Q_{n}$$
@@
 \vspace{5mm}
-We are now ready to prove existence of a kernel element.
-To prove this, we will show that if $w\in W_{2n+r}^r$ is as characterized above, the coordinate of any basis element in $(1+T_i)w$ is zero.
+Me are now ready to prove existence of a kernel element.
+To prove this, we will show that if $w\in M_{2n+r}^r$ is as characterized above, the coordinate of any basis element in $(1+T_i)w$ is zero.
 This will split into various cases related to the previous lemmas.
@@
 \vspace{5mm}
-\begin{proposition}
-	Suppose $e=n+r+1$. Then $\cap\text{ker}(1+T_i)\not=\emptyset$.
-\end{proposition}
+\begin{theorem}
+	Suppose $e=n+r+1$. Then $\cap\text{ker}(1+T_i)\not=0$.
+	\label{kernel existence}
+\end{theorem}
 
 \begin{proof}
-
-	Assume inductively that the statement holds for all $W_{2n'+r'}^{r'}$ where $2n'+r'<2n+r$.
 
@@
 	\vspace{5mm}
-	Now we will prove the inductive step.
-Take $w$ as recursively defined by proposition 3.1.
-Formally, suppose $x_\alpha$ is the rational function corresponding to the coordinate of $\alpha$ in its respective kernel element for $\alpha\in W_{2n'+r'}^{r'}$, $2n'+r'<2n+r$.
-Then we define $w$ by its coordinate vector: $\beta\in W_{2n+r}^r$, if $\beta(1)=a\not=1$ then the coordinate of $\beta$ is $x_{\beta(2,a-1)}(q)x_{a+1,2n+r}(q)\frac{Q_{n-1}...Q_{a/2}}{Q_1...Q_{a/2-1}}$; if $\beta(1)=1$ then the coordinate of $\beta$ is $x_{\beta(2,2n+r)}(q)$.
-	\\
 
-	Let $E_\beta\subset W_{2n+r}^r$ be the pre-image of $\beta\in (1+T_i)W_{2n+r}^r$ under the action of $(1+T_i)$. To prove $w$ is in the kernel, we must show the following: 
-	\begin{center}
-	(i) $(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=0\text{ for all basis elements }\beta$
-	\end{center}
-	Inductively, we assume this equation holds for basis elements in smaller representations $W_{2n'+r'}^{r'}$, but only for $q$ such that $e=n'+r'+1$.
+	Assume inductively that the statement holds for all $M_{2n'+r'}^{r'}$ where $2n'+r'<2n+r$. Take $w$ as defined by proposition \ref{kernel characterization}.
+
+	Given $\psi\in (1+T_i)M_{2n+r}^r$ let $E_\psi\subset M_{2n+r}^r$ be the pre-image of $\psi$ under the action of $(1+T_i)$. To prove $w$ is in the kernel, we must show the following: 
+	\begin{equation}
+	(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=0\text{ for all basis elements }\psi
+	\label{weak kernel}
+	\end{equation}
+	Inductively, we assume this equation holds for basis elements in smaller representations $M_{2n'+r'}^{r'}$, but only for $q$ such that $e=n'+r'+1$.
+Clearly this is true in the base case.
 For the following proof we will need a slightly stronger inductive assumption.
-Take $\beta'\in W_{2n'+r'}^{r'}$, and suppose either that $\beta'(1)=2n'+r'$, and that $T_i\beta'=(1+q)\beta'$, $1<i<2n'+r'-1$, or that 1 is an anchor in $\beta$.
-Defining $E_{\beta'}$ as before, we assume
+Take $\psi'\in M_{2n'+r'}^{r'}$, and suppose either that $\psi'(1)=2n'+r'$, and that $T_i\psi'=(1+q)\psi'$, $1<i<2n'+r'-1$, or that 1 is an anchor in $\psi$.
+Defining $E_{\psi'}$ as before, we assume
 
-	\begin{center}
-		(ii) $(1+q)x_{\beta'}+\sum_{\alpha\in E_{\beta'},\alpha\not=\beta'}q^{1/2}x_\alpha=0\text{ for any } q \text{ with }e>n'+r'$
-	\end{center}
+	\begin{equation}
+		(1+q)x_{\psi'}+\sum_{\sigma\in E_{\psi'},\sigma\not=\psi'}q^{1/2}x_\sigma=0\text{ for any } q \text{ with }e>n'+r'
+		\label{strong kernel}
+	\end{equation}
 
-	\vspace{5mm}
-	To prove the inductive step for both (i) and (ii), we must split into cases.
-Note that if $E_\beta$ is defined to be the pre-image of $\beta$ under the action of $(1+T_i)$, $E_{\beta(a,b)}$ is defined to be the pre-image of $\beta(a,b)$ under action of $(1+T_{i-a+1})$:
+	Note that \ref{strong kernel} does not apply in the base case.
+Our proof of the inductive step will be split into cases, and each case will only depend on sub-cases in which certain inductive hypotheses apply, so this will not lead to any problems.
 
-	\begin{enumerate}
-	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, and that $\exists s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\beta(s)=t$.
+	Before exploring the cases, let us formally define $E_\psi$ to be the pre-image of $\psi$ under the action of $(1+T_i)$, and $E_{\psi(a,b)}$ to be the pre-image of $\psi(a,b)$ under action of $(1+T_{i-a+1})$:
+
+	\begin{enumerate}[label={case \arabic*:}]
+	\item Suppose $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, and that $\exists s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\psi(s)=t$.
 Also suppose the leftmost anchor is at some index $u>t$, or that there are no anchors.
-Then we have a sub-matching $\beta(s,t)$, and by lemma 3.6 $E_\beta\subset Y_\beta$.
-Then, using corollary 3.2, the following equality holds:
+Then we have a sub-matching $\psi(s,t)$, and by lemma \ref{preimage under hump} $E_\psi\subset Y_\psi$.
+Then, using corollary \ref{characterization generalization}, the following equality holds:
 
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=$$
+	\begin{align*}
+	&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)\\
+	=&\prn{x_{\psi(1,s-1)}(q)\Q_{n+r}^{(s-1)/2}}\prn{(1+q)x_{\psi(s,2n+r)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,2n+r)}(q)}\\
+	=&\prn{x_{\psi(1,s-1)}(q)\Q_{n+r}^{(s-1)/2}}\prn{x_{\psi(t+1,2n+r)}(q)\Q_{n+r-(s-1)/2}^{(t-s+1)/2}}\prn{(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,t)}(q)}
+	\end{align*}
 
-	$$(x_{\beta(1,s-1)}(q)\frac{Q_{n+r-1}...Q_{n+r-(s-1)/2}}{Q_1...Q_{(s-1)/2-1}})((1+q)x_{\beta(s,2n+r)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_{\alpha(s,2n+r)}(q))=$$
+	Me have that $e>j$ for any $Q_j$ term appearing in the equation above, and $e>n'+r'$ for any sub-matching coordinate appearing above, so by corollary \ref{coeff nonzero}:
 
-	$$(x_{\beta(t+1,2n+r)}(q)\frac{Q_{n+r-(s-1)/2-1}...Q_{n+r-t/2}}{Q_1...Q_{(t-s+1)/2-1}})(x_{\beta(1,s-1)}(q)\frac{Q_{n+r-1}...Q_{n+r-(s-1)/2}}{Q_1...Q_{(s-1)/2-1}})((1+q)x_{\beta(s,t)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_{\alpha(s,t)}(q))$$
-
-	We have that $e>j$ for any $Q_j$ term appearing in the equation above, and $e>n'+r'$ for any sub-matching coordinate appearing above, so by corollary 3.3:
-
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=0$$
+	$$(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=0$$
 
@@
 
-	$$(1+q)x_{\beta(s,t)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_{\alpha(s,t)}(q)=0$$
+	$$(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,t)}(q)=0$$
 
-	Note that $(\beta(s,t))(1)=t-s+1$. So by our inductive hypothesis (ii), we have
+	Note that $(\psi(s,t))(1)=t-s+1$. So by our inductive hypothesis (ii), we have
 
-	$$(1+q)x_{\beta(s,t)}(q)+\sum_{\alpha\in E_{\beta(s,t)},\alpha\not=\beta(s,t)}q^{1/2}x_{\alpha}(q)=0$$
+	$$(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_{\psi(s,t)},\sigma\not=\psi(s,t)}q^{1/2}x_{\sigma}(q)=0$$
 
-	By lemma 3.5, if $\alpha\in Y_\beta$, $(1+T_i)\alpha=q^{1/2}\beta$ if and only if $(1+T_{i-s+1})\alpha(s,t)=q^{1/2}\beta(s,t)$, so the previous equation implies $$(1+q)x_{\beta(s,t)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_{\alpha(s,t)}(q)=0$$
+	By lemma \ref{sub-matching isomorphism}, if $\sigma\in Y_\psi$, $(1+T_i)\sigma=q^{1/2}\psi$ if and only if $(1+T_{i-s+1})\sigma(s,t)=q^{1/2}\psi(s,t)$, so the previous equation implies $$(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,t)}(q)=0$$
 
@@
 	\vspace{5mm}
-	\item Again take $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, but suppose the leftmost anchor is at some position $u$ where $1<u<i$.
-Then, as before, we have a sub-matching $\beta(u,2n+r)$ and by lemma 3.6 $E_\beta\subset Y_\beta$.
+	\item Again take $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, but suppose the leftmost anchor is at some position $u$ where $1<u<i$.
+Then, as before, we have a sub-matching $\psi(u,2n+r)$ and by lemma \ref{preimage under hump} $E_\psi\subset Y_\psi$.
 
-	Note that in both corollary 3.2 and our inductive hypothesis (ii) we specified cases involving anchors. This allows the exact same logic from the proof of the first case to prove this case.
+	Note that both corollary \ref{characterization generalization} and our inductive hypothesis \ref{strong kernel} still apply in this case, where we consider a left anchor instead of a matching.
+This allows the exact same logic from the proof of the first case to prove this case.
+	\\
+
+	It is important to note that, for both case 1 and case 2, the inductive hypothesis depends only on cases in which \ref{strong kernel} holds.
+Thus, if we show these cases rely on valid base cases, case 1 and 2 follow.
+This will be done in case 4.
 
 	\vspace{5mm}
-	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, the leftmost anchor is at a position $u>i+1$ or there are no anchors, and $\not\exists s,t$ such that $\beta(s)=t$ and $s<i<t-1$.
-Lemma $3.7$ characterizes all $\alpha\in E_\beta$.
-We would like to prove the following for arbitrary $q$ where $e>n+r$:
+	\item Suppose $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, the leftmost anchor is at a position $u>i+1$ or there are no anchors, and $\nexists s,t$ such that $\psi(s)=t$ and $s<i<t-1$.
+Lemma \ref{preimage under nothing} characterizes all $\sigma\in E_\psi$.
+Me would like to prove the following for arbitrary $q$ where $e>n+r$:
 
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}$$
+	$$(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=-q^{1/2}x_{\psi(1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r+1}^{(i+1)/2}$$
 
-	See figure 9 for an example of this equality.
+	\begin{figure}[b]
+		\[
+		\begin{tabular}{l l l l}
+		\GeneralizedAction{7}{1/2,3/4,5/6}{1}{7/1}{3/4}{3}{1/2,3/4,5/6}{7/1}{(1+q)}\\
+
+		\GeneralizedAction{7}{1/4,2/3,5/6}{1}{7/1}{3/4}{3}{1/2,3/4,5/6}{7/1}{(q^{1/2})}\\
+
+		\GeneralizedAction{7}{1/2,3/6,4/5}{1}{7/1}{3/4}{3}{1/2,3/4,5/6}{7/1}{(q^{1/2})}\\
+
+		\GeneralizedAction{7}{1/2,4/7,5/6}{1}{3/1}{3/4}{3}{1/2,3/4,5/6}{7/1}{(q^{1/2})}\\
+
+		\end{tabular}
+		\]
+
+		\caption{The four elements sent to the first element by $(1+T_3)$ are listed.
+The coordinate of the first element is $Q_3Q_2Q_1$.
+The coordinate of the second is $Q_3Q_2$.
+The coordinate of the third is $Q_3Q_2$.
+The coordinate of the fourth is $Q_3$.
+Call the first element $\psi$.
+Then $x_{\psi(1,2)}=1$, $x_{\psi(5,7)}=Q_1$, so $-q^{1/2}x_{\psi(1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r+1}^{(i+1)/2}=-q^{1/2}Q_4Q_3$.
+Me also have $(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=(q+1)(Q_3Q_2Q_1)+q^{1/2}(Q_3Q_2+Q_3Q_2+Q_3)=-q^{1/2}(Q_3Q_2Q_1^2-2Q_3Q_2+Q_3)=-q^{1/2}Q_4Q_3$ as desired (one can verify the last equality by hand or simplify using lemma \ref{Q lemma}).}
+		\label{case 3}
+	\end{figure}
+
+	See figure \ref{case 3} for an example of this equality.
 Note that if $e=n+r+1$, $Q_{n+r}$ is the only zero component in the right side of this equation, so proving this equation is sufficient to prove case three.
@@
 
-	We will prove this equality through yet another inductive proof, this time inducting on the number of top level humps, including the leftmost anchor.
+	Me will prove this equality through yet another inductive proof, this time inducting on the number of top level humps, including the leftmost anchor.
 
-	Formally, as we have in earlier lemmas, we will define $a_j$ by $a_1:=\beta(1)$, $a_j:=\beta(a_{j-1}+1)$.
-Then define $b_\beta$ such that $a_{b_\beta}=u$ if there is an anchor or $a_{b_\beta}=2n+r$ otherwise.
-We induct on $b_\beta$.
+	Formally, as we have in earlier lemmas, we will define $a_j$ by $a_1:=\psi(1)$, $a_j:=\psi(a_{j-1}+1)$.
+Then define $b_\psi$ such that $a_{b_\psi}=u$ if there is an anchor or $a_{b_\psi}=2n+r$ otherwise.
+Me induct on $b_\psi$.
 	\\
 
-	If $b_\beta=1$, we must be in $W_2^0$ to be in case 3 (otherwise $s<i<t-1$ for some $s,t$ where $\beta(s)=t$), which is trivially satisfied. 
+	If $b_\psi=1$, we must be in $M_2^0$ to be in case 3 (otherwise $s<i<t-1$ for some $s,t$ where $\psi(s)=t$), which is trivially satisfied. Thus the base case holds.
 	\\
 
-%	For our base case we will prove $b=2$. This means either $a_1+1$ is an anchor, or $\beta(a_1+1)=2n+r$. 
-%	\\
-%	
-%	First base case:
-%	
-%	If $a_1+1$ is an anchor, to still be in case 3 we must have $i=1$ and $a_1=2$.
-In this case, lemma 3.7 gives that there is only one element in $E_\beta$, and that element is $\alpha$ defined by $\alpha(4,2n+r)=\beta(4,2n+r)$, $\alpha(1)=1$, and $\alpha(2)=3$.
-Then $x_\beta=Q_{n+r-1}x_\beta(3,2n+r)=Q_{n+r-1}\beta(4,2n+r)$ and $x_\alpha=x_{\alpha(2,2n+r)}=Q_{n+r-2}x_{\beta(4,2n+r)}$.
-So, using lemma 2.4, we have $(q+1)x_\beta(q)+q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(4,2n+4)}(q)Q_{n+r}$ as desired.
-%	\\
-%	
-%	Second base case: 
-%	
-%	If $\beta(a_1+1)=2n+r$, to be in case 3 we need either $a_1=2$ or $a_1=2n+r-2$.
-In both cases lemma 3.7 gives only one element $\alpha$ in $E_\beta$.
-In the first case $x_\beta=Q_{n+r-1}x_{\beta(3,2n+r)}=Q_{n+r-1}x_{\beta(4,2n+r-1)}$, and $x_\alpha=x_{\alpha(2,2n+r-1)}=Q_{n+r-2}x_{\beta(4,2n+r-1)}$ so again using lemma 2.4 $(q+1)x_\beta(q)+q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(4,2n+r)}(q)Q_{n+r}$ as desired.
-In the second case $x_\beta=\frac{Q_{n+r-1}...Q_{1}}{Q_1...Q_{n+r-2}}x_{\beta(2,2n+r-3)}=Q_{n+r-1}x_{\beta(2,2n+r-3)}$, and, using corollary 3.3, $x_\alpha=\frac{Q_{n+r-2}...Q_{1}}{Q_1...Q_{n+r-3}}x_{\alpha(2,2n+r-3)}=Q_{n+r-2}x_{\beta(2,2n+r-3)}$, so again using lemma 2.4, we have $(q+1)x_\beta(q)+q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(1,2n+r-2)}(q)Q_{n+r}$ as desired, and all base cases are proved.
-%	\\
-
-	Suppose for all basis elements $\alpha$ such that $b_\alpha<b_\beta$, the equality holds.
+	Suppose for all basis elements $\sigma$ such that $b_\sigma<b_\psi$, the equality holds.
 Suppose $i\not=1$.
-Then $a_1<i$ and lemma 3.7 gives that there is a unique $\upsilon\in E_\beta$ such that $\upsilon(1)\not=a_1$.
+Then $a_1<i$ and lemma \ref{preimage under nothing} gives that there is a unique $\upsilon\in E_\psi$ such that $\upsilon(1)\not=a_1$.
 Thus we have the following equality:
 
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$
+	\begin{align*}
+	&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_\sigma(q)\\
+	=&\prn{x_{\psi(1,a_1)}(q)\Q_{n+r}^{a_1/2}}\prn{(1+q)x_{\psi(a_1+1,2n+r)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_{\sigma(a_1+1,2n+r)}(q)}
+	\end{align*}
 
-	$$(x_{\beta(1,a_1)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}})((1+q)x_{\beta(a_1+1,2n+r)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_{\alpha(a_1+1,2n+r)}(q))$$
+	Define $Y_\psi$ with respect to the sub-matching $\psi(a_1+1,2n+r)$. Then $\sigma\in E_\psi$, $\sigma\not=\upsilon$ implies $\sigma\in Y_\psi$. By our inductive hypothesis, we have that 
+	\begin{align*}
+	&(1+q)x_{\psi(a_1+1,2n+r)}(q)+\sum_{\sigma\in E_{\psi(a_1+1,2n+r)},\sigma\not=\psi(a_1+1,2n+r)}q^{1/2}x_{\sigma}(q)\\
+	=&-q^{1/2}x_{\psi(a_1+1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}
+	\end{align*}
 
-	Define $Y_\beta$ as before with respect to the sub-matching $\beta(a_1+1,2n+r)$.
-Then $\alpha\in E_\beta$, $\alpha\not=\upsilon$ implies $\alpha\in Y_\beta$.
-By our inductive hypothesis, we have that
-	$$(1+q)x_{\beta(a_1+1,2n+r)}(q)+\sum_{\alpha\in E_{\beta(a_1+1,2n+r)},\alpha\not=\beta(a_1+1,2n+r)}q^{1/2}x_{\alpha}(q)=$$
-	$$
-	-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}}$$
+	By lemma \ref{sub-matching isomorphism}, $\sigma\subset Y_\psi$, $\sigma\in E_\psi$ if and only if $\sigma(a_1+1,2n+r)\in E_{\psi(a_1+1,2n+r)}$. This implies:
 
-	By lemma 3.5, $\alpha\subset Y_\beta$, $\alpha\in E_\beta$ if and only if $\alpha(a_1+1,2n+r)\in E_{\beta(a_1+1,2n+r)}$. This implies:
-
-	$$(1+q)x_{\beta(a_1+1,2n+r)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_{\alpha(a_1+1,2n+r)}(q)=$$
-
-	$$-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}}$$
+	\begin{align*}
+	&(1+q)x_{\psi(a_1+1,2n+r)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_{\sigma(a_1+1,2n+r)}(q)\\
+	=&-q^{1/2}x_{\psi(a_1+1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}
+	\end{align*}
 
 	So, combining with the aforementioned equality, we have 
+	\begin{align*}
+	&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_\sigma(q)\\
+	=&\prn{x_{\psi(1,a_1)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}}\prn{-q^{1/2}x_{\psi(a_1+1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}}\\
+	=&\prn{x_{\psi(1,a_1)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}}\prn{-q^{1/2}x_{\psi(a_1+1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}}\prn{\frac{Q_{(i-1)/2-1}...Q_{(i-1-a_1)/2}}{Q_{(i-1)/2-1}...Q_{(i-1-a_1)/2}}}\\
+	=&-q^{1/2}x_{\psi(1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r+1}^{(i+1)/2}\prn{\frac{Q_{n+r-a_1/2}Q_{(i-1)/2}}{Q_{n+r}Q_{(i-1-a_1)/2}}}
+	\end{align*}
 
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$
+	Separately, note that $\upsilon$ is defined by $\upsilon(2,a_1-1)=\psi(2,a_1-1)$, $\upsilon(a_1+1,i-1)=\psi(a_1+1,i-1)$, $\upsilon(i+2,2n+r)=\psi(i+2,2n+r)$, and $\upsilon(1)=i+1$, $\upsilon(a_1)=i$.
+Thus we may determine $x_\upsilon$, again utilizing corollary \ref{characterization generalization}:
 
-	$$(x_{\beta(1,a_1)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}})(-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}})=$$
-
-	$$(x_{\beta(1,a_1)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}})(-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}})(\frac{Q_{(i-1)/2-1}...Q_{(i-1-a_1)/2}}{Q_{(i-1)/2-1}...Q_{(i-1-a_1)/2}})=$$
-
-	$$-q^{1/2}x_{\beta(1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}(\frac{Q_{n+r-a_1/2}Q_{(i-1)/2}}{Q_{(i-1-a_1)/2}})$$
-	\\
-
-	Separately, note that $\upsilon$ is defined by $\upsilon(2,a_1-1)=\beta(2,a_1-1)$, $\upsilon(a_1+1,i-1)=\beta(a_1+1,i-1)$, $\upsilon(i+2,2n+r)=\beta(i+2,2n+r)$, and $\upsilon(1)=i+1$, $\upsilon(a_1)=i$.
-Thus we may determine $x_\upsilon$, again utilizing corollary 3.2:
-
-	$$x_\upsilon=x_{\beta(i+2,2n+r)}x_{\upsilon(2,i)}\frac{Q_{n+r-1}...Q_{n+r-(i+1)/2}}{Q_1...Q_{(i-1)/2}}=$$
-
-	$$x_{\beta(i+2,2n+r)}(x_{\beta(2,a_1-1)}x_{\upsilon(a_1,i)}\frac{Q_{(i-1)/2-1}...Q_{(i-1)/2-(a_1-2)/2}}{Q_1...Q_{(a_1-2)/2-1}})\frac{Q_{n+r-1}...Q_{n+r-(i+1)/2}}{Q_1...Q_{(i-1)/2}}=$$
-
-	$$x_{\beta(i+2,2n+r)}(x_{\beta(1,a_1)}x_{\beta(a_1+1,i-1)}\frac{Q_{(i-1)/2-1}...Q_{(i-1)/2-(a_1-2)/2}}{Q_1...Q_{(a_1-2)/2-1}})\frac{Q_{n+r-1}...Q_{n+r-(i+1)/2}}{Q_1...Q_{(i-1)/2}}=$$
-
-	$$x_{\beta(i+2,2n+r)}x_{\beta(1,i-1)}\frac{Q_{n+r-1}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}(\frac{Q_{n+r-(i+1)/2}Q_{a_1/2-1}}{Q_{(i-1-a_1)/2}})$$
-	\\
+	\begin{align*}
+	x_\upsilon=&x_{\psi(i+2,2n+r)}x_{\upsilon(2,i)}\Q_{n+r}^{(i+1)/2}\\
+	=&x_{\psi(i+2,2n+r)}\prn{x_{\psi(2,a_1-1)}x_{\upsilon(a_1,i)}\Q_{(i-1)/2}^{(a_1-2)/2}}\Q_{n+r}^{(i+1)/2}\\
+	=&x_{\psi(i+2,2n+r)}\prn{x_{\psi(1,a_1)}x_{\psi(a_1+1,i-1)}\Q_{(i-1)/2}^{(a_1-2)/2}}\Q_{n+r}^{(i+1)/2}\\
+	=&x_{\psi(i+2,2n+r)}x_{\psi(1,i-1)}\Q_{n+r+1}^{(i+1)/2}\prn{\frac{Q_{n+r-(i+1)/2}Q_{a_1/2-1}}{Q_{n+r}Q_{(i-1-a_1)/2}}}
+	\end{align*}
 
 	Adding this into our previous equation, we have:
+	\begin{align*}
+	&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)\\
+	=&-q^{1/2}x_{\psi(1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r+1}^{(i+1)/2}\prn{\frac{Q_{n+r-a_1/2}Q_{(i-1)/2}-Q_{n+r-(i+1)/2}Q_{a_1/2-1}}{Q_{n+r}Q_{(i-1-a_1)/2}}}
+	\end{align*}
 
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=$$
+	Applying lemma \ref{Q lemma} to the portion of the equation above in parenthesis, the above is equivalent to
 
-	$$-q^{1/2}x_{\beta(1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}(\frac{Q_{n+r-a_1/2}Q_{(i-1)/2}-Q_{n+r-(i+1)/2}Q_{a_1/2-1}}{Q_{(i-1-a_1)/2}})$$
+	$$(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=-q^{1/2}x_{\psi(1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r+1}^{(i+1)/2}$$
 
-	Applying lemma 3.8 to the portion of the equation above in parenthesis, the above is equivalent to
-
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}$$
-
-	as desired. Note that if $e\geq n+r+1$ the only term above that can be zero is $Q_{n+r}$ (by corollary 3.3). Thus we have proved the inductive step for the case where $i\not=1$.
+	as desired. Note that if $e\geq n+r+1$ the only term above that can be zero is $Q_{n+r}$ (by corollary \ref{coeff nonzero}). Thus we have proved the inductive step for the case where $i\not=1$.
 
 	\vspace{5mm}
-	If $i=1$, we instead look at the sub-matchings $\beta(1,a_{(b_\beta-1)})$, $\beta(a_{(b_\beta-1)}+1,2n+r)$.
-Again lemma 3.7 gives that there is a unique $\upsilon\in E_\beta$ such that $\upsilon(a_{(b_\beta-1)}+1)\not=\beta(a_{(b_\beta-1)}+1)$.
-Taking $Y_\beta$ with respect to the sub-matching $\beta(a_{(b_\beta-1)}+1,a_{b_\beta})$ again we have that $\alpha\in E_\beta$, $\alpha\not=\upsilon$ implies $\alpha\in Y_\beta$.
+	If $i=1$, we instead look at the sub-matchings $\psi(1,a_{(b_\psi-1)})$, $\psi(a_{(b_\psi-1)}+1,2n+r)$.
+Again lemma \ref{preimage under nothing} gives that there is a unique $\upsilon\in E_\psi$ such that $\upsilon(a_{(b_\psi-1)}+1)\not=\psi(a_{(b_\psi-1)}+1)$.
+Taking $Y_\psi$ with respect to the sub-matching $\psi(a_{(b_\psi-1)}+1,a_{b_\psi})$ again we have that $\sigma\in E_\psi$, $\sigma\not=\upsilon$ implies $\sigma\in Y_\psi$.
 Thus, following the same logic as before, we arrive at the following equality:
+	\begin{align*}
+	&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_\sigma(q)\\
+	=&\prn{x_{\psi(a_{(b_\psi-1)}+1,2n+r)}(q)\Q_{n+r}^{a_{(b_\psi-1)}/2}}\prn{-q^{1/2}x_{\psi(3,a_{(b_\psi-1)})}(q)Q_{a_{(b_\psi-1)}/2}}\\
+	=&-q^{1/2}x_{\psi(3,2n+r)}\frac{Q_{n+r-1}Q_{a_{(b_\psi-1)}/2}}{Q_{a_{(b_\psi-1)}/2-1}}
+	\end{align*}
 
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$
+	Again, we know the structure of $\upsilon$ from lemma \ref{preimage under nothing}.
+Suppose for now that $a_{b_\psi}$ is not an anchor, so it is $2n+r$.
+Then $\upsilon$ is defined by $\upsilon(3,a_{(b_\psi-1)})=\psi(3,a_{(b_\psi-1)})$, $\upsilon(a_{(b_\psi-1)}+2,2n+r-1)=\psi(a_{(b_\psi-1)}+2,2n+r-1)$, and $\upsilon(1)=2n+r$, $\upsilon(2)=a_{(b_\psi-1)}+1$.
+So we may again find $x_\upsilon$:
+	\begin{align*}
+	x_\upsilon=x_{\upsilon(2,2n+r-1)}=&x_{\psi(3,a_{(b_\psi-1)})}x_{\psi(a_{(b_\psi-1)}+2,2n+r-1)}\Q_{n+r-1}^{a_{(b_\psi-1)}/2}\\
+	=&x_{\psi(3,a_{(b_\psi-1)})}x_{\psi(a_{(b_\psi-1)}+1,2n+r)}\Q_{n+r-1}^{a_{(b_\psi-1)}/2}\\
+	=&x_{\psi(3,2n+r)}\frac{Q_{n-r-1-a_{(b_\psi-1)}/2}}{Q_{a_{(b_\psi-1)}/2-1}}
+	\end{align*}
 
-	$$(x_{\beta(a_{(b_\beta-1)}+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}})(-q^{1/2}x_{\beta(3,a_{(b_\beta-1)})}(q)Q_{a_{(b_\beta-1)}/2})=$$
+	Alternatively, if $a_{b_\psi}$ is an anchor, the definition of $\upsilon$ is now $\upsilon(3,a_{b_\psi}-1)=\psi(3,a_{b_\psi}-1)$, $\upsilon(a_{b_\psi}+1,2n+r)=\psi(a_{b_\psi}+1,2n+r)$, and $\upsilon(1)=1$, $\upsilon(2)=a_{b_\psi}$, so we have:
 
-	$$-q^{1/2}x_{\beta(3,2n+r)}\frac{Q_{n+r-1}Q_{a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$
-	\\
-
-	Again, we know the structure of $\upsilon$ from lemma 3.7.
-Suppose for now that $a_{b_\beta}$ is not an anchor, so it is $2n+r$.
-Then $\upsilon$ is defined by $\upsilon(3,a_{(b_\beta-1)})=\beta(3,a_{(b_\beta-1)})$, $\upsilon(a_{(b_\beta-1)}+2,2n+r-1)=\beta(a_{(b_\beta-1)}+2,2n+r-1)$, and $\upsilon(1)=2n+r$, $\upsilon(2)=a_{(b_\beta-1)}+1$.
-So we may again find $x_\upsilon$:
-
-	$$x_\upsilon=x_{\upsilon(2,2n+r-1)}=x_{\beta(3,a_{(b_\beta-1)})}x_{\beta(a_{(b_\beta-1)}+2,2n+r-1)}\frac{Q_{n+r-2}...Q_{n+r-1-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}}=$$
-
-	$$x_{\beta(3,a_{(b_\beta-1)})}x_{\beta(a_{(b_\beta-1)}+1,2n+r)}\frac{Q_{n+r-2}...Q_{n+r-1-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}}=x_{\beta(3,2n+r)}\frac{Q_{n-r-1-a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$
-
-	Alternatively, if $a_{b_\beta}$ is an anchor, the definition of $\upsilon$ is now $\upsilon(3,a_{b_\beta}-1)=\beta(3,a_{b_\beta}-1)$, $\upsilon(a_{b_\beta}+1,2n+r)=\beta(a_{b_\beta}+1,2n+r)$, and $\upsilon(1)=1$, $\upsilon(2)=a_{b_\beta}$, so we have:
-
-	$$x_\upsilon=x_{\upsilon(2,2n+r)}=x_{\beta(3,a_{(b_\beta-1)})}x_{\beta(a_{b_\beta}+1,2n+r)}\frac{Q_{n+r-2}...Q_{n+r-1-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}}=x_{\beta(3,2n+r)}\frac{Q_{n-r-1-a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$
+	$$x_\upsilon=x_{\upsilon(2,2n+r)}=x_{\psi(3,a_{(b_\psi-1)})}x_{\psi(a_{b_\psi}+1,2n+r)}\Q_{n+r-1}^{a_{(b_\psi-1)}/2}=x_{\psi(3,2n+r)}\frac{Q_{n-r-1-a_{(b_\psi-1)}/2}}{Q_{a_{(b_\psi-1)}/2-1}}$$
 
@@
 
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=$$
+	$$(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=$$
 
-	$$-q^{1/2}x_{\beta(3,2n+r)}\frac{Q_{n+r-1}Q_{a_{(b_\beta-1)}/2}-Q_{n-r-1-a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$
+	$$-q^{1/2}x_{\psi(3,2n+r)}\frac{Q_{n+r-1}Q_{a_{(b_\psi-1)}/2}-Q_{n-r-1-a_{(b_\psi-1)}/2}}{Q_{a_{(b_\psi-1)}/2-1}}$$
 
-	By lemma 3.8, this is simply $-q^{1/2}x_{\beta(3,2n+r)}Q_{n+r}$ as desired, and we have finished proving case 3.
+	By lemma \ref{Q lemma}, this is simply $-q^{1/2}x_{\psi(3,2n+r)}Q_{n+r}$ as desired, and we have finished proving case 3.
 	\\
 
-	\item The only cases we have not yet dealt with are those where either $1$ is an anchor or $\beta(1)=2n+r$. These are those cases related to our inductive hypothesis (ii).
+	\item The only cases we have not yet dealt with are those where either $1$ is an anchor or $\psi(1)=2n+r$. These are those cases related to our inductive hypothesis (ii).
 
-	To not be in case 1 or 2, we must have that there are no anchors between index 1 and $i$, and that there is no integer $s$ such that $1<s<i<\beta(s)-1$.
-It follows from the same argument that proved lemma 3.6 that there exists exactly one $\upsilon\in E_\beta$ such that $\upsilon(1)\not=\beta(1)$.
+	To not be in case 1 or 2, we must have that there are no anchors between index 1 and $i$, and that there is no integer $s$ such that $1<s<i<\psi(s)-1$.
+It follows from the same argument that proved lemma \ref{preimage under hump} that there exists exactly one $\upsilon\in E_\psi$ such that $\upsilon(1)\not=\psi(1)$.
 Define $N$ to be $2n+r$ if 1 is an anchor, or $2n+r-1$ if 1 is not an anchor.
-Then, defining $Y_\beta$ with respect to the sub-matching $\beta(2,N)$, we have that $\alpha\in E_\beta, \alpha\not=\upsilon$ if and only if $\alpha(2,N)\in E_{\beta(2,N)}$.
-Note that for $E_{\beta(2,N)}$ we may apply the inductive hypothesis from case 3, so we have:
-
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$
-
-	$$(1+q)x_{\beta(2,N)}(q)+\sum_{\alpha\in E_{\beta(2,N)},\alpha\not=\beta(2,N)}q^{1/2}x_{\alpha}(q)=$$
-
-	$$-q^{1/2}x_{\beta(2,i-1)}x_{\beta(i+2,N)}\frac{Q_{n+r-1}...Q_{n+r-i/2}}{Q_1...Q_{(i/2-1}}$$
+Then, defining $Y_\psi$ with respect to the sub-matching $\psi(2,N)$, we have that $\sigma\in E_\psi, \sigma\not=\upsilon$ if and only if $\sigma(2,N)\in E_{\psi(2,N)}$.
+Note that for $E_{\psi(2,N)}$ we may apply the inductive hypothesis from case 3, so we have:
+	\begin{align*}
+	&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_\sigma(q)\\
+	=&(1+q)x_{\psi(2,N)}(q)+\sum_{\sigma\in E_{\psi(2,N)},\sigma\not=\psi(2,N)}q^{1/2}x_{\sigma}(q)\\
+	=&-q^{1/2}x_{\psi(2,i-1)}x_{\psi(i+2,N)}\Q{n+r}^{i/2}
+	\end{align*}
 
 	As in case 3, we can also determine $x_\upsilon$.
-$\upsilon$ is defined by $\upsilon(2,i-1)=\beta(2,i-1)$, $\upsilon(i+2,N)=\beta(i+2,N)$, $\upsilon(1)=i$, and $\upsilon(i+1)=2n+r$ if 1 is not an anchor or $i+1$ if 1 is an anchor, and we have:
+$\upsilon$ is defined by $\upsilon(2,i-1)=\psi(2,i-1)$, $\upsilon(i+2,N)=\psi(i+2,N)$, $\upsilon(1)=i$, and $\upsilon(i+1)=2n+r$ if 1 is not an anchor or $i+1$ if 1 is an anchor, and we have:
 
-	$$x_\upsilon=x_{\beta(2,i-1)}x_{\upsilon(i+2,N)}\frac{Q_{n+r-1}...Q_{n+r-i/2}}{Q_1...Q_{i/2-1}}$$
+	$$x_\upsilon=x_{\psi(2,i-1)}x_{\upsilon(i+2,N)}\Q{n+r}^{i/2}$$
 
@@
 
-	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta}q^{1/2}x_\alpha(q)=$$
+	$$(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=$$
 
-	$$-q^{1/2}x_{\beta(2,i-1)}x_{\beta(i+2,N)}\frac{Q_{n+r-1}...Q_{n+r-i/2}}{Q_1...Q_{(i/2-1}}(1-1)=0$$
+	$$-q^{1/2}x_{\psi(2,i-1)}x_{\psi(i+2,N)}\Q{n+r}^{i/2}\prn{1-1}=0$$
 
-	as desired, and the last case is proved.
+	as desired, and the last case is proved. Note that this only relies on the inductive hypothesis from case 3, for which we showed the base case holds.
 	\end{enumerate}
 
-It should be noted that the induction for all of the above cases are codependent, but they only depend on the inductive hypotheses for $2n'+r'<2n+r$.
-So, since our base case holds for all the cases that apply to it, induction holds and the proposition is proved.
+Thus our inductive hypotheses have all been proven, and those that apply in the base case hold in the base case, so by induction the theorem is proved.
 
@@
 \begin{corollary}
-	If $e=n+r+1$, $W_{2n+r}^r$ is reducible, and has a unique sign subrepresentation.
+	If $e=n+r+1$, $M_{2n+r}^r$ is reducible, and has a unique sign subrepresentation.
 \end{corollary}

### 2019-07-30 tex/Drafts/Draft-2.tex

@@
 
-  \fakesubsection{Crossingless Matchings}
+  \fakesubsection{Crossingless matchings}
   The following definition modifies the crossingless matchings defined by Khovanov.\cite{Khovanov}
@@
   \def\vp{\texttt{0}}
-  \fakesubsection{Fibonacci Representation}
+  \fakesubsection{Fibonacci representation}
   Now suppose that $e = 5$ and $k$ contains the algebraic number $\sqrt{q + q^4}$ for reasons which will be apparent soon.
@@
 
-  \fakesubsection{Overview of Paper}
+  \fakesubsection{Overview of paper}
 
@@
 
-\section{Preliminaries on Specht Modules}\label{Specht Modules Section}
+\section{Preliminaries on Specht modules}\label{Specht Modules Section}
   For this section and the rest of the paper, assume $n > 0$.
@@
   \ytableausetup{mathmode,boxsize=normal}
-  \caption{The young diagram corresponding to the partition $(n+r,n)$ with filled-in ook lengths.}\label{Hooks}
+  \caption{The young diagram corresponding to the partition $(n+r,n)$. The hook lengths are in the center of the corresponding cells.}\label{Hooks}
 \end{figure}
@@
   \end{proof}
-  \subsection{Branching}
+  \subsection{Branching theorems of Specht modules}
   In this section as well as later sections, we will consider the restriction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}\prn{S_{2n + r - 1}}$.
@@
     Further, note that the above characterizations are necessary regardless of $e$-regularity;
-    in the case that $\mu$ below fails too be $e$-regular, this proposition will prove that $\lambda$ does not satisfy \label{D Composition Series}, a contradiction.
+    in the case that $\mu$ below fails too be $e$-regular, this proposition will prove that $\lambda$ does not satisfy \ref{D Composition Series}, a contradiction.
 
@@
 
-\section{Crossingless Matchings and Specht Modules}\label{Crossingless Matchings Section}
-In the following section, we will analyze the crossingless matchings representation $M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \simeq S^{(n+r,n)}$ whenever possible.
-We begin by proving irreducibility of $M_{2n + r}^r$ in all cases that $(n+r,n)$ is $e$ top-indivisible;
-when $p = 2$, this is all cases where $S^{(n+r,n)}$ is irreducible.
-This is proven via an inductive process; if $e \nmid n + r + 1$, then $M$ contains no sign subrepresentation, and this allows us to ``project'' down to the case $M_{2(n-1) + r}^r$, and prove irreducibility of $M$ from irreducibility of this space.
+\section{Crossingless matchings and Specht modules}\label{Crossingless Matchings Section}
+In this section, we will analyze the crossingless matchings representation $M := M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \simeq S^{(n+r,n)}$ under certain conditions in $e$.
+We begin by proving irreducibility of $M_{2n + r}^r$ whenever $e \nmid r+2,r+3,\dots,n+r+1$;
+when $e>n$, this is true if and only if $S^{(n+r,n)}$ is irreducible by Corollary \ref{S irreducibility}.
+This is proven via an inductive process; if $e \nmid n + r + 1$, then $M$ contains no sign subrepresentation, and this allows us to ``project'' down to the case $M_{2(n-1) + r}^r$ and deduce irreducibility of $M$ from irreducibility of this representation.
+
+We will use the following base case to the correspondence throughout:
+\begin{lemma}\label{Base cases}
+  Note that $S^{(1^n)}$ is the sign representation and $S^{(n)}$ the trivial representation.
+  We have the following isomorphisms
+  \begin{enumerate}[label={(\roman*)}]
+    \item $M_2^0 \simeq S^{(2)}$,
+    \item $M_r^r \simeq S^{(1^r)}$.
+  \end{enumerate}
+  Each of these are 1-dimensional, so they are irreducible.
+\end{lemma}
+\begin{proof}
+  (i) follows from the fact that $(1 + T_1)w = (1 + q)w$, and hence $T_1w = qw$ for any nonzero vector $w \in M_2^0$.
+  Similarly, (ii) follows from the fact that $(1 + T_i)w = 0$, so $T_iw = -w$ for any $i$ and any $w \in M_r^r$.
+\end{proof}
 
 \subsection{Irreducibility of $M$}
+We refer to a vector $w \in M$ satisfying $\SH w = M$ as \emph{cyclic}.
+It is a classical result that a representation $W$ is irreducible if and only if every nonzero element of $W$ is cyclic.\cite{Etingof}
+We will prove irreducibility by showing that every nonzero $w \in M$ is cyclic;
+the following lemma is integral in showing this.
+
 \begin{lemma}
@@
 
-    Note that, between anchors $a<a'$ having no arc $b$ with $a < b < a'$, the $M_{a'-a}^0$ case allows us to generate the vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.\footnote{At the ends, we apply the $M_a^0$ case or the $M_{2n + r - a}^{0}$ case in the same way for the first $a$ or last $2n + r - a$ indices.}
-
-  Applying this between each arc gives us a vector with length-2 arcs and anchors, and we may use the appropriate $(1+T_i)$ to move anchors to any positions, and the reverse process from above to generate the correct matchings between arcs and generate any other basis vector.
-\end{proof}
-
-Let $K := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$.
-This will be a large technical tool in our proof of irreducibility.
-
-\iffalse
-\begin{lemma}\label{Represented}
-  Let $w_j$ be the basis vector with anchors $1,\dots,r$ and all arcs of maximal length.
-  Suppose $w \in K \backslash \cbr 0$.
-  Then, $w_j$ is represented in $w$.
-\end{lemma}
-\begin{proof}
-  We will show this in steps; first, we show that, given that a vector is represented with anchors $1,\dots,s$, there must be a vector represented in $w$ with $(s+1)$st anchor, including when $s = 0$;
-  this implies that a vector is represented with anchors $1,\dots,r$.
-  Then, we will show that, given a vector is represented with anchors $1,\dots,r$ and first $s$ arc-lengths $n,n-2,\dots,n-2s$, there is a vector represented with these and the $(s+1)$st arc-length $n-2s-2$.
-  This implies that $w_j$ is represented.
-
-  \def\lemsep{7pt}
-  \vspace{\lemsep}
-  \textit{Step 1.}
-  Suppose that $s < r$ is the maximal number such that a vector with anchors $1,\dots,s$ is represented.
-  Take the vector $w_i$ which, among vectors represented in $w$ with anchors $1,\dots,s$, has $(s+1)$st anchor at minimal index $t > s + 1$,
-  Then, $q^{-1/2}(1 + T_{t-1})w_i$ has anchors $1,\dots,s$ and a earlier index than $t$, so it was not represented before;
-  further, for any other basis vector $w_l \neq w_i$ to map onto $q^{-1/2}(1 + T_{t-1})w_i$, we would require that $w_l$ has anchors $1,\dots,s$ and some other anchor at index $t' < t$, so it is not represented.
-  Hence $w_i$ is unique among the vectors represented mapping onto $q^{-1/2}(1 + T_{t-1})w_i$, and $(1 + T_{t-1})w$ represents this vector, giving $w \notin \ker (1 + T_{t-1})$.
-
-  When $s = 0$, this is similar, and we simply perform this logic on the 1st anchor.
-  Each lead to contradiction, so we must have $s = r$.
-
-  \vspace{\lemsep}
-  \textit{Step 2.}
-  This step is similar;
-  suppose that $s < n$ is the maximal number such that a vector with anchors $1,\dots,r$ and first $s$ arc-lengths $n,\dots,n-2s$ is represented.
-  Take the vector $w_i$ which, among vectors represented in $w$ with anchors $1,\dots,r$ and first $s$ arc-lenths $n,\dots,n-2s$, has maximal length $t$ of the arc beginning at index $r + s + 1$.
-  Then, $q^{1/2}(1 + T_{r + s + t})w_i$ is mapped to only by $w_i$ and vectors having anchors $1,\dots,r$ and first $s+1$ arc-lengths $n,\dots,n-2s,t'$ with $t' > t$, which are not represented in $w$;
-  hence $q^{-1/2}(1 + T_{r + s + t})w_i$ is represented in $(1 + T_{r+s+t})w$, giving $w \notin \ker (1 + T_{r + s + t})$.
-  The $s = 0$ case is similar, and implies that $s = n$.
-\end{proof}
-\fi
+  Note that, between anchors at indices $a<a'$ having no arc at index $b$ with $a < b < a'$, the $M_{a'-a}^0$ case allows us to generate the basis vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.
+  At the ends, we apply the $M_a^0$ case or the $M_{2n + r - a}^{0}$ case in the same way for the first $a$ or last $2n + r - a$ indices.
+
+  Applying this between each arc gives us a vector with anchors and length-2 arcs, and we may use the appropriate $(1+T_i)$ to move anchors to any positions.
+  Then, we may use the reverse process from above to generate the correct matchings between arcs and generate any other basis vector.
+\end{proof}
+
+Let $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$.
+This will be an important technical tool in our proof of irreducibility.
 
@@
   Suppose $e \nmid n + r + 1$.
-  Then, $K = 0$.
+  Then, $K := K_{2n + r}^r = 0$.
 \end{lemma}
@@
   Suppose that $e \nmid r+2,r+3,\dots,n+r+1$.
-  Then, the representation $M_{2n + r}^r$ is irreducible. 
+  Then the representation $M_{2n + r}^r$ is irreducible. 
 \end{theorem}
@@
   We proceed by induction on $n$.
-  Note that, by identification with the trivial and sign representation, the base case $n = 0$ is already proven.
-
-  Take an arbitrary vector $w \in W$.
-  By Lemma \ref{Trivial} there exists some $(1 + T_i) \in \SH$ such that $(1 + T_i)w$.
-  Note that \[\ima (1 + T_i) = \Span\cbr{w_j \mid w_j \text{ contains arc }(i,i+1)}.\]
+  The base case the base case $n = 0, r \neq 0$ and $n = 1, r = 0$ follow from Lemma \ref{Base cases}.
+
+  Take an arbitrary vector $w \in M$.
+  By Lemma \ref{Trivial} there exists some $(1 + T_i) \in \SH$ such that $(1 + T_i)w \neq 0$.
+  Note that \[\ima (1 + T_i) = \Span\cbr{w_j \mid w_j \text{ contains the arc }(i,i+1)}.\]
   Hence, as vector spaces, there is an isomorphism $\varphi:\ima(1 + T_i) \rightarrow M_{2(n-1) + r}^r$ ``deleting'' the arc $(i,i+1)$.
 
-  We will show that, for every action $(1 + T_j') \in \SH(S_{2(n-1) + r})$, there is some action $h_j \in M_{2n + r}^r$ such that the following commutes:
+  We will show that, for every element $(1 + T_j') \in \SH(S_{2(n-1) + r})$, there is some element $h_j \in \SH(S_{2n + r})$ such that the following commutes:
   \[
     \begin{tikzcd}
-      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] \arrow[d,"h_j"] & M_{2(n-1) + r}^r \arrow[d,"1 + T_j"]\\
+      \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] \arrow[d,"h_j"] & M_{2(n-1) + r}^r \arrow[d,"1 + T_j'"]\\
       \ima (1 + T_i) \arrow[r,"\varphi" above, "\sim" below] & M_{2(n-1) + r}^r
@@
   \]
-  Indeed, when $i \neq j$ this is given by $h_j = 1 + T_j$, and we have $h_i = q^{-1}(1 + T_i)(1 + T_{i+1})(1 + T_{i-1})$, as given by Figure \ref{bigloop}.
-
-  Note that, by definition, $e \nmid r+2,\dots,n+r$ as well, and hence $(n+r-1,n-1)$ satisfies the hypotheses of the proposition as well..
-  Then, due to the inductive hypothesis, there is some action $h' \in \SH(S_{2(n-1) + r})$ sending $\varphi((1 + T_i)w)$ to the image of a basis vector;
-  then, the action $\SH$ generates the endomorphism $\varphi^{-1}h'\varphi$ sending $(1 + T_i)w$ to a basis vector, giving $w$ cyclic and hence $M_{2n + r}^r$ irreducible.
+  Indeed, when $i+1 \neq j$ this is given by $h_j = 1 + T_j$, and we have $h_{i+1} = q^{-1}(1 + T_i)(1 + T_{i+1})(1 + T_{i-1})$, as given by Figure \ref{bigloop}.
+
+  Note that, by definition, $e \nmid r+2,\dots,n+r$ as well, and hence $(n+r-1,n-1)$ satisfies the hypotheses of the proposition as well.
+  Then, by the inductive hypothesis, there is some element $h' \in \SH(S_{2(n-1) + r})$ sending $\varphi((1 + T_i)w)$ to the image of a basis vector of $M_{2n + r}^r$ via $\varphi$;
+  then, the action $\SH$ generates the endomorphism $\varphi^{-1}h'\varphi$ of $M$, which sends $(1 + T_i)w$ to a basis vector in $M_{2n + r}^r$.
+  This implies that $w$ is cyclic, and hence $M_{2n + r}^r$ is irreducible.
   \begin{figure}
@@
   \caption{The correspondence between the action of $(1 + T_2)$ on $w'_5 \in M^0_6$ and the action of $q^{-1}(1 + T_3)(1 + T_4)(1 + T_2)$ on the corresponding vector in $M^0_8$ having arc $(3,4)$ first, then on $w'_2 \in M^0_4$.
-  This demonstrates that the action works with and without creating a loop.
+  This demonstrates that the action works with or without creating a loop.
   }
@@
 
-\subsection{Correspondence}
-The following theorem of Mathas generalizes the characteristic-free version of the classical branching theorem.\cite{Mathas-article}
+\begin{figure}
+\[
+  \begin{gathered}\CapNAction{4}{1/1,3/2,2/3}{2}\end{gathered}
+  \longsquigrightarrow
+  \begin{gathered}\BigNAction\end{gathered}
+\]
+  \caption{The isotopy demonstrating the correspondence between $h_{i+1}$ and $T_i'$;
+  the scaling issue with having three simple reflections is handled by the $q^{-1}$ factor in $h_{i+1}$.}
+\end{figure}
+
+\subsection{Correspondence with Specht modules}
+The following theorem due to Mathas (theorem 5.5 in \cite{Mathas-article}) generalizes the classical branching theorem of the symmetric group.
 It will not be necessary for our present proof of the correspondence, but analogy with $M$ is suggestive.
-\begin{theorem}[Characteristic-Free Classical Branching Theorem]
+\begin{theorem}[Characteristic-free classical branching theorem]
   Let $\lambda$ be a partition of $m$ with $\ell$ removable nodes.
-  Then, $\Res \, S^\lambda$ has an $\SH_{k,q}(S_{m-1})$-module filtration
+  Then, $\Res S^\lambda$ has an $\SH_{k,q}(S_{m-1})$-module filtration
   \[
@@
 \end{theorem}
-
+In particular, this holds in cases where $S^\lambda$ fails to be irreducible.
 If we replace $S^\lambda$ with the appropriate $M_{2n + r}^r$ above, we find the statement of the following proposition.
@@
     \begin{equation}
-      0 \subset M_{2n + r - 1}^{r-1} \subset \Res \, M_{2n + r}^r \label{Filtration}
+      0 \subset M_{2n + r - 1}^{r-1} \subset \Res M_{2n + r}^r, \label{Filtration}
      \end{equation}
-     with $\Res \, M_{2n + r}^r / M_{2n + r - 1}^{r-1} \simeq M_{2n + r - 1}^{r + 1}$. 
+     with $\Res M_{2n + r}^r / M_{2n + r - 1}^{r-1} \simeq M_{2n + r - 1}^{r + 1}$. 
     \item
@@
       \begin{equation}
-        M_{2n - 1}^1 \simeq \Res \; M_{2n}^0 \label{0 Restriction}
+        M_{2n - 1}^1 \simeq \Res M_{2n}^0. \label{0 Restriction}
        \end{equation}
   \end{enumerate}
-    When the case is type (i) from the irreduibility lemma, this is a composition series.
+  In the case that $e \nmid r+1,\dots,n + r + 1$, \ref{Filtration} and \ref{0 Restriction} are composition series.
 \end{proposition}
@@
   \textbf{(i)}
-  Note that we may identify the subrepresentation of $\Res \; M_{2n + r}^r$ having anchor $n$ with $M_{2n + r - 1}^{r-1}$.
-
-  Let $U := \Res \; M_{2n + r}^r / M_{2n + r - 1}^{r - 1}$. 
+  Note that we may identify the subrepresentation of $\Res M_{2n + r}^r$ having anchor at index $2n+r$ with $M_{2n + r - 1}^{r-1}$.
+
+  Let $U := \Res M_{2n + r}^r / M_{2n + r - 1}^{r - 1}$, and let $\pi: \Res M_{2n + r}^r \twoheadrightarrow U$ be the associated projection to $U$.
   Let $\phi:U \rightarrow M_{2n + r - 1}^{r + 1}$ be the $k$-linear map which regards the arc $(i,2n + r)$ in $U$ as an anchor at $i$ in $M_{2n + r - 1}^{r + 1}$.
@@
 
-  Given a basis vector $w_j$ with arc $(i,2n + r)$, $\phi$ is clearly compatible with $T_{i'}$ with $i' \neq i,i-1$.
-  Further, it's easy to verify that $\phi$ is compatible with $T_{i}$ and $T_{i-1}$, as actions on one anchor were designed for this deformation.
-  When there are anchors $(i,i+1)$, then $\phi(T_iw_j) = T_i\phi(w_j) = 0$, and similar for $T_{i -1}$.
+  Given a basis vector $w_j$ containing arc $(i,2n + r)$, $\phi$ is clearly compatible with $(1 + T_{i'})$ with $i' \neq i,i-1$.
+  Further, it is easy to verify that $\phi$ is compatible with $T_i$ by definition of the relevant modules, as well as with $(1 + T_{i-1})$ when $w_j$ does not have anchor $i-1$.
+  The case that $w_j$ has anchor $i-1$ is illustrated in the following commutative diagram:
+  \[
+    \begin{tikzcd}
+      M_{2n + r}^r \arrow[r,"1 + T_i"] \arrow[d,"\phi \circ \pi"] & M_{2n + t}^r \arrow[r,"\pi"] & U \arrow[d,"\phi"]\\
+      M_{2(n-1) + r + 1}^{r+1} \arrow[rr,"1 + T_i"] & & M_{2(n-1) + r + 1}^{r+1}
+    \end{tikzcd}
+  \]
+  which we may diagram chase as follows
+    \[
+    \QuotDiagram
+  \]
+
+  In each of these cases, linearity of $\SH$-action and $\phi$ give 
+  \begin{align*}
+    \phi(T_jw_i) 
+    &= \phi(-w_j + (1+T_j)w)\\
+    &= -\phi(w_j) + (1 + T_j)\phi(w_j)\\
+    &= T_j\phi(w_j).
+  \end{align*}
   Hence $\phi$ is an isomorphism of representations, and the statement is proven.
@@
   \textbf{(ii)}
-  This follows with the above proof, defining $M_{2n - 1}^{-1} := 0$
-\end{proof}
-
-We've now assembled the basic pieces necessary to prove our correspondence in the case $e > n + r  1$.
-Due to some problematic phenomena in the $r = 0$ case, we will initially make an assumption that $e \neq 4$ or $r \neq 0$ so that we may use the combinatorics of Proposition \ref{Combinatorics}.
-We will then assume the remaining case $e = 4, r = 0$, and prove our correspondence using process of elimination via the other surrounding cases for $e = 4$.
+  This follows from an analogous proof:
+  now, $\phi:\Res M_{2n}^0 \rightarrow M_{2(n-1)+1}^1$ is an isomorphism of representaitons, which is proven to be $\SH$-linear by the same proof.
+\end{proof}
+
+We've now assembled the basic pieces necessary to prove our correspondence in the case $e > n + r + 1$.
 
@@
 \begin{proof}
-  The case $n = 0$ is already proven, so suppose $n > 0$.
-  In order to use Proposition \ref{Combinatorics}, suppose for now that either $e \nmid 4$ or $r \neq 0$.
-
-  We will prove this inductively; by identification with the trivial and sign representations, the $2n + r = 2$ caseholds, so suppose this is true for $M_{2m + s}^s$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$ (i.e.
-$e > m + s + 1$).
-
-  By irreducibility, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
-  By the inductive hypothesis and irreducibility, we have a composition series given by the exact sequence
+  The case $n = 0$ is already proven, by lemma \ref{Base cases}, so suppose $n > 0$.
+  In order to use Proposition \ref{Combinatorics}, suppose for now that either $e \nmid 4$ or $r > 0$.
+
+  We will prove this inductively; the base case $2n + r = 2$ is implied by \ref{Base cases}, so suppose that $M_{2n + s}^s \simeq S^{(m+s,s)}$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$, so that $e > m + s + 1$.
+
+  Suppose $r > 0$.
+  By Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
+  By the inductive hypothesis and Corollary \ref{S irreducibility}, we have a composition series given by the short exact sequence
   \begin{equation}
@@
    \end{equation}
-  Hence the theorem is given by Proposition \ref{Combinatorics}.
+  Hence the theorem is given by Proposition \ref{Combinatorics} (i).
+
+  Now suppose $r = 0$ and $e \neq 4$.
+  Similarly, by Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$, and by the inductive hypothesis and Corollary \ref{S irreducibility}, we have the irreducible restriction $\Res D^\lambda \simeq D^{(n,n-1)}$.
+  Then, the theorem is given by Proposition \ref{Combinatorics} (ii).
 
@@
 
-\iffalse
-We may reuse the above structure of proof as above;
-suppose $M_{2n + r}^r$ and $S^{(n+r,n)}$ are irreducible, and $\lambda = (n+r,n)$ is the unique diagram having composition series \eqref{Composition Series}.
-Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
-
-We have covered all irreducible cases for $r = 0$ and $n = 0$ above.
-For example, another case where we may show all irreducible cases is $n = 1$, which we will do now.
-\begin{lemma}\label{n=1 irreducibility}
-    Set $n = 1$. 
-    Then $M_{2 + r}^r$ is irreducible iff $e \nmid r + 2$.
-\end{lemma}
-\begin{proof}
-  A basis element $w_i \in W$ is determined entirely by the position of the arc, of which there are $r + 1$ options.
-  Hence $\dim W = r + 1$.
-
-  Further, $\dim\prn{\ima (1 + T_i)} = 1$ for all $i$;
-  by lemma \ref{Cyclic} $W$ is irreducible iff $K := \bigcap_{i = 1}^{r+1} \ker (1 + T_i) = \ker \bigoplus (1 + T_i)$ is trivial.
-  By \ref{Trivial}, this is true iff $e \nmid r + 2$.
-\end{proof}
-
-\begin{theorem}
-  Set $n = 1$ and suppose $e \nmid r + 2$.
-  Then $M_{2 + r}^r \simeq S^{(1+r,1)}$.
-\end{theorem}
-\begin{proof}
-  Using lemma \ref{n=1 irreducibility} and \ref{S irreducibility} it is sufficient to prove that, for $D^\lambda$ having composition series \eqref{Composition Series}, we have $\lambda = (1+r,1)$.
-  Similar to before, we consider the options $\lambda_1 := (r,1,1)$, $\lambda_2 := (r,2)$, and $\lambda_3 = (1+r,1);$.
-  We may straightforwardly check that $\lambda_1$ and $\lambda_2$ have socle containing partitions other than the composition factors in \eqref{Composition Series} by showing that each have a good number 2 as follows:
-  \begin{align*}
-    \beta_{\lambda_1}(1,2) &= 3 - 1 + r = r+2\\
-    \beta_{\lambda_2}(1,2) &= 2 - 1 + r + 1 = r+2.
-  \end{align*}
-  These are each nonvanishing mod $e$, so they are good and $\lambda = \lambda_3$, giving the theorem.
-\end{proof}
-\fi
-
-\subsection{Kernels and Further Work}
+\subsection{Kernels and further work}
 \begin{proposition}\label{Represented}
@@
 
-\section{Fibonacci Representations and Quotients of Specht Modules}\label{Fibonacci Section}
+\section{Fibonacci representations and quotients of Specht modules}\label{Fibonacci Section}
 We have difficulty characterizing the Specht module above when it is irreducible.
@@
 
-\section{Empirical Results}\label{Empirics Section}
-In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representations.\cite{Github}
+\newpage
+\appendix
+\section{Compatibility of Representations with the Relations}
+In general, we defined the representations $V := V^{2n + r}$ and $M := M_{2n + r}$ for the free algebra on generators $\cbr{T_1,\dots,T_{2n + r - 1}}$.
+Recall that we may give a presentation of $\SH$ having generators $T_i$ and relations
+\begin{align}
+  (T_i - q)(T_i + 1) &= 0 \label{quadratic}\\
+  T_iT_{i+1}T_i &= T_{i+1}T_iT_{i+1} \label{braid1}\\ 
+  T_iT_j &= T_jT_i \hspace{40pt} \abs{i - j} > 1. \label{braid2}
+\end{align}
+We call \eqref{quadratic} the \emph{quadratic relation} and \eqref{braid1}, \eqref{braid2} the \emph{braid relations}.
+It is easily seen that a representation of $\SH$ is equivalent to a representation of the free algebra $k\langle T_i \rangle$ which are compatible with the relations.
+We will prove in the following sections that $V$ and $M$ are compatible with the Hecke algebra relations.
+
+\subsection{Explicit Definition of $M$}
+We will give a more careful definition of the crossingless matchings representation here.
+\begin{definition}
+  A \emph{crossingless matching on $2n+r$ indices with $r$ anchors} is a partition of $\cbr{1,\dots,2n+r}$ into $n$ parts of size $2$ and $r$ of size 1 such that no two parts $(a,a')$ and $(b,b')$ satisfy $a < b < a' < b'$, and no parts $(c), (a,a')$ satisfy $a < c < a'$.
+  We will call these arcs and anchors, respectively.
+  Then, define $M^r_{2n+r}$ to be the $k$-vector space with basis the set of crossingless matchings on $2n+r$ indices with $r$ anchors.
+
+  In order to endow $M^r_{2n + r}$ with an $\SH$-action, consider some basis element $w_j$ and some element $(1 + T_i)$ of $\SH$.
+  The elements $\cbr{1} \cup \cbr{1 + T_i | 1 \leq i < 2n + r}$ generate $\SH$, so it is sufficient to define the action of $1 + T_i$ on $w_j$.
+
+  If $w_j$ has arc $(i,i+1)$, define $(1 + T_i)w_j := (1 + q)w_j$.
+  If $w_j$ has anchors $W(i) = i$ and $W(i+1) = i+1$, define $(1 + T_i)w_j := 0$.
+  If $w_j$ has anchor $W(i) = i$ and arc $W(i+1) = b$, define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$, $w_l(b) = b$, and all other arcs agree with $w_j$.
+  If $w_j$ has arcs $W(i) = a$ and $W(i+1) = b$, then define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$,$w(a) = b$, and all other acts agree with $w_j$. 
+  We verify that this is well-defined in Section \ref{Cross Relations}.
+\end{definition}
+
+We may alternately sharpen our topological definition;
+\begin{definition}
+Fix $2n + r$ distinct points $a_1,\dots,a_{2n + r}$ points along $\RR \times \cbr{0} \subset \RR^2$ and $r$ distinct points $b_1,\dots,b_r$ along $\RR \times \cbr{1}$.
+Then, define $M_{2n + r}^r$ to have basis given by the isotopy classes of $n + r$ paths connecting the points $a_1,\dots,a_{2n+r},b_1,\dots,b_r$ such that no distinct $b_i,b_j$ are connected by a path.
+
+We will take some basis element $w_j \in M_{2n +r}^r$ and define the action $(1 + T_i)w_j$.
+To do so, map $w_j$ through the natural embedding $\RR \times \brk{0,1} \hookrightarrow \RR \times \brk{\frac{1}{2},1}$, and form the figure $w_j^i$ by adjoining the lines connecting $a_l$ and $a_l + \prn{0,\frac{1}{2}}$ for all $l \neq i,i+1$ as well as paths from $a_i$ to $a_{i+1}$ and $a_i + \prn{0,\frac{1}{2}}$ to $a_{i+1} + \prn{0,\frac{1}{2}}$.
+This has either 0 or 1 path components which do not intersect $\RR \times \cbr{0,1}$;
+these form ``loops.''
+
+Take the figure $\tilde w_j^i$ without this component.
+If $\tilde w_j^i$ is not isotopic to some $w_l$, then define $(1 + T_i)w_j := 0$.
+If $\tilde w_j^i$ is isotopic to some $w_l$, define $(1 + T_i)w_j := (1 + q)w_l$ if $w_j^i$ has a loop and $(1 + T_i)w_j := q^{1/2}w_l$ otherwise.
+This process is illustrated in Figure \ref{Action}.
+\end{definition}
+
+Let the length of an arc $(i,j)$ be $l(i,j) := j - i + 1$.
+Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
+  This basis is illustrated for $M_{5}^1$ in Figure \ref{S5 Basis}.
 
 \begin{remark}
-  These results are restricted by two things; first and with less recourse, this was computed in Magma, a closed source language with bugs that could not be resolved in certain cases.
-  Second, the memory necessary to store the Hecke algebra via basis elements and structure constants grows with $(n!)^3$;
-  this is prohibitively large when $m > 7$.
-  An implementation as a quotient by a free algebra or only specifying multiplication by generators may fix this, however, this is not possible with the Magma language, and the closed source renders modification of the language impossible.
+  This definition gives a graphical calculus for working with our module.
+  It should be clear that, if $w_j^i$ has a loop then $w_l(i) = i+1$ and $w_l = w_j$.
+  Further, this easily defines an arbitrary composition:
+  \[
+    (1 + T_{i_1})\cdots(1 + T_{i_\ell})w_j = q^{(\ell - t)\frac{1}{2}}(1 + q)^tw_l
+  \]
+  if the figure we make via $(1+T_{i_1})\cdots(1+T_{i_\ell})$ is isotopic to $w_l$ after removing $t$ loops.
 \end{remark}
 
-We give in Figure \ref{Fib Data} some isomorphisms between $M/K$ and $V$ for $e \geq n + r + 1$ with $p = \infty$;
-all but one of these are cases with $e > n + r + 1$, so $K=0$ and this is an isomorphism with our crossingless matchings representation.
-The case $n = 1$, $r = 3$ gives an example of an isomorphism not proven in general, but proven via our computation.
-All of these computations are done for $q$ a primitive 5th root of unity in the algebraic extension of the Cyclotomic field $\QQ(\zeta_{10})$ by a root of the polynomial $x^2 - \tau$.
-
-We give in Figure \ref{Empirical Kernel} some data supporting a conjecture concerning sign subrepresentations of $M_{2n + r}^r$.
-The computations to support this were done over $\CC$ with $q$ a primitive 5th root of unity.
-
-It is known that, for small $2n + r$, each Specht module $S^{(n+r,n)}$ has a composition series of length 2.
-We give in Figures \ref{Composition series e=3} through \ref{Composition series e=6} the map $M_{2n + r}^r \twoheadrightarrow U_{2n + r}^r$, which conjecturally illustrates the quotient $S^{(n+r,n)} \twoheadrightarrow U_{2n + r}^r$ for all $2n + r \leq 7$.
-
+  Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
+  call this the \emph{increasing lexicographical order basis}.
+  Further, we have a surjection $M_{2n + 2r}^0 \twoheadrightarrow M_{2n + r}^r$ which takes basis elements to basis elements;
+  this induces an order on the basis for $M_{2n +r}^r$, which we will henceforth refer to as the \emph{induced lexicographical order basis.}
+  This basis is illustrated for $M_{5}^1$ in Figure \ref{S5 Basis}.
+
+\subsection{Compatibility for the Crossingless Matchings Representations}
+\label{Cross Relations}
+We verify the relations on the crossingless matchings representation $M$.
+Take some basis vector $w_i \in M$.
+We will first check \eqref{quadratic} by case work:
+\begin{itemize}
+  \item Suppose there is an arc $(i,i+1)$.
+    Then, \[(T_i-q)(T_i + 1)w = (1 + q)\prn{(1 + T_i)w - (1 + q)w} = 0,\] giving \eqref{quadratic}.
+  \item Suppose there is no arc $(i,i+1)$ and indices $i,i+1$ do not both have anchors;
+    then $(T_i +  1)w = q^{1/2}w'$ for some basis vector $w'$ having arc $(i,i+1)$, and the computation follows as above for \eqref{quadratic}.
+  \item Suppose $i,i+1$ are anchors;
+    then $(T_i + 1)w = 0$, giving \eqref{quadratic}.
+\end{itemize}
+
+\vspace{5pt}
+Now we verify \eqref{braid1}.
+Let $h := (1 + T_i)(1 + T_{i+1})(1+T_i)$, and let $g := (1 + T_{i+1})(1 + T_i)(1 + T_{i+1})$.
+Note the following expansion:  
+  \begin{align*}
+      hw
+      &= 1 + 2T_i + T_i^2 + T_{i+1} + T_iT_{i+1} + T_{i+1}T_i + T_iT_{i+1}T_i\\
+      &= 1 + (1+q)T_i + T_{i+1} + T_iT_{i+1} + T_{i+1}T_i + T_iT_{i+1}T_i.
+    \end{align*}
+    This equality, with $i$ and $i+1$ interchanged, holds for $g$.
+    Hence we have
+    \[
+      (h-g)w = q(T_i - T_{i+1}) + T_iT_{i+1}T_i - T_{i+1}T_iT_{i+1}.
+    \]
+    Hence we may equivalently check that $(h-g)w = q(T_i - T_{i+1})$.
+    In fact, $hw = q(1 + T_i)$ and $gw = q(1 + T_{i+1})$ by Figure \ref{braid1arc}, giving compatibility.
+    \begin{figure}
+\[
+  \begin{gathered}\EmptyNAction{5}{2/1,3/2,2/3}\end{gathered}
+  \longsquigrightarrow
+  \begin{gathered}\EmptyNAction{5}{2/1}\end{gathered}
+  \hspace{30pt}
+  \begin{gathered}\EmptyNAction{5}{3/1,2/2,3/3}\end{gathered}
+  \longsquigrightarrow
+  \begin{gathered}\EmptyNAction{5}{3/1}\end{gathered}
+\]
+  \caption{
+    The above give visual intuition for isotopies giving rise to equalities between $(1 + T_i)(1 + T_{i-1})(1 + T_i)w_j$ and $q(1 + T_i)$, and between $(1 + T_{i+1})(1 + T_i)(1 + T_{i+1})w_j$ and $q(1 + T_i)$.
+  }
+  \label{braid1arc}
+\end{figure}
+
+\begin{figure}
+\[  
+  \begin{gathered}\EmptyNAction{7}{2/1,5/2}\end{gathered}
+  \longsquigrightarrow
+  \begin{gathered}\EmptyNAction{7}{5/1,2/2}\end{gathered}
+\]
+  \caption{
+    The above give visual intuition for isotopies giving rise to equalities between $(1 + T_i)(1+T_j)w_l$ and $(1 + T_j)(1 + T_i)w_l$.}
+    \label{braid2arc}
+\end{figure}
+
+Lastly, we have the equation
+\[
+  (1 + T_i)(1 + T_j) - (1 + T_j)(1 + T_i) = T_iT_j - T_jT_i
+\]
+and hence we simply need to verify that $(1 + T_i)$ and $(1 + T_j)$ commute, as shown in Figure \ref{braid2arc}
+
+\subsection{Compatibility for the Fibonacci Representations} 
+\label{Fib Relations}
+We verify the relations on the Fibonacci representation $V$.
+Note that \eqref{braid2} follows easily from the ``local'' nature of $V$, and the others may be verified explicitly on strings of length 3 and 4.
+By considering the coefficients in order of \eqref{Fib Action}, the quadratic relation \eqref{quadratic} gives the following polynomials in $q$:
+\begin{equation}
+  \begin{split}
+    (\vara - q)(\vara + 1) &= 0,\\
+    (\varb - q)(\varb + 1) &= 0,\\
+    \varc\vard + \vard\vare &= (q-1)\vard,\\
+    \varc^2 + \vard^2 &= (q -1)\varc + q,\\
+    \vare^2 + \vard^2 &= (q -1)\vare + q
+  \end{split}
+\end{equation}
+The first two of these are easily verified.
+Since $\vard \neq 0$, the third is equivalently given by
+\[
+  (q - 1) = \varc + \vare = \tau(q\tau - 1 + q - \tau) = (\tau^2 + \tau)(q - 1)
+\]
+or that $\prn{\tau^2 + \tau - 1}(q-1) = 0$.
+One may verify that \[\tau^2 + \tau - 1 = q^6 + 2q^5 + q^4 + q^3 + q^2 - 1 = (-1+q+q^2)\brk{5}_q = 0.\]
+
+The fourth is given by the quadratic
+\[
+  \tau^2\brk{(q\tau-1)^2 - \tau(q+1)} = \tau(q-1)(q\tau - 1) + q
+\]
+or equivalently,
+\[
+  (\tau^2 + \tau - 1)\brk{q\prn{qt^2 + 1} + t} = 0.
+\]
+
+The fifth is similarly given by
+\[
+  (\tau^2 + \tau - 1)\brk{q\prn{qt + 1} + t^2} = 0. 
+\]
+All of these vanish for $e = 5$, giving compatibility with \eqref{quadratic}.
+
+\vspace{7pt}
+We now verify \eqref{braid1}.
+We may order the basis for $V^4$ as follows:
+\[
+  \cbr{(\vp\vp\vp\vp),(\vs\vp\vp\vs),(\vp\vp\vp\vs),(\vs\vp\vp\vp),(\vs\vp\vs\vp),(\vp\vs\vp\vs),(\vp\vp\vs\vp),(\vp\vs\vp\vp)}.
+\]
+Then, in verifying the braid relation \eqref{braid1} in this order, we encounter the following quadratics (with tautologies and repetitions omitted):
+\begin{align*}
+    \vara\vare^2 + \varb\vard^2 &= \vara^2 \vare\\
+    \vara\vard\vare + \varb\varc\vard &= \vara\varb\vard\\
+    \varb\varc^2 + \vara\vard^2 &= \varb^2\varc\\
+    \vara\varc^2 + \vard^2\vare &= \vara^2\varc\\
+    \vard\vare^2 + \vara\varc\vard &= \vara\vard\vare
+\end{align*}
+Substituting in $\tau$ and dividing by $\delta$ whenever possible, these are equivalent to the vanishing of the following polynomials in $q$:
+\begin{align*}
+  -q (1 + q) (1 + q^2 + q^3) (2 + q + 3 q^2 + 2 q^3) \brk{5}_q &= 0\\
+  (1 + 2 q + q^3 + q^4) \brk{5}_q &= 0\\
+  (1+q)^2 (1+q^2+q^3) (1+3q^3 - q^4 + q^6)\brk{5}_q &= 0\\
+  (1+q)^2 (1+q^2+q^3) (1+5q+5q^2+3q^3+3q^4+3q^5+q^6)\brk{5}_q &= 0\\
+  (1+q) (1+q^2+q^3) (-1+2q+q^2+q^3+q^4)\brk{5}_q &= 0.
+\end{align*}
+Notably, each of these vanish when $e = 5$, giving compatibility with \eqref{braid1}.
+
+\section{Restrictions to Conjugate Subalgebras}\label{Algebra}
+Throughout the text, for some representation $V$, we refer to $\Res_{\SH(S_{l})}^{\SH(S_m)} V$ without specifying exactly which subalgebra $\SH(S_{l})$.
+For instance, in section \ref{Fibonacci Section}, we explicitly state that the subrepresentations $V_{\vs\vp} \oplus V_{\vs\vs}$ and $V_{\vp\vp}$ are isomorphic because they both may be characterized by such a restriction.
+We will verify that this is justified, using a more general fact about resctrictions to conjugate subalgebras.
+\begin{proposition}
+  Suppose $B,B'$ are subalgebras of a $k$-algebra $A$ with $B = uB'u^{-1}$ for some unit $u \in A^\times$, and let $V$ be a left $A$-module.
+  Let $\phi:V \rightarrow V$ be the linear automorphism specified by $v \mapsto uv$.
+  Then, the following commutes for any $b \in B$:
+  \[
+    \begin{tikzcd}
+      V \arrow[r,"\phi"] \arrow[d,"b"] & V \arrow[d,"ubu^{-1}"]\\
+      V \arrow[r,"\phi"] & V
+    \end{tikzcd}
+  \]
+  Hence, through the identification of $B$ and $B'$ via conjugation by $u$, we have $\Res_{B}^A V \simeq \Res_{B'}^A V$
+\end{proposition}
+\begin{proof}
+  It suffices to note that $(ubu^{-1})uv = ubv$.
+\end{proof}
+
+\begin{corollary}
+  Suppose $\SH',\SH''$ are two subalgebras of $\SH(S_m)$ generated by $l$ simple reflections and $V$ is a representation of $\SH$.
+  Then, $\Res_{\SH'}^{\SH} V \simeq \Res_{\SH''}^\SH V$.
+\end{corollary}
+\begin{proof}
+  Let $\SH'$ and $\SH''$ be the subalgebras of $\SH(S_m)$ generated by the reflections $\cbr{T_{i_1},\dots,T_{i_l}}$ and $\cbr{T_{i_1},\dots,T_{i_{j-1}},T_{i_j + 1},T_{i_{j+1}},\dots,T_{i_l}}$ for $1 \leq i_1 < \dots < i_{j-1} < i_j + 1 < i_{j+1} < \dots < i_l \leq n$.
+  It is sufficient to prove that $\SH'$ and $\SH''$ are conjugate;
+  then transitivity gives conjugacy of any $S_l \subset S_m$, and the previous proposition gives isomorphisms of the representations.
+
+  We will show that $\SH'' = T_{i_j}\SH'T_{i_j}^{-1}$.
+  It suffices to show that $T_{i_j}T_wT_{i_j}^{-1} \in \SH''$ for $w$ a word generated by simple transpositions $s_{i_1},\dots,s_{i_{l}} \in S_m$.
+  First, note that $l(w) < l(s_{i_j}w)$, implying $T_{i_j}T_w = T_{s_{i_j}w}$ by lemma 1.12 in \cite{Mathas-book}.
+  Further, by the same lemma, we have
+  \begin{align*}
+    T_{s_{i_j}w}T_{i_j}^{-1} 
+    &= q^{-1}\prn{T_{s_{i_j}w}T_{i_j} + (1-q)T_{s_{i_j}w}}\\
+    &= q^{-1}\prn{T_{qs_{i_j}ws_{i_j}} + (q-1)T_{s_{i_j}w} + (1-q)T_{s_{i_j}w}}\\
+    &= T_{s_{i_j}ws_{i_j}}
+  \end{align*}
+  which is in $\SH''$.
+\end{proof}
 \begin{figure}[h]
@@
 \begin{align*} 
-  \pi_{3,3}^1 = \pi_{3,4}^0 &=  
+  \iota_{3,3}^1 = \iota_{3,4}^0 &=  
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{3,5}^1 = \pi_{3,6}^0&=  
+\iota_{3,5}^1 = \iota_{3,6}^0&=  
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{3,6}^4&=  
+\iota_{3,6}^4&=  
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{3,7}^3&=  
+\iota_{3,7}^3&=  
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{3,7}^1&=  
+\iota_{3,7}^1&=  
 \begin{bmatrix}
@@
 \end{align*}
-\caption{The maps of representations $\pi_{e,2n+r}^r:M_{2n + r}^r \twoheadrightarrow U_{2n+r}^r$ for $e = 3$.}
+\caption{The maps of representations $\iota_{e,2n+r}^r:U_{2n +r}^r \hookrightarrow M_{2n + r}^r$ for $e = 3$.}
 \label{Composition series e=3}
@@
 \begin{align*}
-  \pi_{4,4}^2&=  
+  \iota_{4,4}^2&=  
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{4,4}^1&=  
+\iota_{4,4}^1&=  
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{4,6}^2 &=
+\iota_{4,6}^2 &=
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{4,6}^0 &=
+\iota_{4,6}^0 &=
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{4,7}^1 &=
+\iota_{4,7}^1 &=
 \begin{bmatrix}
@@
 \end{align*}
-\caption{The maps of representations $\pi_{e,2n+r}^r:M_{2n + r}^r \twoheadrightarrow U_{2n+r}^r$ for $e = 4$.}
+\caption{The maps of representations $\iota_{e,2n+r}^r:U_{2n +r}^r \hookrightarrow M_{2n + r}^r$ for $e = 4$.}
 \label{Composition series e=4}
@@
 \begin{align*}
-  \pi_{5,5}^3 &=
+  \iota_{5,5}^3 &=
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{5,6}^2 &=
+\iota_{5,6}^2 &=
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{5,7}^3 &=
+\iota_{5,7}^3 &=
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{5,7}^1 &=
+\iota_{5,7}^1 &=
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{6,6}^4 &=
+\iota_{6,6}^4 &=
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{6,7}^3 &=
+\iota_{6,7}^3 &=
 \begin{bmatrix}
@@
 \end{bmatrix}^\intercal\\
-\pi_{6,7}^5 &=
+\iota_{6,7}^5 &=
 \begin{bmatrix}
@@
 \end{align*}
-\caption{The maps of representations $\pi_{e,2n+r}^r:M_{2n + r}^r \twoheadrightarrow U_{2n+r}^r$ for $e = 5,6$.}
+\caption{The maps of representations $\iota_{e,2n+r}^r:U_{2n +r}^r \hookrightarrow M_{2n + r}^r$ for $e = 5,6$.}
 \label{Composition series e=6}
@@
 
-\newpage
-\appendix
-\section{Compatibility of Representations with the Relations}
-In general, we define representations above for the free algebra on generators $\cbr{T_i}$.
-Recall that we may give a presentation of $\SH$ having generators $T_i$ and relations
-\begin{align}
-  (T_i - q)(T_i + 1) &= 0 \label{quadratic}\\
-  T_iT_{i+1}T_i &= T_{i+1}T_iT_{i+1} \label{braid1}\\ 
-  T_iT_j &= T_jT_i \hspace{40pt} \abs{i - j} > 1. \label{braid2}
-\end{align}
-We call \eqref{quadratic} the \emph{quadratic relation} and \eqref{braid1}, \eqref{braid2} the \emph{braid relations}.
-It is easily seen that a representation of $\SH$ is equivalent to a representation of the free algebra $k\langle T_i \rangle$ which acts as 0 on the relations (henceforth referred to as \emph{compatibility} with the relations).
-We will prove in the following sections that $V$ and $W$ are compatible with the Hecke algebra relations.
-
-\subsection{Explicit Definition of $M$}
-We will give a more careful definition of the crossingless matchings representation here.
-\begin{definition}
-  A \emph{crossingless matching on $2n+r$ indices with $r$ anchors} is a partition of $\cbr{1,\dots,2n+r}$ into $n$ parts of size $2$ and $r$ of size 1 such that no two parts $(a,a')$ and $(b,b')$ satisfy $a < b < a' < b'$, and no parts $(c), (a,a')$ satisfy $a < c < a'$.
-  We will call these arcs and anchors, respectively.
-  Then, define $M^r_{2n+r}$ to be the $k$-vector space with basis the set of crossingless matchings on $2n+r$ indices with $r$ anchors.
-
-  In order to endow $M^r_{2n + r}$ with an $\SH$-action, consider some basis element $w_j$ and some element $(1 + T_i)$ of $\SH$.
-  The elements $\cbr{1} \cup \cbr{1 + T_i | 1 \leq i < 2n + r}$ generate $\SH$, so it is sufficient to define the action of $1 + T_i$ on $w_j$.
-
-  If $w_j$ has arc $(i,i+1)$, define $(1 + T_i)w_j := (1 + q)w_j$.
-  If $w_j$ has anchors $W(i) = i$ and $W(i+1) = i+1$, define $(1 + T_i)w_j := 0$.
-  If $w_j$ has anchor $W(i) = i$ and arc $W(i+1) = b$, define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$, $w_l(b) = b$, and all other arcs agree with $w_j$.
-  If $w_j$ has arcs $W(i) = a$ and $W(i+1) = b$, then define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$,$w(a) = b$, and all other acts agree with $w_j$. 
-  We verify that this is well-defined in Section \ref{Cross Relations}.
-\end{definition}
-
-We may alternately sharpen our topological definition;
-\begin{definition}
-Fix $2n + r$ distinct points $a_1,\dots,a_{2n + r}$ points along $\RR \times \cbr{0} \subset \RR^2$ and $r$ distinct points $b_1,\dots,b_r$ along $\RR \times \cbr{1}$.
-Then, define $M_{2n + r}^r$ to have basis given by the isotopy classes of $n + r$ paths connecting the points $a_1,\dots,a_{2n+r},b_1,\dots,b_r$ such that no distinct $b_i,b_j$ are connected by a path.
-
-We will take some basis element $w_j \in M_{2n +r}^r$ and define the action $(1 + T_i)w_j$.
-To do so, map $w_j$ through the natural embedding $\RR \times \brk{0,1} \hookrightarrow \RR \times \brk{\frac{1}{2},1}$, and form the figure $w_j^i$ by adjoining the lines connecting $a_l$ and $a_l + \prn{0,\frac{1}{2}}$ for all $l \neq i,i+1$ as well as paths from $a_i$ to $a_{i+1}$ and $a_i + \prn{0,\frac{1}{2}}$ to $a_{i+1} + \prn{0,\frac{1}{2}}$.
-This has either 0 or 1 path components which do not intersect $\RR \times \cbr{0,1}$;
-these form ``loops.''
-
-Take the figure $\tilde w_j^i$ without this component.
-If $\tilde w_j^i$ is not isotopic to some $w_l$, then define $(1 + T_i)w_j := 0$.
-If $\tilde w_j^i$ is isotopic to some $w_l$, define $(1 + T_i)w_j := (1 + q)w_l$ if $w_j^i$ has a loop and $(1 + T_i)w_j := q^{1/2}w_l$ otherwise.
-This process is illustrated in Figure \ref{Action}.
-\end{definition}
-
-Let the length of an arc $(i,j)$ be $l(i,j) := j - i + 1$.
-Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
-  This basis is illustrated for $M_{5}^1$ in Figure \ref{S5 Basis}.
+\section{Data}\label{Empirics Section}
+In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representations.\cite{Github}
 
 \begin{remark}
-  This definition gives a graphical calculus for working with our module.
-  It should be clear that, if $w_j^i$ has a loop then $w_l(i) = i+1$ and $w_l = w_j$.
-  Further, this easily defines an arbitrary composition:
-  \[
-    (1 + T_{i_1})\cdots(1 + T_{i_\ell})w_j = q^{(\ell - t)\frac{1}{2}}(1 + q)^tw_l
-  \]
-  if the figure we make via $(1+T_{i_1})\cdots(1+T_{i_\ell})$ is isotopic to $w_l$ after removing $t$ loops.
+  These results are restricted by two things; first and with less recourse, this was computed in Magma, a closed source language with bugs that could not be resolved in certain cases.
+  Second, the memory necessary to store the Hecke algebra via basis elements and structure constants grows with $(n!)^3$;
+  this is prohibitively large when $m > 7$.
+  An implementation as a quotient by a free algebra or only specifying multiplication by generators may fix this, however, this is not possible with the Magma language, and the closed source renders modification of the language impossible.
 \end{remark}
 
-  Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
-  call this the \emph{increasing lexicographical order basis}.
-  Further, we have a surjection $M_{2n + 2r}^0 \twoheadrightarrow M_{2n + r}^r$ which takes basis elements to basis elements;
-  this induces an order on the basis for $M_{2n +r}^r$, which we will henceforth refer to as the \emph{induced lexicographical order basis.}
-  This basis is illustrated for $M_{5}^1$ in Figure \ref{S5 Basis}.
-
-\subsection{Verifying the Crossingless Matchings Representations}
-\label{Cross Relations}
-Take some basis vector $w_i$.
-We will first check \eqref{quadratic} by case work:
-\begin{itemize}
-  \item Suppose there is an arc $(i,i+1)$.
-    Then, $(T_i-q)(T_i + 1)w = (1 + q)\brk{(1 + T_i)w - (1 + q)w} = 0$, giving \eqref{quadratic}.
-
-  \item Suppose there is no arc $(i,i+1)$ and $i,i+1$ do not both have anchors;
-    then $(T_i +  1)w = q^{1/2}w''$ for some basis vector $w'$ having arc $(i,i+1)$, and the computation follows as above for \eqref{quadratic}.
-  \item Suppose $i,i+1$ are anchrors;
-    then $(T_i + 1)w = 0$, giving \eqref{quadratic}.
-\end{itemize}
-
-\vspace{5pt}
-Now we verify \eqref{braid1}.
-Let $h := (1 + T_i)(1 + T_{i+1})(1+T_i)$, and let $g := (1 + T_{i+1})(1 + T_i)(1 + T_{i+1})$.
-Note the following expansion:  
-  \begin{align*}
-      hw
-      &= 1 + 2T_i + T_i^2 + T_{i+1} + T_iT_{i+1} + T_{i+1}T_i + T_iT_{i+1}T_i\\
-      &= 1 + (1+q)T_i + T_{i+1} + T_iT_{i+1} + T_{i+1}T_i + T_iT_{i+1}T_i.
-    \end{align*}
-    An analogous formula gives an analogous equality in $g$.
-    Hence we have
-    \[
-      (h-g)w = q(T_i - T_{i+1}) + T_iT_{i+1}T_i - T_{i+1}T_iT_{i+1}.
-    \]
-    Hence we may equivalently check that $(h-g)w = q(T_i - T_{i+1})$.
-    In fact, $hw = q(1 + T_i)$ and $gw = q(1 + T_j)$ by Figure \ref{braid1arc}, giving compatibiliy.
-    \begin{figure}
-\[
-  \begin{gathered}\EmptyNAction{3}{1/1,2/2,1/3}\end{gathered}
-  \longsquigrightarrow
-  \begin{gathered}\EmptyNAction{3}{1/2}\end{gathered}
-  \hspace{50pt}
-  \begin{gathered}\EmptyNAction{3}{2/1,1/2,2/3}\end{gathered}
-  \longsquigrightarrow
-  \begin{gathered}\EmptyNAction{3}{2/1}\end{gathered}
-  \hspace{50pt}
-  \begin{gathered}\EmptyNAction{4}{1/1,3/2}\end{gathered}
-  \longsquigrightarrow
-  \begin{gathered}\EmptyNAction{4}{3/1,1/2}\end{gathered}
-\]
-  \caption{
-    The following give visual intuition for isotopy between $(1 + T_i)(1 + T_{i-1})(1 + T_i)w_j$ and $q(1 + T_i)$,between $(1 + T_{i+1})(1 + T_i)(1 + T_{i+1})w_j$ and $q(1 + T_i)$, and between $(1 + T_i)(1+T_j)w_l$ and $(1 + T_j)(1 + T_i)w_l$.
-    In all cases, these isotopies imply equality between the elements listed.
-  }
-  \label{braid1arc}
-\end{figure}
-
-Lastly, we have the equation
-\[
-  (1 + T_i)(1 + T_j) - (1 + T_j)(1 + T_i) = T_iT_j - T_jT_i
-\]
-and hence we simply need to verify that $(1 + T_i)$ and $(1 + T_j)$ commute, as shown in Figure \ref{braid1arc}
-
-\subsection{Verifying the Fibonacci Representations} 
-\label{Fib Relations}
-Similar to before, the reader may verify that \eqref{braid2} follows easily, and the others may be verified on strings of length 3 and 4.
-By considering the coefficients in order of \eqref{Fib Action}, the quadratic relation \eqref{quadratic} gives the following quadratics:
-\begin{equation}
-  \begin{split}
-    (\vara - q)(\vara + 1) &= 0\\
-    (\varb - q)(\varb + 1) &= 0\\
-    \varc\vard + \vard\vare &= (q-1)\vard\\
-    \varc^2 + \vard^2 &= (q -1)\varc + q\\
-    \vare^2 + \vard^2 &= (q -1)\vare + q
-  \end{split}
-\end{equation}
-The first two of these are easily verified for any $q$.
-Since $\vard \neq 0$, the third is equivalently given by
-\[
-  (q - 1) = \varc + \vare = t(q\tau - 1 + q - \tau) = (\tau^2 + \tau)(q - 1)
-\]
-or that $\prn{\tau^2 + \tau - 1}(q-1) = 0$.
-One may verify that \[\tau^2 + \tau - 1 = q^6 + 2q^5 + q^4 + q^3 + q^2 - 1 = (-1+q+q^2)\brk{5}_q = 0.\]
-
-The fourth is given by the quadratic
-\[
-  \tau^2\brk{(q\tau-1)^2 - \tau(q+1)} = \tau(q-1)(q\tau - 1) + q
-\]
-or equivalently,
-\[
-  (\tau^2 + \tau - 1)\brk{q\prn{qt^2 + 1} + t} = 0
-\]
-which is true for every $q$.
-
-The fifth is similarly given by
-\[
-  (\tau^2 + \tau - 1)\brk{q\prn{qt + 1} + t^2} = 0 
-\]
-which is true for every $q$.
-
-\vspace{7pt}
-We now verify \eqref{braid1}.
-We may order the basis for $V^4$ as follows:
-\[
-  \cbr{(\vp\vp\vp\vp),(\vs\vp\vp\vs),(\vp\vp\vp\vs),(\vs\vp\vp\vp),(\vs\vp\vs\vp),(\vp\vs\vp\vs),(\vp\vp\vs\vp),(\vp\vs\vp\vp)}.
-\]
-Then, in verifying the braid relation \eqref{braid1} in this order, we encounter the following quadratics (with tautologies and repetitions omitted):
-\begin{align*}
-    \vara\vare^2 + \varb\vard^2 &= \vara^2 \vare\\
-    \vara\vard\vare + \varb\varc\vard &= \vara\varb\vard\\
-    \varb\varc^2 + \vara\vard^2 &= \varb^2\varc\\
-    \vara\varc^2 + \vard^2\vare &= \vara^2\varc\\
-    \vard\vare^2 + \vara\varc\vard &= \vara\vard\vare
-\end{align*}
-Substituting in $\tau$ and dividing by $\delta$ whenever possible, these are equivalent to the vanishing of the following polynomials in $q$:
-\begin{align*}
-  -q (1 + q) (1 + q^2 + q^3) (2 + q + 3 q^2 + 2 q^3) \brk{5}_q &= 0\\
-  (1 + 2 q + q^3 + q^4) \brk{5}_q &= 0\\
-  (1+q)^2 (1+q^2+q^3) (1+3q^3 - q^4 + q^6)\brk{5}_q &= 0\\
-  (1+q)^2 (1+q^2+q^3) (1+5q+5q^2+3q^3+3q^4+3q^5+q^6)\brk{5}_q &= 0\\
-  (1+q) (1+q^2+q^3) (-1+2q+q^2+q^3+q^4)\brk{5}_q &= 0.
-\end{align*}
-Notably, each of these vanish when $e = 5$.
-
-\section{Conjugate Subalgebras}\label{Algebra}
-Throughout the text, for some representation $V$, we refer to $\Res_{\SH(S_{l})}^{\SH(S_m)} V$ without specifying exactly which subalgebra $\SH(S_{l})$.
-\begin{proposition}
-  Suppose $B,B'$ are subalgebras of the $k$-algebra $A$ with $B = uB'u^{-1}$, and let $V$ be a representation of $A$.
-  Then, the linear isomorphism $V \xrightarrow{\phi} V$ given by $v \mapsto uv$ causes the following to commute for any $b \in B$:
-  \[
-    \begin{tikzcd}
-      V \arrow[r,"\phi"] \arrow[d,"b"] & V \arrow[d,"ubu^{-1}"]\\
-      V \arrow[r,"\phi"] & V
-    \end{tikzcd}
-  \]
-  Hence, through the identification of $B$ and $B'$ via conjugation, we have $\Res_{B}^A V \simeq \Res_{B'}^A V$
-\end{proposition}
-\begin{proof}
-  This is simply given by $(ubu^{-1})uv = ubv$.
-\end{proof}
-
-\begin{corollary}
-  Suppose $\SH',\SH''$ are two subalgebras of $\SH(S_m)$ generated by $l$ reflections and $V$ is a representation of $\SH$.
-  Then, $\Res_{\SH'}^{\SH} V \simeq \Res_{\SH''}^\SH V$.
-\end{corollary}
-\begin{proof}
-  Let $\SH'$ and $\SH''$ be the subalgebras of $\SH(S_m)$ generated by the reflections $\cbr{T_{i_1},\dots,T_{i_l}}$ and $\cbr{T_{i_1},\dots,T_{i_{j-1}},T_{i_j + 1},T_{i_{j+1}},\dots,T_{i_l}}$ for $1 \leq i_1 < \dots < i_{j-1} < i_j + 1 < i_{j+1} < \dots < i_l \leq n$.
-  It is sufficient to prove that $\SH'$ and $\SH''$ are conjugate;
-  then transitivity gives conjugacy of any $S_l \subset S_m$, and the previous proposition gives isomorphisms of the representations.
-
-  In fact, the reader can verify that $\SH'' = T_{i_j}\SH'T_{i_j}^{-1}$.
-\end{proof}
+We give in Figure \ref{Fib Data} some isomorphisms between $M/K$ and $V$ for $e \geq n + r + 1$ with $p = \infty$;
+all but one of these are cases with $e > n + r + 1$, so $K=0$ and this is an isomorphism with our crossingless matchings representation.
+The case $n = 1$, $r = 3$ gives an example of an isomorphism not proven in general, but proven via our computation.
+All of these computations are done for $q$ a primitive 5th root of unity in the algebraic extension of the Cyclotomic field $\QQ(\zeta_{10})$ by a root of the polynomial $x^2 - \tau$.
+
+We give in Figure \ref{Empirical Kernel} some data supporting a conjecture concerning sign subrepresentations of $M_{2n + r}^r$.
+The computations to support this were done over $\CC$ with $q$ a primitive 5th root of unity.
+
+It is known that, for small $2n + r$, each Specht module $S^{(n+r,n)}$ has a composition series of length 2.\cite{Mathas-book}
+We give in Figures \ref{Composition series e=3} through \ref{Composition series e=6} the map $\iota_{e,2n+r}^r:U_{2n + r}^r \hookrightarrow M_{2n + r}^r \twoheadrightarrow U_{2n + r}^r$, which conjecturally illustrates the inclusion of the first composition factor of $S^{(n+r,n)}$ into $S^{(n+r,n)}$ for all $2n + r \leq 7$.
 

### 2019-07-30 tex/Drafts/Draft-2.tex
incorporated kernel stuff

@@
 
-\begin{lemma}\label{Trivial}
+We give two proofs of the following proposition.
+The first, below, intuits the necessary graphical intuition to construct a sub-matrix with nonzero determinant and perform row reduction.
+The second, given in section \ref{kernel}, formalizes the graphical intuition and gives results necessary for the following sections.
+
+\begin{proposition}\label{Trivial}
   Suppose $e \nmid n + r + 1$.
   Then, $K := K_{2n + r}^r = 0$.
-\end{lemma}
+\end{proposition}
 \begin{proof}[Proof 1.]
   Consider the matrix $A = \bigoplus (1 + T_i)$ having kernel $K$.
-  It is sufficient by lemma \ref{Represented} to show that $A$ includes a row $[0,\dots,0,1,0,\dots,0]$ with a nonzero entry only on the row $j$.
+  It is sufficient by lemma \ref{rainbow nonzero} to show that $A$ includes a row $[0,\dots,0,1,0,\dots,0]$ with a nonzero entry only on the row $j$.
 
@@
   Take an arbitrary vector $w \in M$.
-  By Lemma \ref{Trivial} there exists some $(1 + T_i) \in \SH$ such that $(1 + T_i)w \neq 0$.
+  By Proposition \ref{Trivial} there exists some $(1 + T_i) \in \SH$ such that $(1 + T_i)w \neq 0$.
   Note that \[\ima (1 + T_i) = \Span\cbr{w_j \mid w_j \text{ contains the arc }(i,i+1)}.\]
@@
 \subsection{Kernels and further work}
-\begin{proposition}\label{Represented}
-	Let $w$ be an arbitrary vector in $W_{2n+r}^r$. I claim that if $w\in \cap\text{ker}(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero.
+
+In this section, we characterize $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$ for $e \nmid n + r + 1$ and for $e=n+r+1$.
+When the representation is clear, we will simply denote this kernel as $K$ or $\cap\text{ker}(1+T_i)$.
+For compactness, in this section we use $\sim $ to denote "proportional to".
+For convenience, define $M_0^0$ to be the zero representation.
+
+\subsubsection{Proposition \ref{Trivial}}
+\label{kernel}
+\begin{definition}
+
+	Fix some basis element $\psi\in M_{2n+r}^r$.
+For $1 \leq a,b \leq 2n + r$ define $\psi(a):=b$ iff $a$ and $b$ are matched in $\psi$, $\psi(a):=a$ if $a$ is an anchor in $\psi$.
+Given that $\psi$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $\psi(a,b)$ of $\psi$ to be the basis element $\sigma\in M_{b-a+1}^{r'}$ specified by $\sigma(i)=\psi(i+a-1)-a+1$.
+This sub-matching is defined for $a<b$ when $\psi(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$.
+See \ref{sub-matching example}.
+
+	If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, $\psi(a,b)$ will always refer to those nodes and they're matchings, though it may not be a sub-matching unless specified.
+For any other $a,b$, we define $\psi(a,b)$ to be an element of the representation with no nodes.
+
+	\label{sub-matchings}
+\end{definition}
+
+\begin{figure} 
+	\def\cbasisspacing{5mm}
+	$\cbr{
+		\begin{gathered}
+		\Matching{6}{1/2, 3/6, 4/5}, \hspace{\cbasisspacing}
+		\Matching{4}{1/4, 2/3}
+		\end{gathered}}$
+	\caption{$\psi\in M_6^0$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right. $\psi(3,6)=\sigma$. $\psi(2,5)$ is not a sub-matching.}
+	\label{sub-matching example}
+\end{figure}
+
+Define the rainbow element $R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$.
+In other words, the basis element with all anchors to the left then a rainbow.
+
+\begin{proposition}
+	Let $w$ be an arbitrary vector in $M_{2n+r}^r$. I claim that if $w\in \cap\text{ker}(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero.
+
+	\label{rainbow nonzero}
 \end{proposition}
+
 \begin{proof}
 	Let $Y$ be the set of basis elements with nonzero coordinate in $w$.
-Let $k$ be the greatest integer such that there exists $y\in Y$ where $y(1)=...=y(k)=0$ {\color{magenta} should this be $y(1)-1 = \dots = y(k) - k = 0$?
-Also, we should avoid using $k$ as an integer, as it's used elsewhere as a field.}, and let $U\subset Y$ be the set of such $y$.
+Let $z$ be the greatest integer such that there exists $y\in Y$ where $y(1)-1=...=y(z)-z=0$, and let $U\subset Y$ be the set of such $y$.
 In other words, $U$ is the set of basis elements in $Y$ which have the most anchors to the far left.
 
-	Suppose $k<r$.
-Then for each $y\in U$ there exists a minimal $i_y>k+2$ such that $y(i_y)=0$.
+	Suppose $z<r$.
+Then for each $y\in U$ there exists a minimal $i_y>z+2$ such that $y(i_y)=0$.
 In other words, $i_y$ is the position of the next leftmost anchor in $y$.
@@
 Then I claim the basis element $y':=q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}$ has nonzero coordinate in $(1+T_{i_{\tilde{y}}-1})w$, implying $w\not\in \cap\text{ker}(1+T_i)$.
-To see this, we can show that $\tilde{y}$ is the only element in $Y$ such that $q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$.
-$y'$ still has $k$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$.
-If $x\in Y,\not\in U$, the basis element proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$.
-If $x\in U$ the basis element proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$.
-Since this is the only match altered by action $(1+T_{i_{\tilde{y}}-1})$ on $x$, if $(1+T_{i_{\tilde{y}}-1})x\sim y'$ this implies $x=\tilde{y}$.
-So if $k<r$ $w$ is not in the desired kernel.
-
-	Suppose $k=r$ but $R\not\in U$ (so $R\not\in Y$).
+To see this, we can show that $\tilde{y}$ is the only basis element in $Y$ such that $(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$.
+$y'$ still has $z$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$.
+If $x\in Y,\not\in U$, the basis element $x'$ proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$.
+If $x\in U$, $x'$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$.
+Since this is the only match altered by action of $(1+T_{i_{\tilde{y}}-1})$ on $x$, if $(1+T_{i_{\tilde{y}}-1})x\sim y'$ this implies $x=\tilde{y}$.
+So if $z<r$ $w$ is not in the desired kernel.
+
+	Suppose $z=r$ but $R\not\in U$ (so $R\not\in Y$).
 Let us define a sequence of subsets of $U$ in the following way: $U_0:=U$, $U_{i+1}:=\{u\in U_i| u(r+i+1)=2n+2r-i+1 \}$.
@@
 I claim that $\tilde{u}$ is the only element in $Y$ such that $(1+T_{\tilde{u}(r+t+1)})\tilde{u}\sim u'$, again implying that $w$ is not in the desired kernel.
-$u'$ still has $k$ anchors on the left, $u'(r+i)=2n+2r-i+2$, $1\leq i\leq t$, and $u'(r+t+1)>\tilde{u}(r+t+1)$, so $u'\not\in Y$.
+$u'$ still has $r$ anchors on the left, $u'(r+i)=2n+2r-i+2$, $1\leq i\leq t$, and $u'(r+t+1)>\tilde{u}(r+t+1)$, so $u'\not\in Y$.
 If $x\in Y,\not\in U$,  the basis element $x'$ proportional to $(1+T_{\tilde{u}(r+t+1)})x$ will have $r$ leftmost anchors only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
-Similarly, if $x\in U,\not\in U_t$, the basis element $x'$ will have the property $x'(r+t)=2n+2r-t+2$ only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
+Similarly, if $x\in U,\not\in U_t$, the basis element $x'$ will have the property $x'(r+i)=2n+2r-i+2$ for all $i\leq t$ only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
 If $x\in U_t$, $x'(r+t+1)=u'(r+t+1)$ if and only if $x(r+t+1)=\tilde{u}(r+t+1)$ and $x(x(r+t+1)+1)=\tilde{u}(\tilde{u}(r+t+1)+1)$ (since $u'\not \in Y$).
 These are the only matches altered by the action $(1+T_{\tilde{u}(r+t+1)})$, so this implies $x=\tilde{u}$.
-Thus we have proved that if $R\not\in Y$, $w$ is not in the desired kernel.
-\end{proof}
-
-{\color{orange} Necessary characterization of the Kernel goes here.}
+Thus we have proved that if $R\not\in Y$, $w$ is not in the kernel.
+
+\end{proof}
+
+Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively.
+Examples are pictured in \ref{shifted rainbow}.
+Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.
+
+\begin{figure}
+	\def\cbasisspacing{5mm}
+	$\cbr{
+		\begin{gathered}
+		\Matching{8}{1/8, 2/7, 3/6, 4/5}, \hspace{\cbasisspacing}
+		\Matching{8}{1/8, 2/7, 3/4, 5/6}, \hspace{\cbasisspacing}
+		\Matching{8}{1/8, 2/3, 4/7, 5/6}, \hspace{\cbasisspacing}
+		\Matching{8}{1/2,3/8,4/7,5/6}
+		\end{gathered}}$
+	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right}
+	\label{shifted rainbow}
+\end{figure}
+
+Define $Q_n:=(q^n+...+1)/q^{n/2}(-1)^n$ for $n\in \{0,1,...\}$.
+The following proposition says that, for any element in the kernel, if some basis element $y$ has coordinate $c$ in that element, and if $y$ has a rainbow sub-matching, the basis elements where you replace that sub-matching by the shifted rainbow matchings $R_{L,i}$ or $R_{R,i}$ both have coordinate $Q_ic$ in the kernel element.
 
 \begin{proposition}
-  Suppose $e = n + r + 1$.
-  Then $K$ is nontrivial.
+	Let $w$ be an element in the kernel intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation.
+Let $y$ be a basis element with coordinate $c$ in $w$.
+Suppose $\exists a,b$ such that $y(a,b)=R$, the rainbow element.
+Define the basis elements $\theta_i,\phi_i$ by $\theta_i(1,a-1)=\phi(1,a-1)=y(1,a-1)$, $\theta_i(b+1,2n)=\phi(b+1,2n)=y(b+1,2n)$, $\theta_i(a,b)=R_{R,i}$, $\phi_i(a,b)=R_{L,i}$ (leave $\theta_i$ or $\phi_i$ undefined for any $i$ where $R_{R,i},R_{L,i}$ are undefined, respectively).
+The coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.
+
+	\label{shifted rainbow coeffs}
 \end{proposition}
+
+Proof of this proposition requires a simple algebraic fact that will be used throughout this document, so I state it as a lemma.
+
+\begin{lemma}
+	$Q_1Q_n-Q_{n-1}=Q_{n+1}$
+
+	\label{Q alg}
+\end{lemma}
+
+\textit{Proof of lemma.}
+
+\begin{align*}
+Q_1Q_n-Q_{n-1}=&\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}\\
+=&\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}\\
+=&\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}
+\end{align*}
+
+Now let us prove the proposition.
+
+\begin{proof}
+	Consider acting on $w$ by an element $(1+T_z)$.
+The coordinate of $\phi_i$ in $(1+T_z)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_z)$.
+Specifically, it will be $(1+q)c\iota+(q^1/2)\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.
+
+	Let $n:=a+b-1$ and $r$ be the number of anchors in $y(a,b)$.
+Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$.
+This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in \ref{shifted relations}.
+I claim the following:
+
+	\begin{center}
+		\textit{claim}:
+		The only basis elements $\psi$ where $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist\footnote{we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$}.
+
+	\end{center}
+
+	Note that the action of any $(1+T_z)$ on a basis element $\psi$ creates exactly two lines: an arc of length two connecting $z$ and $z+1$, and either an anchor or an arc of length $\geq 2$ connecting $\psi(z)$ and $\psi(z+1)$.\footnote{Although this fact follows directly from our definition of the representation, it will be used throughout the document, so it is important that the reader understands it.\label{two humps created}} The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.
+
+	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in \ref{shifted relations}.
+Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition.
+Me note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
+Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$.
+If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\psi(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor.
+All other matchings remain unchanged, so this implies $\psi=\phi_{i+1}$.
+Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\psi=\phi_{i-1}$.
+For boundary cases, note that for $\phi_0=\theta_0$, the only other basis element sent to this by the middle transposition is $\phi_1=\theta_1$.
+Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case gives no new information.
+Lastly, note that our argument was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors.
+Thus the claim is proved.
+
+	Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction:
+
+	Acting by $(1+T_{a-1+r+n/2})$ on $w$, the new coordinate of $\phi_0=y$ is $(q+1)c+q^{1/2}c_{\phi_1}$ where $c_{\phi_1}$ is the coordinate of $\phi_1$ in $w$.
+Since $w$ is in the kernel, we have $(q+1)c+q^{1/2}c_{\phi_1}=0=>c_{\phi_1}=Q_1c$.
+$\phi_1=\theta_1$ so this gives us all our base cases.
+
+	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$.
+By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_i=0$ so $c_{\phi_{i+1}}=Q_1Q_i-Q_{i-1}=Q_{i+1}$ by lemma \ref{Q alg}.
+$\theta_i$ is an identical proof, so the proposition follows.
+
+	\begin{figure}
+		\[
+		\GeneralizedAction{8}{3/4,5/8,6/7}{2}{1/1,2/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{(1+q)}
+		\]
+		\[
+		\GeneralizedAction{8}{2/3,5/8,6/7}{2}{1/1,4/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
+		\]
+		\[
+		\GeneralizedAction{8}{3/8,4/5,6/7}{2}{1/1,2/2}{1.25}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
+		\]
+		\caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $M_{8}^2$ and $i=2$.}
+		\label{shifted relations}
+	\end{figure}
+\end{proof}
+
+We are now ready to prove proposition \ref{Trivial}.
+
+\begin{proof}
+	Suppose $\cap\text{ker}(1+T_i)=K\not=0$.
+Take nonzero $w\in K$.
+By Proposition \ref{rainbow nonzero}, the coordinate of the rainbow vector $R$ is nonzero; suppose the coordinate is $c$.
+By proposition \ref{shifted rainbow coeffs}, the coordinates of the basis elements $R_{L,n+r-1}$ and $R_{L,n+r-2}$ are $Q_{n+r-1}c$ and $Q_{n+r-2}c$ respectively.
+
+	Consider the coordinate of $R_{L,n+r-1}$ in $(1+T_1)w$.
+Using the same logic as in the proof of proposition \ref{shifted rainbow coeffs}, we note that if a basis element $\psi$ has no anchor at position $3$ and is not equal to $R_{L,n+r-2}$, $(1+T_1)\psi\not\sim R_{L,n+r-1}$.
+Thus the desired coordinate is equal to $(1+q)Q_{n+r-1}c+q^{1/2}Q_{n+r-2}c=-q^{1/2}Q_{n+r}c$ by lemma \ref{Q alg}.
+Since $w\in K$, we must have $-q^{1/2}Q_{n+r}c=0$.
+Me have that $c$ is nonzero, and we assume $q$ nonzero, and $Q_{n+r}$ is zero iff $q$ is a root of $q^{n+r}+...+1$, implying $e|n+r+1$.
+Thus we have arrived at contradiction, and $K=0$.
+\end{proof}
+
+\subsubsection{Kernel Basis}
+
+In this section, we determine an explicit basis for $K$ when $e=n+r+1$, assuming $K\not=0$. In the next section, we prove $K\not=0$.
+
+First let us formalize a useful property of sub-matchings.
+
+\begin{definition}
+	Given a basis element $\psi\in M_{2n+r}^r$, specify some sub-matching $\psi(a,b)$.
+Let $\Res_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}M_{2n+r}^r$ be the restriction to the sub-algebra generated by transpositions $T_a,...,T_{b-1}$.
+Define $Y_\psi\subset\Res_{\SH_{b-a+1}(q)}^{\SH_{2n+r}(q)}M_{2n+r}^r$ to be the subrepresentation generated by the set of basis elements $\{\sigma| \sigma(1,a-1)=\psi(1,a-1),\ \sigma(b+1,2n+r)=\psi(b+1,2n+r)\}$.
+\end{definition}
+
+\begin{lemma}
+	Take a basis element $\psi\in M_{2n+r}^r$. Suppose $\psi$ has some sub-matching $\psi(a,b)$ with $r'$ anchors. Define $Y_\psi$ with respect to this sub-matching.
+
+	The map $\rho:Y_\psi\rightarrow M_{b-a+1}^{r'}$ defined by $$\rho(\sigma)=\sigma(a,b)$$ is an isomorphism of representations.
+
+	\label{sub-matching isomorphism}
+\end{lemma}
+
+\begin{proof}
+
+	The map is clearly bijective. Thus it is sufficient to prove the following: $$\rho(T_{i+a-1}\sigma)=T_i\rho(\sigma)$$
+
+	As mentioned in the previous section, the action of a transposition $T_i$ can change at most 4 nodes, so we need to show that the transpositions end up changing the same nodes in the same way in  $\rho(T_{i+a-1}\sigma)$ and $T_i\rho(\sigma)$.
+
+	Suppose $\sigma(i+a-1)=s,\sigma(i+a)=t$.
+Then $(T_{i+a-1}\sigma)(i+a-1)=i+a$, $(T_{i+a-1}\sigma)(s)=t$, so $\rho(T_{i+a-1}\sigma)(i)=i+1$, $\rho(T_{i+a-1}\sigma)(s-a+1)=t-a+1$.
+Separately, $\rho(\sigma)(i)=s-a+1$ and $\rho(\sigma)(i+1)=t-a+1$, so $T_i\rho(\sigma)(i)=i+1$ and $T_i\rho(\sigma)(s-a+1)=t-a+1$ as desired.
+So the map is an isomorphism and the lemma is proved.
+\end{proof}
+
+\vspace{5mm}
+The lemma above motivates a recursive characterization of the kernel. To do this, it will be convenient to define some notation.
+
+\begin{definition}
+	Recall $Q_i:=(q^i+...+q+1)/q^{i/2}(-1)^i$ (lemma \ref{Q alg}). For $a>0$ define $Q(0,b):=1$. For $b>a>0$ define $$\Q_b^a:=\frac{Q_{b-1}...Q_{b-a}}{Q_1...Q_{a-1}}$$
+
+\end{definition}
+
+\begin{definition}
+	For $\psi \in M_0^0$, define the function $x_\psi(q):=1$.
+
+	For all other basis elements $\psi\in M_{2n+r}^r$, we define $x_\psi$ recursively:
+
+	$$x_\psi(q):=x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}$$
+
+	I will refer to $x_\psi$ as the \textbf{coordinate function} of $\psi$.
+
+	\label{coeff def}
+\end{definition}
+
+\vspace{2mm}
+The following proposition states the forward direction of our characterization.
+\begin{proposition}
+
+	Let $M_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$.
+Let $w\in\cap\text{ker}(1+T_i)$.
+MLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition \ref{rainbow nonzero}).
+Then the coordinate of any basis element $\psi\in M_{2n+r}^r$ in $w$ is $x_{\psi}(q)$.
+
+	\label{kernel characterization}
+
+\end{proposition}
+
+An illustration of this proposition is shown in figure \ref{coeff example}.
+
+\begin{figure}
+	\def\cbasisspacing{5mm}
+
+	$\cbr{
+		\begin{gathered}
+		\GeneralizedMatching{11}{1/6, 2/3,4/5,7/10,8/9}{1}{11/1}{11/8}, \hspace{\cbasisspacing}
+		\Matching{4}{1/2, 3/4}, 
+		\hspace{\cbasisspacing}
+		\GeneralizedMatching{5}{1/4, 2/3}{1}{5/1}{3/4}, \hspace{\cbasisspacing}
+		\end{gathered}}$ 
+	\caption{Suppose the second and third elements have coordinates $x_2(q_1)$ and $x_3(q_2)$ in their respective kernel elements, where for $q_1$, $e=3$ and for $q_2$ $e=4$.
+The coordinate of the first element is $x(q)=x_2(q)x_3(q)\frac{Q_5Q_4Q_3}{Q_1Q_2}$, where for $q$, $e=7$}
+	\label{coeff example}
+\end{figure}
+
+\begin{proof}
+	Suppose $\psi(1)=a$.
+The proof is structured as follows: use proposition \ref{shifted rainbow coeffs} to find the coefficient of the basis element with $\lfloor a/2\rfloor$ humps then a rainbow element; use the same proposition in a reversed manner to find the coefficient of the basis element consisting of the rainbow for the first $a$ nodes, then the rainbow for the final $2n+r-a$ nodes; finally, we finish the proof through induction using lemma \ref{sub-matching isomorphism}.
+
+	\vspace{2mm}
+	By proposition \ref{shifted rainbow coeffs} the element $R_1:=R_{L,n+r-1}$ has coordinate $Q_{n+r-1}$ in $w$.
+Then $R_1(3,2n+r)$ is the rainbow element in  $M_{2(n-1)+r}^r$, so the element $R_2$ defined by $R_2(1,2):=R_1(1,2)$, $R_2(3,2n+r):=R_{L,n+r-2}\in M_{2(n-1)+r}^r$ has coordinate $Q_{n-1}Q_{n-2}$.
+Generally, define $R_i$ by $R_i(1,2(i-1)):=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r):=R_{L,n+r-i}\in M_{2(n-i+1)+r}^r$.
+Then the coefficient of $R_i$ is $Q_{n+r-1}...Q_{n+r-i}$.
+These elements are shown in figure 5.
+
+	\begin{figure}
+		\def\cbasisspacing{5mm}
+
+		$\cbr{
+			\begin{gathered}
+			\GeneralizedMatching{8}{3/8, 4/7,5/6}{2}{1/1,2/2}{5/4}, \hspace{\cbasisspacing}
+			\GeneralizedMatching{8}{1/2, 5/8,6/7}{2}{3/1,4/2}{5/4}, 
+			\hspace{\cbasisspacing}
+			\GeneralizedMatching{8}{1/2, 3/4,7/8}{2}{5/1,6/2}{5/4}, \hspace{\cbasisspacing}
+			\end{gathered}}$ 
+		\caption{In order, the rainbow element, $R_1$, and $R_2$.
+The coordinate of the rainbow element is 1.
+The coordinate of $R_1$ is $Q_{4}$.
+The coordinate of $R_2$ is $Q_4Q_3$.
+Generally, $R_i$ is the element with $i$ humps then a rainbow element, and has coordinate $Q_{n+r-1}...Q_{n+r-i}$.}
+	\end{figure}
+
+	Now define basis elements $E_i$ by $E_i(2i+1,2n+r):=R_i(2i+1,2n+r)$, $E_i(1,2i):=R$, the appropriate rainbow element.
+By the same argument as above, if $E_i$ has coordinate $c$ in $w$, $R_i$ has coordinate $Q_{i-1}...Q_{1}c$.
+One way to make this more clear is to consider intermediate basis elements $\sigma_j^{E_i}$ defined by $\sigma_j^{E_i}(2i+1,2n+r):=E_i(2i+1,2n+r)$ and $\sigma_j^{E_i}(1,2i):=R_{L,j}$.
+Then the coordinates of $\sigma_j^{E_i}(2i+1,2n+r)$ in terms of the coordinate $c$ of $E_i$ are $Q_{i-1}...Q_{i-j}$, and $R_i=\sigma_{i-1}^{E_i}$.
+
+	Since we assume $Q_i\not=0$ for $i< n+r$, this implies the coefficient of $E_i$ is $\frac{Q_{n+r-1}...Q_{n+r-i}}{Q_1...Q_{i-1}}=\Q^i_{n+r}=x_{E_i}$.
+In particular, returning to our desired basis element $\psi$, the coordinate of $E_{\lfloor a/2\rfloor}$ is $\Q^{\lfloor a/2\rfloor}_{n+r}=x_{E_{\lfloor a/2\rfloor}}$.
+
+	Note that the above logic only uses proposition \ref{shifted rainbow coeffs}, which requires only that a sub-matching be a rainbow element.
+So, suppose some basis element $\sigma$ has sub-matching $\sigma(s,t)=R$ with $n'$ nodes and $r'$ anchors, and that the coordinate of $\sigma$ in $w$ is $c$.
+Then it follows that the basis element $\theta_i$ defined by $\theta_i(1,s-1):=\sigma(1,s-1)$, $\theta_i(t+1,2n+r):=\sigma(t+1,2n+r)$, and $\theta_i(s,t):=E_i$ has coefficient $\Q^i_{n'+r'}c$.
+In other words, defining $Y_\psi$ with respect to the sub-matching $\sigma(s,t)$, the operation of finding the coordinate of $E_i$ given the coordinate of $R=\sigma(s,t)$ commutes with the isomorphism to $Y_\psi$.
+An example is given in figure \ref{kernel induct characterization example}.
+
+	\vspace{2mm}
+	The above technique specifies an algorithm for determining the coordinate of $\psi$.
+
+	As a base case, for the zero element have the algorithm return 1.
+
+	Suppose inductively that the algorithm returns the coordinate for any $\sigma\in M_{2n'+r'}^{r'}$, $2n'+r'<2n+r$, and that that coordinate is equal to the coordinate function $x_\sigma$.
+Also suppose that the algorithm commutes with any isomorphism defined by lemma \ref{sub-matching isomorphism}.
+These statements are clearly true for the base case.
+
+	Given $\psi\in M_{2n+r}^r$, if $\psi(1)=a$, we may find the coordinate of $E_{\lfloor a/2\rfloor}$ as before.
+Note that this operation commutes with any isomorphism defined by lemma \ref{sub-matching isomorphism}.
+Me may define $Y_{E_{\lfloor a/2\rfloor}}$ with respect to the sub-matching $E_{\lfloor a/2\rfloor}(2,a-1)$.
+By the inductive hypothesis, we may apply the algorithm to this sub-matching and commute with the isomorphism with $Y_{E_{\lfloor a/2\rfloor}}$.
+In this way, we find that the coordinate of $\tilde{\psi}$ defined by $\tilde{\psi}(1,a):=\psi(1,a)$ and $\tilde{\psi}(a+1,2n+r)=R$ is $x_{\psi(2,a-1)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_{\tilde{\psi}}(q)$.
+Similarly, define $Y_{\tilde{\psi}}$ with respect to the sub-matching $\tilde{\psi}(a+1,2n+r)$, and commute the algorithm with the isomorphism.
+In the same way, we obtain that the coordinate of $\psi\in Y_{\tilde{\psi}}$ is $x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_\psi(q)$ as desired.
+
+	Note that we only added a single operation to the algorithm in the inductive step, which also commutes with any isomorphism defined by lemma \ref{sub-matching isomorphism}.
+Thus the inductive step holds and the proposition is proved.
+
+	\begin{figure}
+		\def\cbasisspacing{1mm}
+		\begin{adjustbox}{width=\textwidth}
+			\GeneralizedMatching{14}{3/12,4/11,5/10,6/9,7/8,13/14}{2}{1/1,2/2}{12/4}, \hspace{\cbasisspacing}
+			\GeneralizedMatching{14}{1/2,3/4,5/6,9/12,10/11,13/14}{2}{7/1,8/2}{12/4}, \hspace{\cbasisspacing}
+			\GeneralizedMatching{14}{1/6,2/5,3/4,9/12,10/11,13/14}{2}{7/1,8/2}{12/4}
+		\end{adjustbox}
+
+		\caption{The figure on the left has sub-matching $R$ ignoring the last two nodes.
+The middle figure has submatching $R_3$ ignoring the last two nodes.
+The figure on the right has sub-matching $E_3$ also ignoring the last two nodes.
+Since the last two nodes have the same structure for all elements, if the coordinate of the first element is $c$, the coordinate of the second is $Q_6Q_5Q_4c$, and the coordinate of the third is $\frac{Q_6Q_5Q_4}{Q_1Q_2}c$.}
+
+		\label{kernel induct characterization example}
+	\end{figure}
+
+\end{proof}
+
+\vspace{5mm}
+The following few corollaries will help to simplify some later arguments.
+
+\begin{corollary}
+	Let $w\in\cap\text{ker}(1+T_i)$, $w\not=0$. Suppose $\psi(1,a)$ is a sub-matching with no anchors. Then:
+
+	$$x_\psi=x_{\psi(1,a)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{a/2}_{n+r}$$
+
+	\label{characterization generalization}
+\end{corollary}
+
+\begin{proof}
+	Define $a_1=\psi(1)$, $a_i=\psi(a_{i-1}+1)$.
+Then for some $j$ we have $a_j=a$.
+If $j=1$, the statement is the same as the proposition.
+Suppose that the statement is true for any matching with $a_v=a$, $v<j$.
+Then the statement holds for the sub-matching $\psi(a_1+1,2n+r)$, and we have:
+	\begin{align*}
+	x_\psi(q)=&x_{\psi(1,a_1)}(q)x_{\psi(a_1+1,2n+r)}(q)\Q^{a_1/2}_{n+r}\\
+	=&x_{\psi(1,a_1)}(q)x_{\psi(a_1+1,a)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{a_1/2}_{n+r}\Q_{n+r-a_1/2}^{a/2-a_1/2}\\
+	=&x_{\psi(1,a_1)}(q)x_{\psi(a_1+1,a)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{a_1/2}_{n+r}\Q_{n+r-a_1/2}^{a/2-a_1/2}\prn{\frac{Q_{a/2-1}...Q_{a/2-a_1/2}}{Q_{a/2-1}...Q_{a/2-a_1/2}}}\\
+	=&x_{\psi(1,a_1)}(q)x_{\psi(a_1+1,a)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{a_1/2}_{a/2}\Q^{a/2}_{n+r}\\
+	=&x_{\psi(1,a)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{a/2}_{n+r}
+	\end{align*}
+
+\end{proof}
+
+\vspace{5mm}
+\begin{corollary}
+	If $\psi\in M_{2n+r}^r$, then $x_\psi(q)\not=0$ if $e>n+r$.
+
+	\label{coeff nonzero}
+\end{corollary}
+
+\begin{proof}
+	For our base cases, if $2n+r=2$ all coefficients are 1, which is nonzero for any $q$.
+
+	Assume the statement is true for all $2n'+r'<2n+r$. Given $\psi(1)=a$ we have $$x_\psi(q)=x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}$$
+
+	If $e>n+r$, non of the $Q_i$ term appearing in $\Q^{\lfloor a/2\rfloor}_{n+r}$ are zero, and $n'+r'<n+r<e$ for any of the sub-matchings that appear, so those coordinates are nonzero and the corollary holds.
+
+\end{proof}
+
+\vspace{5mm}
+The proposition fully characterizes any possible kernel element when $Q_1...Q_{n+r-1}\not=0$. In particular, the following corollary holds:
+
+\begin{corollary}
+	When $Q_1..Q_{n+r-1}\not=0$ and the kernel is nontrivial, the kernel is one dimensional.
+
+	\label{1-D}
+\end{corollary}
+
+This corollary follows from the fact that we may write the coordinate of any basis element as proportional to the coordinate of the rainbow basis element.
+
+\subsubsection{Nontrivial Kernel}
+
+To verify the kernel element, we will need to know exactly which basis elements are mapped to a specific basis element by a given $(1+T_i)$. The next two lemmas help address this question.
+
+\begin{lemma}
+	Take some basis element $\psi\in M_{2n+r}^r$.
+
+	\begin{enumerate}[label={(\roman*)}]
+
+		\item Suppose $\psi(a)=b$ for some $b>a+1$, and that $(1+T_i)\psi=(1+q)\psi$ for some $a<i<b-1$.
+Me then have a subrepresentation $\psi(a,b)$ and define $Y_\psi$ with respect to this subrepresentation.
+Then for all basis elements $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$, we have that $$\sigma\in Y_\psi$$.
+
+		\item Suppose $\psi$ has some anchor at position $u$, and $(1+T_i)\psi=(1+q)\psi$ for some $i>u$, we again have a subrepresentation $\psi(u,2n+r)$ and define $Y_\psi$ with respect to this subrepresentation.
+Then for all basis elements $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$, we have that $\sigma\in Y_\psi$ again.
+
+	\end{enumerate}
+	\label{preimage under hump}
+\end{lemma}
+
+\begin{proof}
+	This lemma follows from an observation I made in section \ref{two humps created}: a transposition can only create two arcs or an arc and an anchor.
+
+	(i) If $\sigma\not\in Y_\psi$ either $\sigma(1,a-1)\not=\psi(1,a-1)$ or $\sigma(b+1,2n+r)\not=\psi(b+1,2n+r)$.
+Suppose it is the first case.
+Then for some $s,t\in [1,a-1]$, $s<t$, we have $\psi(s)=t$ and $\sigma(s)\not=t$.
+To have $(1+T_i)\sigma=q^{1/2}\psi$ we must have $\sigma(t)=i+1$, $\sigma(s)=i$.
+But then $\sigma(a)\not=b$ and $\sigma(a)\not=i$ or $i+1$, so $((1+T_i)\sigma)(a)\not=b$ and $(1+T_i)\sigma\not=q^{1/2}\psi$.
+The same argument proves the $\sigma(b+1,2n+r)\not=\psi(b+1,2n+r)$ case.
+
+	(ii) An analogous argument proves the anchor case. Specifically, the anchor cannot exist at position $u$ and is not created by action of $(1+T_i)$ if $\sigma(s)=i$ and $\sigma(t)=i+1$.
+
+\end{proof}
+
+\vspace{5mm}
+It is important to note that lemma \ref{preimage under hump} only references cases where a transposition acts under an arc or to the right of an anchor.
+An example is given in figure \ref{preimage under hump example}.
+
+The next lemma characterizes cases where the transposition is not under any arcs and all anchors are to the right.
+
+\begin{figure}[b]
+	\[
+	\begin{tabular}{l l l l}
+	\GeneralizedAction{13}{1/4,2/3,6/7,8/13,9/10,11/12}{1}{5/1}{5/4}{9}{1/4,2/3,6/7,8/13,9/10,11/12}{5/1}{(1+q)}\\
+
+	\GeneralizedAction{13}{1/4,2/3,6/7,8/9,10/13,11/12}{1}{5/1}{5/4}{9}{1/4,2/3,6/7,8/13,9/10,11/12}{5/1}{(q^{1/2})}\\
+
+	\GeneralizedAction{13}{1/4,2/3,6/7,8/13,9/10,11/12}{1}{5/1}{5/4}{6}{1/4,2/3,6/7,8/13,9/10,11/12}{5/1}{(1+q)}\\
+
+	\GeneralizedAction{13}{1/4,2/3,5/6,8/13,9/10,11/12}{1}{7/1}{5/4}{6}{1/4,2/3,6/7,8/13,9/10,11/12}{5/1}{(q^{1/2})}\\
+
+	\end{tabular}
+	\]
+
+	\caption{In the first line we act under an arc, so if another element without that arc is sent to that element, it must fix the arc as shown in the second line.
+In the third line we act to the right of an anchor, so if another element without that anchor is sent to that element, it must fix the anchor as shown in the fourth line.
+	}
+	\label{preimage under hump example}
+\end{figure}
+
+Essentially, this lemma states that the only elements sent to the same element are those which break at most one of the top level arcs to the left of the leftmost anchor, or that break the leftmost anchor.
+An illustration is given in figure \ref{preimage under nothing example}.
+
+\vspace{5mm}
+\begin{lemma}
+	Take a basis element $\psi\in M_{2n+r}^r$.
+Suppose the leftmost anchor in $\psi$ is at index $b$, or let $b=2n+r+1$ if there is no anchor.
+Define $a_j$ such that $\psi(a_j)=a_{j-1}+1$ and $\psi(a_1)=1$ for all $j$ such that $a_j<b$.
+
+	Suppose $(1+T_i)\psi=(1+q)\psi$ for some $i<b-1$ where $\nexists s,t$ such that $\psi(s)=t$ and $s<i,t>i+1$. Suppose there is some basis element $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$. Then:
+	\\
+
+	\begin{enumerate}[label={(\roman*)}]
+		\item  $\psi(a_{j-1}+2,a_j-1)=\sigma(a_{j-1}+2,a_j-1)$ for all $j$.
+
+		\item $\psi(b+1,2n+r)=\sigma(b+1,2n+r)$
+
+		\item If $b$ is not an anchor in $\sigma$, $\psi(a_j)=\sigma(a_j)$ for all $j$ such that $a_j\not=i+1$.
+
+		\item If $b$ is an anchor in $\sigma$, there exists exactly one value of $j$ such that $\sigma(a_j)\not=\psi(a_j)$ and $a_j\not=i+1$
+	\end{enumerate}
+	\label{preimage under nothing}
+\end{lemma}
+
+\begin{proof}
+
+	(i) Suppose that, for some $j$ there exists $s,t\in [a_{j-1}+2,a_j-1]$ such that $\psi(s)=t$ but $\sigma(s)\not=t$.
+Then if $(1+T_i)\sigma=q^{1/2}\psi$ we must have $\sigma(i)=s$ or $t$ and $\sigma(i+1)=s$ or $t$.
+But, by definition, $i,i+1\not\in[a_{j-1}+1,a_j]$, so this implies $\sigma(a_j)\not=a_{j-1}+1,i,i+1$, so $((1+T_i)\sigma)(a_j)\not=a_{j-1}+1$ and $(1+T_i)\sigma\not=q^{1/2}\psi$.
+So (i) is proved.
+
+	\vspace{5mm}
+	(ii) The proof of (ii) is analogous to the proof of (i). Me cannot have $\psi(b+1,2n+r)\not=\sigma(b+1,2n+r)$ and $\psi(b+1,2n+r)=((1+T_i)\sigma)(b+1,2n+r)$ if $((1+T_i)\sigma)(b)=b$.
+
+	\vspace{5mm}
+	(iii) If $b$ is not an anchor in $\sigma$ and $(1+T_i)\sigma=q^{1/2}\psi$, we must have $i$ an anchor in $\sigma$, and $\sigma(i+1)=b$. No other nodes in $\sigma$ are changed, so this proves (iii).
+
+	\vspace{5mm}
+	(iiii) From (i)-(iii) we have that the only remaining matchings that can differ are the $(a_{j-1}+1,a_j)$ matchings.
+If one of them differs, by the same argument as before it must be fixed by the action of $(1+T_i)$, and no other nodes are changed, so (iiii) is proved.
+
+\end{proof}
+
+\begin{figure}[b]
+	\[
+	\begin{tabular}{l l l l}
+	\GeneralizedAction{15}{1/6,2/3,4/5,7/8,9/10,12/15,13/14}{1}{11/1}{5/4}{7}{1/6,2/3,4/5,7/8,9/10,12/15,13/14}{11/1}{(1+q)}\\
+
+	\GeneralizedAction{15}{1/8,2/3,4/5,6/7,9/10,12/15,13/14}{1}{11/1}{5/4}{7}{1/6,2/3,4/5,7/8,9/10,12/15,13/14}{11/1}{(q^{1/2})}\\
+
+	\GeneralizedAction{15}{1/6,2/3,4/5,7/10,8/9,12/15,13/14}{1}{11/1}{5/4}{7}{1/6,2/3,4/5,7/8,9/10,12/15,13/14}{11/1}{(q^{1/2})}\\
+
+	\GeneralizedAction{15}{1/6,2/3,4/5,8/11,9/10,12/15,13/14}{1}{7/1}{5/4}{7}{1/6,2/3,4/5,7/8,9/10,12/15,13/14}{11/1}{(q^{1/2})}\\
+
+	\end{tabular}
+	\]
+
+	\caption{The action of $(1+T_7)$ fixes the first basis element.
+Shown are all the basis vectors sent to the same element by the same transposition.
+Note that in all of them nodes 2-5 and 12-15 are the same.
+This illustrates (i) and (ii) in lemma \ref{preimage under nothing}.
+Note that in the last case where the anchor is in a different place, 1,6 and 9,10 are still matched.
+This illustrates (iii).
+In the middle two cases where the anchor is in the same place, only one of 1,6 or 9,10 are not paired.
+This illustrates (iiii).
+	}
+	\label{preimage under nothing example}
+\end{figure}
+
+\vspace{5mm}
+Lastly, we will need a small combinatorial result.
+
+\begin{lemma}
+	Suppose $n>b\geq a>0$ and $e>n$. Then $$Q_{n-a}Q_b-Q_{n-b-1}Q_{a-1}=Q_{n}Q_{b-a}$$
+
+	\label{Q lemma}
+\end{lemma}
+
+\begin{proof}
+	If $b=1$, the only possibility for $a$ is 1, in which reduces to lemma \ref{Q alg}.
+
+	Suppose the lemma is true for all $\tilde{b}<b+1$. Then for $a< b$ we have 
+	\begin{align*}	
+	Q_{n-a}Q_b -Q_{n-b-1}Q_{a-1}=&Q_{n}Q_{b-a}\\
+	Q_1Q_{n-a}Q_b-Q_1Q_{n-b-1}Q_{a-1}=&Q_1Q_{n}Q_{b-a}
+	\end{align*}
+
+	from lemma \ref{Q alg}, we have	
+	$$Q_{n-a}(Q_{b+1}+Q_{b-1})-(Q_{n-b}+Q_{n-b-2})Q_{a-1}=Q_{n}(Q_{b-a-1}+Q_{b-a+1})$$
+
+	and from the inductive hypothesis we have
+
+	$$Q_{n-a}Q_{b+1}-Q_{n-b}Q_{a-1}=Q_{n}Q_{b-a+1}$$
+
+	as desired.
+
+	For $a=b$ we have 
+	\begin{align*}
+	Q_{n-b}Q_b -Q_{n-b-1}Q_{b-1}=&Q_{n}\\
+	Q_1Q_{n-b}Q_b-Q_1Q_{n-b-1}Q_{b-1}=&Q_1Q_{n}
+	\end{align*}
+
+	from lemma \ref{Q alg}, we have
+	\begin{align*}
+	Q_{n-b}(Q_{b+1}+Q_{b-1})-(Q_{n-b}+Q_{n-b-2})Q_{b-1}=&Q_1Q_{n}\\
+	Q_{n-b}Q_{b+1}-Q_{n-b-2}Q_{b-1}=&Q_1Q_{n}\\
+	\end{align*}
+
+	as desired.
+
+	For $a=b+1$, we continue:
+	\begin{align*}
+	Q_1Q_{n-b}Q_{b+1}-Q_1Q_{n-b-2}Q_{b-1}=&Q_1Q_1Q_{n}\\
+	(Q_{n-b-1}+Q_{n-b+1})Q_{b+1}-Q_{n-b-2}(Q_{b}+Q_{b-2})=&(1+Q_2)Q_{n}\\
+	\end{align*}
+
+	So by the inductive hypothesis
+	$$Q_{n-b-1}Q_{b+1}-Q_{n-b-2}Q_{b}=Q_{n}$$
+
+	as desired, and the proof is finished by induction.
+
+\end{proof}
+
+\vspace{5mm}
+Me are now ready to prove existence of a kernel element.
+To prove this, we will show that if $w\in M_{2n+r}^r$ is as characterized above, the coordinate of any basis element in $(1+T_i)w$ is zero.
+This will split into various cases related to the previous lemmas.
+
+\vspace{5mm}
+\begin{theorem}
+	Suppose $e=n+r+1$. Then $\cap\text{ker}(1+T_i)\not=0$.
+	\label{kernel existence}
+\end{theorem}
+
+\begin{proof}
+
+	As a base case, when $2n'+r'\leq 2$, the representation is at most one dimensional.
+If the one basis element has only anchors, it is sent to zero by any $(1+T_i)$, and is in the kernel.
+If the single basis element is a single arc, it is sent to $(1+q)$ times itself, and we take $e=n+r+1=2$ so $1+q=0$ and the base case holds.
+
+	\vspace{5mm}
+
+	Assume inductively that the statement holds for all $M_{2n'+r'}^{r'}$ where $2n'+r'<2n+r$. Take $w$ as defined by proposition \ref{kernel characterization}.
+
+	Given $\psi\in (1+T_i)M_{2n+r}^r$ let $E_\psi\subset M_{2n+r}^r$ be the pre-image of $\psi$ under the action of $(1+T_i)$. To prove $w$ is in the kernel, we must show the following: 
+	\begin{equation}
+	(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=0\text{ for all basis elements }\psi
+	\label{weak kernel}
+	\end{equation}
+	Inductively, we assume this equation holds for basis elements in smaller representations $M_{2n'+r'}^{r'}$, but only for $q$ such that $e=n'+r'+1$.
+Clearly this is true in the base case.
+For the following proof we will need a slightly stronger inductive assumption.
+Take $\psi'\in M_{2n'+r'}^{r'}$, and suppose either that $\psi'(1)=2n'+r'$, and that $T_i\psi'=(1+q)\psi'$, $1<i<2n'+r'-1$, or that 1 is an anchor in $\psi$.
+Defining $E_{\psi'}$ as before, we assume
+
+	\begin{equation}
+	(1+q)x_{\psi'}+\sum_{\sigma\in E_{\psi'},\sigma\not=\psi'}q^{1/2}x_\sigma=0\text{ for any } q \text{ with }e>n'+r'
+	\label{strong kernel}
+	\end{equation}
+
+	Note that \ref{strong kernel} does not apply in the base case.
+Our proof of the inductive step will be split into cases, and each case will only depend on sub-cases in which certain inductive hypotheses apply, so this will not lead to any problems.
+
+	Before exploring the cases, let us formally define $E_\psi$ to be the pre-image of $\psi$ under the action of $(1+T_i)$, and $E_{\psi(a,b)}$ to be the pre-image of $\psi(a,b)$ under action of $(1+T_{i-a+1})$:
+
+	\begin{enumerate}[label={case \arabic*:}]
+		\item Suppose $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, and that $\exists s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\psi(s)=t$.
+Also suppose the leftmost anchor is at some index $u>t$, or that there are no anchors.
+Then we have a sub-matching $\psi(s,t)$, and by lemma \ref{preimage under hump} $E_\psi\subset Y_\psi$.
+Then, using corollary \ref{characterization generalization}, the following equality holds:
+
+		\begin{align*}
+		&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)\\
+		=&\prn{x_{\psi(1,s-1)}(q)\Q_{n+r}^{(s-1)/2}}\prn{(1+q)x_{\psi(s,2n+r)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,2n+r)}(q)}\\
+		=&\prn{x_{\psi(1,s-1)}(q)\Q_{n+r}^{(s-1)/2}}\prn{x_{\psi(t+1,2n+r)}(q)\Q_{n+r-(s-1)/2}^{(t-s+1)/2}}\prn{(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,t)}(q)}
+		\end{align*}
+
+		Me have that $e>j$ for any $Q_j$ term appearing in the equation above, and $e>n'+r'$ for any sub-matching coordinate appearing above, so by corollary \ref{coeff nonzero}:
+
+		$$(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=0$$
+
+		if and only if
+
+		$$(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,t)}(q)=0$$
+
+		Note that $(\psi(s,t))(1)=t-s+1$. So by our inductive hypothesis (ii), we have
+
+		$$(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_{\psi(s,t)},\sigma\not=\psi(s,t)}q^{1/2}x_{\sigma}(q)=0$$
+
+		By lemma \ref{sub-matching isomorphism}, if $\sigma\in Y_\psi$, $(1+T_i)\sigma=q^{1/2}\psi$ if and only if $(1+T_{i-s+1})\sigma(s,t)=q^{1/2}\psi(s,t)$, so the previous equation implies $$(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,t)}(q)=0$$
+
+		as desired, and this case is proved.
+
+		\vspace{5mm}
+		\item Again take $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, but suppose the leftmost anchor is at some position $u$ where $1<u<i$.
+Then, as before, we have a sub-matching $\psi(u,2n+r)$ and by lemma \ref{preimage under hump} $E_\psi\subset Y_\psi$.
+
+		Note that both corollary \ref{characterization generalization} and our inductive hypothesis \ref{strong kernel} still apply in this case, where we consider a left anchor instead of a matching.
+This allows the exact same logic from the proof of the first case to prove this case.
+		\\
+
+		It is important to note that, for both case 1 and case 2, the inductive hypothesis depends only on cases in which \ref{strong kernel} holds.
+Thus, if we show these cases rely on valid base cases, case 1 and 2 follow.
+This will be done in case 4.
+
+		\vspace{5mm}
+		\item Suppose $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, the leftmost anchor is at a position $u>i+1$ or there are no anchors, and $\nexists s,t$ such that $\psi(s)=t$ and $s<i<t-1$.
+Lemma \ref{preimage under nothing} characterizes all $\sigma\in E_\psi$.
+Me would like to prove the following for arbitrary $q$ where $e>n+r$:
+
+		$$(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=-q^{1/2}x_{\psi(1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r+1}^{(i+1)/2}$$
+
+		\begin{figure}[b]
+			\[
+			\begin{tabular}{l l l l}
+			\GeneralizedAction{7}{1/2,3/4,5/6}{1}{7/1}{3/4}{3}{1/2,3/4,5/6}{7/1}{(1+q)}\\
+
+			\GeneralizedAction{7}{1/4,2/3,5/6}{1}{7/1}{3/4}{3}{1/2,3/4,5/6}{7/1}{(q^{1/2})}\\
+
+			\GeneralizedAction{7}{1/2,3/6,4/5}{1}{7/1}{3/4}{3}{1/2,3/4,5/6}{7/1}{(q^{1/2})}\\
+
+			\GeneralizedAction{7}{1/2,4/7,5/6}{1}{3/1}{3/4}{3}{1/2,3/4,5/6}{7/1}{(q^{1/2})}\\
+
+			\end{tabular}
+			\]
+
+			\caption{The four elements sent to the first element by $(1+T_3)$ are listed.
+The coordinate of the first element is $Q_3Q_2Q_1$.
+The coordinate of the second is $Q_3Q_2$.
+The coordinate of the third is $Q_3Q_2$.
+The coordinate of the fourth is $Q_3$.
+Call the first element $\psi$.
+Then $x_{\psi(1,2)}=1$, $x_{\psi(5,7)}=Q_1$, so $-q^{1/2}x_{\psi(1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r+1}^{(i+1)/2}=-q^{1/2}Q_4Q_3$.
+Me also have $(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=(q+1)(Q_3Q_2Q_1)+q^{1/2}(Q_3Q_2+Q_3Q_2+Q_3)=-q^{1/2}(Q_3Q_2Q_1^2-2Q_3Q_2+Q_3)=-q^{1/2}Q_4Q_3$ as desired (one can verify the last equality by hand or simplify using lemma \ref{Q lemma}).}
+			\label{case 3}
+		\end{figure}
+
+		See figure \ref{case 3} for an example of this equality.
+Note that if $e=n+r+1$, $Q_{n+r}$ is the only zero component in the right side of this equation, so proving this equation is sufficient to prove case three.
+		\\
+
+		Me will prove this equality through yet another inductive proof, this time inducting on the number of top level humps, including the leftmost anchor.
+
+		Formally, as we have in earlier lemmas, we will define $a_j$ by $a_1:=\psi(1)$, $a_j:=\psi(a_{j-1}+1)$.
+Then define $b_\psi$ such that $a_{b_\psi}=u$ if there is an anchor or $a_{b_\psi}=2n+r$ otherwise.
+Me induct on $b_\psi$.
+		\\
+
+		If $b_\psi=1$, we must be in $M_2^0$ to be in case 3 (otherwise $s<i<t-1$ for some $s,t$ where $\psi(s)=t$), which is trivially satisfied. Thus the base case holds.
+		\\
+
+		Suppose for all basis elements $\sigma$ such that $b_\sigma<b_\psi$, the equality holds.
+Suppose $i\not=1$.
+Then $a_1<i$ and lemma \ref{preimage under nothing} gives that there is a unique $\upsilon\in E_\psi$ such that $\upsilon(1)\not=a_1$.
+Thus we have the following equality:
+
+		\begin{align*}
+		&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_\sigma(q)\\
+		=&\prn{x_{\psi(1,a_1)}(q)\Q_{n+r}^{a_1/2}}\prn{(1+q)x_{\psi(a_1+1,2n+r)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_{\sigma(a_1+1,2n+r)}(q)}
+		\end{align*}
+
+		Define $Y_\psi$ with respect to the sub-matching $\psi(a_1+1,2n+r)$. Then $\sigma\in E_\psi$, $\sigma\not=\upsilon$ implies $\sigma\in Y_\psi$. By our inductive hypothesis, we have that 
+		\begin{align*}
+		&(1+q)x_{\psi(a_1+1,2n+r)}(q)+\sum_{\sigma\in E_{\psi(a_1+1,2n+r)},\sigma\not=\psi(a_1+1,2n+r)}q^{1/2}x_{\sigma}(q)\\
+		=&-q^{1/2}x_{\psi(a_1+1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}
+		\end{align*}
+
+		By lemma \ref{sub-matching isomorphism}, $\sigma\subset Y_\psi$, $\sigma\in E_\psi$ if and only if $\sigma(a_1+1,2n+r)\in E_{\psi(a_1+1,2n+r)}$. This implies:
+
+		\begin{align*}
+		&(1+q)x_{\psi(a_1+1,2n+r)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_{\sigma(a_1+1,2n+r)}(q)\\
+		=&-q^{1/2}x_{\psi(a_1+1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}
+		\end{align*}
+
+		So, combining with the aforementioned equality, we have 
+		\begin{align*}
+		&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_\sigma(q)\\
+		=&\prn{x_{\psi(1,a_1)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}}\prn{-q^{1/2}x_{\psi(a_1+1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}}\\
+		=&\prn{x_{\psi(1,a_1)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}}\prn{-q^{1/2}x_{\psi(a_1+1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r-a_1/2+1}^{(i+1-a_1)/2}}\prn{\frac{Q_{(i-1)/2-1}...Q_{(i-1-a_1)/2}}{Q_{(i-1)/2-1}...Q_{(i-1-a_1)/2}}}\\
+		=&-q^{1/2}x_{\psi(1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r+1}^{(i+1)/2}\prn{\frac{Q_{n+r-a_1/2}Q_{(i-1)/2}}{Q_{n+r}Q_{(i-1-a_1)/2}}}
+		\end{align*}
+
+		Separately, note that $\upsilon$ is defined by $\upsilon(2,a_1-1)=\psi(2,a_1-1)$, $\upsilon(a_1+1,i-1)=\psi(a_1+1,i-1)$, $\upsilon(i+2,2n+r)=\psi(i+2,2n+r)$, and $\upsilon(1)=i+1$, $\upsilon(a_1)=i$.
+Thus we may determine $x_\upsilon$, again utilizing corollary \ref{characterization generalization}:
+
+		\begin{align*}
+		x_\upsilon=&x_{\psi(i+2,2n+r)}x_{\upsilon(2,i)}\Q_{n+r}^{(i+1)/2}\\
+		=&x_{\psi(i+2,2n+r)}\prn{x_{\psi(2,a_1-1)}x_{\upsilon(a_1,i)}\Q_{(i-1)/2}^{(a_1-2)/2}}\Q_{n+r}^{(i+1)/2}\\
+		=&x_{\psi(i+2,2n+r)}\prn{x_{\psi(1,a_1)}x_{\psi(a_1+1,i-1)}\Q_{(i-1)/2}^{(a_1-2)/2}}\Q_{n+r}^{(i+1)/2}\\
+		=&x_{\psi(i+2,2n+r)}x_{\psi(1,i-1)}\Q_{n+r+1}^{(i+1)/2}\prn{\frac{Q_{n+r-(i+1)/2}Q_{a_1/2-1}}{Q_{n+r}Q_{(i-1-a_1)/2}}}
+		\end{align*}
+
+		Adding this into our previous equation, we have:
+		\begin{align*}
+		&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)\\
+		=&-q^{1/2}x_{\psi(1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r+1}^{(i+1)/2}\prn{\frac{Q_{n+r-a_1/2}Q_{(i-1)/2}-Q_{n+r-(i+1)/2}Q_{a_1/2-1}}{Q_{n+r}Q_{(i-1-a_1)/2}}}
+		\end{align*}
+
+		Applying lemma \ref{Q lemma} to the portion of the equation above in parenthesis, the above is equivalent to
+
+		$$(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=-q^{1/2}x_{\psi(1,i-1)}(q)x_{\psi(i+2,2n+r)}(q)\Q_{n+r+1}^{(i+1)/2}$$
+
+		as desired. Note that if $e\geq n+r+1$ the only term above that can be zero is $Q_{n+r}$ (by corollary \ref{coeff nonzero}). Thus we have proved the inductive step for the case where $i\not=1$.
+
+		\vspace{5mm}
+		If $i=1$, we instead look at the sub-matchings $\psi(1,a_{(b_\psi-1)})$, $\psi(a_{(b_\psi-1)}+1,2n+r)$.
+Again lemma \ref{preimage under nothing} gives that there is a unique $\upsilon\in E_\psi$ such that $\upsilon(a_{(b_\psi-1)}+1)\not=\psi(a_{(b_\psi-1)}+1)$.
+Taking $Y_\psi$ with respect to the sub-matching $\psi(a_{(b_\psi-1)}+1,a_{b_\psi})$ again we have that $\sigma\in E_\psi$, $\sigma\not=\upsilon$ implies $\sigma\in Y_\psi$.
+Thus, following the same logic as before, we arrive at the following equality:
+		\begin{align*}
+		&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_\sigma(q)\\
+		=&\prn{x_{\psi(a_{(b_\psi-1)}+1,2n+r)}(q)\Q_{n+r}^{a_{(b_\psi-1)}/2}}\prn{-q^{1/2}x_{\psi(3,a_{(b_\psi-1)})}(q)Q_{a_{(b_\psi-1)}/2}}\\
+		=&-q^{1/2}x_{\psi(3,2n+r)}\frac{Q_{n+r-1}Q_{a_{(b_\psi-1)}/2}}{Q_{a_{(b_\psi-1)}/2-1}}
+		\end{align*}
+
+		Again, we know the structure of $\upsilon$ from lemma \ref{preimage under nothing}.
+Suppose for now that $a_{b_\psi}$ is not an anchor, so it is $2n+r$.
+Then $\upsilon$ is defined by $\upsilon(3,a_{(b_\psi-1)})=\psi(3,a_{(b_\psi-1)})$, $\upsilon(a_{(b_\psi-1)}+2,2n+r-1)=\psi(a_{(b_\psi-1)}+2,2n+r-1)$, and $\upsilon(1)=2n+r$, $\upsilon(2)=a_{(b_\psi-1)}+1$.
+So we may again find $x_\upsilon$:
+		\begin{align*}
+		x_\upsilon=x_{\upsilon(2,2n+r-1)}=&x_{\psi(3,a_{(b_\psi-1)})}x_{\psi(a_{(b_\psi-1)}+2,2n+r-1)}\Q_{n+r-1}^{a_{(b_\psi-1)}/2}\\
+		=&x_{\psi(3,a_{(b_\psi-1)})}x_{\psi(a_{(b_\psi-1)}+1,2n+r)}\Q_{n+r-1}^{a_{(b_\psi-1)}/2}\\
+		=&x_{\psi(3,2n+r)}\frac{Q_{n-r-1-a_{(b_\psi-1)}/2}}{Q_{a_{(b_\psi-1)}/2-1}}
+		\end{align*}
+
+		Alternatively, if $a_{b_\psi}$ is an anchor, the definition of $\upsilon$ is now $\upsilon(3,a_{b_\psi}-1)=\psi(3,a_{b_\psi}-1)$, $\upsilon(a_{b_\psi}+1,2n+r)=\psi(a_{b_\psi}+1,2n+r)$, and $\upsilon(1)=1$, $\upsilon(2)=a_{b_\psi}$, so we have:
+
+		$$x_\upsilon=x_{\upsilon(2,2n+r)}=x_{\psi(3,a_{(b_\psi-1)})}x_{\psi(a_{b_\psi}+1,2n+r)}\Q_{n+r-1}^{a_{(b_\psi-1)}/2}=x_{\psi(3,2n+r)}\frac{Q_{n-r-1-a_{(b_\psi-1)}/2}}{Q_{a_{(b_\psi-1)}/2-1}}$$
+
+		so for our purposes $x_\upsilon$ is the same in either case.
+
+		Incorporating into the above equation, we have:
+
+		$$(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=$$
+
+		$$-q^{1/2}x_{\psi(3,2n+r)}\frac{Q_{n+r-1}Q_{a_{(b_\psi-1)}/2}-Q_{n-r-1-a_{(b_\psi-1)}/2}}{Q_{a_{(b_\psi-1)}/2-1}}$$
+
+		By lemma \ref{Q lemma}, this is simply $-q^{1/2}x_{\psi(3,2n+r)}Q_{n+r}$ as desired, and we have finished proving case 3.
+		\\
+
+		\item The only cases we have not yet dealt with are those where either $1$ is an anchor or $\psi(1)=2n+r$. These are those cases related to our inductive hypothesis (ii).
+
+		To not be in case 1 or 2, we must have that there are no anchors between index 1 and $i$, and that there is no integer $s$ such that $1<s<i<\psi(s)-1$.
+It follows from the same argument that proved lemma \ref{preimage under hump} that there exists exactly one $\upsilon\in E_\psi$ such that $\upsilon(1)\not=\psi(1)$.
+Define $N$ to be $2n+r$ if 1 is an anchor, or $2n+r-1$ if 1 is not an anchor.
+Then, defining $Y_\psi$ with respect to the sub-matching $\psi(2,N)$, we have that $\sigma\in E_\psi, \sigma\not=\upsilon$ if and only if $\sigma(2,N)\in E_{\psi(2,N)}$.
+Note that for $E_{\psi(2,N)}$ we may apply the inductive hypothesis from case 3, so we have:
+		\begin{align*}
+		&(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi,\upsilon}q^{1/2}x_\sigma(q)\\
+		=&(1+q)x_{\psi(2,N)}(q)+\sum_{\sigma\in E_{\psi(2,N)},\sigma\not=\psi(2,N)}q^{1/2}x_{\sigma}(q)\\
+		=&-q^{1/2}x_{\psi(2,i-1)}x_{\psi(i+2,N)}\Q{n+r}^{i/2}
+		\end{align*}
+
+		As in case 3, we can also determine $x_\upsilon$.
+$\upsilon$ is defined by $\upsilon(2,i-1)=\psi(2,i-1)$, $\upsilon(i+2,N)=\psi(i+2,N)$, $\upsilon(1)=i$, and $\upsilon(i+1)=2n+r$ if 1 is not an anchor or $i+1$ if 1 is an anchor, and we have:
+
+		$$x_\upsilon=x_{\psi(2,i-1)}x_{\upsilon(i+2,N)}\Q{n+r}^{i/2}$$
+
+		Thus we have
+
+		$$(1+q)x_\psi(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_\sigma(q)=$$
+
+		$$-q^{1/2}x_{\psi(2,i-1)}x_{\psi(i+2,N)}\Q{n+r}^{i/2}\prn{1-1}=0$$
+
+		as desired, and the last case is proved. Note that this only relies on the inductive hypothesis from case 3, for which we showed the base case holds.
+	\end{enumerate}
+
+	Thus our inductive hypotheses have all been proven, and those that apply in the base case hold in the base case, so by induction the theorem is proved.
+
+\end{proof}
+
+\begin{corollary}
+	If $e=n+r+1$, $M_{2n+r}^r$ is reducible, and has a unique sign subrepresentation.
+\end{corollary}
 
@@
 \section{Conjecture}\label{Conjecture Section}
-Recall that $K_{2n + r}^r := K$ is the direct sum of all copies of the sign representation in $W$.
-Hence the following characterises sign subrepresentations of $W$ completely:
+Recall that $K_{2n + r}^r := K$ is the direct sum of all copies of the sign representation in $M$.
+Hence the following characterises sign subrepresentations of $M$ completely:
 \begin{proposition}
-  $K \subset M_{2n + r}^r$ is trivial when $e \neq n + r + 1$, and $\dim \, K = 1$ when $e = n + r + 1$.\qed
+  $K \subset M_{2n + r}^r$ is trivial when $e \neq n + r + 1$, and $\dim \, K = 1$ when $e = n + r + 1$.\qed{\color{red} We know this is not accurate anymore, right?}
 \end{proposition} 

### 2019-07-30 tex/comments/2-nat-comments.tex
Kernel e>n+r+1 comments

--- 2019-07-30 tex/Drafts/Draft-2.tex
@@
 
+{\color{magenta} We can make this section-level and work it out, I'm sure.}
+
 \subsection{Kernels and further work}
 
+{\color{magenta} Better subsection label: Sign Subrepresentations of $M$.
+If used, should remind the reader in the beginning that $K$ is a direct sum of all sign subrepresentations (by dimensionality, just a sign representation if it's nonzero).}
+
 In this section, we characterize $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$ for $e \nmid n + r + 1$ and for $e=n+r+1$.
-When the representation is clear, we will simply denote this kernel as $K$ or $\cap\text{ker}(1+T_i)$.
+When the representation is clear {\color{magenta} When the indices $2n + r, r$ are clear\ldots}, we will simply denote this kernel as $K$ or $\cap\ker(1+T_i)$.
 For compactness, in this section we use $\sim $ to denote "proportional to".
 For convenience, define $M_0^0$ to be the zero representation.
-
+{\color{magenta} Replace $\backslash$text\{ker\} with $\backslash$ker;
+I've done it for this document already.}
+
+{\color{magenta} Next section needs new name (perhaps ``The case $e \nmid n+r+1$''?) We can handle the reference 3.3 -> this section near proposition 3.3, and perhaps even name 3.3 by it's name in this section.}
 \subsubsection{Proposition \ref{Trivial}}
@@
 See \ref{sub-matching example}.
-
-	If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, $\psi(a,b)$ will always refer to those nodes and they're matchings, though it may not be a sub-matching unless specified.
-For any other $a,b$, we define $\psi(a,b)$ to be an element of the representation with no nodes.
+  {\color{magenta} For anybody reading via paper or something not handling hrefs, it's better to refer to this as Figure \ref{sub-matching example}.}
+
+  {\color{magenta} use $\backslash$emph for emphasis (in this environment, it will be italicized)}
+
+  If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, {\color{magenta} for nodes $a,b$ satisfying $a \leq b$ (or $1 \leq a \leq b \leq 2n+r)$.}$\psi(a,b)$ will always refer to those nodes and they're {\color{magenta} their} matchings, though it may not be a sub-matching unless specified.{\color{magenta} No need to say ``unless specified''} For any other $a,b$, we define $\psi(a,b)$ to be an element of the representation with no nodes.{\color{magenta} What other $a,b$?
+Is this $a > b$, $a,b \notin \cbr{1,\dots,2n+r}$, etc?
+Also, can this just be defined the unique element of the zero representation?}
 
@@
 		\end{gathered}}$
-	\caption{$\psi\in M_6^0$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right. $\psi(3,6)=\sigma$. $\psi(2,5)$ is not a sub-matching.}
+	\caption{$\psi\in M_6^0$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right. $\psi(3,6)=\sigma$. 
+    {\color{magenta} and }
+  $\psi(2,5)$ is not a sub-matching.}
 	\label{sub-matching example}
@@
 
-Define the rainbow element $R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$.
-In other words, the basis element with all anchors to the left then a rainbow.
+Define the rainbow element 
+{\color{magenta} $\backslash$emph.} 
+$R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$. In other words, the basis element with all anchors to the left then a rainbow.
+{\color{magenta} to the left, followed by a ``rainbow'' on the right.}
 
 \begin{proposition}
-	Let $w$ be an arbitrary vector in $M_{2n+r}^r$. I claim that if $w\in \cap\text{ker}(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero.
-
+  Let $w$ be an arbitrary vector in $M_{2n+r}^r$.
+  {\color{magenta} No need to say ``arbitrary.''} 
+  I claim that if $w\in \cap\ker(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero. 
+  {\color{magenta} No need to say ``I claim.''}
 	\label{rainbow nonzero}
@@
 \begin{proof}
-	Let $Y$ be the set of basis elements with nonzero coordinate in $w$.
-Let $z$ be the greatest integer such that there exists $y\in Y$ where $y(1)-1=...=y(z)-z=0$, and let $U\subset Y$ be the set of such $y$.
+  Let $Y$ be the set of basis elements 
+  {\color{magenta} of $M_{2n + r}^r$} 
+  with nonzero coordinate in $w$. 
+  Let $z$ be the greatest integer such that there exists $y\in Y$ where 
+  {\color{magenta} some element $y \in Y$ satisfying\ldots} 
+  $y(1)-1=...=y(z)-z=0$, and let $U\subset Y$ be the set of such $y$. 
   In other words, $U$ is the set of basis elements in $Y$ which have the most anchors to the far left.
@@
 	Suppose $z<r$. 
-Then for each $y\in U$ there exists a minimal $i_y>z+2$ such that $y(i_y)=0$.
+  Then for each $y\in U$ there exists a minimal $i_y>z+2$ such that $y(i_y) =0$ 
+  {\color{magenta} $y(i_y) = i_y$, or just $y$ contains an anchor at $i_y$}. 
   In other words, $i_y$ is the position of the next leftmost anchor in $y$.
+  {\color{magenta} totally subjective, buy I would put a new paragraph here.}
+
   Fix $\tilde{y}$ such that $i_{\tilde{y}}\leq i_y$ for all $y$. 
-Then I claim the basis element $y':=q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}$ has nonzero coordinate in $(1+T_{i_{\tilde{y}}-1})w$, implying $w\not\in \cap\text{ker}(1+T_i)$.
+  {\color{magenta} Is this just some $\tilde y$ for each $y$?}
+  Then I claim the basis element $y':=q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}$ has nonzero coordinate in $(1+T_{i_{\tilde{y}}-1})w$, implying $w\not\in \cap\ker(1+T_i)$.
+  {\color{magenta} Rather than ``I claim\ldots to see this'', say something like ``We will show\ldots to do so''}
   To see this, we can show that $\tilde{y}$ is the only basis element in $Y$ such that $(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$.
 $y'$ still has $z$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$.
-If $x\in Y,\not\in U$, the basis element $x'$ proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$.
+  If $x\in Y,\not\in U$,
+  {\color{magenta} If $x \in Y$ and $x \not\in U$, then\ldots}
+  the basis element $x'$ proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$.
 If $x\in U$, $x'$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$.
@@
 So if $z<r$ $w$ is not in the desired kernel.
-
+  {\color{magenta} Nice.}
+
+  {\color{magenta} I think a very short vspace would be nice here.}
 	Suppose $z=r$ but $R\not\in U$ (so $R\not\in Y$).
-Let us define a sequence of subsets of $U$ in the following way: $U_0:=U$, $U_{i+1}:=\{u\in U_i| u(r+i+1)=2n+2r-i+1 \}$.
-Since $R\not\in U$, $\exists t<n-1$ such that $U_{t+1}=\emptyset$.
-Choose $\tilde{u}\in U_t$ such that $\tilde{u}(r+t+1)\geq u(r+t+1)$ for all $u\in U_t$.
-Consider the basis element $u':=q^{-1/2}(1+T_{\tilde{u}(r+t+1)})\tilde{u}$.
+  {\color{magenta} Doesn't $U$ just depend on $z$, so that $R \in U$ whenever $z=r$?}
+  Let us define a sequence of subsets of $U$ in the following way: $U_0:=U$, $U_{i+1}:=\{u\in U_i| u(r+i+1)=2n+2r-i+1 \}$. Since $R\not\in U$, $\exists t<n-1$ such that $U_{t+1}=\emptyset$. 
+  {\color{magenta} Don't need ``let us.''}
+  Choose $\tilde{u}\in U_t$ such that $\tilde{u}(r+t+1)\geq u(r+t+1)$ for all $u\in U_t$. Consider the basis element $u':=q^{-1/2}(1+T_{\tilde{u}(r+t+1)})\tilde{u}$.
+
+  {\color{magenta} No ``I claim.'' Also, I would put a new paragraph here, or after the next line (fair if you disagree). Also, maybe say that this is analogous to before.}
   I claim that $\tilde{u}$ is the only element in $Y$ such that $(1+T_{\tilde{u}(r+t+1)})\tilde{u}\sim u'$, again implying that $w$ is not in the desired kernel.
@@
 
+{\color{magenta} This might read better as ``Let $R_{r,i},R_{L_i}$ be the basis elements formed by ''moving.``
+Also, it may be nice to just define it formally and point to Figure \ref{shifted rainbow};
+the moving analogy is clear from the figure.
+}
 Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively.
-Examples are pictured in \ref{shifted rainbow}.
-Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.
+Examples are pictured in {\color{magenta} Figure \ref{shifted rainbow}}.
+Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.{\color{magenta} align might be nicef for these definitions}
 
@@
 		\end{gathered}}$
-	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right}
+	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right
+  {\color{magenta} The elements $R_{L,0},\dots,R_{L_3} \in W_8^0$ are\ldots}
+}
 	\label{shifted rainbow}
@@
 \begin{proposition}
-	Let $w$ be an element in the kernel intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation.
-Let $y$ be a basis element with coordinate $c$ in $w$.
+  Let $w$ be an element in the kernel 
+  {\color{magenta} probably good to refer to it as $K$, or remind the reader of the indices on $T$. Also, why the subscript $T_z$?
+  In general, we may shorten this to ``Let $w$ be an element in $K \subset M$'' to get down on the length of this proposition.
+}
+  intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation. Let $y$ be a basis element with coordinate $c$ in $w$. 
+  {\color{magenta} Better to say ``there exist'' for proposition statements.
+  Also, the reader probably knows what $R$ is by now? Maybe it's good to leave it in, idk, but this statement is already very wordy.
+}
   Suppose $\exists a,b$ such that $y(a,b)=R$, the rainbow element. 
+  {\color{magenta} If it's still too wordy, maybe move the definition of $\theta,\phi$ outside of the statement? Idk.}
   Define the basis elements $\theta_i,\phi_i$ by $\theta_i(1,a-1)=\phi(1,a-1)=y(1,a-1)$, $\theta_i(b+1,2n)=\phi(b+1,2n)=y(b+1,2n)$, $\theta_i(a,b)=R_{R,i}$, $\phi_i(a,b)=R_{L,i}$ (leave $\theta_i$ or $\phi_i$ undefined for any $i$ where $R_{R,i},R_{L,i}$ are undefined, respectively).
@@
 Proof of this proposition requires a simple algebraic fact that will be used throughout this document, so I state it as a lemma.
+{\color{magenta}We will use the following algebraic lemma\ldots.
+Also, the reader knows that you're stating it, no need to tell them.
+}
 
@@
 
-\textit{Proof of lemma.}
-
+\begin{proof}[Proof of lemma]
 \begin{align*}
@@
 \end{align*}
+\end{proof}
+
+{\color{magenta} Nice proof.
+Can be specified by using $\backslash$begin\{proof\}[Proof of lemma], as I've fixed in the text here.}
 
 Now let us prove the proposition.
+{\color{magenta} we will\ldots
+Guiding text may 
+}
 
@@
 The coordinate of $\phi_i$ in $(1+T_z)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_z)$.
-Specifically, it will be $(1+q)c\iota+(q^1/2)\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.
-
-	Let $n:=a+b-1$ and $r$ be the number of anchors in $y(a,b)$.
+Specifically, it will be $(1+q)c\iota+(q^{1/2})\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.
+  {\color{magenta} fixed exponent on $q^{1/2}$.}
+
+  Let $n:=a+b-1$ and {\color{magenta} let } $r$ be the number of anchors in $y(a,b)$.
 Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$.
-This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in \ref{shifted relations}.
+This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in {\color{magenta} Figure }\ref{shifted relations}.
   I claim the following:
-
+  {\color{magenta} Avoid ``I claim''}
+
+  {\color{magenta} put in claim* environment}
 	\begin{center}
@@
 
-	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in \ref{shifted relations}.
-Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition.
-Me note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
+  {\color{magenta} $\backslash$begin\{proof\}[Proof of claim], avoid ``let us'' throughout}
+
+	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$,
+  {\color{magenta} awkward wording}
+  as shown in 
+  {\color{magenta} Figure} 
+  \ref{shifted relations}. Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition. Me
+  {\color{magenta} typo} 
+  note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
 Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$.
@@
 Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case gives no new information.
-Lastly, note that our argument was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors.
-Thus the claim is proved.
-
-	Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction:
+Lastly, note that our argument
+  {\color{magenta} \ldots the above argument was \ldots and hence an analogous argument without anchors illustrates the $\theta_i$ case.}
+  was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors. Thus the claim is proved.
+	  {\color{magenta} three ideas for this:
+    first: break into smaller paragraphs.
+    Second: assign a variable to $a - 1 +  + n/2$ for clarity.
+    Third: here and elsewhere, when saying a dense statement, examine whether it's good to put an intuitive statement for it before, after, or if it's more clear/concise to not include it at all.
+  }
+
+  Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction
+  {\color{magenta} on $i$}:
 
@@
 
+  {\color{magenta} Suppose \ldots then,}
 	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$.
@@
 We are now ready to prove proposition \ref{Trivial}.
-
-\begin{proof}
-	Suppose $\cap\text{ker}(1+T_i)=K\not=0$.
+{\color{magenta} Restate the proposition. I will reference forward to this part.
+  Upon rereading this in the new structure, I actually do agree with you that we could just do away with Proof 2.
+  With the last batch of edits, this is so much more manageable and clear (and less technical) than I remembered it being.
+}
+
+\begin{proof}
+	Suppose $\cap\ker(1+T_i)=K\not=0$.
+  {\color{magenta} More usual to say $K := \cap \ker(1 + T_i) = 0$.}
   Take nonzero $w\in K$.
@@
 
+{\color{magenta} New name, such as ``Charactrizing $K$'' or ``Characterizing the sign subrepresentations.''
+Also, lowercase section titles.}
 \subsubsection{Kernel Basis}
@@
 	Let $M_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$.
-Let $w\in\cap\text{ker}(1+T_i)$.
+Let $w\in\cap\ker(1+T_i)$.
 MLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition \ref{rainbow nonzero}).
@@
 \begin{corollary}
-	Let $w\in\cap\text{ker}(1+T_i)$, $w\not=0$. Suppose $\psi(1,a)$ is a sub-matching with no anchors. Then:
+	Let $w\in\cap\ker(1+T_i)$, $w\not=0$. Suppose $\psi(1,a)$ is a sub-matching with no anchors. Then:
 
@@
 \begin{theorem}
-	Suppose $e=n+r+1$. Then $\cap\text{ker}(1+T_i)\not=0$.
+	Suppose $e=n+r+1$. Then $\cap\ker(1+T_i)\not=0$.
 	\label{kernel existence}

### 2019-07-30 tex/comments/2-nat-comments.tex
Fib revisions

@@
   \begin{definition}
-  Define a \emph{crossingless matching on $2n + r$ nodes and $r$ anchors} to be an isotopy class of $n + r$ nonintersecting paths in the slice $\RR \times \brk{0,1}$ connecting $2n + r$ disctinct points of $\RR \times \cbr{0}$ and $r$ points of $\RR \times \cbr{1}$ such that none of the latter points are conected.
+  Define a \emph{crossingless matching on $2n + r$ nodes and $r$ anchors} to be an isotopy class of $n + r$ non-intersecting paths in the slice $\RR \times \brk{0,1}$ connecting $2n + r$ distinct points of $\RR \times \cbr{0}$ and $r$ points of $\RR \times \cbr{1}$ such that none of the latter points are connected.
   Let $M_{2n + r}^r$ have basis given by these matchings.
@@
 
-  \begin{definition}
-  Let $V^m$ be the $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{n+1}$ such that the bit $\vs$ never appears twice consecutively. 
+  \begin{definition}\label{Fib definition}
+  Let $V^m$ be the $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{m+1}$ such that the bit $\vs$ never appears twice consecutively. 
   We will refer to $V^m$ as the \emph{Fibonacci representation} and suppress the superscript whenever it is clear from context.
@@
   We would also thank Professor Alexander Kleshchev for our helpful conversations concerning branching theorems.
-  Lastly, we would like to express our gratitude to our mentor Oron Propp for his help and advice in both acquiring background knowledge and in executing the mathematics in this paper;
+  Lastly, we would like to express our gratitude to our mentor Oron Propp for his help and advice in both acquiring background knowledge and in executing the mathematics in this paper, as well as his comments on early drafts of this paper;
   this project would not be possible without him.
@@
 \section{Fibonacci representations and quotients of Specht modules}\label{Fibonacci Section}
-We have difficulty characterizing the Specht module above when it is irreducible.
-We may instead attempt to characterize the irreducible quotient $D^\lambda$ of the Specht module.
-In particular, note that, whenever $e \leq r + 2$, the restriction $\Res D^{(n+r,n)}$ decomposes into a direct sum of partitions $(m+s,m)$ such that $e \leq s + 2$ and $2m + s = 2n + r - 1$.
-This forms a recurrence among these representations, allowing a combinatorial description of their dimension.
-In this section we henceforth assume $e = 5$ and note that this recurrence resembles the Fibonacci recurrence;
-we follow this to characterize the restriction $D^{(n+r,n)}$ with $r \leq 3$.
-
-\begin{remark}
-  Let $d_{m}^{0,3}$ be the dimension $\dim D^{(n,n)}$ with $2n = m$ when $m$ is even, and $\dim D^{(n+3,n)}$ with $2n + 3 = m$ when $m$ is odd.
-  Similarly define $d_m^{1,2}$.
-  Then, Corollary \ref{D Restrictions} gives
-  \begin{align*}
-    d_m^{0,3} &= d_{m-1}^{1,2}\\
+The irreducibility of $S^{(n+r,n)}$ is integral to arguments of Section \ref{Crossingless Matchings Section};
+without irreducibility of $M_{2n + r}^r$ (conjecturally equivalent to irreducibility of $S^{(n+r,n)}$), $M$ is not necessarily isomorphic to any Specht module $S^\lambda$ or quotient $D^\lambda$, preventing the arguments of Section \ref{Specht Modules Section} from being used.
+Further, when $S^{(n+r,n)}$ is reducible, we have $e \mid l$ for some $r+2 \leq l \leq n+r+1$, and hence the filtration provided in Proposition \ref{Filtration} fails to be a composition series.
+In summary, for $S^{(n+r,n)}$, nearly every argument in Sections \ref{Specht Modules Section} and \ref{Crossingless Matchings Section} break down, and hence it is difficult to characterize the Specht module $S^{(n+r,n)}$ via crossingless matchings.
+
+Due to these difficulties, we instead seek a graphical realization of the irreducible quotient $D^{(n+r,n)}$.
+In doing so, we may study their branching via Corollary \ref{D Restrictions}, which gives an interesting recurrence in their dimension. 
+\begin{example}
+Let $e = 5$. If $m$ is even, let $t$ be such that $2t = m$;
+if $m$ is odd, let $t'$ be such that $2t' + 3 = m$.
+Then, we may define the following quantity:
+\[
+  d_{m}^{0,3} := \begin{cases}
+    \dim D^{(t,t)} & \text{if } m \text{ is even,}\\
+    \dim D^{(t'+3,t')} & \text{if } m \text{ is odd.}
+  \end{cases}
+\]
+Define $d_m^{1,2}$ similarly.
+Then, by Corollary \ref{D Restrictions}, we have
+\begin{align*}
+    d_m^{0,3} &= d_{m-1}^{1,2},\\
     d_m^{1,2} &= d_{m-1}^{1,2} + d_{m-1}^{0,3}\\
-    &= d_{m-1}^{0,3} + d_{m-2}^{0,3}.
-  \end{align*}
-  Carefully following this and noting the base cases $d_2^{0,3} = d_2^{1,2} = 1$, one may note that this recurrences proves that $d_m^{1,2} = d_{m+1}^{0,3} = f_n$, where $f_n$ is the $n$th \emph{Fibonacci number}.
-  This matches the dimension our Fibonacci subrepresentations, motivating their definition.\qed
-\end{remark}
-
-We can start our study of $V$ by studying low-dimensional cases.
-First, note that $V_{\vs\vp}^2$ is the sign representation $D^{(1^2)}$ and $V_{\vs\vp}^2$ is the trivial representation $D^{(2)}$.
-
-$V_{\vp\vp}^2$ is a 2-dimensional representation of a semisimple commutative algebra, and hence decomposes into a direct sum of two subrepresentations.
-In particular, we can use the basis $\cbr{(\vp\vs\vp),(\vp\vp\vp)}$ and explicitly write the matrix
+    &= d_{m-1}^{1,2} + d_{m-2}^{1,2}.
+\end{align*}
+Further, by lemma \ref{Base cases}, we have that $d_2^{0,3} = d_3^{1,2} = 1$;
+hence $d_m^{1,2} = d_{m+1}^{0,3} = f_m$, where $f_m$ is the $n$th \emph{Fibonacci number}.
+\end{example}
+
+In this section, we henceforth restrict to the case $e = 5$ and $r \leq 3$.
+We note that Shor--Jordan have conveniently used complex representations of the braid group on $m$ letters in \cite{Shor} having dimension $f_m$ and $f_{m-1}$.
+We have rescaled these representations, called subrepresentations of the \emph{Fibonacci representation} in Definition \ref{Fib definition}, in order to satisfy the quadratic relation of $\SH$, and we have otherwise modified them to to fit a general parameter $q$ and field $k$ having $e = 5$.
+
+Note that, Shor--Jordan does not characterize this representation any more than the definition and decomposition into four subrepresentations;
+we will give a characterization of this representation which is stronger than presented in \cite{Shor}.
+
+We will start our study of the Fibonacci representation $V := V^m$ by studying low-dimensional cases.
+Recall that we have decomposed $V$ into a direct sum of the subrepresentations $V_{\vs\vs}$, $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$, indexed by the first and last bit of the basis.
+\begin{proposition}
+  We have the following isomorphisms of representations:
+  \begin{align*}
+    V_{\vs\vs}^2 &\simeq D^{(1^2)}\\
+    V_{\vs\vp}^2 &\simeq D^{(2)}\\
+    V_{\vp\vp}^2 &\simeq V_{\vs\vs}^2 \oplus V_{\vs\vp}.
+  \end{align*}
+\end{proposition}
+\begin{proof}
+  The first isomorphism follows via identification with the trivial representation, and the second with the sign representation.
+
+  Further, $V_{\vp\vp}^2$ is a 2-dimensional representation of a semisimple commutative algebra, and hence decomposes into a direct sum of two 1-dimensional subrepresentations.
+  In particular, we may fix basis $\cbr{(\vp\vs\vp),(\vp\vp\vp)}$ for $V_{\vp\vp}^2$ and note that $T_1$ acts by the matrix
   \[
@@
       \vard & \vare
-  \end{bmatrix}
-\]
-having characteristic polynomial $(\varc - \lambda)(\vare - \lambda) - \vard^2 = \lambda^2 - (\varc + \vare)\lambda +(\varc\vare - \vard^2)$.
+    \end{bmatrix},
+  \]
+  which has characteristic polynomial \[\lambda^2 - (\varc + \vare)\lambda +(\varc\vare - \vard^2).\]
   We may verify that, for $\lambda = -1$, this evaluates to
   \[
-  -((-1 + q + q^2) (1 + q^3 + q^4 + q^5 + 2 q^6 + q^7))\brk{5}_q = 0
+    -((-1 + q + q^2) (1 + q^3 + q^4 + q^5 + 2 q^6 + q^7))\brk{5}_q = 0,
   \]
@@
   \[
--(q^2 (-1 + q + q^2) (1 + q + q^2 + q^3 + 2 q^4 + q^5)) \brk{5}_q = 0
-\]
-hence $\rho_{T_1}$ has eigenvalues $-1$ and $q$.
-
-The eigenspaces with eigenvalues $-1$ and $q$ are subrepresentations isomorphic to the sign and trivial representation, hence $V_{\vp\vp}$ is isomorphic to a direct sum of the trivial and sign representations: $V^2_{\vp\vp} \simeq V^2_{\vs\vp} \oplus V^2_{\vs\vs}$.
-
-Now we may prove that $V^3_{\vs\vp}$ is irreducible;
-this has basis $\cbr{\prn{\vs\vp\vs\vp}, \prn{\vs\vp\vp\vp}}$, and the following matrices:
+  -(q^2 (-1 + q + q^2) (1 + q + q^2 + q^3 + 2 q^4 + q^5)) \brk{5}_q = 0.
+  \]
+  Hence $\rho_{T_1}$ has eigenvalues $-1$ and $q$.
+
+  The eigenspaces with eigenvalues $-1$ and $q$ are subrepresentations isomorphic to the sign and trivial representation, hence $V_{\vp\vp}$ is isomorphic to a direct sum of the trivial and sign representations, as required.
+\end{proof}
+
+We may further study the low-dimensional Fibonacci representations with the following proposition:
+\begin{proposition}
+  The representation $V^3_{\vs\vp}$ is irreducible.
+\end{proposition}
+\begin{proof}
+  Fix the basis $\cbr{\prn{\vs\vp\vs\vp}, \prn{\vs\vp\vp\vp}}$ for $V^3_{\vs\vp}$.
+  Then, $T_1$ and $T_2$ act by the following matrices:
 \[
@@
   Hence $V^3_{\vs\vp}$ is irreducible.
-
-These establish the low-dimensional behavior that we will use as base cases below.
-The rest of this section will proceed first by proving that $V_{\vs\vp}$ and $V_{\vs\vs}$ are irreducible;
-then, we will use combinatorial arguments to prove that these are isomorphic to the correct two-row Specht module quotients.
-
-\begin{proposition}
-  The representation $V_{\vs\vp} := V^m_{\vs\vp}$ is irreducible.
+\end{proof}
+
+These propositions establish the low-dimensional behavior of $V^m$ that we will use in our analysis of general $V^m$ below.
+We will proceed first by proving that $V^m_{\vs\vp}$ and $V^m_{\vs\vs}$ are irreducible;
+then, we will use combinatorial arguments to prove that these are isomorphic to the desired irreducible quotients two-row Specht modules.
+
+\begin{proposition}\label{Fib irreducibility}
+  The representation $V^m_{\vs\vp}$ is irreducible.
 \end{proposition}
@@
   Let $\cbr{v_i}$ be the basis for $V_{\vs\vp}$.
-  Then, each $v_i$ is cyclic; indeed, we can transform every basis vector into $(\vs\vp \dots \vp)$ by multiplying by the appropriate $\frac{1}{\vard-\varc}(T_i - \varc)$, and we can transform $(\vs\vp \dots \vp)$ into any basis vector by multiplying be the appropriate $\frac{1}{\vard-\vare}(T_i - \vare)$.
-  Hence it is sufficient to show that each $v \in V_{\vs\vp}$ generate some basis element.
-
-  Let $v'$ be the basis element $(\vs\vp\vs\vp\dots \vp)$, which is many copies of $\vs\vp$, followed by an extra $\vp$ if $m$ is odd.
-  We will show that each $v \in F$ generates $v'$.
-
-  Suppose that no elements beginning $(\vs\vp\vs\vp)$ are represented in $v_i$;
-  then, all such elements are represented in $T_3v$, so we may assume that at least one is represented in $v$.
-
-  Note that $\ima (T_2 - \vara) = \Span\cbr{\text{Basis vectors beginning }(\vs\vp\vs\vp)}$ and $(T_2 - \vara)v \neq 0$.
-  Further, note that $\Res_{\SH(S_{m-2})}^{\SH(S_m)} \ima (T_2 - \vara) \simeq V^{m-2}_{\vs\vp}$ as representations.
-  Hence irreducibility of $V^{m-2}_{\vs\vp}$ implies that $v'$ is generated by $(T_2 - \vara)v$, and $V^m_{\vs\vp}$ is irreducible.
-\end{proof}
-
-Now, we may begin considering restrictions:
-\begin{lemma}
+  Then each $v_i$ is cyclic; indeed, we can transform every basis vector into $(\vs\vp \dots \vp)$ via action by the appropriate $\frac{1}{\vard}(T_i - \varc)$, and we can transform $(\vs\vp \dots \vp)$ into any basis vector by multiplying be the appropriate $\frac{1}{\vard}(T_i - \vare)$.
+  Hence it is sufficient to show that each $v \in V_{\vs\vp}$ generates some basis element.
+
+  Let $v_j$ be the basis element $(\vs\vp\vs\vp\dots \vp)$, which is many copies of $\vs\vp$, followed by an extra $\vp$ if $m$ is odd.
+  We will show that each $v \in V^m_{\vs\vp}$ generates $v_j$.
+  Then, we will have
+
+  Suppose that no basis elements beginning $(\vs\vp\vs\vp)$ have nonzero coefficient in $v$;
+  then, there is some basis element $v_i$ beginning $(\vs\vp\vp\vp)$ having nonzero coefficient in $v$, and the basis element having all other bits identical to $v_i$ except for beginning $(\vs\vp\vs\vp)$ has nonzero coefficient in $T_3v$.
+  Hence we may assume that at least one element beginning $(\vs\vp\vs\vp)$ has nonzero coefficient in $v$.
+
+  Note that \[\ima (T_1 - \vara) = \Span\cbr{\text{Basis vectors beginning }(\vs\vp\vs\vp)}\] and $(T_1 - \vara)v \neq 0$.
+  Further, note that we may consider $\ima (T_1 - \vara)$ to be a subrepresentation of $\Res_{\SH(S_{m-2})}^{\SH(S_m)} V^m_{\vs\vp}$;
+  this yields that $\ima (T_1 - \vara) \simeq V^{m-2}_{\vs\vp}$ as representations.
+  Hence irreducibility of $V^{m-2}_{\vs\vp}$ implies that $v_j$ is generated by $(T_1 - \vara)v$, and $v$ is cyclic, as desired.
+\end{proof}
+
+Note that the structure of this proof is parallel to the structure of Theorem \ref{Irreducibility Theorem}:
+we project down to the analogous representation on fewer letters, and we inductively lift irreducibility from this smaller representation to our original one.
+
+Now we may begin considering restrictions of Fibonacci representations:
+\begin{lemma}\label{Fib branching}
   The following branching rules hold:
   \begin{align*}
-    V^{m-1}_{\vp\vp} \simeq \Res V_{\vs\vp}^m &\simeq V^{m-1}_{\vs\vs} \oplus V^{m-1}_{\vs\vp}\\
-    \Res V_{\vs\vs}^m &\simeq V_{\vs\vp}^{m-1}.
+    V^{m-1}_{\vp\vp} \simeq \Res V_{\vs\vp}^m &\simeq V^{m-1}_{\vs\vs} \oplus V^{m-1}_{\vs\vp},\\
+    V_{\vp\vs}^{m-1} \simeq \Res V_{\vs\vs}^m &\simeq V_{\vs\vp}^{m-1}.
   \end{align*}
@@
 \begin{proof}
-  The first line follows by considering the last two $m-2$ transpositions for the left isomorphism, then the first two for the right isomorphism.
-  This is well-behaved by Appendix \ref{Algebra}.
-
-  Similarly, the second line follows by considering the last $m-2$ transpositions.
-\end{proof}
-This immediately gives a rather strong characterization of $V$.
+  By the results of Appendix \ref{Algebra}, any two restrictions to distinct subalgebras of $\SH$ generated each by $m-2$ characters are isomorphic.
+  Hence the leftmost isomorphism on each line follows by considering the restrictions to the subalgebra of $\SH$ generated by $\cbr{T_2,\dots,T_{m-1}}$.
+  Further, the rightmost isomorphism on each line follows by considering the restrictions to the subalgebra of $\SH$ generated by $\cbr{T_1,\dots,T_{m-2}}$.
+\end{proof}
 \begin{corollary}
-  The representation $V_{\vs\vs}$ is irreducible.\qed
+  The representation $V^m_{\vs\vs}$ is irreducible.\qed
 \end{corollary}
+\begin{proof}
+  By Lemma \ref{Fib branching} and Proposition \ref{Fib irreducibility}, we have $\Res V^m_{\vs\vs} \simeq V^{m-1}_{\vs\vp}$ is irreducible, implying that $V^m_{\vs\vs}$ is also irreducible.
+\end{proof}
+Recall the decomposition $V^m \simeq V^m_{\vs\vs} \oplus V^m_{\vs\vp} \oplus V^m_{\vp\vs} \oplus V^m_{\vp\vp}$.
+Using this, we may now decompose $V$ into a direct sum of irreducible representations.
 \begin{corollary}
-  The representation $V$ decomposes into a direct sum of irreducible representations as follows:
-  \[
-    V \simeq 3V_{\vs\vp} \oplus 2V_{\vs\vs}.
+  The representation $V^m$ decomposes into a direct sum of irreducible representations as follows:
+  \[
+    V^m \simeq 3V^m_{\vs\vp} \oplus 2V^m_{\vs\vs}.
   \]\qed
@@
 
-Now we may use these in order to apply Young Tableau to characterize $V$.
+Now we may use these in order to characterize $V$ via irreducible quotients of Specht modules.
 \begin{theorem}\label{Fibonacci Theorem}
-  The irreducible components of $V$ are given by the following isomorphisms:
-     \begin{align*}  
-      V^{2n}_{\vs\vs} &\simeq D^{(n,n)}\\ 
-      V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)}\\
-      V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)}\\
+  We have the following isomorphisms:
+     \begin{align*}  
+      V^{2n}_{\vs\vs} &\simeq D^{(n,n)},\\ 
+      V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)},\\
+      V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)},\\
       V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)}.
@@
 \begin{proof}
-  We will prove this by induction on $n$;
+  We will prove this by induction on $m = 2n$;
   we have already proven the base case $V^{2}$, so suppose that we have proven these isomorphisms for $V^{2n-2}$.
@@
 
-  By irreducibility, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\mu}$ for some diagrams $\lambda$ and $\mu$.
+  By Proposition \ref{Fib irreducibility}, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\mu}$ for some diagrams $\lambda$ and $\mu$.
   We will show that $\lambda = (n+1,n-2)$ and $\mu = (n+1,n-1)$.
 
-  First, note that we have \[\Res \; D^{\lambda} \simeq D^{(n,n-2)} \simeq \Res \; D^{(n+1,n-2)}\] and \[\Res \; D^{\mu} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)}.\]
-
-  By irreducibility of $\Res D^{\lambda}$, the only normal number in $\lambda$ is 1.
-  Further, the only tableaux which can remove a cell to yield $D^{(n,n-2)}$ are $(n+1,n-2)$, $(n,n-1)$, and $(n,n-2,1)$ as illustrated in Figure \ref{OddRes};
-  we have already seen that $D^{(n,n-1)}$ does not have irreducible restriction, so we are left with $(n+1,n-2)$ and $\varsigma = (n,n-2,1)$.
-  We may directly check that $\varsigma$ doesn't satisfy this, as we have the following:
-  \begin{align*} 
-    \beta_\varsigma(1,2) &= 3 - 2 + (n-2) = n-1\\
-    \beta_\varsigma(1,3) &= 3 - 1 + n = n+2\\
+  First, by Lemma \ref{Fib branching} and the inductive hypothesis, we have \[\Res \; D^{\lambda} \simeq D^{(n,n-2)} \simeq \Res \; D^{(n+1,n-2)}\] and \[\Res \; D^{\mu} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)}.\]
+
+  By irreducibility of $\Res D^{\lambda}$, the only normal number in $\lambda$ is 1.\cite{Kleshchev,Brundan}
+  Further, the only diagrams which can be transformed into $(n,n-2)$ by removing a cell are $(n+1,n-2)$, $(n,n-1)$, and $(n,n-2,1)$ as illustrated in Figure \ref{OddRes};
+  we have already seen that $D^{(n,n-1)}$ does not have irreducible restriction via Corollary \ref{D Restrictions}, so we are left with $(n+1,n-2)$ and $\varsigma := (n,n-2,1)$.
+  We may directly check that $\varsigma$ doesn't satisfy this, as we have
+  \begin{align*} 
+    \beta_\varsigma(1,2) &= 3 - 2 + (n-2) = n-1,\\
+    \beta_\varsigma(1,3) &= 3 - 1 + n = n+2,\\
     \beta_\varsigma(2,3) &= 2 - 1 + 3 = 4.
    \end{align*} 
-  At least one of $\beta_\varsigma(1,2)$ and $\beta_\varsigma(1,3)$ is nonzero, since $\beta_\varsigma(1,3) - \beta_\varsigma(1,2) = 3 \not\equiv 0 \pmod e$, and hence at least one of $M_2$ and $M_3$ is empty.
+  At least one of $\beta_\varsigma(1,2)$ and $\beta_\varsigma(1,3)$ is nonzero, since $\beta_\varsigma(1,3) - \beta_\varsigma(1,2) = 3 \not\equiv 0 \pmod e$.
   Hence at least one of 2 or 3 is normal in $\varsigma$, and $\lambda = (n+1,n-2)$.
@@
       \caption{
-      Illustration of the partitions of $9$ which can, via row removal, yield $(n,n-2)$ alone, or both $(n,n-2)$ and $(n-1,n-1)$.
+      Illustration of the partitions of $9$ which can, via removal of cells, yield $(n,n-2)$ alone, or both $(n,n-2)$ and $(n-1,n-1)$.
     }\label{OddRes}
@@
 
-  We can perform a similar argument for the $V^{2n}$ case, finding now that 
+  We can perform a similar argument for the $V^{2n}$ case;
+  for $V^{2n}_{\vs\vs} \simeq D^{\lambda'}$ and $V^{2n}_{\vs\vp} \simeq D^{\mu'}$, we have
   \[\Res \; D^{\lambda'} \simeq D^{(n,n-1)} \simeq \Res \; D^{(n,n)}\] and 
@@
   \begin{align*} 
-    V^{2n} &\simeq 3D^{(n+1,n-1)} \oplus 2D^{(n,n)}\\
-    V^{2n - 1} &\simeq 3D^{(n,n-1)} \oplus 2D^{(n+1,n-2)}
+    V^{2n} &\simeq 3D^{(n+1,n-1)} \oplus 2D^{(n,n)},\\
+    V^{2n - 1} &\simeq 3D^{(n,n-1)} \oplus 2D^{(n+1,n-2).}
   \end{align*}
 \end{corollary}
+
+Hence we have entirely characterized Shor--Jordan's Fibonacci representation \cite{Shor} as a direct sum of irreducible quotients of Specht modules, and we have given graphical realizations of $D^{(n+r,n)}$ for $e = 5$ and $r \leq 3$.
 
@@
 
-\bibliographystyle{numeric} 
+\bibliographystyle{plain} 
  \bibliography{../RepBib}

### 2019-07-30 tex/comments/2-miles-comments.tex

--- 2019-07-30 tex/Drafts/Draft-2.tex
@@
    \begin{titlepage}
+   	{\color{red!80!green} Miles commments in reddish}
     \maketitle
@@
   It is a classical result that $\SH$ is semisimple precisely when $e > 2n + r$, in which case the irreducible representations of $\SH$ are given by \emph{Specht modules} $S^\lambda$, which are indexed by the partitions $\lambda$ of $2n + r$.
+{\color{red!80!green} should specific that $S^\lambda$ are defined for $\SH$ not semisimple, and that the following references the general case}
    Further, $\SH$ admits a cellular basis with cell modules given by $S^\lambda$.
@@
   Let the length of an arc $(i,j)$ be $j - i + 1$.
+  {\color{red!80!green} you haven't defined "arc" yet.
+You also haven't numbered the points.
+You will need to do this anyway to define the operation.
+Something like "enumerate the points $1,...,2n+r\in \RR\times\{0\}$ from left to right.
+Define the \emph{arc} $(i,j)$ to be the path connecting points $i,j$ if it exists.
+Let the length of an arc $(i,j)$ be $j-i+1$.}
 
@@
   Additionally, we will prove that $M_{2n + r}^r$ is irreducible everywhere that $e > n$ and $S^{(n+r,n)}$ is irreducible.
-  We will conjecture that $M_{2n + r}^r \simeq S^{(n+r,n)}$ with $e$ unrestricted as well.
+  We will conjecture that $M_{2n + r}^r \simeq S^{(n+r,n)}$ with $e$ unrestricted as well {\color{red!80!green} and give some heuristic evidence}.
 
   This proves a graphical characterization of $S^\lambda$ in many cases, and hence $D^\lambda$ in the cases where $S^\lambda \simeq D^\lambda$.
-  However, the representation theory of $\SH$ is tied to the modules $D^\lambda$ even in cases where $S^\lambda$ is not irreducible;
+  However, the representation theory of $\SH$ is tied to the modules $D^\lambda$ even in cases where $S^\lambda$ is not irreducible {\color{red!80!green} I don't think this first part is necessary.
+You defined the representation theory of $\SH$ in terms of $D^\lambda$ for reducible cases, so its just confusing to state that it matters here.
+Maybe just mention that this is a case where $S^\lambda \neq D^\lambda$.};
   we will present a characterization of the module $D^{(n+r,n)}$ when $e = 5$ and $r \leq 3$.
@@
   Now suppose that $e = 5$ and $k$ contains the algebraic number $\sqrt{q + q^4}$ for reasons which will be apparent soon.
-  For convenience set $m := 2n + 4$.
+  For convenience set $m := 2n + 4${\color{red!80!green} typo, $2n+r$}.
   The following is a modification of Shor--Jordan's Fibonacci representation of the braid group.\cite{Shor}
@@
   \begin{definition}
-  Let $V^m$ be the $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{n+1}$ such that the bit $\vs$ never appears twice consecutively. 
+  Let $V^m$ be the $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{n+1}${\color{red!80!green}Typo, $m$ not $n$} such that the bit $\vs$ never appears twice consecutively. 
   We will refer to $V^m$ as the \emph{Fibonacci representation} and suppress the superscript whenever it is clear from context.
@@
   \end{equation}
-  with $T_i$ acting similarly on the substring $i,i+1,i+2$.
+  with $T_i$ acting similarly {\color{red!80!green}analogously/ identically/ in an identical manner? similarly seems to imply the operation isn't exactly the same} on the substring $i,i+1,i+2$.
   We will verify that this is a representation of $\SH$ in Appendix \ref{Fib Relations}
@@
   In Section \ref{Specht Modules Section} we give corollaries to standard theorems concerning Specht modules.
-  First, James-Mathas provides a sharp characterization of the irreducibility $S^\lambda$ for $\lambda \vdash 2n + r$ which is $e$-regular, called the \emph{Carter criterion}.\cite{Mathas-book}
+  First, James-Mathas provides a sharp characterization of the irreducibility {\color{red!80!green} of} $S^\lambda$ for $\lambda \vdash 2n + r$ which is $e$-regular, called the \emph{Carter criterion}.\cite{Mathas-book}
   We specialize this to the case that $\lambda = (n+r,n)$ to give a combinatorial condition for irreducibility of $S^{(n+r,n)}$.
@@
   using irreducibility, this becomes a composition series, and an inductive argument combined with the branching of Section \ref{Specht Modules Section} allow us to prove the following:
+  {\color{red!80!green}This whole paragraph seems a bit vague and technical.
+I think it would help to just skip some steps here.
+What do you think of something like "We then use an inductive argument based on the correspondence of composition series of $S^{(n+r,n)}$ and $M^r_{2n+r}$ to prove the following:"}
+
   \begingroup
@@
   \endgroup
-  Last, we finish the section by proving more general statements concerning sign subrepresentations of $M$, which contribute to conjectures later in the paper.{\color{orange} Fill in with specific information later.}
+  Last, we finish the section by proving more general statements concerning sign subrepresentations of $M$, which contribute to conjectures later in the paper.{\color{orange} Fill in with specific information later.} {\color{red!80!green} Maybe just "Lastly, we given an explicit basis for the sign subrepresentation of $M_{2n+r}^r$ when $e=n+r+1$"}
 
@@
   In Section \ref{Fibonacci Section}, we begin by establishing isomorphisms as in \ref{Fibonacci Theorem} for the subrepresentations of $V^2$, as well as irreducibility of $V^3_{\vs\vp}$.
-  We then use these cases to prove that $V^m_{\vs\vp}$ is irreducibile for all $m$, which implies that that $V^m_{\vs\vs}$ is irreducible.
+  We then use these cases to prove that $V^m_{\vs\vp}$ is irreducibile for all $m$, which implies that that $V^m_{\vs\vs}$ is irreducible.{\color{red!80!green} Maybe instead of implies just say you proved theyre both irreducible for all $m$.
+At this point, the implication is not clear, and I don't think specifying it is helpful for outlining the general structure of this section}
   From this, we inductively prove the following theorem:
@@
 \section{Preliminaries on Specht modules}\label{Specht Modules Section}
-  For this section and the rest of the paper, assume $n > 0$.
+  For this section and the rest of the paper, assume $n > 0$ {\color{red!80!green} with the exception of section (kernel)}.
 
@@
   identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
-  Identify each of these with a subset $\brk \lambda \subset \NN^2$ as in \cite{Kleshchev}, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.
+  Identify each of these with a subset $\brk \lambda \subset \NN^2$ as in \cite{Kleshchev}, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row {\color{red!80!green} column?} removed.
   Say that $\lambda$ is \emph{$e$-regular} if $\lambda_i - \lambda_{i+1} < e$ for all $i$ and $\lambda_l < e$.
@@
   \]
+
+  {\color{red!80!green} typo above}
   Lastly, let $h_{ab}^\lambda$ be the hook length of node $(a,b)$ in $\brk \lambda$ as defined in \cite{Kleshchev}.
@@
   The following statements, collectively known as \emph{modular branching rules} of $D^\lambda$, were originally written by Kleshchev for Specht modules of the group algebra $k\brk{S_n}$, then generalized to the Hecke algebra case by Brundan.\cite{Kleshchev,Brundan}
-  They entirely characterize the socle of $\Res D^\lambda$, as well as semisimplicity od $\Res D^\lambda$.
+  They entirely characterize the socle of $\Res D^\lambda$, as well as semisimplicity od {\color{red!80!green} of} $\Res D^\lambda$.
   \begin{theorem}[Kleshchev-Brundan]
@@
     \]
+
+    {\color{red!80!green}TYPO above}
     Further, when $e \nmid r$ or $e \mid r + 2$, $\Res D^{(n+r,n)}$ is semisimple.

### 2019-07-31 tex/comments/2-nat-comments.tex
Introduction revisions part 2, electric boogaloo

@@
   \usepackage{../RepStyle} 
+  \usepackage{../NatMacros}
   % Colors links
@@
   urlcolor=blue}
-
-  \usepackage{../NatMacros}
+  \def\thmcolor{black!60!orange}
 
@@
 \section{Introduction} 
-  Let $S_{2n+r}$ be the symmetric group on $2n+r$ letters with $2n + r \geq 2$, let $\SH := \SH_{k,q}(S_{2n+r})$ be the corresponding Hecke algebra over a field $k$ with parameter $q \in k^\times$ having a fixed square root $q^{1/2}$, and let $\cbr{T_i}$ be the simple reflections generating $\SH$.
+  Let $S_{2n+r}$ be the symmetric group on $2n+r$ letters with $2n + r \geq 2$.
+  Let $\SH := \SH_{k,q}(S_{2n+r})$ be the corresponding Iwahori-Hecke algebra (henceforth simply Hecke algebra) over a field $k$ with parameter $q \in k^\times$ having a fixed square root $q^{1/2}$.
+  Let $\cbr{T_1,\dots,T_{2n + r - 1}}$ be the simple reflections generating $\SH$.
 
@@
   hence the representation theory of $\SH$ generalizes the representation theory of the symmetric group.
-  The Hecke algebra is also well known to be connected to the representation theory of the general linear group over a finite field.\cite{Mathas-book}
-
+  The Hecke algebra is also well-known to be connected to the representation theory of the general linear group over a finite field \cite{Mathas-book}.
   It is a classical result that $\SH$ is semisimple precisely when $e > 2n + r$, in which case the irreducible representations of $\SH$ are given by \emph{Specht modules} $S^\lambda$, which are indexed by the partitions $\lambda$ of $2n + r$.
-  Further, $\SH$ admits a cellular basis with cell modules given by $S^\lambda$.
-  In particular, these admit quotients $D^\lambda$ such that the set $\cbr{D^\lambda \mid D^\lambda \neq 0, \lambda \vdash n}$ is a complete set of pairwise-nonisomorphic irreducible $\SH$-modules.
-  This set is indexed by the partitions $\lambda \vdash n$ which are $e$-restricted.\cite{Murphy1,Murphy2}
+
+  For all $e$, $\SH$ admits a cellular basis with cell modules given by $S^\lambda$.
+  In particular, these admit quotients $D^\lambda$ such that the modules $\cbr{D^\lambda \mid D^\lambda \neq 0, \lambda \vdash n}$ are a pairwise-nonisomorphic list of all irreducible $\SH$-modules.
+  This set is indexed by the partitions $\lambda \vdash n$ which are $e$-restricted \cite{Murphy1,Murphy2}.
 
   These representations $D^\lambda$ have explicit constructions, but many of their properties are unknown.
-  For instance, the dimension of these modules is unknown outside of some special cases.\cite{Mathas-book}
-  However, there does exist an algorithm due to Lascoux--Leclerc--Thibon--Ariki which computes the decomposition matrices of the Iwahori--Hecke Algebra $\SH_{\CC,q}(S_{2n + r})$ for $q$ an $e$th root of unity.\cite{LLT,Ariki}
-
-  The cellular basis for $S^\lambda$ and associated construction for $D^\lambda$ tend to be complicated and often computationally intractable.
-  We aim to give simple graphical realizations of $S^\lambda$ and $D^\lambda$ in some cases that $\lambda = (n+r,n)$.
-  These realizations expose the structure of irreducibility and branching in an intuitive and computationally simple way.
+  For instance, the dimension of $D^\lambda$ is unknown outside of some special cases \cite{Mathas-book}.
+  However, there does exist an algorithm due to Lascoux--Leclerc--Thibon--Ariki which computes the decomposition matrices of the Specht modules of the Hecke algebra $\SH_{\CC,q}(S_{2n + r})$ for $q$ an $e$th root of unity \cite{LLT,Ariki}.
+
+  The cellular basis for $S^\lambda$ and associated basis for $D^\lambda$ are complicated and often computationally intractable.
+  We aim to give simple graphical realizations of $S^\lambda$ and $D^\lambda$ in some cases that $\lambda = (n+r,n)$ is a partition of two parts.
+  These realizations behave in an intuitive and computationally simple way.
 
   \vspace{5pt}
-  Note that we follow the convention of Murphy and Kleshchev, which is dual to the conventions of Dipper, James, and Mathas;
+  Throughout this paper, we analyze the \emph{two-row partitions} $(n+r,n) \vdash 2n + r$ and their corresponding modules $S^{(n+r,n)}$ and $D^{(n+r,n)}$.
+  \begin{remark}
+    Note that we follow the convention of Murphy--Kleshchev concerning the correspondence $\lambda \leftrightarrow S^\lambda$, which is dual to the conventions of Dipper--James--Mathas;
     one may translate our results to the latter convention by transposing all partitions.\cite{Kleshchev,Mathas-book,Murphy1} 
-
-  Throughout this paper, we analyze the \emph{two-row partitions} $(n+r,n) \vdash 2n + r$ and their corresponding modules $S^{(n+r,n)}$ and $D^{(n+r,n)}$.
+    For instance, we refer to the \emph{sign representation} as $S^{(1^{2n + r})}$.
+  \end{remark}
+
+  Our first approach uses crossingless matchings, originally defined by Khovanov \cite{Khovanov}, to realize irreducible Specht modules of two-row partitions.
 
   \fakesubsection{Crossingless matchings}
-  The following definition modifies the crossingless matchings defined by Khovanov.\cite{Khovanov}
+  {\color{orange} Literature goes here.}
 
@@
 
+  Order the points on $\RR \times \cbr{0}$ via the order $<$ on $\RR$, and refer to these as \emph{nodes}.
+  Refer to a path connecting the $a$th and $b$th node as an \emph{arc} $(a,b)$, and refer to a path connecting node $a$ to a point in $\RR \times \cbr{1}$ as an \emph{anchor}.
   Let the length of an arc $(i,j)$ be $j - i + 1$.
 
-  We endow $M_{2n + r}^r$ with an action by specifying $(1 + T_i)w_j$ for some basis element $w_j$ of $M_{2n + r}$.
-  We do so by concatenating in ``vertical lines'' below each point other than the $i$th and $i+1$st, concatenating paths between the $i$th and $i+1$st points as well as points below them, removing any ``loops'' this forms, and taking isotopy to some matching $w_l$ if possible;
-  if this is not possible, then there are anchors at $i,i+1$ and we set $(1 + T_i)w_j := 0$;
-  if this is possible and there is a ``loop,'' set $(1 + T_i)w_j := (1 + q)w_j$ and otherwise set $(1 + T_i)w_j := q^{1/2}w_l$.
-  This action is illustrated in Figure \ref{Action}, and we verify that this is well-defined in Appendix \ref{Cross Relations}.
+  We endow $M_{2n + r}^r$ with an action by specifying $(1 + T_i)w_j$ for any basis element $w_j$ of $M_{2n + r}$, as illustrated in Figure \ref{Action}.
+  We do so by concatenating in ``vertical lines'' below each point other than the $i$th and $(i+1)$st, concatenating paths between the $i$th and $(i+1)$st points as well as points below them, removing any ``loops'' this forms, and taking the isotopy class of the resultant diagram;
+  if this is not the isotopy class of a crossingless matching, then there are anchors at $i,i+1$ and we set $(1 + T_i)w_j := 0$;
+  if this is the isotopy class of a crossingless matching $w_l$ and there is a ``loop,'' set $(1 + T_i)w_j := (1 + q)w_j$ and otherwise set $(1 + T_i)w_j := q^{1/2}w_l$.
+
+  A more explicit definition is given in Appendix \ref{Explicit Definition} and we verify that this is well-defined in Appendix \ref{Cross Relations}.
   \end{definition}
-  \begin{figure} 
+  \begin{figure}[b] 
     \def\cbasisspacing{5mm}
@@
     \caption{Illustration of the actions $(1 + T_i)w_{\abs{M^2_6}}$.
-      In general, we act by deleting loops, isotoping onto a new crossingless matching, and scaling by either $q^{1/2}$, $(q + 1)$, or 0.
+      In general, we act by deleting loops, taking an isotopy onto a new crossingless matching, and scaling by either $q^{1/2}$, $(q + 1)$, or 0.
     }
@@
 
-  Note that the representations $M_{0 + r}^r$ and $S^{(r)}$ are isomorphic to the sign representation.
-  In fact, we will prove that $M_{2n + r}^r \simeq S^{(n+r,n)}$ whenever $e > n + r + 1$.
-  Additionally, we will prove that $M_{2n + r}^r$ is irreducible everywhere that $e > n$ and $S^{(n+r,n)}$ is irreducible.
-  We will conjecture that $M_{2n + r}^r \simeq S^{(n+r,n)}$ with $e$ unrestricted as well.
-
-  This proves a graphical characterization of $S^\lambda$ in many cases, and hence $D^\lambda$ in the cases where $S^\lambda \simeq D^\lambda$.
-  However, the representation theory of $\SH$ is tied to the modules $D^\lambda$ even in cases where $S^\lambda$ is not irreducible;
-  we will present a characterization of the module $D^{(n+r,n)}$ when $e = 5$ and $r \leq 3$.
-
+  We will prove the following theorem on irreducibility of $M_{2n + r}^r$.
+  \begingroup
+  \hypersetup{linkcolor=\thmcolor} % no orange theorem label
+  \begin{customthm}{\ref{Irreducibility Theorem}}
+    Suppose $e > n$ and $S^{(n+r,n)}$ is irreducible.
+    Then $M_{2n + r}^r$ is irreducible.
+  \end{customthm}
+  \endgroup
+  Note that the representations $M_{0 + r}^r$ and $S^{(r)}$ are both isomorphic to the sign representation.
+  This and Theorem \ref{Irreducibility Theorem} are suggestive;
+  in fact, we will prove the following.
+  \begingroup
+  \hypersetup{linkcolor=\thmcolor}
+  \begin{customthm}{\ref{Correspondence Theorem}}
+    Suppose $e > n + r + 1$.
+    Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
+  \end{customthm}
+  \endgroup
+  Lastly, we will conjecture that $M_{2n + r}^r \simeq S^{(n+r,n)}$ for all $e$, and support this with heuristic data.
+
+  This proves a graphical characterization of $S^\lambda \simeq D^\lambda$ in many cases.
+  However, when $S^\lambda$ is reducible, the crossingless matchings representations cannot provide a graphical realization of the irreducible quotients $D^\lambda$;
+  our next goal is to provide a similar graphical realization of the modules $D^{(n+r,n)}$ with $r \leq 3$ when $e=5$, using a modification of Shor--Jordan's Fibonacci representation of the braid group \cite{Shor}.
+  It is possible that similar graphical representations can be constructed for other $r$ and $e$, but we do not attempt to do so here.
   \def\vara{\alpha_1}
@@
   \fakesubsection{Fibonacci representation}
-  Now suppose that $e = 5$ and $k$ contains the algebraic number $\sqrt{q + q^4}$ for reasons which will be apparent soon.
-  For convenience set $m := 2n + 4$.
-  The following is a modification of Shor--Jordan's Fibonacci representation of the braid group.\cite{Shor}
+  Now suppose that $e = 5$ and $k$ contains the algebraic number $\sqrt{q + q^4}$ (for reasons which will be apparent soon).
+  For convenience set $m := 2n + r$.
+  The following, in the case that $k = \CC$ and  of Shor--Jordan's Fibonacci representation of the braid group.\cite{Shor}
+
+  {\color{orange} Literature goes here.}
 
   \begin{definition}\label{Fib definition}
-  Let $V^m$ be the $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{m+1}$ such that the bit $\vs$ never appears twice consecutively. 
-  We will refer to $V^m$ as the \emph{Fibonacci representation} and suppress the superscript whenever it is clear from context.
-
-  We wish to endow this with a $\SH$-action which acts on a basis vector only dependent on bits $i,i+1,i+2$, sending each basis vector to a combination of the other basis vectors having the same bits $1,\dots,i,i+2,\dots,n+1$ as follows:
+  Let $V^m$ be the $k$-vector space with basis given by the strings $\cbr{\vs,\vp}^{m+1}$ such that the character $\vs$ never appears twice consecutively. 
+  We will refer to $V^m$ as the \emph{Fibonacci representation}.
+
+  We endow $V^m$ with an $\SH$-action which acts on a basis vector in a manner which depends only on bits $i,i+1,i+2$, sending each basis vector to a combination of other basis vectors agreeing on characters $1,\dots,i,i+2,\dots,n+1$ as follows:
 
@@
     \begin{split}
-      T_1 \, \prn{\vs\vp\vp} &:= \vara\prn{\vs\vp\vp}\\
-      T_1 \, \prn{\vp\vp\vs} &:= \vara\prn{\vp\vp\vs}\\
-      T_1 \, \prn{\vs\vp\vs} &:= \varb\prn{\vs\vp\vs}\\
-      T_1 \, \prn{\vp\vs\vp} &:= \varc\prn{\vp\vs\vp} + \vard\prn{\vp\vp\vp}\\
-      T_1 \, \prn{\vp\vp\vp} &:= \vard\prn{\vp\vs\vp} + \vare\prn{\vp\vp\vp}
+      T_1 \, \prn{\vs\vp\vp} &:= \vara\prn{\vs\vp\vp},\\
+      T_1 \, \prn{\vp\vp\vs} &:= \vara\prn{\vp\vp\vs},\\
+      T_1 \, \prn{\vs\vp\vs} &:= \varb\prn{\vs\vp\vs},\\
+      T_1 \, \prn{\vp\vs\vp} &:= \varc\prn{\vp\vs\vp} + \vard\prn{\vp\vp\vp},\\
+      T_1 \, \prn{\vp\vp\vp} &:= \vard\prn{\vp\vs\vp} + \vare\prn{\vp\vp\vp}.
   \end{split} \label{Fib Action} 
@@
     \begin{split}
-    \tau  &:= q + q^4\\
-    \vara &:= -1\\
-    \varb &:= q\\
-    \varc &:= \tau(q\tau - 1)\\
-    \vard &:= \tau^{3/2}(q + 1)\\
-    \vare &:= \tau(q-\tau)
+    \tau  &:= q + q^4,\\
+    \vara &:= -1,\\
+    \varb &:= q,\\
+    \varc &:= \tau(q\tau - 1),\\
+    \vard &:= \tau^{3/2}(q + 1),\\
+    \vare &:= \tau(q-\tau).
   \end{split} \label{Fib Constants} 
   \end{equation}
-  with $T_i$ acting similarly on the substring $i,i+1,i+2$.
-  We will verify that this is a representation of $\SH$ in Appendix \ref{Fib Relations}
+  with $T_i$ acting analogously on a basis element dependent on the substring $i,i+1,i+2$.
+  We verify that $V^m$ is a representation of $\SH$ in Appendix \ref{Fib Relations}
   \end{definition}
 
-  This contains four subrepresentations spanned by strings with beginning and ending with specified bits.
-  Label the subrepresentation spanned by strings $(\vs\dots\vs)$ by $V_{\vs\vs}$, $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$;
-  these bits are preserved by the action \eqref{Fib Action}.
-  We will show that these are isomorphic to particular $D^\lambda$.
-
-  \fakesubsection{Overview of paper}
-
-  In Section \ref{Specht Modules Section} we give corollaries to standard theorems concerning Specht modules.
-  First, James-Mathas provides a sharp characterization of the irreducibility $S^\lambda$ for $\lambda \vdash 2n + r$ which is $e$-regular, called the \emph{Carter criterion}.\cite{Mathas-book}
-  We specialize this to the case that $\lambda = (n+r,n)$ to give a combinatorial condition for irreducibility of $S^{(n+r,n)}$.
-  We note that this irreducibility depends only on $e$ when $e > n$;
-  otherwise it depends on both $e$ and the characteristic of the field.
-  Further, we use Kleshchev--Brundan's modular branching rules to prove our first significant statement: if $S^\lambda \simeq D^\lambda$ and $e > n$, then a particular length-2 composition series uniquely determines $\lambda$;
-  further, an irreducible restriction to $D^{(n,n-1)}$ determines $\lambda$ as well.\cite{Kleshchev, Brundan}
-
-  \def\thmcolor{black!60!orange}
-  \vspace{5pt}
-  In Section \ref{Crossingless Matchings Section}, we first prove that every basis vector in $M$ is cyclic, then that $M$ contains no sign subrepresentation.
-  Then, we prove the following theorem.
-  \begingroup
-  \hypersetup{linkcolor=\thmcolor} % no orange theorem label
-  \begin{customthm}{\ref{Irreducibility Theorem}}
-    Suppose $e > n$ and $S^{(n+r,n)}$ is irreducible.
-    Then $M_{2n + r}^r$ is irreducible.
-  \end{customthm}
-  \endgroup
-  Following this, we prove the existence of a particular filtration with factors given by other crossingless matchings representations;
-  using irreducibility, this becomes a composition series, and an inductive argument combined with the branching of Section \ref{Specht Modules Section} allow us to prove the following:
-  \begingroup
-  \hypersetup{linkcolor=\thmcolor}
-  \begin{customthm}{\ref{Correspondence Theorem}}
-    Suppose $e > n + r + 1$.
-    Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
-  \end{customthm}
-  \endgroup
-  Last, we finish the section by proving more general statements concerning sign subrepresentations of $M$, which contribute to conjectures later in the paper.{\color{orange} Fill in with specific information later.}
-
-  \vspace{5pt}
-  In Section \ref{Fibonacci Section}, we begin by establishing isomorphisms as in \ref{Fibonacci Theorem} for the subrepresentations of $V^2$, as well as irreducibility of $V^3_{\vs\vp}$.
-  We then use these cases to prove that $V^m_{\vs\vp}$ is irreducibile for all $m$, which implies that that $V^m_{\vs\vs}$ is irreducible.
-  From this, we inductively prove the following theorem:
+  Note that the action $T_i$ does not modify characters $i,i+2$, so characters $1$ and $n+1$ are preserved by $\SH$.
+  Hence the representation $V^m$ contains four subrepresentations spanned by strings with beginning and ending with specified characters.
+  Label the subrepresentation spanned by strings $(\vs\dots\vs)$ by $V_{\vs\vs}$, $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$.
+  We prove the following theorem.
   \begingroup
@@
   \begin{customthm}{\ref{Fibonacci Theorem}}
-    The following isomorphisms characterize the subrepresentations of the Fibonacci representation:
-    \begin{align*}  
-       V^{2n}_{\vs\vs} &\simeq D^{(n,n)}\\ 
-       V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)}\\
-       V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)}\\
-       V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)}.
+    We have the following isomorphisms:
+    \begin{align*}  
+      \emph{$V^{2n}_{\vs\vs}$} &\simeq D^{(n,n)},\\ 
+      \emph{$V^{2n-1}_{\vs\vs}$} &\simeq D^{(n+1,n-2)},\\
+      \emph{$V^{2n}_{\vs\vp}$} &\simeq D^{(n+1,n-1)},\\
+      \emph{$V^{2n-1}_{\vs\vp}$} &\simeq D^{(n,n-1)}.
     \end{align*}
@@
   \endgroup
+  This provides a graphical characterization of $D^{(n+r,n)}$ for $e = 5$, $r \leq 3$, as well as a combinatorial characterization of the Fibonacci representation in \cite{Shor}.
+
+  \fakesubsection{Overview of paper}
+
+  In Section \ref{Specht Modules Section} we give corollaries to standard theorems concerning Specht modules.
+  First, James-Mathas provide a sharp characterization of the irreducibility $S^\lambda$ for $\lambda \vdash 2n + r$ which is $e$-regular, called the \emph{Carter criterion} \cite[Thm.~5.42]{Mathas-book}.
+  We specialize this to the case that $\lambda = (n+r,n)$ to give a combinatorial condition for irreducibility of $S^{(n+r,n)}$.
+  We note that this irreducibility depends only on $e$ when $e > n$;
+  otherwise it depends on both $e$ and the characteristic of $k$.
+  Further, we use Kleshchev--Brundan's modular branching rules to prove our first significant statement: if $S^\lambda \simeq D^\lambda$ and $e > n$, then a particular length-2 composition series uniquely determines $\lambda$;
+  further, an irreducible restriction to $D^{(n,n-1)}$ determines $\lambda$ as well \cite{Kleshchev, Brundan}.
+
+  \vspace{5pt}
+  In Section \ref{Crossingless Matchings Section}, we begin by proving Theorem \ref{Irreducibility Theorem}.
+  Following this, we prove the existence of a particular filtration with factors given by other crossingless matchings representations;
+  using irreducibility, this becomes a composition series.
+  This combined with an inductive argument and the branching of Section \ref{Specht Modules Section} allow us to prove Theorem \ref{Correspondence Theorem}.
+  Last, we finish the section by proving more general statements concerning sign subrepresentations of $M$, which contribute to conjectures later in the paper.{\color{orange} Fill in with specific information later.}
+
+  \vspace{5pt}
+  In Section \ref{Fibonacci Section}, we begin by establishing the $2n = 2$ case of Theorem \ref{Fibonacci Theorem} for the subrepresentations of $V^2$, as well as irreducibility of $V^3_{\vs\vp}$.
+  We then use these cases to prove that $V^m_{\vs\vp}$ and $V^m_{\vs\vs}$ are irreducible for all $m$.
+  From this, we inductively prove Theorem \ref{Fibonacci Theorem}.
   {\color{orange} Overview of Conjecture and Empirics goes here.}
+
+  \vspace{5pt}
+  In Appendix \ref{Compatibility Section}, we begin by giving a precise definition of $M_{2n + r}^r$.
+  Then, we verify that the crossingless matchings and Fibonacci representations are compatible with the Hecke algebra relations.
+  In Appendix \ref{Algebra}, we prove a lemma concerning restrictions to various subalgebras of the Hecke algebra.
+  In Appendix \ref{Empirics Section}, we give explicit data both supporting the conjectures laid out in Section {\color{orange} reference to conjecture section} and giving explicit transitions between $M_{2n + r}^r$ and $V^{2n + r}$ and composition series of $M_{2n + r}^r$ in the case that $2n + r \leq 7$.
 
@@
   The authors thank Prof. Roman Bezrukavnikov for suggesting this project, as well as Dr. Slava Gerovitch for organizing the SPUR+ program.
-  We would also like to thank Profs. David Jerison and Ankur Moitra for their role in SPUR+ as well as general advice.
-  We would also thank Professor Alexander Kleshchev for our helpful conversations concerning branching theorems.
+  We would also like to thank Profs. David Jerison and Ankur Moitra for their role in SPUR+ as well as their general advice.
+  We would also like to thank Professor Alexander Kleshchev for helpful conversations concerning branching theorems.
   Lastly, we would like to express our gratitude to our mentor Oron Propp for his help and advice in both acquiring background knowledge and in executing the mathematics in this paper, as well as his comments on early drafts of this paper;
@@
   Lastly, let $h_{ab}^\lambda$ be the hook length of node $(a,b)$ in $\brk \lambda$ as defined in \cite{Kleshchev}.
-  With this language, we may express the following theorem, parts (ii)-(iii) of which are known as the \emph{Carter criterion} in the symmetric group case, due to James--Mathas.\cite{Mathas-book}
+  With this language, we may express the following theorem, parts (ii)-(iii) of which are known as the \emph{Carter criterion} in the symmetric group case, due to James--Mathas \cite{Mathas-book}.
   \begin{theorem}[James--Mathas]\label{Mathas Irreducibility}
@@
       \item $\nu_{e,p}\prn{h_{ab}^\lambda} = \nu_{e,p}\prn{h_{ac}^\lambda}$ for all nodes $(a,b)$ and $(a,c)$ in $\brk \lambda$.
-    \qed\end{enumerate}
+    \end{enumerate}
   \end{theorem}
   \begin{proof}
-    See \cite{Mathas-book} theorem 5.42.
+    See \cite[Thm~5.42]{Mathas-book}.
   \end{proof}
@@
   \begin{proof}
-    This follows from the proof of Corollary \ref{S irreducibility} part (ii) and the fact that $\nu_p(h) = \nu_p(h')$ for all naturalls $h,h'$. 
+    This follows from the proof of Corollary \ref{S irreducibility} part (ii) and the fact that $\nu_p(h) = \nu_p(h')$ for all naturals $h,h'$. 
   \end{proof}
@@
   \begin{align*}
-    V_{\vs\vs}^2 &\simeq D^{(1^2)}\\
-    V_{\vs\vp}^2 &\simeq D^{(2)}\\
-    V_{\vp\vp}^2 &\simeq V_{\vs\vs}^2 \oplus V_{\vs\vp}.
+    \emph{$V_{\vs\vs}^2$} &\simeq D^{(1^2)}\\
+    \emph{$V_{\vs\vp}^2$} &\simeq D^{(2)}\\
+    \emph{$V_{\vp\vp}^2$} &\simeq V_{\vs\vs}^2 \oplus V_{\vs\vp}.
   \end{align*}
@@
   \begin{align*} 
-    \beta_\varpi(1,2) &= 3 - 2 + (n-1) = n\\
-    \beta_\varpi(1,3) &= 3 - 1 + n = n+2\\
-    \beta_\varpi(2,3) &= 2 - 1 + 2 = 3
+    \beta_\varpi(1,2) &= 3 - 2 + (n-1) = n,\\
+    \beta_\varpi(1,3) &= 3 - 1 + n = n+2,\\
+    \beta_\varpi(2,3) &= 2 - 1 + 2 = 3.
   \end{align*}
@@
 \appendix
-\section{Compatibility of Representations with the Relations}
+\section{Compatibility of Representations with the Relations}\label{Compatibility Section}
 In general, we defined the representations $V := V^{2n + r}$ and $M := M_{2n + r}$ for the free algebra on generators $\cbr{T_1,\dots,T_{2n + r - 1}}$.
@@
 
-\subsection{Explicit Definition of $M$}
+\subsection{Explicit Definition of $M$}\label{Explicit Definition}
 We will give a more careful definition of the crossingless matchings representation here.
@@
   Then, define $M^r_{2n+r}$ to be the $k$-vector space with basis the set of crossingless matchings on $2n+r$ indices with $r$ anchors.
+  If basis element $w_j$ contains arc $(a,b)$, say $w_j(a) := b$ and $w_k(b) := a$.
 
@@
   If $w_j$ has arc $(i,i+1)$, define $(1 + T_i)w_j := (1 + q)w_j$.
-  If $w_j$ has anchors $W(i) = i$ and $W(i+1) = i+1$, define $(1 + T_i)w_j := 0$.
-  If $w_j$ has anchor $W(i) = i$ and arc $W(i+1) = b$, define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$, $w_l(b) = b$, and all other arcs agree with $w_j$.
-  If $w_j$ has arcs $W(i) = a$ and $W(i+1) = b$, then define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$,$w(a) = b$, and all other acts agree with $w_j$. 
-  We verify that this is well-defined in Section \ref{Cross Relations}.
+  If $w_j$ has anchors $w_j(i) = i$ and $w_j(i+1) = i+1$, define $(1 + T_i)w_j := 0$.
+  If $w_j$ has anchor $w_j(i) = i$ and arc $w_j(i+1) = b$, define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$, $w_l(b) = b$, and all other arcs agree with $w_j$.
+  If $w_j$ has arcs $w_j(i) = a$ and $w_j(i+1) = b$, then define $(1 + T_i)w_j := q^{1/2}w_l$, where $w_l(i) = i+1$,$w(a) = b$, and all other acts agree with $w_j$. 
+  We verify that this is well-defined in Appendix \ref{Cross Relations}.
 \end{definition}

### 2019-07-31 tex/Drafts/Draft-2 - Miles Edits.tex
New edits miles

--- 2019-07-30 tex/Drafts/Draft-2.tex
@@
 
-In this section, we characterize $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$ for $e \nmid n + r + 1$ and for $e=n+r+1$.
-When the representation is clear, we will simply denote this kernel as $K$ or $\cap\text{ker}(1+T_i)$.
-For compactness, in this section we use $\sim $ to denote "proportional to".
-For convenience, define $M_0^0$ to be the zero representation.
+Recall $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$ defined before proposition \ref{Trivial}.
+When the limits are clear, we will simply denote this kernel by $K$.
+In this section, we prove $K$ is trivial for $e \nmid n + r + 1$ and give a one-dimensional basis for $e=n+r+1$.
+
+For compactness, in this section we use $\sim $ to denote ``proportional to." For convenience, define $M_0^0$ and $M_1^1$ to be the zero representation.
+Note that in this section we do not assume $n>0$.
 
@@
 \begin{definition}
-
-	Fix some basis element $\psi\in M_{2n+r}^r$.
-For $1 \leq a,b \leq 2n + r$ define $\psi(a):=b$ iff $a$ and $b$ are matched in $\psi$, $\psi(a):=a$ if $a$ is an anchor in $\psi$.
-Given that $\psi$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $\psi(a,b)$ of $\psi$ to be the basis element $\sigma\in M_{b-a+1}^{r'}$ specified by $\sigma(i)=\psi(i+a-1)-a+1$.
-This sub-matching is defined for $a<b$ when $\psi(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$.
-See \ref{sub-matching example}.
-
-	If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, $\psi(a,b)$ will always refer to those nodes and they're matchings, though it may not be a sub-matching unless specified.
-For any other $a,b$, we define $\psi(a,b)$ to be an element of the representation with no nodes.
+	We will use the following notation extensively while exploring the structure of the kernel. Examples are given in figure \ref{sub-matching example}. Fix some basis element $\psi\in M_{2n+r}^r$.
+
+	\begin{itemize}
+		\item For $1 \leq a,b \leq 2n + r$ define $\psi(a):=b$ if $a$ and $b$ are matched in $\psi$, and $\psi(a):=a$ if $a$ is an anchor in $\psi$.
+
+		\item Let $r'$ be the number of anchors in $\psi$ in the range $a,\ldots,b$.
+Suppose $1\leq a\leq b\leq 2n+r$ and $\psi(i)\in \{a,\ldots,b\}$ for all $i\in \{a,\ldots,b\}$.
+Define a \emph{sub-matching} $\psi(a,b)$ of $\psi$ to be the basis element $\sigma\in M_{b-a+1}^{r'}$ specified by $\sigma(i)=\psi(i+a-1)-(a-1)$.
+
+		\item For $a,b$ satisfying $1\leq a\leq b\leq 2n+r$, if $\psi(a,b)$ is not a sub-matching, define it to be the ordered set of nodes $(\psi(a),\ldots,\psi(b))$.
+For any other $a,b$, we define $\psi(a,b)$ to be an element of the zero representation $M_0^0$.
+
+		\item Define the \emph{rainbow element} $R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$.
+In other words, the basis element with all anchors to the left followed by a ``rainbow" to the right.
+	\end{itemize}
 
@@
 		\begin{gathered}
-		\Matching{6}{1/2, 3/6, 4/5}, \hspace{\cbasisspacing}
+		\GeneralizedMatching{8}{3/8, 4/7, 5/6}{2}{1/1,2/2}{5/4}, \hspace{\cbasisspacing}
 		\Matching{4}{1/4, 2/3}
 		\end{gathered}}$
-	\caption{$\psi\in M_6^0$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right. $\psi(3,6)=\sigma$. $\psi(2,5)$ is not a sub-matching.}
+	\caption{The rainbow element $R\in M_8^2$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right.
+The nodes $R(4)=7$, $R(5)=6$, so $R(4,7)$ defines a sub-matching.
+Specifically, $R(4,7)=\sigma$.
+Alternatively, $R(3)=8$, so, for instance $R(2,7)$ is not a sub-matching, and refers to the ordered set $(2,8,7,6,5,4)$.
+$R(2,1)$ is an element of the zero representation since $2>1$.}
 	\label{sub-matching example}
@@
 
-Define the rainbow element $R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$.
-In other words, the basis element with all anchors to the left then a rainbow.
+The following proposition lets us begin to characterize the coordinate vector of any element in $K$, and will serve as the starting point for all following characterizations.
 
 \begin{proposition}
-	Let $w$ be an arbitrary vector in $M_{2n+r}^r$. I claim that if $w\in \cap\text{ker}(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero.
+	Let $w\in M_{2n+r}^r$. If $w\in K$ is nonzero, then the coordinate of the rainbow element $R$ in $w$ is nonzero.
 
@@
 \begin{proof}
-	Let $Y$ be the set of basis elements with nonzero coordinate in $w$.
-Let $z$ be the greatest integer such that there exists $y\in Y$ where $y(1)-1=...=y(z)-z=0$, and let $U\subset Y$ be the set of such $y$.
-In other words, $U$ is the set of basis elements in $Y$ which have the most anchors to the far left.
+	Let $W$ be the set of basis elements with nonzero coordinate in $w$.
+Let $z$ be the maximal number of anchors to the far left in any element $\psi\in W$.
+Formally, $z$ is the greatest positive integer such that there exists some element $\psi\in W$ satisfying $\psi(1)-1=...=\psi(z)-z=0$.
+For some positive integer $j$ define $W^j\subset W$ to be the set of all basis elements in $W$ with $j$ anchors to the far left.
 
 	Suppose $z<r$.
-Then for each $y\in U$ there exists a minimal $i_y>z+2$ such that $y(i_y)=0$.
-In other words, $i_y$ is the position of the next leftmost anchor in $y$.
-Fix $\tilde{y}$ such that $i_{\tilde{y}}\leq i_y$ for all $y$.
-Then I claim the basis element $y':=q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}$ has nonzero coordinate in $(1+T_{i_{\tilde{y}}-1})w$, implying $w\not\in \cap\text{ker}(1+T_i)$.
-To see this, we can show that $\tilde{y}$ is the only basis element in $Y$ such that $(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$.
-$y'$ still has $z$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$.
-If $x\in Y,\not\in U$, the basis element $x'$ proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$.
-If $x\in U$, $x'$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$.
-Since this is the only match altered by action of $(1+T_{i_{\tilde{y}}-1})$ on $x$, if $(1+T_{i_{\tilde{y}}-1})x\sim y'$ this implies $x=\tilde{y}$.
+Then for each $\psi\in W^z$, exactly $z$ anchors are positioned to the far left, so we may define $i_\psi$ to be the position of the next leftmost anchor in $\psi$.
+Fix some $\widehat{\psi}\in W^z$ such that $i_{\widehat{\psi}}\leq i_\psi$ for all $\psi$.
+
+	Define the basis element $\psi':=q^{-1/2}(1+T_{i_{\widehat{\psi}}-1})\widehat{\psi}$.
+First, note that $i_\psi>z+1$, so $i_\psi-1$ is not an anchor and $\psi'\not=0$.
+This follows from the definition of $z$ and $W^z$, which require that the node $z+1$ is not an anchor.
+We will prove that $\psi'$ has nonzero coordinate in $(1+T_{i_{\widehat{\psi}}-1})w$, implying $w\not\in K$.
+
+	It suffices to show that $\widehat{\psi}$ is the only basis element in $W$ brought to $\psi'$ by the action of $(1+T_{i_{\widehat{\psi}}-1})$.
+Formally, we will show that if $\sigma\in W$ and $(1+T_{i_{\widehat{\psi}}-1})\sigma\sim \psi'$, then $\sigma=\widehat{\psi}$.
+
+	Immediately, we may intuit a few properties of $\psi'$:
+	\begin{enumerate}[label={(\roman*)}]
+		\item $\psi'$ still has $z$ anchors on the left.
+		\item Defining $i_{\psi'}$ to be the next leftmost anchor, $i_{\psi'}<i_{\widehat{\psi}}$
+	\end{enumerate}
+
+	Together, (i) and (ii) imply $\psi'\not\in W$. So, if $(1+T_{i_{\widehat{\psi}}-1})\sigma\sim \psi'$, $q^{-1/2}(1+T_{i_{\widehat{\psi}}-1})\sigma=\psi'$.
+
+	Define $\sigma':=q^{-1/2}(1+T_{i_{\widehat{\psi}}-1})\sigma$.If $\sigma\not\in W^z$, $\sigma'$ will have $z$ anchors at the far left only if $\sigma'\in W^{z-1}$ and the $z$th leftmost anchor is at position $i_{\widehat{\psi}}$.
+But then the position of the $z+1$st anchor is unchanged by the action, and must be at position greater than $i_{\widehat{\psi}}$, so from (ii) $\sigma'\not=\psi'$.
+If $\sigma\in W^z$, $\sigma'$ will have anchor at $i_{\psi'}$ if and only if $i_\sigma=i_{\widehat{\psi}}$ and $\sigma(i_{\widehat{\psi}}-1)=\widehat{\psi}(i_{\widehat{\psi}}-1)$.
+Since these are the only three indices altered by action of $(1+T_{i_{\widehat{\psi}}-1})$ on $\sigma$, if $(1+T_{i_{\widehat{\psi}}-1})\sigma\sim \psi'$ this implies $\sigma=\widehat{\psi}$ as desired.
 So if $z<r$ $w$ is not in the desired kernel.
 
-	Suppose $z=r$ but $R\not\in U$ (so $R\not\in Y$).
-Let us define a sequence of subsets of $U$ in the following way: $U_0:=U$, $U_{i+1}:=\{u\in U_i| u(r+i+1)=2n+2r-i+1 \}$.
-Since $R\not\in U$, $\exists t<n-1$ such that $U_{t+1}=\emptyset$.
-Choose $\tilde{u}\in U_t$ such that $\tilde{u}(r+t+1)\geq u(r+t+1)$ for all $u\in U_t$.
-Consider the basis element $u':=q^{-1/2}(1+T_{\tilde{u}(r+t+1)})\tilde{u}$.
-I claim that $\tilde{u}$ is the only element in $Y$ such that $(1+T_{\tilde{u}(r+t+1)})\tilde{u}\sim u'$, again implying that $w$ is not in the desired kernel.
-$u'$ still has $r$ anchors on the left, $u'(r+i)=2n+2r-i+2$, $1\leq i\leq t$, and $u'(r+t+1)>\tilde{u}(r+t+1)$, so $u'\not\in Y$.
-If $x\in Y,\not\in U$,  the basis element $x'$ proportional to $(1+T_{\tilde{u}(r+t+1)})x$ will have $r$ leftmost anchors only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
-Similarly, if $x\in U,\not\in U_t$, the basis element $x'$ will have the property $x'(r+i)=2n+2r-i+2$ for all $i\leq t$ only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
-If $x\in U_t$, $x'(r+t+1)=u'(r+t+1)$ if and only if $x(r+t+1)=\tilde{u}(r+t+1)$ and $x(x(r+t+1)+1)=\tilde{u}(\tilde{u}(r+t+1)+1)$ (since $u'\not \in Y$).
-These are the only matches altered by the action $(1+T_{\tilde{u}(r+t+1)})$, so this implies $x=\tilde{u}$.
-Thus we have proved that if $R\not\in Y$, $w$ is not in the kernel.
-
+	\vspace{1mm}
+	We have proven that there exists an element in $W$ with all anchors to the far left, or equivalently that $W^r$ is nonempty.
+Now we must prove that $R\in W^r$.
+The proof is analogous to the previous case.
+First we define subsets $W^r_j\subset W^r$ that have the top $j$ arcs of the rainbow, and define $y$ to be the most arcs any element has.
+In the previous proof, we showed that if we move the next left-most anchor further left, the image of $w$ under that transposition will be nonzero.
+In this proof, we will show that if we expand the next-largest arc, the image of $w$ under that transposition will be nonzero.
+
+	\vspace{1mm}
+	Suppose $z=r$ but $R\not\in W^r$ (so $R\not\in W$).
+Let us define a sequence of subsets $W^r_i\subset W^r$ to be the set of elements in $W^r$ with the top $i$ humps of the rainbow.
+Formally, $W^r_0:=W^r$, $W^r_{i+1}:=\{\upsilon\in W^r_i| \upsilon(r+i+1)=2n+r-i \}$.
+Since $R\not\in W^r$,  there exists some positive integer $y$ less than $n-1$ such that $W^r_{y+1}=\emptyset$; $y$ is the largest number of contiguous top level rainbow humps that any element in $W^r$ has.
+
+	Choose $\widehat{\upsilon}\in W^r_t$ such that $\widehat{\upsilon}(r+t+1)\geq \upsilon(r+t+1)$ for all $\upsilon\in W^r_t$.
+Define the basis element $\upsilon':=q^{-1/2}(1+T_{\widehat{\upsilon}(r+t+1)})\widehat{\upsilon}$.
+
+	First, note that $\widehat{\upsilon}(r+t+1)<2n+r-t$, so:
+	\begin{enumerate}[label={[\roman*]}]
+		\item $\upsilon'(r+t+1)>\widehat{\upsilon}(r+t+1)$ 
+		\item For $0\leq j\leq t$, $\upsilon'(r+j)=\widehat{\upsilon}(r+j)=2n+r-j+1$.
+	\end{enumerate}
+
+	These properties are analogous to properties (i) and (ii) used earlier in this proof.
+As before, these imply that $\upsilon'\not\in W$, so, for $\sigma\in W$, if $(1+T_{\widehat{\upsilon}(r+t+1)})\sigma\sim \upsilon'$, $q^{-1/2}(1+T_{\widehat{\upsilon}(r+t+1)})\sigma=\upsilon'$.
+
+	We will prove that $\upsilon'$ has nonzero coordinate in $(1+T_{\widehat{\upsilon}(r+t+1)})w$, implying $w\not\in K$.
+Again, it is sufficient to show that, for $\sigma\in W$, $q^{-1/2}(1+T_{\widehat{\upsilon}(r+t+1)})\sigma=\upsilon'$ implies $\sigma=\widehat{\upsilon}$.
+
+	Define $\sigma':=q^{-1/2}(1+T_{\widehat{\upsilon}(r+t+1)})\sigma$.
+Suppose $\sigma\not\in W^r_t$.
+To satisfy [ii], we must have $\sigma\in W^r_{t-1}$ and $\sigma(r+t)=\widehat{\upsilon}(r+t+1)$.
+But then $\sigma(r+t+1)<\widehat{\upsilon}(r+t+1)$ is unchanged by action of $(1+T_{\widehat{\upsilon}(r+t+1)})$, and $\sigma'$ does not satisfy [i], so $\sigma'\not=\upsilon'$.
+If $\sigma\in W^r_t$, to satisfy $\sigma'(r+t+1)=\upsilon'(r+t+1)$, we must have $\sigma(r+t+1)=\widehat{\upsilon}(r+t+1)$ and $\sigma(\widehat{\upsilon}(r+t+1)+1)=\widehat{\upsilon}(\widehat{\upsilon}(r+t+1)+1)$.
+Since these are the only two matchings altered by the transposition, if $q^{-1/2}(1+T_{\widehat{\upsilon}(r+t+1)})\sigma=\upsilon'$ we must have that $\sigma=\widehat{\upsilon}$ as desired.
+Thus, if $w\in K$ is nonzero, $R$ has nonzero coordinate in $w$.
 \end{proof}
@@
 \begin{proof}
-	Suppose $\cap\text{ker}(1+T_i)=K\not=0$.
+	Suppose $\cap\ker(1+T_i)=K\not=0$.
 Take nonzero $w\in K$.
@@
 By the inductive hypothesis, we may apply the algorithm to this sub-matching and commute with the isomorphism with $Y_{E_{\lfloor a/2\rfloor}}$.
-In this way, we find that the coordinate of $\tilde{\psi}$ defined by $\tilde{\psi}(1,a):=\psi(1,a)$ and $\tilde{\psi}(a+1,2n+r)=R$ is $x_{\psi(2,a-1)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_{\tilde{\psi}}(q)$.
-Similarly, define $Y_{\tilde{\psi}}$ with respect to the sub-matching $\tilde{\psi}(a+1,2n+r)$, and commute the algorithm with the isomorphism.
-In the same way, we obtain that the coordinate of $\psi\in Y_{\tilde{\psi}}$ is $x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_\psi(q)$ as desired.
+In this way, we find that the coordinate of $\widehat{\psi}$ defined by $\widehat{\psi}(1,a):=\psi(1,a)$ and $\widehat{\psi}(a+1,2n+r)=R$ is $x_{\psi(2,a-1)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_{\widehat{\psi}}(q)$.
+Similarly, define $Y_{\widehat{\psi}}$ with respect to the sub-matching $\widehat{\psi}(a+1,2n+r)$, and commute the algorithm with the isomorphism.
+In the same way, we obtain that the coordinate of $\psi\in Y_{\widehat{\psi}}$ is $x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_\psi(q)$ as desired.
 
@@
 
-	Suppose the lemma is true for all $\tilde{b}<b+1$. Then for $a< b$ we have 
+	Suppose the lemma is true for all $\widehat{b}<b+1$. Then for $a< b$ we have 
 	\begin{align*}	

### 2019-07-31 tex/comments/2-nat-comments.tex
Nat edits

@@
     Note that we follow the convention of Murphy--Kleshchev concerning the correspondence $\lambda \leftrightarrow S^\lambda$, which is dual to the conventions of Dipper--James--Mathas;
-    one may translate our results to the latter convention by transposing all partitions.\cite{Kleshchev,Mathas-book,Murphy1} 
+    one may translate our results to the latter convention by transposing all partitions \cite{Kleshchev,Mathas-book,Murphy1}. 
     For instance, we refer to the \emph{sign representation} as $S^{(1^{2n + r})}$.
@@
   \end{definition}
-  \begin{figure}[b] 
+  \begin{figure} 
     \def\cbasisspacing{5mm}
@@
   It is possible that similar graphical representations can be constructed for other $r$ and $e$, but we do not attempt to do so here.
+
   \def\vara{\alpha_1}
@@
   For convenience set $m := 2n + r$.
-  The following, in the case that $k = \CC$ and  of Shor--Jordan's Fibonacci representation of the braid group.\cite{Shor}
+  The following is essentially a rescaling of Shor--Jordan's Fibonacci representation of the braid group \cite{Shor}.
 
@@
     \nu_{e,p}(h) := \begin{cases}
-      \nu_p(h) & e \text{if }\mid h\\
-      -1 & e \text{if }\nmid h
-    \end{cases}.
+      \nu_p(h) & \text{if }e \mid h,\\
+      -1 & \text{if }e \nmid h.
+    \end{cases}
   \]
@@
   \begin{align*}
-    \beta_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i}^j a_t\\
+    \beta_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i}^j a_t,\\
     \gamma_\lambda(i,j) &= \lambda_i - \lambda_j + \sum_{t = i+1}^j a_t.
@@
   for these, we will use the facts that 1 is always normal and that $j$ is normal when $\beta_\lambda(i,j) \not\equiv 0 \pmod e$ for all $i \leq j$.
-  Further, we will use that $j$ is good if and only if $j$ is normal and $\gamma_\lambda(j,j') \not\equiv 0 \pmod e$ for all $j' \geq j$ normal.\cite{Brundan,Kleshchev}
+  Further, we will use that $j$ is good if and only if $j$ is normal and $\gamma_\lambda(j,j') \not\equiv 0 \pmod e$ for all $j' \geq j$ normal \cite{Brundan,Kleshchev}.
   When $\lambda(i) = \mu$ for $i$ normal, write $\mu \xrightarrow{\text{normal}} \lambda$, and similar in the good case.
 
-  The following statements, collectively known as \emph{modular branching rules} of $D^\lambda$, were originally written by Kleshchev for Specht modules of the group algebra $k\brk{S_n}$, then generalized to the Hecke algebra case by Brundan.\cite{Kleshchev,Brundan}
+  The following statements, collectively known as \emph{modular branching rules} of $D^\lambda$, were originally written by Kleshchev for Specht modules of the group algebra $k\brk{S_n}$, then generalized to the Hecke algebra case by Brundan \cite{Kleshchev,Brundan}.
   They entirely characterize the socle of $\Res D^\lambda$, as well as semisimplicity od $\Res D^\lambda$.
@@
       &\simeq \begin{cases}
-        k & \text{if } \mu \xrightarrow{\text{good}} \lambda\\
-        0 & \text{otherwise}
+        k & \text{if } \mu \xrightarrow{\text{good}} \lambda,\\
+        0 & \text{otherwise}.
       \end{cases}
@@
     henceforth assume that these are each $e$-regular.
-
     First suppose that that $\lambda = \varpi$.
     We will break into cases with $r$.
-    \begin{itemize}
+    \begin{enumerate}[label={\textit{Case \arabic*.}}]
       \item Suppose that $r > 1$.
         Note that $e \nmid r + 1 = \beta_\varpi(1,2)$, so $2$ is normal.
-        Further, $\gamma_\varpi(2,3) = n \not\equiv 0 \pmod e$, so 2 is good and $D^{(n+r-1,n-1,1)} \subset D^\varpi$, which is not a composition factor in \eqref{D Composition Series}.
-        Hence, by the Jordan-H\"older theorem \cite{Etingof}, we have $\lambda \neq \varpi$.
+        Further, \[\gamma_\varpi(2,3) = n \not\equiv 0 \pmod e,\] so 2 is good and $D^{(n+r-1,n-1,1)} \subset D^\varpi$, which is not a composition factor in \eqref{D Composition Series}.
+        Hence, by the Jordan-H\"older theorem \cite[Thm.~3.7.1]{Etingof}, we have $\lambda \neq \varpi$.
 
       \item Suppose that $r = 1$.
-        Then, $\varpi = (n,n,1)$ has $\gamma_{\varpi}(1,2) = n \not\equiv 0 \pmod e$, giving $D^{(n,n-1,1)} \subset D^\varpi$ and hence $\lambda \neq \varpi$ as in the previous case.
-    \end{itemize} 
-  \iffalse % keeping just in case
-   \begin{align*}
-    \beta_{\varpi}(1,2)     &= r + 1 \\
-    \beta_{\varpi}(1,3)     &= n + r + 1 \\
-    \beta_{\varpi}(2,3)     &= n + 1\\
-    \gamma_{\varpi}(1,2)    &= r\\
-    \gamma_{\varpi}(1,3)    &= n + r\\
-    \gamma_{\varpi}(2,3)    &= n\\
-  \end{align*}
-  \fi
+        Then, $\varpi = (n,n,1)$ has \[\gamma_{\varpi}(1,2) = n \not\equiv 0 \pmod e,\] giving $D^{(n,n-1,1)} \subset D^\varpi$ and hence $\lambda \neq \varpi$ as in the previous case.
+    \end{enumerate}
 
   \vspace{5pt}
-  Now suppose that $\lambda = \varsigma$ and break into cases with $r$:
-  \begin{itemize}
+  Now suppose that $\lambda = \varsigma$.
+  Note that $\varsigma$ is not a partition when $r < 2$, so we may assume that $r \geq 2$.
+  We further break into cases with $r$:
+  \begin{enumerate}[label={\textit{Case \arabic*.}}]
     \item Suppose $r > 2$.
@@
     \item Suppose $r = 2$.
-      Then $\Res \, D^\varsigma \simeq D^{(n+1,n)}$ is irreducible, as $\varsigma = (n+1,n+1)$ has rows of the same length;
-      this contradicts \eqref{D Composition Series}. 
-    \item Suppose $r < 2$. 
-      Then $\varsigma$ is not a partition.
-  \end{itemize}
-  This completes the proof.
+      Then, we have the restriction \[\Res \, D^\varsigma \simeq D^{(n+1,n)},\] as $\varsigma = (n+1,n+1)$ has tworows of the same length.
+      This contradicts \eqref{D Composition Series}. 
+  \end{enumerate}
+  Hence $\lambda = \mu$, completing the proof.
 
@@
   This reduces to the cases of $\varsigma := (n + 1, n - 1)$ and $\mu := (n,n)$;
-  if $\lambda = \varsigma$, then we have that $e \mid \beta_\varsigma(1,2) = 4$, a contradiction.
+  if $\lambda = \varsigma$, then we have that \[\beta_\varsigma(1,2) = 4 \equiv 0 \pmod e,\] a contradiction.
   Hence $\lambda = \mu$.
 \end{proof}
-
-\iffalse
-\begin{proposition}
-  Suppose that $n > 0$ and $e \nmid n + r$.
-  \begin{enumerate}[label={(\roman*)}]
-    \item Suppose $r > 0$, $n > 1$, and either $e \nmid n + 1$ or $e \nmid n + r + 1, n + r - 1$.
-      If $D^\lambda$ has the composition series 
-      \begin{equation}\label{D Composition Series}
-        0 \subset D^{(n+r-1,n)} \subset \Res \, D^{\lambda}
-      \end{equation}
-      with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)} \simeq D^{(n+r,n)}$, then $\lambda = (n+r,n)$.
-    \item Suppose $n = 1$ and $e \nmid r+2$, and suppose that we have composition series \eqref{D Composition Series}.
-      Then $\lambda=(r+1,r+2)$.
-    \item Suppose $r = 0$, either $e \nmid n+2$ or $e > 3$, and $D^{(n,n-1)} \simeq \Res \, D^\lambda$.
-      Then $\lambda = (n,n)$.
-  \end{enumerate}
-  The above conditions are unilaterally met whenever $e > n + r + 1$ and $(n,r) \neq (1,0)$.
-\end{proposition}
-\begin{proof}
-  \textbf{(i)}
-  Let $\lambda_1 := (n+r-1,n,1)$, let $\lambda_2 := (n+r-1,n+1)$, and let $\lambda_3 := (n + r,n)$.
-  Since $D^{(n+r-1,n)} \subset \Res \, D^\lambda$, we have $(n + r - 1,n) \longrightarrow \lambda$, implying $\lambda = \lambda_i$ for some $i = 1,2,3$.
-  We will show that $\lambda_1,\lambda_2$ each have good numbers other than 1, leading to elements of their socle that are not factors in \eqref{D Composition Series};
-  then, we will have $\lambda = \lambda_3$.
-
-  We may straightforwardly compute this.
-  First assume $n \geq 2$, so that
-  \begin{align*}
-    \beta_{\lambda_1}(1,2) &= n + 1\\
-    \beta_{\lambda_1}(1,3) &= n + r + 1\\
-    \beta_{\lambda_1}(2,3) &= n + r - 1\\
-    \beta_{\lambda_2}(1,2) &= n + r
-  \end{align*}
-
-  \textbf{(ii)}
-  The choices are the same as above, but now $\lambda_1$ only has two removable nodes, so that
-  \begin{align*}
-    \beta_{\lambda_1}(1,3) &= r + 2\\
-    \beta_{\lambda_2}(1,2) &= r + 1
-  \end{align*}
-
-  \textbf{(iii)}
-  Let $\lambda_1 := (n,n-1,1)$, let $\lambda_2 := (n+1,n-1)$, and let $\lambda_3 := (n,n)$;
-  as before we know that $\lambda = \lambda_i$ for $i = 1,2,3$, so we will eliminate $\lambda_1,\lambda_2$.
-  First, we will show that $\lambda_1$ has a good number other than 1:
-  \begin{align*}
-    \beta_{\lambda_1}(1,2) &= n\\
-    \beta_{\lambda_1}(1,3) &= n + 2\\
-    \beta_{\lambda_1}(2,3) &= n\\
-  \end{align*}
-  Hence we may rule out $\lambda_1$ when $e | n$.
-
-  Suppose $D^{\lambda_2}$ satisfies the isomorphism;
-  then the number 2 is normal.
-  We may make the following computations:
-   \begin{align*}
-    \beta_{\lambda_2}(1,2) &= n + 2\\
-    \gamma_{\lambda_2}(1,2) &= 3.
-  \end{align*}
-  When $e | n + 2$, this brings contradiction;
-  when $e \nmid n + 2$ and $e > 3$, 2 is a good number (recalling that $e > 2$), giving non-semisimple restriction, a contradiction.
-  Hence $\lambda = \lambda_3$ and the proposition is proven.
-\end{proof}
-\fi
+This will be an integral technical tool in proving the correspondence between the crossingless matchings representation $M_{2n + r}^r$ and the Specht module $S^{(n+r,n)}$ in the following section.
 
 \section{Crossingless matchings and Specht modules}\label{Crossingless Matchings Section}
-In this section, we will analyze the crossingless matchings representation $M := M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \simeq S^{(n+r,n)}$ under certain conditions in $e$.
+In this section, we analyze the crossingless matchings representation $M := M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \simeq S^{(n+r,n)}$ under certain conditions in $e$.
 We begin by proving irreducibility of $M_{2n + r}^r$ whenever $e \nmid r+2,r+3,\dots,n+r+1$;
@@
 We refer to a vector $w \in M$ satisfying $\SH w = M$ as \emph{cyclic}.
-It is a classical result that a representation $W$ is irreducible if and only if every nonzero element of $W$ is cyclic.\cite{Etingof}
+It is a classical result that a representation $W$ is irreducible if and only if every nonzero element of $W$ is cyclic \cite{Etingof}.
 We will prove irreducibility by showing that every nonzero $w \in M$ is cyclic;
@@
   We will show that, for every element $(1 + T_j') \in \SH(S_{2(n-1) + r})$, there is some element $h_j \in \SH(S_{2n + r})$ such that the following commutes:
-  \[
+  \begin{equation}\label{Irreducibility commutative diagram}
     \begin{tikzcd}
@@
     \end{tikzcd}
-  \]
+  \end{equation}
   Indeed, when $i+1 \neq j$ this is given by $h_j = 1 + T_j$, and we have $h_{i+1} = q^{-1}(1 + T_i)(1 + T_{i+1})(1 + T_{i-1})$, as given by Figure \ref{bigloop}.
@@
   Then, by the inductive hypothesis, there is some element $h' \in \SH(S_{2(n-1) + r})$ sending $\varphi((1 + T_i)w)$ to the image of a basis vector of $M_{2n + r}^r$ via $\varphi$;
-  then, the action $\SH$ generates the endomorphism $\varphi^{-1}h'\varphi$ of $M$, which sends $(1 + T_i)w$ to a basis vector in $M_{2n + r}^r$.
+  then, by \eqref{Irreducibility commutative diagram} the action $\SH$ generates the endomorphism $\varphi^{-1}h'\varphi$ of $M$, which sends $(1 + T_i)w$ to a basis vector in $M_{2n + r}^r$.
   This implies that $w$ is cyclic, and hence $M_{2n + r}^r$ is irreducible.
@@
 \subsection{Correspondence with Specht modules}
-The following theorem due to Mathas (theorem 5.5 in \cite{Mathas-article}) generalizes the classical branching theorem of the symmetric group.
-It will not be necessary for our present proof of the correspondence, but analogy with $M$ is suggestive.
+The following theorem due to Mathas \cite[Thm.~5.5]{Mathas-article} generalizes the classical branching theorem of the symmetric group.
+This result is not be necessary for our present proof of the correspondence in the case $e > n + r + 1$, but the analogy with $M$ is suggestive.
 \begin{theorem}[Characteristic-free classical branching theorem]
@@
   \end{enumerate}
-  In the case that $e \nmid r+1,\dots,n + r + 1$, \ref{Filtration} and \ref{0 Restriction} are composition series.
+  In the case that $e \nmid r+1,\dots,n + r + 1$, \eqref{Filtration} and \eqref{0 Restriction} are composition series.
 \end{proposition}
@@
   \textbf{(i)}
-  Note that we may identify the subrepresentation of $\Res M_{2n + r}^r$ having anchor at index $2n+r$ with $M_{2n + r - 1}^{r-1}$.
+  Note that the span of the matchings having an anchor at index $2n + r$ is a subrepresentation of $\Res M_{2n + r}^r$;
+  this subrepresentation is easily verified to be isomorphic to $M_{2n + r - 1}^{r-1}$, and we will henceforth refer to it as such.
 
@@
 
-  Given a basis vector $w_j$ containing arc $(i,2n + r)$, $\phi$ is clearly compatible with $(1 + T_{i'})$ with $i' \neq i,i-1$.
-  Further, it is easy to verify that $\phi$ is compatible with $T_i$ by definition of the relevant modules, as well as with $(1 + T_{i-1})$ when $w_j$ does not have anchor $i-1$.
-  The case that $w_j$ has anchor $i-1$ is illustrated in the following commutative diagram:
-  \[
+  We begin by showing commutativity of the following diagram:
+  \begin{equation}\label{Branching commutative diagram}
     \begin{tikzcd}
-      M_{2n + r}^r \arrow[r,"1 + T_i"] \arrow[d,"\phi \circ \pi"] & M_{2n + t}^r \arrow[r,"\pi"] & U \arrow[d,"\phi"]\\
-      M_{2(n-1) + r + 1}^{r+1} \arrow[rr,"1 + T_i"] & & M_{2(n-1) + r + 1}^{r+1}
+      M_{2n + r}^r \arrow[r,"1 + T_i"] \arrow[d,"\phi \circ \pi"] & M_{2n + t}^r \arrow[d,"\phi \circ \pi"]\\
+      M_{2(n-1) + r + 1}^{r+1} \arrow[r,"1 + T_i"] &  M_{2(n-1) + r + 1}^{r+1}
     \end{tikzcd}
-  \]
-  which we may diagram chase as follows
-    \[
-    \QuotDiagram
-  \]
-
-  In each of these cases, linearity of $\SH$-action and $\phi$ give 
+  \end{equation}
+  We illustrate this compatibility in the following graphic.
+  \[
+    \QuotDiagramOne
+    \hspace{50pt}
+    \QuotDiagramTwo
+  \]
+  In both the left and right square, we see that $\phi$ may be treated as an isotopy which ``unfolds'' the last node into an anchor.
+  This isotopy may equivalently be pre- or post-composed with the isotopy defining the action of $1 + T_i$, implying commutativity of \eqref{Branching commutative diagram}.
+
+  Now, using \eqref{Branching commutative diagram}, we have
   \begin{align*}
@@
   This follows from an analogous proof:
-  now, $\phi:\Res M_{2n}^0 \rightarrow M_{2(n-1)+1}^1$ is an isomorphism of representaitons, which is proven to be $\SH$-linear by the same proof.
+  now, $\phi:\Res M_{2n}^0 \rightarrow M_{2(n-1)+1}^1$ is an isomorphism of representations, which is proven to be $\SH$-linear by the same logic.
 \end{proof}
@@
 The irreducibility of $S^{(n+r,n)}$ is integral to arguments of Section \ref{Crossingless Matchings Section};
-without irreducibility of $M_{2n + r}^r$ (conjecturally equivalent to irreducibility of $S^{(n+r,n)}$), $M$ is not necessarily isomorphic to any Specht module $S^\lambda$ or quotient $D^\lambda$, preventing the arguments of Section \ref{Specht Modules Section} from being used.
+without irreducibility of $M_{2n + r}^r$ (which is conjecturally equivalent to irreducibility of $S^{(n+r,n)}$), $M$ is not necessarily isomorphic to any Specht module $S^\lambda$ or quotient $D^\lambda$, preventing the arguments of Section \ref{Specht Modules Section} from being used.
 Further, when $S^{(n+r,n)}$ is reducible, we have $e \mid l$ for some $r+2 \leq l \leq n+r+1$, and hence the filtration provided in Proposition \ref{Filtration} fails to be a composition series.
@@
 
-Due to these difficulties, we instead seek a graphical realization of the irreducible quotient $D^{(n+r,n)}$.
+Due to these difficulties, we additionally seek a graphical realization of the irreducible quotient $D^{(n+r,n)}$.
 In doing so, we may study their branching via Corollary \ref{D Restrictions}, which gives an interesting recurrence in their dimension. 
 \begin{example}
-Let $e = 5$. If $m$ is even, let $t$ be such that $2t = m$;
+Suppose $e = 5$. 
+If $m$ is even, let $t$ be such that $2t = m$;
 if $m$ is odd, let $t'$ be such that $2t' + 3 = m$.
@@
 \end{align*}
-Further, by lemma \ref{Base cases}, we have that $d_2^{0,3} = d_3^{1,2} = 1$;
+Further, by Lemma \ref{Base cases}, we have that $d_2^{0,3} = d_3^{1,2} = 1$;
 hence $d_m^{1,2} = d_{m+1}^{0,3} = f_m$, where $f_m$ is the $n$th \emph{Fibonacci number}.
@@
 In this section, we henceforth restrict to the case $e = 5$ and $r \leq 3$.
-We note that Shor--Jordan have conveniently used complex representations of the braid group on $m$ letters in \cite{Shor} having dimension $f_m$ and $f_{m-1}$.
-We have rescaled these representations, called subrepresentations of the \emph{Fibonacci representation} in Definition \ref{Fib definition}, in order to satisfy the quadratic relation of $\SH$, and we have otherwise modified them to to fit a general parameter $q$ and field $k$ having $e = 5$.
-
-Note that, Shor--Jordan does not characterize this representation any more than the definition and decomposition into four subrepresentations;
+We note that Shor--Jordan \cite{Shor} have conveniently used complex representations of the braid group on $m$ strands in \cite{Shor} having dimensions $f_m$ and $f_{m-1}$.
+In fact, the \emph{Fibonacci representation} of Definition \ref{Fib definition} with $k = \CC$ and $q = e^{-3\pi i /5}$ is a rescaling of Shor--Jordan's Fibonacci representation.
+
+Note that Shor--Jordan does not characterize this representation any more than the definition and decomposition into four subrepresentations;
 we will give a characterization of this representation which is stronger than presented in \cite{Shor}.
@@
 We will start our study of the Fibonacci representation $V := V^m$ by studying low-dimensional cases.
-Recall that we have decomposed $V$ into a direct sum of the subrepresentations $V_{\vs\vs}$, $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$, indexed by the first and last bit of the basis.
+Recall that we have decomposed $V$ into a direct sum of the subrepresentations $V_{\vs\vs}$, $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$, indexed by the first and last bit of the character of the strings in $V$.
 \begin{proposition}
   We have the following isomorphisms of representations:
-  \begin{align*}
+  \begin {align*}
     \emph{$V_{\vs\vs}^2$} &\simeq D^{(1^2)}\\
     \emph{$V_{\vs\vp}^2$} &\simeq D^{(2)}\\
-    \emph{$V_{\vp\vp}^2$} &\simeq V_{\vs\vs}^2 \oplus V_{\vs\vp}.
+    \emph{$V_{\vp\vp}^2$} &\simeq \emph{$V_{\vs\vs}^2 \oplus V_{\vs\vp}$}.
   \end{align*}
@@
 \begin{proposition}
-  The representation $V^3_{\vs\vp}$ is irreducible.
+  The representation \emph{$V^3_{\vs\vp}$} is irreducible.
 \end{proposition}
@@
   A proper nontrivial subrepresentation of $V_{\vs\vp}^3$ must be one-dimensional, and hence an eigenspace of each of these matrices;
-  since $\varb \neq \vara$, the first has eigenspaces given by the spans of basis elements, and since $\vard \neq 0$, these are not eigenspaces of the second.
+  since $\varb \neq \vara$, the $\rho_{T_1}$ has two independent eigenspaces given by the spans each basis element; since $\vard \neq 0$, neither basis element is an eigenvector of $\rho_{T_2}$.
   Hence $V^3_{\vs\vp}$ is irreducible.
@@
 \begin{proposition}\label{Fib irreducibility}
-  The representation $V^m_{\vs\vp}$ is irreducible.
+  The representation \emph{$V^m_{\vs\vp}$} is irreducible.
 \end{proposition}
@@
   We will prove this inductively in $m$.
-  We've already proven it for $V^2_{\vs\vp}$ and $V^3_{\vs\vp}$, so suppose that $V^{m-2}_{\vs\vp}$ is irreducible.
+  We've already proven irreducibility of $V^2_{\vs\vp}$ and $V^3_{\vs\vp}$, so suppose that $V^{m-2}_{\vs\vp}$ is irreducible.
 
   Let $\cbr{v_i}$ be the basis for $V_{\vs\vp}$.
-  Then each $v_i$ is cyclic; indeed, we can transform every basis vector into $(\vs\vp \dots \vp)$ via action by the appropriate $\frac{1}{\vard}(T_i - \varc)$, and we can transform $(\vs\vp \dots \vp)$ into any basis vector by multiplying be the appropriate $\frac{1}{\vard}(T_i - \vare)$.
+  Then each $v_i$ is cyclic; indeed, we can transform every basis vector into $(\vs\vp \dots \vp)$ via action by the appropriate $\frac{1}{\vard}(T_i - \varc)$, and we can transform $(\vs\vp \dots \vp)$ into any basis vector via action by the appropriate $\frac{1}{\vard}(T_i - \vare)$.
   Hence it is sufficient to show that each $v \in V_{\vs\vp}$ generates some basis element.
@@
   We will show that each $v \in V^m_{\vs\vp}$ generates $v_j$.
-  Then, we will have
+  Then, each $v$ will be cyclic, implying the proposition.
 
   Suppose that no basis elements beginning $(\vs\vp\vs\vp)$ have nonzero coefficient in $v$;
-  then, there is some basis element $v_i$ beginning $(\vs\vp\vp\vp)$ having nonzero coefficient in $v$, and the basis element having all other bits identical to $v_i$ except for beginning $(\vs\vp\vs\vp)$ has nonzero coefficient in $T_3v$.
+  then, there is some basis element $v_i$ beginning $(\vs\vp\vp\vp)$ having nonzero coefficient in $v$, and the basis element having all other characters identical to $v_i$ except for the beginning $(\vs\vp\vs\vp)$ has nonzero coefficient in $T_3v$.
   Hence we may assume that at least one element beginning $(\vs\vp\vs\vp)$ has nonzero coefficient in $v$.
@@
   \begin{align*}
-    V^{m-1}_{\vp\vp} \simeq \Res V_{\vs\vp}^m &\simeq V^{m-1}_{\vs\vs} \oplus V^{m-1}_{\vs\vp},\\
-    V_{\vp\vs}^{m-1} \simeq \Res V_{\vs\vs}^m &\simeq V_{\vs\vp}^{m-1}.
+    \emph{$V^{m-1}_{\vp\vp}$} \simeq \emph{$\Res V_{\vs\vp}^m$} &\simeq \emph{$V^{m-1}_{\vs\vs} \oplus V^{m-1}_{\vs\vp}$},\\
+    \emph{$V_{\vp\vs}^{m-1} \simeq \Res V_{\vs\vs}^m$} &\simeq \emph{$V_{\vs\vp}^{m-1}$}.
   \end{align*}
@@
   By the results of Appendix \ref{Algebra}, any two restrictions to distinct subalgebras of $\SH$ generated each by $m-2$ characters are isomorphic.
-  Hence the leftmost isomorphism on each line follows by considering the restrictions to the subalgebra of $\SH$ generated by $\cbr{T_2,\dots,T_{m-1}}$.
+  Using this fact, the leftmost isomorphism on each line follows by considering the restrictions to the subalgebra of $\SH$ generated by $\cbr{T_2,\dots,T_{m-1}}$.
   Further, the rightmost isomorphism on each line follows by considering the restrictions to the subalgebra of $\SH$ generated by $\cbr{T_1,\dots,T_{m-2}}$.
@@
 \begin{corollary}
-  The representation $V^m_{\vs\vs}$ is irreducible.\qed
+  The representation \emph{$V^m_{\vs\vs}$} is irreducible.\qed
 \end{corollary}
@@
 \end{proof}
-Recall the decomposition $V^m \simeq V^m_{\vs\vs} \oplus V^m_{\vs\vp} \oplus V^m_{\vp\vs} \oplus V^m_{\vp\vp}$.
+Recall that we have the decomposition
+\[
+  V^m \simeq V^m_{\vs\vs} \oplus V^m_{\vs\vp} \oplus V^m_{\vp\vs} \oplus V^m_{\vp\vp}.
+\]
 Using this, we may now decompose $V$ into a direct sum of irreducible representations.
-\begin{corollary}
+\begin{corollary}\label{V decomposition into V}
   The representation $V^m$ decomposes into a direct sum of irreducible representations as follows:
   \[
-    V^m \simeq 3V^m_{\vs\vp} \oplus 2V^m_{\vs\vs}.
+    \emph{$V^m \simeq 3V^m_{\vs\vp} \oplus 2V^m_{\vs\vs}$.}
   \]\qed
@@
 
-  By Proposition \ref{Fib irreducibility}, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\mu}$ for some diagrams $\lambda$ and $\mu$.
-  We will show that $\lambda = (n+1,n-2)$ and $\mu = (n+1,n-1)$.
+  By Proposition \ref{Fib irreducibility}, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\mu}$ for some partitions $\lambda,\mu \vdash 2n - 1$.
+  We will show that $\lambda = (n+1,n-2)$ and $\mu = (n,n-1)$.
 
@@
 \end{corollary}
+\begin{proof}
+  This follows from Corollary \ref{V decomposition into V} and Theorem \ref{Fibonacci Theorem}.
+\end{proof}
 
@@
 \section{Conjecture}\label{Conjecture Section}
-Recall that $K_{2n + r}^r := K$ is the direct sum of all copies of the sign representation in $M$.
+Recall that $K := K_{2n + r}^r$ is the direct sum of all copies of the sign representation in $M$.
 Hence the following characterises sign subrepresentations of $M$ completely:
-\begin{proposition}
-  $K \subset M_{2n + r}^r$ is trivial when $e \neq n + r + 1$, and $\dim \, K = 1$ when $e = n + r + 1$.\qed{\color{red} We know this is not accurate anymore, right?}
+\begin{proposition}\label{Preimage of K}
+  Fix some $M := M_{2n + r}^r$.
+  Suppose there is some $n'$ such that $K_{2n' + r}^r \neq 0$.
+  Let $\pi:M_{2n + r}^r \twoheadrightarrow M_{2n' + r}^r$ be the linear map
+  \[
+    \pi := (1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}).
+  \]
+  Then, $\pi^{-1}(K)$ contains any proper subrepresentations of $M$.
 \end{proposition}
-\begin{proposition}
-  Suppose $e < n + r + 1$, and suppose $n'$ is such that $e = n' + r + 1$.
-  Note that $h := (1 + T_1)(1 + T_3)\dots(1 + T_{n - n'})$ maps $M_{2n + r}^r$ onto $M_{2n' + r}^r$.
-  Then, the preimage $h^{-1}(K_{2n + r}^r)$ is a subrepresentation of $M_{2n + r}^r$, and the series
-  \[
-    0 \subset h^{-1}(K_{2n + r}^r) \subset M_{2n + r}^r
-  \]
-  is a composition series of $M_{2n + r}^r$.\qed
-\end{proposition}
+\begin{proof}
+  {\color{orange} Sketch: subrepresentation $W \supsetneq \pi^{-1}(K)$ maps down to proper subrepresentation containing $K$, a contradiction.}
+\end{proof}
+\begin{conjecture}\label{Preimage subrepresentation}
+  In Proposition \ref{Preimage of K}, $\pi^{-1}(K)$ is an irreducible subrepresentation of $M$.
+\end{conjecture}
+\begin{conjecture}\label{Sharp kernel}
+  $K \subset M_{2n + r}^r$ is nontrivial if and only if $e \mid n + r + 1$, in which case it is one-dimensional.
+\end{conjecture} 
+\begin{corollary}
+  $M := M_{2n + r}^r$ has a composition series given by $0 \subset \pi^{-1}(K) \subset M$.
+\end{corollary}
+\begin{proof}
+  {\color{orange} Sketch: by \ref{Sharp kernel}, we have the filtration;
+  by \ref{Preimage subrepresentation}, the first factor is irreducible, and by \ref{Preimage of K} the second factor is irreducible.}
+\end{proof}
+
+\begin{conjecture}
+  For any $n,r$, we have $M_{2n + r}^r \simeq S^{(n+r,n)}$.
+\end{conjecture}
+
+\iffalse
 \begin{proposition}
@@
 \end{proposition}
+\fi
 

### 2019-07-31 tex/Drafts/Draft-3.tex
incorporation of kernel stuff into sections

--- 2019-07-31 tex/comments/2-nat-comments.tex
@@
 
+\subsection{Lack of Sign Subrepresentations when $e\nmid n+r+1$}
+\label{kernel}
+
+Define $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$.
+When the limits are clear, we will simply denote this kernel by $K$.
+Note that $K$ is the direct sum of all sign subrepresentations of $M_{2n+r}^r$.
+In this section, we prove $K$ is trivial for $e \nmid n + r + 1$, thus $M_{2n+r}^r$ has no sign subrepresentations.
+
+For compactness, in this section we use $\sim $ to denote ``proportional to." For convenience, define $M_0^0$ and $M_1^1$ to be the zero representation.
+Note that in this section, as well as later sections characterizing the sign subrepresentation, we do not assume $n>0$.
+
+\begin{definition}
+	We will use the following notation extensively while exploring the structure of the kernel. Examples are given in figure \ref{sub-matching example}. Fix some basis element $\psi\in M_{2n+r}^r$.
+
+	\begin{itemize}
+		\item For $1 \leq a,b \leq 2n + r$ define $\psi(a):=b$ if $a$ and $b$ are matched in $\psi$, and $\psi(a):=a$ if $a$ is an anchor in $\psi$.
+
+		\item Let $r'$ be the number of anchors in $\psi$ in the range $a,\ldots,b$.
+Suppose $1\leq a\leq b\leq 2n+r$ and $\psi(i)\in \{a,\ldots,b\}$ for all $i\in \{a,\ldots,b\}$.
+Define a \emph{sub-matching} $\psi(a,b)$ of $\psi$ to be the basis element $\sigma\in M_{b-a+1}^{r'}$ specified by $\sigma(i)=\psi(i+a-1)-(a-1)$.
+
+		\item For $a,b$ satisfying $1\leq a\leq b\leq 2n+r$, if $\psi(a,b)$ is not a sub-matching, define it to be the ordered set of nodes $(\psi(a),\ldots,\psi(b))$.
+For any other $a,b$, we define $\psi(a,b)$ to be an element of the zero representation $M_0^0$.
+
+		\item Define the \emph{rainbow element} $R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$.
+In other words, the basis element with all anchors to the left followed by a ``rainbow" to the right.
+	\end{itemize}
+
+	\label{sub-matchings}
+\end{definition}
+
+\begin{figure} 
+	\def\cbasisspacing{5mm}
+	$\cbr{
+		\begin{gathered}
+		\GeneralizedMatching{8}{3/8, 4/7, 5/6}{2}{1/1,2/2}{5/4}, \hspace{\cbasisspacing}
+		\Matching{4}{1/4, 2/3}
+		\end{gathered}}$
+	\caption{The rainbow element $R\in M_8^2$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right.
+The nodes $R(4)=7$, $R(5)=6$, so $R(4,7)$ defines a sub-matching.
+Specifically, $R(4,7)=\sigma$.
+Alternatively, $R(3)=8$, so, for instance $R(2,7)$ is not a sub-matching, and refers to the ordered set $(2,8,7,6,5,4)$.
+$R(2,1)$ is an element of the zero representation since $2>1$.}
+	\label{sub-matching example}
+\end{figure}
+
+The following proposition lets us begin to characterize the coordinate vector of any element in $K$, and will serve as the starting point for all following characterizations.
+
+\begin{proposition}
+	Let $w\in M_{2n+r}^r$. If $w\in K$ is nonzero, then the coordinate of the rainbow element $R$ in $w$ is nonzero.
+
+	\label{rainbow nonzero}
+\end{proposition}
+
+\begin{proof}
+	Let $W$ be the set of basis elements with nonzero coordinate in $w$.
+Let $z$ be the maximal number of anchors to the far left in any element $\psi\in W$.
+Formally, $z$ is the greatest positive integer such that there exists some element $\psi\in W$ satisfying $\psi(1)-1=...=\psi(z)-z=0$.
+For some positive integer $j$ define $W^j\subset W$ to be the set of all basis elements in $W$ with $j$ anchors to the far left.
+
+	Suppose $z<r$.
+Then for each $\psi\in W^z$, exactly $z$ anchors are positioned to the far left, so we may define $i_\psi$ to be the position of the next leftmost anchor in $\psi$.
+Fix some $\widehat{\psi}\in W^z$ such that $i_{\widehat{\psi}}\leq i_\psi$ for all $\psi$.
+
+	Define the basis element $\psi':=q^{-1/2}(1+T_{i_{\widehat{\psi}}-1})\widehat{\psi}$.
+First, note that $i_\psi>z+1$, so $i_\psi-1$ is not an anchor and $\psi'\not=0$.
+This follows from the definition of $z$ and $W^z$, which require that the node $z+1$ is not an anchor.
+We will prove that $\psi'$ has nonzero coordinate in $(1+T_{i_{\widehat{\psi}}-1})w$, implying $w\not\in K$.
+
+	It suffices to show that $\widehat{\psi}$ is the only basis element in $W$ brought to $\psi'$ by the action of $(1+T_{i_{\widehat{\psi}}-1})$.
+Formally, we will show that if $\sigma\in W$ and $(1+T_{i_{\widehat{\psi}}-1})\sigma\sim \psi'$, then $\sigma=\widehat{\psi}$.
+
+	Immediately, we may intuit a few properties of $\psi'$:
+	\begin{enumerate}[label={(\roman*)}]
+		\item $\psi'$ still has $z$ anchors on the left.
+		\item Defining $i_{\psi'}$ to be the next leftmost anchor, $i_{\psi'}<i_{\widehat{\psi}}$
+	\end{enumerate}
+
+	Together, (i) and (ii) imply $\psi'\not\in W$. So, if $(1+T_{i_{\widehat{\psi}}-1})\sigma\sim \psi'$, $q^{-1/2}(1+T_{i_{\widehat{\psi}}-1})\sigma=\psi'$.
+
+	Define $\sigma':=q^{-1/2}(1+T_{i_{\widehat{\psi}}-1})\sigma$.If $\sigma\not\in W^z$, $\sigma'$ will have $z$ anchors at the far left only if $\sigma'\in W^{z-1}$ and the $z$th leftmost anchor is at position $i_{\widehat{\psi}}$.
+But then the position of the $z+1$st anchor is unchanged by the action, and must be at position greater than $i_{\widehat{\psi}}$, so from (ii) $\sigma'\not=\psi'$.
+If $\sigma\in W^z$, $\sigma'$ will have anchor at $i_{\psi'}$ if and only if $i_\sigma=i_{\widehat{\psi}}$ and $\sigma(i_{\widehat{\psi}}-1)=\widehat{\psi}(i_{\widehat{\psi}}-1)$.
+Since these are the only three indices altered by action of $(1+T_{i_{\widehat{\psi}}-1})$ on $\sigma$, if $(1+T_{i_{\widehat{\psi}}-1})\sigma\sim \psi'$ this implies $\sigma=\widehat{\psi}$ as desired.
+So if $z<r$ $w$ is not in the desired kernel.
+
+	\vspace{1mm}
+	We have proven that there exists an element in $W$ with all anchors to the far left, or equivalently that $W^r$ is nonempty.
+Now we must prove that $R\in W^r$.
+The proof is analogous to the previous case.
+First we define subsets $W^r_j\subset W^r$ that have the top $j$ arcs of the rainbow, and define $y$ to be the most arcs any element has.
+In the previous proof, we showed that if we move the next left-most anchor further left, the image of $w$ under that transposition will be nonzero.
+In this proof, we will show that if we expand the next-largest arc, the image of $w$ under that transposition will be nonzero.
+
+	\vspace{1mm}
+	Suppose $z=r$ but $R\not\in W^r$ (so $R\not\in W$).
+Let us define a sequence of subsets $W^r_i\subset W^r$ to be the set of elements in $W^r$ with the top $i$ humps of the rainbow.
+Formally, $W^r_0:=W^r$, $W^r_{i+1}:=\{\upsilon\in W^r_i| \upsilon(r+i+1)=2n+r-i \}$.
+Since $R\not\in W^r$,  there exists some positive integer $y$ less than $n-1$ such that $W^r_{y+1}=\emptyset$; $y$ is the largest number of contiguous top level rainbow humps that any element in $W^r$ has.
+
+	Choose $\widehat{\upsilon}\in W^r_t$ such that $\widehat{\upsilon}(r+t+1)\geq \upsilon(r+t+1)$ for all $\upsilon\in W^r_t$.
+Define the basis element $\upsilon':=q^{-1/2}(1+T_{\widehat{\upsilon}(r+t+1)})\widehat{\upsilon}$.
+
+	First, note that $\widehat{\upsilon}(r+t+1)<2n+r-t$, so:
+	\begin{enumerate}[label={[\roman*]}]
+		\item $\upsilon'(r+t+1)>\widehat{\upsilon}(r+t+1)$ 
+		\item For $0\leq j\leq t$, $\upsilon'(r+j)=\widehat{\upsilon}(r+j)=2n+r-j+1$.
+	\end{enumerate}
+
+	These properties are analogous to properties (i) and (ii) used earlier in this proof.
+As before, these imply that $\upsilon'\not\in W$, so, for $\sigma\in W$, if $(1+T_{\widehat{\upsilon}(r+t+1)})\sigma\sim \upsilon'$, $q^{-1/2}(1+T_{\widehat{\upsilon}(r+t+1)})\sigma=\upsilon'$.
+
+	We will prove that $\upsilon'$ has nonzero coordinate in $(1+T_{\widehat{\upsilon}(r+t+1)})w$, implying $w\not\in K$.
+Again, it is sufficient to show that, for $\sigma\in W$, $q^{-1/2}(1+T_{\widehat{\upsilon}(r+t+1)})\sigma=\upsilon'$ implies $\sigma=\widehat{\upsilon}$.
+
+	Define $\sigma':=q^{-1/2}(1+T_{\widehat{\upsilon}(r+t+1)})\sigma$.
+Suppose $\sigma\not\in W^r_t$.
+To satisfy [ii], we must have $\sigma\in W^r_{t-1}$ and $\sigma(r+t)=\widehat{\upsilon}(r+t+1)$.
+But then $\sigma(r+t+1)<\widehat{\upsilon}(r+t+1)$ is unchanged by action of $(1+T_{\widehat{\upsilon}(r+t+1)})$, and $\sigma'$ does not satisfy [i], so $\sigma'\not=\upsilon'$.
+If $\sigma\in W^r_t$, to satisfy $\sigma'(r+t+1)=\upsilon'(r+t+1)$, we must have $\sigma(r+t+1)=\widehat{\upsilon}(r+t+1)$ and $\sigma(\widehat{\upsilon}(r+t+1)+1)=\widehat{\upsilon}(\widehat{\upsilon}(r+t+1)+1)$.
+Since these are the only two matchings altered by the transposition, if $q^{-1/2}(1+T_{\widehat{\upsilon}(r+t+1)})\sigma=\upsilon'$ we must have that $\sigma=\widehat{\upsilon}$ as desired.
+Thus, if $w\in K$ is nonzero, $R$ has nonzero coordinate in $w$.
+\end{proof}
+
+Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively.
+Examples are pictured in \ref{shifted rainbow}.
+Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.
+
+\begin{figure}
+	\def\cbasisspacing{5mm}
+	$\cbr{
+		\begin{gathered}
+		\Matching{8}{1/8, 2/7, 3/6, 4/5}, \hspace{\cbasisspacing}
+		\Matching{8}{1/8, 2/7, 3/4, 5/6}, \hspace{\cbasisspacing}
+		\Matching{8}{1/8, 2/3, 4/7, 5/6}, \hspace{\cbasisspacing}
+		\Matching{8}{1/2,3/8,4/7,5/6}
+		\end{gathered}}$
+	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right}
+	\label{shifted rainbow}
+\end{figure}
+
+Define $Q_n:=(q^n+...+1)/q^{n/2}(-1)^n$ for $n\in \{0,1,...\}$.
+The following proposition says that, for any element in the kernel, if some basis element $y$ has coordinate $c$ in that element, and if $y$ has a rainbow sub-matching, the basis elements where you replace that sub-matching by the shifted rainbow matchings $R_{L,i}$ or $R_{R,i}$ both have coordinate $Q_ic$ in the kernel element.
+
+\begin{proposition}
+	Let $w$ be an element in the kernel intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation.
+Let $y$ be a basis element with coordinate $c$ in $w$.
+Suppose $\exists a,b$ such that $y(a,b)=R$, the rainbow element.
+Define the basis elements $\theta_i,\phi_i$ by $\theta_i(1,a-1)=\phi(1,a-1)=y(1,a-1)$, $\theta_i(b+1,2n)=\phi(b+1,2n)=y(b+1,2n)$, $\theta_i(a,b)=R_{R,i}$, $\phi_i(a,b)=R_{L,i}$ (leave $\theta_i$ or $\phi_i$ undefined for any $i$ where $R_{R,i},R_{L,i}$ are undefined, respectively).
+The coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.
+
+	\label{shifted rainbow coeffs}
+\end{proposition}
+
+Proof of this proposition requires a simple algebraic fact that will be used throughout this document, so I state it as a lemma.
+
+\begin{lemma}
+	$Q_1Q_n-Q_{n-1}=Q_{n+1}$
+
+	\label{Q alg}
+\end{lemma}
+
+\textit{Proof of lemma.}
+
+\begin{align*}
+Q_1Q_n-Q_{n-1}=&\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}\\
+=&\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}\\
+=&\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}
+\end{align*}
+
+Now let us prove the proposition.
+
+\begin{proof}
+	Consider acting on $w$ by an element $(1+T_z)$.
+The coordinate of $\phi_i$ in $(1+T_z)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_z)$.
+Specifically, it will be $(1+q)c\iota+(q^1/2)\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.
+
+	Let $n:=a+b-1$ and $r$ be the number of anchors in $y(a,b)$.
+Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$.
+This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in \ref{shifted relations}.
+I claim the following:
+
+	\begin{center}
+		\textit{claim}:
+		The only basis elements $\psi$ where $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist\footnote{we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$}.
+
+	\end{center}
+
+	Note that the action of any $(1+T_z)$ on a basis element $\psi$ creates exactly two lines: an arc of length two connecting $z$ and $z+1$, and either an anchor or an arc of length $\geq 2$ connecting $\psi(z)$ and $\psi(z+1)$.\footnote{Although this fact follows directly from our definition of the representation, it will be used throughout the document, so it is important that the reader understands it.\label{two humps created}} The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.
+
+	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in \ref{shifted relations}.
+Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition.
+Me note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
+Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$.
+If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\psi(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor.
+All other matchings remain unchanged, so this implies $\psi=\phi_{i+1}$.
+Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\psi=\phi_{i-1}$.
+For boundary cases, note that for $\phi_0=\theta_0$, the only other basis element sent to this by the middle transposition is $\phi_1=\theta_1$.
+Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case gives no new information.
+Lastly, note that our argument was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors.
+Thus the claim is proved.
+
+	Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction:
+
+	Acting by $(1+T_{a-1+r+n/2})$ on $w$, the new coordinate of $\phi_0=y$ is $(q+1)c+q^{1/2}c_{\phi_1}$ where $c_{\phi_1}$ is the coordinate of $\phi_1$ in $w$.
+Since $w$ is in the kernel, we have $(q+1)c+q^{1/2}c_{\phi_1}=0=>c_{\phi_1}=Q_1c$.
+$\phi_1=\theta_1$ so this gives us all our base cases.
+
+	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$.
+By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_i=0$ so $c_{\phi_{i+1}}=Q_1Q_i-Q_{i-1}=Q_{i+1}$ by lemma \ref{Q alg}.
+$\theta_i$ is an identical proof, so the proposition follows.
+
+	\begin{figure}
+		\[
+		\GeneralizedAction{8}{3/4,5/8,6/7}{2}{1/1,2/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{(1+q)}
+		\]
+		\[
+		\GeneralizedAction{8}{2/3,5/8,6/7}{2}{1/1,4/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
+		\]
+		\[
+		\GeneralizedAction{8}{3/8,4/5,6/7}{2}{1/1,2/2}{1.25}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
+		\]
+		\caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $M_{8}^2$ and $i=2$.}
+		\label{shifted relations}
+	\end{figure}
+\end{proof}
+
+We are now ready to prove the central proposition of this section.
+
+\begin{proposition}
+	Let $W_{2n+r}^r$ be a generalized crossingless matchings representation. Suppose $e$ does not divide $n+r+1$. Then $K=0$.
+
+	\label{trivial kernel}
+\end{proposition}
+
+\begin{proof}
+	Suppose $K\not=0$.
+Take nonzero $w\in K$.
+By Proposition \ref{rainbow nonzero}, the coordinate of the rainbow vector $R$ is nonzero; suppose the coordinate is $c$.
+By proposition \ref{shifted rainbow coeffs}, the coordinates of the basis elements $R_{L,n+r-1}$ and $R_{L,n+r-2}$ are $Q_{n+r-1}c$ and $Q_{n+r-2}c$ respectively.
+
+	Consider the coordinate of $R_{L,n+r-1}$ in $(1+T_1)w$.
+Using the same logic as in the proof of proposition \ref{shifted rainbow coeffs}, we note that if a basis element $\psi$ has no anchor at position $3$ and is not equal to $R_{L,n+r-2}$, $(1+T_1)\psi\not\sim R_{L,n+r-1}$.
+Thus the desired coordinate is equal to $(1+q)Q_{n+r-1}c+q^{1/2}Q_{n+r-2}c=-q^{1/2}Q_{n+r}c$ by lemma \ref{Q alg}.
+Since $w\in K$, we must have $-q^{1/2}Q_{n+r}c=0$.
+Me have that $c$ is nonzero, and we assume $q$ nonzero, and $Q_{n+r}$ is zero iff $q$ is a root of $q^{n+r}+...+1$, implying $e|n+r+1$.
+Thus we have arrived at contradiction, and $K=0$.
+\end{proof}
+
 \subsection{Irreducibility of $M$}
@@
 
-{\color{magenta} We can make this section-level and work it out, I'm sure.}
-
-\subsection{Kernels and further work}
-
-{\color{magenta} Better subsection label: Sign Subrepresentations of $M$.
-If used, should remind the reader in the beginning that $K$ is a direct sum of all sign subrepresentations (by dimensionality, just a sign representation if it's nonzero).}
-
-In this section, we characterize $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$ for $e \nmid n + r + 1$ and for $e=n+r+1$.
-When the representation is clear {\color{magenta} When the indices $2n + r, r$ are clear\ldots}, we will simply denote this kernel as $K$ or $\cap\ker(1+T_i)$.
-For compactness, in this section we use $\sim $ to denote "proportional to".
-For convenience, define $M_0^0$ to be the zero representation.
-{\color{magenta} Replace $\backslash$text\{ker\} with $\backslash$ker;
-I've done it for this document already.}
-
-{\color{magenta} Next section needs new name (perhaps ``The case $e \nmid n+r+1$''?) We can handle the reference 3.3 -> this section near proposition 3.3, and perhaps even name 3.3 by it's name in this section.}
-\subsubsection{Proposition \ref{Trivial}}
-\label{kernel}
-\begin{definition}
-
-	Fix some basis element $\psi\in M_{2n+r}^r$.
-For $1 \leq a,b \leq 2n + r$ define $\psi(a):=b$ iff $a$ and $b$ are matched in $\psi$, $\psi(a):=a$ if $a$ is an anchor in $\psi$.
-Given that $\psi$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $\psi(a,b)$ of $\psi$ to be the basis element $\sigma\in M_{b-a+1}^{r'}$ specified by $\sigma(i)=\psi(i+a-1)-a+1$.
-This sub-matching is defined for $a<b$ when $\psi(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$.
-See \ref{sub-matching example}.
-  {\color{magenta} For anybody reading via paper or something not handling hrefs, it's better to refer to this as Figure \ref{sub-matching example}.}
-
-  {\color{magenta} use $\backslash$emph for emphasis (in this environment, it will be italicized)}
-
-  If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, {\color{magenta} for nodes $a,b$ satisfying $a \leq b$ (or $1 \leq a \leq b \leq 2n+r)$.}$\psi(a,b)$ will always refer to those nodes and they're {\color{magenta} their} matchings, though it may not be a sub-matching unless specified.{\color{magenta} No need to say ``unless specified''} For any other $a,b$, we define $\psi(a,b)$ to be an element of the representation with no nodes.{\color{magenta} What other $a,b$?
-Is this $a > b$, $a,b \notin \cbr{1,\dots,2n+r}$, etc?
-Also, can this just be defined the unique element of the zero representation?}
-
-	\label{sub-matchings}
-\end{definition}
-
-\begin{figure} 
-	\def\cbasisspacing{5mm}
-	$\cbr{
-		\begin{gathered}
-		\Matching{6}{1/2, 3/6, 4/5}, \hspace{\cbasisspacing}
-		\Matching{4}{1/4, 2/3}
-		\end{gathered}}$
-	\caption{$\psi\in M_6^0$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right. $\psi(3,6)=\sigma$. 
-    {\color{magenta} and }
-  $\psi(2,5)$ is not a sub-matching.}
-	\label{sub-matching example}
-\end{figure}
-
-Define the rainbow element 
-{\color{magenta} $\backslash$emph.} 
-$R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$. In other words, the basis element with all anchors to the left then a rainbow.
-{\color{magenta} to the left, followed by a ``rainbow'' on the right.}
-
-\begin{proposition}
-  Let $w$ be an arbitrary vector in $M_{2n+r}^r$.
-  {\color{magenta} No need to say ``arbitrary.''} 
-  I claim that if $w\in \cap\ker(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero. 
-  {\color{magenta} No need to say ``I claim.''}
-	\label{rainbow nonzero}
-\end{proposition}
-
-\begin{proof}
-  Let $Y$ be the set of basis elements 
-  {\color{magenta} of $M_{2n + r}^r$} 
-  with nonzero coordinate in $w$. 
-  Let $z$ be the greatest integer such that there exists $y\in Y$ where 
-  {\color{magenta} some element $y \in Y$ satisfying\ldots} 
-  $y(1)-1=...=y(z)-z=0$, and let $U\subset Y$ be the set of such $y$. 
-  In other words, $U$ is the set of basis elements in $Y$ which have the most anchors to the far left.
-
-	Suppose $z<r$. 
-  Then for each $y\in U$ there exists a minimal $i_y>z+2$ such that $y(i_y) =0$ 
-  {\color{magenta} $y(i_y) = i_y$, or just $y$ contains an anchor at $i_y$}. 
-  In other words, $i_y$ is the position of the next leftmost anchor in $y$.
-  {\color{magenta} totally subjective, buy I would put a new paragraph here.}
-
-  Fix $\tilde{y}$ such that $i_{\tilde{y}}\leq i_y$ for all $y$. 
-  {\color{magenta} Is this just some $\tilde y$ for each $y$?}
-  Then I claim the basis element $y':=q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}$ has nonzero coordinate in $(1+T_{i_{\tilde{y}}-1})w$, implying $w\not\in \cap\ker(1+T_i)$.
-  {\color{magenta} Rather than ``I claim\ldots to see this'', say something like ``We will show\ldots to do so''}
-  To see this, we can show that $\tilde{y}$ is the only basis element in $Y$ such that $(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$.
-$y'$ still has $z$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$.
-  If $x\in Y,\not\in U$,
-  {\color{magenta} If $x \in Y$ and $x \not\in U$, then\ldots}
-  the basis element $x'$ proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$.
-If $x\in U$, $x'$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$.
-Since this is the only match altered by action of $(1+T_{i_{\tilde{y}}-1})$ on $x$, if $(1+T_{i_{\tilde{y}}-1})x\sim y'$ this implies $x=\tilde{y}$.
-So if $z<r$ $w$ is not in the desired kernel.
-  {\color{magenta} Nice.}
-
-  {\color{magenta} I think a very short vspace would be nice here.}
-	Suppose $z=r$ but $R\not\in U$ (so $R\not\in Y$).
-  {\color{magenta} Doesn't $U$ just depend on $z$, so that $R \in U$ whenever $z=r$?}
-  Let us define a sequence of subsets of $U$ in the following way: $U_0:=U$, $U_{i+1}:=\{u\in U_i| u(r+i+1)=2n+2r-i+1 \}$. Since $R\not\in U$, $\exists t<n-1$ such that $U_{t+1}=\emptyset$. 
-  {\color{magenta} Don't need ``let us.''}
-  Choose $\tilde{u}\in U_t$ such that $\tilde{u}(r+t+1)\geq u(r+t+1)$ for all $u\in U_t$. Consider the basis element $u':=q^{-1/2}(1+T_{\tilde{u}(r+t+1)})\tilde{u}$.
-
-  {\color{magenta} No ``I claim.'' Also, I would put a new paragraph here, or after the next line (fair if you disagree). Also, maybe say that this is analogous to before.}
-  I claim that $\tilde{u}$ is the only element in $Y$ such that $(1+T_{\tilde{u}(r+t+1)})\tilde{u}\sim u'$, again implying that $w$ is not in the desired kernel.
-$u'$ still has $r$ anchors on the left, $u'(r+i)=2n+2r-i+2$, $1\leq i\leq t$, and $u'(r+t+1)>\tilde{u}(r+t+1)$, so $u'\not\in Y$.
-If $x\in Y,\not\in U$,  the basis element $x'$ proportional to $(1+T_{\tilde{u}(r+t+1)})x$ will have $r$ leftmost anchors only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
-Similarly, if $x\in U,\not\in U_t$, the basis element $x'$ will have the property $x'(r+i)=2n+2r-i+2$ for all $i\leq t$ only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$.
-If $x\in U_t$, $x'(r+t+1)=u'(r+t+1)$ if and only if $x(r+t+1)=\tilde{u}(r+t+1)$ and $x(x(r+t+1)+1)=\tilde{u}(\tilde{u}(r+t+1)+1)$ (since $u'\not \in Y$).
-These are the only matches altered by the action $(1+T_{\tilde{u}(r+t+1)})$, so this implies $x=\tilde{u}$.
-Thus we have proved that if $R\not\in Y$, $w$ is not in the kernel.
-
-\end{proof}
-
-{\color{magenta} This might read better as ``Let $R_{r,i},R_{L_i}$ be the basis elements formed by ''moving.``
-Also, it may be nice to just define it formally and point to Figure \ref{shifted rainbow};
-the moving analogy is clear from the figure.
-}
-Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively.
-Examples are pictured in {\color{magenta} Figure \ref{shifted rainbow}}.
-Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.{\color{magenta} align might be nicef for these definitions}
-
-\begin{figure}
-	\def\cbasisspacing{5mm}
-	$\cbr{
-		\begin{gathered}
-		\Matching{8}{1/8, 2/7, 3/6, 4/5}, \hspace{\cbasisspacing}
-		\Matching{8}{1/8, 2/7, 3/4, 5/6}, \hspace{\cbasisspacing}
-		\Matching{8}{1/8, 2/3, 4/7, 5/6}, \hspace{\cbasisspacing}
-		\Matching{8}{1/2,3/8,4/7,5/6}
-		\end{gathered}}$
-	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right
-  {\color{magenta} The elements $R_{L,0},\dots,R_{L_3} \in W_8^0$ are\ldots}
-}
-	\label{shifted rainbow}
-\end{figure}
-
-Define $Q_n:=(q^n+...+1)/q^{n/2}(-1)^n$ for $n\in \{0,1,...\}$.
-The following proposition says that, for any element in the kernel, if some basis element $y$ has coordinate $c$ in that element, and if $y$ has a rainbow sub-matching, the basis elements where you replace that sub-matching by the shifted rainbow matchings $R_{L,i}$ or $R_{R,i}$ both have coordinate $Q_ic$ in the kernel element.
-
-\begin{proposition}
-  Let $w$ be an element in the kernel 
-  {\color{magenta} probably good to refer to it as $K$, or remind the reader of the indices on $T$. Also, why the subscript $T_z$?
-  In general, we may shorten this to ``Let $w$ be an element in $K \subset M$'' to get down on the length of this proposition.
-}
-  intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation. Let $y$ be a basis element with coordinate $c$ in $w$. 
-  {\color{magenta} Better to say ``there exist'' for proposition statements.
-  Also, the reader probably knows what $R$ is by now? Maybe it's good to leave it in, idk, but this statement is already very wordy.
-}
-  Suppose $\exists a,b$ such that $y(a,b)=R$, the rainbow element. 
-  {\color{magenta} If it's still too wordy, maybe move the definition of $\theta,\phi$ outside of the statement? Idk.}
-  Define the basis elements $\theta_i,\phi_i$ by $\theta_i(1,a-1)=\phi(1,a-1)=y(1,a-1)$, $\theta_i(b+1,2n)=\phi(b+1,2n)=y(b+1,2n)$, $\theta_i(a,b)=R_{R,i}$, $\phi_i(a,b)=R_{L,i}$ (leave $\theta_i$ or $\phi_i$ undefined for any $i$ where $R_{R,i},R_{L,i}$ are undefined, respectively).
-The coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.
-
-	\label{shifted rainbow coeffs}
-\end{proposition}
-
-Proof of this proposition requires a simple algebraic fact that will be used throughout this document, so I state it as a lemma.
-{\color{magenta}We will use the following algebraic lemma\ldots.
-Also, the reader knows that you're stating it, no need to tell them.
-}
-
-\begin{lemma}
-	$Q_1Q_n-Q_{n-1}=Q_{n+1}$
-
-	\label{Q alg}
-\end{lemma}
-
-\begin{proof}[Proof of lemma]
-\begin{align*}
-Q_1Q_n-Q_{n-1}=&\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}\\
-=&\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}\\
-=&\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}
-\end{align*}
-\end{proof}
-
-{\color{magenta} Nice proof.
-Can be specified by using $\backslash$begin\{proof\}[Proof of lemma], as I've fixed in the text here.}
-
-Now let us prove the proposition.
-{\color{magenta} we will\ldots
-Guiding text may 
-}
-
-\begin{proof}
-  Consider acting on $w$ by an element $(1+T_z)$.
-The coordinate of $\phi_i$ in $(1+T_z)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_z)$.
-Specifically, it will be $(1+q)c\iota+(q^{1/2})\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.
-  {\color{magenta} fixed exponent on $q^{1/2}$.}
-
-  Let $n:=a+b-1$ and {\color{magenta} let } $r$ be the number of anchors in $y(a,b)$.
-Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$.
-This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in {\color{magenta} Figure }\ref{shifted relations}.
-  I claim the following:
-  {\color{magenta} Avoid ``I claim''}
-
-  {\color{magenta} put in claim* environment}
-	\begin{center}
-		\textit{claim}:
-		The only basis elements $\psi$ where $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist\footnote{we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$}.
-
-	\end{center}
-
-	Note that the action of any $(1+T_z)$ on a basis element $\psi$ creates exactly two lines: an arc of length two connecting $z$ and $z+1$, and either an anchor or an arc of length $\geq 2$ connecting $\psi(z)$ and $\psi(z+1)$.\footnote{Although this fact follows directly from our definition of the representation, it will be used throughout the document, so it is important that the reader understands it.\label{two humps created}} The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.
-
-  {\color{magenta} $\backslash$begin\{proof\}[Proof of claim], avoid ``let us'' throughout}
-
-	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$,
-  {\color{magenta} awkward wording}
-  as shown in 
-  {\color{magenta} Figure} 
-  \ref{shifted relations}. Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition. Me
-  {\color{magenta} typo} 
-  note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
-Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$.
-If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\psi(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor.
-All other matchings remain unchanged, so this implies $\psi=\phi_{i+1}$.
-Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\psi=\phi_{i-1}$.
-For boundary cases, note that for $\phi_0=\theta_0$, the only other basis element sent to this by the middle transposition is $\phi_1=\theta_1$.
-Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case gives no new information.
-Lastly, note that our argument
-  {\color{magenta} \ldots the above argument was \ldots and hence an analogous argument without anchors illustrates the $\theta_i$ case.}
-  was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors. Thus the claim is proved.
-	  {\color{magenta} three ideas for this:
-    first: break into smaller paragraphs.
-    Second: assign a variable to $a - 1 +  + n/2$ for clarity.
-    Third: here and elsewhere, when saying a dense statement, examine whether it's good to put an intuitive statement for it before, after, or if it's more clear/concise to not include it at all.
-  }
-
-  Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction
-  {\color{magenta} on $i$}:
-
-	Acting by $(1+T_{a-1+r+n/2})$ on $w$, the new coordinate of $\phi_0=y$ is $(q+1)c+q^{1/2}c_{\phi_1}$ where $c_{\phi_1}$ is the coordinate of $\phi_1$ in $w$.
-Since $w$ is in the kernel, we have $(q+1)c+q^{1/2}c_{\phi_1}=0=>c_{\phi_1}=Q_1c$.
-$\phi_1=\theta_1$ so this gives us all our base cases.
-
-  {\color{magenta} Suppose \ldots then,}
-	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$.
-By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_i=0$ so $c_{\phi_{i+1}}=Q_1Q_i-Q_{i-1}=Q_{i+1}$ by lemma \ref{Q alg}.
-$\theta_i$ is an identical proof, so the proposition follows.
-
-	\begin{figure}
-		\[
-		\GeneralizedAction{8}{3/4,5/8,6/7}{2}{1/1,2/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{(1+q)}
-		\]
-		\[
-		\GeneralizedAction{8}{2/3,5/8,6/7}{2}{1/1,4/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
-		\]
-		\[
-		\GeneralizedAction{8}{3/8,4/5,6/7}{2}{1/1,2/2}{1.25}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
-		\]
-		\caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $M_{8}^2$ and $i=2$.}
-		\label{shifted relations}
-	\end{figure}
-\end{proof}
-
-We are now ready to prove proposition \ref{Trivial}.
-{\color{magenta} Restate the proposition. I will reference forward to this part.
-  Upon rereading this in the new structure, I actually do agree with you that we could just do away with Proof 2.
-  With the last batch of edits, this is so much more manageable and clear (and less technical) than I remembered it being.
-}
-
-\begin{proof}
-	Suppose $\cap\ker(1+T_i)=K\not=0$.
-  {\color{magenta} More usual to say $K := \cap \ker(1 + T_i) = 0$.}
-  Take nonzero $w\in K$.
-By Proposition \ref{rainbow nonzero}, the coordinate of the rainbow vector $R$ is nonzero; suppose the coordinate is $c$.
-By proposition \ref{shifted rainbow coeffs}, the coordinates of the basis elements $R_{L,n+r-1}$ and $R_{L,n+r-2}$ are $Q_{n+r-1}c$ and $Q_{n+r-2}c$ respectively.
-
-	Consider the coordinate of $R_{L,n+r-1}$ in $(1+T_1)w$.
-Using the same logic as in the proof of proposition \ref{shifted rainbow coeffs}, we note that if a basis element $\psi$ has no anchor at position $3$ and is not equal to $R_{L,n+r-2}$, $(1+T_1)\psi\not\sim R_{L,n+r-1}$.
-Thus the desired coordinate is equal to $(1+q)Q_{n+r-1}c+q^{1/2}Q_{n+r-2}c=-q^{1/2}Q_{n+r}c$ by lemma \ref{Q alg}.
-Since $w\in K$, we must have $-q^{1/2}Q_{n+r}c=0$.
-Me have that $c$ is nonzero, and we assume $q$ nonzero, and $Q_{n+r}$ is zero iff $q$ is a root of $q^{n+r}+...+1$, implying $e|n+r+1$.
-Thus we have arrived at contradiction, and $K=0$.
-\end{proof}
-
-{\color{magenta} New name, such as ``Charactrizing $K$'' or ``Characterizing the sign subrepresentations.''
-Also, lowercase section titles.}
-\subsubsection{Kernel Basis}
-
-In this section, we determine an explicit basis for $K$ when $e=n+r+1$, assuming $K\not=0$. In the next section, we prove $K\not=0$.
+\section{Sign Subrepresentations}
+In the previous section, we proved $M_{2n+r}^r\simeq S^{(n+r,n)}$ under certain conditions of $e$.
+In this proof, we used the fact that, given our conditions on $e$, we only projected down to cases with no sign subrepresentation.
+
+In this section, we prove that there is exactly one sign subrepresentation when $e=n+r+1$, and give an explicit basis for this subrepresentation.
+
+\subsection{Kernel Basis}
+
+Recall $K:= K^r_{2n+r}$, defined in section \ref{kernel}, is the direct sum of all sign subrepresentations.
+Here we determine an explicit basis for $K$ when $e=n+r+1$, assuming $K\not=0$.
+In the next section, we prove $K\not=0$.
 
@@
 
-\subsubsection{Nontrivial Kernel}
+\subsection{Nontrivial Kernel}
 

### 2019-07-31 tex/Drafts/Draft-3.tex
aaa

@@
   \indentlabel{\@ifnotempty{#2}{\ignorespaces#1 #2\quad}}#3}
-  \let\tocsubsubsection\tocsubsection% Update for \subsubsection
+%\let\tocsubsubsection\tocsubsection% Update for \subsubsection
 %...
@@
 \newcommand\@dotsep{4.5}
-  \def\@ocline#1#2#3#4#5#6#7{\relax
+\def\@tocline#1#2#3#4#5#6#7{\relax
   \ifnum #1>\c@tocdepth % then omit
@@
   \fi}
-
+\AtBeginDocument{%
+\expandafter\renewcommand\csname r@tocindent0\endcsname{0pt}
+}
 \def\l@subsection{\@tocline{2}{0pt}{2.5pc}{5pc}{}}
@@
 
-  \subsection{Irreducibility of $S^\lambda$}
+  \subsection{Irreducibility of Specht modules}
   Let $\ell$ be the characteristic of $k$;
@@
   \end{proof}
-  \subsection{Branching theorems of Specht modules}
+  \subsection{Branching theorems for Specht modules}
   In this section as well as later sections, we will consider the restriction of representations of $\SH$ to particular subalgebras isomorphic to $\SH_{k,q}\prn{S_{2n + r - 1}}$.
@@
 In this section, we analyze the crossingless matchings representation $M := M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \simeq S^{(n+r,n)}$ under certain conditions in $e$.
-We begin by proving irreducibility of $M_{2n + r}^r$ whenever $e \nmid r+2,r+3,\dots,n+r+1$;
+We begin by proving that $M_{2n + r}^r$ contains no subrepresentations isomorphic to the sign representation (henceforth referred to as \emph{sign subrepresentations}) when $e \nmid n + r + 1$.
+Using this, we prove irreducibility of $M_{2n + r}^r$ whenever $e \nmid r+2,r+3,\dots,n+r+1$;
 when $e>n$, this is true if and only if $S^{(n+r,n)}$ is irreducible by Corollary \ref{S irreducibility}.
-This is proven via an inductive process; if $e \nmid n + r + 1$, then $M$ contains no sign subrepresentation, and this allows us to ``project'' down to the case $M_{2(n-1) + r}^r$ and deduce irreducibility of $M$ from irreducibility of this representation.
 
@@
 \end{proof}
-
-\subsection{Lack of Sign Subrepresentations when $e\nmid n+r+1$}
+In particular, Lemma \ref{Base cases} is the base case in an inductive proof that $M_{2n + r}^r \simeq S^{(n+r,n)}$ whenever $e > n + r + 1$.
+
+\subsection{Sign subrepresentations when $e\nmid n+r+1$}\,
 \label{kernel}
+
+{\color{magenta} \Huge PLEASE ADDRESS: $W$ needs to be replaced with $M$.} 
+{\color{magenta} Also, titles should be lower case (I fixed in this document), and can be more descriptive\ldots e.g.
+``Sign subrepresentations of the crossingless matching; characterizing the sign subrepresentation; Sign subrepresentations when e = n+r+1.}
 
@@
 
-\subsection{Irreducibility of $M$}
+\subsection{Irreducibility of the crossingless matchings representation}
+We will first give a lemma on cyclic vectors.
+Then, we will use triviality of $K$ to ``project down'' onto a copy of $M := M_{2n + r}^r$ with strictly fewer nodes;
+this will prove inductively that $M$ is irreducible when $e > n + r + $.
+
 We refer to a vector $w \in M$ satisfying $\SH w = M$ as \emph{cyclic}.
-It is a classical result that a representation $W$ is irreducible if and only if every nonzero element of $W$ is cyclic \cite{Etingof}.
+It is a classical result that a representation $M$ is irreducible if and only if every nonzero element of $M$ is cyclic \cite{Etingof}.
 We will prove irreducibility by showing that every nonzero $w \in M$ is cyclic;
@@
 \begin{proof}
+  {\color{magenta} I will address the missing part tomorrow.}
   We have already proven this in the $r = 0$ case, so suppose that $r > 0$.
 
-  Note that, between anchors at indices $a<a'$ having no arc at index $b$ with $a < b < a'$, the $M_{a'-a}^0$ case allows us to generate the basis vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.
+  Note that, between anchors at indices $a<a'$ having no anchor at index $b$ with $a < b < a'$, the $M_{a'-a}^0$ case allows us to generate the basis vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.
   At the ends, we apply the $M_a^0$ case or the $M_{2n + r - a}^{0}$ case in the same way for the first $a$ or last $2n + r - a$ indices.
@@
 
-Let $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$.
-This will be an important technical tool in our proof of irreducibility.
-
-We give two proofs of the following proposition.
-The first, below, intuits the necessary graphical intuition to construct a sub-matrix with nonzero determinant and perform row reduction.
-The second, given in section \ref{kernel}, formalizes the graphical intuition and gives results necessary for the following sections.
-
-\begin{proposition}\label{Trivial}
-  Suppose $e \nmid n + r + 1$.
-  Then, $K := K_{2n + r}^r = 0$.
-\end{proposition}
-\begin{proof}[Proof 1.]
-  Consider the matrix $A = \bigoplus (1 + T_i)$ having kernel $K$.
-  It is sufficient by lemma \ref{rainbow nonzero} to show that $A$ includes a row $[0,\dots,0,1,0,\dots,0]$ with a nonzero entry only on the row $j$.
-
-  Now, we may characterize the rows of $A$ as follows;
-  if the row corresponding to $(1 + T_i)$ and mapping onto the element $w_l \in W$ is nonzero, then it is of the form $\brk{a_1,\dots,a_{\abs W}}$ where $a_l = 1 + q$, $a_m = q^{1/2}$ whenever $(1 + T_i)w_m = q^{1/2}w_l$, and $a_m = 0$ otherwise.
-
-  Seeing this, the row corresponding to $(1 + T_{n + r})$ and $w_j$ has nonzero entries $q^{1/2}$ at $w_j$ and $(1 + q)$ at the vector $w$ agreeing with $w_j$ at all indices except having arcs at $(n+r-1,n+r)$ and $(n+r+1,n+r+2)$.
-  Similar justification leads the row corresponding to $(1 + T_{n+r-1})$ at $w$ to have nonzero entries $q^{1/2}$ at $w$ and $(1 + q)$ at $w_j$ and the vector with anchors $1,\dots,r$ , arc $(n+r-3,n+r-2)$, and all other arcs maximum length.
-
-  \begin{figure}
-   \[
-     \Action{10}{1/2,3/10,4/9,5/8,6/7}{2}{1/10,2/3,4/9,5/8,6/7}{q^{1/2}}
-   \]
-   \[
-     \Action{10}{1/10,2/3,4/9,5/8,6/7}{2}{1/10,2/3,4/9,5/8,6/7}{q+1}
-   \]
-   \[
-     \Action{10}{1/10,2/9,3/4,5/8,6/7}{2}{1/10,2/3,4/9,5/8,6/7}{q^{1/2}}
-   \]
-   \caption{Illustrated is the row constructed for transposition $(1 + T_2)$; clearly these are the only basis elements mapping to multiples of the desired element, and they relate to each other.
-     replacing the outermost and/or innermost arc with an anchor typifies the rows constructed with three nonzero coefficients.}
- \label{Submatrix}
-\end{figure}
-
-  We may iterate this process as illustrated in Figure \ref{Submatrix}, eventually ending at a row with two nonzero entries, either an arc $(1,2)$ or an arc $(2,3)$, and all anchors otherwise left-aligned and arcs of maximum length.
-  These rows together form an $(n + r) \times \abs{M_{2n + r}^r}$ submatrix of $A$ which has a nonzero row in the row corresponding to $j$, and has (by removing zero rows) the same row space as the following square matrix:
-  \newcommand*\bigzero{\makebox(0,15){\text{\Huge0}}}
-  \newcommand*\bigzerotwo{\makebox(-20,15){\text{\Huge0}}}
-  \begin{equation}\label{Bnr}
-    B_{n + r} := \begin{bmatrix}
-      \begin{matrix}
-      q + 1 & q^{1/2} & \\
-      q^{1/2} & q + 1 & q^{1/2}\\
-      & q^{1/2} & q + 1 & q^{1/2}\\
-      &  & \ddots & \ddots
-      \end{matrix}
-      &   \bigzero\\
-      \bigzerotwo & \begin{matrix}
-        q^{1/2} & q+1 & q^{1/2}\\
-        &  q^{1/2} & q + 1
-       \end{matrix}
-    \end{bmatrix}.
-  \end{equation}
-  We will show that this matrix is invertible;
-  then, a sequence of elementary row operations will yield the identity, and in particular, when applied to $A$, will yield a row with a nonzero entry only on row $j$, giving $K = 0$.
-
-  We may prove invertibility of this matrix by proving that $\det B_{n + r} = \brk{n + r + 1}_q$ inductively on $n+r$.
-  This is satisfied for our base case $n + r = 1$, so suppose that it is true for each $m < n + r$.
-  Then,
-  \begin{align*}
-    \det B_{n+r} &= (q + 1) \det B_{n + r - 1} - q \det B_{n + r - 2}\\
-    &= (q + 1)(1 + \dots + q^{n + r - 1}) - (q + \dots + q^{n + r - 1})\\
-    &= 1 + \dots + q^{n + r}\\
-    &= \brk{n + r + 1}_q.
-  \end{align*}
-  Hence $\det B_{n + r} \neq 0$, and $K = 0$.
-\end{proof}
+Now we will prove irreducibility.
+
 \begin{theorem}\label{Irreducibility Theorem}
@@
   Take an arbitrary vector $w \in M$.
-  By Proposition \ref{Trivial} there exists some $(1 + T_i) \in \SH$ such that $(1 + T_i)w \neq 0$.
+  By Proposition \ref{trivial kernel} there exists some $(1 + T_i) \in \SH$ such that $(1 + T_i)w \neq 0$.
   Note that \[\ima (1 + T_i) = \Span\cbr{w_j \mid w_j \text{ contains the arc }(i,i+1)}.\]
@@
   \end{equation}
-  Indeed, when $i+1 \neq j$ this is given by $h_j = 1 + T_j$, and we have $h_{i+1} = q^{-1}(1 + T_i)(1 + T_{i+1})(1 + T_{i-1})$, as given by Figure \ref{bigloop}.
+  Indeed, when $i+1 \neq j$ this is given by $h_j = 1 + T_j$, and we have $h_{i+1} = q^{-1}(1 + T_i)(1 + T_{i+1})(1 + T_{i-1})$.
+  This is illustrated by Figure \ref{bigloop}, and can alternately be seen as a consequence of the following isotopy.
+  \[
+  \begin{gathered}\CapNAction{4}{1/1,3/2,2/3}{2}\end{gathered}
+  \longsquigrightarrow
+  \begin{gathered}\BigNAction\end{gathered}
+  \]
+  This may be intuitively viewed as a ``large'' version of the action connecting nodes $i-1$ and $i+2$;
+  it preserves the arc $(i,i+1)$ and the factor $q^{1/2}$ in $h_{i+1}$ gives the correct scaling.
 
@@
 
-\begin{figure}
-\[
-  \begin{gathered}\CapNAction{4}{1/1,3/2,2/3}{2}\end{gathered}
-  \longsquigrightarrow
-  \begin{gathered}\BigNAction\end{gathered}
-\]
-  \caption{The isotopy demonstrating the correspondence between $h_{i+1}$ and $T_i'$;
-  the scaling issue with having three simple reflections is handled by the $q^{-1}$ factor in $h_{i+1}$.}
-\end{figure}
-
 \subsection{Correspondence with Specht modules}
@@
 
-\section{Sign Subrepresentations}
+  This entirely characterizes $M_{2n + r}^r$ in the case that $e > n + r + 1$.
+  In the next section, we will give weaker characterizations of $M_{2n + r}^r$ in the case $e = n + r + 1$, where the representation s $M_{2n + r}^r$ and $S^{(n+r,n)}$ are reducible.
+
+\section{Sign subrepresentations}
+{\color{magenta} Smooth out the beginning of this section to work with the end of last section.}
 In the previous section, we proved $M_{2n+r}^r\simeq S^{(n+r,n)}$ under certain conditions of $e$.
@@
 
-\subsection{Kernel Basis}
+\subsection{Kernel basis}
 
@@
 
-\subsection{Nontrivial Kernel}
+\subsection{Nontrivial kernel}
 
@@
 
+{\color{magenta} Move lemmas to a new appendix $\backslash$section.}
 \begin{lemma}
@@
 
+\subsection{Conjectures on sign subrepresentations}\label{Conjecture Section}
+Recall that $K := K_{2n + r}^r$ is the direct sum of all copies of the sign representation in $M$.
+We will begin with a promising characterization of the socle of some $M_{2n + r}^r$.
+\begin{proposition}\label{Preimage of K}
+  Fix some $M := M_{2n + r}^r$.
+  Suppose there is some natural number $n'$ with $n' < n$ such that $K_{2n' + r}^r \neq 0$.
+  Let $\pi:M_{2n + r}^r \twoheadrightarrow M_{2n' + r}^r$ be the linear map
+  \[
+    \pi := (1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}).
+  \]
+  Then, $\pi^{-1}(K)$ contains any proper subrepresentations of $M$.
+\end{proposition}
+\begin{proof}
+  It suffices to show that any vector $w \in M - \pi^{-1}(K)$ is cyclic;
+  then, any subrepresentation containing $w$ also contains all of $M$, implying the proposition.
+
+  In fact, since $\pi(w) \notin K$, there is some $(1 + T_i) \in \SH$ such that $(1 + T_i)\pi(w) \neq 0$.
+  Since $\ima (1 + T_i)$ is irreducible, we are then able to generate the image of a basis element, and hence generate a basis element in $M_{2n + r}^r$ by analogous argument to \ref{Irreducibility Theorem}.
+{\color{orange} justify soon tomorrow.}
+  {\color{orange} Sketch: subrepresentation $W \supsetneq \pi^{-1}(K)$ maps down to proper subrepresentation containing $K$, a contradiction.}
+\end{proof}
+
+If $\pi^{-1}(K)$ is itself a subrepresentation of $M$, then we will have identified the radical of $M_{2n + r}^r$.
+Observing decomposition matrices for $S_{(n+r,n)}$ for small $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two by \cite{Mathas-book};
+the same appears to be true of $M_{2n + r}^r$ by Figures \ref{Composition series e=3} through \ref{Composition series e=6}.
+This motivates our first conjecture:
+\begin{conjecture}\label{Preimage subrepresentation}
+  In Proposition \ref{Preimage of K}, $\pi^{-1}(K)$ is an irreducible subrepresentation of $M$.
+\end{conjecture}
+
+We can posit more sturcutre than this;
+by observing Figure \ref{Empirical Kernel}, we note that the kernel is nontrivial in more cases than $e = n + r + 1$, and appears to follow a pattern: 
+\begin{conjecture}\label{Sharp kernel}
+  Suppose $p = \infty$.
+  Then, $K \subset M_{2n + r}^r$ is nontrivial if and only if $e \mid n + r + 1$, in which case it is one-dimensional.
+\end{conjecture} 
+Then, assuming that Conjectures \ref{Preimage subrepresentation} and \ref{Sharp kernel} are true, we reach the following corollary.
+\begin{corollary}
+  $M := M_{2n + r}^r$ has a composition series given by \begin{equation}\label{Conjecture filtration}
+    0 \subset \pi^{-1}(K) \subset M.\end{equation}
+\end{corollary}
+\begin{proof}
+  By \ref{Sharp kernel}, we have the filtration \eqref{Conjecture filtration}.
+  By \ref{Preimage subrepresentation}, the first factor is irreducible, and by \ref{Preimage of K}, the second factor is irreducible.
+\end{proof}
+
+This characterizes much of the structure of $M_{2n + r}^r$.
+Due to this structure, the heuristics listed above, their isomorphism in the generic case, and the equality of their dimension, we pose the following conjecture.
+\begin{conjecture}
+  For any $e,n,r$, we have $M_{2n + r}^r \simeq S^{(n+r,n)}$.
+\end{conjecture}
+
 \section{Fibonacci representations and quotients of Specht modules}\label{Fibonacci Section}
@@
 We may further study the low-dimensional Fibonacci representations with the following proposition:
-\begin{proposition}
+\begin{proposition}\label{3 irreducibility}
   The representation \emph{$V^3_{\vs\vp}$} is irreducible.
@@
 \end{proof}
-\begin{corollary}
+\begin{corollary}\label{ss irreducibility}
   The representation \emph{$V^m_{\vs\vs}$} is irreducible.\qed
@@
 \end{corollary}
+
+\begin{remark}
+  As in \cite{Shor}, we may be consider a representation $\tilde V^m$ of the braid group on $m$ strands via Definition \ref{Fib definition}. 
+  In fact, Proposition \ref{Fib irreducibility}, Lemma \ref{Fib branching}, and Corollaries \ref{ss irreducibility} and \ref{V decomposition into V} hold in reference to $\tilde V^m$ by analogous arguments.
+\end{remark}
 
@@
 
-\section{Conjecture}\label{Conjecture Section}
-Recall that $K := K_{2n + r}^r$ is the direct sum of all copies of the sign representation in $M$.
-Hence the following characterises sign subrepresentations of $M$ completely:
-\begin{proposition}\label{Preimage of K}
-  Fix some $M := M_{2n + r}^r$.
-  Suppose there is some $n'$ such that $K_{2n' + r}^r \neq 0$.
-  Let $\pi:M_{2n + r}^r \twoheadrightarrow M_{2n' + r}^r$ be the linear map
-  \[
-    \pi := (1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}).
-  \]
-  Then, $\pi^{-1}(K)$ contains any proper subrepresentations of $M$.
-\end{proposition}
-\begin{proof}
-  {\color{orange} Sketch: subrepresentation $W \supsetneq \pi^{-1}(K)$ maps down to proper subrepresentation containing $K$, a contradiction.}
-\end{proof}
-\begin{conjecture}\label{Preimage subrepresentation}
-  In Proposition \ref{Preimage of K}, $\pi^{-1}(K)$ is an irreducible subrepresentation of $M$.
-\end{conjecture}
-\begin{conjecture}\label{Sharp kernel}
-  $K \subset M_{2n + r}^r$ is nontrivial if and only if $e \mid n + r + 1$, in which case it is one-dimensional.
-\end{conjecture} 
-\begin{corollary}
-  $M := M_{2n + r}^r$ has a composition series given by $0 \subset \pi^{-1}(K) \subset M$.
-\end{corollary}
-\begin{proof}
-  {\color{orange} Sketch: by \ref{Sharp kernel}, we have the filtration;
-  by \ref{Preimage subrepresentation}, the first factor is irreducible, and by \ref{Preimage of K} the second factor is irreducible.}
-\end{proof}
-
-\begin{conjecture}
-  For any $n,r$, we have $M_{2n + r}^r \simeq S^{(n+r,n)}$.
-\end{conjecture}
-
 \iffalse
@@
 
-\subsection{Explicit Definition of $M$}\label{Explicit Definition}
+\subsection{Explicit definition of crossingless matchings}\label{Explicit Definition}
 We will give a more careful definition of the crossingless matchings representation here.
@@
 
-\subsection{Compatibility for the Crossingless Matchings Representations}
+\subsection{Compatibility for the crossingless matchings representations}
 \label{Cross Relations}
@@
 
-\subsection{Compatibility for the Fibonacci Representations} 
+\subsection{Compatibility for the fibonacci representations} 
 \label{Fib Relations}
@@
 
-\section{Restrictions to Conjugate Subalgebras}\label{Algebra}
+\section{Restrictions to conjugate subalgebras}\label{Algebra}
 Throughout the text, for some representation $V$, we refer to $\Res_{\SH(S_{l})}^{\SH(S_m)} V$ without specifying exactly which subalgebra $\SH(S_{l})$.
@@
 
-\section{Data}\label{Empirics Section}
+\section{Heuristics}\label{Empirics Section}
 In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representations.\cite{Github}

### 2019-07-31 tex/Drafts/Draft-3.tex
General restructuring, conjecture section

@@
   \endgroup
-  Lastly, we will conjecture that $M_{2n + r}^r \simeq S^{(n+r,n)}$ for all $e$, and support this with heuristic data.
+  Each of these are powerful characterizations of the module $M_{2n + r}^r$ in the case that it and $S^{(n+r,n)}$ are irrducible.
+  We will prove the following theorem which characterizes $M_{2n + r}^r$ in the reducible case:
+  \begingroup
+  \hypersetup{linkcolor=\thmcolor}
+  \begin{customthm}{\ref{kernel existence}}
+    Suppose $e = n + r + 1$.
+    Then, $M_{2n + r}^r$ contains a subrepresentation isomorphic to the sign representation. 
+  \end{customthm}
+  \endgroup
+  We will go on to prove Corrollary \ref{n+r+1 composition series}, which specifies a composition series for $M_{2n + r}^r$ for the case $e = n + r + 1$.
 
@@
   This combined with an inductive argument and the branching of Section \ref{Specht Modules Section} allow us to prove Theorem \ref{Correspondence Theorem}.
-  Last, we finish the section by proving more general statements concerning sign subrepresentations of $M$, which contribute to conjectures later in the paper.{\color{orange} Fill in with specific information later.}
+  Last, we finish the section by proving more general statements concerning sign subrepresentations of $M$, which contribute to conjectures later in the paper.
+
+  \vspace{5pt}
 
@@
 
-\section{Sign subrepresentations}
+  \section{Sign subrepresentations}\label{Sign section}
 {\color{magenta} Smooth out the beginning of this section to work with the end of last section.}
@@
 
-\subsection{Conjectures on sign subrepresentations}\label{Conjecture Section}
-Recall that $K := K_{2n + r}^r$ is the direct sum of all copies of the sign representation in $M$.
-We will begin with a promising characterization of the socle of some $M_{2n + r}^r$.
+Due to the argument present in Theorem \ref{Irreducibility Theorem}, sign subrepresentations provide a surprisingly strong characterization of some $M_{2n + r}^r$ as follows.
 \begin{proposition}\label{Preimage of K}
   Fix some $M := M_{2n + r}^r$.
-  Suppose there is some natural number $n'$ with $n' < n$ such that $K_{2n' + r}^r \neq 0$.
+  Suppose there is some natural number $n'$ with $n' \leq n$ such that $K_{2n' + r}^r \neq 0$.
   Let $\pi:M_{2n + r}^r \twoheadrightarrow M_{2n' + r}^r$ be the linear map
   \[
-    \pi := (1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}).
-  \]
+    \pi := \begin{cases}
+      (1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}) & \text{if } n < n,'\\
+      \id{M} & \text{if } n = n',
+    \end{cases}
+  \]
+  where $\id M$ is the identity map on $M$.
   Then, $\pi^{-1}(K)$ contains any proper subrepresentations of $M$.
@@
   In fact, since $\pi(w) \notin K$, there is some $(1 + T_i) \in \SH$ such that $(1 + T_i)\pi(w) \neq 0$.
-  Since $\ima (1 + T_i)$ is irreducible, we are then able to generate the image of a basis element, and hence generate a basis element in $M_{2n + r}^r$ by analogous argument to \ref{Irreducibility Theorem}.
-{\color{orange} justify soon tomorrow.}
-  {\color{orange} Sketch: subrepresentation $W \supsetneq \pi^{-1}(K)$ maps down to proper subrepresentation containing $K$, a contradiction.}
-\end{proof}
-
-If $\pi^{-1}(K)$ is itself a subrepresentation of $M$, then we will have identified the radical of $M_{2n + r}^r$.
+  Note that $e > (n'-1) + r + 1$, so $M_{2(n-1) + r}^r$ is irreducible;
+  then, we may use diagram \eqref{Irreducibility commutative diagram} and an analogous argument to Theorem \ref{Irreducibility Theorem} to argue that $(1 + T_i)\pi(w)$ is cyclic, and hence $w$ is cyclic.
+\end{proof}
+\begin{corollary}\label{n+r+1 composition series}
+  Suppose $e = n + r + 1$.
+  Then $M_{2n + r}^r$ has a composition series given by
+  \[
+    0 \subset K \subset M.
+  \]
+\end{corollary}
+
+This is suggestive;
+the preimage $\pi^{-1}(K)$ may be integral in characterizing the representation $M_{2n + r}^r$ in other reducible cases.
+The following section poses several conjectures involving this structure.
+
+\subsection{Conjectures on sign subrepresentations}\label{Conjecture Section}
+If $\pi^{-1}(K)$ is itself a subrepresentation of $M$, then we will have identified the radical of $M_{2n + r}^r$ via Propostion \ref{Preimage of K}.
 Observing decomposition matrices for $S_{(n+r,n)}$ for small $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two by \cite{Mathas-book};
@@
   Suppose $p = \infty$.
-  Then, $K \subset M_{2n + r}^r$ is nontrivial if and only if $e \mid n + r + 1$, in which case it is one-dimensional.
+  Then, $K \subset M_{2n + r}^r$ is nontrivial if and only if $e \mid n + r + 1$ and $e < n$. in which case it is one-dimensional.
 \end{conjecture} 
@@
 \begin{corollary}
-  $M := M_{2n + r}^r$ has a composition series given by \begin{equation}\label{Conjecture filtration}
+  Suppose $e,n,r$ are such that $M_{2n + r}^r$ is irreducible and $e \mid n' + r + 1$ for some $e < n' < n$.
+  Then, $M := M_{2n + r}^r$ has a composition series given by \begin{equation}\label{Conjecture filtration}
     0 \subset \pi^{-1}(K) \subset M.\end{equation}
@@
 
-This characterizes much of the structure of $M_{2n + r}^r$.
-Due to this structure, the heuristics listed above, their isomorphism in the generic case, and the equality of their dimension, we pose the following conjecture.
+These conjectures hope to characterize much of the structure of $M_{2n + r}^r$.
+Due to this structure, the heuristics listed above, their isomorphism in the $e > n + r + 1$ case, and the equality of their dimension, we pose the following conjecture.
 \begin{conjecture}
@@
 Hence we have entirely characterized Shor--Jordan's Fibonacci representation \cite{Shor} as a direct sum of irreducible quotients of Specht modules, and we have given graphical realizations of $D^{(n+r,n)}$ for $e = 5$ and $r \leq 3$.
-
-\iffalse
-\begin{proposition}
-  Denote the composition factor $M_{2n + r}^r / h^{-1}(K_{2n + r}^r)$ by $U_{2n + r}^r$.
-  Then, there exist some naturals $m,s$ satisfying $2m + s = 2n + r$ and $m + s > n + r$ such that the following is an isomorphism of $\SH$-modules \[h^{-1}\prn{K_{2n + r}^r} \simeq U_{2m + s}^s\].
-  \qed
-\end{proposition}
-\begin{proposition}
-  For the same $m,s$ as above, we have the following composition series of Specht modules:
-  \[
-    0 \longrightarrow D^{(m+s,m)} \longrightarrow S^{(n+r,n)} \longrightarrow D^{(n+r,n)} \longrightarrow 0.
-  \]
-\end{proposition}
-\begin{proposition}
-  $M_{2n + r}^r \simeq S^{(n+r,n)}$ and $U_{2m +s}^s \simeq D^{(m+s,m)}$.
-\end{proposition}
-\fi
 

### 2019-07-31 tex/Drafts/Draft-3.tex
Intro outline of new sections, n+r+1 composition series

@@
   \vspace{5pt}
-  In Section \ref{Crossingless Matchings Section}, we begin by proving Theorem \ref{Irreducibility Theorem}.
+  In Section \ref{Crossingless Matchings Section}, we begin by proving proposition \ref{trivial kernel} concerning sign subrepresentations of $M_{2n + r}^r$ when $e \nmid n + r + 1$;
+  this allows us to prove Theorem \ref{Irreducibility Theorem}.
   Following this, we prove the existence of a particular filtration with factors given by other crossingless matchings representations;
@@
   This combined with an inductive argument and the branching of Section \ref{Specht Modules Section} allow us to prove Theorem \ref{Correspondence Theorem}.
-  Last, we finish the section by proving more general statements concerning sign subrepresentations of $M$, which contribute to conjectures later in the paper.
 
   \vspace{5pt}
+  In Section \ref{Sign section}, we begin by determining an explicit basis for the direct sum $K$ of all sign subrepresentations of $M$ in the case $e = n + r + 1$.
+  We prove in Theorem \ref{kernel existence} that such $K$ is nontrivial whe $e = n + r + 1$, and thereby provide an explicit composition series for such $M$ in corrolary \ref{n+r+1 composition series}.
+  We finish the section by providing several corollaries concerning the structure of $M_{2n + r}^r$ at irreducible cases with $e < n + r + 1$.
 

### 2019-07-31 tex/Drafts/Draft-3.tex
Restructured Heuristics

@@
 Observing decomposition matrices for $S_{(n+r,n)}$ for small $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two by \cite{Mathas-book};
-the same appears to be true of $M_{2n + r}^r$ by Figures \ref{Composition series e=3} through \ref{Composition series e=6}.
+the same appears to be true of $M_{2n + r}^r$, as shown in Appendix \ref{Empirics Section}.
 This motivates our first conjecture:
@@
 Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
-  This basis is illustrated for $M_{5}^1$ in Figure \ref{S5 Basis}.
+The basis on $M_5^1$ induced by the quotient $M_6^0 \twoheadrightarrow M_{5}^1$ is illustrated in Figure \ref{S5 Basis}, and we call this the \emph{increasing lexicographic basis}.
 
@@
 \end{proof}
+
 \begin{figure}[h]
-\iffalse
-\def\tho{\Phi_3(q^{1/2})}
-\def\tht{\brk{3}_{q^{1/2}}}
-\def\to{q^{1/2}\brk{2}_{q^{1/2}}}
-Define the following coefficients:
-\begin{align*}
-  \tho &:= q^{3/2} + 1\\
-  \tht &:= q^{3/2} + q + q^{1/2} + 1\\
-  \to &:= q + q^{1/2}
-\end{align*}
-\fi
-
+  \[
+    \ENRGrid{13/7}{2/1,5/1,8/1,11/1,1/2,4/2,7/2,10/2}
+  \]\[
+    \ENRGrid{13/7}{3/1,7/1,11/1,2/2,6/2,10/2,1/3,5/3,9/3}
+  \]
+  \caption{
+    Illustration of the modules $M_{2n + r}^r$ having sign submodules for $p = \infty$ and $e = 3,4$ respectively.
+    The value $n + r + 1$ is filled in the squares, and modules having sign submodules are colored magenta.
+    For $p = \infty$ and $2n + r \leq 14$, it has been verified, through a combination of theorems here and empirical computations, that $K_{2n + r}^r$ is nontrivial if and only if $e | n+r+1$ and $e < n$.
+  }\label{Empirical Kernel}
+\end{figure}
+
+\def\qqo{\alpha}
+\def\tto{\beta}
+\def\vtv{\gamma}
+\def\fft{\delta}
+\def\fto{\varepsilon}
+\setcounter{MaxMatrixCols}{20}
+
+\section{Heuristics}\label{Empirics Section}
+In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representations.\cite{Github}
+The computations were made via a combination of the Python \cite{Python} and Magma \cite{Magma} languages.
+
+\begin{remark}
+  The data on composition series and transition matrices $M/K \rightarrow V$ were computed using our implimentation of the Hecke algebra in the Magma language.
+  This stores the algebra via basis elements and structure constants, and hence the memory required for the structure grows with $(n!)^3$.
+  This is prohibitively large when $m > 7$.
+  An implementation of $\SH$ as a quotient of a free algebra is possible, but potentially difficult to work with via the Magma language.
+\end{remark}
+
+For $M$, the data throughout this section are specified with repsect to the basis on $M_{2n + r}^r$ inuced by the increasing lexicographic basis on $M_{2n + 2r}^0$ and the quotient $M_{2n + 2r}^r \twoheadrightarrow M_{2n + r}^r$ as defined in Appendix \ref{Explicit Definition}.
+For $V$, hey are specified with respect to the basis on $V$ given by increasing lexicographic order $\vs < \vp$.
+
+The following data define representation $\varphi_{2n + r}^r: M_{2n + r}^r / K_{2n + r}^r \rightarrow V_{s}^{2n + r}$ where $s = \vs\vs$ if $r \in \cbr{0,3}$ and $s = \vs\vp$ otherwise.
+All of such computations use $q$ a primitive 5th root of unity in the algebraic extension of the Cyclotomic field $\QQ(\zeta_{10})$ by a root of the polynomial $x^2 - \tau$.
+They cover all cases $2n + r \leq 6$, and they include the cases $n = r = 2$ and $n = 1, r = 3$ where $K_{2n + r}^r \neq 0$.
 \def\tho{q^{3/2} + 1}
@@
   \end{bmatrix}\\
+\end{align*}
+\begin{align*}
   \varphi_5^3 &= \begin{bmatrix}
@@
 
-\caption{We define representations $\varphi_{2n + r}^r:M_{2n + r}^r/K_{2n + r}^r \rightarrow V^{2n + r}_{s}$, where $s = \vs\vs$ if $r = 0,3$ and $s = \vs\vp$ otherwise.
-These are given with respect to the basis on $M_{2n + r}^r$ induced by the increasing lexicographic order basis on $M_{2n + 2r}^0$ and the quotient $M_{2n + 2r}^0 \twoheadrightarrow M_{2n + r}^r$.
-These are also given with respect to the basis on $V$ given by increasing lexicographic order $\vs < \vp$.
-  }\label{Fib Data}
-\end{figure}
-
-\begin{figure}[h]
-  \[
-    \ENRGrid{13/7}{2/1,5/1,8/1,11/1,1/2,4/2,7/2,10/2}
-  \]\[
-    \ENRGrid{13/7}{3/1,7/1,11/1,2/2,6/2,10/2,1/3,5/3,9/3}
-  \]
-  \caption{
-    Illustration of the modules $M_{2n + r}^r$ having sign submodules for $p = \infty$ and $e = 3,4$ respectively.
-    The value $n + r + 1$ is filled in the squares, and modules having sign submodules are colored magenta.
-    For $p = \infty$ and $2n + r \leq 14$, it has been verified, through a combination of theorems here and empirical computations, that $K_{2n + r}^r$ is nontrivial if and only if $e | n+r+1$ and $e < n$.
-  }\label{Empirical Kernel}
-\end{figure}
-
-\def\qqo{\alpha}
-\def\tto{\beta}
-\def\vtv{\gamma}
-\def\fft{\delta}
-\def\fto{\varepsilon}
-\setcounter{MaxMatrixCols}{20}
-
-\begin{figure}[h]
+We give in Figure \ref{Empirical Kernel} some data supporting a conjecture concerning sign subrepresentations of $M_{2n + r}^r$.
+The computations to support this were done over $\CC$ with $q$ a primitive 5th root of unity.
+
+It is known that, for small $2n + r$, each Specht module $S^{(n+r,n)}$ has a composition series of length 2.\cite{Mathas-book}
+Heuristically, $M_{2n + r}^r$ does as well;
+let this series be
+\[
+  0 \subset U_{2n + r}^r \subset M_{2n + r}.
+\]
+In the following data, we specify the inclusion maps map $\iota_{e,2n+r}^r:U_{2n + r}^r \hookrightarrow M_{2n + r}^r $, which conjecturally illustrates the inclusion of the first composition factor of $S^{(n+r,n)}$ into $S^{(n+r,n)}$ for all $2n + r \leq 7$.
 \begin{align*} 
@@
  1 & 0 &-1 &-1 & 1 & 0 & -1 & -1 & 0 & 0 & 0 & 0 & 1 & 1
-\end{bmatrix}^\intercal\\
+\end{bmatrix}^\intercal
+\end{align*}
+\begin{align*}
 \iota_{3,7}^1&=  
@@
 \end{align*}
-\caption{The maps of representations $\iota_{e,2n+r}^r:U_{2n +r}^r \hookrightarrow M_{2n + r}^r$ for $e = 3$.}
-\label{Composition series e=3}
-\end{figure}
-
-\begin{figure}[h]
 \begin{align*}
@@
 \end{bmatrix}^\intercal\\
+\end{align*}
+\begin{align*}
 \iota_{4,6}^0 &=
@@
 \end{align*}
-\caption{The maps of representations $\iota_{e,2n+r}^r:U_{2n +r}^r \hookrightarrow M_{2n + r}^r$ for $e = 4$.}
-\label{Composition series e=4}
-\end{figure}
-
-\begin{figure}[h]
 \begin{align*}
@@
 \end{bmatrix}^\intercal\\
+\end{align*}
+\begin{align*}
 \iota_{5,7}^1 &=
@@
 \end{align*}
-\caption{The maps of representations $\iota_{e,2n+r}^r:U_{2n +r}^r \hookrightarrow M_{2n + r}^r$ for $e = 5,6$.}
-\label{Composition series e=6}
-\end{figure}
-
-\section{Heuristics}\label{Empirics Section}
-In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representations.\cite{Github}
-
-\begin{remark}
-  These results are restricted by two things; first and with less recourse, this was computed in Magma, a closed source language with bugs that could not be resolved in certain cases.
-  Second, the memory necessary to store the Hecke algebra via basis elements and structure constants grows with $(n!)^3$;
-  this is prohibitively large when $m > 7$.
-  An implementation as a quotient by a free algebra or only specifying multiplication by generators may fix this, however, this is not possible with the Magma language, and the closed source renders modification of the language impossible.
-\end{remark}
-
-We give in Figure \ref{Fib Data} some isomorphisms between $M/K$ and $V$ for $e \geq n + r + 1$ with $p = \infty$;
-all but one of these are cases with $e > n + r + 1$, so $K=0$ and this is an isomorphism with our crossingless matchings representation.
-The case $n = 1$, $r = 3$ gives an example of an isomorphism not proven in general, but proven via our computation.
-All of these computations are done for $q$ a primitive 5th root of unity in the algebraic extension of the Cyclotomic field $\QQ(\zeta_{10})$ by a root of the polynomial $x^2 - \tau$.
-
-We give in Figure \ref{Empirical Kernel} some data supporting a conjecture concerning sign subrepresentations of $M_{2n + r}^r$.
-The computations to support this were done over $\CC$ with $q$ a primitive 5th root of unity.
-
-It is known that, for small $2n + r$, each Specht module $S^{(n+r,n)}$ has a composition series of length 2.\cite{Mathas-book}
-We give in Figures \ref{Composition series e=3} through \ref{Composition series e=6} the map $\iota_{e,2n+r}^r:U_{2n + r}^r \hookrightarrow M_{2n + r}^r \twoheadrightarrow U_{2n + r}^r$, which conjecturally illustrates the inclusion of the first composition factor of $S^{(n+r,n)}$ into $S^{(n+r,n)}$ for all $2n + r \leq 7$.
 

### 2019-07-31 tex/Drafts/Draft-3.tex
addressed comments in section 4 and added comment on conjectures

@@
  \section{Sign subrepresentations}\label{Sign section}
-{\color{magenta} Smooth out the beginning of this section to work with the end of last section.}
-In the previous section, we proved $M_{2n+r}^r\simeq S^{(n+r,n)}$ under certain conditions of $e$.
-In this proof, we used the fact that, given our conditions on $e$, we only projected down to cases with no sign subrepresentation.
-
-In this section, we prove that there is exactly one sign subrepresentation when $e=n+r+1$, and give an explicit basis for this subrepresentation.
+ Recall $K:=K^r_{2n+r}$, defined in section \ref{kernel}, is the direct sum of all sign subrepresentations.
+In the previous section, we were not able to prove $M_{2n+r}^r\simeq S^{(n+r,n)}$ for $e=n+r+1$ because we could not assume $K=0$.
+In particular, our proof of irreducibility failed.
+
+ In this section, we prove that there is exactly one sign subrepresentation when $e=n+r+1$, thus $M_{2n+r}^r$ is reducible.
+We give an explicit basis for $K$, and explore how our approach may generalize to finding subrepresentations other $e$.
 
@@
 
-Recall $K:= K^r_{2n+r}$, defined in section \ref{kernel}, is the direct sum of all sign subrepresentations.
-Here we determine an explicit basis for $K$ when $e=n+r+1$, assuming $K\not=0$.
-In the next section, we prove $K\not=0$.
+ Here we determine an explicit basis for $K$ when $e=n+r+1$, assuming $K\not=0$. In the next section, we prove $K\not=0$.
 
@@
  		=&(1+q)x_{\psi(2,N)}(q)+\sum_{\sigma\in E_{\psi(2,N)},\sigma\not=\psi(2,N)}q^{1/2}x_{\sigma}(q)\\
-		=&-q^{1/2}x_{\psi(2,i-1)}x_{\psi(i+2,N)}\Q{n+r}^{i/2}
+ 		=&-q^{1/2}x_{\psi(2,i-1)}x_{\psi(i+2,N)}\Q_{n+r}^{i/2}
  		\end{align*}
@@
 
-		$$x_\upsilon=x_{\psi(2,i-1)}x_{\upsilon(i+2,N)}\Q{n+r}^{i/2}$$
+ 		$$x_\upsilon=x_{\psi(2,i-1)}x_{\upsilon(i+2,N)}\Q_{n+r}^{i/2}$$
 
@@
 
-		$$-q^{1/2}x_{\psi(2,i-1)}x_{\psi(i+2,N)}\Q{n+r}^{i/2}\prn{1-1}=0$$
+ 		$$-q^{1/2}x_{\psi(2,i-1)}x_{\psi(i+2,N)}\Q_{n+r}^{i/2}\prn{1-1}=0$$
 
@@
  \begin{proposition}\label{Preimage of K}
+ 	{\color{red!80!green}This proposition can be strengthened, right? Like we just need a sequence of $n-n'$ actions such that no two of them are closer than two positions apart, right?}
  	Fix some $M := M_{2n + r}^r$.
@@
  Observing decomposition matrices for $S_{(n+r,n)}$ for small $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two by \cite{Mathas-book};
-the same appears to be true of $M_{2n + r}^r$, as shown in Appendix \ref{Empirics Section}.
+ the same appears to be true of $M_{2n + r}^r$ by Figures \ref{Composition series e=3} through \ref{Composition series e=6}.
  This motivates our first conjecture:
@@
  \end{conjecture}
+ {\color{red!80!green}Could we also say the quotient $M/\pi^{-1}(K)$ is irreducible? We believe that right?}
 

### 2019-07-31 tex/comments/3-nat-comments.tex
Some edits to conjectures section

--- 2019-07-31 tex/Drafts/Draft-3.tex
@@
 \end{proof}
-This will be an integral technical tool in proving the correspondence between the crossingless matchings representation $M_{2n + r}^r$ and the Specht module $S^{(n+r,n)}$ in the following section.
+This will be an important technical tool in proving the correspondence between the crossingless matchings representation $M_{2n + r}^r$ and the Specht module $S^{(n+r,n)}$ in the following section.
 
@@
 
-\subsection{Sign subrepresentations when $e\nmid n+r+1$}\,
+\subsection{Sign subrepresentations when $e\nmid n+r+1$}
 \label{kernel}
-
-{\color{magenta} \Huge PLEASE ADDRESS: $W$ needs to be replaced with $M$.} 
-{\color{magenta} Also, titles should be lower case (I fixed in this document), and can be more descriptive\ldots e.g.
-``Sign subrepresentations of the crossingless matching; characterizing the sign subrepresentation; Sign subrepresentations when e = n+r+1.}
 
@@
 We will prove irreducibility by showing that every nonzero $w \in M$ is cyclic;
-the following lemma is integral in showing this.
+the following lemma is plays a key role in showing this.
 
@@
  	\]
- 	where $\id M$ is the identity map on $M$.
- 	Then, $\pi^{-1}(K)$ contains any proper subrepresentations of $M$.
+  where $\id M$ is the identity map on $M_{2n + r}^r$.
+  Then, $\pi^{-1}(K_{2n' + r}^r)$ contains any proper subrepresentations of $M_{2n + r}^r$.
  \end{proposition}
@@
  This is suggestive;
- the preimage $\pi^{-1}(K)$ may be integral in characterizing the representation $M_{2n + r}^r$ in other reducible cases.
+ the preimage $\pi^{-1}(K)$ may play a key role in characterizing the representation $M_{2n + r}^r$ in other reducible cases.
  The following section poses several conjectures involving this structure.
@@
  \subsection{Conjectures on sign subrepresentations}\label{Conjecture Section}
- If $\pi^{-1}(K)$ is itself a subrepresentation of $M$, then we will have identified the radical of $M_{2n + r}^r$ via Propostion \ref{Preimage of K}.
- Observing decomposition matrices for $S_{(n+r,n)}$ for small $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two by \cite{Mathas-book};
- the same appears to be true of $M_{2n + r}^r$ by Figures \ref{Composition series e=3} through \ref{Composition series e=6}.
+ If $\pi^{-1}(K)$ is itself a subrepresentation of $M$, then we will have identified the radical of $M_{2n + r}^r$ via Proposition \ref{Preimage of K}.
+ Observing decomposition matrices for $S_{(n+r,n)}$ for small $e$ and $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two \cite[Appendix~B]{Mathas-book};
+ this is give heuristic support in Appendix \ref{Empirics Section}.
  This motivates our first conjecture:
  \begin{conjecture}\label{Preimage subrepresentation}
- 	In Proposition \ref{Preimage of K}, $\pi^{-1}(K)$ is an irreducible subrepresentation of $M$.
+   In Proposition \ref{Preimage of K}, $\pi^{-1}(K_{2n' + r}^r)$ is an irreducible subrepresentation of $M$.
  \end{conjecture}
  {\color{red!80!green}Could we also say the quotient $M/\pi^{-1}(K)$ is irreducible? We believe that right?}
-
- We can posit more sturcutre than this;
+ This has been verified for {\color{magenta} LIST THE EXAMPLE WHICH HAS BEEN VERIFIED}.
+ In general, this is surprising;
+ $\pi$ is a-priori only a linear map, so one may not expect the preimage of a subrepresentation via $\pi$ to be a subrepresentation of $M_{2n + r}^r$.
+
+ We can posit more structure than this;
  by observing Figure \ref{Empirical Kernel}, we note that the kernel is nontrivial in more cases than $e = n + r + 1$, and appears to follow a pattern: 
@@
  	Suppose $p = \infty$.
- 	Then, $K \subset M_{2n + r}^r$ is nontrivial if and only if $e \mid n + r + 1$ and $e < n$. in which case it is one-dimensional.
+  Then, $K_{2n + r}^r \subset M_{2n + r}^r$ is nontrivial if and only if $e \mid n + r + 1$ and $e > n$, in which case it is one-dimensional.
  \end{conjecture} 
@@
  \begin{corollary}
+  Assume Conjectures \ref{Preimage subrepresentation} and \ref{Sharp kernel}.
  	Suppose $e,n,r$ are such that $M_{2n + r}^r$ is irreducible and $e \mid n' + r + 1$ for some $e < n' < n$.
  	Then, $M := M_{2n + r}^r$ has a composition series given by \begin{equation}\label{Conjecture filtration}
- 	0 \subset \pi^{-1}(K) \subset M.\end{equation}
+    0 \subset \pi^{-1}(K_{2n' + r}^r) \subset M_{2n + r}^r.\end{equation}
  \end{corollary}
  \begin{proof}
- 	By \ref{Sharp kernel}, we have the filtration \eqref{Conjecture filtration}.
- 	By \ref{Preimage subrepresentation}, the first factor is irreducible, and by \ref{Preimage of K}, the second factor is irreducible.
- \end{proof}
-
- These conjectures hope to characterize much of the structure of $M_{2n + r}^r$.
- Due to this structure, the heuristics listed above, their isomorphism in the $e > n + r + 1$ case, and the equality of their dimension, we pose the following conjecture.
+ 	By Conjecture \ref{Sharp kernel}, we have the filtration \eqref{Conjecture filtration}.
+ 	By Conjecture \ref{Preimage subrepresentation}, the first factor is irreducible, and by \ref{Preimage of K}, the second factor is irreducible.
+ \end{proof}
+
+ These conjectures would characterize much of the structure of $M_{2n + r}^r$.
+ We will pose a final conjecture as follows.
  \begin{conjecture}
@@
  \end{conjecture}
+ The support for this includes {\color{magenta} FILL THIS IN.}
 
 \section{Fibonacci representations and quotients of Specht modules}\label{Fibonacci Section}
-The irreducibility of $S^{(n+r,n)}$ is integral to arguments of Section \ref{Crossingless Matchings Section};
+The irreducibility of $S^{(n+r,n)}$ plays a central role in the arguments of Section \ref{Crossingless Matchings Section};
 without irreducibility of $M_{2n + r}^r$ (which is conjecturally equivalent to irreducibility of $S^{(n+r,n)}$), $M$ is not necessarily isomorphic to any Specht module $S^\lambda$ or quotient $D^\lambda$, preventing the arguments of Section \ref{Specht Modules Section} from being used.
@@
     The value $n + r + 1$ is filled in the squares, and modules having sign submodules are colored magenta.
-    For $p = \infty$ and $2n + r \leq 14$, it has been verified, through a combination of theorems here and empirical computations, that $K_{2n + r}^r$ is nontrivial if and only if $e | n+r+1$ and $e < n$.
+    For $p = \infty$ and $2n + r \leq 14$, it has been verified, through a combination of theorems here and empirical computations, that $K_{2n + r}^r$ is nontrivial if and only if $e | n+r+1$ and $e > n$.
   }\label{Empirical Kernel}

### 2019-07-31 tex/comments/3-nat-comments.tex
Addressed Miles comments on conjectures, added bibtex entries

@@
  \begin{proposition}\label{Preimage of K}
- 	{\color{red!80!green}This proposition can be strengthened, right? Like we just need a sequence of $n-n'$ actions such that no two of them are closer than two positions apart, right?}
  	Fix some $M := M_{2n + r}^r$.
@@
  	\pi := \begin{cases}
- 	(1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}) & \text{if } n < n,'\\
+ 	(1 + T_1)(1 + T_3)\cdots(1 + T_{n-n'}) & \text{if } n < n',\\
  	\id{M} & \text{if } n = n',
@@
  \begin{proof}
+   Set $M := M_{2n + r}$ and $K := K_{2n' + r}^r$.
   It suffices to show that any vector $w \in M - \pi^{-1}(K)$ is cyclic;
@@
  	\[
- 	0 \subset K \subset M.
+    0 \subset K_{2n + r}^r \subset M_{2n + r}^r.
  	\]
@@
 
- This is suggestive;
+ \begin{remark}
+   In the case $n < n'$, we may replace $\pi$ with a product of $n-n'$ elements $(1 + T_{z_1})\cdots(1 + T_{z_{n-n'}}) \in \SH$ such that $\abs{z_i - z_j} \geq 2$ for each $1 \leq i < j \leq n-n'$.
+   Then, an analogous statement to Proposition \ref{Preimage of K} follows from an analogous proof.
+ \end{remark}
+
+ Proposition \ref{Preimage of K} and Corollary \ref{n+r+1 composition series} are suggestive;
  the preimage $\pi^{-1}(K)$ may play a key role in characterizing the representation $M_{2n + r}^r$ in other reducible cases.
@@
  \end{conjecture}
- {\color{red!80!green}Could we also say the quotient $M/\pi^{-1}(K)$ is irreducible? We believe that right?}
  This has been verified for {\color{magenta} LIST THE EXAMPLE WHICH HAS BEEN VERIFIED}.
@@
  $\pi$ is a-priori only a linear map, so one may not expect the preimage of a subrepresentation via $\pi$ to be a subrepresentation of $M_{2n + r}^r$.
+
+  \begin{remark}
+    As a corollary to \ref{Preimage subrepresentation}, the quotient $M_{2n + r}^r / \pi^{-1}(K_{2n' + r}^r)$ is irreducible \cite[Thm.~10.4]{Dummit}.
+  \end{remark}
 
@@
  We will pose a final conjecture as follows.
- \begin{conjecture}
+ \begin{conjecture}\label{Final conjecture}
  	For any $e,n,r$, we have $M_{2n + r}^r \simeq S^{(n+r,n)}$.
  \end{conjecture}
- The support for this includes {\color{magenta} FILL THIS IN.}
+ The support for this includes the special case $e > n+r+1$ case proven in Theorem \ref{Correspondence Theorem}, as well as the previous contents of this section.
+ Further, note that the basis of $M_{2n + r}^r$ is defined analogously for all $e$;
+ it is well-known that a basis for $S^\lambda$ is indexed by the standard young tableaux of $\lambda$, which is also independent of $e$ \cite[Prop.~3.22]{Mathas-book}.
+ Hence Theorem \ref{Correspondence Theorem} implies that $M_{2n + r}^r$ and $S^{(n+r,n)}$ have the same dimension. 
+  These facts give heuristic support for Conjecture \ref{Final conjecture}
 

### 2019-07-31 tex/comments/3-nat-comments.tex
Heuristics revisions

@@
 
-  Our first approach uses crossingless matchings, originally defined by Khovanov \cite{Khovanov}, to realize irreducible Specht modules of two-row partitions.
-
-  \fakesubsection{Crossingless matchings}
-  {\color{orange} Literature goes here.}
+  We will use the \emph{crossingless matchings representation}, originally defined by Khovanov \cite{Khovanov, Khovanov-tangle, Khovanov-abelian}, to realize the Specht modules of two-row partitions.
+  These crossingless matchings representations have found applications to knot theory and geometric representation theory.
+
+  In his seminal paper \cite{Khovanov-tangle}, Khovanov constructs a categorification of the crossingless matchings representation as modules over the ``arc algebra'' given by applying a certain 2-dimensional topological quantum field theory (given by the cohomology of the 2-sphere) to all possible concatenations of crossingless matchings.
+  Khovanov then uses this to categorify the Jones polynomial of a tangle by associating to any tangle the chain homotopy class of a certain complex of bimodules over these arc algebras.
+  For a survey of categorification, including the Khovanov's categorification of the crossingless matchings representation, see \cite{Khovanov-abelian}.
+
+  Further, in \cite{Khovanov}, Khovanov proves that the center of the arc algebra is isomorphic as a grading ring to the cohomology of the Springer fiber of complete flags in $\CC^{2n}$ stabilized by a fixed nilpotent operator with two Jordan blocks of size $n$ (corresponding to the two parts of the partition).
+  Moreover, this isomorphism is equivariant with respect to the natural actions of the symmetric group $S_{2n}$ on each ring.
+
+  \begin{remark}
+    Khovanov considers only the partition $(n,n) \vdash 2n$ in his categorification above.
+    We will consider the general two-row partition $(n+r,n)$ in this paper.
+    A possible extension of our and Khovanov's work is to categorify the $r > 0$ case of our crossingless matchings representations as in \cite{Khovanov-tangle} and study whether Khovanov's work generalizes to the cohomology of the Springer fiber of complete flags in $\CC^{2n + r}$ stabilized by an analogous operator with Jordan blocks of size $n+r$ and $n$.
+  \end{remark}
 
@@
   \def\vp{\texttt{0}}
-  \fakesubsection{Fibonacci representation}
-  Now suppose that $e = 5$ and $k$ contains the algebraic number $\sqrt{q + q^4}$ (for reasons which will be apparent soon).
+  Henceforth assume that $e = 5$ and $k$ contains the algebraic number $\sqrt{q + q^4}$ (for reasons which will be apparent soon).
   For convenience set $m := 2n + r$.
@@
 
-\begin{figure}[h]
+\begin{figure}
   \[
@@
 
-\def\qqo{\alpha}
-\def\tto{\beta}
-\def\vtv{\gamma}
-\def\fft{\delta}
-\def\fto{\varepsilon}
-\setcounter{MaxMatrixCols}{20}
-
 \section{Heuristics}\label{Empirics Section}
-In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representations.\cite{Github}
-The computations were made via a combination of the Python \cite{Python} and Magma \cite{Magma} languages.
+In this section we aim both to support Conjectures \ref{Preimage of K} and \ref{Sharp kernel} and to provide transition matrices wherever possible between our two graphical representations \cite{Github}.
+The computations were made via a combination of the \texttt{Python} \cite{Python} and \texttt{Magma} \cite{Magma} languages.
 
 \begin{remark}
-  The data on composition series and transition matrices $M/K \rightarrow V$ were computed using our implimentation of the Hecke algebra in the Magma language.
-  This stores the algebra via basis elements and structure constants, and hence the memory required for the structure grows with $(n!)^3$.
+  The data on composition series and transition matrices $M/K \rightarrow V$ were computed using our implementation \cite{Github} of the Hecke algebra in the \texttt{Magma} language.
+  This stores the algebra via basis elements and structure constants, and hence the memory required for the structure grows with $(m!)^3$.
   This is prohibitively large when $m > 7$.
-  An implementation of $\SH$ as a quotient of a free algebra is possible, but potentially difficult to work with via the Magma language.
+  An implementation of the Hecke algebra as a quotient of a free algebra is possible, but potentially difficult to work with via the Magma language.
 \end{remark}
 
-For $M$, the data throughout this section are specified with repsect to the basis on $M_{2n + r}^r$ inuced by the increasing lexicographic basis on $M_{2n + 2r}^0$ and the quotient $M_{2n + 2r}^r \twoheadrightarrow M_{2n + r}^r$ as defined in Appendix \ref{Explicit Definition}.
-For $V$, hey are specified with respect to the basis on $V$ given by increasing lexicographic order $\vs < \vp$.
-
-The following data define representation $\varphi_{2n + r}^r: M_{2n + r}^r / K_{2n + r}^r \rightarrow V_{s}^{2n + r}$ where $s = \vs\vs$ if $r \in \cbr{0,3}$ and $s = \vs\vp$ otherwise.
-All of such computations use $q$ a primitive 5th root of unity in the algebraic extension of the Cyclotomic field $\QQ(\zeta_{10})$ by a root of the polynomial $x^2 - \tau$.
-They cover all cases $2n + r \leq 6$, and they include the cases $n = r = 2$ and $n = 1, r = 3$ where $K_{2n + r}^r \neq 0$.
+For $M$, the data throughout this section are specified with respect to the basis on $M_{2n + r}^r$ induced by the increasing lexicographic basis on $M_{2n + 2r}^0$ and the quotient $M_{2n + 2r}^r \twoheadrightarrow M_{2n + r}^r$ as defined in Appendix \ref{Explicit Definition}.
+For $V$, the data are specified with respect to the basis on $V^m$ given by increasing lexicographic order $\vs < \vp$.
+
+For the following data, set $e := 5$.
+The following data define the isomorphisms $\varphi_{2n + r}^r: M_{2n + r}^r / K_{2n + r}^r \rightarrow V_{s}^{2n + r}$ where $s = \vs\vs$ if $r \in \cbr{0,3}$ and $s = \vs\vp$ otherwise.
+All of such computations use $q$ a primitive 5th root of unity in the algebraic extension of the Cyclotomic field $\QQ(\zeta_{10})$ by $\sqrt\tau$ \cite{Github}.
+This data covers all cases $2n + r \leq 6$, and they include the cases $n = r = 2$ and $n = 1, r = 3$ where $K_{2n + r}^r \neq 0$.
 \def\tho{q^{3/2} + 1}
@@
     \tht & 0 & \tht & -\tht & 0
-  \end{bmatrix}\\
+  \end{bmatrix}
+\end{align*}
+\begin{align*}
   \varphi_6^2 &= \begin{bmatrix}
@@
     q^{1/2} & 0 & 0 & 0 & -q^{1/2} & -\brk{3}_{q^{1/2}} & 0 & -q^{1/2}
-  \end{bmatrix}\\
+  \end{bmatrix}
 \end{align*}
@@
 We give in Figure \ref{Empirical Kernel} some data supporting a conjecture concerning sign subrepresentations of $M_{2n + r}^r$.
-The computations to support this were done over $\CC$ with $q$ a primitive 5th root of unity.
-
-It is known that, for small $2n + r$, each Specht module $S^{(n+r,n)}$ has a composition series of length 2.\cite{Mathas-book}
+The computations to support this were done over $\CC$ with $q$ a primitive 5th root of unity \cite{Github}.
+
+It is known that, for small $e$ and $2n + r$, each Specht module $S^{(n+r,n)}$ has a composition series of length at most 2 \cite[Appendix B]{Mathas-book}
 Heuristically, $M_{2n + r}^r$ does as well;
@@
 In the following data, we specify the inclusion maps map $\iota_{e,2n+r}^r:U_{2n + r}^r \hookrightarrow M_{2n + r}^r $, which conjecturally illustrates the inclusion of the first composition factor of $S^{(n+r,n)}$ into $S^{(n+r,n)}$ for all $2n + r \leq 7$.
+We begin by defining the following constants.
+\def\qqo{\color{magenta} \varkappa}
+\def\tto{\color{brown!80!black} \varpi}
+\def\vtv{\color{blue!70!green} \varrho}
+\def\fft{\color{black!50!green}\varsigma}
+\def\fto{\color{red!50!orange} \vartheta}
+\setcounter{MaxMatrixCols}{20}
+\begin{align*}
+  \qqo &:= q^{1/2}\prn{q - 1},\\
+  \tto &:= q^{3/2} + q + 1,\\
+  \vtv &:= q^{1/2}\prn{q - 2},\\
+  \fft &:= q^{5/2} + q^2 + q^{3/2} + q + 1,\\ 
+  \fto &:= q^{5/2} + q + 1.
+\end{align*}
+Using these constants, we give the following data.
+We omit the cases where $M_{2n + r}$ is irreducible;
+this includes all cases where $e > 7$, as we then have $e > 2n + r \geq n + r + 1$.
 \begin{align*} 
@@
   0& 0& 0& 0& 1& \frac{1}{2}\qqo& \frac{1}{2}\qqo &1 &\frac{1}{2}\qqo
-\end{bmatrix}^\intercal\\
+\end{bmatrix}^\intercal
 \end{align*}
@@
 0& 0& 0& 0& 0& 0& 0& 0& 0& 1& -\frac{1}{2}\qqo& \frac{1}{2}\qqo& 1& \frac{1}{2}\qqo
-\end{bmatrix}^\intercal\\
+\end{bmatrix}^\intercal
 \end{align*}

### 2019-07-31 tex/comments/3-nat-comments.tex
One more Heuristics revision

@@
 
+A potential extension of this work is to implement a standard basis for the Specht module (e.g.
+the Murphy basis \cite{Murphy1,Murphy2}) in order to draw explicit isomorphisms between the Specht module and crossingless matchings representation, rather than the implicit isomorphisms proven in \ref{Correspondence Theorem}.
+
 \bibliographystyle{plain} 

### 2019-07-31 tex/Drafts/Draft-3-addressingKernelComments.tex
addressed section 3.1 comments

--- 2019-07-31 tex/Drafts/Draft-3.tex
@@
 
-{\color{magenta} \Huge PLEASE ADDRESS: $W$ needs to be replaced with $M$.} 
-{\color{magenta} Also, titles should be lower case (I fixed in this document), and can be more descriptive\ldots e.g.
-``Sign subrepresentations of the crossingless matching; characterizing the sign subrepresentation; Sign subrepresentations when e = n+r+1.}
-
 Define $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$.
@@
 For compactness, in this section we use $\sim $ to denote ``proportional to." For convenience, define $M_0^0$ and $M_1^1$ to be the zero representation.
-Note that in this section, as well as later sections characterizing the sign subrepresentation, we do not assume $n>0$.
+Note that in this subsection, as well as section \ref{Sign section}, we do not assume $n>0$.
 
@@
 In other words, the basis element with all anchors to the left followed by a ``rainbow" to the right.
+
+		\item Define a \emph{rainbow sub-matching} to be a sub-matching $\psi(a,b)$ corresponding to some rainbow element and satisfying the following property: if $a$ is an anchor then $b=2n+r$.
+This definition is motivated by the isotopy mentioned illustrated in diagram \ref{Branching commutative diagram}.
 	\end{itemize}
@@
 The nodes $R(4)=7$, $R(5)=6$, so $R(4,7)$ defines a sub-matching.
-Specifically, $R(4,7)=\sigma$.
+Specifically, $R(4,7)$ is a rainbow sub-matching, and $R(4,7)=\sigma$.
 Alternatively, $R(3)=8$, so, for instance $R(2,7)$ is not a sub-matching, and refers to the ordered set $(2,8,7,6,5,4)$.
@@
 	Let $W$ be the set of basis elements with nonzero coordinate in $w$.
-Let $z$ be the maximal number of anchors to the far left in any element $\psi\in W$.
-Formally, $z$ is the greatest positive integer such that there exists some element $\psi\in W$ satisfying $\psi(1)-1=...=\psi(z)-z=0$.
-For some positive integer $j$ define $W^j\subset W$ to be the set of all basis elements in $W$ with $j$ anchors to the far left.
+First, we will prove that $W$ contains an element with all anchors to the far left.
+Then we will apply the same argument to prove $W$ contains the rainbow element.
+
+	Let $z$ be the maximal number of anchors to the far left in any element $\sigma\in W$.
+Formally, $z$ is the greatest positive integer such that there exists some element $\sigma\in W$ satisfying $\sigma(1)-1=...=\sigma(z)-z=0$.
+For any positive integer $j$ define $W^j\subset W$ to be the set of all basis elements in $W$ with $j$ anchors to the far left.
 
@@
 Then for each $\psi\in W^z$, exactly $z$ anchors are positioned to the far left, so we may define $i_\psi$ to be the position of the next leftmost anchor in $\psi$.
+In other words, $i_y$ is the position of the $z+1$st anchor from the left in $\psi$.
 Fix some $\widehat{\psi}\in W^z$ such that $i_{\widehat{\psi}}\leq i_\psi$ for all $\psi$.
@@
 		\item $\psi'$ still has $z$ anchors on the left.
-		\item Defining $i_{\psi'}$ to be the next leftmost anchor, $i_{\psi'}<i_{\widehat{\psi}}$
+		\item Defining $i_{\psi'}$ to be the position of the next leftmost anchor, $i_{\psi'}<i_{\widehat{\psi}}$
 	\end{enumerate}
@@
 
-	Define $\sigma':=q^{-1/2}(1+T_{i_{\widehat{\psi}}-1})\sigma$.If $\sigma\not\in W^z$, $\sigma'$ will have $z$ anchors at the far left only if $\sigma'\in W^{z-1}$ and the $z$th leftmost anchor is at position $i_{\widehat{\psi}}$.
+	Define $\sigma':=q^{-1/2}(1+T_{i_{\widehat{\psi}}-1})\sigma$.
+Note that the action of $(1+T_{i_{\widehat{\psi}}-1})$ changes exactly two matches in $\sigma$, and these matches must involve the nodes $i_{\widehat{\psi}}-1,i_{\widehat{\psi}}$.
+It follows that if $\sigma\not\in W^z$, $\sigma'$ will have $z$ anchors at the far left only if $\sigma'\in W^{z-1}$ and the $z$th leftmost anchor is at position $i_{\widehat{\psi}}$.
 But then the position of the $z+1$st anchor is unchanged by the action, and must be at position greater than $i_{\widehat{\psi}}$, so from (ii) $\sigma'\not=\psi'$.
@@
 Since these are the only three indices altered by action of $(1+T_{i_{\widehat{\psi}}-1})$ on $\sigma$, if $(1+T_{i_{\widehat{\psi}}-1})\sigma\sim \psi'$ this implies $\sigma=\widehat{\psi}$ as desired.
-So if $z<r$ $w$ is not in the desired kernel.
-
-	\vspace{1mm}
+So, if $z<r$, $w$ is not in the desired kernel.
+
+	\vspace{2mm}
 	We have proven that there exists an element in $W$ with all anchors to the far left, or equivalently that $W^r$ is nonempty.
@@
 The proof is analogous to the previous case.
-First we define subsets $W^r_j\subset W^r$ that have the top $j$ arcs of the rainbow, and define $y$ to be the most arcs any element has.
-In the previous proof, we showed that if we move the next left-most anchor further left, the image of $w$ under that transposition will be nonzero.
-In this proof, we will show that if we expand the next-largest arc, the image of $w$ under that transposition will be nonzero.
-
-	\vspace{1mm}
+First we define subsets $W^r_j\subset W^r$ that have the top $j$ arcs of the rainbow, and define $t$ to be the most arcs any element has.
+Previously, we showed that if we move the next left-most anchor further left, the image of $w$ under that transposition will be nonzero.
+Now, we will show that if we expand the next-largest arc, the image of $w$ under that transposition will be nonzero.
+
+	\vspace{2mm}
 	Suppose $z=r$ but $R\not\in W^r$ (so $R\not\in W$).
-Let us define a sequence of subsets $W^r_i\subset W^r$ to be the set of elements in $W^r$ with the top $i$ humps of the rainbow.
-Formally, $W^r_0:=W^r$, $W^r_{i+1}:=\{\upsilon\in W^r_i| \upsilon(r+i+1)=2n+r-i \}$.
-Since $R\not\in W^r$,  there exists some positive integer $y$ less than $n-1$ such that $W^r_{y+1}=\emptyset$; $y$ is the largest number of contiguous top level rainbow humps that any element in $W^r$ has.
+Let us define a sequence of subsets $W^r_j\subset W^r$ to be the set of elements in $W^r$ with the top $j$ arcs of the rainbow.
+Formally, $W^r_0:=W^r$, $W^r_{j+1}:=\{\upsilon\in W^r_j| \upsilon(r+j+1)=2n+r-j \}$.
+Since $R\not\in W^r$,  there exists some positive integer $t$ less than $n-1$ such that $W^r_{t+1}=\emptyset$; $t$ is the largest number of contiguous top level rainbow arcs that any element in $W^r$ has.
 
@@
 
-Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively.
-Examples are pictured in \ref{shifted rainbow}.
-Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.
+\vspace{3mm}
+\begin{definition}
+	Given a rainbow element $R$, define the \emph{shifted rainbow elements} $R_{R,i},R_{L,i}$ to be those where you ``move the 'length two middle arc' across $i$ lines to the right or left, respectively." This is made clear in figure \ref{shifted rainbow}.
+Formally: $$R_{R,i}:=q^{-i/2}(1+T_{r+n+i})\cdots(1+T_{r+n+1})R$$, $$R_{L,i}:=q^{-i/2}(1+T_{r+n-i})\cdots(1+T_{r+n-1})R$$.
+\end{definition}
 
 \begin{figure}
-	\def\cbasisspacing{5mm}
-	$\cbr{
-		\begin{gathered}
-		\Matching{8}{1/8, 2/7, 3/6, 4/5}, \hspace{\cbasisspacing}
-		\Matching{8}{1/8, 2/7, 3/4, 5/6}, \hspace{\cbasisspacing}
-		\Matching{8}{1/8, 2/3, 4/7, 5/6}, \hspace{\cbasisspacing}
-		\Matching{8}{1/2,3/8,4/7,5/6}
-		\end{gathered}}$
-	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right}
+	\def\cbasisspacing{2mm}
+		\begin{adjustbox}{width=\textwidth}
+		\GeneralizedMatching{9}{2/9, 3/8, 4/7, 5/6}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
+		\GeneralizedMatching{9}{2/9, 3/8, 4/5, 6/7}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
+		\GeneralizedMatching{9}{2/9, 3/4, 5/8, 6/7}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
+		\GeneralizedMatching{9}{2/3,4/9,5/8, 6/7}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
+		\GeneralizedMatching{9}{1/2, 4/9,5/8, 6/7}{1}{3/1}{7/4}
+		\end{adjustbox}
+	\caption{$R_{L,0},...,R_{L,4}$ pictured from left to right.
+If $w\in K_{9}^1$ and $R=R_{L,0}$ has coordinate $c$ in $w$, then proposition \ref{shifted rainbow coeffs} claims $R_{L,1}$ has coordinate $Q_1$, $R_{L,2}$ has coordinate $Q_2$, etc.}
 	\label{shifted rainbow}
@@
 
-Define $Q_n:=(q^n+...+1)/q^{n/2}(-1)^n$ for $n\in \{0,1,...\}$.
-The following proposition says that, for any element in the kernel, if some basis element $y$ has coordinate $c$ in that element, and if $y$ has a rainbow sub-matching, the basis elements where you replace that sub-matching by the shifted rainbow matchings $R_{L,i}$ or $R_{R,i}$ both have coordinate $Q_ic$ in the kernel element.
+\begin{definition}
+	The following $q$-number deformation will be integral to this subsection and section \ref{Sign section}:
+
+		 $$Q_n:=(-1)^n\frac{q^n+\ldots+1}{q^{n/2}} \text{ for }n \text{ a nonnegative integer}$$. 
+\end{definition}
+
+The following proposition applies to any basis element $y$ with a rainbow sub-matching.
+It says that if $y$ has coordinate $c$ in $w\in K$, then those elements $\theta_i,\phi_i$, where you replace the rainbow sub-matching with a ``shifted rainbow sub-matching" $R_{R,i}$ or $R_{L,i}$, have coordinate $Q_ic$ in $w$.
+An example is given in figure \ref{shifted rainbow}.
 
 \begin{proposition}
-	Let $w$ be an element in the kernel intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation.
+	Let $w\in K^r_{2n+r}$.
 Let $y$ be a basis element with coordinate $c$ in $w$.
-Suppose $\exists a,b$ such that $y(a,b)=R$, the rainbow element.
-Define the basis elements $\theta_i,\phi_i$ by $\theta_i(1,a-1)=\phi(1,a-1)=y(1,a-1)$, $\theta_i(b+1,2n)=\phi(b+1,2n)=y(b+1,2n)$, $\theta_i(a,b)=R_{R,i}$, $\phi_i(a,b)=R_{L,i}$ (leave $\theta_i$ or $\phi_i$ undefined for any $i$ where $R_{R,i},R_{L,i}$ are undefined, respectively).
-The coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.
+Suppose that there exist $a,b$ such that $y(a,b)$ is a rainbow sub-matching.
+Define the basis elements $\theta_i,\phi_i$ to be those elements where we replace the rainbow sub-matching with a shifted rainbow sub-matching.
+Formally: $$\theta_i(1,a-1):=\phi(1,a-1):=y(1,a-1)\text{ ,}$$
+	$$\theta_i(b+1,2n):=\phi(b+1,2n):=y(b+1,2n)\text{ ,}$$ 
+	$$\theta_i(a,b)=R_{R,i}\text{ ,}$$ $$\phi_i(a,b)=R_{L,i}\text{.}$$
+
+	We restrict $i$ in $\theta_i,\phi_i$ to be such that $R_{R,i},R_{L,i}$ are defined, respectively.
+
+	Then the coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.
 
@@
 
-Proof of this proposition requires a simple algebraic fact that will be used throughout this document, so I state it as a lemma.
+We will use the following algebraic lemma to prove this proposition. The lemma will also be useful in section \ref{Sign section}.
 
 \begin{lemma}
-	$Q_1Q_n-Q_{n-1}=Q_{n+1}$
+	$Q_1Q_n-Q_{n-1}=Q_{n+1}$ for $n>0$.
 
@@
 
-\textit{Proof of lemma.}
-
-\begin{align*}
-Q_1Q_n-Q_{n-1}=&\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}\\
-=&\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}\\
-=&\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}
-\end{align*}
-
+\begin{proof}[Proof of lemma]
+	We compute:
+\begin{align*}
+Q_1Q_n-Q_{n-1}=&\prn{-\frac{(q+1)}{q^{1/2}}}\prn{(-1)^n\frac{(q^n+\cdots+1)}{q^{n/2}}}-(-1)^{n-1}\frac{(q^{n-1}+\cdots+1)}{q^{(n-1)/2}}\\
+=&(-1)^{n+1}\frac{(q^{n+1}+2q^n+\cdots+2q+1)}{q^{(n+1)/2}}-(-1)^{n+1}\frac{(q^n+\cdots+q)}{q^{(n+1)/2}}\\
+=&(-1)^{n+1}\frac{(q^{n+1}+\cdots+1)}{q^{(n+1)/2}}\\
+=&Q_{n+1}
+\end{align*}
+\end{proof}
 Now let us prove the proposition.
 
-\begin{proof}
-	Consider acting on $w$ by an element $(1+T_z)$.
-The coordinate of $\phi_i$ in $(1+T_z)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_z)$.
-Specifically, it will be $(1+q)c\iota+(q^1/2)\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.
-
-	Let $n:=a+b-1$ and $r$ be the number of anchors in $y(a,b)$.
-Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$.
-This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in \ref{shifted relations}.
-I claim the following:
-
-	\begin{center}
-		\textit{claim}:
-		The only basis elements $\psi$ where $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist\footnote{we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$}.
-
-	\end{center}
-
-	Note that the action of any $(1+T_z)$ on a basis element $\psi$ creates exactly two lines: an arc of length two connecting $z$ and $z+1$, and either an anchor or an arc of length $\geq 2$ connecting $\psi(z)$ and $\psi(z+1)$.\footnote{Although this fact follows directly from our definition of the representation, it will be used throughout the document, so it is important that the reader understands it.\label{two humps created}} The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.
-
-	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in \ref{shifted relations}.
-Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition.
-Me note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
-Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$.
-If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\psi(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor.
-All other matchings remain unchanged, so this implies $\psi=\phi_{i+1}$.
-Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\psi=\phi_{i-1}$.
-For boundary cases, note that for $\phi_0=\theta_0$, the only other basis element sent to this by the middle transposition is $\phi_1=\theta_1$.
-Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case gives no new information.
-Lastly, note that our argument was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors.
-Thus the claim is proved.
-
-	Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction:
+\vspace{1.5mm}
+\textit{\label{two humps created}Note: This proof relies on the simple fact that the action of a transposition $(1+T_i)$, assuming it does not send an element to zero, will update exactly two matches if it is changes the element.
+This follows directly from our definition of the representation, and will be integral to many proofs in this document.}
+
+\vspace{1.5mm}
+\begin{proof}
+
+	First, we will show that if we act by the transposition corresponding to the moved arc in $\phi_i$, the only basis elements sent to $\phi_i$ are $\phi_{i-1}$, $\phi_{i}$, and $\phi_{i+1}$.
+We will show that the analogous statement is true for $\theta_i$, and use this to finish the proof by induction.
+Formally:
+
+	\begin{claim*}
+		Suppose $\psi\in M_{2n+r}^r$ is a basis element.
+Take $i$ such that $\phi_i$, $\phi_{i-1}$, and $\phi_{i+1}$ are all defined.
+Let $2n'+r'$, $r'$ be the number of nodes and anchors in $y(a,b)$, respectively.
+Then $(1+T_{a-1+r'+n'/2-i})\psi\sim \phi_i$ implies $\psi=\phi_i$, $\phi_{i-1}$, or $\phi_{i+1}$.
+
+		Similarly, taking $i$ such that $\theta_i$, $\theta_{i-1}$, and $\theta_{i+1}$ are all defined, $(1+T_{a-1+r'+n'/2+i})\psi\sim \phi_i$ implies $\psi=\phi_i$, $\phi_{i-1}$, or $\phi_{i+1}$.
+	\end{claim*}
+
+	Note that $a-1+r'+n'/2-i$ is simply the starting node of the moved arc in $\phi_i$.
+
+	For the entirety of the proof of this claim, it will be instructive to reference Figure \ref{shifted relations} as an example.
+
+	It is easy to see that the action of $(1+T_{a-1+r'+n'/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\phi$.
+Suppose there exists another basis element $\psi$ sent to $\phi_i$ by the given transposition.
+Consider the arcs (or anchors) starting just inside and just outside of the moved arc in $\phi_i$: these are the arcs $(a-1+r'+n'/2-i-1,\phi_i(a-1+r'+n'/2-i-1))$ and $(a-1+r'+n'/2-i+2,\phi_i(a-1+r'+n'/2-i+2))$.
+
+	If $\psi$ contains both of these arcs, it must contain the arc $(a-1+r'+n'/2-i,a-1+r'+n'/2-i+1)$ to be a crossingless matching.
+This follows from our definition of rainbow sub-matching in definition \ref{sub-matchings}.
+Thus $\psi$ is fixed by the action of $(1+T_{a-1+r'+n'/2-i})$, so $\psi=\phi_i$.
+
+	If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r'+n'/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r'+n'/2-i})$ must create that arc/anchor.
+Thus $\psi(a-1+r'+n'/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r'+n'/2-i+1)=\phi_i(a-1+r'+n'/2-i-1)$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor.
+These matchings are identical to those of $\phi_{i+1}$, and no other matchings are changed by the action, so $\psi=\phi_{i+1}$.
+Likewise, if $\psi$ does not contain the right arc/anchor, that arc/anchor must be created by the action of $(1+T_{a-1+r'+n'/2-i})$, so $\psi=\phi_{i-1}$.
+
+	Lastly, note that the above argument was completely symmetric with respect to the parity of $i$, and hence an analogous argument without anchors handles the $\theta_i$ case. Thus the claim is proved.
+
+	\vspace{2mm}
+	As an edge case related to the claim, note that the only basis element sent to $y=\phi_0=\theta_0$ other than itself by the transposition acting on the middle of the rainbow is $\theta_1=\phi_1$ if they both exist.
+Otherwise, just $\phi_1$ exists and is sent to $y$, or the rainbow element has two nodes and neither exist.
+
+	We finish the proof of the proposition through induction:
 
@@
 Since $w$ is in the kernel, we have $(q+1)c+q^{1/2}c_{\phi_1}=0=>c_{\phi_1}=Q_1c$.
-$\phi_1=\theta_1$ so this gives us all our base cases.
+Since $\phi_1=\theta_1$, this gives us all our base cases.
 
 	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$.
-By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_i=0$ so $c_{\phi_{i+1}}=Q_1Q_i-Q_{i-1}=Q_{i+1}$ by lemma \ref{Q alg}.
-$\theta_i$ is an identical proof, so the proposition follows.
+By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_ic=0$ so $c_{\phi_{i+1}}=Q_1Q_ic-Q_{i-1}c=Q_{i+1}c$ by lemma \ref{Q alg}.
+The case of $\theta_i$ is an identical proof, so the proposition follows.
 
@@
 		\[
-		\GeneralizedAction{8}{3/4,5/8,6/7}{2}{1/1,2/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{(1+q)}
-		\]
-		\[
-		\GeneralizedAction{8}{2/3,5/8,6/7}{2}{1/1,4/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
-		\]
-		\[
-		\GeneralizedAction{8}{3/8,4/5,6/7}{2}{1/1,2/2}{1.25}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
-		\]
-		\caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $M_{8}^2$ and $i=2$.}
+		\GeneralizedAction{10}{1/2,5/6,7/10,8/9}{2}{3/1,4/2}{1}{5}{1/2,5/6,7/10,8/9}{3/1,4/2}{(1+q)}
+		\]
+		\[
+		\GeneralizedAction{10}{1/2,5/10,6/7,8/9}{2}{3/1,4/2}{1}{5}{1/2,5/6,7/10,8/9}{3/1,4/2}{q^{1/2}}
+		\]
+		\[
+		\GeneralizedAction{10}{1/2,4/5,7/10,8/9}{2}{3/1,6/2}{1}{5}{1/2,5/6,7/10,8/9}{3/1,4/2}{q^{1/2}}
+		\]
+		\caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i-1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y(3,10)$ is the rainbow vector in $M_{8}^2$ and $i=2$.
+When both the first anchor and top level rainbow arc are intact, the arc of the transposition must also exist.
+When one of these is broken, there is only one way to fix it.}
 		\label{shifted relations}
@@
 	Consider the coordinate of $R_{L,n+r-1}$ in $(1+T_1)w$.
-Using the same logic as in the proof of proposition \ref{shifted rainbow coeffs}, we note that if a basis element $\psi$ has no anchor at position $3$ and is not equal to $R_{L,n+r-2}$, $(1+T_1)\psi\not\sim R_{L,n+r-1}$.
+By the exact same logic as in the proof of proposition \ref{shifted rainbow coeffs}, we note that the only basis elements sent to $R_{L,n+r-1}$ by action of $(1+T_1)$ are itself and $R_{L,n+r-2}$.
 Thus the desired coordinate is equal to $(1+q)Q_{n+r-1}c+q^{1/2}Q_{n+r-2}c=-q^{1/2}Q_{n+r}c$ by lemma \ref{Q alg}.
+
 	Since $w\in K$, we must have $-q^{1/2}Q_{n+r}c=0$.
-Me have that $c$ is nonzero, and we assume $q$ nonzero, and $Q_{n+r}$ is zero iff $q$ is a root of $q^{n+r}+...+1$, implying $e|n+r+1$.
+We have that $c$ is nonzero, and we assume $q$ nonzero, and $Q_{n+r}$ is zero iff $q$ is a root of $q^{n+r}+...+1$, implying $e|n+r+1$.
 Thus we have arrived at contradiction, and $K=0$.
@@
  	Suppose $\psi(1)=a$.
-The proof is structured as follows: use proposition \ref{shifted rainbow coeffs} to find the coefficient of the basis element with $\lfloor a/2\rfloor$ humps then a rainbow element; use the same proposition in a reversed manner to find the coefficient of the basis element consisting of the rainbow for the first $a$ nodes, then the rainbow for the final $2n+r-a$ nodes; finally, we finish the proof through induction using lemma \ref{sub-matching isomorphism}.
+The proof is structured as follows: use proposition \ref{shifted rainbow coeffs} to find the coefficient of the basis element with $\lfloor a/2\rfloor$ length two arcs then a rainbow element; use the same proposition in a reversed manner to find the coefficient of the basis element consisting of the rainbow for the first $a$ nodes, then the rainbow for the final $2n+r-a$ nodes; finally, we finish the proof through induction using lemma \ref{sub-matching isomorphism}.
 
@@
 The coordinate of $R_2$ is $Q_4Q_3$.
-Generally, $R_i$ is the element with $i$ humps then a rainbow element, and has coordinate $Q_{n+r-1}...Q_{n+r-i}$.}
+Generally, $R_i$ is the element with $i$ length two arcs then a rainbow element, and has coordinate $Q_{n+r-1}...Q_{n+r-i}$.}
  	\end{figure}
@@
 
- 		Me will prove this equality through yet another inductive proof, this time inducting on the number of top level humps, including the leftmost anchor.
+ 		Me will prove this equality through yet another inductive proof, this time inducting on the number of top level arcs, including the leftmost anchor.
 

### 2019-07-31 tex/comments/3-nat-comments.tex
Revisions through p12

@@
 
-  Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of $m$. 
+  Let $\brk{m}_q = 1 + q + \dots + q^{m-1}$ be the $q$-number of the positive integer $m$. 
   Let $e$ be the smallest positive integer such that $\brk{e}_q = 0$, and set $e = \infty$ if no such integer exists.
@@
   The Hecke algebra is also well-known to be connected to the representation theory of the general linear group over a finite field \cite{Mathas-book}.
-  It is a classical result that $\SH$ is semisimple precisely when $e > 2n + r$, in which case the irreducible representations of $\SH$ are given by \emph{Specht modules} $S^\lambda$, which are indexed by the partitions $\lambda$ of $2n + r$.
+  It is a classical result that $\SH$ is semisimple precisely when $e > 2n + r$, in which case the irreducible representations of $\SH$ are given by \emph{Specht modules} $S^\lambda$, which are indexed by the partitions $\lambda$ of $2n + r$ \cite{Mathas-book}.
 
@@
   This set is indexed by the partitions $\lambda \vdash n$ which are $e$-restricted \cite{Murphy1,Murphy2}.
-
   These representations $D^\lambda$ have explicit constructions, but many of their properties are unknown.
@@
   The cellular basis for $S^\lambda$ and associated basis for $D^\lambda$ are complicated and often computationally intractable.
-  We aim to give simple graphical realizations of $S^\lambda$ and $D^\lambda$ in some cases that $\lambda = (n+r,n)$ is a partition of two parts.
+  We aim to give simple graphical realizations of $S^\lambda$ and $D^\lambda$ in some cases that $\lambda = (n+r,n)$ is a partition of two parts (henceforth called \emph{two-row partitions};
   These realizations behave in an intuitive and computationally simple way.
 
-  \vspace{5pt}
-  Throughout this paper, we analyze the \emph{two-row partitions} $(n+r,n) \vdash 2n + r$ and their corresponding modules $S^{(n+r,n)}$ and $D^{(n+r,n)}$.
   \begin{remark}
-    Note that we follow the convention of Murphy--Kleshchev concerning the correspondence $\lambda \leftrightarrow S^\lambda$, which is dual to the conventions of Dipper--James--Mathas;
+    We follow the convention of Murphy--Kleshchev concerning the correspondence $\lambda \leftrightarrow S^\lambda$, which is dual to the conventions of Dipper--James--Mathas;
     one may translate our results to the latter convention by transposing all partitions \cite{Kleshchev,Mathas-book,Murphy1}. 
@@
 
-  We will use the \emph{crossingless matchings representation}, originally defined by Khovanov \cite{Khovanov, Khovanov-tangle, Khovanov-abelian}, to realize the Specht modules of two-row partitions.
-  These crossingless matchings representations have found applications to knot theory and geometric representation theory.
-
-  In his seminal paper \cite{Khovanov-tangle}, Khovanov constructs a categorification of the crossingless matchings representation as modules over the ``arc algebra'' given by applying a certain 2-dimensional topological quantum field theory (given by the cohomology of the 2-sphere) to all possible concatenations of crossingless matchings.
-  Khovanov then uses this to categorify the Jones polynomial of a tangle by associating to any tangle the chain homotopy class of a certain complex of bimodules over these arc algebras.
-  For a survey of categorification, including the Khovanov's categorification of the crossingless matchings representation, see \cite{Khovanov-abelian}.
-
-  Further, in \cite{Khovanov}, Khovanov proves that the center of the arc algebra is isomorphic as a grading ring to the cohomology of the Springer fiber of complete flags in $\CC^{2n}$ stabilized by a fixed nilpotent operator with two Jordan blocks of size $n$ (corresponding to the two parts of the partition).
+  We will use the \emph{crossingless matchings representation}, first defined by Khovanov \cite{Khovanov, Khovanov-tangle, Khovanov-abelian}, to realize the Specht modules of two-row partitions.
+  These crossingless matchings representations have found applications in both knot theory not geometric representation theory.
+
+  In the seminal paper \cite{Khovanov-tangle}, Khovanov constructs a categorification of the crossingless matchings representation as modules over a certain \emph{arc algebra} given by applying a certain 2-dimensional topological quantum field theory (specified via the cohomology of the 2-sphere) to all possible concatenations of crossingless matchings in the plane.
+  Khovanov then uses this to categorify the Jones polynomial of a tangle by associating to any tangle the chain homotopy class of a certain complex of bimodules over the arc algebra.
+  A generalization of the arc algebra was further studied by Brundan--Stroppel in \cite{Brundan-1,Brundan-2,Brundan-3,Brundan-4}, yielding similar results to the original case.
+  For a survey of abelian categorification, including the Khovanov's categorification of the crossingless matchings representation, see \cite{Khovanov-abelian}.
+
+  Further, in \cite{Khovanov} Khovanov proves that the center of the arc algebra is isomorphic as a graded ring to the cohomology of the Springer fiber of complete flags in $\CC^{2n}$ stabilized by a fixed nilpotent operator with two Jordan blocks of size $n$ (corresponding to the two rows of the partition $(n,n)$).
   Moreover, this isomorphism is equivariant with respect to the natural actions of the symmetric group $S_{2n}$ on each ring.
+  In \cite{Stroppel}, Stroppel extended this to an isomorphism between the entire arc algebra and the endomorphism ring of a full projective-injective module in the principal block of the parabolic category $\mathcal{O}$ corresponding to the same two-part partition $(n,n)$.
 
@@
     Define a \emph{crossingless matching on $2n + r$ nodes and $r$ anchors} to be an isotopy class of $n + r$ non-intersecting paths in the slice $\RR \times \brk{0,1}$ connecting $2n + r$ distinct points of $\RR \times \cbr{0}$ and $r$ points of $\RR \times \cbr{1}$ such that none of the latter points are connected.
-  Let $M_{2n + r}^r$ have basis given by these matchings.
+  Let $M_{2n + r}^r$ be the $k$-vector space with a basis given by these matchings.
   This is illustrated in Figure \ref{S5 Basis}.
@@
 
-  We endow $M_{2n + r}^r$ with an action by specifying $(1 + T_i)w_j$ for any basis element $w_j$ of $M_{2n + r}$, as illustrated in Figure \ref{Action}.
+  We endow $M_{2n + r}^r$ with an $\SH$-action by specifying $(1 + T_i)w_j$ for any basis element $w_j$ of $M_{2n + r}$, as illustrated in Figure \ref{Action}.
   We do so by concatenating in ``vertical lines'' below each point other than the $i$th and $(i+1)$st, concatenating paths between the $i$th and $(i+1)$st points as well as points below them, removing any ``loops'' this forms, and taking the isotopy class of the resultant diagram;
@@
 
-  A more explicit definition is given in Appendix \ref{Explicit Definition} and we verify that this is well-defined in Appendix \ref{Cross Relations}.
   \end{definition}
@@
 
-  We will prove the following theorem on irreducibility of $M_{2n + r}^r$.
+  A more explicit definition for $M_{2n + r}^r$ is given in Appendix \ref{Explicit Definition} and we verify that this is well-defined in Appendix \ref{Cross Relations}.
+  In Section \ref{Crossingless Matchings Section}, we will prove the following theorem on irreducibility of $M_{2n + r}^r$.
   \begingroup
@@
     Suppose $e > n + r + 1$.
-    Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
+    Then, $M_{2n + r}^r \cong S^{(n+r,n)}$.
   \end{customthm}
@@
   \endgroup
-  We will go on to prove Corrollary \ref{n+r+1 composition series}, which specifies a composition series for $M_{2n + r}^r$ for the case $e = n + r + 1$.
-
-  This proves a graphical characterization of $S^\lambda \simeq D^\lambda$ in many cases.
+  We will go on to prove Corollary \ref{n+r+1 composition series}, which specifies a composition series for $M_{2n + r}^r$ for the case $e = n + r + 1$.
+
+  This proves a graphical characterization of $S^\lambda \cong D^\lambda$ in many cases.
   However, when $S^\lambda$ is reducible, the crossingless matchings representations cannot provide a graphical realization of the irreducible quotients $D^\lambda$;
@@
   For convenience set $m := 2n + r$.
-  The following is essentially a rescaling of Shor--Jordan's Fibonacci representation of the braid group \cite{Shor}.
-
-  {\color{orange} Literature goes here.}
+
+  In \cite{Shor}, Shor--Jordan originally defined a rescaled version of the following representation, called the \emph{Fibonacci representation}, and showed that the trace of a subrepresentation of this is the Jones polynomial of the trace closure of a braid on $m$ strands evaluated at a fifth root of unity;
+  they used this to show that evaluating a certain approximation of this polynomial is a complete problem for the ``cone clean quibit'' complexity class of quantum computers.
+  The Shor--Jordan fibonacci representation is itself a rescaling of a more general representation of the braid group, named the \emph{path model representation}, defined in \cite{Aharonov}.
+
+  \begin{remark}
+    The path model representation of \cite{Aharonov} is defined for $\ell$th any primitive root of unity $\text{exp}\prn{2 \pi i/\ell} \in \CC$.
+    This gives a potential extension of our work to include realizations of $D^{(n+r,n)}$ at more general $e$ and $r$.
+  \end{remark}
 
@@
 
-  We endow $V^m$ with an $\SH$-action which acts on a basis vector in a manner which depends only on bits $i,i+1,i+2$, sending each basis vector to a combination of other basis vectors agreeing on characters $1,\dots,i,i+2,\dots,n+1$ as follows:
+  We endow $V^m$ with an $\SH$-action which acts on a basis vector in a manner depending only on characters $i,i+1,i+2$, sending each basis vector to a combination of other basis vectors agreeing on characters $1,\dots,i,i+2,\dots,n+1$ as follows:
 
@@
   Note that the action $T_i$ does not modify characters $i,i+2$, so characters $1$ and $n+1$ are preserved by $\SH$.
-  Hence the representation $V^m$ contains four subrepresentations spanned by strings with beginning and ending with specified characters.
-  Label the subrepresentation spanned by strings $(\vs\dots\vs)$ by $V_{\vs\vs}$, $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$.
+  Hence the representation $V^m$ contains four subrepresentations spanned by strings beginning and ending with specified characters.
+  Label the subrepresentation spanned by strings $(\vs\dots\vs)$ by $V_{\vs\vs}$, and similar for $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$.
   We prove the following theorem.
@@
     \begin{align*}  
-      \emph{$V^{2n}_{\vs\vs}$} &\simeq D^{(n,n)},\\ 
-      \emph{$V^{2n-1}_{\vs\vs}$} &\simeq D^{(n+1,n-2)},\\
-      \emph{$V^{2n}_{\vs\vp}$} &\simeq D^{(n+1,n-1)},\\
-      \emph{$V^{2n-1}_{\vs\vp}$} &\simeq D^{(n,n-1)}.
+      \emph{$V^{2n}_{\vs\vs}$} &\cong D^{(n,n)},\\ 
+      \emph{$V^{2n-1}_{\vs\vs}$} &\cong D^{(n+1,n-2)},\\
+      \emph{$V^{2n}_{\vs\vp}$} &\cong D^{(n+1,n-1)},\\
+      \emph{$V^{2n-1}_{\vs\vp}$} &\cong D^{(n,n-1)}.
     \end{align*}
@@
   In Section \ref{Specht Modules Section} we give corollaries to standard theorems concerning Specht modules.
-  First, James-Mathas provide a sharp characterization of the irreducibility $S^\lambda$ for $\lambda \vdash 2n + r$ which is $e$-regular, called the \emph{Carter criterion} \cite[Thm.~5.42]{Mathas-book}.
+  First, James-Mathas provide a sharp characterization of the irreducibility $S^\lambda$ for $\lambda \vdash 2n + r$ an $e$-regular partition, called the \emph{Carter criterion} \cite[Thm.~5.42]{Mathas-book}.
   We specialize this to the case that $\lambda = (n+r,n)$ to give a combinatorial condition for irreducibility of $S^{(n+r,n)}$.
@@
   otherwise it depends on both $e$ and the characteristic of $k$.
-  Further, we use Kleshchev--Brundan's modular branching rules to prove our first significant statement: if $S^\lambda \simeq D^\lambda$ and $e > n$, then a particular length-2 composition series uniquely determines $\lambda$;
+  Further, we use Kleshchev--Brundan's modular branching rules to prove our first significant statement: if $S^\lambda \cong D^\lambda$ and $e > n$, then a particular length-2 composition series uniquely determines $\lambda$;
   further, an irreducible restriction to $D^{(n,n-1)}$ determines $\lambda$ as well \cite{Kleshchev, Brundan}.
@@
   \vspace{5pt}
-  In Section \ref{Crossingless Matchings Section}, we begin by proving proposition \ref{trivial kernel} concerning sign subrepresentations of $M_{2n + r}^r$ when $e \nmid n + r + 1$;
+  In Section \ref{Crossingless Matchings Section}, we begin by proving Proposition \ref{trivial kernel} concerning sign subrepresentations of $M_{2n + r}^r$ when $e \nmid n + r + 1$;
   this allows us to prove Theorem \ref{Irreducibility Theorem}.
-  Following this, we prove the existence of a particular filtration with factors given by other crossingless matchings representations;
+  Following this, we prove the existence of a particular filtration with factors isomorphic to other crossingless matchings representations;
   using irreducibility, this becomes a composition series.
@@
   \vspace{5pt}
-  In Section \ref{Sign section}, we begin by determining an explicit basis for the direct sum $K$ of all sign subrepresentations of $M$ in the case $e = n + r + 1$.
-  We prove in Theorem \ref{kernel existence} that such $K$ is nontrivial whe $e = n + r + 1$, and thereby provide an explicit composition series for such $M$ in corrolary \ref{n+r+1 composition series}.
+  In Section \ref{Sign section}, we begin by determining an explicit basis for the direct sum $K_{2n + r}^r$ of all sign subrepresentations of $M_{2n + r}^r$ in the case $e = n + r + 1$.
+  We prove in Theorem \ref{kernel existence} that such $K_{2n + r}^r$ is nontrivial when $e = n + r + 1$, and thereby provide an explicit composition series for such $M$ in Corollary \ref{n+r+1 composition series}.
   We finish the section by providing several corollaries concerning the structure of $M_{2n + r}^r$ at irreducible cases with $e < n + r + 1$.
@@
   \vspace{5pt}
-  In Section \ref{Fibonacci Section}, we begin by establishing the $2n = 2$ case of Theorem \ref{Fibonacci Theorem} for the subrepresentations of $V^2$, as well as irreducibility of $V^3_{\vs\vp}$.
+  In Section \ref{Fibonacci Section}, we begin by establishing the $2n = 2$ case of Theorem \ref{Fibonacci Theorem}, as well as irreducibility of $V^3_{\vs\vp}$.
   We then use these cases to prove that $V^m_{\vs\vp}$ and $V^m_{\vs\vs}$ are irreducible for all $m$.
   From this, we inductively prove Theorem \ref{Fibonacci Theorem}.
-  {\color{orange} Overview of Conjecture and Empirics goes here.}
 
@@
   In Appendix \ref{Algebra}, we prove a lemma concerning restrictions to various subalgebras of the Hecke algebra.
-  In Appendix \ref{Empirics Section}, we give explicit data both supporting the conjectures laid out in Section {\color{orange} reference to conjecture section} and giving explicit transitions between $M_{2n + r}^r$ and $V^{2n + r}$ and composition series of $M_{2n + r}^r$ in the case that $2n + r \leq 7$.
+  In Appendix \ref{Empirics Section}, we give explicit data both supporting the conjectures laid out in Section \ref{Conjecture Section} and giving explicit transitions between $M_{2n + r}^r$ and $V^{2n + r}$ and composition series of $M_{2n + r}^r$ in the case that $2n + r \leq 7$.
+  In Appendix {\color{orange} reference to the crossingless details section}, we develop several technical lemmas necessary for the arguments within Section \ref{Sign section}.
 
@@
 \section{Preliminaries on Specht modules}\label{Specht Modules Section}
-  For this section and the rest of the paper, assume $n > 0$.
-
-  Throughout the rest of the paper, it will be useful to have precise notation;
-  identify each partition with a tuple $\lambda = (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
+  For this section and the rest of the paper, assume $n > 0$ unless stated otherwise.
+  Throughout the rest of the paper, it will be useful to have precise notation for partitions;
+  identify each partition $\lambda \vdash 2n + r$ with a tuple $\lambda := (\lambda_1^{a_1},\dots,\lambda_l^{a_l})$ having $\lambda_i > \lambda_{i+1}$, $a_i > 0$, and $\sum_i a_i\lambda_i = 2n + r$.
   Identify each of these with a subset $\brk \lambda \subset \NN^2$ as in \cite{Kleshchev}, and define $\lambda(i) = (\lambda_1^{a_1},\dots,\lambda_{i-1}^{a_{i-1}},\lambda_i^{a_i - 1},\lambda_i-1,\lambda_{i+1}^{a_{i+1}},\dots,\lambda_l^{a_l})$ to be the partition with the $i$th row removed.
@@
   In the following subsection, we cite a theorem of James--Mathas which precisely characterizes the irreducibility of $S^\lambda$ in the case that $\lambda$ is $e$-regular, and we specialize this result to the case of two-row Specht modules.
-  This falls into two cases: either $e > n$, where $S^{(n+r,n)}$ is irreducible iff $e \nmid r+2,\dots,n+r+1$, or $e \leq n$, where the irreducibility of $S^{(n+r,n)}$ is more complicated and depends also on the characteristic of $k$.
+  This falls into two cases: either $e > n$, where $S^{(n+r,n)}$ is irreducible iff $e \nmid r+2,\dots,n+r+1$, or $e \leq n$ where the irreducibility of $S^{(n+r,n)}$ is more complicated and depends also on the characteristic of $k$.
   We will focus primarily on the former case.
@@
     \begin{enumerate}[label={(\roman*)}]
-      \item $S^{\lambda} \simeq D^{\lambda}$.
+      \item $S^{\lambda} \cong D^{\lambda}$.
       \item $\lambda$ is $e$-regular and $S^\lambda$ is irreducible.
@@
   \begin{proof}
-    Our initial assumption on $e$ implies that $\lambda$ is $e$-regular, which we will use below.
+    Our initial assumption on $e$ implies that $\lambda$ is $e$-regular, which enables us to use Theorem \ref{Mathas Irreducibility} below.
 
     \textbf{(i)}
-    Note that $\nu_p(h) \neq -1$ for all naturals $h$ and only hook lengths in the top row may vanish mod $e$ by Figure \ref{Hooks};
-    hence we may equivalently prove that $e$ divides no hook lengths in the leftmost $n$ columns of the second row by Theorem \ref{Mathas Irreducibility}.
+    Note that $\nu_p(h) \neq -1$ for all natural numbers $h$ and only hook lengths in the top row may vanish mod $e$ by Figure \ref{Hooks};
+    hence we may equivalently prove that $e$ divides no hook lengths in the leftmost $n$ columns of the top row by Theorem \ref{Mathas Irreducibility}.
     These hook lengths are precisely $r + 2,\dots,n+r+1$.
@@
     \textbf{(ii)}
-    Note that we have $\nu_{e,p}\prn{h^\lambda_{2,n-e+1}} \neq -1$, and $\nu_{e,p}\prn{h^\lambda_{2,n+r}} = -1$ so $\nu_{e,p}$ acquires at least two values.
     Suppose that $e \nmid r + 1$.
@@
   From part (i) we see that irreducibility at $e > n$ is not dependent on $p$, and we may cover many modular cases without reference to the characteristic of $k$.
-  We will finish our discussion of irreducibility of $S^\lambda$ via sharp characterization of the $e \leq n$ case.
+  We will finish our discussion of irreducibility of $S^\lambda$ via sharp characterization of the $e \leq n$ case for large $p$.
   \begin{corollary}
@@
   \begin{proof}
-    This follows from the proof of Corollary \ref{S irreducibility} part (ii) and the fact that $\nu_p(h) = \nu_p(h')$ for all naturals $h,h'$. 
-  \end{proof}
+    This follows from the proof of Corollary \ref{S irreducibility} part (ii) and the fact that $\nu_p(h) = \nu_p(h')$ for all natural numbers $h,h'$. 
+  \end{proof}
+
   \subsection{Branching theorems for Specht modules}
@@
   for these, we will use the facts that 1 is always normal and that $j$ is normal when $\beta_\lambda(i,j) \not\equiv 0 \pmod e$ for all $i \leq j$.
-  Further, we will use that $j$ is good if and only if $j$ is normal and $\gamma_\lambda(j,j') \not\equiv 0 \pmod e$ for all $j' \geq j$ normal \cite{Brundan,Kleshchev}.
+  Further, we will use the definition that $j$ is good if and only if $j$ is normal and $\gamma_\lambda(j,j') \not\equiv 0 \pmod e$ for all $j' \geq j$ normal \cite{Brundan,Kleshchev}.
   When $\lambda(i) = \mu$ for $i$ normal, write $\mu \xrightarrow{\text{normal}} \lambda$, and similar in the good case.
@@
   The following statements, collectively known as \emph{modular branching rules} of $D^\lambda$, were originally written by Kleshchev for Specht modules of the group algebra $k\brk{S_n}$, then generalized to the Hecke algebra case by Brundan \cite{Kleshchev,Brundan}.
-  They entirely characterize the socle of $\Res D^\lambda$, as well as semisimplicity od $\Res D^\lambda$.
+  They combinatorially characterize the socle and semisimplicity of $\Res D^\lambda$.
   \begin{theorem}[Kleshchev-Brundan]
@@
       \Homarg{\SH'}{S^\mu,\Res D^\lambda} 
-      &\simeq \begin{cases}
+      &\cong \begin{cases}
         k & \text{if }\mu \xrightarrow{\text{normal}} \lambda,\\
@@
       \Homarg{\SH'}{D^\mu,\Res D^\lambda} 
-      &\simeq \begin{cases}
+      &\cong \begin{cases}
         k & \text{if } \mu \xrightarrow{\text{good}} \lambda,\\
@@
   \[
-    \Res D^{(m^\ell)} \simeq D^{(m^{\ell-1},m-1)}.
+    \Res D^{(m^\ell)} \cong D^{(m^{\ell-1},m-1)}.
   \]
@@
     \[
-      \soc\prn{\Res \, D^{(n+r,n)}} \simeq \begin{cases}
+      \soc\prn{\Res \, D^{(n+r,n)}} \cong \begin{cases}
         D^{(n + r - 1,n)} & \text{if }e \mid r+2\\
@@
   Now that we've characterized how $D^\lambda$ restrict, we can describe how strongly these restrictions characterize irreducibles.
-  Namely, we will prove that some $D^\lambda$ having the same composition series as  $D^{(n+r,n)}$ is sufficient to determine that $\lambda = (n+r,n)$ in the case that condition (i) of Corollary \ref{S irreducibility} holds and either $r \neq 0$ or $e \neq 4$.
+  Namely, we will prove that some $D^\lambda$ having the same composition series as  $D^{(n+r,n)}$ is sufficient to determine that $\lambda = (n+r,n)$ in a slightly more restricted case than (i) of Corollary \ref{S irreducibility}.
   \begin{proposition}\label{Combinatorics}
@@
         \end{equation}
-        with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)} \simeq D^{(n+r,n)}$, then $\lambda = (n+r,n)$.
-      \item Suppose $r = 0$, suppose $e \nmid 4$, and suppose $D^{(n,n-1)} \simeq \Res \, D^\lambda$.
+        with factor $\Res \, D^{\lambda} / D^{(n+r-1,n)} \cong D^{(n+r,n)}$, then $\lambda = (n+r,n)$.
+      \item Suppose $r = 0$, suppose $e \nmid 4$, and suppose $D^{(n,n-1)} \cong \Res \, D^\lambda$.
         Then $\lambda = (n,n)$. 
@@
 
-    If $\varpi$ or $\varsigma$ are not $e$-regular, then $D^\varpi = 0$ or $D^\varsigma = 0$, and we may immediately rule these out;
+    If $\varpi$ or $\varsigma$ are not $e$-regular, then $D^\varpi \cong 0$ or $D^\varsigma \cong 0$, and we may immediately rule these out;
     henceforth assume that these are each $e$-regular.
@@
     \item Suppose $r = 2$.
-      Then, we have the restriction \[\Res \, D^\varsigma \simeq D^{(n+1,n)},\] as $\varsigma = (n+1,n+1)$ has tworows of the same length.
+      Then, we have the restriction \[\Res \, D^\varsigma \cong D^{(n+1,n)},\] as $\varsigma = (n+1,n+1)$ has two rows of the same length.
       This contradicts \eqref{D Composition Series}. 
@@
   if $\lambda = \varsigma$, then we have that \[\beta_\varsigma(1,2) = 4 \equiv 0 \pmod e,\] a contradiction.
-  Hence $\lambda = \mu$.
+  Hence $\lambda = \mu$, completing the proof.
 \end{proof}
@@
 \section{Crossingless matchings and Specht modules}\label{Crossingless Matchings Section}
-In this section, we analyze the crossingless matchings representation $M := M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \simeq S^{(n+r,n)}$ under certain conditions in $e$.
+In this section, we analyze the crossingless matchings representation $M := M_{2n + r}^r$ with the goal of proving $M_{2n + r}^r \cong S^{(n+r,n)}$ under certain conditions in $e$.
 We begin by proving that $M_{2n + r}^r$ contains no subrepresentations isomorphic to the sign representation (henceforth referred to as \emph{sign subrepresentations}) when $e \nmid n + r + 1$.
@@
   \begin{enumerate}[label={(\roman*)}]
-    \item $M_2^0 \simeq S^{(2)}$,
-    \item $M_r^r \simeq S^{(1^r)}$.
+    \item $M_2^0 \cong S^{(2)}$,
+    \item $M_r^r \cong S^{(1^r)}$.
   \end{enumerate}
@@
 \begin{proof}
-  (i) follows from the fact that $(1 + T_1)w = (1 + q)w$, and hence $T_1w = qw$ for any nonzero vector $w \in M_2^0$.
-  Similarly, (ii) follows from the fact that $(1 + T_i)w = 0$, so $T_iw = -w$ for any $i$ and any $w \in M_r^r$.
-\end{proof}
-In particular, Lemma \ref{Base cases} is the base case in an inductive proof that $M_{2n + r}^r \simeq S^{(n+r,n)}$ whenever $e > n + r + 1$.
-
-\subsection{Sign subrepresentations when $e\nmid n+r+1$}
+  Note that, for any $w \in M_2^0$, we have $(1 + T_1)w = (1 + q)w$, implying $T_1w = qw$ and proving (i).
+  Similarly, for any $w \in M_2^2$, we have $(1 + T_1)w = 0$, implying $T_1w = -w$ and proving (ii).
+\end{proof}
+In particular, Lemma \ref{Base cases} is the base case in an inductive proof that $M_{2n + r}^r \cong S^{(n+r,n)}$ whenever $e > n + r + 1$.
+Before arguing this, we begin by analyzing sign subrepresentations of $M_{2n + r}^r$.
+
+\subsection{Sign subrepresentations for $e\nmid n+r+1$}
 \label{kernel}
@@
 \subsection{Irreducibility of the crossingless matchings representation}
-We will first give a lemma on cyclic vectors.
+In this subsection, we will first give a lemma on cyclic vectors.
 Then, we will use triviality of $K$ to ``project down'' onto a copy of $M := M_{2n + r}^r$ with strictly fewer nodes;
@@
 \begin{proof}
-  {\color{magenta} I will address the missing part tomorrow.}
-  We have already proven this in the $r = 0$ case, so suppose that $r > 0$.
-
+  Take some basis vector $w_j \in M_{2n + r}^r$.
+  We will first prove that $w_j$ is cyclic in the case $r = 0$, then move on to the case $r > 0$.
+
+  Suppose $r = 0$ and $w$ has arcs $(1,b)$ and $(a,b-1)$.
+  Then, $q^{-1/2}(1 + T_{b-1})w_j$ is a basis vector containing arc $(1,a)$ with $a < b$ as by the left mapping as follows:
+  \[
+    \Action{6}{1/4, 2/3, 5/6}{3}{1/2, 3/4, 5/6}{q^{1/2}}; \hspace{20pt} 
+    \Action{6}{1/4, 2/3, 5/6}{4}{1/6, 2/3, 4/5}{q^{1/2}}. 
+  \]
+  Similarly, if $w$ has arc $(b+1,c)$, $q^{-1/2}(1 + T_b)w_j$ is a basis vector containing $(1,c)$ with $c > b$ by the right mapping above.
+  Using these, we may iteratively ``reduce'' each arc to have length 2 and thus generate the vector with all length-2 arcs.
+  Then, we may ``expand'' each arc to generate an arbitrary crossingless matching;
+  this generates the basis of $M_{2n + r}^r$, so it generates all of $M_{2n + r}^r$.
+
+  Now, suppose $r > 0$.
   Note that, between anchors at indices $a<a'$ having no anchor at index $b$ with $a < b < a'$, the $M_{a'-a}^0$ case allows us to generate the basis vector with all length-2 arcs between $a,a'$ and identical arcs/anchors outside of this sub-matching.
@@
   \]
-  such that $S^{t,\lambda} / S^{t-1,\lambda} \simeq S^{\lambda(t)}$ for all $1 \leq t \leq \ell$.\qed
+  such that $S^{t,\lambda} / S^{t-1,\lambda} \cong S^{\lambda(t)}$ for all $1 \leq t \leq \ell$.\qed
 \end{theorem}
@@
      \end{equation}
-     with $\Res M_{2n + r}^r / M_{2n + r - 1}^{r-1} \simeq M_{2n + r - 1}^{r + 1}$. 
+     with $\Res M_{2n + r}^r / M_{2n + r - 1}^{r-1} \cong M_{2n + r - 1}^{r + 1}$. 
     \item
@@
       \begin{equation}
-        M_{2n - 1}^1 \simeq \Res M_{2n}^0. \label{0 Restriction}
+        M_{2n - 1}^1 \cong \Res M_{2n}^0. \label{0 Restriction}
        \end{equation}
@@
   Suppose $e > n + r + 1$.
-  Then, $M_{2n + r}^r \simeq S^{(n+r,n)}$.
+  Then, $M_{2n + r}^r \cong S^{(n+r,n)}$.
 \end{theorem}
@@
 
-  We will prove this inductively; the base case $2n + r = 2$ is implied by \ref{Base cases}, so suppose that $M_{2n + s}^s \simeq S^{(m+s,s)}$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$, so that $e > m + s + 1$.
+  We will prove this inductively; the base case $2n + r = 2$ is implied by \ref{Base cases}, so suppose that $M_{2n + s}^s \cong S^{(m+s,s)}$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$, so that $e > m + s + 1$.
 
   Suppose $r > 0$.
-  By Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$.
+  By Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \cong D^\lambda$ for some $e$-restricted partition $\lambda$.
   By the inductive hypothesis and Corollary \ref{S irreducibility}, we have a composition series given by the short exact sequence
@@
   Now suppose $r = 0$ and $e \neq 4$.
-  Similarly, by Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \simeq D^\lambda$ for some $e$-restricted partition $\lambda$, and by the inductive hypothesis and Corollary \ref{S irreducibility}, we have the irreducible restriction $\Res D^\lambda \simeq D^{(n,n-1)}$.
+  Similarly, by Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \cong D^\lambda$ for some $e$-restricted partition $\lambda$, and by the inductive hypothesis and Corollary \ref{S irreducibility}, we have the irreducible restriction $\Res D^\lambda \cong D^{(n,n-1)}$.
   Then, the theorem is given by Proposition \ref{Combinatorics} (ii).
@@
   We've already proven the $n = 1$ case via the trivial representation, so suppose $n = 2$.
-  Then, from the proof of Proposition \ref{Combinatorics}, we know that $M_{4}^0 \simeq D^\lambda$, where $\lambda \in \cbr{(n,n), (n+1,n-1)}$.
-  We have already proven that $M_4^2 \simeq D^{(n+1,n-1)}$, and we may verify that $\dim M_4^0 = 2 \neq 3 = \dim M_4^2$, so we have that $\lambda = (n,n)$ and the theorem is proven for $e = 4$.
+  Then, from the proof of Proposition \ref{Combinatorics}, we know that $M_{4}^0 \cong D^\lambda$, where $\lambda \in \cbr{(n,n), (n+1,n-1)}$.
+  We have already proven that $M_4^2 \cong D^{(n+1,n-1)}$, and we may verify that $\dim M_4^0 = 2 \neq 3 = \dim M_4^2$, so we have that $\lambda = (n,n)$ and the theorem is proven for $e = 4$.
 \end{proof}
@@
  Recall $K:=K^r_{2n+r}$, defined in section \ref{kernel}, is the direct sum of all sign subrepresentations.
-In the previous section, we were not able to prove $M_{2n+r}^r\simeq S^{(n+r,n)}$ for $e=n+r+1$ because we could not assume $K=0$.
+In the previous section, we were not able to prove $M_{2n+r}^r\cong S^{(n+r,n)}$ for $e=n+r+1$ because we could not assume $K=0$.
 In particular, our proof of irreducibility failed.
@@
  \begin{conjecture}\label{Final conjecture}
- 	For any $e,n,r$, we have $M_{2n + r}^r \simeq S^{(n+r,n)}$.
+ 	For any $e,n,r$, we have $M_{2n + r}^r \cong S^{(n+r,n)}$.
  \end{conjecture}
@@
 We will start our study of the Fibonacci representation $V := V^m$ by studying low-dimensional cases.
-Recall that we have decomposed $V$ into a direct sum of the subrepresentations $V_{\vs\vs}$, $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$, indexed by the first and last bit of the character of the strings in $V$.
+Recall that we have decomposed $V$ into a direct sum of the subrepresentations $V_{\vs\vs}$, $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$, indexed by the first and last character of the strings in $V$.
 \begin{proposition}
@@
   \begin {align*}
-    \emph{$V_{\vs\vs}^2$} &\simeq D^{(1^2)}\\
-    \emph{$V_{\vs\vp}^2$} &\simeq D^{(2)}\\
-    \emph{$V_{\vp\vp}^2$} &\simeq \emph{$V_{\vs\vs}^2 \oplus V_{\vs\vp}$}.
+    \emph{$V_{\vs\vs}^2$} &\cong D^{(1^2)}\\
+    \emph{$V_{\vs\vp}^2$} &\cong D^{(2)}\\
+    \emph{$V_{\vp\vp}^2$} &\cong \emph{$V_{\vs\vs}^2 \oplus V_{\vs\vp}$}.
   \end{align*}
@@
   Further, note that we may consider $\ima (T_1 - \vara)$ to be a subrepresentation of $\Res_{\SH(S_{m-2})}^{\SH(S_m)} V^m_{\vs\vp}$;
-  this yields that $\ima (T_1 - \vara) \simeq V^{m-2}_{\vs\vp}$ as representations.
+  this yields that $\ima (T_1 - \vara) \cong V^{m-2}_{\vs\vp}$ as representations.
   Hence irreducibility of $V^{m-2}_{\vs\vp}$ implies that $v_j$ is generated by $(T_1 - \vara)v$, and $v$ is cyclic, as desired.
@@
   \begin{align*}
-    \emph{$V^{m-1}_{\vp\vp}$} \simeq \emph{$\Res V_{\vs\vp}^m$} &\simeq \emph{$V^{m-1}_{\vs\vs} \oplus V^{m-1}_{\vs\vp}$},\\
-    \emph{$V_{\vp\vs}^{m-1} \simeq \Res V_{\vs\vs}^m$} &\simeq \emph{$V_{\vs\vp}^{m-1}$}.
+    \emph{$V^{m-1}_{\vp\vp}$} \cong \emph{$\Res V_{\vs\vp}^m$} &\cong \emph{$V^{m-1}_{\vs\vs} \oplus V^{m-1}_{\vs\vp}$},\\
+    \emph{$V_{\vp\vs}^{m-1} \cong \Res V_{\vs\vs}^m$} &\cong \emph{$V_{\vs\vp}^{m-1}$}.
   \end{align*}
@@
 \begin{proof}
-  By Lemma \ref{Fib branching} and Proposition \ref{Fib irreducibility}, we have $\Res V^m_{\vs\vs} \simeq V^{m-1}_{\vs\vp}$ is irreducible, implying that $V^m_{\vs\vs}$ is also irreducible.
+  By Lemma \ref{Fib branching} and Proposition \ref{Fib irreducibility}, we have $\Res V^m_{\vs\vs} \cong V^{m-1}_{\vs\vp}$ is irreducible, implying that $V^m_{\vs\vs}$ is also irreducible.
 \end{proof}
@@
 \[
-  V^m \simeq V^m_{\vs\vs} \oplus V^m_{\vs\vp} \oplus V^m_{\vp\vs} \oplus V^m_{\vp\vp}.
+  V^m \cong V^m_{\vs\vs} \oplus V^m_{\vs\vp} \oplus V^m_{\vp\vs} \oplus V^m_{\vp\vp}.
 \]
@@
   \[
-    \emph{$V^m \simeq 3V^m_{\vs\vp} \oplus 2V^m_{\vs\vs}$.}
+    \emph{$V^m \cong 3V^m_{\vs\vp} \oplus 2V^m_{\vs\vs}$.}
   \]\qed
@@
      \begin{align*}  
-      V^{2n}_{\vs\vs} &\simeq D^{(n,n)},\\ 
-      V^{2n-1}_{\vs\vs} &\simeq D^{(n+1,n-2)},\\
-      V^{2n}_{\vs\vp} &\simeq D^{(n+1,n-1)},\\
-      V^{2n-1}_{\vs\vp} &\simeq D^{(n,n-1)}.
+      V^{2n}_{\vs\vs} &\cong D^{(n,n)},\\ 
+      V^{2n-1}_{\vs\vs} &\cong D^{(n+1,n-2)},\\
+      V^{2n}_{\vs\vp} &\cong D^{(n+1,n-1)},\\
+      V^{2n-1}_{\vs\vp} &\cong D^{(n,n-1)}.
      \end{align*}
@@
 
-  By Proposition \ref{Fib irreducibility}, $V^{2n-1}_{\vs\vs} \simeq D^{\lambda}$ and $V^{2n-1}_{\vs\vp} \simeq D^{\mu}$ for some partitions $\lambda,\mu \vdash 2n - 1$.
+  By Proposition \ref{Fib irreducibility}, $V^{2n-1}_{\vs\vs} \cong D^{\lambda}$ and $V^{2n-1}_{\vs\vp} \cong D^{\mu}$ for some partitions $\lambda,\mu \vdash 2n - 1$.
   We will show that $\lambda = (n+1,n-2)$ and $\mu = (n,n-1)$.
 
-  First, by Lemma \ref{Fib branching} and the inductive hypothesis, we have \[\Res \; D^{\lambda} \simeq D^{(n,n-2)} \simeq \Res \; D^{(n+1,n-2)}\] and \[\Res \; D^{\mu} \simeq D^{(n,n-2)} \oplus D^{(n-1,n-1)} \simeq \Res \; D^{(n,n-1)}.\]
+  First, by Lemma \ref{Fib branching} and the inductive hypothesis, we have \[\Res \; D^{\lambda} \cong D^{(n,n-2)} \cong \Res \; D^{(n+1,n-2)}\] and \[\Res \; D^{\mu} \cong D^{(n,n-2)} \oplus D^{(n-1,n-1)} \cong \Res \; D^{(n,n-1)}.\]
 
@@
   We can perform a similar argument for the $V^{2n}$ case;
-  for $V^{2n}_{\vs\vs} \simeq D^{\lambda'}$ and $V^{2n}_{\vs\vp} \simeq D^{\mu'}$, we have
-  \[\Res \; D^{\lambda'} \simeq D^{(n,n-1)} \simeq \Res \; D^{(n,n)}\] and 
-  \[\Res \; D^{\mu'} \simeq D^{(n,n-1)} \oplus D^{(n+1,n-2)} \simeq \Res \; D^{(n+1,n-1)}.\]
+  for $V^{2n}_{\vs\vs} \cong D^{\lambda'}$ and $V^{2n}_{\vs\vp} \cong D^{\mu'}$, we have
+  \[\Res \; D^{\lambda'} \cong D^{(n,n-1)} \cong \Res \; D^{(n,n)}\] and 
+  \[\Res \; D^{\mu'} \cong D^{(n,n-1)} \oplus D^{(n+1,n-2)} \cong \Res \; D^{(n+1,n-1)}.\]
 
@@
   \begin{align*} 
-    V^{2n} &\simeq 3D^{(n+1,n-1)} \oplus 2D^{(n,n)},\\
-    V^{2n - 1} &\simeq 3D^{(n,n-1)} \oplus 2D^{(n+1,n-2).}
+    V^{2n} &\cong 3D^{(n+1,n-1)} \oplus 2D^{(n,n)},\\
+    V^{2n - 1} &\cong 3D^{(n,n-1)} \oplus 2D^{(n+1,n-2).}
   \end{align*}
@@
   \]
-  Hence, through the identification of $B$ and $B'$ via conjugation by $u$, we have $\Res_{B}^A V \simeq \Res_{B'}^A V$
+  Hence, through the identification of $B$ and $B'$ via conjugation by $u$, we have $\Res_{B}^A V \cong \Res_{B'}^A V$
 \end{proposition}
@@
   Suppose $\SH',\SH''$ are two subalgebras of $\SH(S_m)$ generated by $l$ simple reflections and $V$ is a representation of $\SH$.
-  Then, $\Res_{\SH'}^{\SH} V \simeq \Res_{\SH''}^\SH V$.
+  Then, $\Res_{\SH'}^{\SH} V \cong \Res_{\SH''}^\SH V$.
 \end{corollary}
@@
 
-It is known that, for small $e$ and $2n + r$, each Specht module $S^{(n+r,n)}$ has a composition series of length at most 2 \cite[Appendix B]{Mathas-book}
+It is known that, for small $e$ and $2n + r$, each Specht module $S^{(n+r,n)}$ has a composition series of length at most 2 \cite[Appendix B]{Mathas-book}.
 Heuristically, $M_{2n + r}^r$ does as well;
@@
 We begin by defining the following constants.
-\def\qqo{\color{magenta} \varkappa}
-\def\tto{\color{brown!80!black} \varpi}
-\def\vtv{\color{blue!70!green} \varrho}
-\def\fft{\color{black!50!green}\varsigma}
-\def\fto{\color{red!50!orange} \vartheta}
+\def\qqo{\varkappa}
+\def\tto{\eth}
+\def\vtv{\varrho}
+\def\fft{\wp}
+\def\fto{\vartheta}
 \setcounter{MaxMatrixCols}{20}
@@
 
+\begin{remark}
+  From this data, we may explicitly characterize the subrepresentation $\ima \iota_{e,n+r}^r \subset M_{2n + r}^r$;
+  this in turn explicitly characterizes the quotient map $M_{2n + r}^r \twoheadrightarrow M_{2n + r}^r/\ima \iota_{e,n+r}^r$, fully determining the data of the composition series specified by the short exact sequence
+  \[
+    0 \longrightarrow \ima \iota_{e,n+r}^r \longrightarrow M_{2n + r}^r \longrightarrow M_{2n + r}/\ima\iota_{e,n+r}^r \longrightarrow 0.
+  \]
+\end{remark}
+
 A potential extension of this work is to implement a standard basis for the Specht module (e.g.

### 2019-07-31 tex/comments/3-nat-comments.tex
Sections through p26

@@
   In particular, these admit quotients $D^\lambda$ such that the modules $\cbr{D^\lambda \mid D^\lambda \neq 0, \lambda \vdash n}$ are a pairwise-nonisomorphic list of all irreducible $\SH$-modules.
-  This set is indexed by the partitions $\lambda \vdash n$ which are $e$-restricted \cite{Murphy1,Murphy2}.
+  This set is indexed by the partitions $\lambda \vdash n$ which are $e$-regular \cite{Murphy1,Murphy2}.
   These representations $D^\lambda$ have explicit constructions, but many of their properties are unknown.
@@
   Moreover, this isomorphism is equivariant with respect to the natural actions of the symmetric group $S_{2n}$ on each ring.
-  In \cite{Stroppel}, Stroppel extended this to an isomorphism between the entire arc algebra and the endomorphism ring of a full projective-injective module in the principal block of the parabolic category $\mathcal{O}$ corresponding to the same two-part partition $(n,n)$.
+  In \cite{Stroppel}, Stroppel extended this to an isomorphism between the entire arc algebra and the endomorphism ring of a full projective-injective module in the principal block of the parabolic category $\mathcal{O}$ corresponding to the same two-part partition $(n,n) \vdash 2n$.
+  Stroppel also showed in \cite{Stroppel} that the crossingles matchings on $2n$ points and no anchors naturally label label indecomposable self-dual projective modules in the principal block of the parabolic category $\mathcal{0}$ corresponding to $(n,n)$.
+
+  Additionally, in \cite{Anno-t,Anno-tangles}, Anno--Nandakumar proved that the irreducible objects of the heart of the exotic $t$-structure on the derived category of coherent sheaves on a two-block springer fiber are naturally inexed by crossingless matchings on an Annulus.
+  The authors conjecture an ``annular'' analog of Khovanov's arc algebra as a description of the $\mathrm{Ext}$-algebra between these irreducible objects.
 
@@
   \begin{customthm}{\ref{Correspondence Theorem}}
+    If $r = 0$, suppose $e > 2$.
     Suppose $e > n + r + 1$.
@@
   Namely, we will prove that some $D^\lambda$ having the same composition series as  $D^{(n+r,n)}$ is sufficient to determine that $\lambda = (n+r,n)$ in a slightly more restricted case than (i) of Corollary \ref{S irreducibility}.
+  \newpage
   \begin{proposition}\label{Combinatorics}
@@
   We proceed by induction on $n$.
-  The base case the base case $n = 0, r \neq 0$ and $n = 1, r = 0$ follow from Lemma \ref{Base cases}.
+  The base cases $n = 0, r \neq 0$ and $n = 1, r = 0$ follow from Lemma \ref{Base cases}.
 
@@
   This may be intuitively viewed as a ``large'' version of the action connecting nodes $i-1$ and $i+2$;
-  it preserves the arc $(i,i+1)$ and the factor $q^{1/2}$ in $h_{i+1}$ gives the correct scaling.
-
-  Note that, by definition, $e \nmid r+2,\dots,n+r$ as well, and hence $(n+r-1,n-1)$ satisfies the hypotheses of the proposition as well.
+  it preserves the arc $(i,i+1)$ and the factor $q$ in $h_{i+1}$ gives the correct scaling.
+
+  Note that, by the hypothesis of the proposition, $e \nmid r+2,\dots,n+r$ and hence $(n+r-1,n-1)$ satisfies the hypotheses of the proposition as well.
   Then, by the inductive hypothesis, there is some element $h' \in \SH(S_{2(n-1) + r})$ sending $\varphi((1 + T_i)w)$ to the image of a basis vector of $M_{2n + r}^r$ via $\varphi$;
@@
 The following theorem due to Mathas \cite[Thm.~5.5]{Mathas-article} generalizes the classical branching theorem of the symmetric group.
-This result is not be necessary for our present proof of the correspondence in the case $e > n + r + 1$, but the analogy with $M$ is suggestive.
+This result is not be necessary for our proof of the correspondence in the case $e > n + r + 1$, but the analogy with $M$ is suggestive.
 \begin{theorem}[Characteristic-free classical branching theorem]
@@
 \begin{theorem}\label{Correspondence Theorem}
+  If $r = 0$ then suppose $e > 2$.
   Suppose $e > n + r + 1$.
@@
 \begin{proof}
-  The case $n = 0$ is already proven, by lemma \ref{Base cases}, so suppose $n > 0$.
+  The case $n = 0$ is already proven via lemma \ref{Base cases}, so suppose $n > 0$.
   In order to use Proposition \ref{Combinatorics}, suppose for now that either $e \nmid 4$ or $r > 0$.
 
-  We will prove this inductively; the base case $2n + r = 2$ is implied by \ref{Base cases}, so suppose that $M_{2n + s}^s \cong S^{(m+s,s)}$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$, so that $e > m + s + 1$.
+  We will prove this inductively; the base case $2n + r = 2$ is implied by Lemma \ref{Base cases}, so suppose that $M_{2n + s}^s \cong S^{(m+s,s)}$ whenever $2m + s < 2n + r$ and $m + s \leq n + r$.
+  Note that $e > m + s + 1$.
 
   Suppose $r > 0$.
-  By Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \cong D^\lambda$ for some $e$-restricted partition $\lambda$.
+  By Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \cong D^\lambda$ for some $e$-regular partition $\lambda$.
   By the inductive hypothesis and Corollary \ref{S irreducibility}, we have a composition series given by the short exact sequence
@@
   Now suppose $r = 0$ and $e \neq 4$.
-  Similarly, by Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \cong D^\lambda$ for some $e$-restricted partition $\lambda$, and by the inductive hypothesis and Corollary \ref{S irreducibility}, we have the irreducible restriction $\Res D^\lambda \cong D^{(n,n-1)}$.
+  Similarly, by Theorem \ref{Irreducibility Theorem}, we know that $M_{2n + r}^r \cong D^\lambda$ for some $e$-regular partition $\lambda$, and by the inductive hypothesis and Corollary \ref{S irreducibility}, we have the irreducible restriction $\Res D^\lambda \cong D^{(n,n-1)}$.
   Then, the theorem is given by Proposition \ref{Combinatorics} (ii).

### 2019-08-01 tex/comments/3-nat-comments.tex
Final revisions on 3-nat-comments

@@
     0 \subset K_{2n + r}^r \subset M_{2n + r}^r.
- 	\]
+ 	\]\qed
  \end{corollary}
@@
  If $\pi^{-1}(K)$ is itself a subrepresentation of $M$, then we will have identified the radical of $M_{2n + r}^r$ via Proposition \ref{Preimage of K}.
- Observing decomposition matrices for $S_{(n+r,n)}$ for small $e$ and $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two \cite[Appendix~B]{Mathas-book};
- this is give heuristic support in Appendix \ref{Empirics Section}.
+ Observing decomposition matrices for $S_{(n+r,n)}$ for small $e$ and $n$, we note that $S^{(n+r,n)}$ appears to have composition series of length at-most two \cite[~Appendix~B]{Mathas-book};
+ we give heuristic support for an analogous statement on $M_{2n + r}^r$ in Appendix \ref{Empirics Section}.
  This motivates our first conjecture:
  \begin{conjecture}\label{Preimage subrepresentation}
-   In Proposition \ref{Preimage of K}, $\pi^{-1}(K_{2n' + r}^r)$ is an irreducible subrepresentation of $M$.
+   In Proposition \ref{Preimage of K}, $\pi^{-1}(K_{2n' + r}^r)$ is an irreducible subrepresentation of $M_{2n + r}^r$.
  \end{conjecture}
- This has been verified for {\color{magenta} LIST THE EXAMPLE WHICH HAS BEEN VERIFIED}.
+ This has been verified for $\pi:M_6^0 \twoheadrightarrow M_4^0$.
  In general, this is surprising;
- $\pi$ is a-priori only a linear map, so one may not expect the preimage of a subrepresentation via $\pi$ to be a subrepresentation of $M_{2n + r}^r$.
+ $\pi$ is a-priori only a linear map, so we do not expect a-priori that the preimage of a subrepresentation via $\pi$ is a subrepresentation of $M_{2n + r}^r$.
 
@@
 \section{Fibonacci representations and quotients of Specht modules}\label{Fibonacci Section}
-The irreducibility of $S^{(n+r,n)}$ plays a central role in the arguments of Section \ref{Crossingless Matchings Section};
+Irreducibility of $S^{(n+r,n)}$ plays a central role in the arguments of Section \ref{Crossingless Matchings Section};
 without irreducibility of $M_{2n + r}^r$ (which is conjecturally equivalent to irreducibility of $S^{(n+r,n)}$), $M$ is not necessarily isomorphic to any Specht module $S^\lambda$ or quotient $D^\lambda$, preventing the arguments of Section \ref{Specht Modules Section} from being used.
@@
 Note that Shor--Jordan does not characterize this representation any more than the definition and decomposition into four subrepresentations;
-we will give a characterization of this representation which is stronger than presented in \cite{Shor}.
+we will give a characterization of this representation which is stronger than presented in \cite{Shor} or its generalization in \cite{Aharonov}.
 
@@
 Recall that we have decomposed $V$ into a direct sum of the subrepresentations $V_{\vs\vs}$, $V_{\vs\vp}$, $V_{\vp\vs}$, and $V_{\vp\vp}$, indexed by the first and last character of the strings in $V$.
-\begin{proposition}
+\begin{proposition}\label{2 correspondence}
   We have the following isomorphisms of representations:
@@
   We will prove this inductively in $m$.
-  We've already proven irreducibility of $V^2_{\vs\vp}$ and $V^3_{\vs\vp}$, so suppose that $V^{m-2}_{\vs\vp}$ is irreducible.
+  We've already proven irreducibility of $V^2_{\vs\vp}$ and $V^3_{\vs\vp}$ via Propositions \ref{2 correspondence} and \ref{3 irreducibility}, so suppose that $V^{m-2}_{\vs\vp}$ is irreducible.
 
@@
 
-Now we may begin considering restrictions of Fibonacci representations:
+Now we may begin considering restrictions of Fibonacci representations as follows.
 \begin{lemma}\label{Fib branching}
@@
 \begin{remark}
-  As in \cite{Shor}, we may be consider a representation $\tilde V^m$ of the braid group on $m$ strands via Definition \ref{Fib definition}. 
-  In fact, Proposition \ref{Fib irreducibility}, Lemma \ref{Fib branching}, and Corollaries \ref{ss irreducibility} and \ref{V decomposition into V} hold in reference to $\tilde V^m$ by analogous arguments.
+  As in \cite{Shor}, we may be consider a representation $\widetilde V^m$ of the braid group on $m$ strands via Definition \ref{Fib definition}. 
+  In fact, Proposition \ref{Fib irreducibility}, Lemma \ref{Fib branching}, and Corollaries \ref{ss irreducibility} and \ref{V decomposition into V} hold in reference to $\widetilde V^m$ by analogous arguments.
 \end{remark}
@@
   We will prove this by induction on $m = 2n$;
-  we have already proven the base case $V^{2}$, so suppose that we have proven these isomorphisms for $V^{2n-2}$.
+  we have already proven the base case $V^{2}$ via Propoition \ref{2 correspondence}, so suppose that we have proven these isomorphisms for $V^{2n-2}$.
   We will prove the isomorphisms for $V^{2n-1}$ and $V^{2n}$.
@@
 
-  By irreducibility of $\Res D^{\lambda}$, the only normal number in $\lambda$ is 1.\cite{Kleshchev,Brundan}
+  By irreducibility of $\Res D^{\lambda}$, the only normal number in $\lambda$ is 1 \cite{Kleshchev,Brundan}.
   Further, the only diagrams which can be transformed into $(n,n-2)$ by removing a cell are $(n+1,n-2)$, $(n,n-1)$, and $(n,n-2,1)$ as illustrated in Figure \ref{OddRes};
@@
 We call \eqref{quadratic} the \emph{quadratic relation} and \eqref{braid1}, \eqref{braid2} the \emph{braid relations}.
-It is easily seen that a representation of $\SH$ is equivalent to a representation of the free algebra $k\langle T_i \rangle$ which are compatible with the relations.
+It is easily seen that a representation of $\SH$ is equivalent to a representation of the free algebra $k\langle T_i \rangle$ which is compatible with the relations.
+We will begin this appendix by proving a more careful definition of the representation $M_{2n + r}^r$.
 We will prove in the following sections that $V$ and $M$ are compatible with the Hecke algebra relations.
@@
 
-Let the length of an arc $(i,j)$ be $l(i,j) := j - i + 1$.
+Let the length of an arc $(i,j)$ be $j - i + 1$.
 Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
@@
   This definition gives a graphical calculus for working with our module.
-  It should be clear that, if $w_j^i$ has a loop then $w_l(i) = i+1$ and $w_l = w_j$.
+  It should be clear that, if $w_j^i$ has a loop, then $w_l(i) = i+1$ and $w_l = w_j$.
   Further, this easily defines an arbitrary composition:
@@
 
-  Note that the crossingless matchings on $2n$ indices with no anchors can all be identified with a list of $n$ integers describing the lengths of the arcs from left to right;
-  call this the \emph{increasing lexicographical order basis}.
-  Further, we have a surjection $M_{2n + 2r}^0 \twoheadrightarrow M_{2n + r}^r$ which takes basis elements to basis elements;
-  this induces an order on the basis for $M_{2n +r}^r$, which we will henceforth refer to as the \emph{induced lexicographical order basis.}
-  This basis is illustrated for $M_{5}^1$ in Figure \ref{S5 Basis}.
+We now verify that this is well-defined as a representation of $\SH$.
 
@@
   It suffices to show that $T_{i_j}T_wT_{i_j}^{-1} \in \SH''$ for $w$ a word generated by simple transpositions $s_{i_1},\dots,s_{i_{l}} \in S_m$.
-  First, note that $l(w) < l(s_{i_j}w)$, implying $T_{i_j}T_w = T_{s_{i_j}w}$ by lemma 1.12 in \cite{Mathas-book}.
+  First, note that $l(w) < l(s_{i_j}w)$, implying $T_{i_j}T_w = T_{s_{i_j}w}$ by \cite[Leb.~1.12]{Mathas-book}.
   Further, by the same lemma, we have
@@
 For the following data, set $e := 5$.
-The following data define the isomorphisms $\varphi_{2n + r}^r: M_{2n + r}^r / K_{2n + r}^r \rightarrow V_{s}^{2n + r}$ where $s = \vs\vs$ if $r \in \cbr{0,3}$ and $s = \vs\vp$ otherwise.
+The following data define the isomorphisms \[\varphi_{2n + r}^r: M_{2n + r}^r / K_{2n + r}^r \xrightarrow{\sim} V_{s}^{2n + r},\] where $s = \vs\vs$ if $r \in \cbr{0,3}$ and $s = \vs\vp$ otherwise.
 All of such computations use $q$ a primitive 5th root of unity in the algebraic extension of the Cyclotomic field $\QQ(\zeta_{10})$ by $\sqrt\tau$ \cite{Github}.
@@
 It is known that, for small $e$ and $2n + r$, each Specht module $S^{(n+r,n)}$ has a composition series of length at most 2 \cite[Appendix B]{Mathas-book}.
-Heuristically, $M_{2n + r}^r$ does as well;
-let this series be
-\[
+Heuristically, $M_{2n + r}^r$ satisfies this as well;
+when $M_{2n + r}^r$ has such a composition series, denote the series by
+\begin{equation}\label{U composition series}
   0 \subset U_{2n + r}^r \subset M_{2n + r}.
-\]
+\end{equation}
 In the following data, we specify the inclusion maps map $\iota_{e,2n+r}^r:U_{2n + r}^r \hookrightarrow M_{2n + r}^r $, which conjecturally illustrates the inclusion of the first composition factor of $S^{(n+r,n)}$ into $S^{(n+r,n)}$ for all $2n + r \leq 7$.
@@
   \[
-    0 \longrightarrow \ima \iota_{e,n+r}^r \longrightarrow M_{2n + r}^r \longrightarrow M_{2n + r}/\ima\iota_{e,n+r}^r \longrightarrow 0.
-  \]
+    0 \longrightarrow \ima \iota_{e,n+r}^r \longrightarrow M_{2n + r}^r \longrightarrow M_{2n + r}/\ima\iota_{e,n+r}^r \longrightarrow 0,
+  \]
+  i.e. \ref{U composition series}.
 \end{remark}

### 2019-08-01 tex/Drafts/Final_Draft.tex
Final Draft Yay

--- 2019-08-01 tex/comments/3-nat-comments.tex
@@
   In Appendix \ref{Empirics Section}, we give explicit data both supporting the conjectures laid out in Section \ref{Conjecture Section} and giving explicit transitions between $M_{2n + r}^r$ and $V^{2n + r}$ and composition series of $M_{2n + r}^r$ in the case that $2n + r \leq 7$.
-  In Appendix {\color{orange} reference to the crossingless details section}, we develop several technical lemmas necessary for the arguments within Section \ref{Sign section}.
 
@@
 
-\subsection{Sign subrepresentations for $e\nmid n+r+1$}
+\subsection{Sign subrepresentations when $e\nmid n+r+1$}\,
 \label{kernel}
+
+$\ $
 
@@
 
-Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively.
-Examples are pictured in \ref{shifted rainbow}.
-Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.
+\vspace{3mm}
+\begin{definition}
+	Given a rainbow element $R$, define the \emph{shifted rainbow elements} $R_{R,i},R_{L,i}$ to be those where you ``move the 'length two middle arc' across $i$ lines to the right or left, respectively." This is made clear in figure \ref{shifted rainbow}.
+Formally: $$R_{R,i}:=q^{-i/2}(1+T_{r+n+i})\cdots(1+T_{r+n+1})R$$, $$R_{L,i}:=q^{-i/2}(1+T_{r+n-i})\cdots(1+T_{r+n-1})R$$.
+\end{definition}
 
 \begin{figure}
-	\def\cbasisspacing{5mm}
-	$\cbr{
-		\begin{gathered}
-		\Matching{8}{1/8, 2/7, 3/6, 4/5}, \hspace{\cbasisspacing}
-		\Matching{8}{1/8, 2/7, 3/4, 5/6}, \hspace{\cbasisspacing}
-		\Matching{8}{1/8, 2/3, 4/7, 5/6}, \hspace{\cbasisspacing}
-		\Matching{8}{1/2,3/8,4/7,5/6}
-		\end{gathered}}$
-	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right}
+	\def\cbasisspacing{2mm}
+	\begin{adjustbox}{width=\textwidth}
+		\GeneralizedMatching{9}{2/9, 3/8, 4/7, 5/6}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
+		\GeneralizedMatching{9}{2/9, 3/8, 4/5, 6/7}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
+		\GeneralizedMatching{9}{2/9, 3/4, 5/8, 6/7}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
+		\GeneralizedMatching{9}{2/3,4/9,5/8, 6/7}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
+		\GeneralizedMatching{9}{1/2, 4/9,5/8, 6/7}{1}{3/1}{7/4}
+	\end{adjustbox}
+	\caption{$R_{L,0},...,R_{L,4}$ pictured from left to right.
+If $w\in K_{9}^1$ and $R=R_{L,0}$ has coordinate $c$ in $w$, then proposition \ref{shifted rainbow coeffs} claims $R_{L,1}$ has coordinate $Q_1$, $R_{L,2}$ has coordinate $Q_2$, etc.}
 	\label{shifted rainbow}
@@
 
-Define $Q_n:=(q^n+...+1)/q^{n/2}(-1)^n$ for $n\in \{0,1,...\}$.
-The following proposition says that, for any element in the kernel, if some basis element $y$ has coordinate $c$ in that element, and if $y$ has a rainbow sub-matching, the basis elements where you replace that sub-matching by the shifted rainbow matchings $R_{L,i}$ or $R_{R,i}$ both have coordinate $Q_ic$ in the kernel element.
+\begin{definition}
+	The following $q$-number deformation will be integral to this subsection and section \ref{Sign section}:
+
+	$$Q_n:=(-1)^n\frac{q^n+\ldots+1}{q^{n/2}} \text{ for }n \text{ a nonnegative integer}$$. 
+\end{definition}
+
+The following proposition applies to any basis element $y$ with a rainbow sub-matching.
+It says that if $y$ has coordinate $c$ in $w\in K$, then those elements $\theta_i,\phi_i$, where you replace the rainbow sub-matching with a ``shifted rainbow sub-matching" $R_{R,i}$ or $R_{L,i}$, have coordinate $Q_ic$ in $w$.
+An example is given in figure \ref{shifted rainbow}.
 
 \begin{proposition}
-	Let $w$ be an element in the kernel intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation.
+	Let $w\in K^r_{2n+r}$.
 Let $y$ be a basis element with coordinate $c$ in $w$.
-Suppose $\exists a,b$ such that $y(a,b)=R$, the rainbow element.
-Define the basis elements $\theta_i,\phi_i$ by $\theta_i(1,a-1)=\phi(1,a-1)=y(1,a-1)$, $\theta_i(b+1,2n)=\phi(b+1,2n)=y(b+1,2n)$, $\theta_i(a,b)=R_{R,i}$, $\phi_i(a,b)=R_{L,i}$ (leave $\theta_i$ or $\phi_i$ undefined for any $i$ where $R_{R,i},R_{L,i}$ are undefined, respectively).
-The coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.
+Suppose that there exist $a,b$ such that $y(a,b)$ is a rainbow sub-matching.
+Define the basis elements $\theta_i,\phi_i$ to be those elements where we replace the rainbow sub-matching with a shifted rainbow sub-matching.
+Formally: $$\theta_i(1,a-1):=\phi(1,a-1):=y(1,a-1)\text{ ,}$$
+	$$\theta_i(b+1,2n):=\phi(b+1,2n):=y(b+1,2n)\text{ ,}$$ 
+	$$\theta_i(a,b)=R_{R,i}\text{ ,}$$ $$\phi_i(a,b)=R_{L,i}\text{.}$$
+
+	We restrict $i$ in $\theta_i,\phi_i$ to be such that $R_{R,i},R_{L,i}$ are defined, respectively.
+
+	Then the coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.
 
@@
 
-\textit{Proof of lemma.}
-
-\begin{align*}
-Q_1Q_n-Q_{n-1}=&\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}\\
-=&\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}\\
-=&\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}
-\end{align*}
-
+\begin{proof}[Proof of lemma]
+	We compute:
+	\begin{align*}
+		Q_1Q_n-Q_{n-1}=&\prn{-\frac{(q+1)}{q^{1/2}}}\prn{(-1)^n\frac{(q^n+\cdots+1)}{q^{n/2}}}-(-1)^{n-1}\frac{(q^{n-1}+\cdots+1)}{q^{(n-1)/2}}\\
+		=&(-1)^{n+1}\frac{(q^{n+1}+2q^n+\cdots+2q+1)}{q^{(n+1)/2}}-(-1)^{n+1}\frac{(q^n+\cdots+q)}{q^{(n+1)/2}}\\
+		=&(-1)^{n+1}\frac{(q^{n+1}+\cdots+1)}{q^{(n+1)/2}}\\
+		=&Q_{n+1}
+	\end{align*}
+\end{proof}
 Now let us prove the proposition.
 
-\begin{proof}
-	Consider acting on $w$ by an element $(1+T_z)$.
-The coordinate of $\phi_i$ in $(1+T_z)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_z)$.
-Specifically, it will be $(1+q)c\iota+(q^1/2)\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.
-
-	Let $n:=a+b-1$ and $r$ be the number of anchors in $y(a,b)$.
-Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$.
-This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in \ref{shifted relations}.
-I claim the following:
-
-	\begin{center}
-		\textit{claim}:
-		The only basis elements $\psi$ where $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist\footnote{we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$}.
-
-	\end{center}
-
-	Note that the action of any $(1+T_z)$ on a basis element $\psi$ creates exactly two lines: an arc of length two connecting $z$ and $z+1$, and either an anchor or an arc of length $\geq 2$ connecting $\psi(z)$ and $\psi(z+1)$.\footnote{Although this fact follows directly from our definition of the representation, it will be used throughout the document, so it is important that the reader understands it.\label{two humps created}} The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.
-
-	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in \ref{shifted relations}.
-Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition.
-Me note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching.
-Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$.
-If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\psi(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor.
-All other matchings remain unchanged, so this implies $\psi=\phi_{i+1}$.
-Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\psi=\phi_{i-1}$.
-For boundary cases, note that for $\phi_0=\theta_0$, the only other basis element sent to this by the middle transposition is $\phi_1=\theta_1$.
-Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case gives no new information.
-Lastly, note that our argument was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors.
-Thus the claim is proved.
-
-	Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction:
+\vspace{1.5mm}
+\textit{\label{two humps created}Note: This proof relies on the simple fact that the action of a transposition $(1+T_i)$, assuming it does not send an element to zero, will update exactly two matches if it is changes the element.
+This follows directly from our definition of the representation, and will be integral to many proofs in this document.}
+
+\vspace{1.5mm}
+\begin{proof}
+
+	First, we will show that if we act by the transposition corresponding to the moved arc in $\phi_i$, the only basis elements sent to $\phi_i$ are $\phi_{i-1}$, $\phi_{i}$, and $\phi_{i+1}$.
+We will show that the analogous statement is true for $\theta_i$, and use this to finish the proof by induction.
+Formally:
+
+	\begin{claim*}
+		Suppose $\psi\in M_{2n+r}^r$ is a basis element.
+Take $i$ such that $\phi_i$, $\phi_{i-1}$, and $\phi_{i+1}$ are all defined.
+Let $2n'+r'$, $r'$ be the number of nodes and anchors in $y(a,b)$, respectively.
+Then $(1+T_{a-1+r'+n'/2-i})\psi\sim \phi_i$ implies $\psi=\phi_i$, $\phi_{i-1}$, or $\phi_{i+1}$.
+
+		Similarly, taking $i$ such that $\theta_i$, $\theta_{i-1}$, and $\theta_{i+1}$ are all defined, $(1+T_{a-1+r'+n'/2+i})\psi\sim \phi_i$ implies $\psi=\phi_i$, $\phi_{i-1}$, or $\phi_{i+1}$.
+	\end{claim*}
+
+	Note that $a-1+r'+n'/2-i$ is simply the starting node of the moved arc in $\phi_i$.
+
+	For the entirety of the proof of this claim, it will be instructive to reference Figure \ref{shifted relations} as an example.
+
+	It is easy to see that the action of $(1+T_{a-1+r'+n'/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\phi$.
+Suppose there exists another basis element $\psi$ sent to $\phi_i$ by the given transposition.
+Consider the arcs (or anchors) starting just inside and just outside of the moved arc in $\phi_i$: these are the arcs $(a-1+r'+n'/2-i-1,\phi_i(a-1+r'+n'/2-i-1))$ and $(a-1+r'+n'/2-i+2,\phi_i(a-1+r'+n'/2-i+2))$.
+
+	If $\psi$ contains both of these arcs, it must contain the arc $(a-1+r'+n'/2-i,a-1+r'+n'/2-i+1)$ to be a crossingless matching.
+This follows from our definition of rainbow sub-matching in definition \ref{sub-matchings}.
+Thus $\psi$ is fixed by the action of $(1+T_{a-1+r'+n'/2-i})$, so $\psi=\phi_i$.
+
+	If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r'+n'/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r'+n'/2-i})$ must create that arc/anchor.
+Thus $\psi(a-1+r'+n'/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r'+n'/2-i+1)=\phi_i(a-1+r'+n'/2-i-1)$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor.
+These matchings are identical to those of $\phi_{i+1}$, and no other matchings are changed by the action, so $\psi=\phi_{i+1}$.
+Likewise, if $\psi$ does not contain the right arc/anchor, that arc/anchor must be created by the action of $(1+T_{a-1+r'+n'/2-i})$, so $\psi=\phi_{i-1}$.
+
+	Lastly, note that the above argument was completely symmetric with respect to the parity of $i$, and hence an analogous argument without anchors handles the $\theta_i$ case. Thus the claim is proved.
+
+	\vspace{2mm}
+	As an edge case related to the claim, note that the only basis element sent to $y=\phi_0=\theta_0$ other than itself by the transposition acting on the middle of the rainbow is $\theta_1=\phi_1$ if they both exist.
+Otherwise, just $\phi_1$ exists and is sent to $y$, or the rainbow element has two nodes and neither exist.
+
+	We finish the proof of the proposition through induction:
 
@@
   This entirely characterizes $M_{2n + r}^r$ in the case that $e > n + r + 1$.
-  In the next section, we will give weaker characterizations of $M_{2n + r}^r$ in the case $e = n + r + 1$, where the representation s $M_{2n + r}^r$ and $S^{(n+r,n)}$ are reducible.
-
- \section{Sign subrepresentations}\label{Sign section}
+  Next, we will give weaker characterizations of $M_{2n + r}^r$ in the case $e = n + r + 1$, where the representations $M_{2n + r}^r$ and $S^{(n+r,n)}$ are reducible.
+
+ \section{Sign subrepresentations and possible extensions}\label{Sign section}
  Recall $K:=K^r_{2n+r}$, defined in section \ref{kernel}, is the direct sum of all sign subrepresentations.
-In the previous section, we were not able to prove $M_{2n+r}^r\cong S^{(n+r,n)}$ for $e=n+r+1$ because we could not assume $K=0$.
+In the previous section, we were not able to prove $M_{2n+r}^r\simeq S^{(n+r,n)}$ for $e=n+r+1$ because we could not assume $K=0$.
 In particular, our proof of irreducibility failed.
@@
  In this section, we prove that there is exactly one sign subrepresentation when $e=n+r+1$, thus $M_{2n+r}^r$ is reducible.
-We give an explicit basis for $K$, and explore how our approach may generalize to finding subrepresentations other $e$.
+We give an explicit basis for $K$, and explore how our approach may generalize to finding subrepresentations for other $e$.
+
+ Note that we will use notation from section \ref{kernel} freely.
 
@@
 
- First let us formalize a useful property of sub-matchings.
+ First let us formalize a useful property of sub-matchings. Namely, acting on sub-matchings is the same as acting on the corresponding matching.
 
@@
 
- 	The map is clearly bijective. Thus it is sufficient to prove the following: $$\rho(T_{i+a-1}\sigma)=T_i\rho(\sigma)$$
-
- 	As mentioned in the previous section, the action of a transposition $T_i$ can change at most 4 nodes, so we need to show that the transpositions end up changing the same nodes in the same way in  $\rho(T_{i+a-1}\sigma)$ and $T_i\rho(\sigma)$.
+ 	The map is clearly bijective. Thus it is sufficient to prove the following: $$\rho((1+T_{i+a-1})\sigma)=(1+T_i)\rho(\sigma)$$
+
+ 	As mentioned in the previous section, the action of a transposition $T_i$ can change at most 4 nodes, so we need to show that the transpositions end up changing the same nodes in the same way in  $\rho((1+T_{i+a-1})\sigma)$ and $(1+T_i)\rho(\sigma)$.
 
  	Suppose $\sigma(i+a-1)=s,\sigma(i+a)=t$.
-Then $(T_{i+a-1}\sigma)(i+a-1)=i+a$, $(T_{i+a-1}\sigma)(s)=t$, so $\rho(T_{i+a-1}\sigma)(i)=i+1$, $\rho(T_{i+a-1}\sigma)(s-a+1)=t-a+1$.
-Separately, $\rho(\sigma)(i)=s-a+1$ and $\rho(\sigma)(i+1)=t-a+1$, so $T_i\rho(\sigma)(i)=i+1$ and $T_i\rho(\sigma)(s-a+1)=t-a+1$ as desired.
+Then $((1+T_{i+a-1})\sigma)(i+a-1)=i+a$, $((1+T_{i+a-1})\sigma)(s)=t$, so $\rho((1+T_{i+a-1})\sigma)(i)=i+1$, $\rho((T_{i+a-1})\sigma)(s-a+1)=t-a+1$.
+Separately, $\rho(\sigma)(i)=s-a+1$ and $\rho(\sigma)(i+1)=t-a+1$, so $(1+T_i)\rho(\sigma)(i)=i+1$ and $(1+T_i)\rho(\sigma)(s-a+1)=t-a+1$ as desired.
 So the map is an isomorphism and the lemma is proved.
@@
  \begin{definition}
- 	Recall $Q_i:=(q^i+...+q+1)/q^{i/2}(-1)^i$ (lemma \ref{Q alg}). For $a>0$ define $Q(0,b):=1$. For $b>a>0$ define $$\Q_b^a:=\frac{Q_{b-1}...Q_{b-a}}{Q_1...Q_{a-1}}$$
+ 	Recall $Q_i:=(q^i+...+q+1)/q^{i/2}(-1)^i$ (lemma \ref{Q alg}). For $b\geq 0$, define $\Q^0_b:=1$. For $b\geq a>0$ define $$\Q_b^a:=\frac{Q_{b-1}...Q_{b-a}}{Q_0...Q_{a-1}}$$
 
@@
 
- 	I will refer to $x_\psi$ as the \textbf{coordinate function} of $\psi$.
+ 	I will refer to $x_\psi$ as the \emph{coordinate function} of $\psi$.
 
@@
 Let $w\in\cap\ker(1+T_i)$.
-MLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition \ref{rainbow nonzero}).
+WLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition \ref{rainbow nonzero}).
 Then the coordinate of any basis element $\psi\in M_{2n+r}^r$ in $w$ is $x_{\psi}(q)$.
@@
  	By proposition \ref{shifted rainbow coeffs} the element $R_1:=R_{L,n+r-1}$ has coordinate $Q_{n+r-1}$ in $w$.
-Then $R_1(3,2n+r)$ is the rainbow element in  $M_{2(n-1)+r}^r$, so the element $R_2$ defined by $R_2(1,2):=R_1(1,2)$, $R_2(3,2n+r):=R_{L,n+r-2}\in M_{2(n-1)+r}^r$ has coordinate $Q_{n-1}Q_{n-2}$.
+Then $R_1(3,2n+r)$ defines a rainbow sub-matching, and is the rainbow element in  $M_{2(n-1)+r}^r$.
+Thus we may define the element $R_2$ by $R_2(1,2):=R_1(1,2)$, $R_2(3,2n+r):=R_{L,n+r-2}\in M_{2(n-1)+r}^r$.
+By the same proposition, $R_2$ has coordinate $Q_{n-1}Q_{n-2}$ in $w$.
 Generally, define $R_i$ by $R_i(1,2(i-1)):=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r):=R_{L,n+r-i}\in M_{2(n-i+1)+r}^r$.
 Then the coefficient of $R_i$ is $Q_{n+r-1}...Q_{n+r-i}$.
-These elements are shown in figure 5.
+These elements are shown in figure \ref{hump the rainbow}.
 
@@
 The coordinate of $R_2$ is $Q_4Q_3$.
-Generally, $R_i$ is the element with $i$ humps then a rainbow element, and has coordinate $Q_{n+r-1}...Q_{n+r-i}$.}
+Generally, $R_i$ is the element with $i$ length two arcs then a rainbow element, and has coordinate $Q_{n+r-1}...Q_{n+r-i}$.}
+ 		\label{hump the rainbow}
  	\end{figure}
 
- 	Now define basis elements $E_i$ by $E_i(2i+1,2n+r):=R_i(2i+1,2n+r)$, $E_i(1,2i):=R$, the appropriate rainbow element.
+ 	Now define the basis elements $E_i$ to be those basis elements that can be split into two rainbow sub-representations between nodes $2i$ $2i+1$, the first of which has no anchors.
+Formally, they are defined by $E_i(2i+1,2n+r):=R_i(2i+1,2n+r)$, $E_i(1,2i):=R\in M_{2i}^0$.
 By the same argument as above, if $E_i$ has coordinate $c$ in $w$, $R_i$ has coordinate $Q_{i-1}...Q_{1}c$.
-One way to make this more clear is to consider intermediate basis elements $\sigma_j^{E_i}$ defined by $\sigma_j^{E_i}(2i+1,2n+r):=E_i(2i+1,2n+r)$ and $\sigma_j^{E_i}(1,2i):=R_{L,j}$.
-Then the coordinates of $\sigma_j^{E_i}(2i+1,2n+r)$ in terms of the coordinate $c$ of $E_i$ are $Q_{i-1}...Q_{i-j}$, and $R_i=\sigma_{i-1}^{E_i}$.
+To see this, note that $E_i$ by definition has rainbow sub-matchings $E_i(1,2i)$, so we may apply proposition $\ref{shifted rainbow coeffs}$ to that sub-matching and, as above, sequentially move middle arcs out of the rainbow.
+We will eventually reach the point where our rainbow sub-matching only has two nodes, and the basis element that we arrive at has all length two arcs and then a rainbow element starting at node $2i+1$.
+This basis element is $R_i$.
+It is easiest to see this in figure \ref{kernel induct characterization example}.
 
@@
 
- 	Note that the above logic only uses proposition \ref{shifted rainbow coeffs}, which requires only that a sub-matching be a rainbow element.
-So, suppose some basis element $\sigma$ has sub-matching $\sigma(s,t)=R$ with $n'$ nodes and $r'$ anchors, and that the coordinate of $\sigma$ in $w$ is $c$.
-Then it follows that the basis element $\theta_i$ defined by $\theta_i(1,s-1):=\sigma(1,s-1)$, $\theta_i(t+1,2n+r):=\sigma(t+1,2n+r)$, and $\theta_i(s,t):=E_i$ has coefficient $\Q^i_{n'+r'}c$.
-In other words, defining $Y_\psi$ with respect to the sub-matching $\sigma(s,t)$, the operation of finding the coordinate of $E_i$ given the coordinate of $R=\sigma(s,t)$ commutes with the isomorphism to $Y_\psi$.
+ 	Note that the above logic only uses proposition \ref{shifted rainbow coeffs}, which requires only that the basis element has a rainbow sub-matching.
+So, suppose some basis element $\sigma$ has rainbow sub-matching $\sigma(s,t)=R$ with $n'$ nodes and $r'$ anchors, and that the coordinate of $\sigma$ in $w$ is $c$.
+Then it follows that the basis element $\vartheta_i$ defined by $\vartheta_i(1,s-1):=\sigma(1,s-1)$, $\vartheta_i(t+1,2n+r):=\sigma(t+1,2n+r)$, and $\vartheta_i(s,t):=E_i$ has coefficient $\Q^i_{n'+r'}c$.
+In other words, defining $Y_\sigma$ with respect to the rainbow sub-matching $\sigma(s,t)$, the operation of finding the coordinate of $E_i$ given the coordinate of $R=\sigma(s,t)$ commutes with the isomorphism to $Y_\sigma$.
 An example is given in figure \ref{kernel induct characterization example}.
+
+ 	\begin{figure}
+ 		\def\cbasisspacing{1mm}
+ 		\begin{adjustbox}{width=\textwidth}
+ 			\GeneralizedMatching{14}{1/2,5/14,6/13,7/12,8/11,9/10}{2}{3/1,4/2}{12/4}, \hspace{\cbasisspacing}
+ 			\GeneralizedMatching{14}{1/2,3/4,5/6,7/8,12/13,11/14}{2}{9/1,10/2}{12/4}, \hspace{\cbasisspacing}
+ 			\GeneralizedMatching{14}{1/2,3/8,4/7,5/6,12/13,11/14}{2}{9/1,10/2}{12/4}
+ 		\end{adjustbox}
+
+ 		\caption{The figure on the left has sub-matching $R$ ignoring the first two nodes.
+The middle figure has submatching $R_3$ ignoring the first two nodes.
+The figure on the right has sub-matching $E_3$ also ignoring the first two nodes.
+Since the first two nodes have the same structure for all elements, if the coordinate of the first element is $c$, the coordinate of the second is $Q_6Q_5Q_4c$, and the coordinate of the third is $\frac{Q_6Q_5Q_4}{Q_1Q_2}c$.}
+
+ 		\label{kernel induct characterization example}
+ 	\end{figure}
 
@@
 Note that this operation commutes with any isomorphism defined by lemma \ref{sub-matching isomorphism}.
-Me may define $Y_{E_{\lfloor a/2\rfloor}}$ with respect to the sub-matching $E_{\lfloor a/2\rfloor}(2,a-1)$.
+We may define $Y_{E_{\lfloor a/2\rfloor}}$ with respect to the rainbow sub-matching $E_{\lfloor a/2\rfloor}(2,a-1)$.
 By the inductive hypothesis, we may apply the algorithm to this sub-matching and commute with the isomorphism with $Y_{E_{\lfloor a/2\rfloor}}$.
 In this way, we find that the coordinate of $\widehat{\psi}$ defined by $\widehat{\psi}(1,a):=\psi(1,a)$ and $\widehat{\psi}(a+1,2n+r)=R$ is $x_{\psi(2,a-1)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_{\widehat{\psi}}(q)$.
-Similarly, define $Y_{\widehat{\psi}}$ with respect to the sub-matching $\widehat{\psi}(a+1,2n+r)$, and commute the algorithm with the isomorphism.
+Similarly, define $Y_{\widehat{\psi}}$ with respect to the rainbow sub-matching $\widehat{\psi}(a+1,2n+r)$, and commute the algorithm with the isomorphism.
 In the same way, we obtain that the coordinate of $\psi\in Y_{\widehat{\psi}}$ is $x_{\psi(2,a-1)}(q)x_{\psi(a+1,2n+r)}(q)\Q^{\lfloor a/2\rfloor}_{n+r}=x_\psi(q)$ as desired.
@@
 Thus the inductive step holds and the proposition is proved.
-
- 	\begin{figure}
- 		\def\cbasisspacing{1mm}
- 		\begin{adjustbox}{width=\textwidth}
- 			\GeneralizedMatching{14}{3/12,4/11,5/10,6/9,7/8,13/14}{2}{1/1,2/2}{12/4}, \hspace{\cbasisspacing}
- 			\GeneralizedMatching{14}{1/2,3/4,5/6,9/12,10/11,13/14}{2}{7/1,8/2}{12/4}, \hspace{\cbasisspacing}
- 			\GeneralizedMatching{14}{1/6,2/5,3/4,9/12,10/11,13/14}{2}{7/1,8/2}{12/4}
- 		\end{adjustbox}
-
- 		\caption{The figure on the left has sub-matching $R$ ignoring the last two nodes.
-The middle figure has submatching $R_3$ ignoring the last two nodes.
-The figure on the right has sub-matching $E_3$ also ignoring the last two nodes.
-Since the last two nodes have the same structure for all elements, if the coordinate of the first element is $c$, the coordinate of the second is $Q_6Q_5Q_4c$, and the coordinate of the third is $\frac{Q_6Q_5Q_4}{Q_1Q_2}c$.}
-
- 		\label{kernel induct characterization example}
- 	\end{figure}
 
@@
 
- To verify the kernel element, we will need to know exactly which basis elements are mapped to a specific basis element by a given $(1+T_i)$. The next two lemmas help address this question.
-
- {\color{magenta} Move lemmas to a new appendix $\backslash$section.}
+ Now we must verify that the kernel element defined in proposition \ref{kernel characterization} is indeed an element of the kernel when $e=n+r+1$.
+To do this, we will need to know exactly which basis elements $\sigma$ are mapped to a specific basis element $\psi$ by a given $(1+T_i)$ for all $\psi$.
+The next two lemmas help address this question.
+
  \begin{lemma}
@@
  		\item Suppose $\psi(a)=b$ for some $b>a+1$, and that $(1+T_i)\psi=(1+q)\psi$ for some $a<i<b-1$.
-Me then have a subrepresentation $\psi(a,b)$ and define $Y_\psi$ with respect to this subrepresentation.
+We then have a subrepresentation $\psi(a,b)$ and may define $Y_\psi$ with respect to this subrepresentation.
 Then for all basis elements $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$, we have that $$\sigma\in Y_\psi$$.
 
- 		\item Suppose $\psi$ has some anchor at position $u$, and $(1+T_i)\psi=(1+q)\psi$ for some $i>u$, we again have a subrepresentation $\psi(u,2n+r)$ and define $Y_\psi$ with respect to this subrepresentation.
+ 		\item Suppose $\psi$ has some anchor at position $u$, and $(1+T_i)\psi=(1+q)\psi$ for some $i>u$.
+We again have a subrepresentation $\psi(u,2n+r)$ and may define $Y_\psi$ with respect to this subrepresentation.
 Then for all basis elements $\sigma$ such that $(1+T_i)\sigma=q^{1/2}\psi$, we have that $\sigma\in Y_\psi$ again.
@@
  \begin{proof}
- 	This lemma follows from an observation I made in section \ref{two humps created}: a transposition can only create two arcs or an arc and an anchor.
+ 	This lemma follows from a note I made in section \ref{two humps created}: a transposition can only alter two existing matchings.
 
@@
  \vspace{5mm}
- Me are now ready to prove existence of a kernel element.
-To prove this, we will show that if $w\in M_{2n+r}^r$ is as characterized above, the coordinate of any basis element in $(1+T_i)w$ is zero.
+ We are now ready to prove existence of a kernel element.
+To prove this, we will show that if $w\in M_{2n+r}^r$ is as characterized in proposition \ref{kernel characterization}, the coordinate of any basis element in $(1+T_i)w$ is zero.
 This will split into various cases related to the previous lemmas.
@@
  \begin{theorem}
- 	Suppose $e=n+r+1$. Then $\cap\ker(1+T_i)\not=0$.
+ 	Suppose $e=n+r+1$. Then $K\not=0$.
  	\label{kernel existence}
@@
 For the following proof we will need a slightly stronger inductive assumption.
-Take $\psi'\in M_{2n'+r'}^{r'}$, and suppose either that $\psi'(1)=2n'+r'$, and that $T_i\psi'=(1+q)\psi'$, $1<i<2n'+r'-1$, or that 1 is an anchor in $\psi$.
+Take $\psi'\in M_{2n'+r'}^{r'}$, and suppose either that $\psi'(1)=2n'+r'$, and that $(1+T_i)\psi'=(1+q)\psi'$, $1<i<2n'+r'-1$, or that 1 is an anchor in $\psi'$ and $(1+T_i)\psi'=(1+q)\psi'$, $1<i$.
 Defining $E_{\psi'}$ as before, we assume
@@
 
- 	Before exploring the cases, let us formally define $E_\psi$ to be the pre-image of $\psi$ under the action of $(1+T_i)$, and $E_{\psi(a,b)}$ to be the pre-image of $\psi(a,b)$ under action of $(1+T_{i-a+1})$:
-
- 	\begin{enumerate}[label={case \arabic*:}]
- 		\item Suppose $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, and that $\exists s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\psi(s)=t$.
+ 	Before exploring the cases, let us formally define $E_\psi$ to be the pre-image of $\psi$ under the action of $(1+T_i)$, and, given some sub-matching $\psi(a,b)$ where $a\leq i<b$, $E_{\psi(a,b)}$ to be the pre-image of $\psi(a,b)$ under action of $(1+T_{i-a+1})$:
+
+ 	\begin{enumerate}[label={\textit{Case \arabic*.}}]
+ 		\item Suppose $\psi\in (1+T_i)M_{2n+r}^r$ for some $i$, and that there exist $s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\psi(s)=t$.
 Also suppose the leftmost anchor is at some index $u>t$, or that there are no anchors.
@@
 
- 		Me have that $e>j$ for any $Q_j$ term appearing in the equation above, and $e>n'+r'$ for any sub-matching coordinate appearing above, so by corollary \ref{coeff nonzero}:
+ 		We have that $e>j$ for any $Q_j$ term appearing in the equation above, and $e>n'+r'$ for any sub-matching coordinate appearing above, so by corollary \ref{coeff nonzero}:
 
@@
 
- 		$$(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,t)}(q)=0$$
+ 		$$(1+q)x_{\psi(s,t)}(q)+\sum_{\sigma\in E_\psi,\sigma\not=\psi}q^{1/2}x_{\sigma(s,t)}(q)=0\text{.}$$
 
@@
  		Note that both corollary \ref{characterization generalization} and our inductive hypothesis \ref{strong kernel} still apply in this case, where we consider a left anchor instead of a matching.
-This allows the exact same logic from the proof of the first case to prove this case.
+The algebra is identical, and an analogous argument proves Case 2.
+This illustrates the isotopy shown in diagram \ref{Branching commutative diagram}.
  		\\
 
- 		It is important to note that, for both case 1 and case 2, the inductive hypothesis depends only on cases in which \ref{strong kernel} holds.
-Thus, if we show these cases rely on valid base cases, case 1 and 2 follow.
-This will be done in case 4.
+ 		It is important to note that, for both Case 1 and Case 2, the inductive hypothesis depends only on cases in which \ref{strong kernel} holds.
+Thus, if we show these cases rely on valid base cases, Case 1 and Case 2 follow.
+This will be done in Case 4.
 
@@
 Lemma \ref{preimage under nothing} characterizes all $\sigma\in E_\psi$.
-Me would like to prove the following for arbitrary $q$ where $e>n+r$:
+We would like to prove the following for arbitrary $q$ where $e>n+r$:
 
@@
  		See figure \ref{case 3} for an example of this equality.
-Note that if $e=n+r+1$, $Q_{n+r}$ is the only zero component in the right side of this equation, so proving this equation is sufficient to prove case three.
+Note that if $e=n+r+1$, $Q_{n+r}$ is the only zero component in the right side of this equation, so proving this equation is sufficient to prove Case 3.
  		\\
 
- 		Me will prove this equality through yet another inductive proof, this time inducting on the number of top level humps, including the leftmost anchor.
+ 		We will prove this equality through yet another inductive proof, this time inducting on the number of top level arcs, including the leftmost anchor.
 
